### 2019-06-06 tex/ms.tex
first commit

\documentclass[modern]{aastex62}

% Load the corTeX style definitions
\input{cortex}

% Bibliography stuff
\bibliographystyle{aasjournal}

% Begin!
\begin{document}

% Title
\title{Doppler Imaging Fun}

% Author list
\author[0000-0002-0296-3826]{Rodrigo Luger}
\email{rluger@flatironinstitute.org}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
%
\author{Megan Bedell}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}

% Introduction
\section*{Placeholder}
\label{sec:intro}
%
See Figure~\ref{fig:pretty_function}.
%
\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=0.5\linewidth]{figures/pretty_function.pdf}
    \oscaption{pretty_function}{%
        This is a plot of a pretty function. And at the end of this
        caption is a symbol with a link to the \emph{exact} script
        that generated it, hosted on \textsf{GitHub}.
        \label{fig:pretty_function}
    }
    \end{centering}
\end{figure}
%

This is an equation with a ``proof'' in the form of a \textsf{Jupyter} notebook:
%
\begin{proof}{euler}
    \label{eq:euler}
    e^{i\pi} + 1 = 0.
\end{proof}
%

Check out \citet{Luger2018} and stuff.

% Bibliography
\pagebreak
\bibliography{bib}

\end{document}

### 2019-06-06 .ci/build-paper.sh

@@ -1,0 +1,28 @@
+#!/bin/bash -x
+set -e
+
+# Only trigger on regular commits
+if [ "$TRAVIS_PULL_REQUEST" = "false" ]
+then
+
+    # Let's build the paper!
+    echo "Building the paper..."
+    cd $TRAVIS_BUILD_DIR/tex && make
+
+    # Create a temporary directory and initialize
+    # an empty repo with a single file: the compiled PDF
+    mkdir -p travis && cd travis
+    mv ../ms.pdf .
+    git init
+    git add -f ms.pdf
+
+    # Force push this to the [branch_name]-pdf branch on GitHub
+    git status
+    git -c user.name='travis' -c user.email='travis' commit -m "building the paper"
+    git status
+    git push -f https://$GITHUB_USER:$GITHUB_API_KEY@github.com/$TRAVIS_REPO_SLUG HEAD:$TRAVIS_BRANCH-pdf >/dev/null 2>&1
+
+    # Return to top level
+    cd $TRAVIS_BUILD_DIR
+
+fi

### 2019-06-06 tex/ms.tex
added some equations

@@
 
-% Introduction
-\section*{Placeholder}
-\label{sec:intro}
 %
-See Figure~\ref{fig:pretty_function}.
+\section{Introduction}
+Check out \citet{Luger2019} and \citet{Bedell2019} and stuff.
+
 %
-\begin{figure}[h!]
-    \begin{centering}
-    \includegraphics[width=0.5\linewidth]{figures/pretty_function.pdf}
-    \oscaption{pretty_function}{%
-        This is a plot of a pretty function. And at the end of this
-        caption is a symbol with a link to the \emph{exact} script
-        that generated it, hosted on \textsf{GitHub}.
-        \label{fig:pretty_function}
-    }
-    \end{centering}
-\end{figure}
+\section{The equation}
+\label{sec:the_equation}
+
+In the most general form, the Doppler-shifted intensity observed at wavelength $\lambda$ at
+position $x, y$ on the surface of the star at time $t$ is
 %
+\begin{align}
+    I(\lambda, \beta, x, y, t) &=
+        I\big(\lambda, 0, x, y, t\big) \nonumber \\
+        &+ \frac{\mathrm{d}I(\lambda, \beta, x, y, t)}{\mathrm{d}\beta} \Big|_{\beta=0} \Delta\beta(x, y) \nonumber \\
+        &+ \frac{\mathrm{d}^2I(\lambda, \beta, x, y, t)}{\mathrm{d}\beta^2} \Big|_{\beta=0} \Delta\beta^2(x, y) \nonumber \\
+        &+ ...
+\end{align}
+%
+where $\beta \equiv \frac{v}{c}$ is the relativistic parameter for a radial velocity $v$ on the surface.
 
-This is an equation with a ``proof'' in the form of a \textsf{Jupyter} notebook:
 % 
-\begin{proof}{euler}
-    \label{eq:euler}
-    e^{i\pi} + 1 = 0.
+\section{Differentiating the spectrum}
+\label{sec:derivatives}
+The derivatives of the spectrum $I(\lambda)$ with respect to the relativistic parameter
+$\beta$ are found by application of Fa\`a di Bruno's formula for taking high
+order derivatives of the chain rule:
+%
+\begin{proof}{faa_di_bruno}
+    \label{eq:dIdbeta}
+    \frac{\mathrm{d}^n I(\lambda, \beta)}{\mathrm{d}\beta^n} \Big|_{\beta=0} &=
+    \sum_{k=1}^n \frac{\mathrm{d}^k I(\lambda_0)}{\mathrm{d}\lambda_0^k} \Big|_{\lambda_0=\lambda} \lambda^k P_{nk}
 \end{proof}
 %
-
-Check out \citet{Luger2018} and stuff.
+where
+%
+\begin{proof}{faa_di_bruno}
+    \label{eq:Pnk}
+    P_{nk} \equiv B_{n, k}\Bigg( \Big\{(-1)^j j! \Big\}_{j=1}^{n - k + 1} \Bigg)
+\end{proof}
+%
+and $B_{n, k}$ is the incomplete Bell polynomial. The quantity
+$\frac{\mathrm{d}^k I(\lambda_0)}{\mathrm{d}\lambda_0^k} \Big|_{\lambda_0=\lambda}$
+is just the $k^\mathrm{th}$ derivative of the spectrum with respect to wavelength in the
+rest frame, and must either be inferred from the data or computed numerically
+from the spectrum.
 

### 2019-06-07 tex/ms.tex
added probably david hogg
more words

--- 2019-06-06 tex/ms.tex
@@
 \affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
+%
+\author{Probably David W. Hogg}
+\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
 
-% Introduction
-\section*{Placeholder}
-\label{sec:intro}
 %
-See Figure~\ref{fig:pretty_function}.
+\section{Introduction}
+Check out \citet{Luger2019} and \citet{Bedell2019} and stuff.
+
 %
-\begin{figure}[h!]
-    \begin{centering}
-    \includegraphics[width=0.5\linewidth]{figures/pretty_function.pdf}
-    \oscaption{pretty_function}{%
-        This is a plot of a pretty function. And at the end of this
-        caption is a symbol with a link to the \emph{exact} script
-        that generated it, hosted on \textsf{GitHub}.
-        \label{fig:pretty_function}
-    }
-    \end{centering}
-\end{figure}
+\section{Uniform surfaces}
+\label{sec:uniform surfaces}
+
+Let $I(\lambda, x, y)$ be the Doppler-shifted intensity observed at wavelength $\lambda$ at
+position $x, y$ on the surface of the star. We may express it as
 %
+\begin{align}
+    \label{eq:IntensityUnif}
+    I(\lambda, x, y) &= I_0\Big(\mathcal{D}^{-1}_{\beta(x, y)}(\lambda)\Big)
+\end{align}
+%
+where $I_0$ is the (spatially uniform) spectrum in the original, unshifted frame
+and 
+%
+\begin{align}
+    \mathcal{D}^{-1}_{\beta(x, y)}(\lambda) &= \frac{\lambda}{1 + \beta(x, y)} \nonumber \\
+                                            &\equiv \lambda_0
+\end{align}
+%
+is the non-relativistic \emph{inverse} Doppler operator, which takes as input the shifted (observed)
+wavelength $\lambda$ and returns the unshifted wavelength $\lambda_0$.
+The quantity
+%
+\begin{align}
+    \beta(x, y) &= \frac{v(x, y)}{c}
+\end{align}
+%
+is the ratio of the radial velocity $v(x, y)$ at a point on the
+surface to the speed of light.
 
-This is an equation with a ``proof'' in the form of a \textsf{Jupyter} notebook:
+If we Taylor expand Equation~(\ref{eq:IntensityUnif}) about $\beta = 0$, we obtain
 %
-\begin{proof}{euler}
-    \label{eq:euler}
-    e^{i\pi} + 1 = 0.
+\begin{align}
+    \label{eq:TaylorUnifExplicit}
+    I(\lambda, x, y) 
+        &=
+        I_0(\lambda_0) \Bigg|_{\beta=0}
+        + 
+        \frac{\mathrm{d}I_0(\lambda_0)}{\mathrm{d}\beta} \Bigg|_{\beta=0} \Delta\beta(x, y)
+        + 
+        \frac{\mathrm{d}^2I_0(\lambda_0)}{\mathrm{d}\beta^2} \Bigg|_{\beta=0} \Delta\beta(x, y)^2
+        +
+        ... 
+\end{align}
+%
+The derivatives of the spectrum $I_0(\lambda_0)$ with respect to
+$\beta$ are found by application of Fa\`a di Bruno's formula for taking high
+order derivatives of the chain rule:
+%
+\begin{proof}{faa_di_bruno}
+    \label{eq:dIdbeta}
+    \frac{\mathrm{d}^n I_0(\lambda_0)}{\mathrm{d}\beta^n} \Bigg|_{\beta=0} &=
+    \sum_{k=1}^n \frac{\mathrm{d}^k I(\lambda_0)}{\mathrm{d}\lambda_0^k} \lambda_0^k P_{nk}
 \end{proof}
 %
+where
+%
+\begin{proof}{faa_di_bruno}
+    \label{eq:Pnk}
+    P_{nk} \equiv B_{n, k}\Bigg( \Big\{(-1)^j j! \Big\}_{j=1}^{n - k + 1} \Bigg)
+\end{proof}
+%
+is an integer computed from the incomplete Bell polynomial $B_{n, k}$.
+Given this result, and noting that $\lambda_0 = \lambda$ when $\beta = 0$,
+we may re-write Equation~(\ref{eq:TaylorUnifExplicit}) as
+%
+\begin{align}
+    \label{eq:TaylorUnifSum}
+    I(\lambda, x, y) 
+        &=
+        I_0(\lambda)
+        + 
+        \sum_{n=1}^\infty
+            \Bigg(
+                \sum_{k=1}^n \frac{\mathrm{d}^k I(\lambda)}{\mathrm{d}\lambda^k} \lambda^k P_{nk} 
+            \Bigg)
+            \Bigg(
+                \Delta\beta(x, y)^n
+            \Bigg)
+\end{align}
+%
+Assuming we only have access to spatially unresolved spectra of the star, the quantity
+we observe is the integral of the intensity over the surface of the star, which we
+denote $S$:
+%
+\begin{align}
+    \label{eq:TaylorUnifSumIntegral}
+    S(\lambda) 
+        &=
+        \pi I_0(\lambda)
+        + 
+        \sum_{n=1}^\infty
+            \Bigg(
+                \sum_{k=1}^n \frac{\mathrm{d}^k I(\lambda)}{\mathrm{d}\lambda^k} \lambda^k P_{nk} 
+            \Bigg)
+            \Bigg(
+                \int{\Delta\beta(x, y)^n}\mathrm{d}\Omega
+            \Bigg)
+\end{align}
+%
+where $\int\mathrm{d}\Omega$ denotes the surface integral over the visible disk
+of the star.
 
-Check out \citet{Luger2018} and stuff.
+Note, importantly, that the terms in the first set of parentheses depend \emph{only} on the wavelength,
+while the terms in the second set of parentheses depend \emph{only} on the position.
+This Taylor expansion has therefore allowed us to deconvolve the effects of the Doppler
+shift from the actual spectrum of the star.
 
 % Bibliography
-\pagebreak
 \bibliography{bib}

### 2019-06-07 tex/ms.tex
line broadening

@@
 Let $I(\lambda, x, y)$ be the Doppler-shifted intensity observed at wavelength $\lambda$ at
-position $x, y$ on the surface of the star. We may express it as
+sky-projected Cartesian position $x, y$ on the surface of the star. We may express it as
 %
@@
     \frac{\mathrm{d}^n I_0(\lambda_0)}{\mathrm{d}\beta^n} \Bigg|_{\beta=0} &=
-    \sum_{k=1}^n \frac{\mathrm{d}^k I(\lambda_0)}{\mathrm{d}\lambda_0^k} \lambda_0^k P_{nk}
+    \sum_{k=1}^n \frac{\mathrm{d}^k I_0(\lambda_0)}{\mathrm{d}\lambda_0^k} \lambda_0^k P_{nk}
 \end{proof}
@@
             \Bigg(
-                \sum_{k=1}^n \frac{\mathrm{d}^k I(\lambda)}{\mathrm{d}\lambda^k} \lambda^k P_{nk} 
+                \sum_{k=1}^n \frac{\mathrm{d}^k I_0(\lambda)}{\mathrm{d}\lambda^k} \lambda^k P_{nk} 
             \Bigg)
@@
 
+As an example of an application of this equation, consider the case of a rigidly rotating,
+uniform star with equatorial velocity in units of the speed of light equal to $\beta_\mathrm{eq}$. 
+It is easy to show that in this case, $\beta(x, y) = \beta_\mathrm{eq} x$. The integrals
+in Equation~(\ref{eq:TaylorUnifSumIntegral}) are trivial to compute:
+%
+\begin{align}
+    \int{\Delta\beta(x, y)^n}\mathrm{d}\Omega = 
+        \begin{cases} 
+            0 & \quad\quad\quad\quad\quad n \, \mathrm{odd} \\
+            \beta_\mathrm{eq}\frac{\Gamma\big(\frac{n}{2} + \frac{1}{2}\big)}{\Gamma\big(\frac{n}{2} + 2\big)} & \quad\quad\quad\quad\quad n \, \mathrm{even}
+        \end{cases}
+\end{align}
+%
+so the expression for the spectrum becomes
+\begin{align}
+    \label{eq:LineBroadenedSpectrum}
+    S(\lambda) 
+        &=
+        \pi I_0(\lambda)
+        + 
+        \beta_\mathrm{eq}
+        \sum_{n\,\mathrm{even}}
+            \frac{\Gamma\big(\frac{n}{2} + \frac{1}{2}\big)}{\Gamma\big(\frac{n}{2} + 2\big)}
+            \sum_{k=1}^n 
+                \frac{\mathrm{d}^k I_0(\lambda)}{\mathrm{d}\lambda^k} \lambda^k P_{nk} 
+\end{align}
+%
+Equation~(\ref{eq:LineBroadenedSpectrum}) is the analytic expression for line broadening
+due to a rotating star.
+
 % Bibliography

### 2019-06-10 tex/gitlinks.tex
figures, typos, etc

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/602fb3b22bef0cc517cbc90c1b704498dac8234e/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/602fb3b22bef0cc517cbc90c1b704498dac8234e/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/602fb3b22bef0cc517cbc90c1b704498dac8234e/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-06-10 tex/ms.tex
woot
typo
figures, typos, etc

@@
         + 
-        \frac{\mathrm{d}^2I_0(\lambda_0)}{\mathrm{d}\beta^2} \Bigg|_{\beta=0} \Delta\beta(x, y)^2
+        \frac{1}{2}\frac{\mathrm{d}^2I_0(\lambda_0)}{\mathrm{d}\beta^2} \Bigg|_{\beta=0} \Delta\beta(x, y)^2
         +
@@
     \frac{\mathrm{d}^n I_0(\lambda_0)}{\mathrm{d}\beta^n} \Bigg|_{\beta=0} &=
-    \sum_{k=1}^n \frac{\mathrm{d}^k I_0(\lambda_0)}{\mathrm{d}\lambda_0^k} \lambda_0^k P_{nk}
+    \sum_{k=1}^n P_{nk} \frac{\mathrm{d}^k I_0(\lambda_0)}{\mathrm{d}\lambda_0^k} \lambda_0^k
 \end{proof}
@@
             \Bigg(
-                \sum_{k=1}^n \frac{\mathrm{d}^k I_0(\lambda)}{\mathrm{d}\lambda^k} \lambda^k P_{nk} 
+                \sum_{k=1}^n \frac{P_{nk}}{n!} \frac{\mathrm{d}^k I_0(\lambda)}{\mathrm{d}\lambda^k} \lambda^k
             \Bigg)
@@
 It is easy to show that in this case, $\beta(x, y) = \beta_\mathrm{eq} x$. The integrals
-in Equation~(\ref{eq:TaylorUnifSumIntegral}) are trivial to compute:
+in Equation~(\ref{eq:TaylorUnifSumIntegral}) are straightforward to compute:
 %
@@
             0 & \quad\quad\quad\quad\quad n \, \mathrm{odd} \\
-            \beta_\mathrm{eq}\frac{\Gamma\big(\frac{n}{2} + \frac{1}{2}\big)}{\Gamma\big(\frac{n}{2} + 2\big)} & \quad\quad\quad\quad\quad n \, \mathrm{even}
+            \beta_\mathrm{eq}^n\sqrt{\pi}\frac{\Gamma\big(\frac{n}{2} + \frac{1}{2}\big)}{\Gamma\big(\frac{n}{2} + 2\big)} & \quad\quad\quad\quad\quad n \, \mathrm{even}
         \end{cases}
@@
         + 
-        \beta_\mathrm{eq}
-        \sum_{n\,\mathrm{even}}
+        \sqrt{\pi}
+        \sum_{n\,\mathrm{even}>0}
+            \beta_\mathrm{eq}^n
             \frac{\Gamma\big(\frac{n}{2} + \frac{1}{2}\big)}{\Gamma\big(\frac{n}{2} + 2\big)}
             \sum_{k=1}^n 
-                \frac{\mathrm{d}^k I_0(\lambda)}{\mathrm{d}\lambda^k} \lambda^k P_{nk} 
+            \frac{P_{nk}}{n!} \frac{\mathrm{d}^k I_0(\lambda)}{\mathrm{d}\lambda^k} \lambda^k 
 \end{align}
@@
 Equation~(\ref{eq:LineBroadenedSpectrum}) is the analytic expression for line broadening
-due to a rotating star.
+due to a uniform rotating star.
+
+\begin{figure}[p!]
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/convergence.pdf}
+    \oscaption{convergence}{%
+        Fractional root mean square error on the Taylor expansion of a
+        Doppler-shifted Gaussian absorption line profile as a function of 
+        the Doppler parameter 
+        $\xi \equiv \beta / \left( \nicefrac{\sigma}{\mu}\right)$ 
+        and the order of the expansion $N$. The Taylor series
+        does not converge above $\xi \approx 3$.
+        \label{fig:convergence}
+    }
+\end{figure}
+
+\begin{figure}[p!]
+    \centering
+    \subfigure[Local absorption]{\label{fig:convergence_line:a}%
+        \includegraphics[width=2.5in]{figures/local_spectrum.pdf}}
+    \hspace{0.25in}
+    \subfigure[Disk-integrated absorption]{\label{fig:convergence_line:b}%
+        \includegraphics[width=2.5in]{figures/disk_integrated_spectrum.pdf}}
+    \oscaption{convergence}{%
+        Taylor expansion of a Doppler-shifted Gaussian absorption line
+        (orange) for different values of the Doppler parameter 
+        $\xi \equiv \beta / \left( \nicefrac{\sigma}{\mu}\right)$. 
+        The dashed black curve is the line in the rest frame, and the blue
+        curve is the shifted line computed numerically at high precision.
+        \label{fig:convergence_line}
+    }
+\end{figure}
 

### 2019-06-10 .ci/install.sh

@@ -14,18 +14,8 @@ if ! command -v conda > /dev/null; then
       conda create --yes -n test python=$PYTHON_VERSION;
       conda activate test;
       conda install tectonic;
-      conda install -c conda-forge numpy=$NUMPY_VERSION scipy matplotlib setuptools pytest pytest-cov pip;
+      conda install -c conda-forge numpy=$NUMPY_VERSION scipy matplotlib setuptools pytest pytest-cov pip sympy;
 fi
 
 # Display some debugging info
 conda info -a
-
-# DEBUG [November 2 2018]
-# Attempt to resolve issues with SSL certificate expiring for purl.org:
-# https://tectonic.newton.cx/t/how-to-use-tectonic-if-you-can-t-access-purl-org/44
-# https://github.com/tectonic-typesetting/tectonic/issues/131
-#mkdir -p $HOME/.config/Tectonic
-#cat > $HOME/.config/Tectonic/config.toml << EOL
-#[[default_bundles]]
-#url = "https://tectonic.newton.cx/bundles/tlextras-2018.1r0/bundle.tar"
-#EOL

### 2019-06-10 tex/figures/convergence.py

@@ -1,0 +1,184 @@
+"""
+Plot the convergence propoerties of the Taylor expansion
+for a rigidly rotating uniform star.
+"""
+import numpy as np
+import sympy
+from sympy import *
+from sympy.stats import *
+import matplotlib.pyplot as plt
+
+
+# Initialize SymPy
+print("Using sympy version", sympy.__version__)
+#init_session(quiet=True)
+s_I0, s_lam, s_mu, s_sigma, s_amp, s_beta = \
+    symbols(r'I_0 \lambda \mu \sigma A \beta')
+
+
+def P(n, k):
+    """
+    Return the incomplete Bell polynomial needed to compute
+    D/Dbeta.
+    
+    """
+    if k > n:
+        return 0
+    series = [(-1) ** j * factorial(j) for j in range(1, n - k + 2)]
+    return bell(n, k, series)
+
+
+def _S(N=10, integrated=True):
+    """
+    Return the Nth order approximation to the disk-integrated 
+    spectrum as a SymPy expression.
+    
+    """
+    # The rest frame line profile
+    s_I0 = 1 - s_amp * exp(-Rational(1, 2) * (s_lam - s_mu) ** 2 / s_sigma ** 2)
+
+    # The higher order terms
+    SN = 0
+    
+    if integrated:
+        n_range = range(2, N + 1, 2)
+    else:
+        n_range = range(1, N + 1)
+    
+    for n in n_range:
+        sum_k = 0
+        for k in range(1, n + 1):
+            sum_k += s_lam ** k * P(n, k) * diff(s_I0, s_lam, k)
+        if integrated:
+            beta_term = (sqrt(pi) / pi) * s_beta ** n * \
+                gamma(Rational(n, 2) + Rational(1, 2)) / gamma(Rational(n, 2) + 2)
+        else:
+            beta_term = s_beta ** n
+        SN += beta_term * sum_k / factorial(n)
+    
+    # Return
+    return s_I0 + SN
+
+
+def S(lam, beta=0, mu=0.5, sigma=0.001, amp=1.0, N=10, integrated=True):
+    """
+    Return the disk-integrated spectrum as numpy array,
+    computed using the Taylor expansion.
+    
+    """
+    if beta == 0:
+        N = 0
+    args = (s_lam, s_mu, s_sigma, s_amp, s_beta)
[…]

### 2019-06-12 tex/ms.tex
doing stuff in log space

--- 2019-06-07 tex/ms.tex
@@
 
-Let $I(\lambda, x, y)$ be the Doppler-shifted intensity observed at wavelength $\lambda$ at
-position $x, y$ on the surface of the star. We may express it as
+Let $I(\xi, x, y)$ be the Doppler-shifted intensity observed at log wavelength $\xi \equiv \ln\lambda$ at
+sky-projected Cartesian position $x, y$ on the surface of the star. We may express it as
 %
@@
     \label{eq:IntensityUnif}
-    I(\lambda, x, y) &= I_0\Big(\mathcal{D}^{-1}_{\beta(x, y)}(\lambda)\Big)
+    I(\xi, x, y) &= I_0(\xi_0)
 \end{align}
@@
 \begin{align}
-    \mathcal{D}^{-1}_{\beta(x, y)}(\lambda) &= \frac{\lambda}{1 + \beta(x, y)} \nonumber \\
-                                            &\equiv \lambda_0
+    \xi_0 &= \xi - \alpha(x, y)
 \end{align}
 %
-is the non-relativistic \emph{inverse} Doppler operator, which takes as input the shifted (observed)
-wavelength $\lambda$ and returns the unshifted wavelength $\lambda_0$.
-The quantity
+is the log wavelength in the unshifted frame. The quantity $\alpha$ is
+computed from the formula for the relativistic Doppler shift and is equal to
 %
 \begin{align}
-    \beta(x, y) &= \frac{v(x, y)}{c}
+    \alpha(x, y) &\equiv \frac{1}{2}\ln\left( \frac{1 - \nicefrac{v}{c}}{1 + \nicefrac{v}{c}} \right)
 \end{align}
 %
-is the ratio of the radial velocity $v(x, y)$ at a point on the
-surface to the speed of light.
+where $v = v(x, y)$ is the radial velocity at a point on 
+the surface of the star and $c$ is the speed of light.
 
-If we Taylor expand Equation~(\ref{eq:IntensityUnif}) about $\beta = 0$, we obtain
+If we Taylor expand Equation~(\ref{eq:IntensityUnif}) about $\alpha = 0$, we obtain
 %
@@
     \label{eq:TaylorUnifExplicit}
-    I(\lambda, x, y) 
+    I(\xi, x, y) 
         &=
-        I_0(\lambda_0) \Bigg|_{\beta=0}
+        I_0(\xi_0) \Bigg|_{\alpha=0}
         + 
-        \frac{\mathrm{d}I_0(\lambda_0)}{\mathrm{d}\beta} \Bigg|_{\beta=0} \Delta\beta(x, y)
+        \frac{\mathrm{d}I_0(\xi_0)}{\mathrm{d}\alpha} \Bigg|_{\alpha=0} \Delta\alpha(x, y)
         + 
-        \frac{\mathrm{d}^2I_0(\lambda_0)}{\mathrm{d}\beta^2} \Bigg|_{\beta=0} \Delta\beta(x, y)^2
+        \frac{1}{2}\frac{\mathrm{d}^2I_0(\xi_0)}{\mathrm{d}\alpha^2} \Bigg|_{\alpha=0} \Delta\alpha(x, y)^2
         +
@@
 %
-The derivatives of the spectrum $I_0(\lambda_0)$ with respect to
-$\beta$ are found by application of Fa\`a di Bruno's formula for taking high
-order derivatives of the chain rule:
+The derivatives of the spectrum $I_0(\xi_0)$ with respect to
+$\alpha$ are computed by repeated application of the chain rule:
 %
-\begin{proof}{faa_di_bruno}
-    \label{eq:dIdbeta}
-    \frac{\mathrm{d}^n I_0(\lambda_0)}{\mathrm{d}\beta^n} \Bigg|_{\beta=0} &=
-    \sum_{k=1}^n \frac{\mathrm{d}^k I(\lambda_0)}{\mathrm{d}\lambda_0^k} \lambda_0^k P_{nk}
-\end{proof}
+\begin{align}
+    \frac{\mathrm{d}^nI_0(\xi_0)}{\mathrm{d}\alpha^n} &=
+    (-1)^n\dfrac{\mathrm{d}^nI_0(\xi_0)}{\mathrm{d}\xi_0^n}
+\end{align}
 %
-where
-%
-\begin{proof}{faa_di_bruno}
-    \label{eq:Pnk}
-    P_{nk} \equiv B_{n, k}\Bigg( \Big\{(-1)^j j! \Big\}_{j=1}^{n - k + 1} \Bigg)
-\end{proof}
-%
-is an integer computed from the incomplete Bell polynomial $B_{n, k}$.
-Given this result, and noting that $\lambda_0 = \lambda$ when $\beta = 0$,
+Given this result, and noting that $\xi_0 = \xi$ when $\alpha = 0$,
 we may re-write Equation~(\ref{eq:TaylorUnifExplicit}) as
@@
     \label{eq:TaylorUnifSum}
-    I(\lambda, x, y) 
+    I(\xi, x, y) 
         &=
-        I_0(\lambda)
+        I_0(\xi)
         +
         \sum_{n=1}^\infty
-            \Bigg(
-                \sum_{k=1}^n \frac{\mathrm{d}^k I(\lambda)}{\mathrm{d}\lambda^k} \lambda^k P_{nk} 
-            \Bigg)
-            \Bigg(
-                \Delta\beta(x, y)^n
-            \Bigg)
+            \frac{(-1)^n}{n!}
+            \frac{\mathrm{d}^nI_0(\xi)}{\mathrm{d}\xi^n}
+            \Delta\alpha(x, y)^n
 \end{align}
-%
-Assuming we only have access to spatially unresolved spectra of the star, the quantity
-we observe is the integral of the intensity over the surface of the star, which we
-denote $S$:
-%
-\begin{align}
-    \label{eq:TaylorUnifSumIntegral}
-    S(\lambda) 
-        &=
-        \pi I_0(\lambda)
-        + 
-        \sum_{n=1}^\infty
-            \Bigg(
-                \sum_{k=1}^n \frac{\mathrm{d}^k I(\lambda)}{\mathrm{d}\lambda^k} \lambda^k P_{nk} 
-            \Bigg)
-            \Bigg(
-                \int{\Delta\beta(x, y)^n}\mathrm{d}\Omega
-            \Bigg)
-\end{align}
-%
-where $\int\mathrm{d}\Omega$ denotes the surface integral over the visible disk
-of the star.
-
-Note, importantly, that the terms in the first set of parentheses depend \emph{only} on the wavelength,
-while the terms in the second set of parentheses depend \emph{only} on the position.
-This Taylor expansion has therefore allowed us to deconvolve the effects of the Doppler
-shift from the actual spectrum of the star.
 

### 2019-06-13 tex/gitlinks.tex
fourier

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/602fb3b22bef0cc517cbc90c1b704498dac8234e/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/602fb3b22bef0cc517cbc90c1b704498dac8234e/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/602fb3b22bef0cc517cbc90c1b704498dac8234e/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/cba15d33e05edc9c1ec10bdfddd599457165a3d7/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/cba15d33e05edc9c1ec10bdfddd599457165a3d7/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/cba15d33e05edc9c1ec10bdfddd599457165a3d7/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-06-13 tex/ms.tex
fourier

@@
 
-Let $I(\xi, x, y)$ be the Doppler-shifted intensity observed at log wavelength $\xi \equiv \ln\lambda$ at
-sky-projected Cartesian position $x, y$ on the surface of the star. We may express it as
+Let $I(\xi, x, y)$ be the Doppler-shifted intensity observed at log wavelength 
+$\xi \equiv \ln\lambda$ at sky-projected Cartesian position $x, y$ on the 
+surface of the star. We may express it as
 %
@@
 %
-where $I_0$ is the (spatially uniform) spectrum in the original, unshifted frame
-and 
+where $I_0$ is the (spatially uniform) spectrum in the original, unshifted 
+frame and 
 %
 \begin{align}
+    \label{eq:xi0}
     \xi_0 &= \xi - \alpha(x, y)
@@
 is the log wavelength in the unshifted frame. The quantity $\alpha$ is
-computed from the formula for the relativistic Doppler shift and is equal to
+computed from the formula for the Doppler shift and is equal to
 %
 \begin{align}
-    \alpha(x, y) &\equiv \frac{1}{2}\ln\left( \frac{1 - \nicefrac{v}{c}}{1 + \nicefrac{v}{c}} \right)
+    \alpha(x, y) 
+        &=
+        \frac{1}{2}\ln\left( 
+            \frac{1 - \beta}{1 + \beta} 
+        \right) \nonumber \\
+        &\approx
+        \ln(1 - \beta)
 \end{align}
 %
-where $v = v(x, y)$ is the radial velocity at a point on 
-the surface of the star and $c$ is the speed of light.
+where $\beta = v(x, y) / c$ is the ratio of the 
+radial velocity at a point on 
+the surface of the star to the speed of light. We assume the
+$z$-axis points toward the observer, so positive values of $v$ correspond
+to blueshifts.
 
-If we Taylor expand Equation~(\ref{eq:IntensityUnif}) about $\alpha = 0$, we obtain
+A common approach to computing the Doppler-shifted spectrum is to
+evaluate the spectrum at the rest frame wavelength (Equation~\ref{eq:xi0})
+and interpolate back to the grid in $\xi$. This is practical when
+computing the spectrum at a single \emph{point} on the surface, but not
+ideal when one is interested in the \emph{integral} over the entire
+surface, which is typically what we can observe. The standard approach is
+to discretize the surface of the star with a fine grid, evaluate the
+Doppler-shifted spectrum in each cell, and sum over the spatial axes
+to approximate the integral. Depending on the resolution of the grid,
+this is either numerically inaccurate or computationally inefficient 
+(and often both).
+
+\subsection{Linearizing the Doppler operator}
+\label{sec:taylor}
+
+One way to improve upon this could be to linearize the Doppler operator via
+a Taylor expansion in $\alpha$ about $\alpha=0$:
 %
@@
         + 
-        \frac{\mathrm{d}I_0(\xi_0)}{\mathrm{d}\alpha} \Bigg|_{\alpha=0} \Delta\alpha(x, y)
+        \frac{\mathrm{d}I_0(\xi_0)}{\mathrm{d}\alpha} \Bigg|_{\alpha=0} 
+            \Delta\alpha(x, y)
         + 
-        \frac{1}{2}\frac{\mathrm{d}^2I_0(\xi_0)}{\mathrm{d}\alpha^2} \Bigg|_{\alpha=0} \Delta\alpha(x, y)^2
+        \frac{1}{2}\frac{\mathrm{d}^2I_0(\xi_0)}{\mathrm{d}\alpha^2} 
+            \Bigg|_{\alpha=0} \Delta\alpha(x, y)^2
         +
@@
 %
-\begin{align}
+\begin{proof}{Taylor}
     \label{eq:TaylorUnifSum}
@@
             \Delta\alpha(x, y)^n
+\end{proof}
+%
+The utility of this expression is that the spatial dependence of the spectrum
+is now entirely encoded in the terms $\Delta\alpha(x, y)^n$, which is
+\emph{independent of wavelength}. The surface integral of 
+Equation~(\ref{eq:TaylorUnifSum}) is therefore far easier to compute, since
+it is the integral of a \emph{scalar} function that could even be approximated
+analytically for some choice of the velocity field $\alpha(x, y)$.
+
+In practice, however, Equation~(\ref{eq:TaylorUnifSum}) is impractical for
+two reasons. First, it requires knowledge of high order derivatives of the 
+spectrum, which may not always be easy or convenient to compute. Second, and
+more important, the series expansion is typically extremely slow to converge
+and is therefore only practically useful in the limit that the Doppler shift
+is much smaller than the typical width of a spectral line; see the notebook
+link next to Equation~(\ref{eq:TaylorUnifSum}) for an example.
+
+\subsection{Taking the Fourier transform}
+\label{sec:fourier}
+
+A much better approach is to consider what happens when we take the
+Fourier transform of the spectrum $I(\xi, x, y)$, defined as
+%
+\begin{align}
+    \label{eq:FT}
+    \hat{I}(k, x, y)
+    \equiv
+    \mathcal{F}\Big[I(\xi, x, y)\Big](k) 
+    =
+    \int_{-\infty}^\infty
+        I(\xi, x, y)
+        \mathrm{e}^{-2\pi i k \xi} \mathrm{d}\xi
 \end{align}
+%
+where $k$ is the transformed independent variable in units 
+of inverse log wavelength. The utility of this transform is
+that it effectively linearizes the Doppler operator, since
+the Fourier transform of the translation of a function is
+simply a linear scaling of the Fourier transform of the
+original function. Specifically, if the Doppler-shifted spectrum 
+is given by
+%
+\begin{align}
+    I(\xi, x, y) &= I_0\big(\xi - \alpha(x, y)\big) \quad,
+\end{align}
+%
+its Fourier transform is equal to
+%
+\begin{align}
+    \hat{I}(\xi, x, y) &= \mathrm{e}^{-2\pi i k \alpha(x, y)}\hat{I_0}(k)
+\end{align}
+%
 

### 2019-06-13 tex/figures/convergence.py

@@ -1,186 +1,0 @@
-"""
-Plot the convergence propoerties of the Taylor expansion
-for a rigidly rotating uniform star.
-"""
-import numpy as np
-import sympy
-from sympy import *
-from sympy.stats import *
-import matplotlib.pyplot as plt
-
-
-# Initialize SymPy
-print("Using sympy version", sympy.__version__)
-#init_session(quiet=True)
-s_I0, s_lam, s_mu, s_sigma, s_amp, s_beta = \
-    symbols(r'I_0 \lambda \mu \sigma A \beta')
-
-
-def P(n, k):
-    """
-    Return the incomplete Bell polynomial needed to compute
-    D/Dbeta.
-    
-    """
-    if k > n:
-        return 0
-    series = [(-1) ** j * factorial(j) for j in range(1, n - k + 2)]
-    return bell(n, k, series)
-
-
-def _S(N=10, integrated=True):
-    """
-    Return the Nth order approximation to the disk-integrated 
-    spectrum as a SymPy expression.
-    
-    """
-    # The rest frame line profile
-    s_I0 = 1 - s_amp * exp(-Rational(1, 2) * (s_lam - s_mu) ** 2 / s_sigma ** 2)
-
-    # The higher order terms
-    SN = 0
-    
-    if integrated:
-        n_range = range(2, N + 1, 2)
-    else:
-        n_range = range(1, N + 1)
-    
-    for n in n_range:
-        sum_k = 0
-        for k in range(1, n + 1):
-            sum_k += s_lam ** k * P(n, k) * diff(s_I0, s_lam, k)
-        if integrated:
-            beta_term = (sqrt(pi) / pi) * s_beta ** n * \
-                gamma(Rational(n, 2) + Rational(1, 2)) / gamma(Rational(n, 2) + 2)
-        else:
-            beta_term = s_beta ** n
-        SN += beta_term * sum_k / factorial(n)
-    
-    # Return
-    return s_I0 + SN
-
-
-def S(lam, beta=0, mu=0.5, sigma=0.001, amp=1.0, N=10, integrated=True):
-    """
-    Return the disk-integrated spectrum as numpy array,
-    computed using the Taylor expansion.
-    
-    """
-    if beta == 0:
-        N = 0
-    args = (s_lam, s_mu, s_sigma, s_amp, s_beta)
[…]

### 2019-06-13 tex/gitlinks.tex
dev version rocks

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/cba15d33e05edc9c1ec10bdfddd599457165a3d7/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/cba15d33e05edc9c1ec10bdfddd599457165a3d7/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/cba15d33e05edc9c1ec10bdfddd599457165a3d7/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/a251a86a99ed85693dc35868dff23c6c4bdf40ed/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/a251a86a99ed85693dc35868dff23c6c4bdf40ed/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/a251a86a99ed85693dc35868dff23c6c4bdf40ed/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-06-13 tex/ms.tex
dev version rocks

@@
 \section{Introduction}
+%
 Check out \citet{Luger2019} and \citet{Bedell2019} and stuff.
@@
 \label{sec:uniform surfaces}
-
+%
 Let $I(\xi, x, y)$ be the Doppler-shifted intensity observed at log wavelength 
@@
     \label{eq:xi0}
-    \xi_0 &= \xi - \alpha(x, y)
+    \xi_0 &= \xi + \alpha(x, y)
 \end{align}
@@
             \frac{1 - \beta}{1 + \beta} 
-        \right) \nonumber \\
-        &\approx
-        \ln(1 - \beta)
+        \right) 
+        %\nonumber \\
+        %&\approx
+        %\ln(1 - \beta)
 \end{align}
@@
 radial velocity at a point on 
-the surface of the star to the speed of light. We assume the
-$z$-axis points toward the observer, so positive values of $v$ correspond
-to blueshifts.
+the surface of the star to the speed of light. In keeping with the 
+literature, we assume that positive values of $v$ correspond to redshifts.
 
@@
 \label{sec:taylor}
-
+%
 One way to improve upon this could be to linearize the Doppler operator via
@@
 %
-The derivatives of the spectrum $I_0(\xi_0)$ with respect to
-$\alpha$ are computed by repeated application of the chain rule:
+Since the dependence of Equation~(\ref{eq:xi0}) on $\alpha$ is trivial,
+the derivatives of the spectrum $I_0(\xi_0)$ with respect to
+$\alpha$ are simply
 %
@@
     \frac{\mathrm{d}^nI_0(\xi_0)}{\mathrm{d}\alpha^n} &=
-    (-1)^n\dfrac{\mathrm{d}^nI_0(\xi_0)}{\mathrm{d}\xi_0^n}
+    \dfrac{\mathrm{d}^nI_0(\xi_0)}{\mathrm{d}\xi_0^n} \quad.
 \end{align}
@@
         \sum_{n=1}^\infty
-            \frac{(-1)^n}{n!}
+            \frac{1}{n!}
             \frac{\mathrm{d}^nI_0(\xi)}{\mathrm{d}\xi^n}
@@
 
-In practice, however, Equation~(\ref{eq:TaylorUnifSum}) is impractical for
+However, Equation~(\ref{eq:TaylorUnifSum}) is impractical for
 two reasons. First, it requires knowledge of high order derivatives of the 
@@
 \label{sec:fourier}
-
-A much better approach is to consider what happens when we take the
-Fourier transform of the spectrum $I(\xi, x, y)$, defined as
+%
+Recall the definition of the Fourier transform of a function $f(\xi)$,
 %
@@
     \label{eq:FT}
-    \hat{I}(k, x, y)
-    \equiv
-    \mathcal{F}\Big[I(\xi, x, y)\Big](k) 
-    =
+    \mathcal{F}\Big[f(\xi)\Big](k) 
+    &\equiv
     \int_{-\infty}^\infty
-        I(\xi, x, y)
+        f(\xi)
         \mathrm{e}^{-2\pi i k \xi} \mathrm{d}\xi
+    \nonumber \\
+    &=
+    \hat{f}(k)
+    \quad ,
 \end{align}
 %
-where $k$ is the transformed independent variable in units 
-of inverse log wavelength. The utility of this transform is
-that it effectively linearizes the Doppler operator, since
-the Fourier transform of the translation of a function is
-simply a linear scaling of the Fourier transform of the
-original function. Specifically, if the Doppler-shifted spectrum 
+and the corresponding inverse Fourier transform,
+%
+\begin{align}
+    \label{eq:IFT}
+    \mathcal{F}^{-1}\Big[\hat{f}(k)\Big](\xi) 
+    &\equiv
+    \int_{-\infty}^\infty
+        \hat{f}(k)
+        \mathrm{e}^{2\pi i k \xi} \mathrm{d}k
+    \nonumber \\
+    &=
+    f(\xi)
+    \quad .
+\end{align}
+%
+Consider what happens when we take the
+Fourier transform of the spectrum $I(\xi, x, y)$ to obtain
+a function $\hat{I}(k, x, y)$. A useful property of the
+Fourier transform is that a translation of $I(\xi, x, y)$ by
+an amount $\Delta\xi$ corresponds to a linear scaling
+of $\hat{I}(k, x, y)$ by an amount $\mathrm{e}^{-2\pi i k \Delta\xi}$
+\citep[e.g.,][]{Schoenstadt2006}.
+Specifically, if the Doppler-shifted spectrum 
 is given by
@@
 \begin{align}
-    I(\xi, x, y) &= I_0\big(\xi - \alpha(x, y)\big) \quad,
+    I(\xi, x, y) &= I_0\big(\xi + \alpha(x, y)\big) \quad,
 \end{align}
@@
 \begin{align}
-    \hat{I}(\xi, x, y) &= \mathrm{e}^{-2\pi i k \alpha(x, y)}\hat{I_0}(k)
+    \label{eq:translation}
+    \hat{I}(\xi, x, y) &= \mathrm{e}^{2\pi i k \alpha(x, y)}\hat{I_0}(k) \quad,
 \end{align}
 %
+where $\hat{I_0}(k) \equiv \mathcal{F}\left[ I_0(\xi) \right]$.
+%
+Much as in \S\ref{sec:taylor}, we have de-coupled the spatial and spectral
+terms, but this time without the need of a Taylor expansion. To obtain
+the Fourier transform of the disk-integrated spectrum, $\hat{S}$, we may 
+integrate Equation~(\ref{eq:translation})
+over the visible disk $\mathcal{S}$ of the star:
+%
+\begin{align}
+    \label{eq:integral_translation}
+    \hat{S}(k) 
+    &= 
+        \hat{I_0}(k)\iint\limits_{\mathcal{S}(x, y)}
+        \mathrm{e}^{2\pi i k \alpha(x, y)}
+        \mathrm{d}\mathcal{S}(x, y) \nonumber \\
+    &=
+        \hat{I_0}(k)\iint\limits_{\mathcal{S}(x, y)}
+        % MAGIC
+        \left( \frac{1 - \beta(x, y)}{1 + \beta(x, y)} \right) ^ {\pi i k}
+        % MAGIC
+        \mathrm{d}\mathcal{S}(x, y) \nonumber \\
+    &=
+        \hat{I_0}(k) \hat{J}(k)
+\end{align}
+%
+where we define
+%
+\begin{align}
+    \hat{J}(k) \equiv 
+        \iint\limits_{\mathcal{S}(x, y)}
+        % MAGIC
+        \left( \frac{1 - \beta(x, y)}{1 + \beta(x, y)} \right) ^ {\pi i k}
+        % MAGIC
+        \mathrm{d}\mathcal{S}(x, y)
+\end{align}
+%
+to be the surface integral of the velocity field in Fourier space.
+The disk-integrated spectrum is then obtained by applying the inverse Fourier
+transform:
+%
+\begin{align}
+    S(\xi) &= \mathcal{F}^{-1}\Big[ \hat{S}(k) \Big] \nonumber \\
+           &= \mathcal{F}^{-1}\Big[ \hat{I_0}(k) \hat{J}(k) \Big] \\
+           &= I_0(\xi) \circ J(\xi)
+\end{align}
+%
+where the last step follows from the convolution theorem, 
+with $J(\xi) \equiv \mathcal{F}^{-1}\left[ \hat{J}(k) \right]$ and $\circ$
+denoting the convolution operator.
+
+\subsubsection{Integration over the full stellar disk}
+\label{sec:full_disk}
+%
+As an example, consider the case of an unocculted, uniform star of unit
+radius with negligible limb darkening, rigidly rotating about an axis 
+perpendicular to the line of sight with equatorial angular velocity 
+$\omega_\mathrm{eq}$. The velocity profile everywhere on the surface is
+%
+\begin{align}
+    \beta(x, y) &= \frac{\omega_\mathrm{eq}}{c}x \nonumber\\
+                &\equiv \beta_\mathrm{eq} x 
+                \quad .
+\end{align}
+%
+The surface integral term may then be computed as
+%
+\begin{align}
+    \hat{J}(k) 
+    &=
+        \int_{-1}^{1}
+        \int_{-\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
+        % MAGIC
+        \left( 
+            \frac{1 - \beta_\mathrm{eq} x}
+                 {1 + \beta_\mathrm{eq} x} 
+        \right) ^ {\pi i k}
+        % MAGIC
+        \mathrm{d}y
+        \,
+        \mathrm{d}x
+        \nonumber \\[0.75em]
+    &\approx
+        \int_{-1}^{1}
+        \int_{-\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
+        % MAGIC
+        \left( 
+            1 - \beta_\mathrm{eq} x 
+        \right) ^ {2\pi i k}
+        % MAGIC
+        \mathrm{d}y
+        \,
+        \mathrm{d}x
+        \nonumber \\[0.75em]
+    &=
+        \pi \, _{2}F_{1}
+            \left(
+                -\pi i k, \, 
+                \frac{1}{2} - \pi i k; \,
+                2; \,
+                \beta_\mathrm{eq}^2
+            \right)
+    \quad ,
+\end{align}
+%
+where $_{2}F_{1}$ is the hypergeometric function. Note that
+the approximation in the second line is valid when $\beta \ll 1$
+(i.e., the non-relativistic case).
+
+The equation for the observed disk-integrated spectrum is therefore
+%
+\begin{align}
+    S(\xi) &= 
+    \pi
+    \mathcal{F}^{-1}
+    \Big[
+        \mathcal{F}(I_0)
+        \,
+        _{2}F_{1}
+        \left(
+            -\pi i k, \, 
+            \frac{1}{2} - \pi i k; \,
+            2; \,
+            \beta_\mathrm{eq}^2
+        \right)
+    \Big]
+\end{align}
+%
+Figure~\ref{fig:uniform}
+
+\begin{figure}[p!]
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/uniform.pdf}
+    \oscaption{uniform}{%
+        Hello.
+        \label{fig:uniform}
+    }
+\end{figure}
 

### 2019-06-13 tex/figures/uniform.py

@@ -1,0 +1,133 @@
+# -*- coding: utf-8 -*-
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.integrate import dblquad
+import mpmath
+
+
+def _hyp2f1(a, b, c, z):
+    """
+    The Hypergeometric function 2F1 for 
+    complex-valued arguments.
+    
+    """
+    res = mpmath.hyp2f1(a, b, c, z)
+    return float(res.real) + float(res.imag) * 1j
+
+# Vectorize it
+hyp2f1 = np.vectorize(_hyp2f1)
+
+
+def I_num(xi, I0, alpha=0):
+    """
+    Return the shifted spectrum, computed numerically.
+    
+    """
+    xi0 = xi + alpha
+    return np.interp(xi0, xi, I0)
+
+
+def S_num(xi, I0, alpha=0, npts=1000):
+    """
+    Return the disk-integrated spectrum, computed numerically.
+    
+    """
+    S = np.zeros_like(xi)
+    A = 0
+    beta = np.exp(alpha) - 1
+    for x in np.linspace(-1, 1, npts + 2)[1:-1]:
+        beta_x = beta * x
+        alpha_x = np.log(1 + beta_x)
+        S += I_num(xi, I0, alpha=alpha_x) * np.sqrt(1 - x ** 2)
+        A += np.sqrt(1 - x ** 2)
+    return np.pi * S / A
+
+
+def I(xi, I0, alpha=0):
+    """
+    Return the shifted spectrum, computed via an FFT.
+    
+    """
+    # Number of wavelength bins
+    N = len(xi)
+    
+    # Take the FFT
+    fI0 = np.fft.rfft(I0)
+    k = np.fft.rfftfreq(N, xi[1] - xi[0])
+    
+    # Apply the translation
+    fI0 *= np.exp(2 * np.pi * alpha * 1j * k)
+    
+    # Take the inverse FFT and return
+    return np.fft.irfft(fI0, N)
+
+
+def S(xi, I0, alpha=0, npts=1000):
+    """
+    Return the disk-integrated spectrum, computed via an FFT.
+    
+    """
+    # Number of wavelength bins
+    N = len(xi)
+    
+    # Take the FFT
+    fI0 = np.fft.rfft(I0)
+    k = np.fft.rfftfreq(N, xi[1] - xi[0])
+    
+    # Apply the integral of the translation   
[…]

### 2019-06-13 tex/gitlinks.tex
woot

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/a251a86a99ed85693dc35868dff23c6c4bdf40ed/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/a251a86a99ed85693dc35868dff23c6c4bdf40ed/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/a251a86a99ed85693dc35868dff23c6c4bdf40ed/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/a5fcbb15ba3e6d3c33496489dba346647c265f5d/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/a5fcbb15ba3e6d3c33496489dba346647c265f5d/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/a5fcbb15ba3e6d3c33496489dba346647c265f5d/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-06-13 tex/ms.tex
woot

@@
 \begin{align}
+    \label{eq:uniform}
     S(\xi) &= 
@@
 %
-Figure~\ref{fig:uniform}
+Figure~\ref{fig:uniform} shows an example application of this equation
+to the case of rotational broadening of a Gaussian absorption line.
 
@@
     \oscaption{uniform}{%
-        Hello.
+        Application of Equation~(\ref{eq:uniform}) to computation
+        of rotational line broadening of a Gaussian absorption line.
+        \emph{Top:} A line centered at $\lambda = 1.00$ with 
+        standard deviation $\sigma = 0.01$ (dashed black curve) is 
+        redshifted by a Doppler parameter $\beta = 0.05$. The
+        blue curve is the result obtained by interpolation, while
+        the dashed orange curve is the result obtained by scaling
+        the Fourier transform of the line according to
+        Equation~(\ref{eq:translation}) and then applying the inverse
+        Fourier transform.
+        \emph{Bottom:} The same line profile is now integrated over
+        the visible disk of a uniform, rigidly rotating star with
+        $\beta_\mathrm{eq} = 0.05$ numerically (blue curve) and via
+        the Fourier method (Equation~\ref{eq:uniform}). In both cases,
+        the results agree to within the accuracy of the numerical
+        approaches.
         \label{fig:uniform}

### 2019-06-13 tex/gitlinks.tex
wooooot

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/a5fcbb15ba3e6d3c33496489dba346647c265f5d/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/a5fcbb15ba3e6d3c33496489dba346647c265f5d/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/a5fcbb15ba3e6d3c33496489dba346647c265f5d/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/d2fd278bdf8ebf22d2ce73093ca81d6bc0a4939b/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/d2fd278bdf8ebf22d2ce73093ca81d6bc0a4939b/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/d2fd278bdf8ebf22d2ce73093ca81d6bc0a4939b/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-06-13 tex/ms.tex
wooooot

@@
 \begin{align}
+    \label{eq:Jhat}
     \hat{J}(k) \equiv 
@@
     S(\xi) &= \mathcal{F}^{-1}\Big[ \hat{S}(k) \Big] \nonumber \\
+           \label{eq:S}
            &= \mathcal{F}^{-1}\Big[ \hat{I_0}(k) \hat{J}(k) \Big] \\
+           \label{eq:S_conv}
            &= I_0(\xi) \circ J(\xi)
@@
 
-\subsubsection{Integration over the full stellar disk}
-\label{sec:full_disk}
+\subsubsection{Rotational line broadening}
+\label{sec:line_broadening}
 %
@@
 %
-\begin{align}
+\begin{proof}{Fourier}
     \hat{J}(k) 
@@
     \quad ,
-\end{align}
+\end{proof}
 %
@@
 %
-\begin{align}
+\begin{proof}{Fourier}
     \label{eq:uniform}
@@
     \Big]
-\end{align}
+\end{proof}
 %
@@
 
+\subsubsection{Rossiter-McLaughlin Effect}
+\label{sec:rmeffect}
+%
+Consider now the case where the integral is taken over only a portion
+of the stellar disk, as in the case of an occultation by an orbiting planet
+(or stellar companion). We can make use of Equation~(\ref{eq:S}) to
+compute the time evolution of the observed spectrum during a transit
+or occultation, i.e., the Rossiter-McLaughlin effect.
+%
+Working again in the non-relativistic limit, we may approximate
+Equation~(\ref{eq:Jhat}) as
+%
+\begin{align}
+    \label{eq:Jhat_approx}
+    \hat{J}(k) \approx
+        \iint\limits_{\mathcal{S}(x, y)}
+        % MAGIC
+        \left( 1 - \beta(x, y) \right) ^ {2\pi i k}
+        % MAGIC
+        \mathrm{d}\mathcal{S}(x, y)
+\end{align}
+%
+We can further decompose this into its real and imaginary parts,
+keeping only terms up to linear order in $\beta_\mathrm{eq}$:
+%
+\begin{align}
+    \label{eq:Jhat_approx_re}
+    \mathrm{Re}\left[\hat{J}(k)\right] 
+    &\approx
+        \iint\limits_{\mathcal{S}(x, y)}
+        % MAGIC
+        \cos \Big[ 2\pi k \ln\big(1 - \beta(x, y)\big) \Big]
+        % MAGIC
+        \mathrm{d}\mathcal{S}(x, y)
+    \nonumber \\
+    &\approx
+        \iint\limits_{\mathcal{S}(x, y)}
+        \mathrm{d}\mathcal{S}(x, y)
+\end{align}
+%
+and
+%
+\begin{align}
+    \label{eq:Jhat_approx_im}
+    \mathrm{Im}\left[\hat{J}(k)\right] 
+    &\approx
+        \iint\limits_{\mathcal{S}(x, y)}
+        % MAGIC
+        \sin \Big( 2\pi k \ln\big(1 - \beta(x, y)\big) \Big)
+        % MAGIC
+        \mathrm{d}\mathcal{S}(x, y)
+    \nonumber \\
+    &\approx
+        -2\pi k
+        \iint\limits_{\mathcal{S}(x, y)}
+        % MAGIC
+        \beta(x, y)
+        % MAGIC
+        \mathrm{d}\mathcal{S}(x, y)
+        \quad .
+\end{align}
+%
+\cite{Luger2019} developed an analytic formalism to compute these 
+integrals, provided $\beta(x, y)$ can be expressed in terms of
+spherical harmonics. We will see in the following section that
+$\beta(x, y)$ can be expressed exactly as the sum of
+spherical harmonics of low degree in the case of a 
+star with arbitrary inclination and obliquity and linear
+differential rotation. For now, however, let us consider again
+the simple case of a rigidly rotating star with rotation axis
+perpendicular to the line of sight. In this case,
+%
+\begin{align}
+    \mathrm{Re}\left[\hat{J}(k)\right] 
+    &\approx \iint\limits_{\mathcal{S}(x, y)}\mathrm{d}\mathcal{S}(x, y)
+    \nonumber \\
+    &= \mathbf{s}_0(x_o, y_o, r_o)
+\end{align}
+%
+and
+%
+\begin{align}
+    \mathrm{Im}\left[\hat{J}(k)\right] 
+    &\approx 
+    -2\pi k \beta_\mathrm{eq}
+    \iint\limits_{\mathcal{S}(x, y)}
+    x
+    \mathrm{d}\mathcal{S}(x, y)
+    \nonumber \\
+    &= -\pi k \beta_\mathrm{eq} \mathbf{s}_1(x_o, y_o, r_o)
+\end{align}
+%
+
 % Bibliography

### 2019-06-13 tex/gitlinks.tex
rmeffect

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/d2fd278bdf8ebf22d2ce73093ca81d6bc0a4939b/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/d2fd278bdf8ebf22d2ce73093ca81d6bc0a4939b/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/d2fd278bdf8ebf22d2ce73093ca81d6bc0a4939b/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/32ee083fb652e476a27da13b2978124d3d330556/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/32ee083fb652e476a27da13b2978124d3d330556/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/32ee083fb652e476a27da13b2978124d3d330556/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-06-16 tex/gitlinks.tex
wow, much changes

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/32ee083fb652e476a27da13b2978124d3d330556/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/32ee083fb652e476a27da13b2978124d3d330556/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/32ee083fb652e476a27da13b2978124d3d330556/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/551e6d5b6d9ef1a8b666d2b2d389ffacdf625544/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/551e6d5b6d9ef1a8b666d2b2d389ffacdf625544/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/551e6d5b6d9ef1a8b666d2b2d389ffacdf625544/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-06-16 tex/ms.tex
rmeffect
wow, much changes

--- 2019-06-13 tex/ms.tex
@@
 %
-\section{Uniform surfaces}
-\label{sec:uniform surfaces}
+\section{The problem}
+\label{sec:the_problem}
 %
@@
 \begin{align}
-    \label{eq:IntensityUnif}
-    I(\xi, x, y) &= I_0(\xi_0)
+    \label{eq:I}
+    I(\xi, x, y) &= I_0(\xi_0, x, y)
 \end{align}
 %
-where $I_0$ is the (spatially uniform) spectrum in the original, unshifted 
+where $I_0$ is the spectrum at each point on the star in the surface rest
 frame and 
@@
 \begin{align}
+    \label{eq:alpha}
     \alpha(x, y) 
@@
         \right) 
-        %\nonumber \\
-        %&\approx
-        %\ln(1 - \beta)
+        \nonumber \\
+        &\approx
+        \ln(1 - \beta)
 \end{align}
@@
 where $\beta = v(x, y) / c$ is the ratio of the 
-radial velocity at a point on 
-the surface of the star to the speed of light. In keeping with the 
-literature, we assume that positive values of $v$ correspond to redshifts.
+radial velocity at a point on the surface of the star to the speed of light
+and the second line is valid when $\beta \ll 1$ (i.e., the non-relativistic
+Doppler shift). Throughout this paper, we will assume the non-relativistic 
+limit, as it greatly simplifies the math.
+In keeping with the literature, we take positive values of $v$ to mean 
+redshifts.
 
@@
 ideal when one is interested in the \emph{integral} over the entire
-surface, which is typically what we can observe. The standard approach is
+surface of the star $\mathcal{S}$, which is typically all we can observe:
+%
+\begin{align}
+    \label{eq:S}
+    S(\xi) 
+        &\equiv
+        \iint\limits_{\mathcal{S}(x, y)}
+                I(\xi, x, y)
+        \mathrm{d}{\mathcal{S}(x, y)}
+        \quad .
+\end{align}
+%
+The difficulty in solving Equation~(\ref{eq:S}) stems from the fact
+that $I(\xi, x, y)$ is difficult to write down in closed form, given
+the non-linearity of the Doppler shift.
+The standard approach to solving this integral is therefore
 to discretize the surface of the star with a fine grid, evaluate the
@@
 
-\subsection{Linearizing the Doppler operator}
+\section{The Solution}
+
+Below, we consider three alternative methods to solving
+Equation~(\ref{eq:S}) to improve the speed and accuracy of the
+computation.
+
+\subsection{Taylor expanding the Doppler operator}
 \label{sec:taylor}
 %
-One way to improve upon this could be to linearize the Doppler operator via
+One way to tackle the problem is to linearize the Doppler operator via
 a Taylor expansion in $\alpha$ about $\alpha=0$:
@@
 \begin{align}
-    \label{eq:TaylorUnifExplicit}
+    \label{eq:taylor:I}
     I(\xi, x, y) 
         &=
-        I_0(\xi_0) \Bigg|_{\alpha=0}
+        I_0(\xi_0, x, y) \Bigg|_{\alpha=0}
         + 
-        \frac{\mathrm{d}I_0(\xi_0)}{\mathrm{d}\alpha} \Bigg|_{\alpha=0} 
+        \frac{\mathrm{d}I_0(\xi_0, x, y)}{\mathrm{d}\alpha} \Bigg|_{\alpha=0} 
             \Delta\alpha(x, y)
         + 
-        \frac{1}{2}\frac{\mathrm{d}^2I_0(\xi_0)}{\mathrm{d}\alpha^2} 
+        \frac{1}{2}\frac{\mathrm{d}^2I_0(\xi_0, x, y)}{\mathrm{d}\alpha^2} 
             \Bigg|_{\alpha=0} \Delta\alpha(x, y)^2
@@
 \begin{align}
-    \frac{\mathrm{d}^nI_0(\xi_0)}{\mathrm{d}\alpha^n} &=
-    \dfrac{\mathrm{d}^nI_0(\xi_0)}{\mathrm{d}\xi_0^n} \quad.
+    \frac{\mathrm{d}^nI_0(\xi_0, x, y)}{\mathrm{d}\alpha^n} &=
+    \dfrac{\mathrm{d}^nI_0(\xi_0, x, y)}{\mathrm{d}\xi_0^n} \nonumber\\ &\equiv
+    I_0^{(n)}(\xi_0, x, y)
+    \quad.
 \end{align}
@@
 Given this result, and noting that $\xi_0 = \xi$ when $\alpha = 0$,
-we may re-write Equation~(\ref{eq:TaylorUnifExplicit}) as
+we may re-write Equation~(\ref{eq:taylor:I}) as
 %
 \begin{proof}{Taylor}
-    \label{eq:TaylorUnifSum}
+    \label{eq:taylor:ISum}
     I(\xi, x, y) 
         &=
-        I_0(\xi)
-        +
-        \sum_{n=1}^\infty
-            \frac{1}{n!}
-            \frac{\mathrm{d}^nI_0(\xi)}{\mathrm{d}\xi^n}
+        \sum_{n=0}^\infty
+            \frac{I_{0}^{(n)}(\xi, x, y)}{n!}
             \Delta\alpha(x, y)^n
+        \quad ,
 \end{proof}
 %
-The utility of this expression is that the spatial dependence of the spectrum
-is now entirely encoded in the terms $\Delta\alpha(x, y)^n$, which is
-\emph{independent of wavelength}. The surface integral of 
-Equation~(\ref{eq:TaylorUnifSum}) is therefore far easier to compute, since
-it is the integral of a \emph{scalar} function that could even be approximated
-analytically for some choice of the velocity field $\alpha(x, y)$.
+The utility of this expression is that the velocity dependence of the spectrum
+is now entirely encoded in the terms $\Delta\alpha(x, y)^n$, which are
+\emph{independent of wavelength}. We can further decouple the spatial
+dependence from the spectral dependence by expressing the intensity field
+as an expansion over spherical harmonics $Y_{lm}(x, y)$ in the sky-projected
+coordinates:
+%
+\begin{align}
+    I_0(\xi, x, y) = \sum_{l=0}^\infty\sum_{m=-l}^{l} a_{lm}(\xi) Y_{lm}(x, y)
+    \quad .
+\end{align}
+%
+Equation~(\ref{eq:taylor:ISum}) now reads
+%
+\begin{align}
+    \label{eq:taylor:IYlm}
+    I(\xi, x, y) 
+        &=
+        \sum_{n=0}^\infty
+            \sum_{l=0}^\infty\sum_{m=-l}^{l}
+                \frac{a_{lm}^{(n)}(\xi)}{n!}
+                Y_{lm}(x, y)\Delta\alpha(x, y)^n
+            \quad .
+\end{align}
+%
+Finally, integrating this equation over the visible disk of 
+the star, we arrive at an equation for the observed spectrum:
+%
+\begin{align}
+    \label{eq:taylor:S}
+    S(\xi) 
+        &=
+        \sum_{n=0}^\infty
+            \sum_{l=0}^\infty\sum_{m=-l}^{l}
+                \frac{a_{lm}^{(n)}(\xi)}{n!}
+                \iint\limits_{\mathcal{S}(x, y)}
+                Y_{lm}(x, y)\Delta\alpha(x, y)^n
+                \mathrm{d}{\mathcal{S}(x, y)}
+            \quad .
+\end{align}
+%
+By expanding the spectrum in both the spectral and spatial dimensions, we
+have effectively decoupled the two. However, Equation~(\ref{eq:taylor:S}) 
+is impractical for three reasons. First, the surface integrals can be very
+difficult to solve (although we will show later how these integrals may be
+approximated analytically). Second, it requires knowledge of high order 
+derivatives of the spectrum, which may not always be easy or convenient to 
+compute. Third, and most important, the series expansion in $n$ is typically 
+extremely slow to converge and is therefore only practically useful in the 
+limit that the Doppler shift is much smaller than the typical width of a 
+spectral line; see the notebook link next to Equation~(\ref{eq:taylor:ISum}) 
+for an example.
 
-However, Equation~(\ref{eq:TaylorUnifSum}) is impractical for
-two reasons. First, it requires knowledge of high order derivatives of the 
-spectrum, which may not always be easy or convenient to compute. Second, and
-more important, the series expansion is typically extremely slow to converge
-and is therefore only practically useful in the limit that the Doppler shift
-is much smaller than the typical width of a spectral line; see the notebook
-link next to Equation~(\ref{eq:TaylorUnifSum}) for an example.
-
-\subsection{Taking the Fourier transform}
+\subsection{Taking the Fourier transform of the spectrum}
 \label{sec:fourier}
@@
 \begin{align}
-    \label{eq:FT}
+    \label{eq:fourier:FT}
     \mathcal{F}\Big[f(\xi)\Big](k) 
@@
 \begin{align}
-    \label{eq:IFT}
+    \label{eq:fourier:IFT}
     \mathcal{F}^{-1}\Big[\hat{f}(k)\Big](\xi) 
@@
 \citep[e.g.,][]{Schoenstadt2006}.
-Specifically, if the Doppler-shifted spectrum 
-is given by
+Specifically, if the Doppler-shifted spectrum is given by
 %
 \begin{align}
-    I(\xi, x, y) &= I_0\big(\xi + \alpha(x, y)\big) \quad,
+    I(\xi, x, y) &= I_0\big(\xi + \alpha(x, y)\big), x, y) \quad,
 \end{align}
@@
 \begin{align}
-    \label{eq:translation}
-    \hat{I}(\xi, x, y) &= \mathrm{e}^{2\pi i k \alpha(x, y)}\hat{I_0}(k) \quad,
+    \label{eq:fourier:translation}
+    \hat{I}(\xi, x, y) 
+    &= 
+    \mathrm{e}^{2\pi i k \alpha(x, y)}\hat{I_0}(k, x, y)
+    \quad ,
 \end{align}
 %
-where $\hat{I_0}(k) \equiv \mathcal{F}\left[ I_0(\xi) \right]$.
+where $\hat{I_0}(k, x, y) \equiv \mathcal{F}\left[ I_0(\xi, x, y) \right]$.
 %
@@
 terms, but this time without the need of a Taylor expansion. To obtain
-the Fourier transform of the disk-integrated spectrum, $\hat{S}$, we may 
-integrate Equation~(\ref{eq:translation})
+the observed spectrum, we
+expand $\hat{I_0}(k, x, y)$ in terms of spherical harmonics,
+%
+\begin{align}
+    \label{eq:fourier:I0}
+    \hat{I_0}(k, x, y) 
+        &=
+        \sum_{l=0}^\infty\sum_{m=-l}^{l} \hat{a}_{lm}(k) Y_{lm}(x, y)
+\end{align}
+%
+then take the inverse Fourier transform of the integral of 
+Equation~(\ref{eq:fourier:translation})
 over the visible disk $\mathcal{S}$ of the star:
@@
 \begin{align}
-    \label{eq:integral_translation}
-    \hat{S}(k) 
+    \label{eq:fourier:SYlm}
+    S(k) 
     &=
-        \hat{I_0}(k)\iint\limits_{\mathcal{S}(x, y)}
+    \mathcal{F}^{-1}\Big[
+        \sum_{l=0}^\infty\sum_{m=-l}^{l}
+        \hat{a}_{lm}(k)
+        \iint\limits_{\mathcal{S}(x, y)}
+        Y_{lm}(x, y)
         \mathrm{e}^{2\pi i k \alpha(x, y)}
-        \mathrm{d}\mathcal{S}(x, y) \nonumber \\
+        \mathrm{d}\mathcal{S}(x, y)
+    \Big]
+    \nonumber \\
     &=
-        \hat{I_0}(k)\iint\limits_{\mathcal{S}(x, y)}
-        % MAGIC
-        \left( \frac{1 - \beta(x, y)}{1 + \beta(x, y)} \right) ^ {\pi i k}
-        % MAGIC
-        \mathrm{d}\mathcal{S}(x, y) \nonumber \\
-    &=
-        \hat{I_0}(k) \hat{J}(k)
+    \mathcal{F}^{-1}\Big[
+        \iint\limits_{\mathcal{S}(x, y)}
+        \bvec{Y}(x, y)
+        \mathrm{e}^{2\pi i k \alpha(x, y)}
+        \mathrm{d}\mathcal{S}(x, y)
+        \cdot
+        \bvec{\hat{a}}(k)
+    \Big]
+    \quad ,
 \end{align}
 %
-where we define
+where
 %
 \begin{align}
-    \hat{J}(k) \equiv 
-        \iint\limits_{\mathcal{S}(x, y)}
-        % MAGIC
-        \left( \frac{1 - \beta(x, y)}{1 + \beta(x, y)} \right) ^ {\pi i k}
-        % MAGIC
-        \mathrm{d}\mathcal{S}(x, y)
+    \bvec{\hat{a}}(k) \equiv
+\left( 
+    \hat{a}_{0,0}(k) \quad\quad\quad\quad\quad\quad 
+    \hat{a}_{1,-1}(k) \quad\quad\quad\quad\quad\quad 
+    \hat{a}_{1,0}(k) \quad\quad\quad\quad\quad\quad
+    \hat{a}_{1,1}(k) \quad\quad\quad\quad\quad\quad 
+    ... 
+\right)^\top
 \end{align}
 %
-to be the surface integral of the velocity field in Fourier space.
-The disk-integrated spectrum is then obtained by applying the inverse Fourier
-transform:
+is the column vector of spherical harmonic coefficients at wavenumber $k$, and
 %
 \begin{align}
-    S(\xi) &= \mathcal{F}^{-1}\Big[ \hat{S}(k) \Big] \nonumber \\
-           &= \mathcal{F}^{-1}\Big[ \hat{I_0}(k) \hat{J}(k) \Big] \\
-           &= I_0(\xi) \circ J(\xi)
+    \bvec{Y}(x, y) \equiv 
+\left( 
+    Y_{0,0}(x, y) \quad\quad\quad\quad\quad\quad 
+    Y_{1,-1}(x, y) \quad\quad\quad\quad\quad\quad 
+    Y_{1,0}(x, y) \quad\quad\quad\quad\quad\quad 
+    Y_{1,1}(x, y) \quad\quad\quad\quad\quad\quad 
+    ... 
+\right)
 \end{align}
 %
-where the last step follows from the convolution theorem, 
-with $J(\xi) \equiv \mathcal{F}^{-1}\left[ \hat{J}(k) \right]$ and $\circ$
-denoting the convolution operator.
+is the corresponding row vector of spherical harmonics at a point $(x, y)$ 
+on the sphere.
 
-\subsubsection{Integration over the full stellar disk}
-\label{sec:full_disk}
-%
-As an example, consider the case of an unocculted, uniform star of unit
-radius with negligible limb darkening, rigidly rotating about an axis 
-perpendicular to the line of sight with equatorial angular velocity 
-$\omega_\mathrm{eq}$. The velocity profile everywhere on the surface is
+In the case that the integration area $\mathcal{S}$ is the entire surface of
+the star, the integrals in Equation~(\ref{eq:fourier:SYlm}) are
+\emph{analytic}. To see this, we may change bases from spherical harmonics
+to polynomials on the sphere:
 %
 \begin{align}
-    \beta(x, y) &= \frac{\omega_\mathrm{eq}}{c}x \nonumber\\
-                &\equiv \beta_\mathrm{eq} x 
+    \label{eq:fourier:SP}
+    S(k) 
+    &=
+    \mathcal{F}^{-1}\Big[
+        \iint\limits_{\mathcal{S}(x, y)}
+        \bvec{P}(x, y)
+        \mathrm{e}^{2\pi i k \alpha(x, y)}
+        \mathrm{d}\mathcal{S}(x, y)
+        \cdot
+        \bvec{A_1}
+        \bvec{\hat{a}}(k)
+    \Big]
     \quad .
@@
 %
-The surface integral term may then be computed as
+where
 %
 \begin{align}
-    \hat{J}(k) 
-    &=
-        \int_{-1}^{1}
-        \int_{-\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
-        % MAGIC
+    \bvec{P}(x, y) \equiv 
 \left( 
-            \frac{1 - \beta_\mathrm{eq} x}
-                 {1 + \beta_\mathrm{eq} x} 
-        \right) ^ {\pi i k}
-        % MAGIC
-        \mathrm{d}y
-        \,
-        \mathrm{d}x
-        \nonumber \\[0.75em]
-    &\approx
-        \int_{-1}^{1}
-        \int_{-\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
-        % MAGIC
-        \left( 
-            1 - \beta_\mathrm{eq} x 
-        \right) ^ {2\pi i k}
-        % MAGIC
-        \mathrm{d}y
-        \,
-        \mathrm{d}x
-        \nonumber \\[0.75em]
-    &=
-        \pi \, _{2}F_{1}
-            \left(
-                -\pi i k, \, 
-                \frac{1}{2} - \pi i k; \,
-                2; \,
-                \beta_\mathrm{eq}^2
-            \right)
-    \quad ,
+    1 \quad\quad\quad\quad\quad\quad 
+    x \quad\quad\quad\quad\quad\quad 
+    z \quad\quad\quad\quad\quad\quad 
+    y \quad\quad\quad\quad\quad\quad 
+    x^2 \quad\quad\quad\quad\quad\quad 
+    xz \quad\quad\quad\quad\quad\quad 
+    xy \quad\quad\quad\quad\quad\quad
+    yz \quad\quad\quad\quad\quad\quad 
+    y^2 \quad\quad\quad\quad\quad\quad
+    ... 
+\right)^\top
 \end{align}
 %
-where $_{2}F_{1}$ is the hypergeometric function. Note that
-the approximation in the second line is valid when $\beta \ll 1$
-(i.e., the non-relativistic case).
-
-The equation for the observed disk-integrated spectrum is therefore
-%
-\begin{align}
-    S(\xi) &= 
-    \pi
-    \mathcal{F}^{-1}
-    \Big[
-        \mathcal{F}(I_0)
-        \,
-        _{2}F_{1}
-        \left(
-            -\pi i k, \, 
-            \frac{1}{2} - \pi i k; \,
-            2; \,
-            \beta_\mathrm{eq}^2
-        \right)
-    \Big]
-\end{align}
-%
-Figure~\ref{fig:uniform}
-
-\begin{figure}[p!]
-    \centering
-    \includegraphics[width=0.9\textwidth]{figures/uniform.pdf}
-    \oscaption{uniform}{%
-        Hello.
-        \label{fig:uniform}
-    }
-\end{figure}
+is the polynomial basis \citep[Equation 7 in][]{Luger2019}
+and $\bvec{A_1}$ is the change of basis matrix from spherical harmonics
+to polynomials 
+\citep[Equation B11 in][]{Luger2019}.
 

### 2019-06-16 tex/gitlinks.tex
more words

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/551e6d5b6d9ef1a8b666d2b2d389ffacdf625544/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/551e6d5b6d9ef1a8b666d2b2d389ffacdf625544/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/551e6d5b6d9ef1a8b666d2b2d389ffacdf625544/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/6ada7c637710a6b8fe53c4ddba545f13eab2e301/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/6ada7c637710a6b8fe53c4ddba545f13eab2e301/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/6ada7c637710a6b8fe53c4ddba545f13eab2e301/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-06-16 tex/ms.tex
more words

@@
 
-Below, we consider three alternative methods to solving
+In this section, we consider two alternative methods to solving
 Equation~(\ref{eq:S}) to improve the speed and accuracy of the
-computation.
+computation, both of which rely on the Fourier transform of the
+spectrum.
+Recall the definition of the Fourier transform of a function $f(\xi)$,
+%
+\begin{align}
+    \label{eq:fourier:FT}
+    \mathcal{F}\Big[f(\xi)\Big](k) 
+    &\equiv
+    \int_{-\infty}^\infty
+        f(\xi)
+        \mathrm{e}^{-2\pi i k \xi} \mathrm{d}\xi
+    \nonumber \\
+    &=
+    \hat{f}(k)
+    \quad ,
+\end{align}
+%
+and the corresponding inverse Fourier transform,
+%
+\begin{align}
+    \label{eq:fourier:IFT}
+    \mathcal{F}^{-1}\Big[\hat{f}(k)\Big](\xi) 
+    &\equiv
+    \int_{-\infty}^\infty
+        \hat{f}(k)
+        \mathrm{e}^{2\pi i k \xi} \mathrm{d}k
+    \nonumber \\
+    &=
+    f(\xi)
+    \quad .
+\end{align}
+%
+Consider what happens when we take the
+Fourier transform of the spectrum $I(\xi, x, y)$ to obtain
+a function $\hat{I}(k, x, y)$, where we refer to $k$ as a ``wavenumber''. 
+A useful property of the
+Fourier transform is that a translation of $I(\xi, x, y)$ by
+an amount $\Delta\xi$ corresponds to a linear scaling
+of $\hat{I}(k, x, y)$ by an amount $\mathrm{e}^{-2\pi i k \Delta\xi}$
+\citep[e.g.,][]{Schoenstadt2006}.
+Specifically, if the Doppler-shifted spectrum is given by
+%
+\begin{align}
+    I(\xi, x, y) &= I_0\big(\xi + \alpha(x, y)\big), x, y) \quad,
+\end{align}
+%
+its Fourier transform is equal to 
+%
+\begin{align}
+    \label{eq:fourier:translation}
+    \hat{I}(\xi, x, y) 
+    &= 
+    \mathrm{e}^{2\pi i k \alpha(x, y)}\hat{I_0}(k, x, y)
+    \quad ,
+\end{align}
+%
+where $\hat{I_0}(k, x, y) \equiv \mathcal{F}\left[ I_0(\xi, x, y) \right]$.
+%
+To obtain the Fourier transform of the observed spectrum, we
+expand $\hat{I_0}(k, x, y)$ in terms of spherical harmonics,
+%
+\begin{align}
+    \label{eq:fourier:I0}
+    \hat{I_0}(k, x, y) 
+        &=
+        \sum_{l=0}^\infty\sum_{m=-l}^{l} \hat{a}_{lm}(k) Y_{lm}(x, y)
+\end{align}
+%
+then take the integral of 
+Equation~(\ref{eq:fourier:translation})
+over the visible disk $\mathcal{S}$ of the star:
+%
+\begin{align}
+    \label{eq:fourier:SYlm}
+    \hat{S}(k) 
+    &=
+        \sum_{l=0}^\infty\sum_{m=-l}^{l}
+        \hat{a}_{lm}(k)
+        \iint\limits_{\mathcal{S}(x, y)}
+        Y_{lm}(x, y)
+        \mathrm{e}^{2\pi i k \alpha(x, y)}
+        \mathrm{d}\mathcal{S}(x, y)
+    \nonumber \\
+    &=
+        \iint\limits_{\mathcal{S}(x, y)}
+        \tilde{\bvec{y}}(x, y)
+        \mathrm{e}^{2\pi i k \alpha(x, y)}
+        \mathrm{d}\mathcal{S}(x, y)
+        \cdot
+        \bvec{\hat{a}}(k)
+    \quad ,
+\end{align}
+%
+where
+%
+\begin{align}
+    \bvec{\hat{a}}(k) \equiv
+\Big( 
+    \hat{a}_{0,0}(k) \quad\quad\quad\quad\quad\quad 
+    \hat{a}_{1,-1}(k) \quad\quad\quad\quad\quad\quad 
+    \hat{a}_{1,0}(k) \quad\quad\quad\quad\quad\quad
+    \hat{a}_{1,1}(k) \quad\quad\quad\quad\quad\quad 
+    ... 
+\Big)^\top
+\end{align}
+%
+is the column vector of spherical harmonic coefficients at wavenumber $k$, and
+%
+\begin{align}
+    \tilde{\bvec{y}}(x, y) \equiv 
+\Big( 
+    Y_{0,0}(x, y) \quad\quad\quad\quad\quad\quad 
+    Y_{1,-1}(x, y) \quad\quad\quad\quad\quad\quad 
+    Y_{1,0}(x, y) \quad\quad\quad\quad\quad\quad 
+    Y_{1,1}(x, y) \quad\quad\quad\quad\quad\quad 
+    ... 
+\Big)
+\end{align}
+%
+is the corresponding row vector of spherical harmonics at a point $(x, y)$ 
+on the sphere. In order to tackle the integrals in 
+Equation~(\ref{eq:fourier:SYlm}), let us change bases from spherical
+harmonics to polynomials on the sphere:
+%
+\begin{align}
+    \label{eq:fourier:S}
+    \hat{S}(k) 
+    &=
+        \iint\limits_{\mathcal{S}(x, y)}
+        \tilde{\bvec{p}}(x, y)
+        \mathrm{e}^{2\pi i k \alpha(x, y)}
+        \mathrm{d}\mathcal{S}(x, y)
+        \cdot
+        \bvec{A_1}
+        \bvec{\hat{a}}(k)
+    \quad .
+\end{align}
+%
+where
+%
+\begin{align}
+    \tilde{\bvec{p}}(x, y) \equiv 
+\Big( 
+    1 \quad\quad\quad\quad\quad\quad 
+    x \quad\quad\quad\quad\quad\quad 
+    z \quad\quad\quad\quad\quad\quad 
+    y \quad\quad\quad\quad\quad\quad 
+    x^2 \quad\quad\quad\quad\quad\quad 
+    xz \quad\quad\quad\quad\quad\quad 
+    xy \quad\quad\quad\quad\quad\quad
+    yz \quad\quad\quad\quad\quad\quad 
+    y^2 \quad\quad\quad\quad\quad\quad
+    ... 
+\Big)
+\end{align}
+%
+is the polynomial basis \citep[Equation 7 in][]{Luger2019}
+and $\bvec{A_1}$ is the change of basis matrix from spherical harmonics
+to polynomials 
+\citep[Equation B11 in][]{Luger2019}.
 
-\subsection{Taylor expanding the Doppler operator}
+At this point, we have two options: we can remain in Fourier space and
+attempt to solve the surface integral in Equation~(\ref{eq:fourier:S})
+directly, or we can take the inverse Fourier transform of  
+Equation~(\ref{eq:fourier:S}) and attempt to solve the integral in
+log wavelength space. As we will see, there are advantages (and
+disadvantages) to both methods. We do the former in \S\ref{sec:analytic}
+in the latter in \S\ref{sec:convolve}.
+
+\subsection{Analytic solutions}
+\label{sec:analytic}
+In the case that the integration area $\mathcal{S}$ is the entire surface of
+the star, the integrals in Equation~(\ref{eq:fourier:S}) are
+\emph{analytic}. \xxx{Show here how the result can be computed from the 
+hypergeometric function $_3F_2.$}
+
+\subsection{Doppler shifts as a convolution}
+\label{sec:convolve}
+
+If we take the inverse Fourier transform of Equation~(\ref{eq:fourier:S}),
+we arrive at an expression for the observed spectrum:
+%
+\begin{align}
+    \label{eq:convolve:SUgly}
+    S(\xi) 
+    &=
+    \mathcal{F}^{-1} \Bigg[\,\,\,
+        \iint\limits_{\mathcal{S}(x, y)}
+        \tilde{\bvec{p}}(x, y)
+        \mathrm{e}^{2\pi i k \alpha(x, y)}
+        \mathrm{d}\mathcal{S}(x, y)
+        \cdot
+        \bvec{A_1}
+        \bvec{\hat{a}}(k)
+    \Bigg] \nonumber \\
+    &=
+    \mathcal{F}^{-1} \Bigg[\,\,\,
+        \iint\limits_{\mathcal{S}(x, y)}
+        \tilde{\bvec{p}}(x, y)
+        \mathrm{e}^{2\pi i k \alpha(x, y)}
+        \mathrm{d}\mathcal{S}(x, y)
+    \Bigg]
+    \circ
+    \bvec{A_1}
+    \bvec{a}(\xi)
+    \quad ,
+\end{align}
+%
+where the second line follows from the convolution theorem, with
+$\circ$ denoting the convolution operator over $\xi$ and 
+$\bvec{a}(\xi) \equiv \mathcal{F}^{-1}\left[ \bvec{\hat{a}}(k) \right]$.
+Since only the exponential term in the integrand depends on $k$, we may 
+further simplify this expression:
+%
+\begin{align}
+    \label{eq:convolve:SUgly}
+    S(\xi) 
+    &=    
+    \iint\limits_{\mathcal{S}(x, y)}
+    \tilde{\bvec{p}}(x, y)
+    \mathcal{F}^{-1} \Big[
+        \mathrm{e}^{2\pi i k \alpha(x, y)}
+    \Big]
+    \mathrm{d}\mathcal{S}(x, y)
+    \circ
+    \bvec{A_1}
+    \bvec{a}(\xi)
+    \nonumber \\
+    &=    
+    \iint\limits_{\mathcal{S}(x, y)}
+    \tilde{\bvec{p}}(x, y)
+    \delta\big(\xi - \alpha(x, y)\big)
+    \mathrm{d}\mathcal{S}(x, y)
+    \circ
+    \bvec{A_1}
+    \bvec{a}(\xi)
+    \quad,
+\end{align}
+%
+where $\delta$ is the Dirac delta function. Since the integrand in the
+equation above is zero everywhere except where the argument of the
+$\delta$ function is zero, the equation may be written as a line integral 
+along some curve $\mathcal{C}(x, y)$ along which $\xi = \alpha(x, y)$:
+%
+\begin{align}
+    \label{eq:convolve:SUgly}
+    S(\xi) 
+    &=    
+    \int\limits_{\mathcal{C}(x, y)}
+    \tilde{\bvec{p}}(x, y)
+    \mathrm{d}\mathcal{C}(x, y)
+    \circ
+    \bvec{A_1}
+    \bvec{a}(\xi)
+    \quad.
+\end{align}
+%
+
+\appendix
+
+\section{Taylor Expanding the Doppler operator \\ (and why this is a bad idea)}
 \label{sec:taylor}
 %
-One way to tackle the problem is to linearize the Doppler operator via
-a Taylor expansion in $\alpha$ about $\alpha=0$:
+An alternative way to tackle the problem is to linearize the Doppler 
+operator via a Taylor expansion in $\alpha$ about $\alpha=0$:
 %
@@
 
-\subsection{Taking the Fourier transform of the spectrum}
-\label{sec:fourier}
-%
-Recall the definition of the Fourier transform of a function $f(\xi)$,
-%
-\begin{align}
-    \label{eq:fourier:FT}
-    \mathcal{F}\Big[f(\xi)\Big](k) 
-    &\equiv
-    \int_{-\infty}^\infty
-        f(\xi)
-        \mathrm{e}^{-2\pi i k \xi} \mathrm{d}\xi
-    \nonumber \\
-    &=
-    \hat{f}(k)
-    \quad ,
-\end{align}
-%
-and the corresponding inverse Fourier transform,
-%
-\begin{align}
-    \label{eq:fourier:IFT}
-    \mathcal{F}^{-1}\Big[\hat{f}(k)\Big](\xi) 
-    &\equiv
-    \int_{-\infty}^\infty
-        \hat{f}(k)
-        \mathrm{e}^{2\pi i k \xi} \mathrm{d}k
-    \nonumber \\
-    &=
-    f(\xi)
-    \quad .
-\end{align}
-%
-Consider what happens when we take the
-Fourier transform of the spectrum $I(\xi, x, y)$ to obtain
-a function $\hat{I}(k, x, y)$. A useful property of the
-Fourier transform is that a translation of $I(\xi, x, y)$ by
-an amount $\Delta\xi$ corresponds to a linear scaling
-of $\hat{I}(k, x, y)$ by an amount $\mathrm{e}^{-2\pi i k \Delta\xi}$
-\citep[e.g.,][]{Schoenstadt2006}.
-Specifically, if the Doppler-shifted spectrum is given by
-%
-\begin{align}
-    I(\xi, x, y) &= I_0\big(\xi + \alpha(x, y)\big), x, y) \quad,
-\end{align}
-%
-its Fourier transform is equal to 
-%
-\begin{align}
-    \label{eq:fourier:translation}
-    \hat{I}(\xi, x, y) 
-    &= 
-    \mathrm{e}^{2\pi i k \alpha(x, y)}\hat{I_0}(k, x, y)
-    \quad ,
-\end{align}
-%
-where $\hat{I_0}(k, x, y) \equiv \mathcal{F}\left[ I_0(\xi, x, y) \right]$.
-%
-Much as in \S\ref{sec:taylor}, we have de-coupled the spatial and spectral
-terms, but this time without the need of a Taylor expansion. To obtain
-the observed spectrum, we
-expand $\hat{I_0}(k, x, y)$ in terms of spherical harmonics,
-%
-\begin{align}
-    \label{eq:fourier:I0}
-    \hat{I_0}(k, x, y) 
-        &=
-        \sum_{l=0}^\infty\sum_{m=-l}^{l} \hat{a}_{lm}(k) Y_{lm}(x, y)
-\end{align}
-%
-then take the inverse Fourier transform of the integral of 
-Equation~(\ref{eq:fourier:translation})
-over the visible disk $\mathcal{S}$ of the star:
-%
-\begin{align}
-    \label{eq:fourier:SYlm}
-    S(k) 
-    &=
-    \mathcal{F}^{-1}\Big[
-        \sum_{l=0}^\infty\sum_{m=-l}^{l}
-        \hat{a}_{lm}(k)
-        \iint\limits_{\mathcal{S}(x, y)}
-        Y_{lm}(x, y)
-        \mathrm{e}^{2\pi i k \alpha(x, y)}
-        \mathrm{d}\mathcal{S}(x, y)
-    \Big]
-    \nonumber \\
-    &=
-    \mathcal{F}^{-1}\Big[
-        \iint\limits_{\mathcal{S}(x, y)}
-        \bvec{Y}(x, y)
-        \mathrm{e}^{2\pi i k \alpha(x, y)}
-        \mathrm{d}\mathcal{S}(x, y)
-        \cdot
-        \bvec{\hat{a}}(k)
-    \Big]
-    \quad ,
-\end{align}
-%
-where
-%
-\begin{align}
-    \bvec{\hat{a}}(k) \equiv
-\left( 
-    \hat{a}_{0,0}(k) \quad\quad\quad\quad\quad\quad 
-    \hat{a}_{1,-1}(k) \quad\quad\quad\quad\quad\quad 
-    \hat{a}_{1,0}(k) \quad\quad\quad\quad\quad\quad
-    \hat{a}_{1,1}(k) \quad\quad\quad\quad\quad\quad 
-    ... 
-\right)^\top
-\end{align}
-%
-is the column vector of spherical harmonic coefficients at wavenumber $k$, and
-%
-\begin{align}
-    \bvec{Y}(x, y) \equiv 
-\left( 
-    Y_{0,0}(x, y) \quad\quad\quad\quad\quad\quad 
-    Y_{1,-1}(x, y) \quad\quad\quad\quad\quad\quad 
-    Y_{1,0}(x, y) \quad\quad\quad\quad\quad\quad 
-    Y_{1,1}(x, y) \quad\quad\quad\quad\quad\quad 
-    ... 
-\right)
-\end{align}
-%
-is the corresponding row vector of spherical harmonics at a point $(x, y)$ 
-on the sphere.
-
-In the case that the integration area $\mathcal{S}$ is the entire surface of
-the star, the integrals in Equation~(\ref{eq:fourier:SYlm}) are
-\emph{analytic}. To see this, we may change bases from spherical harmonics
-to polynomials on the sphere:
-%
-\begin{align}
-    \label{eq:fourier:SP}
-    S(k) 
-    &=
-    \mathcal{F}^{-1}\Big[
-        \iint\limits_{\mathcal{S}(x, y)}
-        \bvec{P}(x, y)
-        \mathrm{e}^{2\pi i k \alpha(x, y)}
-        \mathrm{d}\mathcal{S}(x, y)
-        \cdot
-        \bvec{A_1}
-        \bvec{\hat{a}}(k)
-    \Big]
-    \quad .
-\end{align}
-%
-where
-%
-\begin{align}
-    \bvec{P}(x, y) \equiv 
-\left( 
-    1 \quad\quad\quad\quad\quad\quad 
-    x \quad\quad\quad\quad\quad\quad 
-    z \quad\quad\quad\quad\quad\quad 
-    y \quad\quad\quad\quad\quad\quad 
-    x^2 \quad\quad\quad\quad\quad\quad 
-    xz \quad\quad\quad\quad\quad\quad 
-    xy \quad\quad\quad\quad\quad\quad
-    yz \quad\quad\quad\quad\quad\quad 
-    y^2 \quad\quad\quad\quad\quad\quad
-    ... 
-\right)^\top
-\end{align}
-%
-is the polynomial basis \citep[Equation 7 in][]{Luger2019}
-and $\bvec{A_1}$ is the change of basis matrix from spherical harmonics
-to polynomials 
-\citep[Equation B11 in][]{Luger2019}.
-
 % Bibliography

### 2019-06-16 tex/gitlinks.tex
tweaks

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/6ada7c637710a6b8fe53c4ddba545f13eab2e301/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/6ada7c637710a6b8fe53c4ddba545f13eab2e301/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/6ada7c637710a6b8fe53c4ddba545f13eab2e301/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/01e5eaaac7f32570634b33ad7aed7769c338a0d0/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/01e5eaaac7f32570634b33ad7aed7769c338a0d0/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/01e5eaaac7f32570634b33ad7aed7769c338a0d0/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-06-16 tex/ideas.tex
tweaks

--- 2019-06-16 tex/ms.tex
@@
-\documentclass[modern]{aastex62}
-
-% Load the corTeX style definitions
-\input{cortex}
-
-% Bibliography stuff
-\bibliographystyle{aasjournal}
-
-% Begin!
-\begin{document}
-
-% Title
-\title{Doppler Imaging Fun}
-
-% Author list
-\author[0000-0002-0296-3826]{Rodrigo Luger}
-\email{rluger@flatironinstitute.org}
-\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
-%
-\author{Megan Bedell}
-\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
-%
-\author{Probably David W. Hogg}
-\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
-
-%
-\section{Introduction}
-%
-Check out \citet{Luger2019} and \citet{Bedell2019} and stuff.
-
-%
-\section{The problem}
-\label{sec:the_problem}
-%
-Let $I(\xi, x, y)$ be the Doppler-shifted intensity observed at log wavelength 
-$\xi \equiv \ln\lambda$ at sky-projected Cartesian position $x, y$ on the 
-surface of the star. We may express it as
-%
-\begin{align}
-    \label{eq:I}
-    I(\xi, x, y) &= I_0(\xi_0, x, y)
-\end{align}
-%
-where $I_0$ is the spectrum at each point on the star in the surface rest
-frame and 
-%
-\begin{align}
-    \label{eq:xi0}
-    \xi_0 &= \xi + \alpha(x, y)
-\end{align}
-%
-is the log wavelength in the unshifted frame. The quantity $\alpha$ is
-computed from the formula for the Doppler shift and is equal to
-%
-\begin{align}
-    \label{eq:alpha}
-    \alpha(x, y) 
-        &=
-        \frac{1}{2}\ln\left( 
-            \frac{1 - \beta}{1 + \beta} 
-        \right) 
-        \nonumber \\
-        &\approx
-        \ln(1 - \beta)
-\end{align}
-%
-where $\beta = v(x, y) / c$ is the ratio of the 
-radial velocity at a point on the surface of the star to the speed of light
-and the second line is valid when $\beta \ll 1$ (i.e., the non-relativistic
-Doppler shift). Throughout this paper, we will assume the non-relativistic 
-limit, as it greatly simplifies the math.
-In keeping with the literature, we take positive values of $v$ to mean 
-redshifts.
-
-A common approach to computing the Doppler-shifted spectrum is to
-evaluate the spectrum at the rest frame wavelength (Equation~\ref{eq:xi0})
-and interpolate back to the grid in $\xi$. This is practical when
-computing the spectrum at a single \emph{point} on the surface, but not
-ideal when one is interested in the \emph{integral} over the entire
-surface of the star $\mathcal{S}$, which is typically all we can observe:
-%
-\begin{align}
-    \label{eq:S}
-    S(\xi) 
-        &\equiv
-        \iint\limits_{\mathcal{S}(x, y)}
-                I(\xi, x, y)
-        \mathrm{d}{\mathcal{S}(x, y)}
-        \quad .
-\end{align}
-%
-The difficulty in solving Equation~(\ref{eq:S}) stems from the fact
-that $I(\xi, x, y)$ is difficult to write down in closed form, given
-the non-linearity of the Doppler shift.
-The standard approach to solving this integral is therefore
-to discretize the surface of the star with a fine grid, evaluate the
-Doppler-shifted spectrum in each cell, and sum over the spatial axes
-to approximate the integral. Depending on the resolution of the grid,
-this is either numerically inaccurate or computationally inefficient 
-(and often both).
-
-\section{The Solution}
-
-Below, we consider three alternative methods to solving
-Equation~(\ref{eq:S}) to improve the speed and accuracy of the
-computation.
-
-\subsection{Taylor expanding the Doppler operator}
+\section{Taylor Expanding the Doppler operator \\ (and why this is a bad idea)}
 \label{sec:taylor}
 %
-One way to tackle the problem is to linearize the Doppler operator via
-a Taylor expansion in $\alpha$ about $\alpha=0$:
+An alternative way to tackle the problem is to linearize the Doppler 
+operator via a Taylor expansion in $\alpha$ about $\alpha=0$:
 %
@@
 for an example.
-
-\subsection{Taking the Fourier transform of the spectrum}
-\label{sec:fourier}
-%
-Recall the definition of the Fourier transform of a function $f(\xi)$,
-%
-\begin{align}
-    \label{eq:fourier:FT}
-    \mathcal{F}\Big[f(\xi)\Big](k) 
-    &\equiv
-    \int_{-\infty}^\infty
-        f(\xi)
-        \mathrm{e}^{-2\pi i k \xi} \mathrm{d}\xi
-    \nonumber \\
-    &=
-    \hat{f}(k)
-    \quad ,
-\end{align}
-%
-and the corresponding inverse Fourier transform,
-%
-\begin{align}
-    \label{eq:fourier:IFT}
-    \mathcal{F}^{-1}\Big[\hat{f}(k)\Big](\xi) 
-    &\equiv
-    \int_{-\infty}^\infty
-        \hat{f}(k)
-        \mathrm{e}^{2\pi i k \xi} \mathrm{d}k
-    \nonumber \\
-    &=
-    f(\xi)
-    \quad .
-\end{align}
-%
-Consider what happens when we take the
-Fourier transform of the spectrum $I(\xi, x, y)$ to obtain
-a function $\hat{I}(k, x, y)$. A useful property of the
-Fourier transform is that a translation of $I(\xi, x, y)$ by
-an amount $\Delta\xi$ corresponds to a linear scaling
-of $\hat{I}(k, x, y)$ by an amount $\mathrm{e}^{-2\pi i k \Delta\xi}$
-\citep[e.g.,][]{Schoenstadt2006}.
-Specifically, if the Doppler-shifted spectrum is given by
-%
-\begin{align}
-    I(\xi, x, y) &= I_0\big(\xi + \alpha(x, y)\big), x, y) \quad,
-\end{align}
-%
-its Fourier transform is equal to 
-%
-\begin{align}
-    \label{eq:fourier:translation}
-    \hat{I}(\xi, x, y) 
-    &= 
-    \mathrm{e}^{2\pi i k \alpha(x, y)}\hat{I_0}(k, x, y)
-    \quad ,
-\end{align}
-%
-where $\hat{I_0}(k, x, y) \equiv \mathcal{F}\left[ I_0(\xi, x, y) \right]$.
-%
-Much as in \S\ref{sec:taylor}, we have de-coupled the spatial and spectral
-terms, but this time without the need of a Taylor expansion. To obtain
-the observed spectrum, we
-expand $\hat{I_0}(k, x, y)$ in terms of spherical harmonics,
-%
-\begin{align}
-    \label{eq:fourier:I0}
-    \hat{I_0}(k, x, y) 
-        &=
-        \sum_{l=0}^\infty\sum_{m=-l}^{l} \hat{a}_{lm}(k) Y_{lm}(x, y)
-\end{align}
-%
-then take the inverse Fourier transform of the integral of 
-Equation~(\ref{eq:fourier:translation})
-over the visible disk $\mathcal{S}$ of the star:
-%
-\begin{align}
-    \label{eq:fourier:SYlm}
-    S(k) 
-    &=
-    \mathcal{F}^{-1}\Big[
-        \sum_{l=0}^\infty\sum_{m=-l}^{l}
-        \hat{a}_{lm}(k)
-        \iint\limits_{\mathcal{S}(x, y)}
-        Y_{lm}(x, y)
-        \mathrm{e}^{2\pi i k \alpha(x, y)}
-        \mathrm{d}\mathcal{S}(x, y)
-    \Big]
-    \nonumber \\
-    &=
-    \mathcal{F}^{-1}\Big[
-        \iint\limits_{\mathcal{S}(x, y)}
-        \bvec{Y}(x, y)
-        \mathrm{e}^{2\pi i k \alpha(x, y)}
-        \mathrm{d}\mathcal{S}(x, y)
-        \cdot
-        \bvec{\hat{a}}(k)
-    \Big]
-    \quad ,
-\end{align}
-%
-where
-%
-\begin{align}
-    \bvec{\hat{a}}(k) \equiv
-\left( 
-    \hat{a}_{0,0}(k) \quad\quad\quad\quad\quad\quad 
-    \hat{a}_{1,-1}(k) \quad\quad\quad\quad\quad\quad 
-    \hat{a}_{1,0}(k) \quad\quad\quad\quad\quad\quad
-    \hat{a}_{1,1}(k) \quad\quad\quad\quad\quad\quad 
-    ... 
-\right)^\top
-\end{align}
-%
-is the column vector of spherical harmonic coefficients at wavenumber $k$, and
-%
-\begin{align}
-    \bvec{Y}(x, y) \equiv 
-\left( 
-    Y_{0,0}(x, y) \quad\quad\quad\quad\quad\quad 
-    Y_{1,-1}(x, y) \quad\quad\quad\quad\quad\quad 
-    Y_{1,0}(x, y) \quad\quad\quad\quad\quad\quad 
-    Y_{1,1}(x, y) \quad\quad\quad\quad\quad\quad 
-    ... 
-\right)
-\end{align}
-%
-is the corresponding row vector of spherical harmonics at a point $(x, y)$ 
-on the sphere.
-
-In the case that the integration area $\mathcal{S}$ is the entire surface of
-the star, the integrals in Equation~(\ref{eq:fourier:SYlm}) are
-\emph{analytic}. To see this, we may change bases from spherical harmonics
-to polynomials on the sphere:
-%
-\begin{align}
-    \label{eq:fourier:SP}
-    S(k) 
-    &=
-    \mathcal{F}^{-1}\Big[
-        \iint\limits_{\mathcal{S}(x, y)}
-        \bvec{P}(x, y)
-        \mathrm{e}^{2\pi i k \alpha(x, y)}
-        \mathrm{d}\mathcal{S}(x, y)
-        \cdot
-        \bvec{A_1}
-        \bvec{\hat{a}}(k)
-    \Big]
-    \quad .
-\end{align}
-%
-where
-%
-\begin{align}
-    \bvec{P}(x, y) \equiv 
-\left( 
-    1 \quad\quad\quad\quad\quad\quad 
-    x \quad\quad\quad\quad\quad\quad 
-    z \quad\quad\quad\quad\quad\quad 
-    y \quad\quad\quad\quad\quad\quad 
-    x^2 \quad\quad\quad\quad\quad\quad 
-    xz \quad\quad\quad\quad\quad\quad 
-    xy \quad\quad\quad\quad\quad\quad
-    yz \quad\quad\quad\quad\quad\quad 
-    y^2 \quad\quad\quad\quad\quad\quad
-    ... 
-\right)^\top
-\end{align}
-%
-is the polynomial basis \citep[Equation 7 in][]{Luger2019}
-and $\bvec{A_1}$ is the change of basis matrix from spherical harmonics
-to polynomials 
-\citep[Equation B11 in][]{Luger2019}.
-
-% Bibliography
-\bibliography{bib}
-
-\end{document}

### 2019-06-16 tex/ms.tex
tweaks

@@
 %
-To obtain the Fourier transform of the observed spectrum, we
+To obtain the Fourier transform of the observed spectrum, we first
 expand $\hat{I_0}(k, x, y)$ in terms of spherical harmonics,
@@
         &=
-        \sum_{l=0}^\infty\sum_{m=-l}^{l} \hat{a}_{lm}(k) Y_{lm}(x, y)
-\end{align}
-%
-then take the integral of 
-Equation~(\ref{eq:fourier:translation})
-over the visible disk $\mathcal{S}$ of the star:
-%
-\begin{align}
-    \label{eq:fourier:SYlm}
-    \hat{S}(k) 
-    &=
-        \sum_{l=0}^\infty\sum_{m=-l}^{l}
-        \hat{a}_{lm}(k)
-        \iint\limits_{\mathcal{S}(x, y)}
-        Y_{lm}(x, y)
-        \mathrm{e}^{2\pi i k \alpha(x, y)}
-        \mathrm{d}\mathcal{S}(x, y)
+        \sum_{l=0}^\infty\sum_{m=-l}^{l} Y_{lm}(x, y) \hat{a}_{lm}(k)
     \nonumber \\
     &= 
-        \iint\limits_{\mathcal{S}(x, y)}
-        \tilde{\bvec{y}}(x, y)
-        \mathrm{e}^{2\pi i k \alpha(x, y)}
-        \mathrm{d}\mathcal{S}(x, y)
-        \cdot
-        \bvec{\hat{a}}(k)
+    \tilde{\bvec{y}}^\top(x, y) \cdot \bvec{\hat{a}}(k)
     \quad ,
@@
 \begin{align}
-    \tilde{\bvec{y}}(x, y) \equiv 
+    \tilde{\bvec{y}}^\top(x, y) \equiv 
 \Big( 
@@
 is the corresponding row vector of spherical harmonics at a point $(x, y)$ 
-on the sphere. In order to tackle the integrals in 
+on the sphere.
+%
+We then take the integral of Equation~(\ref{eq:fourier:translation})
+over the visible disk $\mathcal{S}$ of the star:
+%
+\begin{align}
+    \label{eq:fourier:SYlm}
+    \hat{S}(k) 
+    &=
+        \iint\limits_{\mathcal{S}(x, y)}
+        \tilde{\bvec{y}}^\top(x, y)
+        \mathrm{e}^{2\pi i k \alpha(x, y)}
+        \mathrm{d}\mathcal{S}(x, y)
+        \cdot
+        \bvec{\hat{a}}(k)
+    \quad ,
+\end{align}
+%
+In order to tackle the integrals in 
 Equation~(\ref{eq:fourier:SYlm}), let us change bases from spherical
@@
         \iint\limits_{\mathcal{S}(x, y)}
-        \tilde{\bvec{p}}(x, y)
+        \tilde{\bvec{p}}^\top(x, y)
         \mathrm{e}^{2\pi i k \alpha(x, y)}
@@
 \begin{align}
-    \tilde{\bvec{p}}(x, y) \equiv 
+    \tilde{\bvec{p}}^\top(x, y) \equiv 
 \Big( 
@@
     \iint\limits_{\mathcal{S}(x, y)}
-    \tilde{\bvec{p}}(x, y)
+    \tilde{\bvec{p}}^\top(x, y)
     \mathcal{F}^{-1} \Big[
@@
     \iint\limits_{\mathcal{S}(x, y)}
-    \tilde{\bvec{p}}(x, y)
+    \tilde{\bvec{p}}^\top(x, y)
     \delta\big(\xi - \alpha(x, y)\big)
@@
 $\delta$ function is zero, the equation may be written as a line integral 
-along some curve $\mathcal{C}(x, y)$ along which $\xi = \alpha(x, y)$:
+along some curve $\mathcal{C}(x, y)$ that satisfies $\alpha(x, y) = \xi$
+and $x^2 + y^2 \le 1$:
 %
@@
     \int\limits_{\mathcal{C}(x, y)}
-    \tilde{\bvec{p}}(x, y)
+    \tilde{\bvec{p}}^\top(x, y)
     \mathrm{d}\mathcal{C}(x, y)
@@
 
-\appendix
-
-\section{Taylor Expanding the Doppler operator \\ (and why this is a bad idea)}
-\label{sec:taylor}
-%
-An alternative way to tackle the problem is to linearize the Doppler 
-operator via a Taylor expansion in $\alpha$ about $\alpha=0$:
-%
-\begin{align}
-    \label{eq:taylor:I}
-    I(\xi, x, y) 
-        &=
-        I_0(\xi_0, x, y) \Bigg|_{\alpha=0}
-        + 
-        \frac{\mathrm{d}I_0(\xi_0, x, y)}{\mathrm{d}\alpha} \Bigg|_{\alpha=0} 
-            \Delta\alpha(x, y)
-        + 
-        \frac{1}{2}\frac{\mathrm{d}^2I_0(\xi_0, x, y)}{\mathrm{d}\alpha^2} 
-            \Bigg|_{\alpha=0} \Delta\alpha(x, y)^2
-        +
-        ... 
-\end{align}
-%
-Since the dependence of Equation~(\ref{eq:xi0}) on $\alpha$ is trivial,
-the derivatives of the spectrum $I_0(\xi_0)$ with respect to
-$\alpha$ are simply
-%
-\begin{align}
-    \frac{\mathrm{d}^nI_0(\xi_0, x, y)}{\mathrm{d}\alpha^n} &=
-    \dfrac{\mathrm{d}^nI_0(\xi_0, x, y)}{\mathrm{d}\xi_0^n} \nonumber\\ &\equiv
-    I_0^{(n)}(\xi_0, x, y)
-    \quad.
-\end{align}
-%
-Given this result, and noting that $\xi_0 = \xi$ when $\alpha = 0$,
-we may re-write Equation~(\ref{eq:taylor:I}) as
-%
-\begin{proof}{Taylor}
-    \label{eq:taylor:ISum}
-    I(\xi, x, y) 
-        &=
-        \sum_{n=0}^\infty
-            \frac{I_{0}^{(n)}(\xi, x, y)}{n!}
-            \Delta\alpha(x, y)^n
-        \quad ,
-\end{proof}
-%
-The utility of this expression is that the velocity dependence of the spectrum
-is now entirely encoded in the terms $\Delta\alpha(x, y)^n$, which are
-\emph{independent of wavelength}. We can further decouple the spatial
-dependence from the spectral dependence by expressing the intensity field
-as an expansion over spherical harmonics $Y_{lm}(x, y)$ in the sky-projected
-coordinates:
-%
-\begin{align}
-    I_0(\xi, x, y) = \sum_{l=0}^\infty\sum_{m=-l}^{l} a_{lm}(\xi) Y_{lm}(x, y)
-    \quad .
-\end{align}
-%
-Equation~(\ref{eq:taylor:ISum}) now reads
-%
-\begin{align}
-    \label{eq:taylor:IYlm}
-    I(\xi, x, y) 
-        &=
-        \sum_{n=0}^\infty
-            \sum_{l=0}^\infty\sum_{m=-l}^{l}
-                \frac{a_{lm}^{(n)}(\xi)}{n!}
-                Y_{lm}(x, y)\Delta\alpha(x, y)^n
-            \quad .
-\end{align}
-%
-Finally, integrating this equation over the visible disk of 
-the star, we arrive at an equation for the observed spectrum:
-%
-\begin{align}
-    \label{eq:taylor:S}
-    S(\xi) 
-        &=
-        \sum_{n=0}^\infty
-            \sum_{l=0}^\infty\sum_{m=-l}^{l}
-                \frac{a_{lm}^{(n)}(\xi)}{n!}
-                \iint\limits_{\mathcal{S}(x, y)}
-                Y_{lm}(x, y)\Delta\alpha(x, y)^n
-                \mathrm{d}{\mathcal{S}(x, y)}
-            \quad .
-\end{align}
-%
-By expanding the spectrum in both the spectral and spatial dimensions, we
-have effectively decoupled the two. However, Equation~(\ref{eq:taylor:S}) 
-is impractical for three reasons. First, the surface integrals can be very
-difficult to solve (although we will show later how these integrals may be
-approximated analytically). Second, it requires knowledge of high order 
-derivatives of the spectrum, which may not always be easy or convenient to 
-compute. Third, and most important, the series expansion in $n$ is typically 
-extremely slow to converge and is therefore only practically useful in the 
-limit that the Doppler shift is much smaller than the typical width of a 
-spectral line; see the notebook link next to Equation~(\ref{eq:taylor:ISum}) 
-for an example.
-
 % Bibliography

### 2019-06-18 tex/gitlinks.tex
woot

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/01e5eaaac7f32570634b33ad7aed7769c338a0d0/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/01e5eaaac7f32570634b33ad7aed7769c338a0d0/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/01e5eaaac7f32570634b33ad7aed7769c338a0d0/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/3428daf248495c61773970e1703192fbe198cb85/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/3428daf248495c61773970e1703192fbe198cb85/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/3428daf248495c61773970e1703192fbe198cb85/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-06-18 tex/ms.tex
woot

@@
         f(\xi)
-        \mathrm{e}^{-2\pi i k \xi} \mathrm{d}\xi
+        \mathrm{e}^{-2\pi \imag k \xi} \mathrm{d}\xi
     \nonumber \\
@@
         \hat{f}(k)
-        \mathrm{e}^{2\pi i k \xi} \mathrm{d}k
+        \mathrm{e}^{2\pi \imag k \xi} \mathrm{d}k
     \nonumber \\
@@
 an amount $\Delta\xi$ corresponds to a linear scaling
-of $\hat{I}(k, x, y)$ by an amount $\mathrm{e}^{-2\pi i k \Delta\xi}$
+of $\hat{I}(k, x, y)$ by an amount $\mathrm{e}^{-2\pi \imag k \Delta\xi}$
 \citep[e.g.,][]{Schoenstadt2006}.
@@
     &= 
-    \mathrm{e}^{2\pi i k \alpha(x, y)}\hat{I_0}(k, x, y)
+    \mathrm{e}^{2\pi \imag k \alpha(x, y)}\hat{I_0}(k, x, y)
     \quad ,
@@
         \tilde{\bvec{y}}^\top(x, y)
-        \mathrm{e}^{2\pi i k \alpha(x, y)}
+        \mathrm{e}^{2\pi \imag k \alpha(x, y)}
         \mathrm{d}\mathcal{S}(x, y)
@@
         \tilde{\bvec{p}}^\top(x, y)
-        \mathrm{e}^{2\pi i k \alpha(x, y)}
+        \mathrm{e}^{2\pi \imag k \alpha(x, y)}
         \mathrm{d}\mathcal{S}(x, y)
@@
         \bvec{A_1}
+        \cdot
         \bvec{\hat{a}}(k)
@@
 to polynomials 
-\citep[Equation B11 in][]{Luger2019}.
+\citep[Equation B11 in][]{Luger2019}. On the observer-facing surface of 
+the unit sphere, the coordinate $z$ is given by $\sqrt{1 - x^2 - y^2}$.
 
@@
 \begin{align}
-    \label{eq:convolve:SUgly}
+    \label{eq:convolve:SUgly1}
     S(\xi) 
@@
         \tilde{\bvec{p}}^\top(x, y)
-        \mathrm{e}^{2\pi i k \alpha(x, y)}
+        \mathrm{e}^{2\pi \imag k \alpha(x, y)}
         \mathrm{d}\mathcal{S}(x, y)
+        \cdot
+        \bvec{A_1}
     \Bigg]
     \circ
-    \bvec{A_1}
     \bvec{a}(\xi)
@@
 \begin{align}
-    \label{eq:convolve:SUgly}
+    \label{eq:convolve:SUgly2}
     S(\xi) 
@@
     \mathcal{F}^{-1} \Big[
-        \mathrm{e}^{2\pi i k \alpha(x, y)}
+        \mathrm{e}^{2\pi \imag k \alpha(x, y)}
     \Big]
     \mathrm{d}\mathcal{S}(x, y)
+    \cdot
+    \bvec{A_1}
     \circ
-    \bvec{A_1}
     \bvec{a}(\xi)
@@
     \mathrm{d}\mathcal{S}(x, y)
+    \cdot
+    \bvec{A_1}
     \circ
-    \bvec{A_1}
     \bvec{a}(\xi)
@@
 $\delta$ function is zero, the equation may be written as a line integral 
-along some curve $\mathcal{C}(x, y)$ that satisfies $\alpha(x, y) = \xi$
-and $x^2 + y^2 \le 1$:
+along some curve $\mathcal{C}(x, y)$ whose points satisfy 
+$\alpha(x, y) = \xi$
+and lie within $\mathcal{S}$:
 %
 \begin{align}
-    \label{eq:convolve:SUgly}
+    \label{eq:convolve:S}
     S(\xi) 
     &=    
+    \mathbf{g}(\xi)
+    \circ
+    \bvec{a}(\xi)
+    \quad,
+\end{align}
+%
+where we define
+%
+\begin{align}
+    \label{eq:convolve:g}
+    \mathbf{g}(\xi) 
+    &\equiv    
+    \mathbf{s}^\top(\xi) 
+    \cdot
+    \bvec{A_1}
+\end{align}
+%
+and
+%
+\begin{align}
+    \label{eq:convolve:sT}
+    \mathbf{s}^\top(\xi) 
+    &\equiv    
     \int\limits_{\mathcal{C}(x, y)}
@@
     \mathrm{d}\mathcal{C}(x, y)
-    \circ
-    \bvec{A_1}
-    \bvec{a}(\xi)
+    \quad.
+\end{align}
+
+In order to solve Equation~(\ref{eq:convolve:S}), we must assume 
+explicit functional
+forms for the velocity field $\alpha(x, y)$ and the region of integration
+$\mathcal{S}$, which we do in the following sections.
+
+\section{Doppler imaging of rigid rotators}
+\label{sec:rigid}
+%
+In the case that the star's rotation is rigid (i.e., differential rotation
+is negligible), the radial velocity at any point on the surface is 
+simply proportional to the distance to the axis of rotation. Without loss
+of generality, if we assume the axis of rotation lies along the $y-z$ plane,
+we have
+%
+\begin{align}
+    \beta(x, y) = \frac{\omega \sin i \, x}{c}
+\end{align}
+%
+and
+%
+\begin{align}
+    \label{eq:rigid:alpha}
+    \alpha(x, y) = \ln\left( 1 - \frac{\omega \sin i \, x}{c} \right)
+    \quad ,
+\end{align}
+%
+where $\omega$ is the angular velocity of the star and $i$ is the
+inclination relative to $\hat{y}$. Furthermore, if
+we assume the star is unocculted, the region of integration $\mathcal{S}$ 
+is simply the unit disk, so $\mathcal{C}(x, y)$ is the set of all points
+that satisfy both $\alpha(x, y) = \xi$ and $x^2 + y^2 \le 1$.
+Solving Equation~(\ref{eq:rigid:alpha}) for $x$ and 
+setting $\alpha(x, y) = \xi$, we find that the curves $\mathcal{C}(x, y)$ 
+are simply vertical lines on the unit disk given by
+%
+\begin{align}
+    x &= 
+        \frac{c}{\omega\sin i} \left(1 - \mathrm{e}^{\xi}\right)
+    \nonumber \\
+    &\equiv \gamma(\xi)
+    \quad .
+\end{align}
+%
+The integral in Equation~(\ref{eq:convolve:sT}) is therefore just an integral
+over $y$:
+%
+\begin{align}
+    \label{eq:rigid:sT}
+    \bvec{s}^\top(\xi) 
+    &=    
+    \int\limits_{-\sqrt{1 - \gamma(\xi)^2}}^{\sqrt{1 - \gamma(\xi)^2}}
+    \tilde{\bvec{p}}^\top
+    \Big(\gamma(\xi), y\Big)
+    \mathrm{d}y
+    \quad .
+\end{align}
+%
+From \citet{Luger2019}, the $n^\mathrm{th}$ term of the polynomial basis
+is a polynomial in $x$, $y$, and $z = \sqrt{1 - x^2 - y^2}$:
+%
+\begin{proof}{PolynomialBasis}
+    \tilde{p}_n 
+    &=
+    x^i y^j z^k
+\end{proof}
+%
+where $i, j, k$ are integers given by
+%
+\begin{proof}{PolynomialBasis}
+    \label{eq:lm}
+    i &= \floor*{\Lambda - \Delta}
+    \nonumber \\[0.5em]
+    j &= \floor*{\Delta}
+    \nonumber \\[0.5em]
+    k &= \ceil*{\Delta} - \floor*{\Delta}
+\end{proof}
+%
+with
+%
+\begin{proof}{PolynomialBasis}
+    \Lambda &= \floor*{\sqrt{n}}
+    \nonumber \\[0.5em]
+    \Delta &= \frac{n - \Lambda^2}{2}
+    \quad .
+\end{proof}
+%
+We may now explicitly write down the $n^\mathrm{th}$ term of 
+Equation~(\ref{eq:rigid:sT}),
+%
+\begin{align}
+    s_n(\xi) 
+    &=    
+    \begin{dcases}
+        \gamma(\xi)^i
+        \int\limits_{-\sqrt{1 - \gamma(\xi)^2}}^{\sqrt{1 - \gamma(\xi)^2}}
+            y^j
+        \mathrm{d}y
+        &
+        \qquad k = 0
+        \\[1em]
+        \gamma(\xi)^i
+        \int\limits_{-\sqrt{1 - \gamma(\xi)^2}}^{\sqrt{1 - \gamma(\xi)^2}}
+            y^j
+            \sqrt{1 - \gamma(\xi)^2 - y^2} \,
+        \mathrm{d}y 
+        & 
+        \qquad k = 1 \quad ,
+    \end{dcases}
+\end{align}
+%
+and solve it analytically:
+%
+\begin{align}
+        \label{eq:rigid:sTAnalytic}
+        s_n(\xi) 
+        &=     
+    \begin{dcases}
+        \frac{2 \gamma(\xi)^i \big(1 - \gamma(\xi)^ 2\big)^{\frac{j + 1}{2}}}{j + 1}
+        &
+        \qquad k = 0 \,\,\, \& \,\,\, j \, \mathrm{even}
+        \\[1em]
+        \gamma(\xi)^{i} \mathcal{I}_{j}\big(\gamma(\xi)\big)
+        &
+        \qquad k = 1 \,\,\, \& \,\,\, j \, \mathrm{even}
+        \\[1em]
+        0
+        &
+        \qquad j \, \mathrm{odd} \quad,
+    \end{dcases}
+\end{align}
+%
+where $\mathcal{I}_j(\gamma)$ is computed analytically
+from the upward recurrence relation given by Equation~(\ref{eq:app:Ij}),
+with $\mathcal{I}_0(\gamma)$ given by Equation~(\ref{eq:app:I0}).
+
+\appendix
+
+\section{Integrals}
+\subsection{Equation~(\ref{eq:rigid:sTAnalytic})}
+%
+When $k = 1$, we may write the $n^\mathrm{th}$ component
+of Equation~(\ref{eq:rigid:sTAnalytic}) as
+%
+\begin{align}
+    s_n(\xi) = 
+        \gamma(\xi)^{i}
+        \mathcal{I}_{j}\big(\gamma(\xi)\big)
+\end{align}
+%
+where
+%
+\begin{align}
+    \mathcal{I}_j(\gamma) &\equiv
+    \int\limits_{-\sqrt{1-\gamma^2}}^{\sqrt{1-\gamma^2}}
+        y^{j}
+        \sqrt{1 - \gamma^2 - y^2} \,
+    \mathrm{d}y
     \quad.
@@
 %
+Substituting $y = \sin\psi\sqrt{1 - \gamma^2}$, we have
+%
+\begin{align}
+    \mathcal{I}_j(\gamma) &=
+    %
+    (1 - \gamma^2)^{\frac{j + 2}{2}}
+    \int\limits_{-\frac{\pi}{2}}^{\frac{\pi}{2}}
+        \sin^j\psi
+        \cos^2\psi \,
+    \mathrm{d}\psi
+    \quad.
+\end{align}
+%
+We may solve this integral using the recurrence relation
+%
+\begin{align}
+    \int
+        \sin^j\psi
+        \cos^m\psi \,
+    \mathrm{d}\psi
+    &=
+    -\frac{\sin^{j-1}\psi \cos^{m+1}\psi}{j + m}
+    +
+    \frac{j - 1}{j + m}\int\sin^{j-2}\psi \cos^m\psi \mathrm{d}\psi
+    \quad ,
+\end{align}
+%
+which, in our case, simplifies to
+%
+\begin{align}
+    \int\limits_{-\frac{\pi}{2}}^{\frac{\pi}{2}}
+        \sin^j\psi
+        \cos^2\psi \,
+    \mathrm{d}\psi
+    &=
+    \frac{j - 1}{j + 2}\int\limits_{-\frac{\pi}{2}}^{\frac{\pi}{2}}\sin^{j-2}\psi \cos^2\psi \mathrm{d}\psi
+    \quad.
+\end{align}
+%
+We thus arrive at the recurrence relation
+%
+\begin{align}
+    \label{eq:app:Ij}
+    \mathcal{I}_j(\gamma) &=
+    \frac{j - 1}{j + 2}
+    (1 - \gamma^2)
+    \mathcal{I}_{j-2}(\gamma)
+    \quad.
+\end{align}
+%
+Since this expression is only used when $j$ is even, we only need one
+initial condition for upward recursion:
+%
+\begin{align}
+    \label{eq:app:I0}
+    \mathcal{I}_0(\gamma) &\equiv
+    \int\limits_{-\sqrt{1-\gamma^2}}^{\sqrt{1-\gamma^2}}
+        \sqrt{1 - \gamma^2 - y^2} \,
+    \mathrm{d}y
+    \nonumber \\
+    &= \frac{\pi}{2}(1 - \gamma^2)
+    \quad.
+\end{align}
 

### 2019-06-20 tex/gitlinks.tex
added luminosity attribute

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/3428daf248495c61773970e1703192fbe198cb85/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/3428daf248495c61773970e1703192fbe198cb85/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/3428daf248495c61773970e1703192fbe198cb85/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/20af4c44c5da64772f41f1bf46eeb2d730a15e55/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/20af4c44c5da64772f41f1bf46eeb2d730a15e55/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/20af4c44c5da64772f41f1bf46eeb2d730a15e55/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-06-20 tex/ms.tex
added luminosity attribute

@@
     \Bigg]
-    \circ
+    *
     \bvec{a}(\xi)
@@
 where the second line follows from the convolution theorem, with
-$\circ$ denoting the convolution operator over $\xi$ and 
-$\bvec{a}(\xi) \equiv \mathcal{F}^{-1}\left[ \bvec{\hat{a}}(k) \right]$.
+$\bvec{a}(\xi) \equiv \mathcal{F}^{-1}\left[ \bvec{\hat{a}}(k) \right]$
+and $*$ denoting the convolution operator over $\xi$:
+%
+\begin{align}
+    (f * g)(\xi) \equiv \int\limits_{-\infty}^{\infty}f(\tau)g(\xi - \tau)\mathrm{d}\tau
+\end{align}
+%
 Since only the exponential term in the integrand depends on $k$, we may 
@@
     \bvec{A_1}
-    \circ
+    *
     \bvec{a}(\xi)
@@
     \mathbf{g}(\xi)
-    \circ
+    *
     \bvec{a}(\xi)

### 2019-07-02 tex/gitlinks.tex
writing

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/20af4c44c5da64772f41f1bf46eeb2d730a15e55/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/20af4c44c5da64772f41f1bf46eeb2d730a15e55/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/20af4c44c5da64772f41f1bf46eeb2d730a15e55/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/eb7d083b11987bee6d9b5f4615518f4746270309/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/eb7d083b11987bee6d9b5f4615518f4746270309/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/eb7d083b11987bee6d9b5f4615518f4746270309/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-07-02 tex/ms.tex
writing

--- 2019-06-16 tex/ms.tex
@@
 %
-\author{Probably David W. Hogg}
+\author{David W. Hogg}
 \affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
@@
 %
-Let $I(\xi, x, y)$ be the Doppler-shifted intensity observed at log wavelength 
-$\xi \equiv \ln\lambda$ at sky-projected Cartesian position $x, y$ on the 
-surface of the star. We may express it as
+Let $I_\xi(\xi, \mathbf{x}, t, \mathbf{d})$ be the specific 
+intensity observed 
+at log wavelength $\xi \equiv \ln\lambda$ and at sky-projected 
+Cartesian position $\mathbf{x} = (x, y, z)$ on the surface of the 
+star at time $t$, where
+$\mathbf{d}$ is a set of arbitrary parameters of the Doppler field.
+We may express this intensity as
 %
 \begin{align}
-    \label{eq:I}
-    I(\xi, x, y) &= I_0(\xi_0, x, y)
+    \label{eq:intro:Ixi}
+    I_\xi(\xi, \mathbf{x}, t, \mathbf{d}) &= 
+        I_{\xi}^0(\xi_0(\mathbf{x}, \mathbf{d}), \mathbf{x}, t)
 \end{align}
 %
-where $I_0$ is the spectrum at each point on the star in the surface rest
-frame and 
+where $I_{\xi}^0$ is the specific intensity at each point on the star 
+in the surface rest frame and 
 %
 \begin{align}
-    \label{eq:xi0}
-    \xi_0 &= \xi + \alpha(x, y)
+    \label{eq:intro:xi0}
+    \xi_0(\mathbf{x}, \mathbf{d}) &= \xi + \mathcal{D}(\mathbf{x}, \mathbf{d})
 \end{align}
 %
-is the log wavelength in the unshifted frame. The quantity $\alpha$ is
+is the log wavelength in the rest frame. The quantity $\mathcal{D}$ is
 computed from the formula for the Doppler shift and is equal to
@@
 \begin{align}
-    \label{eq:alpha}
-    \alpha(x, y) 
+    \label{eq:intro:D}
+    \mathcal{D}(\mathbf{x}, \mathbf{d}) 
         &=
         \frac{1}{2}\ln\left( 
-            \frac{1 - \beta}{1 + \beta} 
+            \frac{1 - \beta(\mathbf{x}, \mathbf{d})}{1 + \beta(\mathbf{x}, \mathbf{d})} 
         \right)
-        \nonumber \\
-        &\approx
-        \ln(1 - \beta)
 \end{align}
 %
-where $\beta = v(x, y) / c$ is the ratio of the 
-radial velocity at a point on the surface of the star to the speed of light
-and the second line is valid when $\beta \ll 1$ (i.e., the non-relativistic
-Doppler shift). Throughout this paper, we will assume the non-relativistic 
-limit, as it greatly simplifies the math.
+where $\beta = v(\mathbf{x}, \mathbf{d}) / c$ is the ratio of the 
+radial velocity at a point on the surface of the star to the speed of light.
 In keeping with the literature, we take positive values of $v$ to mean 
@@
 A common approach to computing the Doppler-shifted spectrum is to
-evaluate the spectrum at the rest frame wavelength (Equation~\ref{eq:xi0})
+evaluate the spectrum at the rest frame wavelength 
+(Equation~\ref{eq:intro:xi0})
 and interpolate back to the grid in $\xi$. This is practical when
 computing the spectrum at a single \emph{point} on the surface, but not
-ideal when one is interested in the \emph{integral} over the entire
+ideal when one is interested in the \emph{integral} over the visible
 surface of the star $\mathcal{S}$, which is typically all we can observe:
 %
+% TODO: We may need to divide by the distance ^ 2 for unit consistency
 \begin{align}
-    \label{eq:S}
-    S(\xi) 
+    \label{eq:intro:Fxi}
+    F_\xi(\xi, t) 
         &\equiv
-        \iint\limits_{\mathcal{S}(x, y)}
-                I(\xi, x, y)
-        \mathrm{d}{\mathcal{S}(x, y)}
+        \iint\limits_{\mathcal{S}(\mathbf{x})}
+                I(\xi, \mathbf{x}, t, \mathbf{d})
+        \mathrm{d}{\mathcal{S}(\mathbf{x})}
         \quad .
@@
 %
-The difficulty in solving Equation~(\ref{eq:S}) stems from the fact
-that $I(\xi, x, y)$ is difficult to write down in closed form, given
+The difficulty in solving Equation~(\ref{eq:intro:Fxi}) stems from the fact
+that $I_\xi(\xi, \mathbf{x}, t, \mathbf{d})$ is difficult to write down in closed form, given
 the non-linearity of the Doppler shift.
@@
 
-In this section, we consider two alternative methods to solving
-Equation~(\ref{eq:S}) to improve the speed and accuracy of the
-computation, both of which rely on the Fourier transform of the
-spectrum.
-Recall the definition of the Fourier transform of a function $f(\xi)$,
+The observed spectrum is a complex function
+of spatial, spectral, temporal, and velocity terms. The goal in this
+section is to deconvolve each of these terms to make solving the integral
+in Equation~(\ref{eq:intro:Fxi}) easier.
+%
+The first thing we will do is to expand the spatial dependence of the
+specific intensity in terms of spherical harmonics on the unit disk:
 %
 \begin{align}
-    \label{eq:fourier:FT}
-    \mathcal{F}\Big[f(\xi)\Big](k) 
-    &\equiv
-    \int_{-\infty}^\infty
-        f(\xi)
-        \mathrm{e}^{-2\pi i k \xi} \mathrm{d}\xi
-    \nonumber \\
+    \label{eq:solution:Ixi0}
+    I_{\xi}^0(\xi_0, \mathbf{x}, t) 
         &=
-    \hat{f}(k)
+        \sum_{l=0}^\infty\sum_{m=-l}^{l} a_{lm}(\xi_0, t) Y_{lm}(\mathbf{x})
     \quad ,
@@
 %
-and the corresponding inverse Fourier transform,
+where $Y_{lm}(\mathbf{x})$ is a spherical harmonic on the projected disk
+and $a_{lm}(\xi_0, t)$ is the corresponding spherical harmonic 
+coefficient at log wavelength in the rest frame $\xi_0$ and time $t$. For 
+convenience, we may write this equation in vector form:
 %
 \begin{align}
-    \label{eq:fourier:IFT}
-    \mathcal{F}^{-1}\Big[\hat{f}(k)\Big](\xi) 
-    &\equiv
-    \int_{-\infty}^\infty
-        \hat{f}(k)
-        \mathrm{e}^{2\pi i k \xi} \mathrm{d}k
-    \nonumber \\
-    &=
-    f(\xi)
-    \quad .
-\end{align}
-%
-Consider what happens when we take the
-Fourier transform of the spectrum $I(\xi, x, y)$ to obtain
-a function $\hat{I}(k, x, y)$, where we refer to $k$ as a ``wavenumber''. 
-A useful property of the
-Fourier transform is that a translation of $I(\xi, x, y)$ by
-an amount $\Delta\xi$ corresponds to a linear scaling
-of $\hat{I}(k, x, y)$ by an amount $\mathrm{e}^{-2\pi i k \Delta\xi}$
-\citep[e.g.,][]{Schoenstadt2006}.
-Specifically, if the Doppler-shifted spectrum is given by
-%
-\begin{align}
-    I(\xi, x, y) &= I_0\big(\xi + \alpha(x, y)\big), x, y) \quad,
-\end{align}
-%
-its Fourier transform is equal to 
-%
-\begin{align}
-    \label{eq:fourier:translation}
-    \hat{I}(\xi, x, y) 
-    &= 
-    \mathrm{e}^{2\pi i k \alpha(x, y)}\hat{I_0}(k, x, y)
-    \quad ,
-\end{align}
-%
-where $\hat{I_0}(k, x, y) \equiv \mathcal{F}\left[ I_0(\xi, x, y) \right]$.
-%
-To obtain the Fourier transform of the observed spectrum, we first
-expand $\hat{I_0}(k, x, y)$ in terms of spherical harmonics,
-%
-\begin{align}
-    \label{eq:fourier:I0}
-    \hat{I_0}(k, x, y) 
-        &=
-        \sum_{l=0}^\infty\sum_{m=-l}^{l} Y_{lm}(x, y) \hat{a}_{lm}(k)
-    \nonumber \\
-    &= 
-    \tilde{\bvec{y}}^\top(x, y) \cdot \bvec{\hat{a}}(k)
+    \label{eq:solution:Ixi0vec}
+    I_{\xi}^0(\xi_0, \mathbf{x}, t) &=
+    \tilde{\bvec{y}}^\top(\mathbf{x})
+    \bvec{a}(\xi_0, t)
     \quad ,
@@
 \begin{align}
-    \bvec{\hat{a}}(k) \equiv
+    \bvec{a}(\xi_0, t) \equiv
 \Big( 
-    \hat{a}_{0,0}(k) \quad\quad\quad\quad\quad\quad 
-    \hat{a}_{1,-1}(k) \quad\quad\quad\quad\quad\quad 
-    \hat{a}_{1,0}(k) \quad\quad\quad\quad\quad\quad
-    \hat{a}_{1,1}(k) \quad\quad\quad\quad\quad\quad 
+    a_{0,0}(\xi_0, t) \quad\quad\quad\quad\quad\quad 
+    a_{1,-1}(\xi_0, t) \quad\quad\quad\quad\quad\quad 
+    a_{1,0}(\xi_0, t) \quad\quad\quad\quad\quad\quad
+    a_{1,1}(\xi_0, t) \quad\quad\quad\quad\quad\quad 
     ... 
@@
 %
-is the column vector of spherical harmonic coefficients at wavenumber $k$, and
+is the vector of spherical harmonic coefficients and
 %
 \begin{align}
-    \tilde{\bvec{y}}^\top(x, y) \equiv 
+    \tilde{\bvec{y}}^\top(\mathbf{x}) \equiv 
 \Big( 
-    Y_{0,0}(x, y) \quad\quad\quad\quad\quad\quad 
-    Y_{1,-1}(x, y) \quad\quad\quad\quad\quad\quad 
-    Y_{1,0}(x, y) \quad\quad\quad\quad\quad\quad 
-    Y_{1,1}(x, y) \quad\quad\quad\quad\quad\quad 
+    Y_{0,0}(\mathbf{x}) \quad\quad\quad\quad\quad\quad 
+    Y_{1,-1}(\mathbf{x}) \quad\quad\quad\quad\quad\quad 
+    Y_{1,0}(\mathbf{x}) \quad\quad\quad\quad\quad\quad 
+    Y_{1,1}(\mathbf{x}) \quad\quad\quad\quad\quad\quad 
     ... 
@@
 %
-is the corresponding row vector of spherical harmonics at a point $(x, y)$ 
-on the sphere.
-%
-We then take the integral of Equation~(\ref{eq:fourier:translation})
-over the visible disk $\mathcal{S}$ of the star:
+is the corresponding vector of spherical harmonics. We may further
+decompose our expression by linearizing the time dependence of the
+spherical harmonic coefficients:
 %
 \begin{align}
-    \label{eq:fourier:SYlm}
-    \hat{S}(k) 
-    &=
-        \iint\limits_{\mathcal{S}(x, y)}
-        \tilde{\bvec{y}}^\top(x, y)
-        \mathrm{e}^{2\pi i k \alpha(x, y)}
-        \mathrm{d}\mathcal{S}(x, y)
-        \cdot
-        \bvec{\hat{a}}(k)
+    \label{eq:solution:R}
+    \bvec{a}(\xi_0, t) = \mathbf{R}(t) \bvec{a}(\xi_0)
     \quad ,
@@
 %
-In order to tackle the integrals in 
-Equation~(\ref{eq:fourier:SYlm}), let us change bases from spherical
-harmonics to polynomials on the sphere:
+where $\bvec{a}(\xi_0) = \bvec{a}(\xi_0, t=t_0)$ for some reference time $t_0$.
+For rigid body rotation, the result is exact and $\mathbf{R}(t)$ is the Wigner 
+rotation matrix for real spherical harmonics 
+\citep[e.g.][]{AlvarezCollado1989}, which is implicitly a 
+function of the inclination, obliquity, and rotation period of the star.
+In the case that other processes such as differential rotation or spot 
+evolution are significant
+over the course of an observation, Equation~(\ref{eq:solution:R}) can be
+made to hold approximately for some effective rotation matrix 
+$\mathbf{R}(t)$; we discuss this further below.
+
+The equation for the specific intensity now reads
 %
 \begin{align}
-    \label{eq:fourier:S}
-    \hat{S}(k) 
+    \label{eq:solution:Ixi0vecfull}
+    I_{\xi}^0(\xi_0, \mathbf{x}, t) &=
+    \tilde{\bvec{y}}^\top(\mathbf{x})
+    \mathbf{R}(t)
+    \bvec{a}(\xi_0)
+    \quad ,
+\end{align}
+%
+where it is clear that we have fully separated the spatial, temporal, and
+spectral terms. However, in order to compute the observed spectrum, we must
+still Doppler shift this expression and integrate it over the visible
+portion of the star. To this end, it is convenient to express the Doppler
+shift as a convolution
+of the spectrum in the rest frame with a delta function:
+%
+\begin{align}
+    I_\xi(\xi, \mathbf{x}, t) &= 
+        I_{\xi}^0(\zeta, \mathbf{x}, t) 
+        * \delta\big(\zeta - \mathcal{D}(\mathbf{x}, \mathbf{d})\big)
+        \quad,
+\end{align}
+%
+where $*$ denotes the convolution operation over a dummy (log wavelength-like)
+parameter
+$\zeta$, returning a function of the shifted log wavelength, $\xi$.
+Inserting this into Equation~(\ref{eq:solution:Ixi0vecfull}) and integrating
+over the visible portion of the star, we arrive at the expression for the 
+observed spectrum:
+%
+%
+\begin{align}
+    \label{eq:solution:Fxi}
+    F_{\xi}(\xi, t) &=
+    \iint\limits_{\mathcal{S}(\mathbf{x})}
+    \tilde{\bvec{y}}^\top(\mathbf{x})
+    \mathbf{R}(t)
+    \bvec{a}(\zeta)
+    * \delta\big(\zeta - \mathcal{D}(\mathbf{x}, \mathbf{d})\big)
+    \mathrm{d}\mathcal{S}(\mathbf{x})
+    \nonumber \\[0.5em]
     &=
-        \iint\limits_{\mathcal{S}(x, y)}
-        \tilde{\bvec{p}}^\top(x, y)
-        \mathrm{e}^{2\pi i k \alpha(x, y)}
-        \mathrm{d}\mathcal{S}(x, y)
-        \cdot
+    \mathbf{g}^\top(\zeta, \mathbf{d})
+    *
+    \,
+    \mathbf{R}(t)
+    \,
+    \bvec{a}(\zeta)
+    \quad ,
+\end{align}
+%
+%
+where we made use of the commutativity of the convolution operator and 
+the fact that the integral is taken only over the spatial dimensions.
+We further define
+%
+\begin{align}
+    \label{eq:solution:g}
+    \mathbf{g}^\top(\zeta, \mathbf{d})
+    &\equiv
+    \iint\limits_{\mathcal{S}(\mathbf{x})}
+    \tilde{\bvec{y}}^\top(\mathbf{x})
+    \delta\big(\zeta - \mathcal{D}(\mathbf{x}, \mathbf{d})\big)
+    \mathrm{d}\mathcal{S}(\mathbf{x})
+    \nonumber \\[0.5em]
+    &=  
+    \int\limits_{\mathcal{C}(\mathbf{x}, \mathbf{d})}
+    \tilde{\bvec{y}}^\top(\mathbf{x})
+    \mathrm{d}\mathcal{C}(\mathbf{x}, \mathbf{d})
+    \quad.
+\end{align}
+%
+where the integral in the second line denotes the line integral about
+some function $\mathcal{C}(\mathbf{x}, \mathbf{d})$ corresponding to the
+set of all points on the visible disk where 
+$\zeta = \mathcal{D}(\mathbf{x}, \mathbf{d})$.
+
+Equation~(\ref{eq:solution:Fxi}) is the complete deconvolution of the
+observed spectrum into velocity terms, temporal terms, and spectral/spatial
+terms, respectively. In the following sections, we will discuss how to
+efficiently solve Equation~(\ref{eq:solution:g}).
+
+\section{Doppler imaging of rigid rotators}
+\label{sec:rigid}
+%
+In the case that the star's rotation is rigid (i.e., differential rotation
+is negligible) and other effects such as convective blueshift
+may be ignored, the radial velocity at any point on the surface is 
+simply proportional to the distance to the axis of rotation. Without loss
+of generality, if we assume the axis of rotation lies along the $y-z$ plane,
+we have
+%
+\begin{align}
+    \beta(\mathbf{x}, \mathbf{d}) = \frac{\omega \sin i \, x}{c}
+\end{align}
+%
+and
+%
+\begin{align}
+    \label{eq:rigid:D}
+    \mathcal{D}(\mathbf{x}, \mathbf{d}) &= 
+        \frac{1}{2}\ln\left( 
+            \dfrac{1 - \dfrac{\omega \sin i \, x}{c}}
+                 {1 + \dfrac{\omega \sin i \, x}{c}}
+        \right)
+    \quad ,
+\end{align}
+%
+where the parameters $\mathbf{d}$ of the Doppler field are the
+angular velocity, $\omega$, and the inclination of the star with
+respect to $\hat{y}$, $i$.
+
+In order to solve Equation~(\ref{eq:solution:g}), let us change basis from
+spherical harmonics to polynomials on the sphere:
+%
+\begin{align}
+    \label{eq:rigid:g}
+    \mathbf{g}^\top(\zeta, \mathbf{d}) &\equiv
+    \bvec{s}^\top(\zeta, \mathbf{d})
     \bvec{A_1}
-        \bvec{\hat{a}}(k)
-    \quad .
 \end{align}
@@
 \begin{align}
-    \tilde{\bvec{p}}^\top(x, y) \equiv 
+    \label{eq:rigid:sTdef}
+    \mathbf{s}^\top(\zeta, \mathbf{d})
+    &\equiv
+    \int\limits_{\mathcal{C}(\mathbf{x}, \mathbf{d})}
+    \tilde{\bvec{p}}^\top(\mathbf{x})
+    \mathrm{d}\mathcal{C}(\mathbf{x}, \mathbf{d})
+\end{align}
+%
+is the vector of integral solutions for each spherical harmonic,
+%
+\begin{align}
+    \tilde{\bvec{p}}(\mathbf{x}) \equiv 
 \Big( 
@@
     ... 
-\Big)
+\Big)^\top
 \end{align}
 %
-is the polynomial basis \citep[Equation 7 in][]{Luger2019}
+is the polynomial basis \citep[Equation 7 in][]{Luger2019},
 and $\bvec{A_1}$ is the change of basis matrix from spherical harmonics
 to polynomials 
-\citep[Equation B11 in][]{Luger2019}.
+\citep[Equation B11 in][]{Luger2019}. On the observer-facing surface of 
+the unit sphere, the coordinate $z$ is given by $\sqrt{1 - x^2 - y^2}$.
 
-At this point, we have two options: we can remain in Fourier space and
-attempt to solve the surface integral in Equation~(\ref{eq:fourier:S})
-directly, or we can take the inverse Fourier transform of  
-Equation~(\ref{eq:fourier:S}) and attempt to solve the integral in
-log wavelength space. As we will see, there are advantages (and
-disadvantages) to both methods. We do the former in \S\ref{sec:analytic}
-in the latter in \S\ref{sec:convolve}.
-
-\subsection{Analytic solutions}
-\label{sec:analytic}
-In the case that the integration area $\mathcal{S}$ is the entire surface of
-the star, the integrals in Equation~(\ref{eq:fourier:S}) are
-\emph{analytic}. \xxx{Show here how the result can be computed from the 
-hypergeometric function $_3F_2.$}
-
-\subsection{Doppler shifts as a convolution}
-\label{sec:convolve}
-
-If we take the inverse Fourier transform of Equation~(\ref{eq:fourier:S}),
-we arrive at an expression for the observed spectrum:
+If
+we assume the star is unocculted, the region of integration $\mathcal{S}$ 
+is simply the unit disk, so $\mathcal{C}(\mathbf{x}, \mathbf{d})$ 
+is the set of all points
+that satisfy both $\mathcal{D}(\mathbf{x}, \mathbf{d}) = \zeta$ and 
+$x^2 + y^2 \le 1$.
+Solving Equation~(\ref{eq:rigid:D}) for $x$ and 
+setting $\mathcal{D}(\mathbf{x}, \mathbf{d}) = \zeta$, we find that 
+the curves $\mathcal{C}(\mathbf{x}, \mathbf{d})$ 
+are simply vertical lines on the unit disk given by
 %
 \begin{align}
-    \label{eq:convolve:SUgly}
-    S(\xi) 
+    x &= 
+        \Bigg(\frac{c}{\omega\sin i}\Bigg) 
+        \Bigg(\frac{1 - \mathrm{e}^{2\zeta}}{1 + \mathrm{e}^{2\zeta}}\Bigg)
+    \nonumber \\
+    &\equiv \gamma(\zeta, \mathbf{d})
+    \quad .
+\end{align}
+%
+The integral in Equation~(\ref{eq:rigid:sTdef}) is therefore just an integral
+over $y$:
+%
+\begin{align}
+    \label{eq:rigid:sT}
+    \bvec{s}^\top(\zeta, \mathbf{d}) 
     &=    
-    \mathcal{F}^{-1} \Bigg[\,\,\,
-        \iint\limits_{\mathcal{S}(x, y)}
-        \tilde{\bvec{p}}^\top(x, y)
-        \mathrm{e}^{2\pi i k \alpha(x, y)}
-        \mathrm{d}\mathcal{S}(x, y)
-        \cdot
-        \bvec{A_1}
-        \bvec{\hat{a}}(k)
-    \Bigg] \nonumber \\
+    \int\limits_{-\sqrt{1 - \gamma(\zeta, \mathbf{d})^2}}^
+                {\sqrt{1 - \gamma(\zeta, \mathbf{d})^2}}
+    \tilde{\bvec{p}}^\top
+    \Big(\gamma(\zeta, \mathbf{d}), y\Big)
+    \mathrm{d}y
+    \quad .
+\end{align}
+%
+From \citet{Luger2019}, the $n^\mathrm{th}$ term of the polynomial basis
+is a polynomial in $x$, $y$, and $z = \sqrt{1 - x^2 - y^2}$:
+%
+\begin{proof}{PolynomialBasis}
+    \tilde{p}_n 
     &=
-    \mathcal{F}^{-1} \Bigg[\,\,\,
-        \iint\limits_{\mathcal{S}(x, y)}
-        \tilde{\bvec{p}}^\top(x, y)
-        \mathrm{e}^{2\pi i k \alpha(x, y)}
-        \mathrm{d}\mathcal{S}(x, y)
-    \Bigg]
-    \circ
-    \bvec{A_1}
-    \bvec{a}(\xi)
+    x^i y^j z^k
+\end{proof}
+%
+where $i, j, k$ are integers given by
+%
+\begin{proof}{PolynomialBasis}
+    \label{eq:lm}
+    i &= \floor*{\Lambda - \Delta}
+    \nonumber \\[0.5em]
+    j &= \floor*{\Delta}
+    \nonumber \\[0.5em]
+    k &= \ceil*{\Delta} - \floor*{\Delta}
+\end{proof}
+%
+with
+%
+\begin{proof}{PolynomialBasis}
+    \Lambda &= \floor*{\sqrt{n}}
+    \nonumber \\[0.5em]
+    \Delta &= \frac{n - \Lambda^2}{2}
+    \quad .
+\end{proof}
+%
+We may now explicitly write down the $n^\mathrm{th}$ term of 
+Equation~(\ref{eq:rigid:sT}),
+%
+\begin{align}
+    s_n(\zeta, \mathbf{d}) 
+    &=    
+    \gamma(\zeta, \mathbf{d})^i
+    \int\limits_{-\sqrt{1 - \gamma(\zeta, \mathbf{d})^2}}^
+                {\sqrt{1 - \gamma(\zeta, \mathbf{d})^2}}
+        y^j
+        \sqrt{1 - \gamma(\zeta, \mathbf{d})^2 - y^2}^k \,
+    \mathrm{d}y 
     \quad ,
@@
 %
-where the second line follows from the convolution theorem, with
-$\circ$ denoting the convolution operator over $\xi$ and 
-$\bvec{a}(\xi) \equiv \mathcal{F}^{-1}\left[ \bvec{\hat{a}}(k) \right]$.
-Since only the exponential term in the integrand depends on $k$, we may 
-further simplify this expression:
+and solve it analytically:
 %
 \begin{align}
-    \label{eq:convolve:SUgly}
-    S(\xi) 
+        \label{eq:rigid:sTAnalytic}
+        s_n(\zeta, \mathbf{d}) 
         &=     
-    \iint\limits_{\mathcal{S}(x, y)}
-    \tilde{\bvec{p}}^\top(x, y)
-    \mathcal{F}^{-1} \Big[
-        \mathrm{e}^{2\pi i k \alpha(x, y)}
-    \Big]
-    \mathrm{d}\mathcal{S}(x, y)
-    \circ
-    \bvec{A_1}
-    \bvec{a}(\xi)
-    \nonumber \\
-    &=    
-    \iint\limits_{\mathcal{S}(x, y)}
-    \tilde{\bvec{p}}^\top(x, y)
-    \delta\big(\xi - \alpha(x, y)\big)
-    \mathrm{d}\mathcal{S}(x, y)
-    \circ
-    \bvec{A_1}
-    \bvec{a}(\xi)
-    \quad,
+    \begin{dcases}
+        0
+        &
+        \qquad j \, \mathrm{odd}
+        \\[1em]
+        \frac{2 \gamma(\zeta, \mathbf{d})^i 
+        \big(1 - \gamma(\zeta, \mathbf{d})^ 2\big)^{\frac{j + 1}{2}}}{j + 1}
+        &
+        \qquad k = 0
+        \\[1em]
+        \gamma(\zeta, \mathbf{d})^{i} \mathcal{I}_{j}
+        \big(\gamma(\zeta, \mathbf{d})\big)
+        &
+        \qquad k = 1
+        \quad ,
+    \end{dcases}
 \end{align}
 %
-where $\delta$ is the Dirac delta function. Since the integrand in the
-equation above is zero everywhere except where the argument of the
-$\delta$ function is zero, the equation may be written as a line integral 
-along some curve $\mathcal{C}(x, y)$ that satisfies $\alpha(x, y) = \xi$
-and $x^2 + y^2 \le 1$:
+where $\mathcal{I}_j(\gamma)$ is computed analytically
+from the upward recurrence relation given by Equation~(\ref{eq:app:Ij}),
+with $\mathcal{I}_0(\gamma)$ given by Equation~(\ref{eq:app:I0}).
+
+\appendix
+
+\section{Integrals}
+\subsection{Equation~(\ref{eq:rigid:sTAnalytic})}
+%
+When $k = 1$, we may write the $n^\mathrm{th}$ component
+of Equation~(\ref{eq:rigid:sTAnalytic}) as
 %
 \begin{align}
-    \label{eq:convolve:SUgly}
-    S(\xi) 
-    &=    
-    \int\limits_{\mathcal{C}(x, y)}
-    \tilde{\bvec{p}}^\top(x, y)
-    \mathrm{d}\mathcal{C}(x, y)
-    \circ
-    \bvec{A_1}
-    \bvec{a}(\xi)
+    s_n(\zeta, \mathbf{d}) = 
+        \gamma(\zeta, \mathbf{d})^{i}
+        \mathcal{I}_{j}\big(\gamma(\zeta, \mathbf{d})\big)
+\end{align}
+%
+where
+%
+\begin{align}
+    \mathcal{I}_j(\gamma) &\equiv
+    \int\limits_{-\sqrt{1-\gamma^2}}^{\sqrt{1-\gamma^2}}
+        y^{j}
+        \sqrt{1 - \gamma^2 - y^2} \,
+    \mathrm{d}y
     \quad.

### 2019-07-02 tex/gitlinks.tex
better notation

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/eb7d083b11987bee6d9b5f4615518f4746270309/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/eb7d083b11987bee6d9b5f4615518f4746270309/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/eb7d083b11987bee6d9b5f4615518f4746270309/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/3e0f48e4bb8ff5966748e55ca6c681051db1d652/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/3e0f48e4bb8ff5966748e55ca6c681051db1d652/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/3e0f48e4bb8ff5966748e55ca6c681051db1d652/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-07-02 tex/ms.tex
better notation

@@
 %
-Let $I_\xi(\xi, \mathbf{x}, t, \mathbf{d})$ be the specific 
+Let $I(\xi, \mathbf{x}, t, \mathbf{d})$ be the specific 
 intensity observed 
@@
     \label{eq:intro:Ixi}
-    I_\xi(\xi, \mathbf{x}, t, \mathbf{d}) &= 
-        I_{\xi}^0(\xi_0(\mathbf{x}, \mathbf{d}), \mathbf{x}, t)
+    I(\xi, \mathbf{x}, t, \mathbf{d}) &= 
+        I_0\Big(\xi_0(\xi, \mathbf{x}, \mathbf{d}), \mathbf{x}, t\Big)
 \end{align}
 %
-where $I_{\xi}^0$ is the specific intensity at each point on the star 
+where $I_0$ is the specific intensity at each point on the star 
 in the surface rest frame and 
@@
     \label{eq:intro:xi0}
-    \xi_0(\mathbf{x}, \mathbf{d}) &= \xi + \mathcal{D}(\mathbf{x}, \mathbf{d})
+    \xi_0(\xi, \mathbf{x}, \mathbf{d}) &= 
+    \xi + \mathcal{D}(\mathbf{x}, \mathbf{d})
 \end{align}
@@
         \frac{1}{2}\ln\left( 
-            \frac{1 - \beta(\mathbf{x}, \mathbf{d})}{1 + \beta(\mathbf{x}, \mathbf{d})} 
+            \frac{1 - \beta(\mathbf{x}, \mathbf{d})}{1 + \beta(\mathbf{x}, 
+            \mathbf{d})} 
         \right)
@@
 %
-% TODO: We may need to divide by the distance ^ 2 for unit consistency
 \begin{align}
     \label{eq:intro:Fxi}
-    F_\xi(\xi, t) 
+    F(\xi, t) 
         &\equiv
@@
         \mathrm{d}{\mathcal{S}(\mathbf{x})}
-        \quad .
+        \quad ,
 \end{align}
@@
 The difficulty in solving Equation~(\ref{eq:intro:Fxi}) stems from the fact
-that $I_\xi(\xi, \mathbf{x}, t, \mathbf{d})$ is difficult to write down in closed form, given
+that $I(\xi, \mathbf{x}, t, \mathbf{d})$ is difficult to write down in 
+closed form, given
 the non-linearity of the Doppler shift.
@@
     \label{eq:solution:Ixi0}
-    I_{\xi}^0(\xi_0, \mathbf{x}, t) 
+    I_0(\xi_0, \mathbf{x}, t) 
         &=
@@
     \label{eq:solution:Ixi0vec}
-    I_{\xi}^0(\xi_0, \mathbf{x}, t) &=
+    I_0(\xi_0, \mathbf{x}, t) &=
     \tilde{\bvec{y}}^\top(\mathbf{x})
@@
     \label{eq:solution:Ixi0vecfull}
-    I_{\xi}^0(\xi_0, \mathbf{x}, t) &=
+    I_0(\xi_0, \mathbf{x}, t) &=
     \tilde{\bvec{y}}^\top(\mathbf{x})
@@
 \begin{align}
-    I_\xi(\xi, \mathbf{x}, t) &= 
-        I_{\xi}^0(\zeta, \mathbf{x}, t) 
-        * \delta\big(\zeta - \mathcal{D}(\mathbf{x}, \mathbf{d})\big)
+    I(\xi, \mathbf{x}, t) &= 
+        I_0(\xi_0, \mathbf{x}, t) 
+        * \delta\big(\xi_0 - \xi - \mathcal{D}(\mathbf{x}, \mathbf{d})\big)
         \quad,
@@
 %
-where $*$ denotes the convolution operation over a dummy (log wavelength-like)
-parameter
-$\zeta$, returning a function of the shifted log wavelength, $\xi$.
+where $*$ denotes the convolution operation, 
+returning a function of the shifted log wavelength, $\xi$.
 Inserting this into Equation~(\ref{eq:solution:Ixi0vecfull}) and integrating
@@
     \label{eq:solution:Fxi}
-    F_{\xi}(\xi, t) &=
+    F(\xi, t) &=
     \iint\limits_{\mathcal{S}(\mathbf{x})}
@@
     \mathbf{R}(t)
-    \bvec{a}(\zeta)
-    * \delta\big(\zeta - \mathcal{D}(\mathbf{x}, \mathbf{d})\big)
+    \bvec{a}(\xi_0)
+    * \delta\big(\xi_0 - \xi - \mathcal{D}(\mathbf{x}, \mathbf{d})\big)
     \mathrm{d}\mathcal{S}(\mathbf{x})
@@
     &=
-    \mathbf{g}^\top(\zeta, \mathbf{d})
+    \mathbf{g}^\top(\mathcal{D})
     *
@@
     \,
-    \bvec{a}(\zeta)
+    \bvec{a}(\xi_0)
     \quad ,
@@
     \label{eq:solution:g}
-    \mathbf{g}^\top(\zeta, \mathbf{d})
+    \mathbf{g}^\top(\mathcal{D})
     &\equiv
@@
     \tilde{\bvec{y}}^\top(\mathbf{x})
-    \delta\big(\zeta - \mathcal{D}(\mathbf{x}, \mathbf{d})\big)
+    \delta\big(\xi_0 - \xi - \mathcal{D}(\mathbf{x}, \mathbf{d})\big)
     \mathrm{d}\mathcal{S}(\mathbf{x})
@@
 set of all points on the visible disk where 
-$\zeta = \mathcal{D}(\mathbf{x}, \mathbf{d})$.
+$\xi_0 - \xi = \mathcal{D}(\mathbf{x}, \mathbf{d})$.
 
@@
     \label{eq:rigid:g}
-    \mathbf{g}^\top(\zeta, \mathbf{d}) &\equiv
-    \bvec{s}^\top(\zeta, \mathbf{d})
+    \mathbf{g}^\top(\mathcal{D}) &\equiv
+    \bvec{s}^\top(\mathcal{D})
     \bvec{A_1}
@@
     \label{eq:rigid:sTdef}
-    \mathbf{s}^\top(\zeta, \mathbf{d})
+    \mathbf{s}^\top(\mathcal{D})
     &\equiv
@@
 is the set of all points
-that satisfy both $\mathcal{D}(\mathbf{x}, \mathbf{d}) = \zeta$ and 
+that satisfy both $\xi_0 - \xi = \mathcal{D}(\mathbf{x}, \mathbf{d})$ and 
 $x^2 + y^2 \le 1$.
-Solving Equation~(\ref{eq:rigid:D}) for $x$ and 
-setting $\mathcal{D}(\mathbf{x}, \mathbf{d}) = \zeta$, we find that 
+Solving Equation~(\ref{eq:rigid:D}) for $x$, we find that 
 the curves $\mathcal{C}(\mathbf{x}, \mathbf{d})$ 
@@
 \begin{align}
-    x &= 
+    x(\mathcal{D}) &= 
         \Bigg(\frac{c}{\omega\sin i}\Bigg) 
-        \Bigg(\frac{1 - \mathrm{e}^{2\zeta}}{1 + \mathrm{e}^{2\zeta}}\Bigg)
-    \nonumber \\
-    &\equiv \gamma(\zeta, \mathbf{d})
+        \Bigg(\frac{1 - \mathrm{e}^{2\mathcal{D}}}
+                   {1 + \mathrm{e}^{2\mathcal{D}}}\Bigg)
     \quad .
@@
     \label{eq:rigid:sT}
-    \bvec{s}^\top(\zeta, \mathbf{d}) 
+    \bvec{s}^\top(\mathcal{D}) 
     &=    
-    \int\limits_{-\sqrt{1 - \gamma(\zeta, \mathbf{d})^2}}^
-                {\sqrt{1 - \gamma(\zeta, \mathbf{d})^2}}
+    \int\limits_{-\sqrt{1 - x(\mathcal{D})^2}}^
+                {\sqrt{1 - x(\mathcal{D})^2}}
     \tilde{\bvec{p}}^\top
-    \Big(\gamma(\zeta, \mathbf{d}), y\Big)
+    \Big(x(\mathcal{D}), y\Big)
     \mathrm{d}y
@@
 \begin{align}
-    s_n(\zeta, \mathbf{d}) 
+    s_n(\mathcal{D}) 
     &=    
-    \gamma(\zeta, \mathbf{d})^i
-    \int\limits_{-\sqrt{1 - \gamma(\zeta, \mathbf{d})^2}}^
-                {\sqrt{1 - \gamma(\zeta, \mathbf{d})^2}}
+    x(\mathcal{D})^i
+    \int\limits_{-\sqrt{1 - x(\mathcal{D})^2}}^
+                {\sqrt{1 - x(\mathcal{D})^2}}
         y^j
-        \sqrt{1 - \gamma(\zeta, \mathbf{d})^2 - y^2}^k \,
+        \left(1 - x(\mathcal{D})^2 - y^2\right)^{\frac{k}{2}} \,
     \mathrm{d}y 
@@
         \label{eq:rigid:sTAnalytic}
-        s_n(\zeta, \mathbf{d}) 
+        s_n(\mathcal{D}) 
         &=     
@@
         \\[1em]
-        \frac{2 \gamma(\zeta, \mathbf{d})^i 
-        \big(1 - \gamma(\zeta, \mathbf{d})^ 2\big)^{\frac{j + 1}{2}}}{j + 1}
+        \frac{2 x(\mathcal{D})^i 
+        \big(1 - x(\mathcal{D})^ 2\big)^{\frac{j + 1}{2}}}{j + 1}
         &
@@
         \\[1em]
-        \gamma(\zeta, \mathbf{d})^{i} \mathcal{I}_{j}
-        \big(\gamma(\zeta, \mathbf{d})\big)
+        x(\mathcal{D})^{i} \mathcal{I}_{j}
+        \big(x(\mathcal{D})\big)
         &
@@
 %
-where $\mathcal{I}_j(\gamma)$ is computed analytically
+where $\mathcal{I}_j(x)$ is computed analytically
 from the upward recurrence relation given by Equation~(\ref{eq:app:Ij}),
-with $\mathcal{I}_0(\gamma)$ given by Equation~(\ref{eq:app:I0}).
+with $\mathcal{I}_0(x)$ given by Equation~(\ref{eq:app:I0}).
 
@@
 \begin{align}
-    s_n(\zeta, \mathbf{d}) = 
-        \gamma(\zeta, \mathbf{d})^{i}
-        \mathcal{I}_{j}\big(\gamma(\zeta, \mathbf{d})\big)
+    s_n(\mathcal{D}) = 
+        x(\mathcal{D})^{i}
+        \mathcal{I}_{j}\big(x(\mathcal{D})\big)
 \end{align}
@@
 \begin{align}
-    \mathcal{I}_j(\gamma) &\equiv
-    \int\limits_{-\sqrt{1-\gamma^2}}^{\sqrt{1-\gamma^2}}
+    \mathcal{I}_j(x) &\equiv
+    \int\limits_{-\sqrt{1-x^2}}^{\sqrt{1-x^2}}
         y^{j}
-        \sqrt{1 - \gamma^2 - y^2} \,
+        \sqrt{1 - x^2 - y^2} \,
     \mathrm{d}y
@@
 %
-Substituting $y = \sin\psi\sqrt{1 - \gamma^2}$, we have
+Substituting $y = \sin\psi\sqrt{1 - x^2}$, we have
 %
 \begin{align}
-    \mathcal{I}_j(\gamma) &=
+    \mathcal{I}_j(x) &=
     %
-    (1 - \gamma^2)^{\frac{j + 2}{2}}
+    (1 - x^2)^{\frac{j + 2}{2}}
     \int\limits_{-\frac{\pi}{2}}^{\frac{\pi}{2}}
@@
     \label{eq:app:Ij}
-    \mathcal{I}_j(\gamma) &=
+    \mathcal{I}_j(x) &=
     \frac{j - 1}{j + 2}
-    (1 - \gamma^2)
-    \mathcal{I}_{j-2}(\gamma)
+    (1 - x^2)
+    \mathcal{I}_{j-2}(x)
     \quad.
@@
     \label{eq:app:I0}
-    \mathcal{I}_0(\gamma) &\equiv
-    \int\limits_{-\sqrt{1-\gamma^2}}^{\sqrt{1-\gamma^2}}
-        \sqrt{1 - \gamma^2 - y^2} \,
+    \mathcal{I}_0(x) &\equiv
+    \int\limits_{-\sqrt{1-x^2}}^{\sqrt{1-x^2}}
+        \sqrt{1 - x^2 - y^2} \,
     \mathrm{d}y
     \nonumber \\
-    &= \frac{\pi}{2}(1 - \gamma^2)
+    &= \frac{\pi}{2}(1 - x^2)
     \quad.

### 2019-07-03 tex/gitlinks.tex
more text

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/3e0f48e4bb8ff5966748e55ca6c681051db1d652/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/3e0f48e4bb8ff5966748e55ca6c681051db1d652/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/3e0f48e4bb8ff5966748e55ca6c681051db1d652/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/40d52a59e985547aaf7d10e12ac20e4c2247ac4d/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/40d52a59e985547aaf7d10e12ac20e4c2247ac4d/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/40d52a59e985547aaf7d10e12ac20e4c2247ac4d/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-07-03 tex/ms.tex
more text

@@
     \xi_0(\xi, \mathbf{x}, \mathbf{d}) &= 
-    \xi + \mathcal{D}(\mathbf{x}, \mathbf{d})
+    \xi - \mathcal{D}(\mathbf{x}, \mathbf{d})
 \end{align}
@@
 is the log wavelength in the rest frame. The quantity $\mathcal{D}$ is
-computed from the formula for the Doppler shift and is equal to
+the Doppler shift in log wavelength space:
 %
@@
         \frac{1}{2}\ln\left( 
-            \frac{1 - \beta(\mathbf{x}, \mathbf{d})}{1 + \beta(\mathbf{x}, 
+            \frac{1 + \beta(\mathbf{x}, \mathbf{d})}{1 - \beta(\mathbf{x}, 
             \mathbf{d})} 
@@
 radial velocity at a point on the surface of the star to the speed of light.
-In keeping with the literature, we take positive values of $v$ to mean 
-redshifts.
+In keeping with the literature, we take positive values of $v$ (and
+$\mathcal{D}$) to mean redshifts.
 
@@
         I_0(\xi_0, \mathbf{x}, t) 
-        * \delta\big(\xi_0 - \xi - \mathcal{D}(\mathbf{x}, \mathbf{d})\big)
+        * \delta\big(\mathcal{D}(\mathbf{x}, \mathbf{d}) - (\xi - \xi_0)\big)
         \quad,
@@
     \bvec{a}(\xi_0)
-    * \delta\big(\xi_0 - \xi - \mathcal{D}(\mathbf{x}, \mathbf{d})\big)
+    * \delta\big(\mathcal{D}(\mathbf{x}, \mathbf{d}) - (\xi - \xi_0)\big)
     \mathrm{d}\mathcal{S}(\mathbf{x})
@@
 \begin{align}
-    \label{eq:solution:g}
+    \label{eq:solution:gT}
     \mathbf{g}^\top(\mathcal{D})
@@
     \tilde{\bvec{y}}^\top(\mathbf{x})
-    \delta\big(\xi_0 - \xi - \mathcal{D}(\mathbf{x}, \mathbf{d})\big)
+    \delta\big(\mathcal{D}(\mathbf{x}, \mathbf{d}) - (\xi - \xi_0)\big)
     \mathrm{d}\mathcal{S}(\mathbf{x})
@@
 set of all points on the visible disk where 
-$\xi_0 - \xi = \mathcal{D}(\mathbf{x}, \mathbf{d})$.
+$\mathcal{D}(\mathbf{x}, \mathbf{d}) = \xi - \xi_0$.
 
@@
 terms, respectively. In the following sections, we will discuss how to
-efficiently solve Equation~(\ref{eq:solution:g}).
+efficiently solve Equation~(\ref{eq:solution:gT}).
 
@@
         \frac{1}{2}\ln\left( 
-            \dfrac{1 - \dfrac{\omega \sin i \, x}{c}}
-                 {1 + \dfrac{\omega \sin i \, x}{c}}
+            \dfrac{1 + \dfrac{\omega \sin i \, x}{c}}
+                 {1 - \dfrac{\omega \sin i \, x}{c}}
         \right)
@@
 
-In order to solve Equation~(\ref{eq:solution:g}), let us change basis from
+In order to solve Equation~(\ref{eq:solution:gT}), let us change basis from
 spherical harmonics to polynomials on the sphere:
@@
 \begin{align}
-    \label{eq:rigid:g}
+    \label{eq:rigid:gT}
     \mathbf{g}^\top(\mathcal{D}) &\equiv
@@
 
-If
-we assume the star is unocculted, the region of integration $\mathcal{S}$ 
+\begin{figure}[h!]
+    \begin{centering}
+    \includegraphics[width=\linewidth]{figures/g_rigid.pdf}
+    \oscaption{g_rigid}{%
+        The Doppler $\mathbf{g}$ basis for a rigidly rotating star
+        computed from Equation~(\ref{eq:rigid:gT}) and
+        Equation~(\ref{eq:rigid:sTAnalytic}) up to spherical 
+        harmonic degree $l=10$. Rows correspond to the degree $l$ and
+        columns correspond to the order $m$. These functions encode
+        the contribution of each spherical harmonic to the rotational
+        broadening of features in the stellar spectrum. Because the
+        rotational axis is chosen to be aligned with $\hat{y}$,
+        none of the $m < 0$ harmonics contribute
+        \label{fig:g_rigid}
+    }
+    \end{centering}
+\end{figure}
+
+If we assume the star is unocculted, the region of integration $\mathcal{S}$ 
 is simply the unit disk, so $\mathcal{C}(\mathbf{x}, \mathbf{d})$ 
 is the set of all points
-that satisfy both $\xi_0 - \xi = \mathcal{D}(\mathbf{x}, \mathbf{d})$ and 
+that satisfy both $\mathcal{D}(\mathbf{x}, \mathbf{d}) = \xi - \xi_0$ and 
 $x^2 + y^2 \le 1$.
@@
         \Bigg(\frac{c}{\omega\sin i}\Bigg) 
-        \Bigg(\frac{1 - \mathrm{e}^{2\mathcal{D}}}
-                   {1 + \mathrm{e}^{2\mathcal{D}}}\Bigg)
+        \Bigg(\frac{\mathrm{e}^{2\mathcal{D}} - 1}
+                   {\mathrm{e}^{2\mathcal{D}} + 1}\Bigg)
     \quad .
@@
 with $\mathcal{I}_0(x)$ given by Equation~(\ref{eq:app:I0}).
+%
+Figure~\ref{fig:g_rigid} shows the $\mathbf{g}$ basis computed from
+the formulae above and Equation~(\ref{eq:rigid:gT}) up to spherical 
+harmonic degree $l=10$.
 
+\begin{figure}[p!]
+    \begin{centering}
+    \includegraphics[width=0.6\linewidth]{figures/spot_rigid.pdf}
+    \oscaption{spot_rigid}{%
+        A caption.
+        \label{fig:spot_rigid}
+    }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[h!]
+    \begin{centering}
+    \includegraphics[width=0.65\linewidth]{figures/compare_rigid.pdf}
+    \oscaption{compare_rigid}{%
+        A caption.
+        \label{fig:compare_rigid}
+    }
+    \end{centering}
+\end{figure}
+
+%
+%
+%
+%
 \appendix
+%
+%
+%
+%
 
@@
     &=
-    \frac{j - 1}{j + 2}\int\limits_{-\frac{\pi}{2}}^{\frac{\pi}{2}}\sin^{j-2}\psi \cos^2\psi \mathrm{d}\psi
+    \frac{j - 1}{j + 2}\int\limits_{-\frac{\pi}{2}}^
+        {\frac{\pi}{2}}\sin^{j-2}\psi \cos^2\psi \mathrm{d}\psi
     \quad.

### 2019-07-03 tex/figures/compare_rigid.py

@@ -1,0 +1,77 @@
+# -*- coding: utf-8 -*-
+import matplotlib.pyplot as plt
+from mpl_toolkits.axes_grid1.inset_locator import inset_axes
+import numpy as np
+from scipy.signal import convolve
+import starry
+from utils import RigidRotationSolver
+
+
+# Instantiate a map with a Gaussian spot
+lmax = 20
+N = (lmax + 1) ** 2
+map = starry.Map(lmax, lazy=False)
+map.add_spot(amp=-0.1, sigma=0.05, lat=30, lon=30)
+ylm = np.array(map.y)
+
+# Check that the specific intensity is positive everywhere
+assert np.nanmin(map.render()) > 0
+
+# Log wavelength array
+xi = np.linspace(-2e-5, 2e-5, 9999)
+dxi = xi[1] - xi[0]
+obs = np.abs(xi) < 1e-5
+
+# A Gaussian absorption line
+amp = 1.0
+mu = 0.0
+sigma = 3e-7
+a0 = 1 - amp * np.exp(-0.5 * (xi - mu) ** 2 / sigma ** 2)
+wsini_c = 2.0e-6
+
+# Starry
+maxD = 0.5 * np.log((1 + wsini_c) / (1 - wsini_c))
+D = xi[(xi >= -maxD) & (xi <= maxD)]
+solver = RigidRotationSolver(lmax)
+g = solver.g(D, wsini_c)
+a = np.dot(ylm.reshape(-1, 1), a0.reshape(1, -1))
+S = np.zeros_like(xi)
+for n in range(N):
+    S += convolve(a[n], g[:, n], mode="same")
+S /= S[obs][0]
+
+# Numerical
+res_arr = [50, 100, 300] #, 600]
+Snum = [np.zeros_like(xi) for i in range(len(res_arr))]
+for i, res in enumerate(res_arr):
+    image = np.tile(map.render(res=res).reshape(-1, 1), len(xi))
+    x, y, z = map.ops.compute_ortho_grid(res).eval()
+    D = 0.5 * np.log((1 + wsini_c * x) / (1 - wsini_c * x))
+    spec = np.interp(xi + D.reshape(-1, 1), xi, a0)
+    Snum[i] = np.nansum(image * spec, axis=0)
+    Snum[i] /= Snum[i][0]
+
+# Compare
+fig, ax = plt.subplots(2, sharex=True, figsize=(8, 8))
[…]

### 2019-07-03 tex/figures/spot_rigid.py

@@ -1,0 +1,102 @@
+# -*- coding: utf-8 -*-
+import matplotlib.pyplot as plt
+import numpy as np
+from scipy.signal import convolve
+import starry
+from utils import RigidRotationSolver
+
+
+# Instantiate a map with a Gaussian spot
+lmax = 20
+N = (lmax + 1) ** 2
+map = starry.Map(lmax, lazy=False)
+map.add_spot(amp=-0.1, sigma=0.05, lat=30)
+ylm = np.array(map.y)
+
+# Check that the specific intensity is positive everywhere
+assert np.nanmin(map.render()) > 0
+
+# Log wavelength array
+xi = np.linspace(-2e-5, 2e-5, 9999)
+dxi = xi[1] - xi[0]
+obs = np.abs(xi) < 1e-5
+
+# A Gaussian absorption line
+amp = 1.0
+mu = 0.0
+sigma = 3e-7
+a0 = 1 - amp * np.exp(-0.5 * (xi - mu) ** 2 / sigma ** 2)
+
+# The Doppler `g` function
+solver = RigidRotationSolver(lmax)
+npts = 1000
+wsini_c = 2.0e-6
+maxD = 0.5 * np.log((1 + wsini_c) / (1 - wsini_c))
+D = xi[(xi >= -maxD) & (xi <= maxD)]
+g = solver.g(D, wsini_c)
+
+# Set up the plot
+nt = 15
+theta = np.linspace(-90, 90, nt)
+fig, ax = plt.subplots(nt, 3, figsize=(6, 12))
+fig.subplots_adjust(hspace=0.3)
+cmap = plt.get_cmap("plasma")
+img = map.render()
+vmin = np.nanmin(img)
+vmax = np.nanmax(img)
+rng = vmax - vmin
+vmin -= 0.1 * rng
+vmax += 0.1 * rng
+
+# Compute the spectrum when the spot is on 
+# the backside for reference
+map.rotate(180)
+a = np.dot(map.y.reshape(-1, 1), a0.reshape(1, -1))
+S0 = np.zeros_like(xi)
+for n in range(N):
+    S0 += convolve(a[n], g[:, n], mode="same")
+S0 -= S0[obs][0]
+
+# Compute & plot each spectrum
+for t in range(nt):
+    # Rotate & compute spectrum
+    map[1:, :] = ylm[1:]
+    map.rotate(theta[t])
[…]

### 2019-07-03 tex/figures/uniform.py

@@ -1,198 +1,0 @@
-# -*- coding: utf-8 -*-
-import numpy as np
-import matplotlib.pyplot as plt
-from scipy.special import jv, gamma
-import mpmath
-
-def _hyp2f1(a, b, c, z):
-    """
-    The Hypergeometric function 2F1 for 
-    complex-valued arguments.
-    
-    """
-    res = mpmath.hyp2f1(a, b, c, z)
-    return float(res.real) + float(res.imag) * 1j
-
-# Vectorize it
-hyp2f1 = np.vectorize(_hyp2f1)
-
-
-def randu(lo=0, hi=1, size=1):
-    """
-    Return random numbers sampled uniformly between
-    ``lo`` and ``hi``.
-
-    """
-    return lo + (hi - lo) * np.random.rand(size)
-
-
-def I_num(xi, I0, alpha=0):
-    """
-    Return the shifted spectrum, computed numerically.
-    
-    """
-    xi0 = xi + alpha
-    return np.interp(xi0, xi, I0)
-
-
-def S_num(xi, I0, alpha=0, npts=1000):
-    """
-    Return the disk-integrated spectrum, computed numerically.
-    
-    """
-    S = np.zeros_like(xi)
-    A = 0
-    beta = np.exp(alpha) - 1
-    for x in np.linspace(-1, 1, npts + 2)[1:-1]:
-        beta_x = beta * x
-        alpha_x = np.log(1 + beta_x)
-        S += I_num(xi, I0, alpha=alpha_x) * np.sqrt(1 - x ** 2)
-        A += np.sqrt(1 - x ** 2)
-    return np.pi * S / A
-
-
-def I(xi, I0, alpha=0):
-    """
-    Return the shifted spectrum, computed via an FFT.
-    
-    """
-    # Number of wavelength bins
-    N = len(xi)
-    
-    # Take the FFT
-    fI0 = np.fft.rfft(I0)
-    k = np.fft.rfftfreq(N, xi[1] - xi[0])
-    
-    # Apply the translation
-    fI0 *= np.exp(2 * np.pi * alpha * 1j * k)
-    
-    # Take the inverse FFT and return
-    return np.fft.irfft(fI0, N)
-
-
-def S(xi, I0, alpha=0, method="exact", order=2, kmax=None):
-    """
-    Return the disk-integrated spectrum, computed via an FFT.
-    This uses the non-relativistic Doppler formula.
-
-    """
-    # Number of wavelength bins
-    N = len(xi)
-    
[…]

### 2019-07-03 tex/gitlinks.tex
nothin

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/40d52a59e985547aaf7d10e12ac20e4c2247ac4d/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/40d52a59e985547aaf7d10e12ac20e4c2247ac4d/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/40d52a59e985547aaf7d10e12ac20e4c2247ac4d/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/91e40d1f56ca84e6a02a7a8d0a650deefdd735aa/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/91e40d1f56ca84e6a02a7a8d0a650deefdd735aa/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/91e40d1f56ca84e6a02a7a8d0a650deefdd735aa/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-07-03 tex/gitlinks.tex
stuff

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/91e40d1f56ca84e6a02a7a8d0a650deefdd735aa/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/91e40d1f56ca84e6a02a7a8d0a650deefdd735aa/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/91e40d1f56ca84e6a02a7a8d0a650deefdd735aa/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/a5f045717b27f4123fcdb1f0bcc4048d6ec47be9/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/a5f045717b27f4123fcdb1f0bcc4048d6ec47be9/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/a5f045717b27f4123fcdb1f0bcc4048d6ec47be9/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-07-03 tex/ms.tex
stuff

@@
         rotational axis is chosen to be aligned with $\hat{y}$,
-        none of the $m < 0$ harmonics contribute
+        none of the $m < 0$ harmonics contribute to the observed
+        spectrum.
         \label{fig:g_rigid}
@@
     \oscaption{spot_rigid}{%
-        A caption.
+        Time evolution of a Gaussian absorption line on a rigidly rotating, 
+        spotted star computed from the analytic formulae in \S\ref{sec:rigid}.
+        The stellar surface is modeled as a spherical harmonic expansion
+        up to $l=20$, and the line shape is assumed to be the same everywhere;
+        the spot simply downweights the local intensity at all wavelengths.
+        As the spot rotates into view (left panel), the line shape changes
+        slightly (center panel). The residuals between the line when the
+        spot is in view (solid) and when it is on the backside of the star
+        (dotted) are shown in the right panel, where
+        a Gaussian-like feature can be seen tracking the spot as it rotates
+        from the blueshifted hemisphere to the redshifted hemisphere of
+        the star.
         \label{fig:spot_rigid}
@@
     \oscaption{compare_rigid}{%
-        A caption.
+        The observed spectrum when the spot is in view computed with
+        \starry (blue) and numerically (orange). The problem setup
+        is the same as that in Figure~\ref{fig:spot_rigid}. The bottom
+        panel shows the absolute value of the difference between the 
+        two spectra for different grid resolutions in the numerical solution.
+        As the number of grid points increases, the numerical solution
+        converges to the \starry solution.
         \label{fig:compare_rigid}

### 2019-07-03 .ci/install.sh

@@ -14,8 +14,18 @@ if ! command -v conda > /dev/null; then
       conda create --yes -n test python=$PYTHON_VERSION;
       conda activate test;
       conda install tectonic;
-      conda install -c conda-forge numpy=$NUMPY_VERSION scipy matplotlib setuptools pytest pytest-cov pip sympy;
+      conda install -c conda-forge numpy=$NUMPY_VERSION scipy matplotlib setuptools pytest pytest-cov pip sympy pybind11;
 fi
 
 # Display some debugging info
 conda info -a
+
+# Install exoplanet
+pip install astropy
+pip install exoplanet
+
+# Install the dev version of starry
+git clone --single-branch --branch dev https://github.com/rodluger/starry.git
+pushd starry
+      python setup.py develop
+popd

### 2019-07-29 tex/gitlinks.tex
finished linalg fig

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/a5f045717b27f4123fcdb1f0bcc4048d6ec47be9/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/a5f045717b27f4123fcdb1f0bcc4048d6ec47be9/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/a5f045717b27f4123fcdb1f0bcc4048d6ec47be9/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/54ab337d6e461cf208c768298131f9cd7e577ad7/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/54ab337d6e461cf208c768298131f9cd7e577ad7/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/54ab337d6e461cf208c768298131f9cd7e577ad7/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-07-29 tex/ms.tex
finished linalg fig

@@
     \begin{centering}
-    \includegraphics[width=\linewidth]{figures/g_rigid.pdf}
-    \oscaption{g_rigid}{%
+    \includegraphics[width=\linewidth]{figures/g.pdf}
+    \oscaption{g}{%
         The Doppler $\mathbf{g}$ basis for a rigidly rotating star
@@
         spectrum.
-        \label{fig:g_rigid}
+        \label{fig:g}
     }
@@
 %
-Figure~\ref{fig:g_rigid} shows the $\mathbf{g}$ basis computed from
+Figure~\ref{fig:g} shows the $\mathbf{g}$ basis computed from
 the formulae above and Equation~(\ref{eq:rigid:gT}) up to spherical 
@@
     \begin{centering}
-    \includegraphics[width=0.6\linewidth]{figures/spot_rigid.pdf}
-    \oscaption{spot_rigid}{%
+    \includegraphics[width=0.6\linewidth]{figures/spot.pdf}
+    \oscaption{spot}{%
         Time evolution of a Gaussian absorption line on a rigidly rotating, 
@@
         the star.
-        \label{fig:spot_rigid}
+        \label{fig:spot}
     }
@@
     \begin{centering}
-    \includegraphics[width=0.65\linewidth]{figures/compare_rigid.pdf}
-    \oscaption{compare_rigid}{%
+    \includegraphics[width=0.65\linewidth]{figures/compare.pdf}
+    \oscaption{compare}{%
         The observed spectrum when the spot is in view computed with
         \starry (blue) and numerically (orange). The problem setup
-        is the same as that in Figure~\ref{fig:spot_rigid}. The bottom
+        is the same as that in Figure~\ref{fig:spot}. The bottom
         panel shows the absolute value of the difference between the 
@@
         converges to the \starry solution.
-        \label{fig:compare_rigid}
+        \label{fig:compare}
+    }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[p!]
+    \begin{centering}
+    \includegraphics[width=0.95\linewidth]{figures/linalg.pdf}
+    \oscaption{linalg}{%
+        The linear Doppler imaging problem.
+        \label{fig:linalg}
     }

### 2019-07-30 tex/gitlinks.tex
terrible notation

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/54ab337d6e461cf208c768298131f9cd7e577ad7/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/54ab337d6e461cf208c768298131f9cd7e577ad7/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/54ab337d6e461cf208c768298131f9cd7e577ad7/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/028c5691ad07f44dc9bd359433907a5c2863b82c/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/028c5691ad07f44dc9bd359433907a5c2863b82c/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/028c5691ad07f44dc9bd359433907a5c2863b82c/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-07-30 tex/ms.tex
terrible notation

@@
 % Title
-\title{Doppler Imaging Fun}
+\title{Analytic Doppler Imaging}
 
@@
 \author{Megan Bedell}
+\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
+%
+\author{Daniel Foreman-Mackey}
 \affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
@@
 %
-Let $I(\xi, \mathbf{x}, t, \mathbf{d})$ be the specific 
+Let $I(\lnlam, \mathbf{x}, t, \mathbf{d})$ be the specific 
 intensity observed 
-at log wavelength $\xi \equiv \ln\lambda$ and at sky-projected 
+at log wavelength $\lnlam \equiv \ln\lambda$ and at sky-projected 
 Cartesian position $\mathbf{x} = (x, y, z)$ on the surface of the 
@@
     \label{eq:intro:Ixi}
-    I(\xi, \mathbf{x}, t, \mathbf{d}) &= 
-        I_0\Big(\xi_0(\xi, \mathbf{x}, \mathbf{d}), \mathbf{x}, t\Big)
+    I(\lnlam, \mathbf{x}, t, \mathbf{d}) &= 
+        I_0\Big(\lnlam_0(\lnlam, \mathbf{x}, \mathbf{d}), \mathbf{x}, t\Big)
 \end{align}
@@
     \label{eq:intro:xi0}
-    \xi_0(\xi, \mathbf{x}, \mathbf{d}) &= 
-    \xi - \mathcal{D}(\mathbf{x}, \mathbf{d})
+    \lnlam_0(\lnlam, \mathbf{x}, \mathbf{d}) &= 
+    \lnlam - \mathcal{D}(\mathbf{x}, \mathbf{d})
 \end{align}
@@
 (Equation~\ref{eq:intro:xi0})
-and interpolate back to the grid in $\xi$. This is practical when
+and interpolate back to the grid in $\lnlam$. This is practical when
 computing the spectrum at a single \emph{point} on the surface, but not
@@
     \label{eq:intro:Fxi}
-    F(\xi, t) 
+    F(\lnlam, t) 
         &\equiv
         \iint\limits_{\mathcal{S}(\mathbf{x})}
-                I(\xi, \mathbf{x}, t, \mathbf{d})
+                I(\lnlam, \mathbf{x}, t, \mathbf{d})
         \mathrm{d}{\mathcal{S}(\mathbf{x})}
@@
 The difficulty in solving Equation~(\ref{eq:intro:Fxi}) stems from the fact
-that $I(\xi, \mathbf{x}, t, \mathbf{d})$ is difficult to write down in 
+that $I(\lnlam, \mathbf{x}, t, \mathbf{d})$ is difficult to write down in 
 closed form, given
@@
     \label{eq:solution:Ixi0}
-    I_0(\xi_0, \mathbf{x}, t) 
+    I_0(\lnlam_0, \mathbf{x}, t) 
         &=
-        \sum_{l=0}^\infty\sum_{m=-l}^{l} a_{lm}(\xi_0, t) Y_{lm}(\mathbf{x})
+        \sum_{l=0}^\infty\sum_{m=-l}^{l} a_{lm}(\lnlam_0, t) Y_{lm}(\mathbf{x})
     \quad ,
@@
 where $Y_{lm}(\mathbf{x})$ is a spherical harmonic on the projected disk
-and $a_{lm}(\xi_0, t)$ is the corresponding spherical harmonic 
-coefficient at log wavelength in the rest frame $\xi_0$ and time $t$. For 
+and $a_{lm}(\lnlam_0, t)$ is the corresponding spherical harmonic 
+coefficient at log wavelength in the rest frame $\lnlam_0$ and time $t$. For 
 convenience, we may write this equation in vector form:
@@
     \label{eq:solution:Ixi0vec}
-    I_0(\xi_0, \mathbf{x}, t) &=
-    \tilde{\bvec{y}}^\top(\mathbf{x})
-    \bvec{a}(\xi_0, t)
+    I_0(\lnlam_0, \mathbf{x}, t) &=
+    \bvec{Y}^\top(\mathbf{x}) \,
+    \bvec{a}(\lnlam_0, t)
     \quad ,
@@
 \begin{align}
-    \bvec{a}(\xi_0, t) \equiv
+    \bvec{a}(\lnlam_0, t) \equiv
 \Big( 
-    a_{0,0}(\xi_0, t) \quad\quad\quad\quad\quad\quad 
-    a_{1,-1}(\xi_0, t) \quad\quad\quad\quad\quad\quad 
-    a_{1,0}(\xi_0, t) \quad\quad\quad\quad\quad\quad
-    a_{1,1}(\xi_0, t) \quad\quad\quad\quad\quad\quad 
+    a_{0,0}(\lnlam_0, t) \quad\quad\quad\quad\quad\quad 
+    a_{1,-1}(\lnlam_0, t) \quad\quad\quad\quad\quad\quad 
+    a_{1,0}(\lnlam_0, t) \quad\quad\quad\quad\quad\quad
+    a_{1,1}(\lnlam_0, t) \quad\quad\quad\quad\quad\quad 
     ... 
@@
 \begin{align}
-    \tilde{\bvec{y}}^\top(\mathbf{x}) \equiv 
+    \bvec{Y}^\top(\mathbf{x}) \equiv 
 \Big( 
@@
     \label{eq:solution:R}
-    \bvec{a}(\xi_0, t) = \mathbf{R}(t) \bvec{a}(\xi_0)
+    \bvec{a}(\lnlam_0, t) = \mathbf{R}(t) \bvec{a}(\lnlam_0)
     \quad ,
@@
 %
-where $\bvec{a}(\xi_0) = \bvec{a}(\xi_0, t=t_0)$ for some reference time $t_0$.
+where $\bvec{a}(\lnlam_0) = \bvec{a}(\lnlam_0, t=t_0)$ for some reference time $t_0$.
 For rigid body rotation, the result is exact and $\mathbf{R}(t)$ is the Wigner 
@@
 made to hold approximately for some effective rotation matrix 
-$\mathbf{R}(t)$; we discuss this further below.
+$\mathbf{R}(t)$; we discuss this later.
 
@@
     \label{eq:solution:Ixi0vecfull}
-    I_0(\xi_0, \mathbf{x}, t) &=
-    \tilde{\bvec{y}}^\top(\mathbf{x})
+    I_0(\lnlam_0, \mathbf{x}, t) &=
+    \bvec{Y}^\top(\mathbf{x})
     \mathbf{R}(t)
-    \bvec{a}(\xi_0)
+    \bvec{a}(\lnlam_0)
     \quad ,
@@
 \begin{align}
-    I(\xi, \mathbf{x}, t) &= 
-        I_0(\xi_0, \mathbf{x}, t) 
-        * \delta\big(\mathcal{D}(\mathbf{x}, \mathbf{d}) - (\xi - \xi_0)\big)
+    I(\lnlam, \mathbf{x}, t) &= 
+        I_0(\lnlam_0, \mathbf{x}, t) 
+        * \delta\big(\lnlam - \lnlam_0\big)
         \quad,
@@
 where $*$ denotes the convolution operation, 
-returning a function of the shifted log wavelength, $\xi$.
+returning a function of the shifted log wavelength, $\lnlam$.
 Inserting this into Equation~(\ref{eq:solution:Ixi0vecfull}) and integrating
@@
 \begin{align}
-    \label{eq:solution:Fxi}
-    F(\xi, t) &=
+    \label{eq:solution:Fxi2d}
+    F(\lnlam, t) &=
     \iint\limits_{\mathcal{S}(\mathbf{x})}
-    \tilde{\bvec{y}}^\top(\mathbf{x})
+    \bvec{Y}^\top(\mathbf{x})
     \mathbf{R}(t)
-    \bvec{a}(\xi_0)
-    * \delta\big(\mathcal{D}(\mathbf{x}, \mathbf{d}) - (\xi - \xi_0)\big)
+    \bvec{a}(\lnlam_0)
+    * \delta\big(\lnlam - \lnlam_0\big)
     \mathrm{d}\mathcal{S}(\mathbf{x})
@@
     &=
-    \mathbf{g}^\top(\mathcal{D})
-    *
+    \iint\limits_{\mathcal{S}(\mathbf{x})}
+    \bvec{Y}^\top(\mathbf{x})
+    \delta\big(\lnlam - \lnlam_0\big)
+    \mathrm{d}\mathcal{S}(\mathbf{x})
     \,
@@
     \,
-    \bvec{a}(\xi_0)
+    *
+    \,
+    \bvec{a}(\lnlam_0)
+    %\mathbf{g}^\top(\lnlam_0) \, \mathbf{R}(t)
+    %*
+    %\bvec{a}(\lnlam_0)
     \quad ,
@@
 the fact that the integral is taken only over the spatial dimensions.
-We further define
+Note, importantly, that the convolution operation
+above is implicitly a vector operation---i.e., the
+convolution is taken for each spherical harmonic term and then summed over 
+all terms.
+
+Finally, we can simplify Equation~(\ref{eq:solution:Fxi2d}) by noting that the
+delta function in the integrand allows us to reduce the double integral 
+to a line integral:
 %
@@
     \label{eq:solution:gT}
-    \mathbf{g}^\top(\mathcal{D})
-    &\equiv
     \iint\limits_{\mathcal{S}(\mathbf{x})}
-    \tilde{\bvec{y}}^\top(\mathbf{x})
-    \delta\big(\mathcal{D}(\mathbf{x}, \mathbf{d}) - (\xi - \xi_0)\big)
+    \bvec{Y}^\top(\mathbf{x})
+    \delta\big(\lnlam - \lnlam_0\big)
     \mathrm{d}\mathcal{S}(\mathbf{x})
+    \, \,
+    &=  
+    \int\limits_{\mathcal{C}(\lnlam - \lnlam_0)}
+    \hspace*{-1em}\bvec{Y}^\top(\mathbf{x})
+    \mathrm{d}\mathcal{C}(\lnlam - \lnlam_0)
     \nonumber \\[0.5em]
-    &=  
-    \int\limits_{\mathcal{C}(\mathbf{x}, \mathbf{d})}
-    \tilde{\bvec{y}}^\top(\mathbf{x})
-    \mathrm{d}\mathcal{C}(\mathbf{x}, \mathbf{d})
+    &\equiv \mathbf{g}^\top(\lnlam - \lnlam_0)
     \quad.
@@
 %
-where the integral in the second line denotes the line integral about
-some function $\mathcal{C}(\mathbf{x}, \mathbf{d})$ corresponding to the
-set of all points on the visible disk where 
-$\mathcal{D}(\mathbf{x}, \mathbf{d}) = \xi - \xi_0$.
+where the path $\mathcal{C}$ corresponds to the
+set of all points on the visible disk where \xxx{what???}
 
-Equation~(\ref{eq:solution:Fxi}) is the complete deconvolution of the
+We thus have
+%
+\begin{align}
+    \label{eq:solution:Fxi}
+    F(\lnlam, t) 
+    &=
+    \mathbf{g}^\top(\lnlam - \lnlam_0) \, \mathbf{R}(t)
+    *
+    \bvec{a}(\lnlam_0)
+    \quad.
+\end{align}
+%
+Equation~(\ref{eq:solution:Fxi}) is the deconvolution of the
 observed spectrum into velocity terms, temporal terms, and spectral/spatial
 terms, respectively. In the following sections, we will discuss how to
-efficiently solve Equation~(\ref{eq:solution:gT}).
+efficiently solve the line integral in Equation~(\ref{eq:solution:gT}).
 
@@
     \label{eq:rigid:gT}
-    \mathbf{g}^\top(\mathcal{D}) &\equiv
-    \bvec{s}^\top(\mathcal{D})
+    \mathbf{g}^\top(\lnlam_0) &\equiv
+    \bvec{s}^\top(\lnlam_0)
     \bvec{A_1}
@@
     \label{eq:rigid:sTdef}
-    \mathbf{s}^\top(\mathcal{D})
+    \mathbf{s}^\top(\lnlam_0)
     &\equiv
-    \int\limits_{\mathcal{C}(\mathbf{x}, \mathbf{d})}
+    \int\limits_{\mathcal{C}(\lnlam_0, \mathbf{x}, \mathbf{d})}
     \tilde{\bvec{p}}^\top(\mathbf{x})
-    \mathrm{d}\mathcal{C}(\mathbf{x}, \mathbf{d})
+    \mathrm{d}\mathcal{C}(\lnlam_0, \mathbf{x}, \mathbf{d})
 \end{align}
@@
         computed from Equation~(\ref{eq:rigid:gT}) and
-        Equation~(\ref{eq:rigid:sTAnalytic}) up to spherical 
+        Equation~(\ref{eq:rigid:sTrecurrence}) up to spherical 
         harmonic degree $l=10$. Rows correspond to the degree $l$ and
@@
 If we assume the star is unocculted, the region of integration $\mathcal{S}$ 
-is simply the unit disk, so $\mathcal{C}(\mathbf{x}, \mathbf{d})$ 
+is simply the unit disk, so $\mathcal{C}(\lnlam_0, \mathbf{x}, \mathbf{d})$ 
 is the set of all points
-that satisfy both $\mathcal{D}(\mathbf{x}, \mathbf{d}) = \xi - \xi_0$ and 
+that satisfy both $\mathcal{D}(\mathbf{x}, \mathbf{d}) = \lnlam - \lnlam_0$ and 
 $x^2 + y^2 \le 1$.
 Solving Equation~(\ref{eq:rigid:D}) for $x$, we find that 
-the curves $\mathcal{C}(\mathbf{x}, \mathbf{d})$ 
+the curves $\mathcal{C}(\lnlam_0, \mathbf{x}, \mathbf{d})$ 
 are simply vertical lines on the unit disk given by 
 %
+\xxx{(this should be $\lnlam - \lnlam_0$, no?)}
+%
 \begin{align}
-    x(\mathcal{D}) &= 
+    x(\lnlam_0) &= 
         \Bigg(\frac{c}{\omega\sin i}\Bigg) 
-        \Bigg(\frac{\mathrm{e}^{2\mathcal{D}} - 1}
-                   {\mathrm{e}^{2\mathcal{D}} + 1}\Bigg)
+        \Bigg(\frac{\mathrm{e}^{2{\lnlam_0}} - 1}
+                   {\mathrm{e}^{2{\lnlam_0}} + 1}\Bigg)
     \quad .
@@
     \label{eq:rigid:sT}
-    \bvec{s}^\top(\mathcal{D}) 
+    \bvec{s}^\top(\lnlam_0) 
     &=    
-    \int\limits_{-\sqrt{1 - x(\mathcal{D})^2}}^
-                {\sqrt{1 - x(\mathcal{D})^2}}
+    \int\limits_{-\sqrt{1 - x^2}}^
+                {\sqrt{1 - x^2}}
     \tilde{\bvec{p}}^\top
-    \Big(x(\mathcal{D}), y\Big)
+    \Big(x, y\Big)
     \mathrm{d}y
@@
 \begin{proof}{PolynomialBasis}
-    \label{eq:lm}
+    \label{eq:rigid:lm}
     i &= \floor*{\Lambda - \Delta}
@@
 \begin{align}
-    s_n(\mathcal{D}) 
+    \label{eq:rigid:sTexpression}
+    s_n(\lnlam_0) 
     &=    
-    x(\mathcal{D})^i
-    \int\limits_{-\sqrt{1 - x(\mathcal{D})^2}}^
-                {\sqrt{1 - x(\mathcal{D})^2}}
+    s_{i,\,j,\,k}(\lnlam_0) 
+    =    
+    x^i
+    \int\limits_{-\sqrt{1 - x^2}}^
+                {\sqrt{1 - x^2}}
         y^j
-        \left(1 - x(\mathcal{D})^2 - y^2\right)^{\frac{k}{2}} \,
+        \left(1 - x^2 - y^2\right)^{\frac{k}{2}} \,
     \mathrm{d}y 
-    \quad ,
+    \quad .
 \end{align}
 %
-and solve it analytically:
+As we show in the Appendix, the solution to this integral
+is analytic and expressible in terms of simple recurrence
+relations. Given the boundary conditions
 %
 \begin{align}
-        \label{eq:rigid:sTAnalytic}
-        s_n(\mathcal{D}) 
-        &=     
-    \begin{dcases}
-        0
-        &
-        \qquad j \, \mathrm{odd}
-        \\[1em]
-        \frac{2 x(\mathcal{D})^i 
-        \big(1 - x(\mathcal{D})^ 2\big)^{\frac{j + 1}{2}}}{j + 1}
-        &
-        \qquad k = 0
-        \\[1em]
-        x(\mathcal{D})^{i} \mathcal{I}_{j}
-        \big(x(\mathcal{D})\big)
-        &
-        \qquad k = 1
-        \quad ,
-    \end{dcases}
+    s_{0,\,0,\,0} &= 2 \sqrt{1-x^2} \nonumber \\
+    s_{0,\,0,\,1} &= \frac{\pi}{2} \big(1-x^2\big) \nonumber \\
+    s_{0,\,1,\,0} &= 0 \nonumber \\
+    s_{0,\,1,\,1} &= 0 \quad ,
 \end{align}
 %
-where $\mathcal{I}_j(x)$ is computed analytically
-from the upward recurrence relation given by Equation~(\ref{eq:app:Ij}),
-with $\mathcal{I}_0(x)$ given by Equation~(\ref{eq:app:I0}).
+we may compute any term in the series via the expressions
+%
+\begin{align}
+    \label{eq:rigid:sTrecurrence}
+    s_{0,\,j,\,0} &= \frac{j - 1}{j + 1} \big(1 - x^2\big) s_{0,\,j-2,\,0} \nonumber \\
+    s_{0,\,j,\,1} &= \frac{j - 1}{j + 2} \big(1 - x^2\big) s_{0,\,j-2,\,1} \nonumber \\
+    s_{i,\,j,\,k} &= x s_{i-1,\,j,\,k} \quad.
+\end{align}
 %
@@
         As the number of grid points increases, the numerical solution
-        converges to the \starry solution.
+        approaches the \starry solution.
         \label{fig:compare}
@@
     \begin{centering}
-    \includegraphics[width=0.95\linewidth]{figures/linalg.pdf}
+    \includegraphics[width=1.0\linewidth]{figures/linalg.pdf}
     \oscaption{linalg}{%
-        The linear Doppler imaging problem.
+        The linear Doppler imaging problem, $\bvec{f} = \bvec{D} \bvec{a}$.
+        The vector on the left hand side, $\bvec{f}$, is the model for the
+        observed flux, a sequence of $M$ spectra taken at different times,
+        each measured at $K$ wavelength bins. The matrix on the right hand 
+        side, $\bvec{D}$, is
+        the Doppler design matrix, constructed from $M \times N$ Toeplitz
+        matrices, each of shape $K \times (K + W)$, where $W$ is the width
+        of the convolution kernel and $N$ is the number of spherical harmonic
+        coefficients in the expansion of the stellar surface.
+        The $N$ columns of $\mathcal{D}$ correspond
+        to the Toeplitz matrices for each of the $N$ spherical harmonics;
+        the $M$ rows correspond to the Toeplitz matrices rotated to each
+        of the $M$ stellar phases observed. Finally, the vector at the 
+        right is the weight vector $\bvec{a}$, a sequence of $N$ spectral 
+        components, each of length $K + W$. In this example, each segment of
+        $\bvec{a}$ is equal to a simple Gaussian line profile weighted by
+        the spherical harmonic coefficients of a large equatorial starspot;
+        this corresponds to a star whose spectrum is the same everywhere, but
+        whose overall brightness varies spatially.
         \label{fig:linalg}
+    }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[p!]
+    \begin{centering}
+    \includegraphics[width=1.0\linewidth]{figures/linalg_u.pdf}
+    \oscaption{linalg_u}{%
+        Similar to Figure~\ref{fig:linalg}, but isolating the linear dependence
+        of the model on the spherical harmonic coefficients $\bvec{u}$.
+        \label{fig:linalg_u}
     }
@@
 %
+\clearpage
 \appendix
@@
 \section{Integrals}
-\subsection{Equation~(\ref{eq:rigid:sTAnalytic})}
+\subsection{Equation~(\ref{eq:rigid:sTexpression})}
 %
-When $k = 1$, we may write the $n^\mathrm{th}$ component
-of Equation~(\ref{eq:rigid:sTAnalytic}) as
+In this section we derive the recurrence relations
+(\ref{eq:rigid:sTrecurrence}) for computing $\mathbf{s}^\top$.
+When $i = k = 0$, the integral is easy to evaluate:
 %
 \begin{align}
-    s_n(\mathcal{D}) = 
-        x(\mathcal{D})^{i}
-        \mathcal{I}_{j}\big(x(\mathcal{D})\big)
+    s_{i,\,j,\,0}(\lnlam_0) 
+    &=    
+    \begin{cases}
+        2 \left( 1 - x^2 \right)^\frac{j + 1}{2} 
+        \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad 
+        &  j \, \mathrm{even} \\
+        0 & j \, \mathrm{odd} \quad .
+    \end{cases}
 \end{align}
 %
-where
+The general term may be computed from the recurrence relation
 %
 \begin{align}
-    \mathcal{I}_j(x) &\equiv
-    \int\limits_{-\sqrt{1-x^2}}^{\sqrt{1-x^2}}
-        y^{j}
-        \sqrt{1 - x^2 - y^2} \,
-    \mathrm{d}y
-    \quad.
+    s_{0,\,j,\,0}(\lnlam_0) = \frac{j - 1}{j + 1} \big(1 - x^2\big) s_{0,\,j-2,\,0}
 \end{align}
 %
-Substituting $y = \sin\psi\sqrt{1 - x^2}$, we have
+provided 
 %
 \begin{align}
-    \mathcal{I}_j(x) &=
+    s_{0,\,0,\,0} &= 2 \sqrt{1-x^2} \nonumber \\
+    s_{0,\,1,\,0} &= 0 \quad.
+\end{align}
 %
+When $i = 0$ and $k = 1$, we may substitute $y = \sin\psi\sqrt{1 - x^2}$ in
+the integrand to obtain
+%
+\begin{align}
+    s_{0,\,j,\,1}(\lnlam_0)
+    &=
     (1 - x^2)^{\frac{j + 2}{2}}
@@
 \begin{align}
-    \label{eq:app:Ij}
-    \mathcal{I}_j(x) &=
-    \frac{j - 1}{j + 2}
-    (1 - x^2)
-    \mathcal{I}_{j-2}(x)
-    \quad.
+    s_{0,\,j,\,1} &= \frac{j - 1}{j + 2} \big(1 - x^2\big) s_{0,\,j-2,\,1}
 \end{align}
 %
-Since this expression is only used when $j$ is even, we only need one
-initial condition for upward recursion:
+with initial conditions
 %
 \begin{align}
-    \label{eq:app:I0}
-    \mathcal{I}_0(x) &\equiv
-    \int\limits_{-\sqrt{1-x^2}}^{\sqrt{1-x^2}}
-        \sqrt{1 - x^2 - y^2} \,
-    \mathrm{d}y
-    \nonumber \\
-    &= \frac{\pi}{2}(1 - x^2)
-    \quad.
+    s_{0,\,0,\,1} &= \frac{\pi}{2} \big(1-x^2\big) \nonumber \\
+    s_{0,\,1,\,1} &= 0 \quad.
+\end{align}
+%
+Given these expressions, recursing upward in $i$ is easy:
+%
+\begin{align}
+    s_{i,\,j,\,k} &= x s_{i-1,\,j,\,k} \quad.
 \end{align}

### 2019-07-30 tex/figures/compare.py

@@ -63,7 +63,7 @@ for i in range(len(Snum)):
 ax[0].set_ylabel(r"spectrum")
 ax[0].legend(fontsize=12, loc="lower left")
 ax[1].set_yscale("log")
-ax[1].set_xlabel(r"$10^{6}\times\xi$")
+ax[1].set_xlabel(r"$\lambdabar$ (arbitrary units)")
 ax[1].legend(fontsize=10, loc="upper right")
 ax[1].set_ylim(1e-10, 1e0)
 ax[1].set_ylabel(r"residuals")

### 2019-07-30 tex/figures/linalg.py

@@ -2,7 +2,7 @@
 import matplotlib.pyplot as plt
 import numpy as np
 import paparazzi as pp
-from scipy.sparse import hstack, vstack, csr_matrix
+from scipy.sparse import hstack, vstack, csr_matrix, block_diag
 import starry
 
 
@@ -150,204 +150,465 @@ def get_ortho_longitude_lines(inc=np.pi/2, obl=0, theta=0,
     return res
 
 
-# Settings for this figure
-ydeg = 2
-ntheta = 11
-inc = 40.
-vsini = 80.
-nlam = 11
+def plot_main():
+    """
+    Plot the main figure showing the equation ``f = D a``.
 
-#
-# Compute stuff!
-#
+    """
+    # Settings for this figure
+    ydeg = 2
+    ntheta = 11
+    inc = 40.
+    vsini = 80.
+    nlam = 11
 
-# Compute the g-functions and the corresponding Toeplitz matrices
-doppler = pp.Doppler(np.linspace(-6e-4, 6e-4, nlam), 
-    ydeg=ydeg, vsini=vsini, inc=inc, P=1.0)
-g = doppler._g()
-T = doppler._T()
+    #
+    # Compute stuff!
+    #
 
-# Pad them to reveal the structure
-for n in range(doppler.N):
-    T[n] = T[n].toarray()
-    T[n][:, 0] = np.nan
-    T[n][:, -1] = np.nan
-    T[n] = csr_matrix(T[n])
-    T[n] = vstack((T[n], np.nan * np.ones((2, T[n].shape[1]))))
+    # Compute the g-functions and the corresponding Toeplitz matrices
+    doppler = pp.Doppler(np.linspace(-6e-4, 6e-4, nlam), 
+        ydeg=ydeg, vsini=vsini, inc=inc, P=1.0)
+    g = doppler.g()
+    T = doppler.T()
 
-# Tensordot with rotation matrices to get the full Doppler matrix
-theta = np.linspace(0, 2 * np.pi, ntheta)
-R = [doppler._R(doppler._axis, t) for t in theta]
-D = [None for t in range(ntheta)]
-for t in range(ntheta):
-    TR = [None for n in range(doppler.N)]
-    for l in range(ydeg + 1):
-        idx = slice(l ** 2, (l + 1) ** 2)
-        TR[idx] = np.tensordot(R[t][l].T, T[idx], axes=1)
-    D[t] = hstack(TR)
-D = vstack(D).toarray()
-D /= np.nanmax(D)
[…]

### 2019-07-30 tex/gitlinks.tex
writing

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/028c5691ad07f44dc9bd359433907a5c2863b82c/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/028c5691ad07f44dc9bd359433907a5c2863b82c/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/028c5691ad07f44dc9bd359433907a5c2863b82c/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/2720441d1bd09da0ba8e768041eb50d5230512fc/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/2720441d1bd09da0ba8e768041eb50d5230512fc/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/2720441d1bd09da0ba8e768041eb50d5230512fc/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-07-30 tex/ms.tex
writing

@@
     \oscaption{linalg}{%
-        The linear Doppler imaging problem, $\bvec{f} = \bvec{D} \bvec{a}$.
+        The linear Doppler imaging problem, $\bvec{f} = \bvec{D} \bvec{a}$
+        (Equation~\ref{eq:fDa}).
         The vector on the left hand side, $\bvec{f}$, is the model for the
         observed flux, a sequence of $M$ spectra taken at different times,
-        each measured at $K$ wavelength bins. The matrix on the right hand 
+        each measured at $K$ wavelength bins (plotted to the left of $\bvec{f}$). 
+        The matrix on the right hand 
         side, $\bvec{D}$, is
@@
         matrices, each of shape $K \times (K + W)$, where $W$ is the width
-        of the convolution kernel and $N$ is the number of spherical harmonic
+        of the convolution kernels (plotted at the top) and $N$ is the 
+        number of spherical harmonic
         coefficients in the expansion of the stellar surface.
@@
         the $M$ rows correspond to the Toeplitz matrices rotated to each
-        of the $M$ stellar phases observed. Finally, the vector at the 
+        of the $M$ stellar phases observed (indicated graphically 
+        to the left of $\mathbf{D}$). Finally, the vector at the 
         right is the weight vector $\bvec{a}$, a sequence of $N$ spectral 
-        components, each of length $K + W$. In this example, each segment of
+        components, each of length $K + W$ (plotted to the right). 
+        In this example, each segment of
         $\bvec{a}$ is equal to a simple Gaussian line profile weighted by
@@
         Similar to Figure~\ref{fig:linalg}, but isolating the linear dependence
-        of the model on the spherical harmonic coefficients $\bvec{u}$.
+        of the model on the spherical harmonic coefficients:
+        $\bvec{f} = \bvec{D}\bvec{V}\bvec{u}$ (Equation~\ref{eq:fDVu}).
+        The $\bvec{f}$ vector and the $\bvec{D}$ design matrix are the same
+        as before, but the spectra have been factored out 
+        of the weight vector and into the $(N \times NP)$ matrix
+        $\bvec{V}$, a block diagonal matrix constructed from $P$
+        distinct spectral components (plotted at the top).
         \label{fig:linalg_u}

### 2019-07-30 tex/figures/compare.py

@@ -53,8 +53,8 @@ for i, res in enumerate(res_arr):
 
 # Compare
 fig, ax = plt.subplots(2, sharex=True, figsize=(8, 8))
-ax[0].plot(1e6 * xi[obs], S[obs], label="starry")
-ax[0].plot(1e6 * xi[obs], Snum[-1][obs], "--", label="numerical")
+ax[0].plot(1e6 * xi[obs], S[obs], lw=2.5, label="Luger et al. (2019)")
+ax[0].plot(1e6 * xi[obs], Snum[-1][obs], "--", lw=2.5, label="numerical")
 ax[0].set_xlim(-4, 4)
 alpha = [0.2, 0.5, 1.0]
 for i in range(len(Snum)):

### 2019-07-30 tex/figures/linalg.py

@@ -4,6 +4,7 @@ import numpy as np
 import paparazzi as pp
 from scipy.sparse import hstack, vstack, csr_matrix, block_diag
 import starry
+np.random.seed(15)
 
 
 def RAxisAngle(axis=[0, 1, 0], theta=0):
@@ -181,7 +182,7 @@ def plot_main():
         T[n] = vstack((T[n], np.nan * np.ones((2, T[n].shape[1]))))
 
     # Tensordot with rotation matrices to get the full Doppler matrix
-    theta = np.linspace(-np.pi, np.pi, ntheta)
+    theta = np.linspace(0, 2 * np.pi, ntheta)
     R = [doppler._R(doppler._axis, t) for t in theta]
     D = [None for t in range(ntheta)]
     for t in range(ntheta):
@@ -197,7 +198,7 @@ def plot_main():
     vT = 1 - 0.5 * np.exp(-0.5 * doppler.lam_padded ** 2 / (1e-4) ** 2)
     map = starry.Map(ydeg)
     map.inc = inc
-    map.add_spot(-1)
+    map.add_spot(-1, lon=-180)
     u = np.array(map.y.eval())
     A = u.reshape(-1, 1).dot(vT.reshape(1, -1))
 
@@ -259,7 +260,7 @@ def plot_main():
     height = 0.0622
     for n in range(ntheta):
         axins = ax.inset_axes([x0, y0 - n * (height + pad), width, height])
-        axins.plot(lam, F[n], "k-")
+        axins.plot(lam, F[n], "k-", alpha=0.3)
         axins.set_ylim(0.6, 1.45)
         axins.axis("off")
 
@@ -272,7 +273,7 @@ def plot_main():
     for n in range(doppler.N):
         axins = ax.inset_axes([x0 + n * (width + pad), y0, width, height])
         axins.axis('off')
-        axins.plot(g[n], "k-")
+        axins.plot(g[n], "k-", alpha=0.3)
 
     # Plot the spectral components
     x0 = 1.03
@@ -283,7 +284,7 @@ def plot_main():
     for n in range(doppler.N):
         axins = ax.inset_axes([x0, y0 - n * (height + pad), width, height])
         axins.axis('off')
-        axins.plot(A[n], doppler.lam_padded, "k-")
[…]

### 2019-07-30 tex/gitlinks.tex
beefing up the Doppler class

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/2720441d1bd09da0ba8e768041eb50d5230512fc/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/2720441d1bd09da0ba8e768041eb50d5230512fc/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/2720441d1bd09da0ba8e768041eb50d5230512fc/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/06d5b85a111d278d05c6eec5df6638f529432379/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/06d5b85a111d278d05c6eec5df6638f529432379/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/06d5b85a111d278d05c6eec5df6638f529432379/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-07-30 tex/gitlinks.tex
better conventions

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/06d5b85a111d278d05c6eec5df6638f529432379/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/06d5b85a111d278d05c6eec5df6638f529432379/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/06d5b85a111d278d05c6eec5df6638f529432379/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/a5ecdb613d8739abff5e3bdf3536e894d4ec184d/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/a5ecdb613d8739abff5e3bdf3536e894d4ec184d/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/a5ecdb613d8739abff5e3bdf3536e894d4ec184d/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-07-30 tex/ms.tex
better conventions

@@
     I(\lnlam, \mathbf{x}, t, \mathbf{d}) &= 
-        I_0\Big(\lnlam_0(\lnlam, \mathbf{x}, \mathbf{d}), \mathbf{x}, t\Big)
+        I\Big(\lnlam_0 + \mathcal{D}(\bvec{x}, \bvec{d}), \mathbf{x}, t\Big)
 \end{align}
 %
-where $I_0$ is the specific intensity at each point on the star 
-in the surface rest frame and 
-%
-\begin{align}
-    \label{eq:intro:xi0}
-    \lnlam_0(\lnlam, \mathbf{x}, \mathbf{d}) &= 
-    \lnlam - \mathcal{D}(\mathbf{x}, \mathbf{d})
-\end{align}
-%
-is the log wavelength in the rest frame. The quantity $\mathcal{D}$ is
+where $\lnlam_0$ is the log wavelength in the rest frame and $\mathcal{D}$ is
 the Doppler shift in log wavelength space:
@@
 A common approach to computing the Doppler-shifted spectrum is to
-evaluate the spectrum at the rest frame wavelength 
-(Equation~\ref{eq:intro:xi0})
+evaluate the spectrum at the rest frame wavelength $\lnlam_0$
 and interpolate back to the grid in $\lnlam$. This is practical when
@@
     \label{eq:intro:Fxi}
-    F(\lnlam, t) 
+    F(\lnlam, t, \bvec{d}) 
         &\equiv
@@
 %
-The first thing we will do is to expand the spatial dependence of the
-specific intensity in terms of spherical harmonics on the unit disk:
+The first thing we will do is to express Equation~(\ref{eq:intro:Ixi})
+as a convolution:
+%
+\begin{align}
+    \label{eq:solution:convolution}
+    I(\lnlam, \mathbf{x}, t, \mathbf{d}) &= 
+        I(\lnlam_0, \mathbf{x}, t) 
+        * 
+        \delta\big(\lnlam_0 + \mathcal{D}(\bvec{x}, \bvec{d})\big)
+\end{align}
+%
+where $\delta$ is the
+Dirac delta function and
+$*$ denotes the linear convolution operator,
+returning a function of the shifted log wavelength, 
+$\lnlam = \lnlam_0 + \mathcal{D}$. The convolution with the delta function
+has the effect of ``sliding'' the spectrum by an amount $\mathcal{D}$
+onto the observed wavelength grid.
+
+Next, we expand the spatial dependence of the
+specific intensity at the rest frame wavelength
+in terms of spherical harmonics on the unit disk:
 %
@@
     \label{eq:solution:Ixi0}
-    I_0(\lnlam_0, \mathbf{x}, t) 
+    I(\lnlam_0, \mathbf{x}, t) 
         &=
@@
     \label{eq:solution:Ixi0vec}
-    I_0(\lnlam_0, \mathbf{x}, t) &=
+    I(\lnlam_0, \mathbf{x}, t) &=
     \bvec{Y}^\top(\mathbf{x}) \,
@@
 
-The equation for the specific intensity now reads
+The equation for the specific intensity in the rest frame now reads
 %
@@
     \label{eq:solution:Ixi0vecfull}
-    I_0(\lnlam_0, \mathbf{x}, t) &=
+    I(\lnlam_0, \mathbf{x}, t) &=
     \bvec{Y}^\top(\mathbf{x})
+    \,
     \mathbf{R}(t)
+    \,
     \bvec{a}(\lnlam_0)
@@
 where it is clear that we have fully separated the spatial, temporal, and
-spectral terms. However, in order to compute the observed spectrum, we must
-still Doppler shift this expression and integrate it over the visible
-portion of the star. To this end, it is convenient to express the Doppler
-shift as a convolution
-of the spectrum in the rest frame with a delta function:
-%
-\begin{align}
-    I(\lnlam, \mathbf{x}, t) &= 
-        I_0(\lnlam_0, \mathbf{x}, t) 
-        * \delta\big(\lnlam - \lnlam_0\big)
-        \quad,
-\end{align}
-%
-where $*$ denotes the convolution operation, 
-returning a function of the shifted log wavelength, $\lnlam$.
-Inserting this into Equation~(\ref{eq:solution:Ixi0vecfull}) and integrating
+spectral terms. Inserting this into Equation~(\ref{eq:solution:convolution}) 
+and integrating
 over the visible portion of the star, we arrive at the expression for the 
@@
     \label{eq:solution:Fxi2d}
-    F(\lnlam, t) &=
+    F(\lnlam, t, \bvec{d}) &=
     \iint\limits_{\mathcal{S}(\mathbf{x})}
     \bvec{Y}^\top(\mathbf{x})
+    \,
     \mathbf{R}(t)
+    \,
     \bvec{a}(\lnlam_0)
-    * \delta\big(\lnlam - \lnlam_0\big)
+    * \delta\big(\lnlam_0 + \mathcal{D}(\bvec{x}, \bvec{d})\big)
     \mathrm{d}\mathcal{S}(\mathbf{x})
@@
     \bvec{Y}^\top(\mathbf{x})
-    \delta\big(\lnlam - \lnlam_0\big)
+    \delta\big(\lnlam_0 + \mathcal{D}(\bvec{x}, \bvec{d})\big)
     \mathrm{d}\mathcal{S}(\mathbf{x})
@@
     \bvec{a}(\lnlam_0)
-    %\mathbf{g}^\top(\lnlam_0) \, \mathbf{R}(t)
-    %*
-    %\bvec{a}(\lnlam_0)
     \quad ,
@@
     &=  
-    \int\limits_{\mathcal{C}(\lnlam - \lnlam_0)}
-    \hspace*{-1em}\bvec{Y}^\top(\mathbf{x})
-    \mathrm{d}\mathcal{C}(\lnlam - \lnlam_0)
+    \int\limits_{\mathcal{C}(\lnlam, \bvec{x}, \bvec{d})}
+    \hspace*{-0.6em}\bvec{Y}^\top(\mathbf{x})
+    \mathrm{d}\mathcal{C}(\lnlam, \bvec{x}, \bvec{d})
     \nonumber \\[0.5em]
-    &\equiv \mathbf{g}^\top(\lnlam - \lnlam_0)
+    &\equiv \mathbf{g}^\top(\lnlam, \bvec{d})
     \quad.
@@
 %
-where the path $\mathcal{C}$ corresponds to the
-set of all points on the visible disk where \xxx{what???}
-
+where the path $\mathcal{C}(\lnlam, \bvec{x}, \bvec{d})$ corresponds to the
+set of all points on the visible disk where 
+$\lnlam_0 + \mathcal{D}(\bvec{x}, \bvec{d}) = 0$.
+%
 We thus have
@@
     \label{eq:solution:Fxi}
-    F(\lnlam, t) 
+    F(\lnlam, t, \bvec{d}) 
     &=
-    \mathbf{g}^\top(\lnlam - \lnlam_0) \, \mathbf{R}(t)
+    \mathbf{g}^\top(\lnlam, \bvec{d}) \, \mathbf{R}(t)
     *
@@
     \label{eq:rigid:gT}
-    \mathbf{g}^\top(\lnlam_0) &\equiv
-    \bvec{s}^\top(\lnlam_0)
+    \mathbf{g}^\top(\lnlam, \bvec{d}) &\equiv
+    \bvec{s}^\top(\lnlam, \bvec{d})
     \bvec{A_1}
@@
     \label{eq:rigid:sTdef}
-    \mathbf{s}^\top(\lnlam_0)
+    \mathbf{s}^\top(\lnlam, \bvec{d})
     &\equiv
-    \int\limits_{\mathcal{C}(\lnlam_0, \mathbf{x}, \mathbf{d})}
+    \int\limits_{\mathcal{C}(\lnlam, \mathbf{x}, \mathbf{d})}
     \tilde{\bvec{p}}^\top(\mathbf{x})
-    \mathrm{d}\mathcal{C}(\lnlam_0, \mathbf{x}, \mathbf{d})
+    \mathrm{d}\mathcal{C}(\lnlam, \mathbf{x}, \mathbf{d})
 \end{align}
@@
 If we assume the star is unocculted, the region of integration $\mathcal{S}$ 
-is simply the unit disk, so $\mathcal{C}(\lnlam_0, \mathbf{x}, \mathbf{d})$ 
+is simply the unit disk, so $\mathcal{C}(\lnlam, \mathbf{x}, \mathbf{d})$ 
 is the set of all points
-that satisfy both $\mathcal{D}(\mathbf{x}, \mathbf{d}) = \lnlam - \lnlam_0$ and 
+that satisfy both $\lnlam_0 + \mathcal{D}(\bvec{x}, \bvec{d}) = 0$ and 
 $x^2 + y^2 \le 1$.
 Solving Equation~(\ref{eq:rigid:D}) for $x$, we find that 
-the curves $\mathcal{C}(\lnlam_0, \mathbf{x}, \mathbf{d})$ 
+the curves $\mathcal{C}(\lnlam, \mathbf{x}, \mathbf{d})$ 
 are simply vertical lines on the unit disk given by 
 %
-\xxx{(this should be $\lnlam - \lnlam_0$, no?)}
+\xxx{(TODO: Check signs in the code.)}
 %
 \begin{align}
-    x(\lnlam_0) &= 
+    x &= 
         \Bigg(\frac{c}{\omega\sin i}\Bigg) 
-        \Bigg(\frac{\mathrm{e}^{2{\lnlam_0}} - 1}
-                   {\mathrm{e}^{2{\lnlam_0}} + 1}\Bigg)
+        \Bigg(\frac{\mathrm{e}^{-2{\lnlam_0}} - 1}
+                   {\mathrm{e}^{-2{\lnlam_0}} + 1}\Bigg)
     \quad .
@@
     \label{eq:rigid:sT}
-    \bvec{s}^\top(\lnlam_0) 
+    \bvec{s}^\top(\lnlam, \bvec{d}) 
     &=    
@@
     \label{eq:rigid:sTexpression}
-    s_n(\lnlam_0) 
+    s_n(\lnlam, \bvec{d}) 
     &=    
-    s_{i,\,j,\,k}(\lnlam_0) 
+    s_{i,\,j,\,k}(\lnlam, \bvec{d}) 
     =    

### 2019-08-01 paparazzi/__init__.py
bugfix

@@ -12,3 +12,4 @@ if not __PAPARAZZI_SETUP__:
 
     # Import the main interface
     from .doppler import Doppler
+    from . import utils

### 2019-08-01 scratch/newvogt.py

@@ -1,16 +1,191 @@
 import paparazzi as pp
 import numpy as np
 import matplotlib.pyplot as plt
+import theano
+import theano.tensor as tt
+import theano.sparse as ts
+from tqdm import tqdm
+from scipy.linalg import block_diag as dense_block_diag
+from scipy.sparse import block_diag as sparse_block_diag
+np.random.seed(13)
 
 
-doppler = pp.Doppler(ydeg=10)
-doppler.generate_data()
+def current_best():
+    """
+    Currently getting loss = 2600 (loss_true = 1500).
 
-doppler.solve(b=doppler.b_true, vT=doppler.vT_true)
-plt.plot(doppler.u_true)
-plt.plot(doppler.u)
-#plt.show()
+    """
+    D = pp.Doppler(ydeg=8)
+    D.generate_data(ferr=1e-3)
 
-#doppler.solve(vT=doppler.vT_true, b=doppler.b_true)
-doppler.map[1:, :] = doppler.u
-doppler.map.show(projection="rect")
+    D.u = D.u_true
+    D.vT = D.vT_true
+    loss_true = D.loss()
+
+
+    '''
+    # This works but is SO slow
+    u_guess = 1e-2 * np.random.randn(D.N - 1)
+    loss = D.solve(vT=D.vT_true, u_guess=u_guess, niter_adam=20000, lr=1e-5)
+    '''
+
+
+    D.u = 1e-2 * np.random.randn(D.N - 1)
+    loss = D.solve(T=1, vT=D.vT_true, u_guess=D.u, niter=200)
+    print(D.loss())
+
+    fig, ax = plt.subplots(1, figsize=(6, 8))
+    ax.plot(loss)
+    ax.axhline(loss_true, color="C1", ls="--")
+    ax.set_yscale("log")
+    plt.show()
+
+
+# Generate data
+dop = pp.Doppler(ydeg=1)
+dop.generate_data(ferr=1e-5)
+dop.u = dop.u_true
+dop.vT = dop.vT_true
+loss_true = dop.loss()
+u11 = dop.u_true[2]
+
+# Priors
+u_guess = np.array([-0.1, 0.1, u11])
+u_mu = 0.0
+u_sig = 0.01
+baseline_mu = 1.0
+baseline_sig = 0.1
+
+# Vars
+dop.u = u_guess
+dop.vT = dop.vT_true
+u = theano.shared(dop.u[:2])
+vT = theano.shared(dop.vT)
+
[…]

### 2019-08-01 scratch/vogtstar.py

@@ -259,7 +259,7 @@ class Solver(object):
 
         # Prior on `u`
         self.u_cinv = np.ones(self.N - 1) / u_sig ** 2
-        self.u_mu = np.ones(self.N - 1) * u_mu ** 2
+        self.u_mu = np.ones(self.N - 1) * u_mu
         self.u_lndet = np.sum(np.log(2 * np.pi * self.u_cinv))
 
         # Gaussian process prior on `vT`

### 2019-08-02 tex/ms.tex
bugfix
woot

@@
 $\lnlam = \lnlam_0 + \mathcal{D}$. The convolution with the delta function
-has the effect of ``sliding'' the spectrum by an amount $\mathcal{D}$
+has the effect of shifting the spectrum by an amount $\mathcal{D}$
 onto the observed wavelength grid.
@@
 above is implicitly a vector operation---i.e., the
-convolution is taken for each spherical harmonic term and then summed over 
-all terms.
+convolution is taken for each spherical harmonic term individually
+and then summed over all terms.
 
@@
 %
-\xxx{(TODO: Check signs in the code.)}
-%
 \begin{align}
@@
     s_{0,\,0,\,1} &= \frac{\pi}{2} \big(1-x^2\big) \nonumber \\
-    s_{0,\,1,\,0} &= 0 \nonumber \\
-    s_{0,\,1,\,1} &= 0 \quad ,
+    s_{0,\,1,\,k} &= 0 \quad ,
 \end{align}
@@
     \label{eq:rigid:sTrecurrence}
-    s_{0,\,j,\,0} &= \frac{j - 1}{j + 1} \big(1 - x^2\big) s_{0,\,j-2,\,0} \nonumber \\
-    s_{0,\,j,\,1} &= \frac{j - 1}{j + 2} \big(1 - x^2\big) s_{0,\,j-2,\,1} \nonumber \\
-    s_{i,\,j,\,k} &= x s_{i-1,\,j,\,k} \quad.
+    s_{0,\,j,\,k} &= \frac{j - 1}{j + 1 + k} \big(1 - x^2\big) s_{0,\,j-2,\,k} \nonumber \\
+    s_{i,\,j,\,k} &= x \, s_{i-1,\,j,\,k} \quad.
 \end{align}
@@
 \begin{align}
-    s_{i,\,j,\,k} &= x s_{i-1,\,j,\,k} \quad.
+    s_{i,\,j,\,k} &= x \, s_{i-1,\,j,\,k} \quad.
 \end{align}

### 2019-08-02 scratch/newvogt.py

@@ -1,66 +1,64 @@
 import paparazzi as pp
 import numpy as np
 import matplotlib.pyplot as plt
-import theano
-import theano.tensor as tt
-import theano.sparse as ts
 from tqdm import tqdm
-from scipy.linalg import block_diag as dense_block_diag
-from scipy.sparse import block_diag as sparse_block_diag
+import celerite
+from scipy.linalg import cho_factor
 np.random.seed(13)
 
 
-def current_best():
+def learn_everything(high_snr=False):
     """
-    Currently getting loss = 2600 (loss_true = 1500).
 
     """
+    # High or low SNR?
+    if high_snr:
+        ferr = 1e-4
+        niter_bilinear = 25
+        niter_adam = 2000
+    else:
+        ferr = 1e-3
+        niter_bilinear = 6
+        niter_adam = 0
+
+    # Generate data
     D = pp.Doppler(ydeg=15)
-    D.generate_data(ferr=1e-3)
+    D.generate_data(ferr=ferr)
 
-
-    # DEBUG
-    '''
-    truth = D.vT_true
-    truth -= np.mean(truth)
-    fmean = D.T[0].dot(truth)
-
-    fmean = np.mean(D.F, axis=0)
-    fmean -= np.mean(fmean)
-
-    A = D.T[0]
-    LInv = 1e-8 * np.eye(D.vT_true.shape[0])
-    estimate = np.linalg.solve(A.T.dot(A).toarray() + LInv, A.T.dot(fmean))
-    plt.figure()
-    plt.plot(truth)
-    plt.plot(estimate)
-    
-    plt.figure()
-    plt.plot(fmean)
-    plt.plot(D.T[0].dot(estimate))
-
-    plt.show()
-    quit()
-    '''
-
+    # Compute loss @ true value
     D.u = D.u_true
     D.vT = D.vT_true
     loss_true = D.loss()
 
+    # Estimate the rest frame spectrum from the deconvolved mean spectrum
     fmean = np.mean(D.F, axis=0)
     fmean -= np.mean(fmean)
     A = D.T[0]
-    LInv = 1e-5 * np.eye(A.shape[1])
+    LInv = 1e-4 * np.eye(A.shape[1])
[…]

### 2019-08-02 tex/gitlinks.tex
text

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/a5ecdb613d8739abff5e3bdf3536e894d4ec184d/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/a5ecdb613d8739abff5e3bdf3536e894d4ec184d/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/a5ecdb613d8739abff5e3bdf3536e894d4ec184d/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/7c3f626863f61d2a592a381e10d381862ebcb9fb/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/7c3f626863f61d2a592a381e10d381862ebcb9fb/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/7c3f626863f61d2a592a381e10d381862ebcb9fb/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-08-02 tex/ms.tex
text

@@
 \input{cortex}
+
+\newcommand{\s}{\bvec{s}}
+\newcommand{\p}{\bvec{p}}
+\newcommand{\R}{\bvec{R}}
+\newcommand{\AOne}{\bvec{A_1}}
+\newcommand{\alm}{\bvec{a}}
+\newcommand{\Y}{\bvec{Y}}
+\newcommand{\x}{\bvec{x}}
+\newcommand{\g}{\bvec{g}}
+\newcommand{\D}{\mathcal{D}}
+\newcommand{\Surf}{\mathcal{S}}
+\newcommand{\Curve}{\mathcal{C}}
+\newcommand{\Dargs}{\bvec{d}}
+\newcommand{\lmax}{\ensuremath{l_\mathrm{max}}}
 
@@
 %
-Let $I(\lnlam, \mathbf{x}, t, \mathbf{d})$ be the specific 
+Let $I(\lnlam, \x, t, \Dargs)$ be the specific 
 intensity observed 
 at log wavelength $\lnlam \equiv \ln\lambda$ and at sky-projected 
-Cartesian position $\mathbf{x} = (x, y, z)$ on the surface of the 
+Cartesian position $\x = (x, y, z)$ on the surface of the 
 star at time $t$, where
-$\mathbf{d}$ is a set of arbitrary parameters of the Doppler field.
+$\Dargs$ is a set of arbitrary parameters of the Doppler field.
 We may express this intensity as
@@
     \label{eq:intro:Ixi}
-    I(\lnlam, \mathbf{x}, t, \mathbf{d}) &= 
-        I\Big(\lnlam_0 + \mathcal{D}(\bvec{x}, \bvec{d}), \mathbf{x}, t\Big)
+    I(\lnlam, \x, t, \Dargs) &= 
+        I\Big(\lnlam_0 + \D(\x, \Dargs), \x, t\Big)
 \end{align}
 %
-where $\lnlam_0$ is the log wavelength in the rest frame and $\mathcal{D}$ is
+where $\lnlam_0$ is the log wavelength in the rest frame and $\D$ is
 the Doppler shift in log wavelength space:
@@
     \label{eq:intro:D}
-    \mathcal{D}(\mathbf{x}, \mathbf{d}) 
+    \D(\x, \Dargs) 
         &=
         \frac{1}{2}\ln\left( 
-            \frac{1 + \beta(\mathbf{x}, \mathbf{d})}{1 - \beta(\mathbf{x}, 
-            \mathbf{d})} 
+            \frac{1 + \beta(\x, \Dargs)}{1 - \beta(\x, 
+            \Dargs)} 
         \right)
@@
 %
-where $\beta = v(\mathbf{x}, \mathbf{d}) / c$ is the ratio of the 
+where $\beta = v(\x, \Dargs) / c$ is the ratio of the 
 radial velocity at a point on the surface of the star to the speed of light.
 In keeping with the literature, we take positive values of $v$ (and
-$\mathcal{D}$) to mean redshifts.
+$\D$) to mean redshifts.
 
@@
 ideal when one is interested in the \emph{integral} over the visible
-surface of the star $\mathcal{S}$, which is typically all we can observe:
+surface of the star $\Surf$, which is typically all we can observe:
 %
 \begin{align}
-    \label{eq:intro:Fxi}
-    F(\lnlam, t, \bvec{d}) 
+    \label{eq:intro:F}
+    F(\lnlam, t, \Dargs) 
         &\equiv
-        \iint\limits_{\mathcal{S}(\mathbf{x})}
-                I(\lnlam, \mathbf{x}, t, \mathbf{d})
-        \mathrm{d}{\mathcal{S}(\mathbf{x})}
+        \iint\limits_{\Surf(\x)}
+                I(\lnlam, \x, t, \Dargs)
+        \mathrm{d}{\Surf(\x)}
         \quad ,
@@
 %
-The difficulty in solving Equation~(\ref{eq:intro:Fxi}) stems from the fact
-that $I(\lnlam, \mathbf{x}, t, \mathbf{d})$ is difficult to write down in 
+The difficulty in solving Equation~(\ref{eq:intro:F}) stems from the fact
+that $I(\lnlam, \x, t, \Dargs)$ is difficult to write down in 
 closed form, given
@@
 
+\subsection{Doppler Deconvolution}
+
 The observed spectrum is a complex function
@@
 section is to deconvolve each of these terms to make solving the integral
-in Equation~(\ref{eq:intro:Fxi}) easier.
+in Equation~(\ref{eq:intro:F}) easier.
 %
@@
 \begin{align}
-    \label{eq:solution:convolution}
-    I(\lnlam, \mathbf{x}, t, \mathbf{d}) &= 
-        I(\lnlam_0, \mathbf{x}, t) 
+    \label{eq:deconv:convolution}
+    I(\lnlam, \x, t, \Dargs) &= 
+        I(\lnlam_0, \x, t) 
         * 
-        \delta\big(\lnlam_0 + \mathcal{D}(\bvec{x}, \bvec{d})\big)
+        \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
 \end{align}
@@
 returning a function of the shifted log wavelength, 
-$\lnlam = \lnlam_0 + \mathcal{D}$. The convolution with the delta function
-has the effect of shifting the spectrum by an amount $\mathcal{D}$
+$\lnlam = \lnlam_0 + \D$. The convolution with the delta function
+has the effect of shifting the spectrum by an amount $\D$
 onto the observed wavelength grid.
@@
 \begin{align}
-    \label{eq:solution:Ixi0}
-    I(\lnlam_0, \mathbf{x}, t) 
+    \label{eq:deconv:Ixi0}
+    I(\lnlam_0, \x, t) 
         &=
-        \sum_{l=0}^\infty\sum_{m=-l}^{l} a_{lm}(\lnlam_0, t) Y_{lm}(\mathbf{x})
+        \sum_{l=0}^\infty\sum_{m=-l}^{l} a_{lm}(\lnlam_0, t) Y_{lm}(\x)
     \quad ,
@@
 %
-where $Y_{lm}(\mathbf{x})$ is a spherical harmonic on the projected disk
+where $Y_{lm}(\x)$ is a spherical harmonic on the projected disk
 and $a_{lm}(\lnlam_0, t)$ is the corresponding spherical harmonic 
@@
 \begin{align}
-    \label{eq:solution:Ixi0vec}
-    I(\lnlam_0, \mathbf{x}, t) &=
-    \bvec{Y}^\top(\mathbf{x}) \,
-    \bvec{a}(\lnlam_0, t)
+    \label{eq:deconv:Ixi0vec}
+    I(\lnlam_0, \x, t) &=
+    \Y^\top(\x) \,
+    \alm(\lnlam_0, t)
     \quad ,
@@
 \begin{align}
-    \bvec{a}(\lnlam_0, t) \equiv
+    \alm(\lnlam_0, t) \equiv
 \Big( 
@@
 \begin{align}
-    \bvec{Y}^\top(\mathbf{x}) \equiv 
+    \Y^\top(\x) \equiv 
 \Big( 
-    Y_{0,0}(\mathbf{x}) \quad\quad\quad\quad\quad\quad 
-    Y_{1,-1}(\mathbf{x}) \quad\quad\quad\quad\quad\quad 
-    Y_{1,0}(\mathbf{x}) \quad\quad\quad\quad\quad\quad 
-    Y_{1,1}(\mathbf{x}) \quad\quad\quad\quad\quad\quad 
+    Y_{0,0}(\x) \quad\quad\quad\quad\quad\quad 
+    Y_{1,-1}(\x) \quad\quad\quad\quad\quad\quad 
+    Y_{1,0}(\x) \quad\quad\quad\quad\quad\quad 
+    Y_{1,1}(\x) \quad\quad\quad\quad\quad\quad 
     ... 
@@
 \begin{align}
-    \label{eq:solution:R}
-    \bvec{a}(\lnlam_0, t) = \mathbf{R}(t) \bvec{a}(\lnlam_0)
+    \label{eq:deconv:R}
+    \alm(\lnlam_0, t) = \R(t) \alm(\lnlam_0)
     \quad ,
@@
 %
-where $\bvec{a}(\lnlam_0) = \bvec{a}(\lnlam_0, t=t_0)$ for some reference time $t_0$.
-For rigid body rotation, the result is exact and $\mathbf{R}(t)$ is the Wigner 
+where $\alm(\lnlam_0) = \alm(\lnlam_0, t=t_0)$ for some reference time $t_0$.
+For rigid body rotation, the result is exact and $\R(t)$ is the Wigner 
 rotation matrix for real spherical harmonics 
@@
 evolution are significant
-over the course of an observation, Equation~(\ref{eq:solution:R}) can be
+over the course of an observation, Equation~(\ref{eq:deconv:R}) can be
 made to hold approximately for some effective rotation matrix 
-$\mathbf{R}(t)$; we discuss this later.
+$\R(t)$; we discuss this later.
 
@@
 \begin{align}
-    \label{eq:solution:Ixi0vecfull}
-    I(\lnlam_0, \mathbf{x}, t) &=
-    \bvec{Y}^\top(\mathbf{x})
+    \label{eq:deconv:Ixi0vecfull}
+    I(\lnlam_0, \x, t) &=
+    \Y^\top(\x)
     \,
-    \mathbf{R}(t)
+    \R(t)
     \,
-    \bvec{a}(\lnlam_0)
+    \alm(\lnlam_0)
     \quad ,
@@
 where it is clear that we have fully separated the spatial, temporal, and
-spectral terms. Inserting this into Equation~(\ref{eq:solution:convolution}) 
+spectral terms. Inserting this into Equation~(\ref{eq:deconv:convolution}) 
 and integrating
@@
 \begin{align}
-    \label{eq:solution:Fxi2d}
-    F(\lnlam, t, \bvec{d}) &=
-    \iint\limits_{\mathcal{S}(\mathbf{x})}
-    \bvec{Y}^\top(\mathbf{x})
+    \label{eq:deconv:F2d}
+    F(\lnlam, t, \Dargs) &=
+    \iint\limits_{\Surf(\x)}
+    \Y^\top(\x)
     \,
-    \mathbf{R}(t)
+    \R(t)
     \,
-    \bvec{a}(\lnlam_0)
-    * \delta\big(\lnlam_0 + \mathcal{D}(\bvec{x}, \bvec{d})\big)
-    \mathrm{d}\mathcal{S}(\mathbf{x})
+    \alm(\lnlam_0)
+    * \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
+    \mathrm{d}\Surf(\x)
     \nonumber \\[0.5em]
     &=
-    \iint\limits_{\mathcal{S}(\mathbf{x})}
-    \bvec{Y}^\top(\mathbf{x})
-    \delta\big(\lnlam_0 + \mathcal{D}(\bvec{x}, \bvec{d})\big)
-    \mathrm{d}\mathcal{S}(\mathbf{x})
+    \iint\limits_{\Surf(\x)}
+    \Y^\top(\x)
+    \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
+    \mathrm{d}\Surf(\x)
     \,
-    \mathbf{R}(t)
+    \R(t)
     \,
@@
     \,
-    \bvec{a}(\lnlam_0)
+    \alm(\lnlam_0)
     \quad ,
@@
 
-Finally, we can simplify Equation~(\ref{eq:solution:Fxi2d}) by noting that the
+Finally, we can simplify Equation~(\ref{eq:deconv:F2d}) by noting that the
 delta function in the integrand allows us to reduce the double integral 
@@
 \begin{align}
-    \label{eq:solution:gT}
-    \iint\limits_{\mathcal{S}(\mathbf{x})}
-    \bvec{Y}^\top(\mathbf{x})
-    \delta\big(\lnlam_0 + \mathcal{D}(\bvec{x}, \bvec{d})\big)
-    \mathrm{d}\mathcal{S}(\mathbf{x})
+    \label{eq:deconv:gT}
+    \iint\limits_{\Surf(\x)}
+    \Y^\top(\x)
+    \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
+    \mathrm{d}\Surf(\x)
     \, \,
     &=  
-    \int\limits_{\mathcal{C}(\lnlam, \bvec{x}, \bvec{d})}
-    \hspace*{-0.6em}\bvec{Y}^\top(\mathbf{x})
-    \mathrm{d}\mathcal{C}(\lnlam, \bvec{x}, \bvec{d})
+    \int\limits_{\Curve(\lnlam, \x, \Dargs)}
+    \hspace*{-0.6em}\Y^\top(\x)
+    \mathrm{d}\Curve(\lnlam, \x, \Dargs)
     \nonumber \\[0.5em]
-    &\equiv \mathbf{g}^\top(\lnlam, \bvec{d})
+    &\equiv \g^\top(\lnlam, \Dargs)
     \quad.
@@
 %
-where the path $\mathcal{C}(\lnlam, \bvec{x}, \bvec{d})$ corresponds to the
+where the path $\Curve(\lnlam, \x, \Dargs)$ corresponds to the
 set of all points on the visible disk where 
-$\lnlam_0 + \mathcal{D}(\bvec{x}, \bvec{d}) = 0$.
+$\lnlam_0 + \D(\x, \Dargs) = 0$.
 %
@@
 \begin{align}
-    \label{eq:solution:Fxi}
-    F(\lnlam, t, \bvec{d}) 
+    \label{eq:deconv:F}
+    F(\lnlam, t, \Dargs) 
     &=
-    \mathbf{g}^\top(\lnlam, \bvec{d}) \, \mathbf{R}(t)
+    \g^\top(\lnlam, \Dargs) \, \R(t)
     *
-    \bvec{a}(\lnlam_0)
+    \alm(\lnlam_0)
     \quad.
@@
 %
-Equation~(\ref{eq:solution:Fxi}) is the deconvolution of the
+Equation~(\ref{eq:deconv:F}) is the deconvolution of the
 observed spectrum into velocity terms, temporal terms, and spectral/spatial
 terms, respectively. In the following sections, we will discuss how to
-efficiently solve the line integral in Equation~(\ref{eq:solution:gT}).
+efficiently solve the line integral in Equation~(\ref{eq:deconv:gT}).
 
-\section{Doppler imaging of rigid rotators}
-\label{sec:rigid}
+\subsection{Computing $\g$}
+\label{sec:g}
 %
@@
 \begin{align}
-    \beta(\mathbf{x}, \mathbf{d}) = \frac{\omega \sin i \, x}{c}
+    \beta(\x, \Dargs) = \frac{\omega \sin i \, x}{c}
 \end{align}
@@
 \begin{align}
-    \label{eq:rigid:D}
-    \mathcal{D}(\mathbf{x}, \mathbf{d}) &= 
+    \label{eq:g:D}
+    \D(\x, \Dargs) &= 
         \frac{1}{2}\ln\left( 
@@
 %
-where the parameters $\mathbf{d}$ of the Doppler field are the
+where the parameters $\Dargs$ of the Doppler field are the
 angular velocity, $\omega$, and the inclination of the star with
@@
 
-In order to solve Equation~(\ref{eq:solution:gT}), let us change basis from
+In order to solve Equation~(\ref{eq:deconv:gT}), let us change basis from
 spherical harmonics to polynomials on the sphere:
@@
 \begin{align}
-    \label{eq:rigid:gT}
-    \mathbf{g}^\top(\lnlam, \bvec{d}) &\equiv
-    \bvec{s}^\top(\lnlam, \bvec{d})
-    \bvec{A_1}
+    \label{eq:g:gT}
+    \g^\top(\lnlam, \Dargs) &\equiv
+    \s^\top(\lnlam, \Dargs)
+    \AOne
 \end{align}
@@
 \begin{align}
-    \label{eq:rigid:sTdef}
-    \mathbf{s}^\top(\lnlam, \bvec{d})
+    \label{eq:g:sTdef}
+    \s^\top(\lnlam, \Dargs)
     &\equiv
-    \int\limits_{\mathcal{C}(\lnlam, \mathbf{x}, \mathbf{d})}
-    \tilde{\bvec{p}}^\top(\mathbf{x})
-    \mathrm{d}\mathcal{C}(\lnlam, \mathbf{x}, \mathbf{d})
+    \int\limits_{\Curve(\lnlam, \x, \Dargs)}
+    \tilde{\p}^\top(\x)
+    \mathrm{d}\Curve(\lnlam, \x, \Dargs)
 \end{align}
@@
 \begin{align}
-    \tilde{\bvec{p}}(\mathbf{x}) \equiv 
+    \tilde{\p}(\x) \equiv 
 \Big( 
@@
 is the polynomial basis \citep[Equation 7 in][]{Luger2019},
-and $\bvec{A_1}$ is the change of basis matrix from spherical harmonics
+and $\AOne$ is the change of basis matrix from spherical harmonics
 to polynomials 
@@
     \oscaption{g}{%
-        The Doppler $\mathbf{g}$ basis for a rigidly rotating star
-        computed from Equation~(\ref{eq:rigid:gT}) and
-        Equation~(\ref{eq:rigid:sTrecurrence}) up to spherical 
+        The Doppler $\g$ basis for a rigidly rotating star
+        computed from Equation~(\ref{eq:g:gT}) and
+        Equation~(\ref{eq:g:sTrecurrence}) up to spherical 
         harmonic degree $l=10$. Rows correspond to the degree $l$ and
@@
 
-If we assume the star is unocculted, the region of integration $\mathcal{S}$ 
-is simply the unit disk, so $\mathcal{C}(\lnlam, \mathbf{x}, \mathbf{d})$ 
+If we assume the star is unocculted, the region of integration $\Surf$ 
+is simply the unit disk, so $\Curve(\lnlam, \x, \Dargs)$ 
 is the set of all points
-that satisfy both $\lnlam_0 + \mathcal{D}(\bvec{x}, \bvec{d}) = 0$ and 
+that satisfy both $\lnlam_0 + \D(\x, \Dargs) = 0$ and 
 $x^2 + y^2 \le 1$.
-Solving Equation~(\ref{eq:rigid:D}) for $x$, we find that 
-the curves $\mathcal{C}(\lnlam, \mathbf{x}, \mathbf{d})$ 
+Solving Equation~(\ref{eq:g:D}) for $x$, we find that 
+the curves $\Curve(\lnlam, \x, \Dargs)$ 
 are simply vertical lines on the unit disk given by 
@@
 %
-The integral in Equation~(\ref{eq:rigid:sTdef}) is therefore just an integral
+The integral in Equation~(\ref{eq:g:sTdef}) is therefore just an integral
 over $y$:
@@
 \begin{align}
-    \label{eq:rigid:sT}
-    \bvec{s}^\top(\lnlam, \bvec{d}) 
+    \label{eq:g:sT}
+    \s^\top(\lnlam, \Dargs) 
     &=    
@@
                 {\sqrt{1 - x^2}}
-    \tilde{\bvec{p}}^\top
+    \tilde{\p}^\top
     \Big(x, y\Big)
@@
 \begin{proof}{PolynomialBasis}
-    \label{eq:rigid:lm}
+    \label{eq:g:lm}
     i &= \floor*{\Lambda - \Delta}
@@
 We may now explicitly write down the $n^\mathrm{th}$ term of 
-Equation~(\ref{eq:rigid:sT}),
+Equation~(\ref{eq:g:sT}),
 %
 \begin{align}
-    \label{eq:rigid:sTexpression}
-    s_n(\lnlam, \bvec{d}) 
+    \label{eq:g:sTexpression}
+    s_n(\lnlam, \Dargs) 
     &=    
-    s_{i,\,j,\,k}(\lnlam, \bvec{d}) 
+    s_{i,\,j,\,k}(\lnlam, \Dargs) 
     =    
@@
 \begin{align}
-    \label{eq:rigid:sTrecurrence}
+    \label{eq:g:sTrecurrence}
     s_{0,\,j,\,k} &= \frac{j - 1}{j + 1 + k} \big(1 - x^2\big) s_{0,\,j-2,\,k} \nonumber \\
@@
 %
-Figure~\ref{fig:g} shows the $\mathbf{g}$ basis computed from
-the formulae above and Equation~(\ref{eq:rigid:gT}) up to spherical 
+Figure~\ref{fig:g} shows the $\g$ basis computed from
+the formulae above and Equation~(\ref{eq:g:gT}) up to spherical 
 harmonic degree $l=10$.
+
+This completes our derivation of the analytic expression for the
+observed spectrum (Equation~\ref{eq:deconv:F}).
+
+\subsection{Linearization}
+\label{sec:linear}
+
+\section{Performance}
+\label{sec:performance}
+Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires 
+first the rotation of the $(\lmax + 1)^2$
+$\g$ functions (each of length $W$) to the correct stellar 
+rotational phase, an operation that scales approximately
+as $W \lmax^3$,
+followed by $(\lmax + 1)^2$
+linear convolutions of the rotated $\g$ functions with the 
+spectral components (each of length $K$), which scales
+approximately as $W K \lmax^2$. Since typically $K \gg \lmax$,
+the latter computation dominates and the entire evaluation 
+takes $\mathcal{O}(W K \lmax^2)$ operations.
 
@@
         Time evolution of a Gaussian absorption line on a rigidly rotating, 
-        spotted star computed from the analytic formulae in \S\ref{sec:rigid}.
+        spotted star computed from the analytic formulae in \S\ref{sec:g}.
         The stellar surface is modeled as a spherical harmonic expansion
@@
     \oscaption{linalg}{%
-        The linear Doppler imaging problem, $\bvec{f} = \bvec{D} \bvec{a}$
-        (Equation~\ref{eq:fDa}).
-        The vector on the left hand side, $\bvec{f}$, is the model for the
-        observed flux, a sequence of $M$ spectra taken at different times,
-        each measured at $K$ wavelength bins (plotted to the left of $\bvec{f}$). 
-        The matrix on the right hand 
-        side, $\bvec{D}$, is
-        the Doppler design matrix, constructed from $M \times N$ Toeplitz
-        matrices, each of shape $K \times (K + W)$, where $W$ is the width
-        of the convolution kernels (plotted at the top) and $N$ is the 
-        number of spherical harmonic
-        coefficients in the expansion of the stellar surface.
-        The $N$ columns of $\mathcal{D}$ correspond
-        to the Toeplitz matrices for each of the $N$ spherical harmonics;
+        The Doppler design matrix, constructed from a grid of Toeplitz
+        matrices, each of shape $K \times (K + W - 1)$, where $K$
+        is the number of wavelength bins in the observed spectrum and
+        $W$ is the width of the convolution kernels.
+        The $N$ columns of $\D$ correspond
+        to the Toeplitz matrices for each of the $N$ spherical harmonics
+        (shown at the top);
         the $M$ rows correspond to the Toeplitz matrices rotated to each
         of the $M$ stellar phases observed (indicated graphically 
-        to the left of $\mathbf{D}$). Finally, the vector at the 
-        right is the weight vector $\bvec{a}$, a sequence of $N$ spectral 
-        components, each of length $K + W$ (plotted to the right). 
-        In this example, each segment of
-        $\bvec{a}$ is equal to a simple Gaussian line profile weighted by
-        the spherical harmonic coefficients of a large equatorial starspot;
-        this corresponds to a star whose spectrum is the same everywhere, but
-        whose overall brightness varies spatially.
+        to the left of $\bvec{D}$).
         \label{fig:linalg}
-    }
-    \end{centering}
-\end{figure}
-
-\begin{figure}[p!]
-    \begin{centering}
-    \includegraphics[width=1.0\linewidth]{figures/linalg_u.pdf}
-    \oscaption{linalg_u}{%
-        Similar to Figure~\ref{fig:linalg}, but isolating the linear dependence
-        of the model on the spherical harmonic coefficients:
-        $\bvec{f} = \bvec{D}\bvec{V}\bvec{u}$ (Equation~\ref{eq:fDVu}).
-        The $\bvec{f}$ vector and the $\bvec{D}$ design matrix are the same
-        as before, but the spectra have been factored out 
-        of the weight vector and into the $(N \times NP)$ matrix
-        $\bvec{V}$, a block diagonal matrix constructed from $P$
-        distinct spectral components (plotted at the top).
-        \label{fig:linalg_u}
     }
@@
 \section{Integrals}
-\subsection{Equation~(\ref{eq:rigid:sTexpression})}
+\subsection{Equation~(\ref{eq:g:sTexpression})}
 %
 In this section we derive the recurrence relations
-(\ref{eq:rigid:sTrecurrence}) for computing $\mathbf{s}^\top$.
+(\ref{eq:g:sTrecurrence}) for computing $\s^\top$.
 When $i = k = 0$, the integral is easy to evaluate:

### 2019-08-02 tex/figures/linalg.py

@@ -2,7 +2,7 @@
 import matplotlib.pyplot as plt
 import numpy as np
 import paparazzi as pp
-from scipy.sparse import hstack, vstack, csr_matrix, block_diag
+from scipy.sparse import hstack, vstack, csr_matrix, block_diag, diags
 import starry
 np.random.seed(11)
 
@@ -151,473 +151,107 @@ def get_ortho_longitude_lines(inc=np.pi/2, obl=0, theta=0,
     return res
 
 
-def plot_main():
-    """
-    Plot the main figure showing the equation ``f = D a``.
 
-    """
-    # Settings for this figure
-    ydeg = 2
-    ntheta = 11
-    inc = 40.
-    vsini = 80.
-    nlam = 11
+# Settings for this figure
+ydeg = 2
+ntheta = 11
+inc = 40.
+vsini = 80.
+nlam = 121
 
-    #
-    # Compute stuff!
-    #
+#
+# Compute stuff!
+#
 
-    # Compute the g-functions and the corresponding Toeplitz matrices
-    lnlam = np.linspace(-6e-4, 6e-4, nlam)
-    doppler = pp.Doppler(ydeg=ydeg, vsini=vsini, inc=inc)
-    doppler._set_lnlam(lnlam)
-    g = doppler.g
-    T = doppler.T
+# Compute the g-functions and the corresponding Toeplitz matrices
+lnlam = np.linspace(-6e-4, 6e-4, nlam)
+doppler = pp.Doppler(ydeg=ydeg, vsini=vsini, inc=inc)
+doppler._set_lnlam(lnlam)
+g = doppler.g
+T = [None for n in range(doppler.N)]
+for n in range(doppler.N):
+    diagonals = np.tile(g[n].reshape(-1, 1), doppler.K)
+    if np.any(diagonals):
+        diagonals[diagonals == 0] = 1e-5
+    offsets = np.arange(doppler.W)
+    T[n] = diags(diagonals, offsets, 
+                (doppler.K, doppler.K + doppler.W - 1), format="csr")
 
-    # Pad them to reveal the structure
-    for n in range(doppler.N):
-        T[n] = T[n].toarray()
-        T[n][:, 0] = np.nan
-        T[n][:, -1] = np.nan
-        T[n] = csr_matrix(T[n])
-        T[n] = vstack((T[n], np.nan * np.ones((2, T[n].shape[1]))))
[…]

### 2019-08-02 tex/gitlinks.tex
more words

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/7c3f626863f61d2a592a381e10d381862ebcb9fb/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/7c3f626863f61d2a592a381e10d381862ebcb9fb/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/7c3f626863f61d2a592a381e10d381862ebcb9fb/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/93997d2ef089c7be911a4ebbb4e4d41963d4d260/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/93997d2ef089c7be911a4ebbb4e4d41963d4d260/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/93997d2ef089c7be911a4ebbb4e4d41963d4d260/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-08-02 tex/ms.tex
more words

@@
 Dirac delta function and
-$*$ denotes the linear convolution operator,
-returning a function of the shifted log wavelength, 
-$\lnlam = \lnlam_0 + \D$. The convolution with the delta function
-has the effect of shifting the spectrum by an amount $\D$
-onto the observed wavelength grid.
+$*$ denotes the linear convolution operator, defined for
+two arbitrary functions $f$ and $h$ as the integral
+%
+\begin{align}
+    \label{eq:deconv:convolution_def}
+    (f * h)(t) \equiv \int_{-\infty}^\infty f(\tau) h(t - \tau) d\tau
+\end{align}
+%
+for some independent coordinate $t$ and dummy parameter $\tau$.
+%
+The convolution of $I(\lnlam_0)$ with a delta function
+has the effect of shifting the spectrum by an amount $\D$, returning
+a function of the shifted (observed) log wavelength, 
+$\lnlam = \lnlam_0 + \D$.
 
@@
 
-\subsection{Computing $\g$}
+\subsection{Computing $\g^\top$}
 \label{sec:g}
@@
 This completes our derivation of the analytic expression for the
-observed spectrum (Equation~\ref{eq:deconv:F}).
+observed spectrum (Equation~\ref{eq:deconv:F}). As we show later,
+this equation allows us to compute the forward model for the
+spectrum very efficiently, particularly if we make use of Fast-Fourier
+Transform (FFT) -based convolution techniques. However, a convolution
+can also be represented as a matrix dot product, which we can use to
+express the model for the observed spectrum as a purely linear
+operation on the map decomposition $\alm(\lnlam_0)$. In the following section
+we derive this expression and show how it can be used to obtain
+fast, analytic solutions to the Doppler problem.
 
@@
 
-\section{Performance}
-\label{sec:performance}
-Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires 
-first the rotation of the $(\lmax + 1)^2$
-$\g$ functions (each of length $W$) to the correct stellar 
-rotational phase, an operation that scales approximately
-as $W \lmax^3$,
-followed by $(\lmax + 1)^2$
-linear convolutions of the rotated $\g$ functions with the 
-spectral components (each of length $K$), which scales
-approximately as $W K \lmax^2$. Since typically $K \gg \lmax$,
-the latter computation dominates and the entire evaluation 
-takes $\mathcal{O}(W K \lmax^2)$ operations.
+\begin{figure}[ht!]
+    \begin{centering}
+    \includegraphics[width=0.8\linewidth]{figures/linalg.pdf}
+    \oscaption{linalg}{%
+        The Doppler design matrix $\bvec{D}$ (Equation~\ref{eq:linear:f}), 
+        constructed from a grid of Toeplitz
+        matrices, each of shape $K \times (K + W - 1)$, where $K$
+        is the number of wavelength bins in the observed spectrum and
+        $W$ is the width of the convolution kernels.
+        The $N$ columns of $\bvec{D}$ correspond
+        to the Toeplitz matrices for each of the $N$ spherical harmonics
+        (shown at the top);
+        the $M$ rows correspond to the Toeplitz matrices rotated to each
+        of the $M$ stellar phases observed (indicated graphically 
+        to the left of $\bvec{D}$).
+        \label{fig:linalg}
+    }
+    \end{centering}
+\end{figure}
+
+Although the convolution operator (Equation~\ref{eq:deconv:convolution_def})
+is defined for continuous functions, the problem of Doppler imaging deals with
+discrete measurements of a spectrum in bins of log wavelength. Provided our
+wavelength grid is fine enough, we may therefore approximate 
+Equation~(\ref{eq:deconv:convolution_def}) with a discrete convolution.
+For discrete arrays $\bvec{f}$ and $\bvec{h}$, we have
+%
+\begin{align}
+    \label{eq:linear:convolution_def}
+    \bvec{f} * \bvec{h} = \bvec{T}(\bvec{f}) \, \bvec{h}
+\end{align}
+%
+where $\bvec{T}(\bvec{f})$ is a Toeplitz matrix, a matrix whose diagonals
+are constant from top left to bottom right. In this case, the diagonals
+are constructed from the values of $\bvec{f}$. If $\bvec{f}$ has length
+$N$, element $f_n$ is placed everywhere along the $k^\mathrm{th}$ diagonal 
+of $\bvec{T}$ for $k = -N / 2 + n$; all other entries of $\bvec{T}$ are 
+set to zero.
+
+Given this formulation, we may re-write Equation~(\ref{eq:deconv:F}) as a
+purely linear operation on $\alm(\lnlam_0)$:
+%
+\begin{align}
+    \label{eq:linear:f}
+    \bvec{f}
+    &=
+    \bvec{D}(\g^\top, \R)
+    \,
+    \alm
+    \quad,
+\end{align}
+%
+where we introduce the \emph{Doppler design matrix} $\bvec{D}$, constructed
+by concatenating the Toeplitz matrices for each of the components of the
+convolution kernel $\g^\top(\lnlam, \Dargs)$ after rotating it (via $\R(t)$) 
+to the correct stellar phase.
+
+\section{Validation}
+\label{sec:validation}
+
+Words here. Figure~\ref{fig:spot} and Figure~\ref{fig:compare}.
 
@@
 
-\begin{figure}[p!]
-    \begin{centering}
-    \includegraphics[width=1.0\linewidth]{figures/linalg.pdf}
-    \oscaption{linalg}{%
-        The Doppler design matrix, constructed from a grid of Toeplitz
-        matrices, each of shape $K \times (K + W - 1)$, where $K$
-        is the number of wavelength bins in the observed spectrum and
-        $W$ is the width of the convolution kernels.
-        The $N$ columns of $\D$ correspond
-        to the Toeplitz matrices for each of the $N$ spherical harmonics
-        (shown at the top);
-        the $M$ rows correspond to the Toeplitz matrices rotated to each
-        of the $M$ stellar phases observed (indicated graphically 
-        to the left of $\bvec{D}$).
-        \label{fig:linalg}
-    }
-    \end{centering}
-\end{figure}
+\section{Performance}
+\label{sec:performance}
+
+Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires 
+first the rotation of the $(\lmax + 1)^2$
+$\g$ functions (each of length $W$) to the correct stellar 
+rotational phase, an operation that scales approximately
+as $W \lmax^3$,
+followed by $(\lmax + 1)^2$
+linear convolutions of the rotated $\g$ functions with the 
+spectral components (each of length $K$), which scales
+approximately as $W K \lmax^2$. Since typically $K \gg \lmax$,
+the latter computation dominates and the entire evaluation 
+takes $\mathcal{O}(W K \lmax^2)$ operations.
 

### 2019-08-05 tex/gitlinks.tex
reorg

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/93997d2ef089c7be911a4ebbb4e4d41963d4d260/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/93997d2ef089c7be911a4ebbb4e4d41963d4d260/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/93997d2ef089c7be911a4ebbb4e4d41963d4d260/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/e25a0b01c116a70302de31d94e501d0c03ad9d70/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/e25a0b01c116a70302de31d94e501d0c03ad9d70/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/e25a0b01c116a70302de31d94e501d0c03ad9d70/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-08-05 tex/ms.tex
reorg

@@
 \newcommand{\x}{\bvec{x}}
-\newcommand{\g}{\bvec{g}}
+\newcommand{\kT}{\bvec{k}^\top}
 \newcommand{\D}{\mathcal{D}}
+\newcommand{\Doppler}{\bvec{D}}
 \newcommand{\Surf}{\mathcal{S}}
@@
 \begin{align}
+    \label{eq:deconv:alm}
     \alm(\lnlam_0, t) \equiv
@@
     \nonumber \\[0.5em]
-    &\equiv \g^\top(\lnlam, \Dargs)
+    &\equiv \kT(\lnlam, \Dargs)
     \quad.
@@
     &=
-    \g^\top(\lnlam, \Dargs) \, \R(t)
+    \kT(\lnlam, \Dargs) \, \R(t)
     *
@@
 
-\subsection{Computing $\g^\top$}
+\subsection{Computing the kernel $\kT$}
 \label{sec:g}
@@
     \label{eq:g:gT}
-    \g^\top(\lnlam, \Dargs) &\equiv
+    \kT(\lnlam, \Dargs) &\equiv
     \s^\top(\lnlam, \Dargs)
@@
     \oscaption{g}{%
-        The Doppler $\g$ basis for a rigidly rotating star
+        The Doppler $\kT$ basis for a rigidly rotating star
         computed from Equation~(\ref{eq:g:gT}) and
@@
 %
-Figure~\ref{fig:g} shows the $\g$ basis computed from
+Figure~\ref{fig:g} shows the $\kT$ basis computed from
 the formulae above and Equation~(\ref{eq:g:gT}) up to spherical 
@@
     \oscaption{linalg}{%
-        The Doppler design matrix $\bvec{D}$ (Equation~\ref{eq:linear:f}), 
+        The Doppler design matrix $\Doppler$ (Equation~\ref{eq:linear:f}), 
         constructed from a grid of Toeplitz
-        matrices, each of shape $K \times (K + W - 1)$, where $K$
+        matrices, each of shape $K \times K'$, where $K$
         is the number of wavelength bins in the observed spectrum and
-        $W$ is the width of the convolution kernels.
-        The $N$ columns of $\bvec{D}$ correspond
+        $K' = K + W - 1$ is the number of bins in the model spectrum,
+        where $W$ is the width of the convolution kernel.
+        The $N$ columns of $\Doppler$ correspond
         to the Toeplitz matrices for each of the $N$ spherical harmonics
@@
         of the $M$ stellar phases observed (indicated graphically 
-        to the left of $\bvec{D}$).
+        to the left of $\Doppler$).
         \label{fig:linalg}
@@
     &=
-    \bvec{D}(\g^\top, \R)
+    \Doppler(\kT, \R)
     \,
@@
 %
-where we introduce the \emph{Doppler design matrix} $\bvec{D}$, constructed
-by concatenating the Toeplitz matrices for each of the components of the
-convolution kernel $\g^\top(\lnlam, \Dargs)$ after rotating it (via $\R(t)$) 
+where we introduce the $(K \times N K')$ Doppler design matrix $\Doppler$, 
+constructed
+by concatenating the Toeplitz matrices for each of the $N$ components of the
+convolution kernel $\kT(\lnlam, \Dargs)$ after rotating it (via $\R(t)$) 
 to the correct stellar phase. 
+%
+The $(K \times 1)$ vector $\mathbf{f}$ is the model for 
+the flux observed at each wavelength at a particular time, and the 
+$(N K' \times 1)$ vector $\alm$ is the vector representation of the
+spatially-dependent spectrum of the star. The latter is constructed
+by concatenating the ...
+(Equation~\ref{eq:deconv:alm})
+
+In Figure~\ref{fig:linalg} we show an
+example of $\Doppler$.
 
@@
 first the rotation of the $(\lmax + 1)^2$
-$\g$ functions (each of length $W$) to the correct stellar 
+$\kT$ kernels (each of length $W$) to the correct stellar 
 rotational phase, an operation that scales approximately
@@
 followed by $(\lmax + 1)^2$
-linear convolutions of the rotated $\g$ functions with the 
+linear convolutions of the rotated $\kT$ kernels with the 
 spectral components (each of length $K$), which scales

### 2019-08-05 scratch/newvogt.py

@@ -1,144 +1,0 @@
-import paparazzi as pp
-import numpy as np
-import matplotlib.pyplot as plt
-from tqdm import tqdm
-import celerite
-from scipy.linalg import cho_factor
-np.random.seed(13)
-
-
-def learn_everything(high_snr=False):
-    """
-
-    """
-    # High or low SNR?
-    if high_snr:
-        ferr = 1e-4
-        niter_bilinear = 25
-        niter_adam = 2500
-    else:
-        ferr = 1e-3
-        niter_bilinear = 10
-        niter_adam = 0
-
-    # Generate data
-    D = pp.Doppler(ydeg=15)
-    D.generate_data(ferr=ferr)
-
-    # Compute loss @ true value
-    D.u = D.u_true
-    D.vT = D.vT_true
-    loss_true = D.loss()
-
-    # Estimate the rest frame spectrum from the deconvolved mean spectrum
-    fmean = np.mean(D.F, axis=0)
-    fmean -= np.mean(fmean)
-    A = D.T[0]
-    LInv = 1e-4 * np.eye(A.shape[1])
-    vT_guess = 1 + np.linalg.solve(A.T.dot(A).toarray() + LInv, A.T.dot(fmean))
-    D.vT = vT_guess
-
-    # Pre-compute the Cholesky factorization of the GP for vT
-    sig = 0.3
-    rho = 3.e-5
-    kernel = celerite.terms.Matern32Term(np.log(sig), np.log(rho))
-    gp = celerite.GP(kernel)
-    C = gp.get_matrix(D.lnlam_padded)
-    cho_C = cho_factor(C)
-
-    # Reset the map
-    D.compute_u(baseline=np.ones(D.M))
-
-    # Iterative Bi-linear solve
-    loss = np.zeros(niter_bilinear)
-    
-    for i in tqdm(range(niter_bilinear)):
-        D.compute_u()
-        D.compute_vT(cho_C=cho_C)
-        loss[i] = D.loss()
-    
-    # Refine with NAdam, slow learning rate
-    if niter_adam > 0:
-        loss = np.append(loss, 
-            D.solve(vT_guess=D.vT, u_guess=D.u, niter=niter_adam, lr=1e-4))
-
-    # Plot the results
-    fig, ax = plt.subplots(1, figsize=(6, 8))
-    ax.plot(loss)
-    ax.axhline(loss_true, color="C1", ls="--")
-    ax.set_yscale("log")
-
-    fig = plt.figure()
-    plt.plot(D.vT_true)
[…]

### 2019-08-05 scratch/vogtstar.py

@@ -1,590 +1,144 @@
-# -*- coding: utf-8 -*-
-import matplotlib.pyplot as plt
-import numpy as np
-import starry
 import paparazzi as pp
-import os
-import subprocess
-import celerite
-from scipy.linalg import cho_factor, cho_solve
-from scipy.sparse import block_diag, diags
-from scipy.linalg import block_diag as dense_block_diag
+import numpy as np
+import matplotlib.pyplot as plt
 from tqdm import tqdm
-import theano.tensor as tt
-import theano.sparse as ts
-import theano
-from theano.ifelse import ifelse
+import celerite
+from scipy.linalg import cho_factor
+np.random.seed(13)
 
 
-__all__ = ["Solver"]
-
-
-def Adam(cost, params, lr=0.001, b1=0.9, b2=0.999, e=1e-8):
-    """https://gist.github.com/Newmu/acb738767acb4788bac3
+def learn_everything(high_snr=False):
+    """
 
     """
-    updates = []
-    grads = tt.grad(cost, params)
-    i = theano.shared(np.array(0.,dtype=theano.config.floatX))
-    i_t = i + 1.
-    fix1 = 1. - (1. - b1)**i_t
-    fix2 = 1. - (1. - b2)**i_t
-    lr_t = lr * (tt.sqrt(fix2) / fix1)
-    for p, g in zip(params, grads):
-        m = theano.shared(p.get_value() * 0.)
-        v = theano.shared(p.get_value() * 0.)
-        m_t = (b1 * g) + ((1. - b1) * m)
-        v_t = (b2 * tt.sqr(g)) + ((1. - b2) * v)
-        g_t = m_t / (tt.sqrt(v_t) + e)
-        p_t = p - (lr_t * g_t)
-        updates.append((m, m_t))
-        updates.append((v, v_t))
-        updates.append((p, p_t))
-    updates.append((i, i_t))
-    return updates
+    # High or low SNR?
+    if high_snr:
+        ferr = 1e-4
+        niter_bilinear = 25
+        niter_adam = 2500
+    else:
+        ferr = 1e-3
+        niter_bilinear = 10
+        niter_adam = 0
 
+    # Generate data
+    D = pp.Doppler(ydeg=15)
+    D.generate_data(ferr=ferr)
 
-class Solver(object):
-    """Solve the Doppler imaging problem.
+    # Compute loss @ true value
+    D.u = D.u_true
+    D.vT = D.vT_true
[…]

### 2019-08-06 tex/gitlinks.tex
require celerite

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/e25a0b01c116a70302de31d94e501d0c03ad9d70/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/e25a0b01c116a70302de31d94e501d0c03ad9d70/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/e25a0b01c116a70302de31d94e501d0c03ad9d70/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/7b48dcaaefaaa4a6801c5b8d446707174e057c94/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/7b48dcaaefaaa4a6801c5b8d446707174e057c94/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/7b48dcaaefaaa4a6801c5b8d446707174e057c94/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-08-07 tex/gitlinks.tex
working on the paper

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/7b48dcaaefaaa4a6801c5b8d446707174e057c94/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/7b48dcaaefaaa4a6801c5b8d446707174e057c94/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/7b48dcaaefaaa4a6801c5b8d446707174e057c94/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/b9ff114beba2d54f032d05754e1d62ef624acd09/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/b9ff114beba2d54f032d05754e1d62ef624acd09/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/b9ff114beba2d54f032d05754e1d62ef624acd09/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-08-07 tex/ms.tex
working on the paper

@@
 
-\newcommand{\s}{\bvec{s}}
-\newcommand{\p}{\bvec{p}}
+\newcommand{\sT}{\bvec{s}^\top}
 \newcommand{\R}{\bvec{R}}
@@
 \newcommand{\alm}{\bvec{a}}
-\newcommand{\Y}{\bvec{Y}}
 \newcommand{\x}{\bvec{x}}
@@
 \newcommand{\lmax}{\ensuremath{l_\mathrm{max}}}
+
+% TODO: Use blackboard bold (bbm)
+\newcommand{\ylmbasis}{\boldsymbol{\psi}^\top}
+\newcommand{\pbasis}{\boldsymbol{\phi}^\top}
+\newcommand{\pbasisn}{\ensuremath{\phi_n}}
 
@@
 $*$ denotes the linear convolution operator, defined for
-two arbitrary functions $f$ and $h$ as the integral
+two arbitrary functions $g$ and $h$ as the integral
 %
@@
     \label{eq:deconv:convolution_def}
-    (f * h)(t) \equiv \int_{-\infty}^\infty f(\tau) h(t - \tau) d\tau
+    (g * h)(t) \equiv \int_{-\infty}^\infty f(\tau) h(t - \tau) d\tau
 \end{align}
@@
 \begin{align}
-    \label{eq:deconv:Ixi0vec}
+    \label{eq:deconv:Ivec}
     I(\lnlam_0, \x, t) &=
-    \Y^\top(\x) \,
+    \ylmbasis(\x) \,
     \alm(\lnlam_0, t)
@@
 \begin{align}
-    \Y^\top(\x) \equiv 
+    \ylmbasis(\x) \equiv 
 \Big( 
@@
 \begin{align}
-    \label{eq:deconv:Ixi0vecfull}
+    \label{eq:deconv:Ivecfull}
     I(\lnlam_0, \x, t) &=
-    \Y^\top(\x)
+    \ylmbasis(\x)
     \,
@@
     \iint\limits_{\Surf(\x)}
-    \Y^\top(\x)
+    \ylmbasis(\x)
     \,
@@
     \iint\limits_{\Surf(\x)}
-    \Y^\top(\x)
+    \ylmbasis(\x)
     \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
@@
 \begin{align}
-    \label{eq:deconv:gT}
+    \label{eq:deconv:kT}
     \iint\limits_{\Surf(\x)}
-    \Y^\top(\x)
+    \ylmbasis(\x)
     \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
@@
     \int\limits_{\Curve(\lnlam, \x, \Dargs)}
-    \hspace*{-0.6em}\Y^\top(\x)
+    \hspace*{-0.6em}\ylmbasis(\x)
     \mathrm{d}\Curve(\lnlam, \x, \Dargs)
@@
 terms, respectively. In the following sections, we will discuss how to
-efficiently solve the line integral in Equation~(\ref{eq:deconv:gT}).
+efficiently solve the line integral in Equation~(\ref{eq:deconv:kT}).
 
 \subsection{Computing the kernel $\kT$}
-\label{sec:g}
+\label{sec:kT}
 %
@@
 \begin{align}
-    \label{eq:g:D}
+    \label{eq:kT:D}
     \D(\x, \Dargs) &= 
@@
 
-In order to solve Equation~(\ref{eq:deconv:gT}), let us change basis from
-spherical harmonics to polynomials on the sphere:
-%
-\begin{align}
-    \label{eq:g:gT}
-    \kT(\lnlam, \Dargs) &\equiv
-    \s^\top(\lnlam, \Dargs)
-    \AOne
-\end{align}
-%
-where
-%
-\begin{align}
-    \label{eq:g:sTdef}
-    \s^\top(\lnlam, \Dargs)
-    &\equiv
-    \int\limits_{\Curve(\lnlam, \x, \Dargs)}
-    \tilde{\p}^\top(\x)
-    \mathrm{d}\Curve(\lnlam, \x, \Dargs)
-\end{align}
-%
-is the vector of integral solutions for each spherical harmonic,
-%
-\begin{align}
-    \tilde{\p}(\x) \equiv 
-\Big( 
-    1 \quad\quad\quad\quad\quad\quad 
-    x \quad\quad\quad\quad\quad\quad 
-    z \quad\quad\quad\quad\quad\quad 
-    y \quad\quad\quad\quad\quad\quad 
-    x^2 \quad\quad\quad\quad\quad\quad 
-    xz \quad\quad\quad\quad\quad\quad 
-    xy \quad\quad\quad\quad\quad\quad
-    yz \quad\quad\quad\quad\quad\quad 
-    y^2 \quad\quad\quad\quad\quad\quad
-    ... 
-\Big)^\top
-\end{align}
-%
-is the polynomial basis \citep[Equation 7 in][]{Luger2019},
-and $\AOne$ is the change of basis matrix from spherical harmonics
-to polynomials 
-\citep[Equation B11 in][]{Luger2019}. On the observer-facing surface of 
-the unit sphere, the coordinate $z$ is given by $\sqrt{1 - x^2 - y^2}$.
-
-\begin{figure}[h!]
+\begin{figure}[t!]
     \begin{centering}
-    \includegraphics[width=\linewidth]{figures/g.pdf}
+    \includegraphics[width=\linewidth]{figures/kT.pdf}
     \oscaption{g}{%
         The Doppler $\kT$ basis for a rigidly rotating star
-        computed from Equation~(\ref{eq:g:gT}) and
-        Equation~(\ref{eq:g:sTrecurrence}) up to spherical 
+        computed from Equation~(\ref{eq:kT:kT}) and
+        Equation~(\ref{eq:kT:sTrecurrence}) up to spherical 
         harmonic degree $l=10$. Rows correspond to the degree $l$ and
@@
         spectrum.
-        \label{fig:g}
+        \label{fig:kT}
     }
@@
 
-If we assume the star is unocculted, the region of integration $\Surf$ 
-is simply the unit disk, so $\Curve(\lnlam, \x, \Dargs)$ 
+If we assume the star is unocculted, the region of integration $\Surf(\x)$ 
+in Equation~(\ref{eq:deconv:kT}) is simply the unit disk, 
+so $\Curve(\lnlam, \x, \Dargs)$ 
 is the set of all points
@@
 $x^2 + y^2 \le 1$.
-Solving Equation~(\ref{eq:g:D}) for $x$, we find that 
+Solving Equation~(\ref{eq:kT:D}) for $x$, we find that 
 the curves $\Curve(\lnlam, \x, \Dargs)$ 
@@
 %
-The integral in Equation~(\ref{eq:g:sTdef}) is therefore just an integral
-over $y$:
+The integral in Equation~(\ref{eq:deconv:kT}) is therefore just the line integral
+of the spherical harmonic basis over $y$:
 %
 \begin{align}
-    \label{eq:g:sT}
-    \s^\top(\lnlam, \Dargs) 
+    \label{eq:kT:kT}
+    \kT(\lnlam, \Dargs) 
     &=    
@@
                 {\sqrt{1 - x^2}}
-    \tilde{\p}^\top
+    \ylmbasis
     \Big(x, y\Big)
@@
 %
-From \citet{Luger2019}, the $n^\mathrm{th}$ term of the polynomial basis
-is a polynomial in $x$, $y$, and $z = \sqrt{1 - x^2 - y^2}$:
+In the Appendix we derive an analytic solution to this integral and show
+how to recursively solve it for all terms in the spherical harmonic basis. 
 %
-\begin{proof}{PolynomialBasis}
-    \tilde{p}_n 
-    &=
-    x^i y^j z^k
-\end{proof}
-%
-where $i, j, k$ are integers given by
-%
-\begin{proof}{PolynomialBasis}
-    \label{eq:g:lm}
-    i &= \floor*{\Lambda - \Delta}
-    \nonumber \\[0.5em]
-    j &= \floor*{\Delta}
-    \nonumber \\[0.5em]
-    k &= \ceil*{\Delta} - \floor*{\Delta}
-\end{proof}
-%
-with
-%
-\begin{proof}{PolynomialBasis}
-    \Lambda &= \floor*{\sqrt{n}}
-    \nonumber \\[0.5em]
-    \Delta &= \frac{n - \Lambda^2}{2}
-    \quad .
-\end{proof}
-%
-We may now explicitly write down the $n^\mathrm{th}$ term of 
-Equation~(\ref{eq:g:sT}),
-%
-\begin{align}
-    \label{eq:g:sTexpression}
-    s_n(\lnlam, \Dargs) 
-    &=    
-    s_{i,\,j,\,k}(\lnlam, \Dargs) 
-    =    
-    x^i
-    \int\limits_{-\sqrt{1 - x^2}}^
-                {\sqrt{1 - x^2}}
-        y^j
-        \left(1 - x^2 - y^2\right)^{\frac{k}{2}} \,
-    \mathrm{d}y 
-    \quad .
-\end{align}
-%
-As we show in the Appendix, the solution to this integral
-is analytic and expressible in terms of simple recurrence
-relations. Given the boundary conditions
-%
-\begin{align}
-    s_{0,\,0,\,0} &= 2 \sqrt{1-x^2} \nonumber \\
-    s_{0,\,0,\,1} &= \frac{\pi}{2} \big(1-x^2\big) \nonumber \\
-    s_{0,\,1,\,k} &= 0 \quad ,
-\end{align}
-%
-we may compute any term in the series via the expressions
-%
-\begin{align}
-    \label{eq:g:sTrecurrence}
-    s_{0,\,j,\,k} &= \frac{j - 1}{j + 1 + k} \big(1 - x^2\big) s_{0,\,j-2,\,k} \nonumber \\
-    s_{i,\,j,\,k} &= x \, s_{i-1,\,j,\,k} \quad.
-\end{align}
-%
-Figure~\ref{fig:g} shows the $\kT$ basis computed from
-the formulae above and Equation~(\ref{eq:g:gT}) up to spherical 
+Figure~\ref{fig:kT} shows the $\kT$ basis computed from
+the formulae above and Equation~(\ref{eq:kT:kT}) up to spherical 
 harmonic degree $l=10$.
@@
 Equation~(\ref{eq:deconv:convolution_def}) with a discrete convolution.
-For discrete arrays $\bvec{f}$ and $\bvec{h}$, we have
+For discrete arrays $\bvec{g}$ and $\bvec{h}$, we have
 %
@@
     \label{eq:linear:convolution_def}
-    \bvec{f} * \bvec{h} = \bvec{T}(\bvec{f}) \, \bvec{h}
+    \bvec{g} * \bvec{h} = \bvec{G} \, \bvec{h}
 \end{align}
 %
-where $\bvec{T}(\bvec{f})$ is a Toeplitz matrix, a matrix whose diagonals
+where $\bvec{G}$ is a Toeplitz matrix, a matrix whose diagonals
 are constant from top left to bottom right. In this case, the diagonals
-are constructed from the values of $\bvec{f}$. If $\bvec{f}$ has length
-$N$, element $f_n$ is placed everywhere along the $k^\mathrm{th}$ diagonal 
-of $\bvec{T}$ for $k = -N / 2 + n$; all other entries of $\bvec{T}$ are 
-set to zero.
+are constructed from the values of $\bvec{g}$. If $\bvec{g}$ has length
+$N$, element $g_n$ is placed everywhere along the $k^\mathrm{th}$ diagonal 
+of $\bvec{G}$ for $k = -N / 2 + n$; all other entries of $\bvec{G}$ are 
+set to zero. Note that the matrix $\bvec{G}$ need not be square; in fact,
+for our purposes, it is a $(K \times K')$ matrix, where $K$ is the 
+size of the observed wavelength grid and $K' = K + W - 1$ is the size of the
+wavelength grid in the rest frame, where $W$ is the width of the convolution
+kernel.
 
@@
 \begin{align}
-    \label{eq:linear:f}
-    \bvec{f}
+    \label{eq:linear:ft}
+    \bvec{f}_t
     &=
-    \Doppler(\kT, \R)
+    \Doppler_t
     \,
@@
 %
-where we introduce the $(K \times N K')$ Doppler design matrix $\Doppler$, 
-constructed
-by concatenating the Toeplitz matrices for each of the $N$ components of the
-convolution kernel $\kT(\lnlam, \Dargs)$ after rotating it (via $\R(t)$) 
-to the correct stellar phase. 
+where $\Doppler_t$ is a $(K \times N K')$ matrix constructed
+by horizontally concatenating the Toeplitz matrices for each of the $N$ 
+components of the convolution kernel $\kT(\lnlam, \Dargs)$ after rotating 
+them (via $\R(t)$) to the stellar phase at time $t$. 
 %
@@
 spatially-dependent spectrum of the star. The latter is constructed
-by concatenating the ...
-(Equation~\ref{eq:deconv:alm})
+by flattening the spherical harmonic expansion of the star
+such that the first $K'$ terms in $\alm$ correspond
+to the the values of $a_{0,0}$ at each wavelength $\lnlam_0$,
+followed by the values of $a_{0,0}$ at each wavelength, and so forth.
 
-In Figure~\ref{fig:linalg} we show an
+In general, our data will consist of observations made at several
+epochs, corresponding to different rotational phases of the star. 
+If we concatenate all $M$ spectra $\bvec{f}_t$ into the $(MK \times 1)$ 
+vector $\bvec{f}$, we may write
+%
+\begin{align}
+    \label{eq:linear:f}
+    \bvec{f}
+    &=
+    \Doppler
+    \,
+    \alm
+    \quad,
+\end{align}
+%
+where $\Doppler$ is the full $(MK \times N K')$ Doppler design matrix, 
+constructed by vertically concatenating the individual matrices $\Doppler_t$.
+This equation represents the full linearization of the problem, where we
+have expressed the quantity we can observe, $\bvec{f}$, as a linear
+operation on the quantity of interest, the spectral/spatial decomposition
+of the stellar surface, $\alm$. Figure~\ref{fig:linalg} shows an
 example of $\Doppler$.
+
+\section{The inverse problem}
+\label{sec:inverse}
+%
+In the previous section we showed how to express the data vector $\bvec{f}$,
+a series of spectra obtained at different epochs, as a purely linear
+operation on the map vector $\alm$, the spherical harmonic decomposition of
+the specific intensity on the surface of the star. The advantage of this
+linearity is that, given suitable priors, it allows one to compute both 
+the maximum likelihood solution for $\alm$ \emph{and} its uncertainty
+\emph{analytically}.
+
+Equation~(\ref{eq:deconv:Ivecfull})
+
+\subsection{Continuum normalization}
+
+\subsection{Limb darkening}
+
+\section{Other stuff}
+\subsection{Limb darkening}
+\subsection{Differential rotation and convective blueshift}
 
@@
         Time evolution of a Gaussian absorption line on a rigidly rotating, 
-        spotted star computed from the analytic formulae in \S\ref{sec:g}.
+        spotted star computed from the analytic formulae in \S\ref{sec:kT}.
         The stellar surface is modeled as a spherical harmonic expansion
@@
 
-\section{Integrals}
-\subsection{Equation~(\ref{eq:g:sTexpression})}
+\section{Solving the $\kT$ integral}
 %
-In this section we derive the recurrence relations
-(\ref{eq:g:sTrecurrence}) for computing $\s^\top$.
+In this section we will show how to compute the integral in
+Equation~(\ref{eq:kT:kT}), yielding the terms of the convolution
+kernel $\kT$. It is convenient to first change basis from spherical harmonics to 
+polynomials on the sphere:
+%
+\begin{align}
+    \label{eq:appendix:kT}
+    \kT(\lnlam, \Dargs) 
+    &=    
+    \int\limits_{-\sqrt{1 - x^2}}^
+                {\sqrt{1 - x^2}}
+    \pbasis
+    \Big(x, y\Big)
+    \mathrm{d}y
+    \,
+    \AOne
+    \nonumber \\[0.5em]
+    &\equiv
+    \sT(\lnlam, \Dargs) 
+    \,
+    \AOne
+    \quad,
+\end{align}
+%
+where $\AOne$ is the change of basis matrix from spherical harmonics
+to polynomials \citep[Equation B11 in][]{Luger2019} and
+%
+\begin{align}
+    \pbasis(\x) \equiv 
+\Big( 
+    1 \quad\quad\quad\quad\quad\quad 
+    x \quad\quad\quad\quad\quad\quad 
+    z \quad\quad\quad\quad\quad\quad 
+    y \quad\quad\quad\quad\quad\quad 
+    x^2 \quad\quad\quad\quad\quad\quad 
+    xz \quad\quad\quad\quad\quad\quad 
+    xy \quad\quad\quad\quad\quad\quad
+    yz \quad\quad\quad\quad\quad\quad 
+    y^2 \quad\quad\quad\quad\quad\quad
+    ... 
+\Big)^\top
+\quad,
+\end{align}
+%
+is the polynomial basis \citep[Equation 7][]{Luger2019}. 
+Specifically, the $n^\mathrm{th}$ term of the polynomial basis
+is a polynomial in $x$, $y$, and $z = \sqrt{1 - x^2 - y^2}$:
+%
+\begin{proof}{PolynomialBasis}
+    \pbasisn
+    &=
+    x^i y^j z^k
+\end{proof}
+%
+where $i, j, k$ are integers given by
+%
+\begin{proof}{PolynomialBasis}
+    \label{eq:kT:lm}
+    i &= \floor*{\Lambda - \Delta}
+    \nonumber \\[0.5em]
+    j &= \floor*{\Delta}
+    \nonumber \\[0.5em]
+    k &= \ceil*{\Delta} - \floor*{\Delta}
+\end{proof}
+%
+with
+%
+\begin{proof}{PolynomialBasis}
+    \Lambda &= \floor*{\sqrt{n}}
+    \nonumber \\[0.5em]
+    \Delta &= \frac{n - \Lambda^2}{2}
+    \quad .
+\end{proof}
+%
+We may now explicitly write down the $n^\mathrm{th}$ term of 
+the vector $\sT(\lnlam, \Dargs)$ in Equation~(\ref{eq:appendix:kT}),
+%
+\begin{align}
+    \label{eq:kT:sTexpression}
+    s_n(\lnlam, \Dargs) 
+    &=    
+    s_{i,\,j,\,k}(\lnlam, \Dargs) 
+    =    
+    x^i
+    \int\limits_{-\sqrt{1 - x^2}}^
+                {\sqrt{1 - x^2}}
+        y^j
+        \left(1 - x^2 - y^2\right)^{\frac{k}{2}} \,
+    \mathrm{d}y 
+    \quad .
+\end{align}
+%
 When $i = k = 0$, the integral is easy to evaluate:
@@
 \end{align}
+%
+This completes our derivation. To summarize, given the boundary conditions
+%
+\begin{align}
+    s_{0,\,0,\,0} &= 2 \sqrt{1-x^2} \nonumber \\
+    s_{0,\,0,\,1} &= \frac{\pi}{2} \big(1-x^2\big) \nonumber \\
+    s_{0,\,1,\,k} &= 0 \quad ,
+\end{align}
+%
+we may compute any term in $\sT$ via the expressions
+%
+\begin{align}
+    \label{eq:kT:sTrecurrence}
+    s_{0,\,j,\,k} &= \frac{j - 1}{j + 1 + k} \big(1 - x^2\big) s_{0,\,j-2,\,k} \nonumber \\
+    s_{i,\,j,\,k} &= x \, s_{i-1,\,j,\,k} \quad.
+\end{align}
+%
+The terms of the convolution kernel $\kT$ are then obtained by dotting
+this vector into the change of basis matrix $\AOne$, as discussed above.
 

### 2019-08-07 tex/figures/kT.py

@@ -13,7 +13,7 @@ import paparazzi as pp
 ydeg = 10
 dop = pp.Doppler(ydeg=ydeg)
 dop.generate_data(R=1e6, nlam=99, u=np.zeros(dop.N - 1))
-g = dop.gT()
+kT = dop.kT()
 
 # Set up the plot
 fig, ax = plt.subplots(
@@ -33,7 +33,7 @@ n = 0
 for i, l in enumerate(range(ydeg + 1)):
     for j, m in enumerate(range(-l, l + 1)):
         j += ydeg - l
-        ax[i, j].plot(g[n])
+        ax[i, j].plot(kT[n])
         n += 1
 
 # Labels
@@ -50,4 +50,4 @@ for i, l in enumerate(range(ydeg + 1)):
     )
 
 # Save
-fig.savefig("g.pdf", bbox_inches="tight")
+fig.savefig("kT.pdf", bbox_inches="tight")

### 2019-08-08 paparazzi/doppler.py
working on vogtstar

@@ -711,6 +711,7 @@ class Doppler(object):
         niter2=100,
         T1=1.0,
         T2=1.0,
+        lr=2e-3,
         optimizer="NAdam",
         dcf=10.0,
         quiet=False,
@@ -756,6 +757,7 @@ class Doppler(object):
         niter2 = np.atleast_1d(niter2)
         T1 = np.ones_like(niter1) * T1
         T2 = np.ones_like(niter2) * T2
+        lr = np.ones_like(niter2) * lr
 
         # Figure out what to solve for
         known = []
@@ -923,7 +925,7 @@ class Doppler(object):
                             )
 
                         loss_T = -(lnlike / T2[k] + lnprior)  # tempered loss
-                        upd = optimizer(loss_T, theano_vars, **kwargs)
+                        upd = optimizer(loss_T, theano_vars, lr=lr[k], **kwargs)
                         train = theano.function([], [u, vT, loss], updates=upd)
                         for n in tqdm(n0 + np.arange(niter), disable=quiet):
                             u_val, vT_val, loss_val[n] = train()

### 2019-08-08 tex/gitlinks.tex
added vogtstar fig

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/b9ff114beba2d54f032d05754e1d62ef624acd09/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/b9ff114beba2d54f032d05754e1d62ef624acd09/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/b9ff114beba2d54f032d05754e1d62ef624acd09/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/4e5cae5dc1b1284c9989d7eb27427acca7088476/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/4e5cae5dc1b1284c9989d7eb27427acca7088476/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/4e5cae5dc1b1284c9989d7eb27427acca7088476/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-08-08 paparazzi/doppler.py

@@ -257,6 +257,18 @@ class Doppler(object):
         self._vT_rho = value
         self._compute_gp()
 
+    @property
+    def u(self):
+        return self._u
+
+    @u.setter
+    def u(self, value):
+        self._u = value
+        if value is None:
+            self._map[1:, :] = 0.0
+        else:
+            self._map[1:, :] = self._u
+
     def _compute_gp(self):
         # Compute the GP prior on the spectrum
         if self._lnlam is None:
@@ -528,15 +540,21 @@ class Doppler(object):
         Show the image of the current map solution.
 
         """
-        self._map[1:, :] = self.u
         self._map.show(**kwargs)
+
+    def render(self, **kwargs):
+        """
+        Render the image of the current map solution.
+
+        """
+        func = theano.function([], self._map.render(**kwargs))
+        return func()
 
     def baseline(self):
         """
         Return the photometric baseline at each epoch.
 
         """
-        self._map[1:, :] = self.u
         return self._map.flux(theta=self.theta).eval().reshape(-1, 1)
 
     def model(self):
@@ -860,8 +878,10 @@ class Doppler(object):
                         ),
                         (-1,),
                     )
-                    self._map[1:, :] = u
-                    b = self._map.flux(theta=self.theta)
+                    b = tt.dot(
+                        self._map.X(theta=self.theta),
+                        tt.reshape(tt.concatenate([[1.0], u]), (-1, 1)),
+                    )
                     B = tt.reshape(b, (-1, 1))
                     M = tt.reshape(ts.dot(D, a), (self.M, -1)) / B
 

### 2019-08-08 tex/gitlinks.tex
misc

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/4e5cae5dc1b1284c9989d7eb27427acca7088476/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/4e5cae5dc1b1284c9989d7eb27427acca7088476/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/4e5cae5dc1b1284c9989d7eb27427acca7088476/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/689c6f0d93a04bf4a19694742579915b3bfc57f2/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/689c6f0d93a04bf4a19694742579915b3bfc57f2/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/689c6f0d93a04bf4a19694742579915b3bfc57f2/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-08-08 tex/gitlinks.tex
working on the paper figs

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/689c6f0d93a04bf4a19694742579915b3bfc57f2/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/689c6f0d93a04bf4a19694742579915b3bfc57f2/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/689c6f0d93a04bf4a19694742579915b3bfc57f2/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/60dfb1cf40302ddb3818411b0925c910a2f52625/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/60dfb1cf40302ddb3818411b0925c910a2f52625/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/60dfb1cf40302ddb3818411b0925c910a2f52625/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-08-08 tex/ms.tex
working on vogtstar
added vogtstar fig
misc
working on the paper figs

@@
 \newcommand{\lmax}{\ensuremath{l_\mathrm{max}}}
+\newcommand{\vogtstar}{\texttt{VOGTSTAR}\xspace}
 
@@
 
+\section{The VOGTSTAR}
+\label{sec:vogtstar}
+
+\begin{figure}[p!]
+    \begin{centering}
+    \includegraphics[width=0.49\linewidth]{figures/learn_map_high_snr_timeseries.pdf}
+    \includegraphics[width=0.49\linewidth]{figures/learn_map_high_snr_rect.pdf}
+    \oscaption{vogtstar}{%
+        Solution to the \vogtstar problem at high SNR when both the rest frame spectrum
+        and the baseline are known.
+        \label{fig:vogtstar_learn_map_high_snr}
+    }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[h!]
+    \begin{centering}
+    \includegraphics[width=0.95\linewidth]{figures/inclinations.pdf}
+    \oscaption{inclinations}{%
+        Recovered \vogtstar map as a function of inclination.
+        \label{fig:inclinations}
+    }
+    \end{centering}
+\end{figure}
+
 \section{Performance}
@@
 is the polynomial basis \citep[Equation 7][]{Luger2019}. 
-Specifically, the $n^\mathrm{th}$ term of the polynomial basis
+The $n^\mathrm{th}$ term of the polynomial basis
 is a polynomial in $x$, $y$, and $z = \sqrt{1 - x^2 - y^2}$:

### 2019-08-09 tex/ms.tex
woot; all vogtstar runs good

--- 2019-08-07 tex/ms.tex
@@
 
+\section{The VOGTSTAR}
+\label{sec:vogtstar}
+
+\begin{figure}[p!]
+    \begin{centering}
+    \includegraphics[width=0.49\linewidth]{figures/vogtstar_u_timeseries.pdf}
+    \includegraphics[width=0.49\linewidth]{figures/vogtstar_u_rect.pdf}
+    \oscaption{vogtstar_u}{%
+        Solution to the \vogtstar problem at high SNR when both 
+        the rest frame spectrum and the baseline are known.
+        \label{fig:vogtstar_u}
+    }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[p!]
+    \begin{centering}
+    \includegraphics[width=0.49\linewidth]{figures/vogtstar_ub_timeseries.pdf}
+    \includegraphics[width=0.49\linewidth]{figures/vogtstar_ub_rect.pdf}
+    \\[0.5em]
+    \includegraphics[width=0.405\linewidth]{figures/vogtstar_ub_baseline.pdf}
+    \includegraphics[width=0.575\linewidth]{figures/vogtstar_ub_coeffs.pdf}
+    \oscaption{vogtstar_ub}{%
+        Similar to Figure~\ref{fig:vogtstar_u}, but assuming the baseline
+        is not known.
+        \label{fig:vogtstar_ub}
+    }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[p!]
+    \begin{centering}
+    \includegraphics[width=0.49\linewidth]{figures/vogtstar_ubvT_timeseries.pdf}
+    \includegraphics[width=0.49\linewidth]{figures/vogtstar_ubvT_rect.pdf}
+    \\[0.5em]
+    \includegraphics[width=0.405\linewidth]{figures/vogtstar_ubvT_baseline.pdf}
+    \includegraphics[width=0.575\linewidth]{figures/vogtstar_ubvT_coeffs.pdf}
+    \\[0.5em]
+    \includegraphics[width=0.98\linewidth]{figures/vogtstar_ubvT_spectrum.pdf}
+    \oscaption{vogtstar_ubvT}{%
+        Similar to Figure~\ref{fig:vogtstar_u}, but assuming we have no
+        information about either the spectrum, the baseline, or the map
+        coefficients.
+        \label{fig:vogtstar_ubvT}
+    }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[h!]
+    \begin{centering}
+    \includegraphics[width=0.98\linewidth]{figures/inclinations.pdf}
+    \oscaption{inclinations}{%
+        Recovered \vogtstar map as a function of inclination.
+        \label{fig:inclinations}
+    }
+    \end{centering}
+\end{figure}
+
 \section{Performance}

### 2019-08-09 tex/figures/utils/vogtstar_plot.py

@@ -7,7 +7,7 @@ import subprocess
 from scipy.linalg import cho_solve
 import theano.sparse as ts
 
-np.random.seed(13)
+__all__ = ["plot_results"]
 
 
 def plot_results(
@@ -31,6 +31,7 @@ def plot_results(
     theta = doppler.theta
     u_true = doppler.u_true
     vT_true = doppler.vT_true
+    vT_deconv = doppler.vT_deconv
     baseline_true = doppler.baseline_true
     u = np.array(doppler.u)
     vT = np.array(doppler.vT)
@@ -61,14 +62,14 @@ def plot_results(
         baseline_sig = np.sqrt(np.sum(A ** 2, axis=0))
         baseline_sig_ = np.append(baseline_sig, [baseline_sig[0]])
         ax.fill_between(
-            theta,
-            baseline - baseline_sig,
-            baseline + baseline_sig,
+            theta_,
+            baseline_ - baseline_sig_,
+            baseline_ + baseline_sig_,
             color="C1",
             alpha=0.25,
             lw=0,
         )
-    ax.legend(loc="lower left")
+    ax.legend(loc="lower left", fontsize=14)
     ax.set_xlabel(r"$\theta$ (degrees)")
     ax.margins(0, None)
     ax.set_xticks([-180, -135, -90, -45, 0, 45, 90, 135, 180])
@@ -84,6 +85,10 @@ def plot_results(
         doppler.u = u_true
         doppler.vT = vT_true
         loss_true = doppler.loss()
+
+        # Print for the record
+        print("True loss: %.2f" % loss_true)
+        print("Best loss: %.2f" % np.min(loss))
 
         # Plot
         fig, ax = plt.subplots(1, figsize=(12, 5))
@@ -111,7 +116,7 @@ def plot_results(
         ax.fill_between(n, u - sig_u, u + sig_u, color="C1", alpha=0.5)
     ax.set_ylabel("spherical harmonic coefficient")
     ax.set_xlabel("coefficient number")
-    ax.legend(loc="upper right")
+    ax.legend(loc="lower right", fontsize=14)
     ax.margins(0.01, None)
     fig.savefig("%s_coeffs.pdf" % name, bbox_inches="tight")
     files.append("coeffs.pdf")
@@ -333,6 +338,15 @@ def plot_results(
     # Plot the rest frame spectrum
     fig, ax = plt.subplots(1)
     ax.plot(lnlam_padded, vT_true.reshape(-1), "C0-", label="true")
+    if vT_deconv is not None:
[…]

### 2019-08-09 tex/figures/vogtstar_ubvT.py

@@ -1,0 +1,53 @@
+# -*- coding: utf-8 -*-
+"""
+Solve the VOGTSTAR problem.
+
+In this case, we know nothing: we're going to learn
+both the map and the spectrum. We're not giving the
+algorithm an initial guess, either: the spectrum is
+learned by deconvolving the data, and the initial
+guess for the map is computed via the linearized
+problem.
+
+"""
+import paparazzi as pp
+import numpy as np
+from utils.vogtstar_plot import plot_results
+
+np.random.seed(13)
+
+# Let's plot the high SNR case for the paper
+high_snr = True
+
+# High or low SNR?
+if high_snr:
+    # We rely heavily on tempering here. Once we get
+    # a good initial guess via the bilinear solver,
+    # we run the non-linear solver with a slow learning
+    # rate.
+    ferr = 1e-4
+    T = 5000.0
+    niter = 3000
+    lr = 1.5e-4
+else:
+    # This case is easier; just a little tempering for
+    # good measure, followed by a fast non-linear
+    # refinement.
+    ferr = 1e-3
+    T = 10.0
+    niter = 250
+    lr = 2e-3
+
+# Generate data
+dop = pp.Doppler(ydeg=15)
+dop.generate_data(ferr=ferr)
+
+# Reset all coefficients
+dop.u = None
+dop.vT = None
+
+# Solve!
+loss, cho_u, cho_vT = dop.solve(niter=niter, lr=lr, T=T)
+
+# Plot the results
+plot_results(dop, name="vogtstar_ubvT", loss=loss, cho_u=cho_u, cho_vT=cho_vT)

### 2019-08-12 tex/ms.tex
reorg

@@
 
-\newcommand{\sT}{\bvec{s}^\top}
 \newcommand{\R}{\bvec{R}}
@@
 \newcommand{\x}{\bvec{x}}
-\newcommand{\kT}{\bvec{k}^\top}
-\newcommand{\D}{\mathcal{D}}
+
+\newcommand{\D}{D}
 \newcommand{\Doppler}{\bvec{D}}
@@
 
-% TODO: Use blackboard bold (bbm)
+\newcommand{\kT}{\boldsymbol{\kappa}^\top}
+\newcommand{\rhoT}{\boldsymbol{\rho}^\top}
 \newcommand{\ylmbasis}{\boldsymbol{\psi}^\top}
@@
 Check out \citet{Luger2019} and \citet{Bedell2019} and stuff.
+
+%
+\begin{center}
+    \begin{longtable}{cll}
+    \caption{Notation used in this paper} 
+    \label{tab:notation} \\
+    %
+    \toprule
+    \multicolumn{1}{c}{\textbf{Symbol}} &
+    \multicolumn{1}{c}{\textbf{Description}} &
+    \multicolumn{1}{c}{\textbf{Type}} \\
+    \toprule
+    \endhead
+    %
+    \endfoot
+    %
+    \endlastfoot
+    %
+    $a$                             & lowercase italic & scalar\\
+    $A$                             & uppercase italic & scalar\\
+    $\alpha$                        & lowercase italic Greek & scalar\\
+    $\bvec{a}$                      & lowercase boldface & column vector\\
+    $\bvec{A}$                      & uppercase boldface & matrix\\
+    $\boldsymbol{\alpha}^\top$      & lowercase boldface Greek & basis row vector
+\end{longtable}
+\end{center}
 
@@
 observed spectrum into velocity terms, temporal terms, and spectral/spatial
-terms, respectively. In the following sections, we will discuss how to
+terms, respectively. In the next section, we will discuss how to
 efficiently solve the line integral in Equation~(\ref{eq:deconv:kT}).
@@
 the maximum likelihood solution for $\alm$ \emph{and} its uncertainty
-\emph{analytically}.
+\emph{analytically}. In particular, if one places a (multidimensional)
+Gaussian prior on $\alm$ with mean $\boldsymbol{\mu}$ and 
+covariance $\boldsymbol{\Lambda}$, the maximum \emph{a posteriori} (MAP) 
+solution for $\alm$ is
+%
+\begin{align}
+    \bvec{\hat{a}} &= 
+    \boldsymbol{\Sigma}_\mathbf{\hat{a}}
+    \left(
+        \Doppler^\top
+        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
+        \bvec{f}
+        +
+        \boldsymbol{\Lambda}^{-1} \boldsymbol{\mu}
+    \right)
+    \quad,
+\end{align}
+%
+with posterior covariance given by
+%
+\begin{align}
+    \boldsymbol{\Sigma}_\mathbf{\hat{a}} &= 
+    \left(
+        \Doppler^\top
+        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
+        \Doppler
+        +
+        \boldsymbol{\Lambda}^{-1}
+    \right)^{-1}
+    \quad,
+\end{align}
+%
+where $\boldsymbol{\Sigma}_\mathbf{f}$ is the data covariance
+matrix. These equations require the inversion of a few fairly
+large matrices, but as we will see later, it allows one to obtain
+the map of the star ($\bvec{\hat{a}}$) and its uncertainty
+($\boldsymbol{\Sigma}_\mathbf{\hat{a}}$) in under a second for
+a typical dataset.
+
+There is, however, a catch: for most practical purposes, it is 
+difficult to find a good Gaussian prior for $\alm$. Usually
+we will have some prior information on what the spectrum of the
+star is, and perhaps some prior information on the distribution
+of surface features such as starspots. The problem is that
+even if these priors are Gaussian, the corresponding prior
+on $\alm$ is \emph{not}. To understand this, consider the
+matrix $\bvec{A}$, constructed by reshaping $\alm$ into
+a matrix of shape $(N \times K')$, whose rows correspond
+to the spectral components associated with each spherical harmonic coefficient.
+By performing singular value decomposition (SVD) on this matrix, we may
+write
+%
+\begin{align}
+    \bvec{A} = \bvec{U} \, \bvec{S} \, \bvec{V}^\top
+\end{align}
+%
+where $\bvec{U}$ is a matrix of shape $(N \times P)$, $\bvec{V}^\top$ is a 
+matrix of shape $(P \times K')$, and $\bvec{S}$ is a diagonal matrix of 
+shape $(P \times P)$ for some integer $P$.
 
@@
     &\equiv
-    \sT(\lnlam, \Dargs) 
+    \rhoT(\lnlam, \Dargs) 
     \,
@@
 We may now explicitly write down the $n^\mathrm{th}$ term of 
-the vector $\sT(\lnlam, \Dargs)$ in Equation~(\ref{eq:appendix:kT}),
+the vector $\rhoT(\lnlam, \Dargs)$ in Equation~(\ref{eq:appendix:kT}),
 %
@@
     \label{eq:kT:sTexpression}
-    s_n(\lnlam, \Dargs) 
+    \rho_n(\lnlam, \Dargs) 
     &=    
-    s_{i,\,j,\,k}(\lnlam, \Dargs) 
+    \rho_{i,\,j,\,k}(\lnlam, \Dargs) 
     =    
@@
 \begin{align}
-    s_{i,\,j,\,0}(\lnlam_0) 
+    \rho_{i,\,j,\,0}(\lnlam_0) 
     &=    
@@
 \begin{align}
-    s_{0,\,j,\,0}(\lnlam_0) = \frac{j - 1}{j + 1} \big(1 - x^2\big) s_{0,\,j-2,\,0}
+    \rho_{0,\,j,\,0}(\lnlam_0) = \frac{j - 1}{j + 1} \big(1 - x^2\big) \rho_{0,\,j-2,\,0}
 \end{align}
@@
 \begin{align}
-    s_{0,\,0,\,0} &= 2 \sqrt{1-x^2} \nonumber \\
-    s_{0,\,1,\,0} &= 0 \quad.
+    \rho_{0,\,0,\,0} &= 2 \sqrt{1-x^2} \nonumber \\
+    \rho_{0,\,1,\,0} &= 0 \quad.
 \end{align}
@@
 \begin{align}
-    s_{0,\,j,\,1}(\lnlam_0)
+    \rho_{0,\,j,\,1}(\lnlam_0)
     &=
@@
 \begin{align}
-    s_{0,\,j,\,1} &= \frac{j - 1}{j + 2} \big(1 - x^2\big) s_{0,\,j-2,\,1}
+    \rho_{0,\,j,\,1} &= \frac{j - 1}{j + 2} \big(1 - x^2\big) \rho_{0,\,j-2,\,1}
 \end{align}
@@
 \begin{align}
-    s_{0,\,0,\,1} &= \frac{\pi}{2} \big(1-x^2\big) \nonumber \\
-    s_{0,\,1,\,1} &= 0 \quad.
+    \rho_{0,\,0,\,1} &= \frac{\pi}{2} \big(1-x^2\big) \nonumber \\
+    \rho_{0,\,1,\,1} &= 0 \quad.
 \end{align}
@@
 \begin{align}
-    s_{i,\,j,\,k} &= x \, s_{i-1,\,j,\,k} \quad.
+    \rho_{i,\,j,\,k} &= x \, \rho_{i-1,\,j,\,k} \quad.
 \end{align}
@@
 \begin{align}
-    s_{0,\,0,\,0} &= 2 \sqrt{1-x^2} \nonumber \\
-    s_{0,\,0,\,1} &= \frac{\pi}{2} \big(1-x^2\big) \nonumber \\
-    s_{0,\,1,\,k} &= 0 \quad ,
+    \rho_{0,\,0,\,0} &= 2 \sqrt{1-x^2} \nonumber \\
+    \rho_{0,\,0,\,1} &= \frac{\pi}{2} \big(1-x^2\big) \nonumber \\
+    \rho_{0,\,1,\,k} &= 0 \quad ,
 \end{align}
 %
-we may compute any term in $\sT$ via the expressions
+we may compute any term in $\rhoT$ via the expressions
 %
@@
     \label{eq:kT:sTrecurrence}
-    s_{0,\,j,\,k} &= \frac{j - 1}{j + 1 + k} \big(1 - x^2\big) s_{0,\,j-2,\,k} \nonumber \\
-    s_{i,\,j,\,k} &= x \, s_{i-1,\,j,\,k} \quad.
+    \rho_{0,\,j,\,k} &= \frac{j - 1}{j + 1 + k} \big(1 - x^2\big) \rho_{0,\,j-2,\,k} \nonumber \\
+    \rho_{i,\,j,\,k} &= x \, \rho_{i-1,\,j,\,k} \quad.
 \end{align}

### 2019-08-12 tex/ms.tex
so much text

@@
 \newcommand{\pbasisn}{\ensuremath{\phi_n}}
+
+\newcommand{\azero}{\ensuremath{\bvec{a_0}}}
 
@@
     \label{eq:deconv:R}
-    \alm(\lnlam_0, t) = \R(t) \alm(\lnlam_0)
+    \alm(\lnlam_0, t) = \R(t) \, \azero(\lnlam_0)
     \quad ,
@@
 %
-where $\alm(\lnlam_0) = \alm(\lnlam_0, t=t_0)$ for some reference time $t_0$.
+where $\azero(\lnlam_0) = \bvec{a}(\lnlam_0, t=t_0)$ 
+for some reference time $t_0$.
 For rigid body rotation, the result is exact and $\R(t)$ is the Wigner 
@@
 function of the inclination, obliquity, and rotation period of the star.
-In the case that other processes such as differential rotation or spot 
-evolution are significant
-over the course of an observation, Equation~(\ref{eq:deconv:R}) can be
-made to hold approximately for some effective rotation matrix 
-$\R(t)$; we discuss this later.
+%In the case that other processes such as differential rotation or spot 
+%evolution are significant
+%over the course of an observation, Equation~(\ref{eq:deconv:R}) can be
+%made to hold approximately for some effective rotation matrix 
+%$\R(t)$; we discuss this later.
 
@@
     \,
-    \alm(\lnlam_0)
+    \azero(\lnlam_0)
     \quad ,
@@
     *
-    \alm(\lnlam_0)
+    \azero(\lnlam_0)
     \quad.
@@
 This completes our derivation of the analytic expression for the
-observed spectrum (Equation~\ref{eq:deconv:F}). As we show later,
-this equation allows us to compute the forward model for the
-spectrum very efficiently, particularly if we make use of Fast-Fourier
-Transform (FFT) -based convolution techniques. However, a convolution
-can also be represented as a matrix dot product, which we can use to
-express the model for the observed spectrum as a purely linear
-operation on the map decomposition $\alm(\lnlam_0)$. In the following section
-we derive this expression and show how it can be used to obtain
-fast, analytic solutions to the Doppler problem.
-
-\subsection{Linearization}
+observed spectrum (Equation~\ref{eq:deconv:F}).
+
+\subsection{Example}
+%
+Figure~\ref{fig:spot} shows an example application of the formulae derived 
+in this section. We used \starry to generate a synthetic stellar surface with a 
+single large Gaussian spot at a latitude of $30^\circ$, yielding a vector of
+spherical harmonic coefficients $\bvec{y}$.
+The stellar rest frame spectrum $I(\lnlam_0)$ is taken to be a single Gaussian 
+absorption line that is spatially constant 
+everywhere save for a multiplicative factor equal to the local spot intensity.
+This corresponds to a spectral/spatial expansion vector $\azero(\lnlam_0)$ 
+whose coefficient at degree $l$ and order $m$ is equal to $y_{lm} I(\lnlam_0)$.
+In the Figure, we rotated the star about an axis perpendicular to the line
+of sight (left panel) and computed the observed spectrum using 
+Equation~(\ref{eq:deconv:F}) (center panel). The right panel shows the difference
+between the observed spectrum and the spectrum when the spot is not in view.
+The effect of the spot on the absorption line is evident: a ``bump'' that
+travels from the blueshifted side of to the redshifted side of the line
+in sync with the change in longitude of the spot. This correspondence between
+line shape residuals and spot location is the cornerstone of the Doppler
+imaging technique \citep[compare to, e.g., Figures 1 and 4 in][]{Vogt1983}.
+
+\begin{figure}[p!]
+    \begin{centering}
+    \includegraphics[width=0.6\linewidth]{figures/spot.pdf}
+    \oscaption{spot}{%
+        Time evolution of a Gaussian absorption line on a rigidly rotating, 
+        spotted star computed from the analytic formulae in \S\ref{sec:kT}.
+        The stellar surface is modeled as a spherical harmonic expansion
+        up to $l=20$, and the line shape is assumed to be the same everywhere;
+        the spot simply downweights the local intensity at all wavelengths.
+        As the spot rotates into view (left panel), the line shape changes
+        slightly (center panel). The residuals between the line when the
+        spot is in view (solid) and when it is on the backside of the star
+        (dotted) are shown in the right panel, where
+        a Gaussian-like feature can be seen tracking the spot as it rotates
+        from the blueshifted hemisphere to the redshifted hemisphere of
+        the star.
+        \label{fig:spot}
+    }
+    \end{centering}
+\end{figure}
+
+Figure~\ref{fig:compare} shows one of the spectra in Figure~\ref{fig:spot},
+this time computed using both our formulae (blue line) and the traditional
+technique of discretizing the stellar surface, Doppler-shifting the spectrum
+in each grid cell according to the local radial velocity, interpolating back
+to a uniform wavelength grid, and summing over the spatial dimension
+(dotted orange line). We show the residuals in the lower panel, where it
+is clear that as the number of grid cells increases from 2,000 (light grey)
+to 71,000 (dark grey), the numerical solution approaches the solution
+obtained using our approach. \xxx{Understand---and comment on---the fundamental
+differences between a discrete linear convolution and traditional linear 
+interpolation. Should we expect the numerical solution to actually \emph{converge}
+to the \starry solution, or is the way the two are interpolating fundamentally
+different?}
+
+\begin{figure}[t!]
+    \begin{centering}
+    \includegraphics[width=0.65\linewidth]{figures/compare.pdf}
+    \oscaption{compare}{%
+        The observed spectrum when the spot is in view computed with
+        \starry (blue) and numerically (orange). The problem setup
+        is the same as that in Figure~\ref{fig:spot}. The bottom
+        panel shows the absolute value of the difference between the 
+        two spectra for different number of grid points in the 
+        numerical solution.
+        As the number of grid points increases, the numerical solution
+        approaches the \starry solution.
+        \label{fig:compare}
+    }
+    \end{centering}
+\end{figure}
+
+\section{Linearization}
 \label{sec:linear}
@@
 Given this formulation, we may re-write Equation~(\ref{eq:deconv:F}) as a
-purely linear operation on $\alm(\lnlam_0)$:
+purely linear operation on $\azero(\lnlam_0)$:
 %
@@
     \,
-    \alm
+    \azero
     \quad,
@@
 the flux observed at each wavelength at a particular time, and the 
-$(N K' \times 1)$ vector $\alm$ is the vector representation of the
+$(N K' \times 1)$ vector $\azero$ is the vector representation of the
 spatially-dependent spectrum of the star. The latter is constructed
 by flattening the spherical harmonic expansion of the star
-such that the first $K'$ terms in $\alm$ correspond
-to the the values of $a_{0,0}$ at each wavelength $\lnlam_0$,
-followed by the values of $a_{0,0}$ at each wavelength, and so forth.
+such that the first $K'$ terms in $\azero$ correspond
+to the the values of $(a_0)_{0,0}$ at each wavelength $\lnlam_0$,
+followed by the values of $(a_0)_{1,-1}$ at each wavelength, and so forth.
 
@@
 operation on the quantity of interest, the spectral/spatial decomposition
-of the stellar surface, $\alm$. Figure~\ref{fig:linalg} shows an
+of the stellar surface, $\azero$. Figure~\ref{fig:linalg} shows an
 example of $\Doppler$.
@@
 a series of spectra obtained at different epochs, as a purely linear
-operation on the map vector $\alm$, the spherical harmonic decomposition of
+operation on the map vector $\azero$, the spherical harmonic decomposition of
 the specific intensity on the surface of the star. The advantage of this
 linearity is that, given suitable priors, it allows one to compute both 
-the maximum likelihood solution for $\alm$ \emph{and} its uncertainty
+the maximum likelihood solution for $\azero$ and its uncertainty
 \emph{analytically}. In particular, if one places a (multidimensional)
-Gaussian prior on $\alm$ with mean $\boldsymbol{\mu}$ and 
-covariance $\boldsymbol{\Lambda}$, the maximum \emph{a posteriori} (MAP) 
-solution for $\alm$ is
-%
-\begin{align}
-    \bvec{\hat{a}} &= 
-    \boldsymbol{\Sigma}_\mathbf{\hat{a}}
+Gaussian prior on $\azero$ with mean $\boldsymbol{\mu}_\mathbf{a_0}$ and 
+covariance $\boldsymbol{\Lambda}_\mathbf{a_0}$, the maximum \emph{a posteriori} (MAP) 
+solution for $\azero$ is
+%
+\begin{align}
+    \label{eq:inverse:ahat}
+    \bvec{\hat{a}_0} &= 
+    \boldsymbol{\Sigma}_\mathbf{\hat{a}_0}
     \left(
@@
         +
-        \boldsymbol{\Lambda}^{-1} \boldsymbol{\mu}
+        {\boldsymbol{\Lambda}_{\azero}}^{-1} \boldsymbol{\mu}_\mathbf{a_0}
     \right)
@@
 \begin{align}
-    \boldsymbol{\Sigma}_\mathbf{\hat{a}} &= 
+    \label{eq:inverse:acov}
+    \boldsymbol{\Sigma}_\mathbf{\hat{a}_0} &= 
     \left(
@@
         +
-        \boldsymbol{\Lambda}^{-1}
+        {\boldsymbol{\Lambda}_{\azero}}^{-1}
     \right)^{-1}
@@
 large matrices, but as we will see later, it allows one to obtain
-the map of the star ($\bvec{\hat{a}}$) and its uncertainty
-($\boldsymbol{\Sigma}_\mathbf{\hat{a}}$) in under a second for
+the map of the star ($\bvec{\hat{a}_0}$) and its uncertainty
+($\boldsymbol{\Sigma}_{\mathbf{\hat{a}_0}}$) in under a second for
 a typical dataset.
@@
 There is, however, a catch: for most practical purposes, it is 
-difficult to find a good Gaussian prior for $\alm$. Usually
+difficult to find a good Gaussian prior for $\bvec{a_0}$. Usually
 we will have some prior information on what the spectrum of the
@@
 even if these priors are Gaussian, the corresponding prior
-on $\alm$ is \emph{not}. To understand this, consider the
-matrix $\bvec{A}$, constructed by reshaping $\alm$ into
-a matrix of shape $(N \times K')$, whose rows correspond
-to the spectral components associated with each spherical harmonic coefficient.
-By performing singular value decomposition (SVD) on this matrix, we may
-write
-%
-\begin{align}
-    \bvec{A} = \bvec{U} \, \bvec{S} \, \bvec{V}^\top
-\end{align}
-%
-where $\bvec{U}$ is a matrix of shape $(N \times P)$, $\bvec{V}^\top$ is a 
-matrix of shape $(P \times K')$, and $\bvec{S}$ is a diagonal matrix of 
-shape $(P \times P)$ for some integer $P$.
-
-Equation~(\ref{eq:deconv:Ivecfull})
-
-\subsection{Continuum normalization}
-
-\subsection{Limb darkening}
+on $\bvec{a_0}$ is \emph{not}. To understand this, consider the
+case where the stellar rest frame spectrum is spatially constant,
+save for an amplitude that is spatially variable. We can then
+describe the rest frame spectrum by the $(K' \times 1)$ vector
+$\bvec{s}$ and the amplitude by the $(N \times 1)$ vector 
+$\bvec{y}$ representing the spherical harmonic expansion of the
+intensity profile of the star. The vector $\azero$ is then
+given by the (flattened) outer product of the two vectors:
+%
+\begin{align}
+    \azero &= \mathrm{vec}\left( \bvec{A_0} \right) \nonumber \\
+         &= \mathrm{vec}\left( \bvec{s} \, \bvec{y}^\top \right) \quad,
+\end{align}
+%
+where $\mathrm{vec}$ denotes the vectorization operation, which in this case
+transforms the $(K' \times N)$ matrix $\bvec{A_0}$ into the $(N K' \times 1)$
+column vector $\azero$ by vertically stacking all of its columns. In other
+words, the vector $\azero$ consists of the set of $K'$ intensities in
+each wavelength bin repeated $N$ times, each time multiplied by the 
+$n^\mathrm{th}$ spherical harmonic coefficient in the expansion of the 
+surface intensity. Returning to our point about priors, note that all of the
+entries of $\azero$ are the product of two independent random variables. Since
+the product of two random variables is generally non-Gaussian, even
+when the variables themselves are Gaussian%
+\footnote{see, e.g., \url{http://mathworld.wolfram.com/NormalProductDistribution.html}}%
+, so too is the prior on $\azero$. This point makes
+Equation~(\ref{eq:inverse:ahat}) of little practical use, since a 
+multivariate Gaussian will not 
+generally be a suitable prior for $\azero$.
+
+That said, a Gaussian prior \emph{is} typically suitable for both the spectrum
+$\bvec{s}$ and the intensity $\bvec{y}$ (just not their product). It is
+straightforward to show that because Equation~(\ref{eq:linear:f}) is linear
+in $\azero$, it is also linear in both $\bvec{s}$ and $\bvec{y}$, so
+MAP solutions can be found analytically for $\bvec{s}$ 
+(conditioned on $\bvec{y}$) and $\bvec{y}$ (conditioned on $\bvec{s}$). We
+investigate these solutions below.
+
+\subsection{Solution for the intensity}
+For a fixed, spatially constant rest-frame spectrum $\bvec{s}$, the model
+for the flux vector may be written as
+%
+\begin{align}
+    \label{eq:inverse:fy}
+    \bvec{f}
+    &=
+    \Doppler
+    \,
+    \bvec{S}
+    \,
+    \bvec{y}
+    \quad,
+\end{align}
+%
+where
+%
+\begin{align}
+    \setstackgap{L}{1.25\baselineskip}
+    \bvec{S} =
+        \begin{pmatrix}
+        \quadquad\bvec{s}\quadquad & &            &            &  \\
+        & \quadquad\bvec{s}\quadquad &            &            &  \\
+        &            & \quadquad\bvec{s}\quadquad &            &  \\
+        &            &            & \quadquad\bvec{s}\quadquad &  \\
+        &            &            &               & \ddots
+        \end{pmatrix}
+\end{align}
+%
+is a $(NK' \times N)$ block matrix constructed by repeating the column
+vector $\bvec{s}$ $N$ times in blocks along the main diagonal. Given
+prior mean $\boldsymbol{\mu}_\mathbf{y}$ and covariance
+$\boldsymbol{\Lambda}_\mathbf{y}$ on $\mathbf{y}$, the MAP solution
+is given by
+%
+\begin{align}
+    \label{eq:inverse:yhat}
+    \bvec{\hat{y}} &= 
+    \boldsymbol{\Sigma}_\mathbf{\hat{y}}
+    \left(
+        \bvec{S}^\top\Doppler^\top
+        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
+        \bvec{f}
+        +
+        {\boldsymbol{\Lambda}_\mathbf{y}}^{-1} \boldsymbol{\mu}_\mathbf{y}
+    \right)
+    \quad,
+\end{align}
+%
+with covariance
+%
+\begin{align}
+    \label{eq:inverse:ycov}
+    \boldsymbol{\Sigma}_\mathbf{\hat{y}} &= 
+    \left(
+        \bvec{S}^\top\Doppler^\top
+        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
+        \Doppler\bvec{S}
+        +
+        {\boldsymbol{\Lambda}_\mathbf{y}}^{-1}
+    \right)^{-1}
+    \quad.
+\end{align}
+%
+If we choose a prior with zero mean ($\boldsymbol{\mu}_\bvec{y} = 0$)
+and a diagonal covariance that is constant for each spherical harmonic 
+order $m$,
+%
+\begin{align}
+    \boldsymbol{\Lambda}_\bvec{y} &=
+    \mathrm{diag} \left(
+        \sigma_0^2
+        \quad\quad\quad\quad
+        \sigma_1^2
+        \quad\quad\quad\quad
+        \sigma_1^2
+        \quad\quad\quad\quad
+        \sigma_1^2
+        \quad\quad\quad\quad
+        \sigma_2^2
+        \quad\quad\quad\quad
+        \sigma_2^2
+        \quad\quad\quad\quad
+        \sigma_2^2
+        \quad\quad\quad\quad
+        \sigma_2^2
+        \quad\quad\quad\quad
+        \sigma_2^2
+        \quad\quad\quad\quad
+        \cdots
+    \right)
+    \quad,
+\end{align}
+%
+we are in fact imposing an isotropic prior with an angular power spectrum
+given by $C_l = \sigma_l^2$
+\citep[e.g.,][]{Baldi2006}. This is especially useful if the typical
+angular scale of features on the surface of the star is known or if
+a Gaussian prior can be placed on it.
+
+\subsection{Solution for the spectrum}
+If, on the other hand, the spatial intensity profile is known, the
+model for the flux vector may be written in terms of the spectrum $\bvec{s}$
+as
+%
+\begin{align}
+    \label{eq:inverse:fs}
+    \bvec{f}
+    &=
+    \Doppler
+    \,
+    \bvec{Y}
+    \,
+    \bvec{s}
+    \quad,
+\end{align}
+%
+where
+%
+\begin{align}
+    \setstackgap{L}{1.25\baselineskip}
+    \bvec{Y} =
+        \begin{pmatrix}
+            y_0\, \bvec{I}_{K'} \\
+            y_1\, \bvec{I}_{K'} \\
+            y_2\, \bvec{I}_{K'} \\
+            y_3\, \bvec{I}_{K'} \\
+            \cdots
+        \end{pmatrix}
+\end{align}
+%
+is a $(NK' \times K')$ matrix constructed by vertically stacking
+$N$ $(K' \times K')$ identity matrices, each multiplied by the
+corresponding coefficient of $\bvec{y}$. Given
+prior mean $\boldsymbol{\mu}_\mathbf{s}$ and covariance
+$\boldsymbol{\Lambda}_\mathbf{s}$ on $\mathbf{s}$, the MAP solution
+is given by
+%
+\begin{align}
+    \label{eq:inverse:shat}
+    \bvec{\hat{s}} &= 
+    \boldsymbol{\Sigma}_\mathbf{\hat{s}}
+    \left(
+        \bvec{Y}^\top\Doppler^\top
+        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
+        \bvec{f}
+        +
+        {\boldsymbol{\Lambda}_\mathbf{s}}^{-1} \boldsymbol{\mu}_\mathbf{s}
+    \right)
+    \quad,
+\end{align}
+%
+with covariance
+%
+\begin{align}
+    \label{eq:inverse:scov}
+    \boldsymbol{\Sigma}_\mathbf{\hat{s}} &= 
+    \left(
+        \bvec{Y}^\top\Doppler^\top
+        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
+        \Doppler\bvec{Y}
+        +
+        {\boldsymbol{\Lambda}_\mathbf{s}}^{-1}
+    \right)^{-1}
+    \quad.
+\end{align}
+
+\subsection{The full solution}
+In the previous two sections we showed how, if the stellar
+rest-frame spectrum is spatially constant and known \emph{a priori} 
+(from, say, a template spectrum), the posterior distribution
+for the surface map $\bvec{y}$ is \emph{analytic} 
+(Equations~\ref{eq:inverse:yhat}
+and \ref{eq:inverse:ycov}). Conversely, if the surface map is known,
+the posterior for the spectrum is also analytic 
+(Equations~\ref{eq:inverse:shat} and \ref{eq:inverse:scov}). Both sets of
+solutions require Gaussian priors on the quantities of interest, but these
+are easily interpretable. A Gaussian prior on
+the spherical harmonic coefficients of the surface map corresponds 
+to the angular power spectrum of the surface features, whereas a Gaussian
+prior on the spectrum can be used to correctly propagate uncertainties in
+the stellar spectrum from observational uncertainties on the stellar
+metallicity, temperature, etc.
+
+Importantly, the framework developed here allows one to analytically
+compute not only the ``optimal'' solution to the Doppler imaging problem,
+but also its uncertainty. The problem of re-constructing surface images
+of stars from spectra and/or light curves is fundamentally ill-posed because
+of intrinsic degeneracies and a large null space
+\citep[e.g.,][]{Luger2019} \xxx{more cites}. Coupled to uncertainties in
+the observations themselves, this makes the process of searching for the
+``optimal'' solution flawed at best, and meaningless at worst. Access to the
+full covariance matrix of the solution is therefore essential to assessing our
+confidence in the various features of the inferred surface maps.
+
+However, as we mentioned above, the Doppler imaging problem can be solved
+analytically for either the surface map or the spectrum, but not both. If
+neither are known exactly \emph{a priori}, which is quite often the case,
+we can still find the MAP solution quickly by guessing at an initial
+spectrum $\bvec{s}$ and iterating between optimizing for $\bvec{y}$ and
+optimizing for $\bvec{s}$. This bi-linear problem is not generally convex,
+but given a good starting point for $\bvec{s}$ and sufficient regularization
+on $\bvec{y}$, we find that it typically converges to the correct solution,
+especially after refinement with a non-linear solver;
+we discuss this in detail below.
+
+Once the MAP solution has been found for both $\bvec{s}$ and $\bvec{y}$,
+the covariance of one conditioned on the other can be computed from the
+formulae above. However, this is necessarily a lower bound on the true
+covariance of the solution, since it neglects any covariance \emph{between}
+$\bvec{s}$ and $\bvec{y}$. To \emph{correctly} account for this, one must
+resort to Monte Carlo methods or other sampling techniques. We discuss
+this further below.
 
@@
 
-\section{Validation}
-\label{sec:validation}
-
-Words here. Figure~\ref{fig:spot} and Figure~\ref{fig:compare}.
-
-\begin{figure}[p!]
-    \begin{centering}
-    \includegraphics[width=0.6\linewidth]{figures/spot.pdf}
-    \oscaption{spot}{%
-        Time evolution of a Gaussian absorption line on a rigidly rotating, 
-        spotted star computed from the analytic formulae in \S\ref{sec:kT}.
-        The stellar surface is modeled as a spherical harmonic expansion
-        up to $l=20$, and the line shape is assumed to be the same everywhere;
-        the spot simply downweights the local intensity at all wavelengths.
-        As the spot rotates into view (left panel), the line shape changes
-        slightly (center panel). The residuals between the line when the
-        spot is in view (solid) and when it is on the backside of the star
-        (dotted) are shown in the right panel, where
-        a Gaussian-like feature can be seen tracking the spot as it rotates
-        from the blueshifted hemisphere to the redshifted hemisphere of
-        the star.
-        \label{fig:spot}
-    }
-    \end{centering}
-\end{figure}
-
-\begin{figure}[h!]
-    \begin{centering}
-    \includegraphics[width=0.65\linewidth]{figures/compare.pdf}
-    \oscaption{compare}{%
-        The observed spectrum when the spot is in view computed with
-        \starry (blue) and numerically (orange). The problem setup
-        is the same as that in Figure~\ref{fig:spot}. The bottom
-        panel shows the absolute value of the difference between the 
-        two spectra for different grid resolutions in the numerical solution.
-        As the number of grid points increases, the numerical solution
-        approaches the \starry solution.
-        \label{fig:compare}
-    }
-    \end{centering}
-\end{figure}
-
 \section{The VOGTSTAR}
 \label{sec:vogtstar}
+
+\cite{Vogt1987}
 

### 2019-08-12 paparazzi/doppler.py

@@ -306,7 +306,7 @@ class Doppler(object):
         return x
 
     def rT(self):
-        """
+        r"""
         Return the :math:`\rho^\top` solution vector.
         
         """
@@ -339,7 +339,7 @@ class Doppler(object):
         return s
 
     def kT(self):
-        """
+        r"""
         Return the vectorized convolution kernels :math:`\kappa^\top`.
 
         This is a matrix whose rows are equal to the convolution kernels

### 2019-08-13 tex/ms.tex
more text

@@
 \begin{align}
+    \label{eq:inverse:azero}
     \azero &= \mathrm{vec}\left( \bvec{A_0} \right) \nonumber \\
@@
 \subsection{Solution for the intensity}
+\label{sec:solve_y}
 For a fixed, spatially constant rest-frame spectrum $\bvec{s}$, the model
@@
 \subsection{Solution for the spectrum}
+\label{sec:solve_s}
 If, on the other hand, the spatial intensity profile is known, the
@@
 
-\section{Other stuff}
+\section{Bells and Whistles}
+\label{sec:bells}
+
+\subsection{Unknown continuum normalization}
+\label{sec:norm}
+%
+Consider the star depicted in Figure~\ref{fig:spot}. When the spot is in
+view, absorption lines become distorted due to the suppression of either
+blueshifted or redshifted light. However, what is not shown in the figure
+is the fact that overall, the star also gets \emph{dimmer}: the 
+continuum level drops in the presence of the spot. Unfortunately, 
+spectrographs are not usually designed to measure this, since the
+change in the star's overall brightness from one observation to the next
+is often dwarfed by (unknown) changes in the spectrograph sensitivity. 
+For this reason, the spectra are usually normalized to have a
+fixed baseline continuum, and Equation~\ref{eq:linear:f} is no longer
+a good model for the data.
+
+One option is to collect simultaneous photometry on the target in a band
+similar to the wavelength range observed, and use this light curve to
+(un-)normalize the spectral timeseries $\bvec{f}$. However, when this is
+not an option, our model for $\bvec{f}$ (Equation~\ref{eq:linear:f}) must
+be amended.
+
+%
+\begin{align}
+    \label{eq:norm:f}
+    \bvec{f}
+    &=
+    \frac{
+        \Doppler
+        \,
+        \azero
+    } {
+        \bvec{b}
+    }
+    \quad,
+\end{align}
+%
+where $\bvec{b}$ is the baseline and the vector division is
+taken elementwise. When $\azero$ is given by Equation~(\ref{eq:inverse:azero}),
+the baseline $\bvec{b}$ is simply the total (wavelength-integrated) flux
+at each epoch, which \citet{Luger2019} showed is a linear operation on the
+spherical harmonic vector $\bvec{y}$:
+%
+\begin{align}
+    \label{eq:norm:b}
+    \bvec{b}
+    &=
+    \bvec{r}^\top \bvec{A_1} \bvec{R}(t) \, \bvec{y}
+    \nonumber \\
+    &\equiv
+    \bvec{B} \, \bvec{y}
+\end{align}
+%
+where $\bvec{r}$ is given by Equation~(18) in \citet{Luger2019},
+$\bvec{A_1}$ is given in Appendix B of \citet{Luger2019}, and \bvec{R}(t)
+is the rotation matrix defined previously.
+
+Given this new equation, we must change how we approach the inverse problem
+(\S\ref{sec:inverse}). When solving for the spectrum given the spherical 
+harmonic vector (\S\ref{sec:solve_s}), we need only make the replacements
+$\bvec{f} \rightarrow \nicefrac{\bvec{f}}{\bvec{B}\, \bvec{y}}$
+and 
+$\boldsymbol{\Sigma}_\mathbf{f} \rightarrow \nicefrac{\boldsymbol{\Sigma}_\mathbf{f}}{\bvec{B}\, \bvec{y}}$ 
+in Equations~(\ref{eq:inverse:shat}) and (\ref{eq:inverse:scov}).
+However, when solving for the spherical harmonic vector given the spectrum
+(\ref{sec:solve_y}), the problem is no longer linear in $\bvec{y}$.
+
 \subsection{Limb darkening}
-\subsection{Differential rotation and convective blueshift}
+Hello.
+
+\subsection{Multiple spectra}
+Hello.
 
@@
 
+\section{Stuff we're not addressing}
+%
+Differential rotation and convective blueshift.
+
 %

### 2019-08-13 tex/ms.tex
install numpy before scipy

@@
 However, when solving for the spherical harmonic vector given the spectrum
-(\ref{sec:solve_y}), the problem is no longer linear in $\bvec{y}$.
+(\ref{sec:solve_y}), the problem is no longer linear in $\bvec{y}$, as the
+vector of interest appears in both the numerator and the denominator:
+%
+\begin{align}
+    \label{eq:norm:fy}
+    \bvec{f}
+    &=
+    \frac{
+        \Doppler
+        \,
+        \bvec{S}
+        \,
+        \bvec{y}
+    }{
+        \bvec{B}
+        \,
+        \bvec{y}
+    }
+    \quad.
+\end{align}
+%
+While we can solver for $\bvec{y}$ using a non-linear optimizer, it is
+often the case that the denominator in Equation~(\ref{eq:norm:fy}) is close
+to unity; i.e., the total flux from the star typically varies by only a
+few percent. When this is the case, it is straightforward to linearize
+this equation.
 

### 2019-08-13 tex/ms.tex
issues with numpy on azure

@@
 are constructed from the values of $\bvec{g}$. If $\bvec{g}$ has length
-$N$, element $g_n$ is placed everywhere along the $k^\mathrm{th}$ diagonal 
-of $\bvec{G}$ for $k = -N / 2 + n$; all other entries of $\bvec{G}$ are 
+$L$, element $g_n$ is placed everywhere along the $k^\mathrm{th}$ diagonal 
+of $\bvec{G}$ for $k = -L / 2 + n$; all other entries of $\bvec{G}$ are 
 set to zero. Note that the matrix $\bvec{G}$ need not be square; in fact,
@@
 few percent. When this is the case, it is straightforward to linearize
-this equation.
+this equation. First, we note that the coefficient of the $Y_{0,0}$ spherical
+harmonic, $y_0$, sets the baseline intensity level on the surface of the 
+star, a quantity that is constant across all observations%
+\footnote{Unless the star's total luminosity is changing with time, 
+but we do not model that here.}%
+and formally degenerate with the luminosity of the star. We are therefore
+free to fix it, so for simplicity we choose $y_0 = 1$.
 

### 2019-08-13 tex/ms.tex
downgrade to Python 3.6

@@
 the baseline $\bvec{b}$ is simply the total (wavelength-integrated) flux
-at each epoch, which \citet{Luger2019} showed is a linear operation on the
+at each epoch %
+\xxx{need to repeat it for each wavelength bin in each epoch}%
+, which \citet{Luger2019} showed is a linear operation on the
 spherical harmonic vector $\bvec{y}$:
@@
 and formally degenerate with the luminosity of the star. We are therefore
-free to fix it, so for simplicity we choose $y_0 = 1$.
+free to fix it, so for simplicity we choose $y_0 = 1$. We may 
+therefore write %
+\xxx{this equation needs work}%
+%
+\begin{align}
+    \bvec{f}
+    &=
+    \frac{
+        \Doppler
+        \,
+        \bvec{S}
+        \,
+        + 
+        \,
+        \Doppler
+        \,
+        \bvec{S}
+        \,
+        \bvec{y}
+    }{
+        1
+        \,
+        +
+        \bvec{B}
+        \,
+        \bvec{y}
+    }
+    \quad.
+\end{align}
+%
 

### 2019-08-13 tex/ms.tex
more words

--- 2019-08-13 tex/ms.tex
@@
 is a $(NK' \times N)$ block matrix constructed by repeating the column
-vector $\bvec{s}$ $N$ times in blocks along the main diagonal. Given
-prior mean $\boldsymbol{\mu}_\mathbf{y}$ and covariance
-$\boldsymbol{\Lambda}_\mathbf{y}$ on $\mathbf{y}$, the MAP solution
+vector $\bvec{s}$ $N$ times in blocks along the main diagonal. 
+%
+Before we solve this equation for $\bvec{y}$, we note that in practice
+it is convenient to fix the coefficient of the $Y_{0,0}$ spherical
+harmonic, $y_0$, to unity. After all, this coefficient is not directly
+constrained by the data, as it merely sets the baseline intensity on the
+surface of the star and is therefore formally degenerate with the stellar 
+luminosity (which also cannot be directly inferred from the data). This
+choice further ensures a mean baseline of unity for the model 
+vector $\mathbf{f}$. We may therefore write
+%
+\begin{align}
+    \label{eq:inverse:fy1}
+    \bvec{f}
+    &=
+    \Doppler
+    \,
+    \bvec{s}_\bvec{0}
+    \,
+    +
+    \,
+    \Doppler
+    \,
+    \bvec{S_1}
+    \,
+    \bvec{y}_\bvec{1}
+    \quad,
+\end{align}
+%
+where the vector $\bvec{s_0}$ denotes the first column of $\bvec{S}$,
+the matrix $\bvec{S_1}$ denotes the remaining columns of $\bvec{S}$, and
+$\bvec{y_1}$ is the quantity we wish to solve for: the vector of spherical 
+harmonic coefficients of degree $l \ge 1$.
+
+Given prior mean $\boldsymbol{\mu}_\bvec{y_1}$ and covariance
+$\boldsymbol{\Lambda}_\bvec{y_1}$ on $\bvec{y_1}$, the MAP solution
 is given by
@@
 \begin{align}
-    \label{eq:inverse:yhat}
-    \bvec{\hat{y}} &= 
-    \boldsymbol{\Sigma}_\mathbf{\hat{y}}
+    \label{eq:inverse:y1hat}
+    \bvec{\hat{y}_1} &= 
+    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1}
     \left(
-        \bvec{S}^\top\Doppler^\top
+        \bvec{S_1}^\top\Doppler^\top
         {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
-        \bvec{f}
+        \left(\bvec{f} - \Doppler\bvec{s}_\bvec{0}\right)
         +
-        {\boldsymbol{\Lambda}_\mathbf{y}}^{-1} \boldsymbol{\mu}_\mathbf{y}
+        {\boldsymbol{\Lambda}_\bvec{y_1}}^{-1} \boldsymbol{\mu}_\bvec{y_1}
     \right)
@@
 \begin{align}
-    \label{eq:inverse:ycov}
-    \boldsymbol{\Sigma}_\mathbf{\hat{y}} &= 
+    \label{eq:inverse:y1cov}
+    \boldsymbol{\Sigma}_\bvec{\hat{y}_1} &= 
     \left(
-        \bvec{S}^\top\Doppler^\top
-        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
-        \Doppler\bvec{S}
+        \bvec{S_1}^\top\Doppler^\top
+        {\boldsymbol{\Sigma}_\bvec{f}}^{-1}
+        \Doppler\bvec{S_1}
         +
-        {\boldsymbol{\Lambda}_\mathbf{y}}^{-1}
+        {\boldsymbol{\Lambda}_\bvec{y_1}}^{-1}
     \right)^{-1}
@@
 %
-If we choose a prior with zero mean ($\boldsymbol{\mu}_\bvec{y} = 0$)
+If we choose a prior with zero mean ($\boldsymbol{\mu}_\bvec{y_1} = 0$)
 and a diagonal covariance that is constant for each spherical harmonic 
@@
 \begin{align}
-    \boldsymbol{\Lambda}_\bvec{y} &=
+    \boldsymbol{\Lambda}_\bvec{y_1} &=
     \mathrm{diag} \left(
-        \sigma_0^2
-        \quad\quad\quad\quad
         \sigma_1^2
@@
 for the surface map $\bvec{y}$ is \emph{analytic} 
-(Equations~\ref{eq:inverse:yhat}
-and \ref{eq:inverse:ycov}). Conversely, if the surface map is known,
+(Equations~\ref{eq:inverse:y1hat}
+and \ref{eq:inverse:y1cov}). Conversely, if the surface map is known,
 the posterior for the spectrum is also analytic 
@@
 the baseline $\bvec{b}$ is simply the total (wavelength-integrated) flux
-at each epoch, which \citet{Luger2019} showed is a linear operation on the
-spherical harmonic vector $\bvec{y}$:
+at each epoch, repeated for every element in each spectrum. 
+Based on \citet{Luger2019}, this can be computed as a purely linear operation 
+on the spherical harmonic vector $\bvec{y}$:
 %
@@
     &=
-    \bvec{r}^\top \bvec{A_1} \bvec{R}(t) \, \bvec{y}
-    \nonumber \\
+    %
+    \begin{pmatrix}
+        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_0) \\
+        \cdots \\
+        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_0) \\
+        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_1) \\
+        \cdots \\
+        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_1) \\
+        \cdots \\
+        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_{M-1}) \\
+        \cdots \\
+        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_{M-1})
+    \end{pmatrix}
+    \bvec{y}
+    %
+    \nonumber \\[0.5em]
     &\equiv
@@
 where $\bvec{r}$ is given by Equation~(18) in \citet{Luger2019},
-$\bvec{A_1}$ is given in Appendix B of \citet{Luger2019}, and \bvec{R}(t)
+$\bvec{A_1}$ is given in Appendix B of \citet{Luger2019}, and $\bvec{R}(t)$
 is the rotation matrix defined previously.
@@
     \frac{
-        \Doppler
+        \bvec{D}
         \,
@@
 %
-While we can solver for $\bvec{y}$ using a non-linear optimizer, it is
+While we can solve for $\bvec{y}$ using a non-linear optimizer, it is
 often the case that the denominator in Equation~(\ref{eq:norm:fy}) is close
@@
 this equation.
+Following the notation from \S\ref{sec:solve_y}, we may therefore write
+%
+\begin{align}
+    \bvec{f}
+    &=
+    \frac{
+        \bvec{D} \, \bvec{s_0}
+        \,
+        + 
+        \,
+        \bvec{D}\bvec{S_1}
+        \,
+        \bvec{y_1}
+    }{
+        \bvec{B_0}
+        \,
+        +
+        \bvec{B_1}
+        \,
+        \bvec{y_1}
+    }
+    \quad,
+\end{align}
+%
+where $\bvec{B_0} = \bvec{1}$ is the first column of $\bvec{B}$
+and $\bvec{B}_\bvec{1}$ denotes the
+matrix composed from the remaining $N - 1$ columns of $\bvec{B}$.
+Expanding the expression above about 
+$\bvec{B_1} \bvec{y_1} = \bvec{0}$, we have
+%
+\begin{align}
+    \bvec{f}
+    &\approx
+    \left(
+        \bvec{D} \, \bvec{s_0}
+        \,
+        + 
+        \,
+        \bvec{D}\bvec{S_1}
+        \,
+        \bvec{y_1}
+    \right)
+    \circ
+    \left(
+        \bvec{1}
+        \,
+        -
+        \bvec{B_1}
+        \,
+        \bvec{y_1}
+    \right)
+    \nonumber \\
+    &=
+    \left(
+        \bvec{D}\bvec{S_1}
+        \,
+        -
+        \bvec{C}
+    \right)
+    \bvec{y_1}
+    \,
+    +
+    \,
+    \bvec{D} \, \bvec{s_0}
+    \quad,
+\end{align}
+%
+where $\circ$ denotes an elementwise product and $\bvec{C}$ is a matrix
+constructed by multiplying the $i^\mathrm{th}$ row of $\bvec{B_1}$ by the
+$i^\mathrm{th}$ element of $\bvec{D}\bvec{s_0}$.
+%
+This equation is now
+linear in $\bvec{y}_\bvec{1}$, so we may solve the least-squares problem
+as before:
+%
+\begin{align}
+    \label{eq:norm:yhat}
+    \bvec{\hat{y}_1} &= 
+    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1}
+    \left(
+        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
+        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
+        (\bvec{f} - \bvec{D}\bvec{s_0})
+        +
+        {\boldsymbol{\Lambda}_{\mathbf{y}_\bvec{1}}}^{-1} \boldsymbol{\mu}_{\mathbf{y}_\bvec{1}}
+    \right)
+    \quad,
+\end{align}
+%
+with covariance
+%
+\begin{align}
+    \label{eq:norm:ycov}
+    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1} &= 
+    \left(
+        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
+        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
+        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)
+        +
+        {\boldsymbol{\Lambda}_{\mathbf{y}_1}}^{-1}
+    \right)^{-1}
+    \quad.
+\end{align}
 

### 2019-08-13 tex/ms.tex
two spectra example

@@
 \end{align}
+%
+Note, importantly, that these equations are valid only in the limit that the
+change in the total flux from the star is small. Nevertheless, even in the 
+general case, we find that solving this linear problem yields a good
+starting point for a non-linear optimization, which we revisit in more
+detail below.
 

### 2019-08-15 tex/ms.tex
reorg; spotstar

@@
 \newcommand{\lmax}{\ensuremath{l_\mathrm{max}}}
-\newcommand{\vogtstar}{\texttt{VOGTSTAR}\xspace}
+\newcommand{\spot}{\texttt{SPOT}\xspace}
 
@@
 
-\section{The VOGTSTAR}
-\label{sec:vogtstar}
+\section{The SPOT star}
+\label{sec:spotstar}
 
@@
     \begin{centering}
-    \includegraphics[width=0.49\linewidth]{figures/vogtstar_u_timeseries.pdf}
-    \includegraphics[width=0.49\linewidth]{figures/vogtstar_u_rect.pdf}
-    \oscaption{vogtstar_u}{%
-        Solution to the \vogtstar problem at high SNR when both 
+    \includegraphics[width=0.49\linewidth]{figures/spot_y1_timeseries.pdf}
+    \includegraphics[width=0.49\linewidth]{figures/spot_y1_rect.pdf}
+    \oscaption{spot_y1}{%
+        Solution to the \spot problem at high SNR when both 
         the rest frame spectrum and the baseline are known.
-        \label{fig:vogtstar_u}
+        \label{fig:spot_y1}
     }
@@
     \begin{centering}
-    \includegraphics[width=0.49\linewidth]{figures/vogtstar_ub_timeseries.pdf}
-    \includegraphics[width=0.49\linewidth]{figures/vogtstar_ub_rect.pdf}
+    \includegraphics[width=0.49\linewidth]{figures/spot_y1b_timeseries.pdf}
+    \includegraphics[width=0.49\linewidth]{figures/spot_y1b_rect.pdf}
     \\[0.5em]
-    \includegraphics[width=0.405\linewidth]{figures/vogtstar_ub_baseline.pdf}
-    \includegraphics[width=0.575\linewidth]{figures/vogtstar_ub_coeffs.pdf}
-    \oscaption{vogtstar_ub}{%
-        Similar to Figure~\ref{fig:vogtstar_u}, but assuming the baseline
+    \includegraphics[width=0.405\linewidth]{figures/spot_y1b_baseline.pdf}
+    \includegraphics[width=0.575\linewidth]{figures/spot_y1b_coeffs.pdf}
+    \oscaption{spot_y1b}{%
+        Similar to Figure~\ref{fig:spot_y1}, but assuming the baseline
         is not known.
-        \label{fig:vogtstar_ub}
+        \label{fig:spot_y1b}
     }
@@
     \begin{centering}
-    \includegraphics[width=0.49\linewidth]{figures/vogtstar_ubvT_timeseries.pdf}
-    \includegraphics[width=0.49\linewidth]{figures/vogtstar_ubvT_rect.pdf}
+    \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_timeseries.pdf}
+    \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_rect.pdf}
     \\[0.5em]
-    \includegraphics[width=0.405\linewidth]{figures/vogtstar_ubvT_baseline.pdf}
-    \includegraphics[width=0.575\linewidth]{figures/vogtstar_ubvT_coeffs.pdf}
+    \includegraphics[width=0.405\linewidth]{figures/spot_y1bs_baseline.pdf}
+    \includegraphics[width=0.575\linewidth]{figures/spot_y1bs_coeffs.pdf}
     \\[0.5em]
-    \includegraphics[width=0.98\linewidth]{figures/vogtstar_ubvT_spectrum.pdf}
-    \oscaption{vogtstar_ubvT}{%
-        Similar to Figure~\ref{fig:vogtstar_u}, but assuming we have no
+    \includegraphics[width=0.98\linewidth]{figures/spot_y1bs_spectrum.pdf}
+    \oscaption{spot_y1bs}{%
+        Similar to Figure~\ref{fig:spot_y1}, but assuming we have no
         information about either the spectrum, the baseline, or the map
         coefficients.
-        \label{fig:vogtstar_ubvT}
+        \label{fig:spot_y1bs}
     }
@@
     \oscaption{inclinations}{%
-        Recovered \vogtstar map as a function of inclination.
+        Recovered \spot map as a function of inclination.
         \label{fig:inclinations}

### 2019-08-15 paparazzi/doppler.py

@@ -28,15 +28,15 @@ class Doppler(object):
         vsini (int, optional): Projected equatorial velocity in km/s. 
             Defaults to 40.
         inc (float, optional): Inclination in degrees. Defaults to 40.0.
-        u_mu (float or ndarray, optional): Prior mean on the spherical 
+        y1_mu (float or ndarray, optional): Prior mean on the spherical 
             harmonic coefficients. Defaults to 0.0.
-        u_sig (float or ndarray, optional): Prior standard deviation on 
+        y1_sig (float or ndarray, optional): Prior standard deviation on 
             the spherical harmonic coefficients. Defaults to 0.01.
-        vT_mu (float or ndarray, optional): Prior mean on the spectrum. 
+        s_mu (float or ndarray, optional): Prior mean on the spectrum. 
             Defaults to 1.0.
-        vT_sig (float, optional): Prior standard deviation on
+        s_sig (float, optional): Prior standard deviation on
             the spectrum. Defaults to 0.3.
-        vT_rho (float, optional): Prior lengthscale on the Gaussian Process
+        s_rho (float, optional): Prior lengthscale on the Gaussian Process
             prior on the spectrum. Set to zero to disable the GP.
             Defaults to 3.e-5.
         baseline_mu (float or ndarray, optional): Prior mean on the 
@@ -50,11 +50,11 @@ class Doppler(object):
         ydeg=15,
         vsini=40,
         inc=40.0,
-        u_mu=0.0,
-        u_sig=0.01,
-        vT_mu=1.0,
-        vT_sig=0.3,
-        vT_rho=3.0e-5,
+        y1_mu=0.0,
+        y1_sig=0.01,
+        s_mu=1.0,
+        s_sig=0.3,
+        s_rho=3.0e-5,
         baseline_mu=1.0,
         baseline_sig=0.1,
     ):
@@ -69,25 +69,25 @@ class Doppler(object):
         self._lnlam = None
         self.F = None
         self.ferr = None
-        self.u_true = None
-        self.vT_true = None
+        self.y1_true = None
+        self.s_true = None
         self.baseline_true = None
 
         # Inference params
-        self.u_mu = u_mu
-        self.u_sig = u_sig
-        self.vT_mu = vT_mu
-        self._vT_sig = vT_sig
-        self._vT_rho = vT_rho
+        self.y1_mu = y1_mu
+        self.y1_sig = y1_sig
+        self.s_mu = s_mu
[…]

### 2019-08-15 scratch/twospec.py

@@ -13,17 +13,7 @@ import theano.tensor as tt
 import theano.sparse as ts
 from tqdm import tqdm
 from inspect import getmro
-
-# Initialize some stuff
-niter = 100
-lr = 1e-5
-np.random.seed(13)
-ferr = 1.0e-4
-res = 300
-dop = pp.Doppler(ydeg=15, vT_sig=0.1)
-dop.generate_data(ferr=ferr, ntheta=32)
-B1 = dop._map.X(theta=dop.theta).eval()[:, 1:]
-B1 = np.repeat(B1, dop.K, axis=0)
+import celerite
 
 
 def is_theano(*objs):
@@ -38,252 +28,326 @@ def is_theano(*objs):
     return False
 
 
-def model(y1, s):
-    # Theano or numpy?
-    if is_theano(y1, s):
-        math = tt
-    else:
-        math = np
-
-    # Compute the baseline
-    b = 1.0 + math.dot(B1, y1)
-
-    # Compute the first component
-    A1 = math.dot(
-        math.reshape(s[0], (-1, 1)),
-        math.reshape(math.concatenate([[1.0], y1]), (1, -1)),
-    )
-    a1 = math.reshape(math.transpose(A1), (-1,))
-    if math == tt:
-        M1 = math.reshape(ts.dot(dop.D(), a1), (dop.M, -1))
-    else:
-        M1 = math.reshape(dop.D().dot(a1), (dop.M, -1))
-    M1 /= math.reshape(b, (dop.M, -1))
-
-    # Compute the second component
-    A2 = math.dot(
-        math.reshape(s[1], (-1, 1)),
-        math.reshape(math.concatenate([[1.0], -y1]), (1, -1)),
-    )
-    a2 = math.reshape(math.transpose(A2), (-1,))
-    if math == tt:
-        M2 = math.reshape(ts.dot(dop.D(), a2), (dop.M, -1))
-    else:
-        M2 = math.reshape(dop.D().dot(a2), (dop.M, -1))
-    M2 /= math.reshape((1 - (b - 1)), (dop.M, -1))
-
-    return M1 + M2
-
-
-# TODO: Better
-s_mu = [0.5, 0.5]
-
-
-def loss(y1, s):
-    # Theano or numpy?
-    if is_theano(y1, s):
[…]

### 2019-08-15 tex/figures/spot_y1.py

@@ -1,6 +1,6 @@
 # -*- coding: utf-8 -*-
 """
-Solve the VOGTSTAR problem.
+Solve the SPOT problem.
 
 In this case, we know the spectrum and the baseline
 perfectly. The problem is linear in the map, so solving
@@ -9,7 +9,7 @@ the Doppler problem is easy!
 """
 import paparazzi as pp
 import numpy as np
-from utils.vogtstar_plot import plot_results
+from utils.spot import plot_results
 
 np.random.seed(13)
 
@@ -27,15 +27,15 @@ dop = pp.Doppler(ydeg=15)
 dop.generate_data(ferr=ferr)
 
 # Compute the true baseline (assumed to be known exactly)
-dop.u = dop.u_true
+dop.y1 = dop.y1_true
 baseline = dop.baseline()
 
 # Reset all coefficients
-dop.vT = dop.vT_true
-dop.u = None
+dop.s = dop.s_true
+dop.y1 = None
 
 # Solve!
-loss, cho_u, cho_vT = dop.solve(vT=dop.vT, baseline=baseline)
+loss, cho_y1, cho_s = dop.solve(s=dop.s, baseline=baseline)
 
 # Plot the results
-plot_results(dop, name="vogtstar_u", loss=loss, cho_u=cho_u, cho_vT=cho_vT)
+plot_results(dop, name="spot_y1", loss=loss, cho_y1=cho_y1, cho_s=cho_s)

### 2019-08-15 tex/figures/utils/spot.py

@@ -13,8 +13,8 @@ __all__ = ["plot_results"]
 def plot_results(
     doppler,
     loss=[],
-    cho_u=None,
-    cho_vT=None,
+    cho_y1=None,
+    cho_s=None,
     name="vogtstar",
     nframes=None,
     render_movies=False,
@@ -29,12 +29,12 @@ def plot_results(
     # Get the values we'll need for plotting
     ydeg = doppler.ydeg
     theta = doppler.theta
-    u_true = doppler.u_true
-    vT_true = doppler.vT_true
-    vT_deconv = doppler.vT_deconv
+    y1_true = doppler.y1_true
+    s_true = doppler.s_true
+    s_deconv = doppler.s_deconv
     baseline_true = doppler.baseline_true
-    u = np.array(doppler.u)
-    vT = np.array(doppler.vT)
+    y1 = np.array(doppler.y1)
+    s = np.array(doppler.s)
     baseline = doppler.baseline().reshape(-1)
     model = doppler.model()
     F = doppler.F
@@ -55,8 +55,8 @@ def plot_results(
     fig, ax = plt.subplots(1, figsize=(8, 5))
     ax.plot(theta_, baseline_true_, label="true")
     ax.plot(theta_, baseline_, label="inferred")
-    if cho_u is not None:
-        U = np.triu(cho_u[0])
+    if cho_y1 is not None:
+        U = np.triu(cho_y1[0])
         B = doppler._map.X(theta=doppler.theta).eval()[:, 1:]
         A = np.linalg.solve(U.T, B.T)
         baseline_sig = np.sqrt(np.sum(A ** 2, axis=0))
@@ -82,8 +82,8 @@ def plot_results(
     if len(np.atleast_1d(loss).flatten()) > 1:
 
         # Compute the loss @ true value
-        doppler.u = u_true
-        doppler.vT = vT_true
+        doppler.y1 = y1_true
+        doppler.s = s_true
         loss_true = doppler.loss()
 
         # Print for the record
@@ -105,15 +105,15 @@ def plot_results(
     # Plot the Ylm coeffs
     fig, ax = plt.subplots(1, figsize=(12, 5))
     n = np.arange(1, doppler.N)
-    ax.plot(n, u_true, "C0-", label="true")
-    lo = (doppler.u_mu - doppler.u_sig) * np.ones_like(u)
-    hi = (doppler.u_mu + doppler.u_sig) * np.ones_like(u)
+    ax.plot(n, y1_true, "C0-", label="true")
[…]

### 2019-08-16 tex/ms.tex
twospec working

@@
     \multicolumn{1}{c}{\textbf{Description}} &
-    \multicolumn{1}{c}{\textbf{Type}} \\
+    \multicolumn{1}{c}{\textbf{Reference}} \\
     \toprule
@@
     %
-    $a$                             & lowercase italic & scalar\\
-    $A$                             & uppercase italic & scalar\\
-    $\alpha$                        & lowercase italic Greek & scalar\\
-    $\bvec{a}$                      & lowercase boldface & column vector\\
-    $\bvec{A}$                      & uppercase boldface & matrix\\
-    $\boldsymbol{\alpha}^\top$      & lowercase boldface Greek & basis row vector
+    $a_{lm}$    & spectral spherical harmonic coefficient               & Equation~(\ref{eq:deconv:Ixi0})\\
+    $\alm$      & vector of spectral spherical harmonic coefficients    & Equation~(\ref{eq:deconv:alm})\\
+    $\bvec{a_0}$& $\alm$ at reference time $t = t_0$                    & Equation~(\ref{eq:deconv:R})\\
+    $c$         & speed of light                                        & Equation~(\ref{eq:kT:beta})\\
+    $\Curve$    & curve of constant radial velocity                     & Equation~(\ref{eq:deconv:kT})\\
+    $\Dargs$    & parameters of the Doppler field                       & \S\ref{sec:the_problem}\\
+    $\D$        & logarithmic Doppler shift                             & Equation~(\ref{eq:the_problem:D})\\
+    $F$         & flux                                                  & Equation~(\ref{eq:the_problem:F})\\
+    $i$         & inclination                                           & Equation~(\ref{eq:kT:beta})\\
+    $I$         & specific intensity                                    & Equation~(\ref{eq:the_problem:Ixi})\\
+    $l$         & spherical harmonic degree                             & \\
+    $m$         & spherical harmonic order                              & \\
+    $\bvec{R}$  & Wigner rotation matrix                                & Equation~(\ref{eq:deconv:R})\\
+    $\Surf$     & projected visible area of the star                    & Equation~(\ref{eq:the_problem:F})\\
+    $t$         & time                                                  & \S\ref{sec:the_problem}\\
+    $\x$        & Cartesian position on the sky                         & \S\ref{sec:the_problem}\\
+    $y_{lm}$    & spherical harmonic coefficient                        & \S\ref{sec:inverse}\\
+    $Y_{lm}$    & spherical harmonic                                    & Equation~(\ref{eq:deconv:Ixi0})\\
+    %
+    %
+    $\beta$     & relativistic parameter                                & Equation~(\ref{eq:the_problem:D})\\
+    $\delta$    & Dirac delta function                                  & Equation~(\ref{eq:deconv:convolution})\\
+    $\kT$       & convolution kernel basis vector                       & Equation~(\ref{eq:deconv:kT})\\
+    $\lambda$   & wavelength (in nm)                                    & \S\ref{sec:the_problem}\\
+    $\lnlam$    & $\ln\lambda$ (observer frame)                         & \S\ref{sec:the_problem}\\
+    $\lnlam_0$  & $\ln\lambda$ (rest frame)                             & \S\ref{sec:the_problem}\\
+    $\ylmbasis$ & spherical harmonic basis vector                       & Equation~(\ref{eq:deconv:ylmbasis})\\
+    $\omega$    & angular velocity                                      & Equation~(\ref{eq:kT:beta})\\
+    %
+    %
+    $*$         & convolution                                           & Equation~(\ref{eq:deconv:convolution_def})\\
+    $\circ$     & element-wise product                                  & Equation~(\ref{eq:norm:fapprox})
 \end{longtable}
@@
 \begin{align}
-    \label{eq:intro:Ixi}
+    \label{eq:the_problem:Ixi}
     I(\lnlam, \x, t, \Dargs) &= 
@@
 \begin{align}
-    \label{eq:intro:D}
+    \label{eq:the_problem:D}
     \D(\x, \Dargs) 
@@
 \begin{align}
-    \label{eq:intro:F}
+    \label{eq:the_problem:F}
     F(\lnlam, t, \Dargs) 
@@
 %
-The difficulty in solving Equation~(\ref{eq:intro:F}) stems from the fact
+The difficulty in solving Equation~(\ref{eq:the_problem:F}) stems from the fact
 that $I(\lnlam, \x, t, \Dargs)$ is difficult to write down in 
@@
 section is to deconvolve each of these terms to make solving the integral
-in Equation~(\ref{eq:intro:F}) easier.
-%
-The first thing we will do is to express Equation~(\ref{eq:intro:Ixi})
+in Equation~(\ref{eq:the_problem:F}) easier.
+%
+The first thing we will do is to express Equation~(\ref{eq:the_problem:Ixi})
 as a convolution:
@@
     \label{eq:deconv:convolution_def}
-    (g * h)(t) \equiv \int_{-\infty}^\infty f(\tau) h(t - \tau) d\tau
+    (g * h)(t) \equiv \int_{-\infty}^\infty g(\tau) h(t - \tau) d\tau
 \end{align}
@@
 \begin{align}
+    \label{eq:deconv:ylmbasis}
     \ylmbasis(\x) \equiv 
@@
 \begin{align}
+    \label{eq:kT:beta}
     \beta(\x, \Dargs) = \frac{\omega \sin i \, x}{c}
@@
 where $\bvec{b}$ is the baseline and the vector division is
-taken elementwise. When $\azero$ is given by Equation~(\ref{eq:inverse:azero}),
+performed elementwise. When $\azero$ is given by Equation~(\ref{eq:inverse:azero}),
 the baseline $\bvec{b}$ is simply the total (wavelength-integrated) flux
@@
 and 
-$\boldsymbol{\Sigma}_\mathbf{f} \rightarrow \nicefrac{\boldsymbol{\Sigma}_\mathbf{f}}{\bvec{B}\, \bvec{y}}$ 
+$\boldsymbol{\Sigma}_\mathbf{f} \rightarrow \nicefrac{\boldsymbol{\Sigma}_\mathbf{f}}{(\bvec{B}\, \bvec{y})^2}$ 
 in Equations~(\ref{eq:inverse:shat}) and (\ref{eq:inverse:scov}).
@@
 \begin{align}
+    \label{eq:norm:fapprox}
     \bvec{f}

### 2019-08-16 scratch/twospec.py

@@ -42,6 +42,7 @@ Kp = dop.Kp
 W = dop.W
 N = dop.N
 M = dop.M
+lnlam = dop.lnlam
 lnlam_padded = dop.lnlam_padded
 B1 = dop._map.X(theta=dop.theta).eval()[:, 1:]
 B1 = np.repeat(B1, K, axis=0)
@@ -51,11 +52,7 @@ map = starry.Map(15, lazy=False)
 map.inc = 40
 
 # Add a spot, then subtract the median & reload
-map.add_spot(-1.0, sigma=0.25, lat=30)
-I = map.render(projection="rect", res=res)[0]
-I -= np.nanmedian(I)
-I = np.flipud(I)
-map.load(I)
+map.load("spot")
 y1_true = np.array(map[1:, :])
 b_true = np.repeat(map.flux(theta=theta), K)
 img_true = map.render(projection="rect", res=res)[0]
@@ -79,30 +76,28 @@ for _ in range(nlines - 1):
     s1_true -= amp * np.exp(-0.5 * (lnlam_padded - mu) ** 2 / sigma ** 2)
 
 # This is the amplitude of the perturbation for the 2nd spectrum
-w_true = -0.5
+w_true = -0.25
 
 # Priors
-w_mu = -0.5
-w_sig = 1e-12  # We assume we know this exactly.
-s0_mu = s0_true
-s0_sig = 1e-12  # We assume we know this exactly.
-s0_rho = 0.0
-s1_mu = s1_true
-s1_sig = 1e-12  # We assume we know this exactly.
-s1_rho = 0.0
+w_mu = -0.20
+w_sig = 0.1
+s0_mu = s0_true  # We assume we know the base spectrum exactly.
+s0_sig = 1e-12
+s0_rho = 3.0e-5
+s1_mu = 1.0
+s1_sig = 0.3
+s1_rho = 3.0e-5
 y1_mu = 0.0
-y1_sig = np.array(
-    [l ** -2.5 for l in range(1, map.ydeg + 1) for m in range(-l, l + 1)]
-)
+y1_sig = 0.03
 b_mu = 1.0
 b_sig = 0.1
 dcf = 10.0
 
 # Optimization params
-T = 1.01  # 500000
-dlogT = -0.025
-niter = 0
-lr = 1e-3
+T = 50000
+dlogT = -0.02
+niter = 500
+lr = 1e-4
 
 # Compute the GP on the spectra
[…]

### 2019-08-16 tex/figures/utils/spot.py

@@ -189,7 +189,7 @@ def plot_results(
         )
 
     # Normalize to the maximum for plotting
-    vmax = max(np.nanmax(img_rect), np.nanmax(img_true_rect))
+    vmax = np.nanmax(img_true_rect)
     img /= vmax
     img_rect /= vmax
     img_true_rect /= vmax

### 2019-08-19 tex/ms.tex
better twospec

@@
 Check out \citet{Luger2019} and \citet{Bedell2019} and stuff.
-
-%
-\begin{center}
-    \begin{longtable}{cll}
-    \caption{Notation used in this paper} 
-    \label{tab:notation} \\
-    %
-    \toprule
-    \multicolumn{1}{c}{\textbf{Symbol}} &
-    \multicolumn{1}{c}{\textbf{Description}} &
-    \multicolumn{1}{c}{\textbf{Reference}} \\
-    \toprule
-    \endhead
-    %
-    \endfoot
-    %
-    \endlastfoot
-    %
-    $a_{lm}$    & spectral spherical harmonic coefficient               & Equation~(\ref{eq:deconv:Ixi0})\\
-    $\alm$      & vector of spectral spherical harmonic coefficients    & Equation~(\ref{eq:deconv:alm})\\
-    $\bvec{a_0}$& $\alm$ at reference time $t = t_0$                    & Equation~(\ref{eq:deconv:R})\\
-    $c$         & speed of light                                        & Equation~(\ref{eq:kT:beta})\\
-    $\Curve$    & curve of constant radial velocity                     & Equation~(\ref{eq:deconv:kT})\\
-    $\Dargs$    & parameters of the Doppler field                       & \S\ref{sec:the_problem}\\
-    $\D$        & logarithmic Doppler shift                             & Equation~(\ref{eq:the_problem:D})\\
-    $F$         & flux                                                  & Equation~(\ref{eq:the_problem:F})\\
-    $i$         & inclination                                           & Equation~(\ref{eq:kT:beta})\\
-    $I$         & specific intensity                                    & Equation~(\ref{eq:the_problem:Ixi})\\
-    $l$         & spherical harmonic degree                             & \\
-    $m$         & spherical harmonic order                              & \\
-    $\bvec{R}$  & Wigner rotation matrix                                & Equation~(\ref{eq:deconv:R})\\
-    $\Surf$     & projected visible area of the star                    & Equation~(\ref{eq:the_problem:F})\\
-    $t$         & time                                                  & \S\ref{sec:the_problem}\\
-    $\x$        & Cartesian position on the sky                         & \S\ref{sec:the_problem}\\
-    $y_{lm}$    & spherical harmonic coefficient                        & \S\ref{sec:inverse}\\
-    $Y_{lm}$    & spherical harmonic                                    & Equation~(\ref{eq:deconv:Ixi0})\\
-    %
-    %
-    $\beta$     & relativistic parameter                                & Equation~(\ref{eq:the_problem:D})\\
-    $\delta$    & Dirac delta function                                  & Equation~(\ref{eq:deconv:convolution})\\
-    $\kT$       & convolution kernel basis vector                       & Equation~(\ref{eq:deconv:kT})\\
-    $\lambda$   & wavelength (in nm)                                    & \S\ref{sec:the_problem}\\
-    $\lnlam$    & $\ln\lambda$ (observer frame)                         & \S\ref{sec:the_problem}\\
-    $\lnlam_0$  & $\ln\lambda$ (rest frame)                             & \S\ref{sec:the_problem}\\
-    $\ylmbasis$ & spherical harmonic basis vector                       & Equation~(\ref{eq:deconv:ylmbasis})\\
-    $\omega$    & angular velocity                                      & Equation~(\ref{eq:kT:beta})\\
-    %
-    %
-    $*$         & convolution                                           & Equation~(\ref{eq:deconv:convolution_def})\\
-    $\circ$     & element-wise product                                  & Equation~(\ref{eq:norm:fapprox})
-\end{longtable}
-\end{center}
 
@@
 Expanding the expression above about 
-$\bvec{B_1} \bvec{y_1} = \bvec{0}$, we have
+$\bvec{B_1} \bvec{y_1} = \bvec{0}$ and keeping only terms up to
+first order, we have
 %
@@
     \nonumber \\
-    &=
+    &\approx
     \left(
@@
 where $\circ$ denotes an elementwise product and $\bvec{C}$ is a matrix
-constructed by multiplying the $i^\mathrm{th}$ row of $\bvec{B_1}$ by the
-$i^\mathrm{th}$ element of $\bvec{D}\bvec{s_0}$.
+constructed by multiplying each row of $\bvec{B_1}$ by the
+corresponding element of $\bvec{D}\bvec{s_0}$.
 %
@@
 
+% Table
+\clearpage
+\begin{center}
+    \begin{longtable}{cll}
+    \caption{Notation used in this paper \xxx{mostly complete up to sec 5}} 
+    \label{tab:notation} \\
+    %
+    \toprule
+    \multicolumn{1}{c}{\textbf{Symbol}} &
+    \multicolumn{1}{c}{\textbf{Description}} &
+    \multicolumn{1}{c}{\textbf{Reference}} \\
+    \toprule
+    \endhead
+    %
+    \endfoot
+    %
+    \endlastfoot
+    %
+    $a_{lm}$                 & spectral spherical harmonic coefficient               & Equation~(\ref{eq:deconv:Ixi0})\\
+    $\alm$                   & vector of spectral spherical harmonic coefficients    & Equation~(\ref{eq:deconv:alm})\\
+    $\bvec{a_0}$             & $\alm$ at reference time $t = t_0$                    & Equation~(\ref{eq:deconv:R})\\
+    $\bvec{A_0}$             & matrix form of $\bvec{a_0}$                           & Equation~(\ref{eq:inverse:azero})\\
+    $c$                      & speed of light                                        & Equation~(\ref{eq:kT:beta})\\
+    $\Curve$                 & curve of constant radial velocity                     & Equation~(\ref{eq:deconv:kT})\\
+    $\Dargs$                 & parameters of the Doppler field                       & \S\ref{sec:the_problem}\\
+    $\D$                     & logarithmic Doppler shift                             & Equation~(\ref{eq:the_problem:D})\\
+    $\Doppler$               & Doppler design matrix                                 & Equation~(\ref{eq:linear:f})\\
+    $\bvec{f}$               & vector of observed flux values                        & Equation~(\ref{eq:linear:f})\\
+    $F$                      & flux                                                  & Equation~(\ref{eq:the_problem:F})\\
+    $i$                      & inclination                                           & Equation~(\ref{eq:kT:beta})\\
+    $I$                      & specific intensity                                    & Equation~(\ref{eq:the_problem:Ixi})\\
+    $l$                      & spherical harmonic degree                             & \\
+    $m$                      & spherical harmonic order                              & \\
+    $\bvec{R}$               & Wigner rotation matrix                                & Equation~(\ref{eq:deconv:R})\\
+    $\bvec{s}$               & vector representation of the spectrum                 & Equation~(\ref{eq:inverse:azero})\\
+    $\Surf$                  & projected visible area of the star                    & Equation~(\ref{eq:the_problem:F})\\
+    $t$                      & time                                                  & \S\ref{sec:the_problem}\\
+    $\x$                     & Cartesian position on the sky                         & \S\ref{sec:the_problem}\\
+    $y_{lm}$                 & spherical harmonic coefficient                        & \S\ref{sec:inverse}\\
+    $\bvec{s}$               & vector of spherical harmonic coefficients             & Equation~(\ref{eq:inverse:azero})\\
+    $Y_{lm}$                 & spherical harmonic                                    & Equation~(\ref{eq:deconv:Ixi0})\\
+    %
+    %
+    $\beta$                  & relativistic parameter                                & Equation~(\ref{eq:the_problem:D})\\
+    $\delta$                 & Dirac delta function                                  & Equation~(\ref{eq:deconv:convolution})\\
+    $\kT$                    & convolution kernel basis vector                       & Equation~(\ref{eq:deconv:kT})\\
+    $\lambda$                & wavelength (in nm)                                    & \S\ref{sec:the_problem}\\
+    $\lnlam$                 & $\ln\lambda$ (observer frame)                         & \S\ref{sec:the_problem}\\
+    $\lnlam_0$               & $\ln\lambda$ (rest frame)                             & \S\ref{sec:the_problem}\\
+    $\boldsymbol{\Lambda}$   & prior covariance matrix                               & \\
+    $\ylmbasis$              & spherical harmonic basis vector                       & Equation~(\ref{eq:deconv:ylmbasis})\\
+    $\boldsymbol{\Sigma}$    & covariance matrix                                     & \\
+    $\omega$                 & angular velocity                                      & Equation~(\ref{eq:kT:beta})\\
+    %
+    %
+    $*$         & convolution                                           & Equation~(\ref{eq:deconv:convolution_def})\\
+    $\circ$     & element-wise product                                  & Equation~(\ref{eq:norm:fapprox})
+\end{longtable}
+\end{center}
+
 % Bibliography
+\clearpage
 \bibliography{bib}

### 2019-08-19 tex/ms.tex
finalllllly

@@
 \begin{align}
+    \label{eq:inverse:S}
     \setstackgap{L}{1.25\baselineskip}
@@
 \begin{align}
+    \label{eq:inverse:Y}
     \setstackgap{L}{1.25\baselineskip}
@@
 
-\section{Bells and Whistles}
-\label{sec:bells}
+\section{Further considerations}
+\label{sec:bellswhistles}
 
@@
 \subsection{Limb darkening}
-Hello.
+\label{sec:ld}
+Thus far we have avoided mention of limb darkening, whose effect
+on the observed spectrum can often be significant. A proper treatment of
+limb darkening requires solution of radiative transfer equations and
+should account for the temperature and composition gradients in the
+stellar atmosphere. However, in the spirit of data-driven inference, we 
+may simply weight the spatial component of our map by the limb darkening
+profile of the star, which can either be imposed or learned from the data.
 
@@
     \begin{longtable}{cll}
-    \caption{Notation used in this paper \xxx{mostly complete up to sec 5}} 
+    \caption{Notation used in this paper} 
     \label{tab:notation} \\
@@
     $\bvec{A_0}$             & matrix form of $\bvec{a_0}$                           & Equation~(\ref{eq:inverse:azero})\\
+    $\bvec{b}$               & flux baseline vector                                  & Equation~(\ref{eq:norm:b})\\
+    $\bvec{B}$               & block matrix representation of $\bvec{b}$             & Equation~(\ref{eq:norm:b})\\
     $c$                      & speed of light                                        & Equation~(\ref{eq:kT:beta})\\
@@
     $\bvec{s}$               & vector representation of the spectrum                 & Equation~(\ref{eq:inverse:azero})\\
+    $\bvec{S}$               & block matrix representation of $\bvec{s}$             & Equation~(\ref{eq:inverse:S})\\
     $\Surf$                  & projected visible area of the star                    & Equation~(\ref{eq:the_problem:F})\\
@@
     $y_{lm}$                 & spherical harmonic coefficient                        & \S\ref{sec:inverse}\\
-    $\bvec{s}$               & vector of spherical harmonic coefficients             & Equation~(\ref{eq:inverse:azero})\\
+    $\bvec{y}$               & vector of spherical harmonic coefficients             & Equation~(\ref{eq:inverse:azero})\\
     $Y_{lm}$                 & spherical harmonic                                    & Equation~(\ref{eq:deconv:Ixi0})\\
+    $\bvec{Y}$               & block matrix representation of $\bvec{y}$             & Equation~(\ref{eq:inverse:Y})\\
     %
@@
     $\boldsymbol{\Lambda}$   & prior covariance matrix                               & \\
+    $\boldsymbol{\mu}$       & prior mean vector                                     & \\
     $\ylmbasis$              & spherical harmonic basis vector                       & Equation~(\ref{eq:deconv:ylmbasis})\\

### 2019-08-19 scratch/twospec.py

@@ -14,6 +14,7 @@ import theano.sparse as ts
 from tqdm import tqdm
 from inspect import getmro
 import celerite
+from matplotlib.patches import Rectangle
 
 
 def is_theano(*objs):
@@ -44,56 +45,52 @@ N = dop.N
 M = dop.M
 lnlam = dop.lnlam
 lnlam_padded = dop.lnlam_padded
-B = dop._map.X(theta=dop.theta).eval()
-B = np.repeat(B, K, axis=0)
+B1 = dop._map.X(theta=dop.theta).eval()[:, 1:]
+B1 = np.repeat(B1, K, axis=0)
 
 # Get the Ylm decomposition & the baseline
 map = starry.Map(15, lazy=False)
 map.inc = 40
 
-# Generate a map, 10% level
+# Generate a spot map
 map.load("spot")
-y_true = np.array(map[:, :])
-y_true *= 0.10
+y1_true = np.array(map[1:, :])
 b_true = np.repeat(map.flux(theta=theta), K)
 img_true = map.render(projection="rect", res=res)[0]
 
 # Generate two different spectra
-s0_true = np.empty(Kp)
-s1_true = np.empty(Kp)
 sigma = 7.5e-6
-nlines = 21
-mu1 = -0.00005
-mu2 = 0.00005
-s0_true = 1 - 0.5 * np.exp(-0.5 * (lnlam_padded - mu1) ** 2 / sigma ** 2)
+nlines = 0
+mu1 = -0.00015
+mu2 = 0.00015
+s_bkg = 1 - 0.5 * np.exp(-0.5 * (lnlam_padded - mu1) ** 2 / sigma ** 2)
 for _ in range(nlines - 1):
     amp = 0.1 * np.random.random()
     mu = 2.1 * (0.5 - np.random.random()) * lnlam_padded.max()
-    s0_true -= amp * np.exp(-0.5 * (lnlam_padded - mu) ** 2 / sigma ** 2)
-s1_true = 1 - 0.5 * np.exp(-0.5 * (lnlam_padded - mu2) ** 2 / sigma ** 2)
+    s_bkg -= amp * np.exp(-0.5 * (lnlam_padded - mu) ** 2 / sigma ** 2)
+s_spot = 1 - 0.5 * np.exp(-0.5 * (lnlam_padded - mu2) ** 2 / sigma ** 2)
 for _ in range(nlines - 1):
     amp = 0.1 * np.random.random()
     mu = 2.1 * (0.5 - np.random.random()) * lnlam_padded.max()
[…]

### 2019-08-19 tex/ms.tex
twospec working beautifully

@@
 stellar atmosphere. However, in the spirit of data-driven inference, we 
-may simply weight the spatial component of our map by the limb darkening
-profile of the star, which can either be imposed or learned from the data.
+can approximate the effect of limb darkening by weighting the spatial
+component of our map by the limb darkening profile of the star, which can 
+either be imposed or learned from the data.
 

### 2019-08-20 tex/ms.tex
woot
more text

@@
         &=
-        \sum_{l=0}^\infty\sum_{m=-l}^{l} a_{lm}(\lnlam_0, t) Y_{lm}(\x)
+        \sum_{l=0}^{l_\mathrm{max}}\sum_{m=-l}^{l} a_{lm}(\lnlam_0, t) Y_{lm}(\x)
     \quad ,
@@
 %
-is the vector of spherical harmonic coefficients and
+is the vector of $N = (l_\mathrm{max} + 1)^2$ spherical harmonic coefficients and
 %
@@
 %
-is the corresponding vector of spherical harmonics. We may further
+is the corresponding vector of $N$ spherical harmonics. We may further
 decompose our expression by linearizing the time dependence of the
@@
 for some reference time $t_0$.
-For rigid body rotation, the result is exact and $\R(t)$ is the Wigner 
+For rigid body rotation, the result is exact and $\R(t)$ is the $(N \times N)$ Wigner 
 rotation matrix for real spherical harmonics 
@@
         Equation~(\ref{eq:kT:sTrecurrence}) up to spherical 
-        harmonic degree $l=10$. Rows correspond to the degree $l$ and
+        harmonic degree $l_\mathrm{max}=10$. Rows correspond to the degree $l$ and
         columns correspond to the order $m$. These functions encode
@@
 the formulae above and Equation~(\ref{eq:kT:kT}) up to spherical 
-harmonic degree $l=10$.
+harmonic degree $l_\mathrm{max}=10$.
 
@@
         The stellar surface is modeled as a spherical harmonic expansion
-        up to $l=20$, and the line shape is assumed to be the same everywhere;
+        up to $l_\mathrm{max}=20$, and the line shape is assumed to be the same everywhere;
         the spot simply downweights the local intensity at all wavelengths.
@@
     \label{eq:linear:convolution_def}
-    \bvec{g} * \bvec{h} = \bvec{G} \, \bvec{h}
-\end{align}
-%
-where $\bvec{G}$ is a Toeplitz matrix, a matrix whose diagonals
+    \bvec{g} * \bvec{h} = \bvec{T(g)} \, \bvec{h}
+\end{align}
+%
+where $\bvec{T}$ is a Toeplitz matrix, a matrix whose diagonals
 are constant from top left to bottom right. In this case, the diagonals
@@
 $L$, element $g_n$ is placed everywhere along the $k^\mathrm{th}$ diagonal 
-of $\bvec{G}$ for $k = -L / 2 + n$; all other entries of $\bvec{G}$ are 
-set to zero. Note that the matrix $\bvec{G}$ need not be square; in fact,
+of $\bvec{T}$ for $k = -L / 2 + n$; all other entries of $\bvec{T}$ are 
+set to zero. Note that the matrix $\bvec{T}$ need not be square; in fact,
 for our purposes, it is a $(K \times K')$ matrix, where $K$ is the 
@@
     \label{eq:linear:ft}
-    \bvec{f}_t
-    &=
-    \Doppler_t
+    \bvec{f}_m
+    &=
+    \Doppler_m
     \,
@@
 %
-where $\Doppler_t$ is a $(K \times N K')$ matrix constructed
+where $\Doppler_m$ is a $(K \times N K')$ matrix constructed
 by horizontally concatenating the Toeplitz matrices for each of the $N$ 
-components of the convolution kernel $\kT(\lnlam, \Dargs)$ after rotating 
-them (via $\R(t)$) to the stellar phase at time $t$. 
-%
-The $(K \times 1)$ vector $\mathbf{f}$ is the model for 
-the flux observed at each wavelength at a particular time, and the 
+components of the convolution kernel $\kT(\lnlam, \Dargs)$ 
+transformed by the rotation matrix $\bvec{R}(t)$ evaluated at time $t = t_m$:
+%
+\begin{align}
+    \label{eq:linear:Dm}
+    \Doppler_m = 
+    \begin{pmatrix}
+        \quad
+        \bvec{T}(\kT_0)
+        \quad
+        &
+        \quad
+        \bvec{T}(\kT_1)
+        \quad
+        &
+        \quad
+        \cdots
+        \quad
+        &
+        \quad
+        \bvec{T}(\kT_N)
+        \quad
+    \end{pmatrix}
+    (\bvec{R}(t_m) \otimes \bvec{I}_{K'})
+    \quad.
+\end{align}
+%
+where $\bvec{I}_{K'}$ is the $(K' \times K')$ identity matrix and
+$\otimes$ denotes the Kronecker product.
+%
+The $(K \times 1)$ vector $\mathbf{f}_m$ is the model for 
+the flux observed at each wavelength at time $t = t_m$, and the 
 $(N K' \times 1)$ vector $\azero$ is the vector representation of the
@@
 epochs, corresponding to different rotational phases of the star. 
-If we concatenate all $M$ spectra $\bvec{f}_t$ into the $(MK \times 1)$ 
+If we concatenate all $M$ spectra $\bvec{f}_m$ into the $(MK \times 1)$ 
 vector $\bvec{f}$, we may write
@@
 where $\Doppler$ is the full $(MK \times N K')$ Doppler design matrix, 
-constructed by vertically concatenating the individual matrices $\Doppler_t$.
-This equation represents the full linearization of the problem, where we
+constructed by vertically concatenating the individual matrices $\Doppler_m$:
+%
+%
+\begin{align}
+    \label{eq:linear:D}
+    \Doppler =
+    \begin{pmatrix}
+        \Doppler_0
+        \\
+        \Doppler_1
+        \\
+        \cdots 
+        \\
+        \Doppler_m
+    \end{pmatrix}
+    \quad.
+\end{align}
+%
+%
+Equation~(\ref{eq:linear:f}) represents the full linearization of the problem, 
+where we
 have expressed the quantity we can observe, $\bvec{f}$, as a linear
@@
 component of our map by the limb darkening profile of the star, which can 
-either be imposed or learned from the data.
-
-\subsection{Multiple spectra}
-Hello.
+either be imposed or learned from the data. For a polynomial limb darkening
+law of the form
+%
+\begin{align}
+    \label{eq:ld:I}
+    \frac{I(\mu)}{I(\mu = 1)} = 1 - \sum_{n=1}^{n_\mathrm{max}} u_n(1 - \mu)^n
+    \quad,
+\end{align}
+%
+where $\mu = z = \sqrt{1 - x^2 - y^2}$ is the radial coordinate on the 
+projected disk and $u_n$ is a limb darkening coefficient, the effect of 
+limb darkening on the stellar map can be expressed exactly as a linear 
+operation on the spherical harmonic coefficient vector 
+\citep{Luger2019,Agol2019}. This can be understood by noting that all terms
+in Equation~(\ref{eq:ld:I}) are strictly polynomials in $x$, $y$, and $z$,
+all of which can be expressed exactly as sums of spherical harmonics
+\citep{Luger2019}. When weighting the surface intensity by the limb darkening
+profile, the resulting intensity is simply a product of spherical harmonics,
+which is itself a sum of spherical harmonics. Given a limb darkening law
+of degree $n_\mathrm{max}$, we can always construct a matrix $\bvec{L}$
+that transforms a spherical harmonic vector $\bvec{y}$ of degree
+$l_\mathrm{max}$ to a limb-darkened spherical harmonic vector $\bvec{y'}$
+of degree $l_\mathrm{max} + n_\mathrm{max}$. As an example, consider 
+a map of degree $l_\mathrm{max} = 1$ and the linear limb darkening law
+($n_\mathrm{max} = 1$).
+The transformation matrix from $\bvec{y}$ to $\bvec{y'}$ is
+%
+\begin{align}
+    \label{eq:ld:L}
+    \setstackgap{L}{1.5\baselineskip}
+    \bvec{L} =
+        \frac{1}{1 - \frac{u_1}{3}}
+        \begin{pmatrix}
+        \quadquad1-u_1\quadquad & 0                         & \frac{u_1}{\sqrt{3}}      & 0                         \\
+        0                       & \quadquad1-u_1\quadquad   & 0                         & 0                         \\
+        \frac{u_1}{\sqrt{3}}    & 0                         & \quadquad1-u_1\quadquad   & 0                         \\
+        0                       & 0                         & 0                         & \quadquad1-u_1\quadquad   \\
+        0                       & 0                         & 0                         & 0                         \\
+        0                       & \frac{u_1}{\sqrt{5}}      & 0                         & 0                         \\
+        0                       & 0                         & \frac{2u_1}{\sqrt{15}}    & 0                         \\
+        0                       & 0                         & 0                         & \frac{u_1}{\sqrt{5}}      \\
+        0                       & 0                         & 0                         & 0          
+        \end{pmatrix}
+        \quad.
+\end{align}
+%
+The columns of $\bvec{L}$ are constructed from the coefficient vectors of
+each transformed spherical harmonic, which are in turn computed by 
+multiplying each spherical harmonic by the spherical harmonic decomposition 
+of the particular limb darkening law.
+Figure~\ref{fig:ld} shows this transformation with $u_1 = 1$ applied to each
+of the first four spherical harmonics.
+%
+\begin{figure}[t!]
+    \begin{centering}
+    \includegraphics[width=0.6\linewidth]{figures/ld.pdf}
+    \oscaption{ld}{%
+        Illustration of the limb darkening transformation given by
+        Equation~(\ref{eq:ld:L}) for a linear limb darkening law with
+        $u_1 = 1$. Each row shows a spherical harmonic before
+        (left) and after (right) transformation by $\bvec{L}$.
+        \label{fig:ld}
+    }
+    \end{centering}
+\end{figure}
+%
+
+Now, to incorporate limb darkening into our model, we must modify how we
+compute the Doppler design matrix $\Doppler$
+(Equation~\ref{eq:linear:D} and Figure~\ref{fig:linalg}). Recall that
+this matrix is constructed by vertically stacking the submatrices 
+$\Doppler_m$ given by Equation~(\ref{eq:linear:Dm}), which we now compute
+as
+%
+\begin{align}
+    \label{eq:ld:Dm}
+    \Doppler_m =
+    \begin{pmatrix}
+        \quad
+        \bvec{T}(\kT_0)
+        \quad
+        &
+        \quad
+        \bvec{T}(\kT_1)
+        \quad
+        &
+        \quad
+        \cdots
+        \quad
+        &
+        \quad
+        \bvec{T}(\kT_{N'})
+        \quad
+    \end{pmatrix}
+    (\bvec{L} \, \bvec{R}(t_m) \otimes \bvec{I}_{K'})
+    \quad,
+\end{align}
+%
+where we have replaced the rotation matrix $\bvec{R}(t_m)$ with
+the linear transformation $\bvec{L}\,\bvec{R}(t_m)$, which first rotates the
+input spherical harmonic coefficient vector to the correct phase then
+limb darkens it. Note also that the terms in the convolution kernel $\kT$
+are now indexed from 0 to $N' = (l_\mathrm{max} + n_\mathrm{max} + 1)^2$,
+where $n_\mathrm{max}$ is the degree of the limb darkening operator.
+
+Note that it is also possible to model wavelength-dependent limb darkening
+in this fashion. The procedure is similar, except that the limb darkening
+coefficients $u_n$ are now functions of $\lnlam$, and each element of the
+matrix $\bvec{L}$ is now a vector of length $K'$. The submatrices
+$\Doppler_m$ may be written as
+%
+\begin{align}
+    \label{eq:ld:Dmwav}
+    \resizebox{0.91\textwidth}{!}{
+    $
+    \Doppler_m =
+    \begin{pmatrix}
+        \quad
+        \bvec{T}(\kT_0)
+        \quad
+        &
+        \quad
+        \bvec{T}(\kT_1)
+        \quad
+        &
+        \quad
+        \cdots
+        \quad
+        &
+        \quad
+        \bvec{T}(\kT_{N'})
+        \quad
+    \end{pmatrix}
+    \begin{pmatrix}
+        \mathrm{diag}(\bvec{L}_{0,0})
+        &
+        \mathrm{diag}(\bvec{L}_{0,1})
+        &
+        \cdots
+        &
+        \mathrm{diag}(\bvec{L}_{0,N})
+        \\
+        \mathrm{diag}(\bvec{L}_{1,0})
+        &
+        \mathrm{diag}(\bvec{L}_{1,1})
+        &
+        \cdots
+        &
+        \mathrm{diag}(\bvec{L}_{1,N})
+        \\
+        \cdots
+        &
+        \cdots
+        &
+        \ddots
+        &
+        \cdots
+        \\
+        \mathrm{diag}(\bvec{L}_{N',0})
+        &
+        \mathrm{diag}(\bvec{L}_{N',1})
+        &
+        \cdots
+        &
+        \mathrm{diag}(\bvec{L}_{N',N})
+    \end{pmatrix}
+    (\bvec{R}(t_m) \otimes \bvec{I}_{K'})
+    $
+    }
+    \quad,
+\end{align}
+%
+where $\mathrm{diag}(\bvec{v})$ denotes the $(K' \times K')$ diagonal matrix
+constructed by placing the vector $\bvec{v}$ along the main diagonal.
+
+\subsection{Multiple spectral components}
+%
+In our discussion so far we have focused on the particular case where the
+spectral/spatial decomposition of the stellar surface can be expressed as 
+the outer product of two vectors (Equation~\ref{eq:inverse:azero}). As we
+mentioned previously, this corresponds to the case where the spectrum is
+constant across the surface of the star except for a spatially-variable 
+amplitude: i.e., spots have the same spectrum as the rest of the star, but
+emit less flux overall. However, most of the formalism developed here also
+applies to the more general case where the spectrum at a particular point
+on the surface of the star is a linear combination of $P$
+
+\begin{align}
+    \azero &= \mathrm{vec}\left( \bvec{A_0} \right) \nonumber \\
+           &= \mathrm{vec}\left( \bvec{S} \, \bvec{Y}^\top \right) \quad,
+\end{align}
 
@@
 
+\begin{figure}[t!]
+    \begin{centering}
+    \includegraphics[width=\linewidth]{figures/twospec.pdf}
+    \oscaption{twospec}{%
+        Learning two spectra simultaneously.
+        \label{fig:twospec}
+    }
+    \end{centering}
+\end{figure}
+
 \section{Performance}
@@
     \begin{longtable}{cll}
-    \caption{Notation used in this paper} 
+    \caption{Common notation used in this paper} 
     \label{tab:notation} \\
@@
     \multicolumn{1}{c}{\textbf{Reference}} \\
+    \midrule
+    \endfirsthead
+    %
+    \multicolumn{3}{c}%
+    {{\bfseries \tablename\ \thetable{}}. (continued from previous page)} \\[0.5em]
     \toprule
+    \multicolumn{1}{c}{\textbf{Symbol}} &
+    \multicolumn{1}{c}{\textbf{Definition}} &
+    \multicolumn{1}{c}{\textbf{Reference}} \\
+    \midrule
     \endhead
+    \bottomrule
     %
@@
     \endlastfoot
+    %
+    \midrule
+    \multicolumn{3}{c}{\emph{Dimensions}}\\
+    \midrule
+    %
+    $K$                      & \# of wavelength bins in the observed spectrum        & \\
+    $K'$                     & \# of wavelength bins in the latent spectrum          & \\
+    $M$                      & \# of epochs observed                                 & \\
+    $N$                      & \# of spherical harmonic coefficients                 & \\
+    $N'$                     & \# of spherical harmonic coefficients after limb darkening            & \\
+    $W$                      & \# of wavelength bins in the convolution kernel       & \\
+    %
+    \midrule
+    \multicolumn{3}{c}{\emph{Variables}}\\
+    \midrule
     %
@@
     $I$                      & specific intensity                                    & Equation~(\ref{eq:the_problem:Ixi})\\
+    $\bvec{I}$               & identity matrix                                       & \\
     $l$                      & spherical harmonic degree                             & \\
+    $\bvec{L}$               & limb darkening operator                               & Equation~(\ref{eq:ld:L})\\
     $m$                      & spherical harmonic order                              & \\
@@
     $t$                      & time                                                  & \S\ref{sec:the_problem}\\
+    $u$                      & limb darkening coefficient                            & \S\ref{sec:ld}\\
     $\x$                     & Cartesian position on the sky                         & \S\ref{sec:the_problem}\\
@@
     %
+    \pagebreak
+    \midrule
+    \multicolumn{3}{c}{\emph{Variables (Greek)}}\\
+    \midrule
     %
@@
     %
-    %
+    \midrule
+    \multicolumn{3}{c}{\emph{Operators}}\\
+    \midrule
+    %
+    $\mathrm{diag}$          & diagonal matricization                                & Equation~(\ref{eq:ld:Dmwav})\\
+    $\mathrm{vec}$           & vectorization                                         & Equation~(\ref{eq:inverse:azero})\\
     $*$                      & convolution                                           & Equation~(\ref{eq:deconv:convolution_def})\\
-    $\circ$     & element-wise product                                  & Equation~(\ref{eq:norm:fapprox})
+    $\circ$                  & element-wise product                                  & Equation~(\ref{eq:norm:fapprox})\\
+    $\otimes$                & Kronecker product                                     & Equation~(\ref{eq:linear:Dm})\\
+    $\ceil*{\,}$             & ceiling                                               & Equation~(\ref{eq:kT:lm})\\
+    $\floor*{\,}$            & floor                                                 & Equation~(\ref{eq:kT:lm})
 \end{longtable}

### 2019-08-20 tex/ms.tex
more text, more figs

@@
 \subsection{Multiple spectral components}
+\label{sec:eigen}
 %
@@
 applies to the more general case where the spectrum at a particular point
-on the surface of the star is a linear combination of $P$
-
-\begin{align}
-    \azero &= \mathrm{vec}\left( \bvec{A_0} \right) \nonumber \\
-           &= \mathrm{vec}\left( \bvec{S} \, \bvec{Y}^\top \right) \quad,
-\end{align}
+on the surface of the star is a linear combination of several different
+spectral components. In this case, the map vector $\azero$
+may be written as the sum over $J$ spectra $\bvec{s}_j$, each of which is dotted into
+a different vector of spherical harmonic coefficients $\bvec{y}_j^\top$:
+%
+\begin{align}
+    \label{eq:eigen:azero}
+    \azero 
+        &= 
+        \sum_{j=0}^{J-1}\mathrm{vec}\left( \bvec{s}_j \, \bvec{y}_j^\top \right) \\
+        &=
+        \mathrm{vec}\left( \boldsymbol{\mathbb{S}} \, \boldsymbol{\mathbb{Y}}^\top \right) \quad,
+\end{align}
+%
+where $\boldsymbol{\mathbb{S}}$ is the $(K' \times J)$ matrix whose columns are
+the $J$ spectral components and $\boldsymbol{\mathbb{Y}}^\top$ is the
+$(J \times N)$ matrix whose rows are the corresponding $J$ spherical harmonic
+coefficient vectors.
+
+The model remains linear in both the spherical harmonic coefficients and the
+spectral components, and the procedures outlined in \S\ref{sec:inverse} may
+still be followed to solve the inverse problem, provided we unroll these
+matrices into vectors, letting
+$\mathbf{s} = \mathrm{vec}(\boldsymbol{\mathbb{S}})$
+and
+$\mathbf{y} = \mathrm{vec}(\boldsymbol{\mathbb{Y}})$.
+A detailed discussion of this general case is deferred to future work,
+but we present an example of a two-component stellar spectrum in the
+examples section below.
 
@@
 
+\begin{figure}[h!]
+    \begin{centering}
+    \includegraphics[width=0.98\linewidth]{figures/snr.pdf}
+    \oscaption{snr}{%
+        Recovered \spot map as a function of SNR per resolution element.
+        \label{fig:snr}
+    }
+    \end{centering}
+\end{figure}
+
 \begin{figure}[t!]
@@
 \label{sec:performance}
-
+%
+\xxx{In progress...}
 Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires 
@@
 %
+\xxx{In progress...}
 Differential rotation and convective blueshift.
@@
     %
+    $J$                      & \# of spectral components                             & \\
     $K$                      & \# of wavelength bins in the observed spectrum        & \\

### 2019-08-20 tex/ms.tex
fixing blas

@@
     \begin{centering}
+    \oscaption{spotstar}{%
+        \xxx{Figure here with the problem setup.}
+        \label{fig:spotstar}
+    }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[p!]
+    \begin{centering}
     \includegraphics[width=0.49\linewidth]{figures/spot_y1_timeseries.pdf}
@@
     %
-    $J$                      & \# of spectral components                             & \\
-    $K$                      & \# of wavelength bins in the observed spectrum        & \\
-    $K'$                     & \# of wavelength bins in the latent spectrum          & \\
-    $M$                      & \# of epochs observed                                 & \\
-    $N$                      & \# of spherical harmonic coefficients                 & \\
-    $N'$                     & \# of spherical harmonic coefficients after limb darkening            & \\
-    $W$                      & \# of wavelength bins in the convolution kernel       & \\
+    $J$                      & \# of spectral components                             & \S\ref{sec:eigen} \\
+    $K$                      & \# of wavelength bins in the observed spectrum        & \S\ref{sec:linear} \\
+    $K'$                     & \# of wavelength bins in the latent spectrum          & \S\ref{sec:linear}\\
+    $M$                      & \# of epochs observed                                 & \S\ref{sec:linear}\\
+    $N$                      & \# of spherical harmonic coefficients                 & \S\ref{sec:linear}\\
+    $N'$                     & \# of spherical harmonic coefficients after limb darkening & \S\ref{sec:ld}\\
+    $W$                      & \# of wavelength bins in the convolution kernel       & \S\ref{sec:linear}\\
     %
@@
     $\bvec{S}$               & block matrix representation of $\bvec{s}$             & Equation~(\ref{eq:inverse:S})\\
+    $\boldsymbol{\mathbb{S}}$& matrix of $J$ spectral components                     & Equation~(\ref{eq:eigen:azero})\\
     $\Surf$                  & projected visible area of the star                    & Equation~(\ref{eq:the_problem:F})\\
@@
     $\bvec{Y}$               & block matrix representation of $\bvec{y}$             & Equation~(\ref{eq:inverse:Y})\\
+    $\boldsymbol{\mathbb{Y}}$& matrix of $J$ spherical harmonic components           & Equation~(\ref{eq:eigen:azero})\\
     %

### 2019-08-20 paparazzi/doppler.py

@@ -61,10 +61,10 @@ class Doppler(object):
         baseline_sig=0.1,
     ):
         # Stellar params
+        self._udeg = len(u)
         self.ydeg = ydeg
         self.inc = inc
         self.vsini = vsini
-        self._udeg = len(u)
         self.u = u
 
         # Reset!
@@ -112,14 +112,19 @@ class Doppler(object):
         assert (
             len(value.shape) == 1
         ), "Wavelength-dependent limb darkening not yet supported."
-        assert len(value) == self._udeg, (
-            "Incorrect vector length. To change the limb darkening degree, "
-            "you'll have to re-instantiate the class."
-        )
         self._u = value
+
+        # Did the degree of limb darkening change?
+        if len(self._u) != self._udeg:
+            self._udeg = len(self._u)
+            # Force the re-instantiation of the internal map
+            self.ydeg = self._ydeg
+
         # Compute the limb darkening operator
-        F = self._map.ops.F(self._u, [np.pi])
-        self._L = ts.dot(ts.dot(self._map.ops.A1Inv, F), self._map.ops.A1)
+        if self._udeg > 0:
+            map_ld = starry.Map(ydeg=self._ydeg, udeg=self._udeg)
+            F = map_ld.ops.F(np.append([-1.0], self._u), [np.pi])
+            self._L = ts.dot(ts.dot(map_ld.ops.A1Inv, F), map_ld.ops.A1).eval()
 
     @property
     def ydeg(self):
@@ -134,9 +139,16 @@ class Doppler(object):
         # Degree of the Ylm expansion
         self._ydeg = value
 
-        # Grab the `A1` matrix from `starry`
-        self._map = starry.Map(value)
-        self._A1T = self._map.ops.A1.eval().T
+        # Instantiate the internal map
+        self._map = starry.Map(self._ydeg)
+
+        # Compute the `A1` matrix
+        if self._udeg > 0:
+            # We need an augmented version if there's LD!
+            map_ld = starry.Map(self._ydeg + self._udeg)
+            self._A1T = map_ld.ops.A1.eval().T
+        else:
+            self._A1T = self._map.ops.A1.eval().T
 
         # Grab the rotation matrix op
         self._R = self._map.ops.R
@@ -250,7 +262,15 @@ class Doppler(object):
         The number of spherical harmonic coefficients.
 
         """
-        return (self.ydeg + 1) ** 2
[…]

### 2019-08-21 tex/gitlinks.tex
timing figure generation

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/60dfb1cf40302ddb3818411b0925c910a2f52625/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/60dfb1cf40302ddb3818411b0925c910a2f52625/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/60dfb1cf40302ddb3818411b0925c910a2f52625/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/bc985edc746c392492307b3c3f2ebfe9f0fac247/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/bc985edc746c392492307b3c3f2ebfe9f0fac247/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/bc985edc746c392492307b3c3f2ebfe9f0fac247/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\cilink}[1]{\href{https://dev.azure.com/user/repo/_build}{#1}}

### 2019-08-21 tex/figures/inclinations.py

@@ -2,10 +2,6 @@
 Investigate how our recovered map varies with the
 stellar inclination (assumed to be known exactly).
 
-NOTE: I get the same results (qualitatively) whether
-or not the baseline is assumed to be known, which
-is great!
-
 """
 import paparazzi as pp
 import numpy as np
@@ -14,8 +10,7 @@ import matplotlib.pyplot as plt
 
 # Instantiate
 res = 300
-known_baseline = False
-dop = pp.Doppler(ydeg=15)
+dop = pp.Doppler(ydeg=15, u=[0.5, 0.25])
 
 # Velocity is computed such that v * sin(40 deg) = 40 km / s
 # so that we can compare directly to Vogt et al. (1987)
@@ -40,14 +35,9 @@ for i, inc in enumerate(incs):
     np.random.seed(13)
     dop.generate_data(ferr=1e-4)
 
-    # Assume we know the baseline?
-    if known_baseline:
-        dop.y1 = dop.y1_true
-        baseline = dop.baseline()
-        T = 1.0
-    else:
-        baseline = None
-        T = 100.0
+    # Assume we don't know the baseline
+    baseline = None
+    T = 100.0
 
     # Reset all coefficients
     dop.s = dop.s_true

### 2019-08-21 tex/figures/linalg.py

@@ -168,6 +168,7 @@ ntheta = 11
 inc = 40.0
 vsini = 80.0
 nlam = 121
+u = []
 
 #
 # Compute stuff!
@@ -175,7 +176,7 @@ nlam = 121
 
 # Compute the g-functions and the corresponding Toeplitz matrices
 lnlam = np.linspace(-6e-4, 6e-4, nlam)
-doppler = pp.Doppler(ydeg=ydeg, vsini=vsini, inc=inc)
+doppler = pp.Doppler(ydeg=ydeg, vsini=vsini, inc=inc, u=u)
 doppler._set_lnlam(lnlam)
 kT = doppler.kT()
 T = [None for n in range(doppler.N)]

### 2019-08-21 tex/figures/spot_y1bs.py

@@ -39,7 +39,7 @@ else:
     lr = 2e-3
 
 # Generate data
-dop = pp.Doppler(ydeg=15)
+dop = pp.Doppler(ydeg=15, u=[0.5, 0.25])
 dop.generate_data(ferr=ferr)
 
 # Reset all coefficients

### 2019-08-21 tex/gitlinks.tex
gen paper only if tag present

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/bc985edc746c392492307b3c3f2ebfe9f0fac247/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/bc985edc746c392492307b3c3f2ebfe9f0fac247/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/bc985edc746c392492307b3c3f2ebfe9f0fac247/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/3bca8febf1e8738da63bacbc3959e6442e52272c/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/3bca8febf1e8738da63bacbc3959e6442e52272c/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/3bca8febf1e8738da63bacbc3959e6442e52272c/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
 \newcommand{\cilink}[1]{\href{https://dev.azure.com/user/repo/_build}{#1}}

### 2019-08-21 tex/ms.tex
timing figure generation
gen paper only if tag present

@@
 
+\begin{abstract}
+We derive a closed form, analytic solution to the problem of Doppler imaging
+of stellar surfaces in the limit of negligible differential rotation and
+convective blueshift. The model for the observed spectrum is linear in 
+both the unbroadened spectrum and the surface map of the star, provided the
+latter is expressed as a sum of spherical harmonics. As a result, the 
+posterior distributions of both the unbroadened spectrum and the stellar map
+conditioned on each other have a closed form, analytic solution that is 
+computationally trivial to evaluate. When neither the unbroadened spectrum
+nor the stellar map is known a priori, the global optimum can usually be
+found via a fast iterative approach that also yields a lower bound on the
+uncertainties.
+%
+\href{https://github.com/rodluger/paparazzi}{\color{linkcolor}\faGithub}
+\figtime{allfigures}
+\end{abstract}
+
 %
@@
 Check out \citet{Luger2019} and \citet{Bedell2019} and stuff.
+%
+All figures in this paper include links {\color{linkcolor}\faFileCodeO}
+to the \Python scripts that generated them. These figures were auto-generated
+using the 
+\href{https://dev.azure.com/rodluger/paparazzi/_build}{Azure Pipelines}
+continuous integration (CI) service, and
+icons next to each caption \figtimebox{XXmYYs} indicate the runtime
+for each figure. The total runtime for the generation of this paper is
+displayed above, at the end of the abstract.
 
@@
     \includegraphics[width=\linewidth]{figures/kT.pdf}
-    \oscaption{g}{%
+    \oscaption{kT}{%
         The Doppler $\kT$ basis for a rigidly rotating star
@@
 to 71,000 (dark grey), the numerical solution approaches the solution
-obtained using our approach. \xxx{Understand---and comment on---the fundamental
-differences between a discrete linear convolution and traditional linear 
-interpolation. Should we expect the numerical solution to actually \emph{converge}
-to the \starry solution, or is the way the two are interpolating fundamentally
-different?}
+obtained using our approach.
+
+%Understand---and comment on---the fundamental
+%differences between a discrete linear convolution and traditional linear 
+%interpolation. Should we expect the numerical solution to actually \emph{converge}
+%to the \starry solution, or is the way the two are interpolating fundamentally
+%different?
 
@@
     \begin{centering}
-    \oscaption{spotstar}{%
-        \xxx{Figure here with the problem setup.}
-        \label{fig:spotstar}
+    \includegraphics[width=0.85\linewidth]{figures/spot_setup.pdf}
+    \oscaption{spot_setup}{%
+        Setup for the \spot problem.
+        \label{fig:spot_setup}
     }

### 2019-08-22 tex/gitlinks.tex
increased line width to match Vogt1987

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/3bca8febf1e8738da63bacbc3959e6442e52272c/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/3bca8febf1e8738da63bacbc3959e6442e52272c/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/3bca8febf1e8738da63bacbc3959e6442e52272c/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/076a0d29804b1875a480b0fd74a7ea6738368263/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/076a0d29804b1875a480b0fd74a7ea6738368263/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/076a0d29804b1875a480b0fd74a7ea6738368263/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
 \newcommand{\cilink}[1]{\href{https://dev.azure.com/user/repo/_build}{#1}}

### 2019-08-22 tex/ms.tex
increased line width to match Vogt1987

@@
 \input{cortex}
-
-\newcommand{\R}{\bvec{R}}
-\newcommand{\AOne}{\bvec{A_1}}
-\newcommand{\alm}{\bvec{a}}
-\newcommand{\x}{\bvec{x}}
-
-\newcommand{\D}{D}
-\newcommand{\Doppler}{\bvec{D}}
-\newcommand{\Surf}{\mathcal{S}}
-\newcommand{\Curve}{\mathcal{C}}
-\newcommand{\Dargs}{\bvec{d}}
-\newcommand{\lmax}{\ensuremath{l_\mathrm{max}}}
-\newcommand{\spot}{\texttt{SPOT}\xspace}
-
-\newcommand{\kT}{\boldsymbol{\kappa}^\top}
-\newcommand{\rhoT}{\boldsymbol{\rho}^\top}
-\newcommand{\ylmbasis}{\boldsymbol{\psi}^\top}
-\newcommand{\pbasis}{\boldsymbol{\phi}^\top}
-\newcommand{\pbasisn}{\ensuremath{\phi_n}}
-
-\newcommand{\azero}{\ensuremath{\bvec{a_0}}}
 
@@
 uncertainties.
+\xxx{%
+Data-driven modeling at its finest $\cdot$ %
+Works on blended lines $\cdot$ %
+Uses the whole spectrum $\cdot$ %
+Uncertainties FTW $\cdot$ %
+Probably works on slow rotators $\cdot$ %
+Differentiable! $\cdot$ %
+Fast! $\cdot$ %
+Use in MCMC to marginalize over inclination and stuff $\cdot$ %
+}
 %
 \href{https://github.com/rodluger/paparazzi}{\color{linkcolor}\faGithub}
-\figtime{allfigures}
 \end{abstract}
@@
 %
-Check out \citet{Luger2019} and \citet{Bedell2019} and stuff.
-%
+\xxx{Check out \citet{Luger2019} and \citet{Bedell2019} and stuff.}
+
+%
+
+The paper is organized as follows: in \S\ref{sec:the_problem}~and~%
+\S\ref{sec:the_solution} we introduce the math behind the Doppler imaging
+problem and derive a closed form expression for the model. In
+\S\ref{sec:linear},~\S\ref{sec:inverse},~and~\S\ref{sec:bellswhistles} 
+we demonstrate how to re-express 
+the model as a linear operation on the input spectrum and stellar map and
+derive closed form expressions for the two conditioned on the data and priors.
+In \S\ref{sec:spotstar} we apply our techniques to a mock problem. We
+further discuss and summarize our results in
+\S\ref{sec:discussion}~and~\S\ref{sec:conclusions}. Finally, auxiliary
+derivations are presented in the Appendix.
+
+%
+
 All figures in this paper include links {\color{linkcolor}\faFileCodeO}
-to the \Python scripts that generated them. These figures were auto-generated
+to the \Python scripts that generated them. The figures were auto-generated
 using the 
 \href{https://dev.azure.com/rodluger/paparazzi/_build}{Azure Pipelines}
-continuous integration (CI) service, and
-icons next to each caption \figtimebox{XXmYYs} indicate the runtime
-for each figure. The total runtime for the generation of this paper is
-displayed above, at the end of the abstract.
+continuous integration (CI) service, running on
+a two-core 2.3 GHz \texttt{Standard\_DS2\_v2} virtual machine with 6 GiB physical memory.
+% https://docs.microsoft.com/en-us/azure/virtual-machines/windows/sizes-general#dsv2-series
+We also include icons next to each caption \figtimebox{XXmYYs} that
+indicate the total CPU time taken to generate each figure.
 
@@
 intensity observed 
-at log wavelength $\lnlam \equiv \ln\lambda$ and at sky-projected 
+at log wavelength $\lnlam \equiv \ln\nicefrac{\lambda}{\lambda_\mathrm{r}}$ 
+and at sky-projected 
 Cartesian position $\x = (x, y, z)$ on the surface of the 
 star at time $t$, where
-$\Dargs$ is a set of arbitrary parameters of the Doppler field.
+$\Dargs$ is a set of arbitrary parameters of the Doppler field
+and $\lambda_\mathrm{r}$ is a reference wavelength.
 We may express this intensity as
@@
 \section{The Solution}
+\label{sec:the_solution}
 
@@
 
-\subsection{Solution for the intensity}
+\subsection{Solution for the map}
 \label{sec:solve_y}
@@
 \label{sec:bellswhistles}
+
+Before we demonstrate our formalism in practice, we consider three
+modifications to our model that are often required when modeling real
+data. Below we discuss what to do when the relative brightness of the
+star across different observations is unknown (\S\ref{sec:norm}), how
+to account for the effects of limb darkening (\S\ref{sec:ld}), and how
+to model stars whose local spectra differ within and outside of starspots
+(\S\ref{sec:eigen}).
 
@@
 but we present an example of a two-component stellar spectrum in the
-examples section below.
-
-\section{The SPOT star}
+following section.
+
+\section{Application to a spotted star}
 \label{sec:spotstar}
 
-\cite{Vogt1987}
-
-\begin{figure}[p!]
+In this section we apply the formalism developed in \S\ref{sec:inverse}
+and \S\ref{sec:bellswhistles} to a synthetic dataset of a rapidly
+rotating spotted star. This section is motivated by the
+examples in \cite{Vogt1987}, who generated rotationally-broadened spectra
+of a rapidly-rotating star with the letters ``VOGT'' painted across 
+the northern hemisphere. In that paper, the authors
+generated synthetic line profiles of the Fe I 
+$\lambda 6430$ absorption line with equivalent width $W \approx 10$~km/s
+and from these computed rotationally broadened spectra for a star at an 
+inclination $i=40^\circ$ rotating at projected velocity $v\sin i = 40$~km/s.
+The spectra were computed at 16 equally spaced rotational phases and
+downsampled to 32 wavelength bins per epoch, for a total of 512 data
+points.
+
+We generated our spectrum at high resolution 
+($R \equiv \frac{\lambda}{\Delta\lambda} = 300,000$)
+centered at a reference wavelength $\lambda_\mathrm{r} = 6430$ nm.
+The spectrum consists of a Gaussian absorption line in log-wavelength
+($\lnlam$) space with amplitude $0.5$ and standard deviation 
+$\sigma_{\lnlam} = 1.4\times 10^{-5}$. This corresponds to a FWHM of about
+$2.355~\sigma_{\lnlam}~\lambda_\mathrm{r}~\approx~0.2$ nm or, in velocity space,
+$2.355~\sigma_{\lnlam}~c~\approx~10$ km/s, equal to the value used in
+\citet{Vogt1987}. Unlike \citet{Vogt1987}, we add 20 additional small
+absorption lines at random positions throughout the spectrum, all of 
+the same FWHM but of varying depths, including some line blends. In total,
+our spectrum consists of $K = 201$ log-wavelength bins in the range
+$-3.3\times 10^{-4} < \lnlam < 3.3\times 10^{-4}$ plus an additional
+%
+\begin{align}
+    W - 1 &= \frac{40~\mathrm{km/s}}{c} \frac{201}{3.3 \times 10^{-4}} - 1 \nonumber \\
+          &= 80
+\end{align}
+%
+log-wavelength bins of padding (40 on either side) to eliminate edge
+effects due to the convolution. As in \citet{Vogt1987},
+we assume a projected velocity of $v\sin i = 40$ km/s and an inclination
+$i = 40^\circ$.
+
+% Our default SNR is about 75.
+
+Recover images with an effective resolution of $12^\circ$.
+
+\begin{figure}[t!]
     \begin{centering} 
@@
     \oscaption{spot_setup}{%
-        Setup for the \spot problem.
+        The basic setup for the \spot problem. We compute the 
+        $l_\mathrm{max} = 15$ spherical harmonic expansion of 
+        a map where the word ``SPOT'' has been placed across the northern 
+        hemisphere (top left). Each point on the surface is
+        given the same spectrum, composed of a sum of synthetic 
+        Gaussian absorption lines (top right). The specific intensity
+        at each point on the surface is equal to this spectrum weighted
+        by the intensity of the map, which is close to zero within the
+        spot (point labeled \texttt{B}) and close ot unity 
+        outside the spot (point labeled \texttt{A}).
+        %
+        To generate the synthetic dataset, the star is inclined at
+        $40^\circ$ with respect to the line of sight and the disk-integrated
+        spectrum is computed at 16 equally-spaced phases between
+        $-180^\circ$ and $180^\circ$ (lower panel).
+        %
         \label{fig:spot_setup}
@@
     \oscaption{spot_y1}{%
-        Solution to the \spot problem at high SNR when both 
+        The solution to the \spot problem at high SNR when both 
         the rest frame spectrum and the baseline are known.
+        The panel on the left shows the inferred map at each of the 16
+        epochs, alongside the observed spectrum (black points) and the
+        best-fit model (orange lines). The rectangular projection of the
+        original map is shown at the top right; the inferred map is
+        displayed below it. The bottom panel shows the posterior uncertainty
+        as a function of latitude and longitude, ranging from close to zero
+        in the northern hemisphere to $\sigma_\mathrm{prior} \approx 10\%$
+        below a latitude of $-30^\circ$. The latter is the uncertainty
+        associated with our particular choice of prior, as the southernmost
+        latitudes of the star are never visible to the observer.
         \label{fig:spot_y1}
@@
         Similar to Figure~\ref{fig:spot_y1}, but assuming the baseline
-        is not known.
+        is not known. The panel at the bottom left shows the true baseline
+        (blue) and the inferred baseline (orange), along with its $1\sigma$
+        uncertainty. The large offset between the two highlights one of the
+        fundamental degeneracies of the problem: since most of the southern
+        hemisphere of the star is never visible, the coefficient of the
+        $Y_{1,-1}$
+        (\raisebox{-0.2em}{\includegraphics[width=1em]{figures/Y1m1.pdf}})
+        spherical harmonic is not constrained by the data, resulting in 
+        an unknowable additive offset in the baseline.
+        This effect can be seen also in (\emph{a}) the inferred map, 
+        where the background 
+        intensity in the northern hemisphere is significantly larger than 
+        that in the southern hemisphere, and (\emph{b}) the spherical
+        harmonic coefficients (bottom right), where a large discrepancy is
+        visible between the true and inferred values of the first two
+        coefficients.
         \label{fig:spot_y1b}
@@
         information about either the spectrum, the baseline, or the map
-        coefficients.
+        coefficients. The bottommost panel now shows the true rest frame
+        spectrum (blue line), the initial guess based on a deconvolution
+        (dotted orange line), and the inferred spectrum (orange line, with
+        shaded $1\sigma$ uncertainty). The grey regions indicate wavelength
+        regions outside the observation window, but whose features still
+        contribute to the observed spectrum due to rotational broadening.
         \label{fig:spot_y1bs}
@@
 
-\begin{figure}[h!]
+\begin{figure}[p!]
     \begin{centering}
@@
     \oscaption{inclinations}{%
-        Recovered \spot map as a function of inclination.
+        Recovered \spot map as a function of stellar inclination. The
+        rest frame spectrum is assumed to be known exactly, but the
+        baseline is not. At very low inclinations, the small
+        projected velocities begin to degrade the spatial resolution of
+        the inferred map, while at inclinations close to $90^\circ$ there
+        is a degeneracy between the northern and southern hemispheres.
         \label{fig:inclinations}
@@
         Recovered \spot map as a function of SNR per resolution element.
+        The quality of the inferred map in the northern hemisphere improves
+        with SNR, but at very high SNR the region surrounding the global
+        optimum becomes so small that our optimization methods struggle to
+        converge on the correct solution.
         \label{fig:snr}
@@
     \oscaption{twospec}{%
-        Learning two spectra simultaneously.
+        An example of a star whose spectrum is different within the spot
+        (\texttt{B}) and outside of the spot (\texttt{A}). Everywhere on 
+        the surface, the spectrum is a linear combination of two
+        ``eigenspectra'' ($s_1$ and $s_2$).
+        As in Figure~\ref{fig:spot_y1bs}, we assume
+        we do not know the map, the baseline, or either of the eigenspectra.
+        The top row shows the true values for the map and the spectra, and
+        the bottom row shows our inferred values.
         \label{fig:twospec}
@@
 
-\section{Performance}
-\label{sec:performance}
+\section{Discussion}
+\label{sec:discussion}
 %
@@
 
-\section{Stuff we're not addressing}
-%
-\xxx{In progress...}
-Differential rotation and convective blueshift.
+\xxx{We are not addressing differential rotation and convective blueshift.}
+\xxx{Telluric lines could be treated much as in Figure~\ref{fig:twospec}.}
+\xxx{Instrumental profile is another Toeplitz matrix.}
+
+\section{Conclusions}
+\label{sec:conclusions}
+\xxx{Hello.}
 
@@
     $\kT$                    & convolution kernel basis vector                       & Equation~(\ref{eq:deconv:kT})\\
-    $\lambda$                & wavelength (in nm)                                    & \S\ref{sec:the_problem}\\
-    $\lnlam$                 & $\ln\lambda$ (observer frame)                         & \S\ref{sec:the_problem}\\
-    $\lnlam_0$               & $\ln\lambda$ (rest frame)                             & \S\ref{sec:the_problem}\\
+    $\lambda$                & wavelength                                            & \S\ref{sec:the_problem}\\
+    $\lambda_\mathrm{r}$     & reference wavelength                                  & \S\ref{sec:the_problem}\\
+    $\lnlam$                 & $\ln\nicefrac{\lambda}{\lambda_\mathrm{r}}$ (observer frame)  & \S\ref{sec:the_problem}\\
+    $\lnlam_0$               & $\ln\nicefrac{\lambda}{\lambda_\mathrm{r}}$ (rest frame)      & \S\ref{sec:the_problem}\\
     $\boldsymbol{\Lambda}$   & prior covariance matrix                               & \\

### 2019-08-22 paparazzi/doppler.py

@@ -127,7 +127,9 @@ class Doppler(object):
 
             # Compute the limb darkening operator
             F = self._map.ops.F(np.append([-1.0], self._u), [np.pi])
-            self._L = ts.dot(ts.dot(self._map.ops.A1Inv, F), self._map.ops.A1).eval()
+            self._L = ts.dot(
+                ts.dot(self._map.ops.A1Inv, F), self._map.ops.A1
+            ).eval()
             self._L = csr_matrix(self._L)
 
     @property
@@ -510,7 +512,7 @@ class Doppler(object):
         self,
         R=3e5,
         nlam=200,
-        sigma=7.5e-6,
+        sigma=1.4e-5,  # 7.5e-6,
         nlines=21,
         ntheta=16,
         ferr=1.0e-4,

### 2019-08-22 tex/figures/spot_setup.py

@@ -120,7 +120,7 @@ for lat, lon in zip(lats, lons):
 
 # Tweak & save
 ax[1].set_ylabel(r"intensity", fontsize=10)
-ax[1].set_xlabel(r"$\ln\left(\lambda/\mathrm{nm}\right)$", fontsize=10)
+ax[1].set_xlabel(r"$\ln\left(\lambda/\ln_0\right)$", fontsize=10)
 ax[1].set_aspect(7e-4)
 for tick in ax[1].xaxis.get_major_ticks() + ax[1].yaxis.get_major_ticks():
     tick.label.set_fontsize(10)

### 2019-08-22 tex/figures/utils/spot.py

@@ -355,7 +355,7 @@ def plot_results(
     ax.axvspan(lnlam_padded[0], lnlam[0], color="k", alpha=0.3)
     ax.axvspan(lnlam[-1], lnlam_padded[-1], color="k", alpha=0.3)
     ax.set_xlim(lnlam_padded[0], lnlam_padded[-1])
-    ax.set_xlabel(r"$\ln\left(\lambda/\mathrm{nm}\right)$")
+    ax.set_xlabel(r"$\ln\left(\lambda/\lambda_0\right)$")
     ax.set_ylabel(r"Normalized intensity")
     ax.legend(loc="lower left", fontsize=12)
     fig.savefig("%s_spectrum.pdf" % name, bbox_inches="tight")

### 2019-08-22 tex/ms.tex
misc

@@
+% !TeX root = ./ms.tex
 \documentclass[modern]{aastex62}
@@
 
-We generated our spectrum at high resolution 
-($R \equiv \frac{\lambda}{\Delta\lambda} = 300,000$)
-centered at a reference wavelength $\lambda_\mathrm{r} = 6430$ nm.
-The spectrum consists of a Gaussian absorption line in log-wavelength
-($\lnlam$) space with amplitude $0.5$ and standard deviation 
-$\sigma_{\lnlam} = 1.4\times 10^{-5}$. This corresponds to a FWHM of about
-$2.355~\sigma_{\lnlam}~\lambda_\mathrm{r}~\approx~0.2$ nm or, in velocity space,
-$2.355~\sigma_{\lnlam}~c~\approx~10$ km/s, equal to the value used in
-\citet{Vogt1987}. Unlike \citet{Vogt1987}, we add 20 additional small
-absorption lines at random positions throughout the spectrum, all of 
-the same FWHM but of varying depths, including some line blends. In total,
-our spectrum consists of $K = 201$ log-wavelength bins in the range
-$-3.3\times 10^{-4} < \lnlam < 3.3\times 10^{-4}$ plus an additional
-%
-\begin{align}
-    W - 1 &= \frac{40~\mathrm{km/s}}{c} \frac{201}{3.3 \times 10^{-4}} - 1 \nonumber \\
-          &= 80
-\end{align}
-%
-log-wavelength bins of padding (40 on either side) to eliminate edge
-effects due to the convolution. As in \citet{Vogt1987},
-we assume a projected velocity of $v\sin i = 40$ km/s and an inclination
-$i = 40^\circ$.
-
-% Our default SNR is about 75.
-
-Recover images with an effective resolution of $12^\circ$.
-
 \begin{figure}[t!]
@@
         given the same spectrum, composed of a sum of synthetic 
-        Gaussian absorption lines (top right). The specific intensity
+        Gaussian absorption lines (blue curve in the bottom panel). 
+        The specific intensity
         at each point on the surface is equal to this spectrum weighted
@@
         %
-        To generate the synthetic dataset, the star is inclined at
+        To generate the synthetic dataset (orange curves in the bottom
+        panel), the star is inclined at
         $40^\circ$ with respect to the line of sight and the disk-integrated
         spectrum is computed at 16 equally-spaced phases between
-        $-180^\circ$ and $180^\circ$ (lower panel).
+        $-180^\circ$ and $180^\circ$ (middle panel).
         %
@@
 \end{figure}
+
+We repeat the same experiment here using our new formalism, except we
+instead generate a stellar surface with the word ``SPOT'' written across
+the northern hemisphere (top left panel of Figure~\ref{fig:spot_setup}).
+We do this by computing the $l_\mathrm{max} = 15$ spherical harmonic
+decomposition of an image of the word, generating a set of 
+$N = (l_\mathrm{max} + 1)^2 = 256$ spherical harmonic coefficients 
+$\bvec{y} = (1 \quadquad \bvec{y_1})$.
+
+Our input spectrum $\bvec{s}$ was generated at high resolution 
+($R \equiv \frac{\lambda}{\Delta\lambda} = 300,000$)
+centered at a reference wavelength $\lambda_\mathrm{r} = 6430$ nm
+(blue curve in the bottom panel of Figure~\ref{fig:spot_setup}).
+The spectrum consists of a Gaussian absorption line in log-wavelength
+($\lnlam$) space with amplitude $0.5$ and standard deviation 
+$\sigma_{\lnlam} = 1.4\times 10^{-5}$. This corresponds to a FWHM of about
+$2.355~\sigma_{\lnlam}~\lambda_\mathrm{r}~\approx~0.2$ nm or, in velocity space,
+$2.355~\sigma_{\lnlam}~c~\approx~10$~km/s, equal to the value used in
+\citet{Vogt1987}. Unlike \citet{Vogt1987}, we add 20 additional small
+absorption lines at random positions throughout the spectrum, all of 
+the same FWHM but of varying depths, including some line blends. In total,
+the rest frame spectrum $\bvec{s}$ consists of $K = 201$ log-wavelength bins in the range
+$-\Delta\lnlam < \lnlam < \Delta\lnlam$ for $\Delta\lnlam = 3.3\times 10^{-4}$ plus an additional 
+%
+\begin{align}
+    W - 1 &= \frac{v\sin i}{c} \frac{K}{\Delta\lnlam} - 1 \nonumber \\
+          &= \left(\frac{40~\mathrm{km/s}}{3\times 10^5~\mathrm{km/s}}\right)
+          \left(\frac{201}{3.3 \times 10^{-4}}\right)  - 1 \nonumber \\ 
+          &= 80
+\end{align}
+%
+log-wavelength bins of padding (40 on either side) to eliminate edge
+effects due to the convolution, for a total of 
+$K' = 281$ wavelength bins. As in \citet{Vogt1987},
+we assume a projected velocity of $v\sin i = 40$ km/s and an inclination
+$i = 40^\circ$.
+
+\xxx{note on the intensities at A and B.}
+
+Given $\bvec{y_1}$ and $\bvec{s}$, we compute the data vector $\bvec{f}$
+at $M = 16$ equally spaced rotational phases; these phases are shown in orthographic
+projection (as an observer would see the star) in the center
+panel of Figure~\ref{fig:spot_setup}. The synthetic spectra for each phase
+are shown as the orange curves in the bottom panel of the figure (note the
+different scaling, as all spectral lines become shallower due to the
+broadening). We assume a wavelength-independent,
+quadratic limb darkening law with $u_1 = 0.5$ and $u_2 = 0.25$. Finally,
+we add random Gaussian noise with amplitude $\sigma_\bvec{f} = 10^{-4}$ to
+simulate a very high signal-to-noise ratio (SNR) spectrum. The mean
+standard deviation in each wavelength bin across all 16 epochs in the
+noiseless data vector is about $10^{-2}$, so our choice of $\sigma_\bvec{f}$
+corresponds to SNR $\sim$ 100 in each of the 201 wavelength bins of $\bvec{f}$.
+%
+%For reference, \citet{Vogt1987} report SNRs per 60 m\AA\, pixel, while our
+%resolution elements are approximately $\lambda_r\Delta\lnlam/K \approx 100$ m\AA\,
+%across, so our SNR in the same units as \citet{Vogt1987} is about 80.
+%
+% TODO: Perhaps Vogt computes the "signal" as the line depth, rather than
+% as the amplitude of the perturbations? Check this.
+
+% We Recover images with an effective resolution of $12^\circ$.
+
+\subsection{Known baseline and spectrum}
+In our first experiment, we attempt to infer the stellar map...
 

### 2019-08-22 tex/ms.tex
more text [build paper]

@@
         %
+        The grey regions indicate wavelength
+        regions outside the observation window, but whose features still
+        contribute to the observed spectrum due to rotational broadening.
         \label{fig:spot_setup}
@@
 
-Given $\bvec{y_1}$ and $\bvec{s}$, we compute the data vector $\bvec{f}$
+Given $\bvec{y_1}$ and $\bvec{s}$, we use Equation~(\ref{eq:deconv:F}) to
+compute the data vector $\bvec{f}$
 at $M = 16$ equally spaced rotational phases; these phases are shown in orthographic
@@
 quadratic limb darkening law with $u_1 = 0.5$ and $u_2 = 0.25$. Finally,
-we add random Gaussian noise with amplitude $\sigma_\bvec{f} = 10^{-4}$ to
+we divide the flux by the baseline at each epoch (Equation~\ref{eq:norm:b})
+and add random Gaussian noise with amplitude $\sigma_\bvec{f} = 10^{-4}$ to
 simulate a very high signal-to-noise ratio (SNR) spectrum. The mean
@@
 
+In the following sections we discuss various approaches to 
+solving the Doppler imaging problem for this dataset.
+Unless otherwise noted, in all experiments we adopt a Gaussian prior
+for the spherical harmonic coefficients $\bvec{y_1}$ with mean
+$\boldsymbol{\mu}_\bvec{y_1} = \bvec{0}$ and covariance
+$\boldsymbol{\Lambda}_\bvec{y_1} = (10^{-2})^2\bvec{I}$,
+corresponding to a flat power spectrum prior.
+We place a Gaussian process prior on the spectrum $\bvec{s}$ with mean
+$\boldsymbol{\mu}_\bvec{s} = \bvec{1}$ and a covariance matrix
+$\boldsymbol{\Lambda}_\bvec{s}$ computed from
+ a Mat\'ern-3/2 kernel with amplitude $\sigma_\bvec{s} = 0.3$
+and lengthscale $\rho_\bvec{s} = 3\times 10^{-5}$.
+
 \subsection{Known baseline and spectrum}
-In our first experiment, we attempt to infer the stellar map...
+%
+In our first experiment, we attempt to infer the stellar map assuming
+we have perfect knowledge of the rest frame spectrum $\bvec{s}$ and
+the baseline $\bvec{b}$ (Equation~\ref{eq:norm:b}). 
+This is analogous to the case where a good physical model exists for
+the stellar spectrum and simultaneous photometry is available to
+constrain the baseline variations.
+As we showed in
+\S\ref{sec:solve_y}, the posterior distribution for the map coefficients 
+$\bvec{y_1}$ is analytic in this case, with mean given by Equation~(\ref{eq:inverse:y1hat})
+and covariance given by Equation~(\ref{eq:inverse:y1cov}). Note that
+we must first scale the data vector $\bvec{f}$ by $\bvec{b}$ (which in this
+case is known).
 
@@
 \end{figure}
+
+The results are shown in Figure~\ref{fig:spot_y1}. The left hand panel
+shows the inferred map alongside the data
+(black points) and best fit model (orange curves) at each of the 16 epochs.
+The panels on the right show the true map (top), the inferred map (center)
+and the posterior pointwise uncertainty (bottom) on a rectangular
+latitude-longitude grid. The uncertainty on the vector of pixels $\bvec{p}$ where
+we evaluate the map is equal to the square root of the diagonal of
+the posterior covariance matrix for the pixel values, computed from
+%
+\begin{align}
+    \label{eq:spotstar:uncert}
+    \boldsymbol{\Sigma}_\bvec{p} = \bvec{P} \boldsymbol{\Sigma}_\bvec{\hat{y}_1}^{-1} \bvec{P}^\top
+\end{align}
+%
+where $\bvec{P}$ is the change-of-basis matrix from spherical harmonic 
+coefficients to pixels on the grid.
+
+The inferred map is nearly indistinguishable from the true map, save for a
+few small differences, particularly below the stellar equator. This is 
+captured by the uncertainty, which increases
+south of $+30^\circ$ latitude, reaching a maximum at $-30^\circ$, below
+which the uncertainty is constant at about 10\%. This is due to the fact
+that regions below $-40^\circ$ latitude are never in view from the
+observer's perspective, while regions between about $-30^\circ$ and
+$-40^\circ$ are so strongly limb-darkened that the data contains little
+information about them. The particular value of the uncertainty in this
+region---10\%---is the uncertainty associated with the prior, which can
+be computed by replacing $\boldsymbol{\Sigma}_\bvec{\hat{y}_1}$ with 
+$\boldsymbol{\Lambda}_\bvec{y_1}$ in Equation~(\ref{eq:spotstar:uncert}).
+
+\subsection{Known spectrum, unknown baseline}
+%
+We next investigate the case where the spectrum is known exactly, but
+the baseline is not.
 
@@
         (dotted orange line), and the inferred spectrum (orange line, with
-        shaded $1\sigma$ uncertainty). The grey regions indicate wavelength
-        regions outside the observation window, but whose features still
-        contribute to the observed spectrum due to rotational broadening.
+        shaded $1\sigma$ uncertainty).
         \label{fig:spot_y1bs}

### 2019-08-23 tex/ms.tex
paper coming along

@@
 \xxx{%
-Data-driven modeling at its finest $\cdot$ %
+\textbf{Mention the following things:}
+Advantages of data-driven modeling $\cdot$ %
+Interpretable priors $\cdot$ %
 Works on blended lines $\cdot$ %
 Uses the whole spectrum $\cdot$ %
-Uncertainties FTW $\cdot$ %
+Yields uncertainties! $\cdot$ %
 Probably works on slow rotators $\cdot$ %
@@
 Fast! $\cdot$ %
-Use in MCMC to marginalize over inclination and stuff $\cdot$ %
+Use in MCMC to marginalize over inclination and stuff
 }
@@
 %
-\xxx{Check out \citet{Luger2019} and \citet{Bedell2019} and stuff.}
-
+\xxx{%
+\noindent Introduce the problem of Doppler imaging. Then cite the following papers:\\[0.5em]
+\noindent\textbf{Misc.} \\
+\noindent\citet{Luger2019} --- Surface modeling with spherical harmonics: \starry \\
+\noindent\citet{Bedell2019} --- Data-driven spectral inference: \texttt{wobble} \\[0.5em]
+%
+\noindent\textbf{Theory} \\
+\noindent\citet{Khokhlova1976,Goncharskii1977} --- Local line profile from observed spectrum\\
+\noindent\citet{Vogt1983,Vogt1987} --- Seminal papers on Doppler imaging \\
+\noindent\citet{Rice1989} ---  Another seminal paper\\
+\noindent\citet{Deutsch1958,Deutsch1970,Falk1974} ---  Ylms + Doppler imaging\\
+\noindent\citet{Unruh1995} --- sensitivity to line profile models\\
+\noindent\citet{Piskunov1990} --- notes on regularization \\[0.5em]
+%
+\noindent\textbf{Application} \\
+\noindent\citet{Crossfield2014} --- Global cloud map of Luhman 16B \\
+\noindent\citet{Roettenbacher2016} --- Doppler imaging of $\zeta$ Andromedae \\
+\noindent\citet{Roettenbacher2017} --- Doppler imaging of $\sigma$ Geminorum \\
+}
 %
@@
 \subsection{The full solution}
+\label{sec:full_solve}
 In the previous two sections we showed how, if the stellar
@@
     \begin{centering}
-    \includegraphics[width=0.6\linewidth]{figures/ld.pdf}
+    \includegraphics[width=0.5\linewidth]{figures/ld.pdf}
     \oscaption{ld}{%
@@
 A detailed discussion of this general case is deferred to future work,
-but we present an example of a two-component stellar spectrum in the
-following section.
+but we present an example of a two-component stellar spectrum in \S\ref{sec:eigen}
+below.
 
@@
 
-\xxx{note on the intensities at A and B.}
-
-Given $\bvec{y_1}$ and $\bvec{s}$, we use Equation~(\ref{eq:deconv:F}) to
+Given $\bvec{y_1}$ and $\bvec{s}$, we use Equations~(\ref{eq:deconv:F}) and~%
+(\ref{eq:inverse:azero}) to
 compute the data vector $\bvec{f}$
@@
 \subsection{Known baseline and spectrum}
+\label{sec:spot_y1}
 %
@@
 \subsection{Known spectrum, unknown baseline}
+\label{sec:spot_y1b}
 %
 We next investigate the case where the spectrum is known exactly, but
-the baseline is not.
+the baseline is not. This corresponds to the case discussed in 
+\S\ref{sec:norm}. We use the solution to the linearized problem,
+Equation~(\ref{eq:norm:yhat}), to obtain an initial guess for 
+$\bvec{y_1}$. We then repeatedly solve
+Equation~(\ref{eq:inverse:y1hat}) for $\bvec{y_1}$, given the baseline 
+computed from the previous value of $\bvec{y_1}$ from Equation~(\ref{eq:norm:b}).
+Because of the high SNR of our data, we find that it is necessary to employ
+a simple tempering procedure to avoid getting stuck in local minima. We
+introduce an artificial temperature $T$ that decreases every iteration
+in equally spaced logarithmic steps $\Delta \log T$ from an initial temperature 
+$T=T_0$ to $T=1$. This temperature is used to scale the data covariance
+$\boldsymbol{\Sigma}_\bvec{f}$; in practice, we simply replace
+$\boldsymbol{\Sigma}_\bvec{f}$ with $T \boldsymbol{\Sigma}_\bvec{f}$
+in Equation~(\ref{eq:inverse:y1hat}). This has the effect of smoothing
+out the likelihood space, reducing the likelihood that the solver
+will get stuck in a local minimum. For this particular experiment, we
+set $T_0 = 100$ and $\Delta \log T = -0.25$, for a total of $9$ steps of
+the bilinear solver. 
+%
+In a final step, we run a gradient-descent optimizer, initializing it
+at the solution obtained with the bilinear solver. We use
+the \texttt{Keras} \citep{Keras} implementation of the
+Nesterov momentum-enhanced Adam solver \citep[\texttt{NAdam};][]{NAdam},
+running it for $N_\mathrm{nadam} = 80$ iterations at a learning rate
+$L_\mathrm{nadam} = 10^{-4}$. Our loss function is simply the (negative)
+log probability, equal to the sum of the log likelihood and log prior:
+%
+\begin{align}
+    \label{eq:spotstar:logP}
+    -\ln P &= 
+    \frac{1}{2}
+    \Big(
+        \bvec{r}^\top \boldsymbol{\Sigma}_\bvec{f}^{-1} \bvec{r} \, + \,
+        \bvec{y_1}^\top \boldsymbol{\Lambda}_\bvec{y_1}^{-1} \bvec{y_1} \, + \,
+        (\bvec{b - 1})^\top \boldsymbol{\Lambda}_\bvec{b}^{-1} (\bvec{b - 1})
+    \Big)
+\end{align}
+%
+where $\bvec{r}$ is the residual (data minus model) vector and the last term
+is a prior we include on the baseline $\bvec{b}$, which we force to be close
+to a mean of unity with covariance $\boldsymbol{\Lambda}_\bvec{b} = (0.1)^2\bvec{I}$.
 
@@
 
+Our results are shown in 
+Figure~\ref{fig:spot_y1b}. The panels at the top are the same as those
+in Figure~\ref{fig:spot_y1}, but now we also plot the inferred baseline
+(lower left) and spherical harmonic coefficients (lower right) next to
+the true values. We recover the \texttt{SPOT} map just as well as before,
+except for the presence of a strong dipolar artifact; the background
+intensity level is higher in the northern hemisphere and lower in the
+southern hemisphere. This effect is closely related to the fact that
+we do not know the true baseline. While we are able to infer the
+shape of the baseline exceedingly well (lower left panel), there is a large
+offset between the true value and our inferred value. This is due to
+a fundamental degeneracy involving the 
+$Y_{1,-1}$ (\raisebox{-0.2em}{\includegraphics[width=1em]{figures/Y1m1.pdf}})
+spherical harmonic coefficient, which, because a large portion of the southern
+hemisphere is never in view, cannot be constrained by the data. The 
+magnitude of the true value of the coefficient is quite large (lower right
+panel), since the northern hemisphere \emph{is} significantly darker than
+the southern hemisphere; however, the data do not constrain this, and 
+our prior shrinks all coefficients toward zero. The net effect is that the
+region surrounding the spot in the northern hemisphere gets brighter to 
+even out the difference between the two hemispheres. This causes the 
+visible portion of the star to get brighter, raising the baseline
+relative to the true value.
+
+Note, importantly, that even in cases where the baseline is known (from, say,
+simultaneous photometry), it is typically only known in a \emph{relative} 
+sense. This degeneracy will typically apply in that case as well, so in
+principle the dipole term will always be unconstrained for stars at
+similar inclinations. For inclinations closer to $90^\circ$ this is much 
+less of an issue, although (as we will see below) other degeneracies show up.
+
+Finally, we note that the pixelwise uncertainty shown is a strict
+\emph{lower bound} on the map uncertainty, since it is the uncertainty
+conditioned on the inferred value of the baseline. Sampling methods
+such as MCMC are required to obtain the \emph{true} uncertainty on the 
+map. We discuss this further in \S\ref{sec:discussion}.
+
+\subsection{Unknown spectrum, unknown baseline}
+\label{sec:spot_y1bs}
+%
+Suppose we are handed a series of spectra in a wavelength regime where
+we do not have a good physical model for the line generation mechanisms,
+or a wavelength regime with many line blends for which we do not have
+reliable templates. Or perhaps the spectra are of a star whose
+rotational broadening does not dominate over other broadening mechanisms,
+in which case our template might not be accurate enough to allow us to
+tease out the small Doppler signals. In these cases, we may want to relax
+the assumption that we know the rest frame spectrum $\bvec{s}$ exactly,
+and instead try to \emph{learn} it from the data.
+
+Given the same data as before, we now try to learn both the stellar map
+and the stellar spectrum, conditioned only on the wide Gaussian priors
+discussed above. We must follow the iterative procedure presented in
+\S\ref{sec:full_solve}, adjusting for the fact that we do not know
+the true baseline, either (\S\ref{sec:norm}).
+
 \begin{figure}[p!]
@@
         spectrum (blue line), the initial guess based on a deconvolution
-        (dotted orange line), and the inferred spectrum (orange line, with
+        (dashed orange line), and the inferred spectrum (orange line, with
         shaded $1\sigma$ uncertainty).
@@
     \begin{centering}
-    \includegraphics[width=0.98\linewidth]{figures/inclinations.pdf}
-    \oscaption{inclinations}{%
-        Recovered \spot map as a function of stellar inclination. The
-        rest frame spectrum is assumed to be known exactly, but the
-        baseline is not. At very low inclinations, the small
-        projected velocities begin to degrade the spatial resolution of
-        the inferred map, while at inclinations close to $90^\circ$ there
-        is a degeneracy between the northern and southern hemispheres.
-        \label{fig:inclinations}
+    \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_low_snr_timeseries.pdf}
+    \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_low_snr_rect.pdf}
+    \\[0.5em]
+    \includegraphics[width=0.405\linewidth]{figures/spot_y1bs_low_snr_baseline.pdf}
+    \includegraphics[width=0.575\linewidth]{figures/spot_y1bs_low_snr_coeffs.pdf}
+    \\[0.5em]
+    \includegraphics[width=0.98\linewidth]{figures/spot_y1bs_low_snr_spectrum.pdf}
+    \oscaption{spot_y1bs_low_snr}{%
+        Same as Figure~\ref{fig:spot_y1bs}, but for $10\times$ lower SNR.
+        We still recover the \spot map and the input spectrum, albeit with
+        higher uncertainty, as expected.
+        \label{fig:spot_y1bs_low_snr}
     }
@@
 
-\begin{figure}[p!]
-    \begin{centering}
-    \includegraphics[width=0.98\linewidth]{figures/snr.pdf}
-    \oscaption{snr}{%
-        Recovered \spot map as a function of SNR per resolution element.
-        The quality of the inferred map in the northern hemisphere improves
-        with SNR, but at very high SNR the region surrounding the global
-        optimum becomes so small that our optimization methods struggle to
-        converge on the correct solution.
-        \label{fig:snr}
-    }
-    \end{centering}
-\end{figure}
+Because the problem is generally not convex, we need a good starting
+guess for either the spectrum or the map coefficients. We note that
+we can very crudely approximate the rest frame spectrum by deconvolving the 
+average observed spectrum with the first term of the convolution kernel
+$\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{figures/kT00.pdf}}).
+This is equivalent to assuming the average map of the star
+across all observations is featureless, and the average spectrum is equal
+to the (symmetrically) rotationally-broadened version of the rest frame
+spectrum. In practice, this is a fairly poor approximation, but we find that it
+suffices as an initial guess. Given this starting value of $\bvec{s}$, we 
+compute an initial guess for $\bvec{y_1}$ using the linear baseline
+approximation. We then iterate between solving for $\bvec{s}$ and
+solving for $\bvec{y_1}$, always using the previous value of the 
+baseline to compute $\bvec{y_1}$. As in the previous section, we find it
+necessary to implement a tempering scheme, except with a much higher
+starting temperature $T_0 = 5,000$ and a slower decay $\Delta\log T = -0.04$.
+We again refine our solution with \texttt{NAdam}, this time setting
+$N_\mathrm{nadam} = 3,000$ and $L_\mathrm{nadam} = 2.5\times 10^{-5}$. Since
+we are now solving for the spectrum as well, we include the negative log prior 
+term for the spectrum, 
+$\frac{1}{2}(\bvec{s - 1})^\top \boldsymbol{\Lambda}_\bvec{s}^{-1}(\bvec{s - 1})$, 
+in Equation~(\ref{eq:spotstar:logP}).
+
+Figure~\ref{fig:spot_y1bs} shows the results. The top portion of the figure is
+the same as before. A panel at the bottom has been added showing the true
+rest frame spectrum (blue), the initial guess based on the deconvolution
+(dashed orange), and the inferred spectrum (orange). We recover the \spot
+feature as before, albeit with more noise, particularly south of about
+$+30^\circ$ latitude. Our uncertainties are somewhat underestimated, as 
+expected, since they are computed conditioned on the optimum value of 
+the spectrum. On the other hand, we recover the spectrum exceedingly well,
+with low uncertainty and virtually no bias anywhere.
+
+To test our technique on more realistic data, in Figure~\ref{fig:spot_y1bs_low_snr}
+we repeat the experiment on data with $10$ times higher uncertainty,
+setting $\sigma_\bvec{f} = 10^{-3}$. Because the higher uncertainty increases
+the volume of the region surrounding the global optimum, it is
+actually significantly \emph{easier} for the algorithm to converge on the
+best solution, so we set $T_0 = 500$, $\Delta\log T = -0.05$, 
+$N_\mathrm{nadam} = 500$, and $R_\mathrm{nadam} = 10^{-4}$. Interestingly,
+while the uncertainty on the spectrum increased, the quality of the
+recovered \spot map did not noticeably degrade. This suggests we did not
+quite find the global optimum in Figure~\ref{fig:spot_y1bs}. We discuss
+this further in \S\ref{sec:discussion}.
+
+\subsection{Spatially-variable spectrum}
+\label{sec:twospec}
+%
+In our final experiment, we relax the assumption that the stellar
+rest frame spectrum is spatially constant, allowing for different
+spectral features inside and outside of the \spot. This is the case
+for, say, chemically peculiar Ap stars, whose abundance of certain
+elements is significantly different within spotted regions on their
+surfaces. It is also the case in general for spots that are significantly
+cooler than the rest of the photosphere, where the relative abundance
+of different ionization states or molecular features may be different
+than in the hotter, unspotted regions.
+
+The problem setup is the same as that discussed in \S\ref{sec:eigen}, where
+our full map vector $\bvec{a_0}$ is the outer product of a spectral matrix
+$\mathbb{S}$, whose $J$ columns are the different spectral components, and
+a spherical harmonic coefficient matrix $\mathbb{Y}^\top$, whose $J$ rows
+are the corresponding coefficient vectors. For simplicity, in this experiment
+we consider only $J = 2$ spectral components and further require that the
+first component is spatially constant, i.e., the first row of 
+$\mathbb{Y}^\top$ is the vector $(1 \quadquad \bvec{0}^\top)$. The second
+row of $\mathbb{Y}^\top$ is the vector $(1 \quadquad \bvec{y_1}^\top)$, where
+$\bvec{y_1}$ is the (unknown) spherical harmonic expansion of the spot. The
+two columns of $\mathbb{S}$ are $\bvec{s_1}$ and $\bvec{s_2}$, the unknown
+spectral components.
 
@@
 \end{figure}
+%
+\xxx{Figure~\ref{fig:twospec} shows...}
 
@@
 %
-\xxx{In progress...}
+\subsection{Scaling of the computations}
+\label{sec:scaling}
+%
 Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires 
@@
 the latter computation dominates and the entire evaluation 
-takes $\mathcal{O}(W K \lmax^2)$ operations.
-
-\xxx{We are not addressing differential rotation and convective blueshift.}
-\xxx{Telluric lines could be treated much as in Figure~\ref{fig:twospec}.}
-\xxx{Instrumental profile is another Toeplitz matrix.}
+takes $\mathcal{O}(W K \lmax^2)$ operations. \xxx{More on this.}
+
+\subsection{Dependence on SNR}
+\label{sec:snr}
+%
+\begin{figure}[p!]
+    \begin{centering}
+    \includegraphics[width=0.98\linewidth]{figures/snr.pdf}
+    \oscaption{snr}{%
+        Recovered \spot map as a function of SNR per resolution element.
+        The quality of the inferred map in the northern hemisphere improves
+        with SNR, but at very high SNR the region surrounding the global
+        optimum becomes so small that our optimization methods struggle to
+        converge on the correct solution.
+        \label{fig:snr}
+    }
+    \end{centering}
+\end{figure}
+%
+\xxx{Figure~\ref{fig:snr} shows...}
+
+\subsection{Dependence on inclination}
+\label{sec:inc}
+%
+\begin{figure}[p!]
+    \begin{centering}
+    \includegraphics[width=0.98\linewidth]{figures/inclinations.pdf}
+    \oscaption{inclinations}{%
+        Recovered \spot map as a function of stellar inclination. The
+        rest frame spectrum is assumed to be known exactly, but the
+        baseline is not. At very low inclinations, the small
+        projected velocities begin to degrade the spatial resolution of
+        the inferred map, while at inclinations close to $90^\circ$ there
+        is a degeneracy between the northern and southern hemispheres.
+        \label{fig:inclinations}
+    }
+    \end{centering}
+\end{figure}
+%
+\xxx{Figure~\ref{fig:inclinations} shows...}
+
+\subsection{Miscellaneous}
+\label{sec:misc}
+\xxx{%
+\begin{enumerate}
+\item In a more realistic scenario, we'd know more info about the spectrum.
+\item We are not addressing differential rotation and convective blueshift.
+\item Telluric lines could be treated much as in Figure~\ref{fig:twospec}.
+\item Instrumental profile is another Toeplitz matrix.
+\end{enumerate}
+}
 
@@
 \label{sec:conclusions}
-\xxx{Hello.}
+\xxx{Conclusions here.}
 
@@
     \endlastfoot
-    %
-    \midrule
-    \multicolumn{3}{c}{\emph{Dimensions}}\\
-    \midrule
-    %
-    $J$                      & \# of spectral components                             & \S\ref{sec:eigen} \\
-    $K$                      & \# of wavelength bins in the observed spectrum        & \S\ref{sec:linear} \\
-    $K'$                     & \# of wavelength bins in the latent spectrum          & \S\ref{sec:linear}\\
-    $M$                      & \# of epochs observed                                 & \S\ref{sec:linear}\\
-    $N$                      & \# of spherical harmonic coefficients                 & \S\ref{sec:linear}\\
-    $N'$                     & \# of spherical harmonic coefficients after limb darkening & \S\ref{sec:ld}\\
-    $W$                      & \# of wavelength bins in the convolution kernel       & \S\ref{sec:linear}\\
     %
@@
     $l$                      & spherical harmonic degree                             & \\
+    $L_\mathrm{nadam}$       & \texttt{NAdam} learning rate                          & \S\ref{sec:spotstar}\\
     $\bvec{L}$               & limb darkening operator                               & Equation~(\ref{eq:ld:L})\\
     $m$                      & spherical harmonic order                              & \\
+    $N_\mathrm{nadam}$       & number of \texttt{NAdam} iterations                   & \S\ref{sec:spotstar}\\
+    $\bvec{P}$               & Change of basis matrix from $Y_{lm}$ to pixels        & Equation~(\ref{eq:spotstar:uncert})\\
     $\bvec{R}$               & Wigner rotation matrix                                & Equation~(\ref{eq:deconv:R})\\
@@
     $t$                      & time                                                  & \S\ref{sec:the_problem}\\
+    $T$                      & artificial temperature in bilinear solver             & \S\ref{sec:spotstar}\\
+    $T_0$                    & initial artificial temperature setting                & \S\ref{sec:spotstar}\\
+    $\Delta\log T$           & artificial temperature step size                      & \S\ref{sec:spotstar}\\
     $u$                      & limb darkening coefficient                            & \S\ref{sec:ld}\\
@@
     \midrule
-    \multicolumn{3}{c}{\emph{Operators}}\\
+    \multicolumn{3}{c}{\emph{Dimensions}}\\
+    \midrule
+    %
+    $J$                      & \# of spectral components                             & \S\ref{sec:eigen} \\
+    $K$                      & \# of wavelength bins in the observed spectrum        & \S\ref{sec:linear} \\
+    $K'$                     & \# of wavelength bins in the latent spectrum          & \S\ref{sec:linear}\\
+    $M$                      & \# of epochs observed                                 & \S\ref{sec:linear}\\
+    $N$                      & \# of spherical harmonic coefficients                 & \S\ref{sec:linear}\\
+    $N'$                     & \# of spherical harmonic coefficients after limb darkening & \S\ref{sec:ld}\\
+    $W$                      & \# of wavelength bins in the convolution kernel       & \S\ref{sec:linear}\\
+    %
+    \midrule
+    \multicolumn{3}{c}{\emph{Operators \& Other symbols}}\\
     \midrule
@@
     $\ceil*{\,}$             & ceiling                                               & Equation~(\ref{eq:kT:lm})\\
-    $\floor*{\,}$            & floor                                                 & Equation~(\ref{eq:kT:lm})
+    $\floor*{\,}$            & floor                                                 & Equation~(\ref{eq:kT:lm})\\
+    $\bvec{0}$               & the zero vector,     
+                             $(0 \quadquad 0 \quadquad \cdots \quadquad 0)^\top$     & \\  
+    $\bvec{1}$               & the one vector,     
+                             $(1 \quadquad 1 \quadquad \cdots \quadquad 1)^\top$     & \\
+
 \end{longtable}

### 2019-08-23 tex/figures/kT.py

@@ -9,7 +9,7 @@ import numpy as np
 import paparazzi as pp
 
 
-# Get the `g` functions at high res
+# Get the `kT` functions at high res
 ydeg = 10
 dop = pp.Doppler(ydeg=ydeg)
 dop.generate_data(R=1e6, nlam=99, y1=np.zeros(dop.N - 1))

### 2019-08-23 tex/figures/kT00.py

@@ -1,0 +1,18 @@
+# -*- coding: utf-8 -*-
+"""
+Plots the first term of the convolution kernel.
+
+"""
+import matplotlib.pyplot as plt
+import paparazzi as pp
+
+dop = pp.Doppler(ydeg=1)
+dop.generate_data(R=1e6, nlam=99, y1=[0, 0, 0])
+kT00 = dop.kT()[0]
+
+fig, ax = plt.subplots(1, figsize=(0.5, 0.25))
+fig.subplots_adjust(left=0, right=1, bottom=0, top=1)
+ax.plot(kT00)
+ax.axis("off")
+ax.margins(0.2, 0.2)
+fig.savefig("kT00.pdf", dpi=500)

### 2019-08-23 tex/figures/ld.py

@@ -55,26 +55,27 @@ for l in range(ydeg + 1):
         ax[n, 0].imshow(render(y), origin="lower", cmap="plasma")
         ax[n, 1].imshow(render(yprime), origin="lower", cmap="plasma")
 
-        ax[n, 0].set_ylabel(r"$Y_{%d, %d}$" % (l, m), rotation=0)
+        ax[n, 0].set_ylabel(r"$Y_{%d, %d}$" % (l, m), rotation=0, fontsize=24)
         ax[n, 0].yaxis.set_label_coords(-0.35, 0.4)
 
         n += 1
 
 # Label the results
-ax[0, 1].set_ylabel(r"$\frac{\sqrt{3}}{2}Y_{1, 0}$", rotation=0)
-ax[0, 1].yaxis.set_label_coords(1.4, 0.4)
-ax[1, 1].set_ylabel(r"$\frac{3}{2\sqrt{5}}Y_{2, -1}$", rotation=0)
-ax[1, 1].yaxis.set_label_coords(1.5, 0.4)
+ax[0, 1].set_ylabel(r"$\frac{\sqrt{3}}{2}Y_{1, 0}$", rotation=0, fontsize=24)
+ax[0, 1].yaxis.set_label_coords(1.5, 0.3)
+ax[1, 1].set_ylabel(r"$\frac{3}{2\sqrt{5}}Y_{2, -1}$", rotation=0, fontsize=24)
+ax[1, 1].yaxis.set_label_coords(1.6, 0.3)
 ax[2, 1].set_ylabel(
     r"$\frac{\sqrt{3}}{2}Y_{0, 0} + \frac{\sqrt{3}}{\sqrt{5}}Y_{2, 0}$",
     rotation=0,
+    fontsize=24,
 )
-ax[2, 1].yaxis.set_label_coords(1.8, 0.4)
-ax[3, 1].set_ylabel(r"$\frac{3}{2\sqrt{5}}Y_{2, 1}$", rotation=0)
-ax[3, 1].yaxis.set_label_coords(1.5, 0.4)
+ax[2, 1].yaxis.set_label_coords(2.0, 0.3)
+ax[3, 1].set_ylabel(r"$\frac{3}{2\sqrt{5}}Y_{2, 1}$", rotation=0, fontsize=24)
+ax[3, 1].yaxis.set_label_coords(1.6, 0.3)
 
 # Transformation arrow
-eps = -0.06
+eps = -0.09
[…]

### 2019-08-26 tex/ms.tex
full draft [build paper]

@@
 % Title
-\title{Analytic Doppler Imaging}
+\title{A Closed-Form Solution to the Doppler Imaging Problem}
 
@@
 of stellar surfaces in the limit of negligible differential rotation and
-convective blueshift. The model for the observed spectrum is linear in 
-both the unbroadened spectrum and the surface map of the star, provided the
-latter is expressed as a sum of spherical harmonics. As a result, the 
-posterior distributions of both the unbroadened spectrum and the stellar map
-conditioned on each other have a closed form, analytic solution that is 
-computationally trivial to evaluate. When neither the unbroadened spectrum
-nor the stellar map is known a priori, the global optimum can usually be
-found via a fast iterative approach that also yields a lower bound on the
-uncertainties.
-\xxx{%
-\textbf{Mention the following things:}
-Advantages of data-driven modeling $\cdot$ %
-Interpretable priors $\cdot$ %
-Works on blended lines $\cdot$ %
-Uses the whole spectrum $\cdot$ %
-Yields uncertainties! $\cdot$ %
-Probably works on slow rotators $\cdot$ %
-Differentiable! $\cdot$ %
-Fast! $\cdot$ %
-Use in MCMC to marginalize over inclination and stuff
-}
+convective blueshift. The model for the observed spectrum is linear in the
+coefficients of the spherical harmonic expansion of the specific intensity
+distribution on the surface and, in certain limits, the posterior over surface maps
+has a closed form, analytic solution that is computationally trivial to
+evaluate. The model is also linear in the local (rest frame) stellar spectrum,
+which may itself be spatially variable. This allows one to perform Doppler
+imaging without knowledge of the local stellar spectrum and therefore works
+on blended lines or regions of the spectrum where line formation mechanisms
+are not well understood. Finally, the model is fast, differentiable, and allows
+one to calculate uncertainties on the inferred surface map.
 %
@@
 closed form, given
-the non-linearity of the Doppler shift.
+the nonlinearity of the Doppler shift.
 The standard approach to solving this integral is therefore
@@
 of intrinsic degeneracies and a large null space
-\citep[e.g.,][]{Luger2019} \xxx{more cites}. Coupled to uncertainties in
+\citep[e.g.,][]{Cowan2017,Luger2019}. Coupled to uncertainties in
 the observations themselves, this makes the process of searching for the
@@
 spectrum $\bvec{s}$ and iterating between optimizing for $\bvec{y}$ and
-optimizing for $\bvec{s}$. This bi-linear problem is not generally convex,
+optimizing for $\bvec{s}$. This bilinear problem is not generally convex,
 but given a good starting point for $\bvec{s}$ and sufficient regularization
 on $\bvec{y}$, we find that it typically converges to the correct solution,
-especially after refinement with a non-linear solver;
+especially after refinement with a nonlinear solver;
 we discuss this in detail below.
@@
 %
-While we can solve for $\bvec{y}$ using a non-linear optimizer, it is
+While we can solve for $\bvec{y}$ using a nonlinear optimizer, it is
 often the case that the denominator in Equation~(\ref{eq:norm:fy}) is close
@@
 general case, we find that solving this linear problem yields a good
-starting point for a non-linear optimization, which we revisit in more
+starting point for a nonlinear optimization, which we revisit in more
 detail below.
@@
         the surface, the spectrum is a linear combination of two
-        ``eigenspectra'' ($s_1$ and $s_2$).
+        spectral components ($s_1$ and $s_2$).
         As in Figure~\ref{fig:spot_y1bs}, we assume
-        we do not know the map, the baseline, or either of the eigenspectra.
+        we do not know the map, the baseline, or either of the spectra.
         The top row shows the true values for the map and the spectra, and
@@
 %
-\xxx{Figure~\ref{fig:twospec} shows...}
+We set \bvec{s_1} equal to a flat spectrum with two absorption lines of
+different depths, and \bvec{s_2} to the same spectrum, except we make the
+second line an emission feature. The local rest-frame spectrum everywhere on the 
+surface is a linear combination of these two spectra. In our simple problem,
+the weight given to the first spectrum is the same everywhere (encoded in 
+the first row of $\mathbb{Y}^\top$), and the weight
+given to the second spectrum is large outside of the spot and small within
+the spot (encoded in the second row of $\mathbb{Y}^\top$, which we set equal
+to the spherical harmonic expansion of the \spot feature).
+The first row of Figure ~\ref{fig:twospec} shows the problem setup. The two
+spectral components are shown as the blue ($\bvec{s_1}$) and green
+($\bvec{s_2}$) curves at the right. Point \texttt{A} on the map (left panel)
+is outside the spot feature, so its local spectrum has nearly equal
+contributions from $\bvec{s_1}$ and $\bvec{s_2}$, and the second spectral
+line is absent (center panel). Point \texttt{B} is inside the spot, so
+it receives a contribution from $\bvec{s_1}$ only.
+
+In our inference step, we again assume we have no knowledge of the map,
+the baseline, or either of the spectral components. As before, we initialize 
+$\bvec{s_1}$ to the deconvolved mean spectrum and $\bvec{s_2}$ to the
+deconvolved mean spectrum after subtracting $\bvec{s_1}$. In practice this
+leads to a decent approximation to $\bvec{s_1}$ but a rather featureless
+guess for $\bvec{s_2}$. We use the same priors as before, except we 
+set $\sigma_\bvec{s_1} = \sigma_\bvec{s_2} = 0.01$ to force the continuum
+to be flatter. We run our bilinear solver with $T_0 = 5,000$ and 
+$\Delta\log T = -0.025$ followed by the nonlinear solver with
+$N_\mathrm{nadam} = 2,000$ and $L_\mathrm{nadam} = 3\times 10^{-4}$.
+
+The results are shown in the bottom panel of Figure~\ref{fig:twospec}.
+We recover the \spot feature reasonably well, although with more artifacts
+than in the previous experiments. We also recover the two spectral components,
+although our solution for $\bvec{s_2}$ is significantly better than that for
+$\bvec{s_1}$. This is due to the fact that the only information
+about $\bvec{s_1}$ that makes it into our dataset is the convolution of
+$\bvec{s_1}$ with the first term of the convolution kernel
+$\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{figures/kT00.pdf}}),
+since this spectral component has no spatial variability.
+Since the deconvolution operation is in general ill-posed, there is no
+unique solution for $\bvec{s_1}$. On the other hand, the other spectral
+component projects into the data via convolutions with all other
+terms of the kernel and is therefore very well constrained.
+Finally, we can estimate the spectra at points \texttt{A} and \texttt{B}
+as before (center panel). We recover the single spectral line at \texttt{A}
+and the two lines at \texttt{B}, albeit rather noisily due to the uncertainty
+in $\bvec{s_1}$.
 
@@
 %
-\subsection{Scaling of the computations}
-\label{sec:scaling}
-%
+
+\xxx{%
+\begin{enumerate}
+    %
+    \item%
+    A gaussian prior with unit mean is a pretty bad prior for the spectrum.
+    In a more realistic scenario, we'd know a lot more information about the
+    spectrum---such as where the lines are and some estimate of their shapes
+    and depths---so the fidelity of our maps would be higher.
+    %
+    \item We are not addressing differential rotation and convective blueshift.
+    These make the integral in Equation~(\ref{eq:deconv:kT}) very difficult
+    to solve. We will tackle this in the next paper.
+    %
+    \item Telluric lines could be treated much as in Figure~\ref{fig:twospec},
+    and marginalized over as in \citet{Bedell2019}.
+    %
+    \item The instrumental profile is another Toeplitz matrix that can be
+    dotted into Equation~(\ref{eq:linear:f}).
+    %
+    \item Discuss the case where the inclination/period/velocity is unknown.
+    The problem is not linear in these variables, so we need MCMC. But our
+    model is differentiable, so we can easily use HMC. Discuss.
+    %
+    \item%
     Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires 
@@
     the latter computation dominates and the entire evaluation 
-takes $\mathcal{O}(W K \lmax^2)$ operations. \xxx{More on this.}
+    takes $\mathcal{O}(W K \lmax^2)$ operations.
+\end{enumerate}
+}
 
@@
 \label{sec:snr}
+%
+Most of the examples in this paper considered very high SNR spectra.
+Figure~\ref{fig:snr} shows the effect of different SNR on the quality
+of the inferred map. As before, the SNR we report is the ratio of the
+standard deviation of the true model in each wavelength bin across 
+all epochs, averaged over all wavelength bins (i.e., the ``signal'') to the 
+standard deviation of the added noise term, $\sigma_\bvec{f}$ (the ``noise'').
+The panels in Figure~\ref{fig:snr} show the inferred map for SNR in the range
+1---1000, where SNR $\sim 100$ is the fiducial case considered in the
+examples so far. The setup is the same as that in \S\ref{sec:spot_y1b}, where
+the spectrum is known exactly but the map coefficients and the baseline are
+not.
+
+As may be expected, the quality of the map decreases with lower SNR, but
+a reduction of the SNR by $\sim 20\times$ still allows for reasonable
+recovery of the \spot feature. In general, as the SNR decreases further, 
+two things happen: the \spot contrast decreases, and the features begin to
+blur out, especially south of about $+30^\circ$ latitude, where features 
+are more limb-darkened
+at this inclination and in view for a smaller fraction of the time.
+
+As the SNR incraeses, however, the quality of the \spot feature does not
+improve appreciably, since a SNR of 100 is more than sufficient to recover 
+a $l_\mathrm{max} = 15$ band-limited map. Interestingly, south of the equator,
+the map quality actually begins to degrade with higher SNR. This is due to
+the fact that finding the global optimum becomes exponentially more difficult
+with higher SNR, as the posterior volume becomes ever smaller. Even with
+aggressive tempering, we were unable to converge on the best solution for
+SNR $\gtrsim 500$ given our standard, conservative priors and initial
+guesses (\S\ref{sec:spotstar}).
 %
@@
 %
-\xxx{Figure~\ref{fig:snr} shows...}
-
 \subsection{Dependence on inclination}
@@
 \end{figure}
-%
-\xxx{Figure~\ref{fig:inclinations} shows...}
-
-\subsection{Miscellaneous}
-\label{sec:misc}
+As in \citet{Vogt1987},
+we also investigate the dependence of the solution on the inclination
+of the star.
+Figure~\ref{fig:inclinations} shows the inferred map for the same problem
+setup as before (with SNR $\sim 100$), but this time varying the
+inclination between $10^\circ$ (nearly face-on) and $90^\circ$ (perfectly
+edge-on). As before, the inclination is assumed to be known exactly. We
+further keep the true equatorial velocity of the star constant across
+all panels, so that the figure corresponds to the same star viewed at
+different orientations. Because of this, decreasing the inclination
+decreases $v\sin i$, reducing the width of the convolution kernel and
+therefore the spatial resolution of our inferred map. Increasing the
+inclination does not result in appreciable changes until an inclination of
+$\sim 80^\circ$, above which it becomes difficult to differentiate between
+features in the northern and southern hemispheres, whose projected
+velocities are nearly equal. At $i = 90^\circ$, there is a formal
+degeneracy between the two hemispheres, which can be seen from the
+mirror-image symmetry in the inferred map. These results are broadly consistent
+with those of \citet{Vogt1987}.
+
+\section{Conclusions}
+\label{sec:conclusions}
 \xxx{%
 \begin{enumerate}
-\item In a more realistic scenario, we'd know more info about the spectrum.
-\item We are not addressing differential rotation and convective blueshift.
-\item Telluric lines could be treated much as in Figure~\ref{fig:twospec}.
-\item Instrumental profile is another Toeplitz matrix.
+    \item Advantages of data-driven modeling
+    \item Interpretable priors
+    \item Works on blended lines
+    \item Uses the whole spectrum
+    \item Yields uncertainties!
+    \item Probably works on slow rotators
+    \item Differentiable!
+    \item Fast!
+    \item Use in MCMC to marginalize over inclination and stuff
 \end{enumerate}
 }
-
-\section{Conclusions}
-\label{sec:conclusions}
-\xxx{Conclusions here.}
 

### 2019-08-26 paparazzi/doppler.py

@@ -512,7 +512,7 @@ class Doppler(object):
         self,
         R=3e5,
         nlam=200,
-        sigma=1.4e-5,  # 7.5e-6,
+        sigma=1.4e-5,
         nlines=21,
         ntheta=16,
         ferr=1.0e-4,

### 2019-08-26 tex/gitlinks.tex
paper coming along
increase timeout

@@
-\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/076a0d29804b1875a480b0fd74a7ea6738368263/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/076a0d29804b1875a480b0fd74a7ea6738368263/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/076a0d29804b1875a480b0fd74a7ea6738368263/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/894b8b3d87b3d52f0fc1e69e5ff06527060ac89c/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/894b8b3d87b3d52f0fc1e69e5ff06527060ac89c/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/894b8b3d87b3d52f0fc1e69e5ff06527060ac89c/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
 \newcommand{\cilink}[1]{\href{https://dev.azure.com/user/repo/_build}{#1}}

### 2021-08-12 tex/ms.tex
ref [build paper]
showyourwork

--- 2019-08-22 tex/ms.tex
@@
-% !TeX root = ./ms.tex
-\documentclass[modern]{aastex62}
-
-% Load the corTeX style definitions
-\input{cortex}
-
-% Bibliography stuff
-\bibliographystyle{aasjournal}
+% Define document class & import showyourwork
+\documentclass[modern]{aastex631}
 
@@
 \begin{abstract}
-We derive a closed form, analytic solution to the problem of Doppler imaging
-of stellar surfaces in the limit of negligible differential rotation and
-convective blueshift. The model for the observed spectrum is linear in 
-both the unbroadened spectrum and the surface map of the star, provided the
-latter is expressed as a sum of spherical harmonics. As a result, the 
-posterior distributions of both the unbroadened spectrum and the stellar map
-conditioned on each other have a closed form, analytic solution that is 
-computationally trivial to evaluate. When neither the unbroadened spectrum
-nor the stellar map is known a priori, the global optimum can usually be
-found via a fast iterative approach that also yields a lower bound on the
-uncertainties.
-\xxx{%
-Data-driven modeling at its finest $\cdot$ %
-Works on blended lines $\cdot$ %
-Uses the whole spectrum $\cdot$ %
-Uncertainties FTW $\cdot$ %
-Probably works on slow rotators $\cdot$ %
-Differentiable! $\cdot$ %
-Fast! $\cdot$ %
-Use in MCMC to marginalize over inclination and stuff $\cdot$ %
-}
-%
-\href{https://github.com/rodluger/paparazzi}{\color{linkcolor}\faGithub}
+    We derive a closed form, analytic solution to the problem of Doppler imaging of stellar surfaces in the limit of negligible differential rotation and convective blueshift.
+    The model for the observed spectrum is linear in the coefficients of the spherical harmonic expansion of the specific intensity distribution on the surface and, in certain limits, the posterior over surface maps has a closed form, analytic solution that is computationally trivial to evaluate.
+    The model is also linear in the local (rest frame) stellar spectrum, which may itself be spatially variable.
+    This allows one to perform Doppler imaging without knowledge of the local stellar spectrum and therefore works on blended lines or regions of the spectrum where line formation mechanisms are not well understood.
+    Finally, the model is fast, differentiable, and allows one to calculate uncertainties on the inferred surface map.
 \end{abstract}
 
-%
+% Main body
 \section{Introduction}
-%
-\xxx{Check out \citet{Luger2019} and \citet{Bedell2019} and stuff.}
-
-%
-
-The paper is organized as follows: in \S\ref{sec:the_problem}~and~%
-\S\ref{sec:the_solution} we introduce the math behind the Doppler imaging
-problem and derive a closed form expression for the model. In
-\S\ref{sec:linear},~\S\ref{sec:inverse},~and~\S\ref{sec:bellswhistles} 
-we demonstrate how to re-express 
-the model as a linear operation on the input spectrum and stellar map and
-derive closed form expressions for the two conditioned on the data and priors.
-In \S\ref{sec:spotstar} we apply our techniques to a mock problem. We
-further discuss and summarize our results in
-\S\ref{sec:discussion}~and~\S\ref{sec:conclusions}. Finally, auxiliary
-derivations are presented in the Appendix.
-
-%
-
-All figures in this paper include links {\color{linkcolor}\faFileCodeO}
-to the \Python scripts that generated them. The figures were auto-generated
-using the 
-\href{https://dev.azure.com/rodluger/paparazzi/_build}{Azure Pipelines}
-continuous integration (CI) service, running on
-a two-core 2.3 GHz \texttt{Standard\_DS2\_v2} virtual machine with 6 GiB physical memory.
-% https://docs.microsoft.com/en-us/azure/virtual-machines/windows/sizes-general#dsv2-series
-We also include icons next to each caption \figtimebox{XXmYYs} that
-indicate the total CPU time taken to generate each figure.
-
-%
-\section{The problem}
-\label{sec:the_problem}
-%
-Let $I(\lnlam, \x, t, \Dargs)$ be the specific 
-intensity observed 
-at log wavelength $\lnlam \equiv \ln\nicefrac{\lambda}{\lambda_\mathrm{r}}$ 
-and at sky-projected 
-Cartesian position $\x = (x, y, z)$ on the surface of the 
-star at time $t$, where
-$\Dargs$ is a set of arbitrary parameters of the Doppler field
-and $\lambda_\mathrm{r}$ is a reference wavelength.
-We may express this intensity as
-%
-\begin{align}
-    \label{eq:the_problem:Ixi}
-    I(\lnlam, \x, t, \Dargs) &= 
-        I\Big(\lnlam_0 + \D(\x, \Dargs), \x, t\Big)
-\end{align}
-%
-where $\lnlam_0$ is the log wavelength in the rest frame and $\D$ is
-the Doppler shift in log wavelength space:
-%
-\begin{align}
-    \label{eq:the_problem:D}
-    \D(\x, \Dargs) 
-        &=
-        \frac{1}{2}\ln\left( 
-            \frac{1 + \beta(\x, \Dargs)}{1 - \beta(\x, 
-            \Dargs)} 
-        \right)
-\end{align}
-%
-where $\beta = v(\x, \Dargs) / c$ is the ratio of the 
-radial velocity at a point on the surface of the star to the speed of light.
-In keeping with the literature, we take positive values of $v$ (and
-$\D$) to mean redshifts.
-
-A common approach to computing the Doppler-shifted spectrum is to
-evaluate the spectrum at the rest frame wavelength $\lnlam_0$
-and interpolate back to the grid in $\lnlam$. This is practical when
-computing the spectrum at a single \emph{point} on the surface, but not
-ideal when one is interested in the \emph{integral} over the visible
-surface of the star $\Surf$, which is typically all we can observe:
-%
-\begin{align}
-    \label{eq:the_problem:F}
-    F(\lnlam, t, \Dargs) 
-        &\equiv
-        \iint\limits_{\Surf(\x)}
-                I(\lnlam, \x, t, \Dargs)
-        \mathrm{d}{\Surf(\x)}
-        \quad ,
-\end{align}
-%
-The difficulty in solving Equation~(\ref{eq:the_problem:F}) stems from the fact
-that $I(\lnlam, \x, t, \Dargs)$ is difficult to write down in 
-closed form, given
-the non-linearity of the Doppler shift.
-The standard approach to solving this integral is therefore
-to discretize the surface of the star with a fine grid, evaluate the
-Doppler-shifted spectrum in each cell, and sum over the spatial axes
-to approximate the integral. Depending on the resolution of the grid,
-this is either numerically inaccurate or computationally inefficient 
-(and often both).
-
-\section{The Solution}
-\label{sec:the_solution}
-
-\subsection{Doppler Deconvolution}
-
-The observed spectrum is a complex function
-of spatial, spectral, temporal, and velocity terms. The goal in this
-section is to deconvolve each of these terms to make solving the integral
-in Equation~(\ref{eq:the_problem:F}) easier.
-%
-The first thing we will do is to express Equation~(\ref{eq:the_problem:Ixi})
-as a convolution:
-%
-\begin{align}
-    \label{eq:deconv:convolution}
-    I(\lnlam, \x, t, \Dargs) &= 
-        I(\lnlam_0, \x, t) 
-        * 
-        \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
-\end{align}
-%
-where $\delta$ is the
-Dirac delta function and
-$*$ denotes the linear convolution operator, defined for
-two arbitrary functions $g$ and $h$ as the integral
-%
-\begin{align}
-    \label{eq:deconv:convolution_def}
-    (g * h)(t) \equiv \int_{-\infty}^\infty g(\tau) h(t - \tau) d\tau
-\end{align}
-%
-for some independent coordinate $t$ and dummy parameter $\tau$.
-%
-The convolution of $I(\lnlam_0)$ with a delta function
-has the effect of shifting the spectrum by an amount $\D$, returning
-a function of the shifted (observed) log wavelength, 
-$\lnlam = \lnlam_0 + \D$.
-
-Next, we expand the spatial dependence of the
-specific intensity at the rest frame wavelength
-in terms of spherical harmonics on the unit disk:
-%
-\begin{align}
-    \label{eq:deconv:Ixi0}
-    I(\lnlam_0, \x, t) 
-        &=
-        \sum_{l=0}^{l_\mathrm{max}}\sum_{m=-l}^{l} a_{lm}(\lnlam_0, t) Y_{lm}(\x)
-    \quad ,
-\end{align}
-%
-where $Y_{lm}(\x)$ is a spherical harmonic on the projected disk
-and $a_{lm}(\lnlam_0, t)$ is the corresponding spherical harmonic 
-coefficient at log wavelength in the rest frame $\lnlam_0$ and time $t$. For 
-convenience, we may write this equation in vector form:
-%
-\begin{align}
-    \label{eq:deconv:Ivec}
-    I(\lnlam_0, \x, t) &=
-    \ylmbasis(\x) \,
-    \alm(\lnlam_0, t)
-    \quad ,
-\end{align}
-%
-where
-%
-\begin{align}
-    \label{eq:deconv:alm}
-    \alm(\lnlam_0, t) \equiv
-\Big( 
-    a_{0,0}(\lnlam_0, t) \quad\quad\quad\quad\quad\quad 
-    a_{1,-1}(\lnlam_0, t) \quad\quad\quad\quad\quad\quad 
-    a_{1,0}(\lnlam_0, t) \quad\quad\quad\quad\quad\quad
-    a_{1,1}(\lnlam_0, t) \quad\quad\quad\quad\quad\quad 
-    ... 
-\Big)^\top
-\end{align}
-%
-is the vector of $N = (l_\mathrm{max} + 1)^2$ spherical harmonic coefficients and
-%
-\begin{align}
-    \label{eq:deconv:ylmbasis}
-    \ylmbasis(\x) \equiv 
-\Big( 
-    Y_{0,0}(\x) \quad\quad\quad\quad\quad\quad 
-    Y_{1,-1}(\x) \quad\quad\quad\quad\quad\quad 
-    Y_{1,0}(\x) \quad\quad\quad\quad\quad\quad 
-    Y_{1,1}(\x) \quad\quad\quad\quad\quad\quad 
-    ... 
-\Big)
-\end{align}
-%
-is the corresponding vector of $N$ spherical harmonics. We may further
-decompose our expression by linearizing the time dependence of the
-spherical harmonic coefficients:
-%
-\begin{align}
-    \label{eq:deconv:R}
-    \alm(\lnlam_0, t) = \R(t) \, \azero(\lnlam_0)
-    \quad ,
-\end{align}
-%
-where $\azero(\lnlam_0) = \bvec{a}(\lnlam_0, t=t_0)$ 
-for some reference time $t_0$.
-For rigid body rotation, the result is exact and $\R(t)$ is the $(N \times N)$ Wigner 
-rotation matrix for real spherical harmonics 
-\citep[e.g.][]{AlvarezCollado1989}, which is implicitly a 
-function of the inclination, obliquity, and rotation period of the star.
-%In the case that other processes such as differential rotation or spot 
-%evolution are significant
-%over the course of an observation, Equation~(\ref{eq:deconv:R}) can be
-%made to hold approximately for some effective rotation matrix 
-%$\R(t)$; we discuss this later.
-
-The equation for the specific intensity in the rest frame now reads
-%
-\begin{align}
-    \label{eq:deconv:Ivecfull}
-    I(\lnlam_0, \x, t) &=
-    \ylmbasis(\x)
-    \,
-    \R(t)
-    \,
-    \azero(\lnlam_0)
-    \quad ,
-\end{align}
-%
-where it is clear that we have fully separated the spatial, temporal, and
-spectral terms. Inserting this into Equation~(\ref{eq:deconv:convolution}) 
-and integrating
-over the visible portion of the star, we arrive at the expression for the 
-observed spectrum:
-%
-%
-\begin{align}
-    \label{eq:deconv:F2d}
-    F(\lnlam, t, \Dargs) &=
-    \iint\limits_{\Surf(\x)}
-    \ylmbasis(\x)
-    \,
-    \R(t)
-    \,
-    \alm(\lnlam_0)
-    * \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
-    \mathrm{d}\Surf(\x)
-    \nonumber \\[0.5em]
-    &=
-    \iint\limits_{\Surf(\x)}
-    \ylmbasis(\x)
-    \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
-    \mathrm{d}\Surf(\x)
-    \,
-    \R(t)
-    \,
-    *
-    \,
-    \azero(\lnlam_0)
-    \quad ,
-\end{align}
-%
-%
-where we made use of the commutativity of the convolution operator and 
-the fact that the integral is taken only over the spatial dimensions.
-Note, importantly, that the convolution operation
-above is implicitly a vector operation---i.e., the
-convolution is taken for each spherical harmonic term individually
-and then summed over all terms.
-
-Finally, we can simplify Equation~(\ref{eq:deconv:F2d}) by noting that the
-delta function in the integrand allows us to reduce the double integral 
-to a line integral:
-%
-\begin{align}
-    \label{eq:deconv:kT}
-    \iint\limits_{\Surf(\x)}
-    \ylmbasis(\x)
-    \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
-    \mathrm{d}\Surf(\x)
-    \, \,
-    &=  
-    \int\limits_{\Curve(\lnlam, \x, \Dargs)}
-    \hspace*{-0.6em}\ylmbasis(\x)
-    \mathrm{d}\Curve(\lnlam, \x, \Dargs)
-    \nonumber \\[0.5em]
-    &\equiv \kT(\lnlam, \Dargs)
-    \quad.
-\end{align}
-%
-where the path $\Curve(\lnlam, \x, \Dargs)$ corresponds to the
-set of all points on the visible disk where 
-$\lnlam_0 + \D(\x, \Dargs) = 0$.
-%
-We thus have
-%
-\begin{align}
-    \label{eq:deconv:F}
-    F(\lnlam, t, \Dargs) 
-    &=
-    \kT(\lnlam, \Dargs) \, \R(t)
-    *
-    \azero(\lnlam_0)
-    \quad.
-\end{align}
-%
-Equation~(\ref{eq:deconv:F}) is the deconvolution of the
-observed spectrum into velocity terms, temporal terms, and spectral/spatial
-terms, respectively. In the next section, we will discuss how to
-efficiently solve the line integral in Equation~(\ref{eq:deconv:kT}).
-
-\subsection{Computing the kernel $\kT$}
-\label{sec:kT}
-%
-In the case that the star's rotation is rigid (i.e., differential rotation
-is negligible) and other effects such as convective blueshift
-may be ignored, the radial velocity at any point on the surface is 
-simply proportional to the distance to the axis of rotation. Without loss
-of generality, if we assume the axis of rotation lies along the $y-z$ plane,
-we have
-%
-\begin{align}
-    \label{eq:kT:beta}
-    \beta(\x, \Dargs) = \frac{\omega \sin i \, x}{c}
-\end{align}
-%
-and
-%
-\begin{align}
-    \label{eq:kT:D}
-    \D(\x, \Dargs) &= 
-        \frac{1}{2}\ln\left( 
-            \dfrac{1 + \dfrac{\omega \sin i \, x}{c}}
-                 {1 - \dfrac{\omega \sin i \, x}{c}}
-        \right)
-    \quad ,
-\end{align}
-%
-where the parameters $\Dargs$ of the Doppler field are the
-angular velocity, $\omega$, and the inclination of the star with
-respect to $\hat{y}$, $i$.
-
-\begin{figure}[t!]
-    \begin{centering}
-    \includegraphics[width=\linewidth]{figures/kT.pdf}
-    \oscaption{kT}{%
-        The Doppler $\kT$ basis for a rigidly rotating star
-        computed from Equation~(\ref{eq:kT:kT}) and
-        Equation~(\ref{eq:kT:sTrecurrence}) up to spherical 
-        harmonic degree $l_\mathrm{max}=10$. Rows correspond to the degree $l$ and
-        columns correspond to the order $m$. These functions encode
-        the contribution of each spherical harmonic to the rotational
-        broadening of features in the stellar spectrum. Because the
-        rotational axis is chosen to be aligned with $\hat{y}$,
-        none of the $m < 0$ harmonics contribute to the observed
-        spectrum.
-        \label{fig:kT}
-    }
-    \end{centering}
-\end{figure}
-
-If we assume the star is unocculted, the region of integration $\Surf(\x)$ 
-in Equation~(\ref{eq:deconv:kT}) is simply the unit disk, 
-so $\Curve(\lnlam, \x, \Dargs)$ 
-is the set of all points
-that satisfy both $\lnlam_0 + \D(\x, \Dargs) = 0$ and 
-$x^2 + y^2 \le 1$.
-Solving Equation~(\ref{eq:kT:D}) for $x$, we find that 
-the curves $\Curve(\lnlam, \x, \Dargs)$ 
-are simply vertical lines on the unit disk given by 
-%
-\begin{align}
-    x &= 
-        \Bigg(\frac{c}{\omega\sin i}\Bigg) 
-        \Bigg(\frac{\mathrm{e}^{-2{\lnlam_0}} - 1}
-                   {\mathrm{e}^{-2{\lnlam_0}} + 1}\Bigg)
-    \quad .
-\end{align}
-%
-The integral in Equation~(\ref{eq:deconv:kT}) is therefore just the line integral
-of the spherical harmonic basis over $y$:
-%
-\begin{align}
-    \label{eq:kT:kT}
-    \kT(\lnlam, \Dargs) 
-    &=    
-    \int\limits_{-\sqrt{1 - x^2}}^
-                {\sqrt{1 - x^2}}
-    \ylmbasis
-    \Big(x, y\Big)
-    \mathrm{d}y
-    \quad .
-\end{align}
-%
-In the Appendix we derive an analytic solution to this integral and show
-how to recursively solve it for all terms in the spherical harmonic basis. 
-%
-Figure~\ref{fig:kT} shows the $\kT$ basis computed from
-the formulae above and Equation~(\ref{eq:kT:kT}) up to spherical 
-harmonic degree $l_\mathrm{max}=10$.
-
-This completes our derivation of the analytic expression for the
-observed spectrum (Equation~\ref{eq:deconv:F}).
-
-\subsection{Example}
-%
-Figure~\ref{fig:spot} shows an example application of the formulae derived 
-in this section. We used \starry to generate a synthetic stellar surface with a 
-single large Gaussian spot at a latitude of $30^\circ$, yielding a vector of
-spherical harmonic coefficients $\bvec{y}$.
-The stellar rest frame spectrum $I(\lnlam_0)$ is taken to be a single Gaussian 
-absorption line that is spatially constant 
-everywhere save for a multiplicative factor equal to the local spot intensity.
-This corresponds to a spectral/spatial expansion vector $\azero(\lnlam_0)$ 
-whose coefficient at degree $l$ and order $m$ is equal to $y_{lm} I(\lnlam_0)$.
-In the Figure, we rotated the star about an axis perpendicular to the line
-of sight (left panel) and computed the observed spectrum using 
-Equation~(\ref{eq:deconv:F}) (center panel). The right panel shows the difference
-between the observed spectrum and the spectrum when the spot is not in view.
-The effect of the spot on the absorption line is evident: a ``bump'' that
-travels from the blueshifted side of to the redshifted side of the line
-in sync with the change in longitude of the spot. This correspondence between
-line shape residuals and spot location is the cornerstone of the Doppler
-imaging technique \citep[compare to, e.g., Figures 1 and 4 in][]{Vogt1983}.
-
-\begin{figure}[p!]
-    \begin{centering}
-    \includegraphics[width=0.6\linewidth]{figures/spot.pdf}
-    \oscaption{spot}{%
-        Time evolution of a Gaussian absorption line on a rigidly rotating, 
-        spotted star computed from the analytic formulae in \S\ref{sec:kT}.
-        The stellar surface is modeled as a spherical harmonic expansion
-        up to $l_\mathrm{max}=20$, and the line shape is assumed to be the same everywhere;
-        the spot simply downweights the local intensity at all wavelengths.
-        As the spot rotates into view (left panel), the line shape changes
-        slightly (center panel). The residuals between the line when the
-        spot is in view (solid) and when it is on the backside of the star
-        (dotted) are shown in the right panel, where
-        a Gaussian-like feature can be seen tracking the spot as it rotates
-        from the blueshifted hemisphere to the redshifted hemisphere of
-        the star.
-        \label{fig:spot}
-    }
-    \end{centering}
-\end{figure}
-
-Figure~\ref{fig:compare} shows one of the spectra in Figure~\ref{fig:spot},
-this time computed using both our formulae (blue line) and the traditional
-technique of discretizing the stellar surface, Doppler-shifting the spectrum
-in each grid cell according to the local radial velocity, interpolating back
-to a uniform wavelength grid, and summing over the spatial dimension
-(dotted orange line). We show the residuals in the lower panel, where it
-is clear that as the number of grid cells increases from 2,000 (light grey)
-to 71,000 (dark grey), the numerical solution approaches the solution
-obtained using our approach.
-
-%Understand---and comment on---the fundamental
-%differences between a discrete linear convolution and traditional linear 
-%interpolation. Should we expect the numerical solution to actually \emph{converge}
-%to the \starry solution, or is the way the two are interpolating fundamentally
-%different?
-
-\begin{figure}[t!]
-    \begin{centering}
-    \includegraphics[width=0.65\linewidth]{figures/compare.pdf}
-    \oscaption{compare}{%
-        The observed spectrum when the spot is in view computed with
-        \starry (blue) and numerically (orange). The problem setup
-        is the same as that in Figure~\ref{fig:spot}. The bottom
-        panel shows the absolute value of the difference between the 
-        two spectra for different number of grid points in the 
-        numerical solution.
-        As the number of grid points increases, the numerical solution
-        approaches the \starry solution.
-        \label{fig:compare}
-    }
-    \end{centering}
-\end{figure}
-
-\section{Linearization}
-\label{sec:linear}
-
-\begin{figure}[ht!]
-    \begin{centering}
-    \includegraphics[width=0.8\linewidth]{figures/linalg.pdf}
-    \oscaption{linalg}{%
-        The Doppler design matrix $\Doppler$ (Equation~\ref{eq:linear:f}), 
-        constructed from a grid of Toeplitz
-        matrices, each of shape $K \times K'$, where $K$
-        is the number of wavelength bins in the observed spectrum and
-        $K' = K + W - 1$ is the number of bins in the model spectrum,
-        where $W$ is the width of the convolution kernel.
-        The $N$ columns of $\Doppler$ correspond
-        to the Toeplitz matrices for each of the $N$ spherical harmonics
-        (shown at the top);
-        the $M$ rows correspond to the Toeplitz matrices rotated to each
-        of the $M$ stellar phases observed (indicated graphically 
-        to the left of $\Doppler$).
-        \label{fig:linalg}
-    }
-    \end{centering}
-\end{figure}
-
-Although the convolution operator (Equation~\ref{eq:deconv:convolution_def})
-is defined for continuous functions, the problem of Doppler imaging deals with
-discrete measurements of a spectrum in bins of log wavelength. Provided our
-wavelength grid is fine enough, we may therefore approximate 
-Equation~(\ref{eq:deconv:convolution_def}) with a discrete convolution.
-For discrete arrays $\bvec{g}$ and $\bvec{h}$, we have
-%
-\begin{align}
-    \label{eq:linear:convolution_def}
-    \bvec{g} * \bvec{h} = \bvec{T(g)} \, \bvec{h}
-\end{align}
-%
-where $\bvec{T}$ is a Toeplitz matrix, a matrix whose diagonals
-are constant from top left to bottom right. In this case, the diagonals
-are constructed from the values of $\bvec{g}$. If $\bvec{g}$ has length
-$L$, element $g_n$ is placed everywhere along the $k^\mathrm{th}$ diagonal 
-of $\bvec{T}$ for $k = -L / 2 + n$; all other entries of $\bvec{T}$ are 
-set to zero. Note that the matrix $\bvec{T}$ need not be square; in fact,
-for our purposes, it is a $(K \times K')$ matrix, where $K$ is the 
-size of the observed wavelength grid and $K' = K + W - 1$ is the size of the
-wavelength grid in the rest frame, where $W$ is the width of the convolution
-kernel.
-
-Given this formulation, we may re-write Equation~(\ref{eq:deconv:F}) as a
-purely linear operation on $\azero(\lnlam_0)$:
-%
-\begin{align}
-    \label{eq:linear:ft}
-    \bvec{f}_m
-    &=
-    \Doppler_m
-    \,
-    \azero
-    \quad,
-\end{align}
-%
-where $\Doppler_m$ is a $(K \times N K')$ matrix constructed
-by horizontally concatenating the Toeplitz matrices for each of the $N$ 
-components of the convolution kernel $\kT(\lnlam, \Dargs)$ 
-transformed by the rotation matrix $\bvec{R}(t)$ evaluated at time $t = t_m$:
-%
-\begin{align}
-    \label{eq:linear:Dm}
-    \Doppler_m = 
-    \begin{pmatrix}
-        \quad
-        \bvec{T}(\kT_0)
-        \quad
-        &
-        \quad
-        \bvec{T}(\kT_1)
-        \quad
-        &
-        \quad
-        \cdots
-        \quad
-        &
-        \quad
-        \bvec{T}(\kT_N)
-        \quad
-    \end{pmatrix}
-    (\bvec{R}(t_m) \otimes \bvec{I}_{K'})
-    \quad.
-\end{align}
-%
-where $\bvec{I}_{K'}$ is the $(K' \times K')$ identity matrix and
-$\otimes$ denotes the Kronecker product.
-%
-The $(K \times 1)$ vector $\mathbf{f}_m$ is the model for 
-the flux observed at each wavelength at time $t = t_m$, and the 
-$(N K' \times 1)$ vector $\azero$ is the vector representation of the
-spatially-dependent spectrum of the star. The latter is constructed
-by flattening the spherical harmonic expansion of the star
-such that the first $K'$ terms in $\azero$ correspond
-to the the values of $(a_0)_{0,0}$ at each wavelength $\lnlam_0$,
-followed by the values of $(a_0)_{1,-1}$ at each wavelength, and so forth.
-
-In general, our data will consist of observations made at several
-epochs, corresponding to different rotational phases of the star. 
-If we concatenate all $M$ spectra $\bvec{f}_m$ into the $(MK \times 1)$ 
-vector $\bvec{f}$, we may write
-%
-\begin{align}
-    \label{eq:linear:f}
-    \bvec{f}
-    &=
-    \Doppler
-    \,
-    \azero
-    \quad,
-\end{align}
-%
-where $\Doppler$ is the full $(MK \times N K')$ Doppler design matrix, 
-constructed by vertically concatenating the individual matrices $\Doppler_m$:
-%
-%
-\begin{align}
-    \label{eq:linear:D}
-    \Doppler =
-    \begin{pmatrix}
-        \Doppler_0
-        \\
-        \Doppler_1
-        \\
-        \cdots 
-        \\
-        \Doppler_m
-    \end{pmatrix}
-    \quad.
-\end{align}
-%
-%
-Equation~(\ref{eq:linear:f}) represents the full linearization of the problem, 
-where we
-have expressed the quantity we can observe, $\bvec{f}$, as a linear
-operation on the quantity of interest, the spectral/spatial decomposition
-of the stellar surface, $\azero$. Figure~\ref{fig:linalg} shows an
-example of $\Doppler$.
-
-\section{The inverse problem}
-\label{sec:inverse}
-%
-In the previous section we showed how to express the data vector $\bvec{f}$,
-a series of spectra obtained at different epochs, as a purely linear
-operation on the map vector $\azero$, the spherical harmonic decomposition of
-the specific intensity on the surface of the star. The advantage of this
-linearity is that, given suitable priors, it allows one to compute both 
-the maximum likelihood solution for $\azero$ and its uncertainty
-\emph{analytically}. In particular, if one places a (multidimensional)
-Gaussian prior on $\azero$ with mean $\boldsymbol{\mu}_\mathbf{a_0}$ and 
-covariance $\boldsymbol{\Lambda}_\mathbf{a_0}$, the maximum \emph{a posteriori} (MAP) 
-solution for $\azero$ is
-%
-\begin{align}
-    \label{eq:inverse:ahat}
-    \bvec{\hat{a}_0} &= 
-    \boldsymbol{\Sigma}_\mathbf{\hat{a}_0}
-    \left(
-        \Doppler^\top
-        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
-        \bvec{f}
-        +
-        {\boldsymbol{\Lambda}_{\azero}}^{-1} \boldsymbol{\mu}_\mathbf{a_0}
-    \right)
-    \quad,
-\end{align}
-%
-with posterior covariance given by
-%
-\begin{align}
-    \label{eq:inverse:acov}
-    \boldsymbol{\Sigma}_\mathbf{\hat{a}_0} &= 
-    \left(
-        \Doppler^\top
-        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
-        \Doppler
-        +
-        {\boldsymbol{\Lambda}_{\azero}}^{-1}
-    \right)^{-1}
-    \quad,
-\end{align}
-%
-where $\boldsymbol{\Sigma}_\mathbf{f}$ is the data covariance
-matrix. These equations require the inversion of a few fairly
-large matrices, but as we will see later, it allows one to obtain
-the map of the star ($\bvec{\hat{a}_0}$) and its uncertainty
-($\boldsymbol{\Sigma}_{\mathbf{\hat{a}_0}}$) in under a second for
-a typical dataset.
-
-There is, however, a catch: for most practical purposes, it is 
-difficult to find a good Gaussian prior for $\bvec{a_0}$. Usually
-we will have some prior information on what the spectrum of the
-star is, and perhaps some prior information on the distribution
-of surface features such as starspots. The problem is that
-even if these priors are Gaussian, the corresponding prior
-on $\bvec{a_0}$ is \emph{not}. To understand this, consider the
-case where the stellar rest frame spectrum is spatially constant,
-save for an amplitude that is spatially variable. We can then
-describe the rest frame spectrum by the $(K' \times 1)$ vector
-$\bvec{s}$ and the amplitude by the $(N \times 1)$ vector 
-$\bvec{y}$ representing the spherical harmonic expansion of the
-intensity profile of the star. The vector $\azero$ is then
-given by the (flattened) outer product of the two vectors:
-%
-\begin{align}
-    \label{eq:inverse:azero}
-    \azero &= \mathrm{vec}\left( \bvec{A_0} \right) \nonumber \\
-         &= \mathrm{vec}\left( \bvec{s} \, \bvec{y}^\top \right) \quad,
-\end{align}
-%
-where $\mathrm{vec}$ denotes the vectorization operation, which in this case
-transforms the $(K' \times N)$ matrix $\bvec{A_0}$ into the $(N K' \times 1)$
-column vector $\azero$ by vertically stacking all of its columns. In other
-words, the vector $\azero$ consists of the set of $K'$ intensities in
-each wavelength bin repeated $N$ times, each time multiplied by the 
-$n^\mathrm{th}$ spherical harmonic coefficient in the expansion of the 
-surface intensity. Returning to our point about priors, note that all of the
-entries of $\azero$ are the product of two independent random variables. Since
-the product of two random variables is generally non-Gaussian, even
-when the variables themselves are Gaussian%
-\footnote{see, e.g., \url{http://mathworld.wolfram.com/NormalProductDistribution.html}}%
-, so too is the prior on $\azero$. This point makes
-Equation~(\ref{eq:inverse:ahat}) of little practical use, since a 
-multivariate Gaussian will not 
-generally be a suitable prior for $\azero$.
-
-That said, a Gaussian prior \emph{is} typically suitable for both the spectrum
-$\bvec{s}$ and the intensity $\bvec{y}$ (just not their product). It is
-straightforward to show that because Equation~(\ref{eq:linear:f}) is linear
-in $\azero$, it is also linear in both $\bvec{s}$ and $\bvec{y}$, so
-MAP solutions can be found analytically for $\bvec{s}$ 
-(conditioned on $\bvec{y}$) and $\bvec{y}$ (conditioned on $\bvec{s}$). We
-investigate these solutions below.
-
-\subsection{Solution for the map}
-\label{sec:solve_y}
-For a fixed, spatially constant rest-frame spectrum $\bvec{s}$, the model
-for the flux vector may be written as
-%
-\begin{align}
-    \label{eq:inverse:fy}
-    \bvec{f}
-    &=
-    \Doppler
-    \,
-    \bvec{S}
-    \,
-    \bvec{y}
-    \quad,
-\end{align}
-%
-where
-%
-\begin{align}
-    \label{eq:inverse:S}
-    \setstackgap{L}{1.25\baselineskip}
-    \bvec{S} =
-        \begin{pmatrix}
-        \quadquad\bvec{s}\quadquad & &            &            &  \\
-        & \quadquad\bvec{s}\quadquad &            &            &  \\
-        &            & \quadquad\bvec{s}\quadquad &            &  \\
-        &            &            & \quadquad\bvec{s}\quadquad &  \\
-        &            &            &               & \ddots
-        \end{pmatrix}
-\end{align}
-%
-is a $(NK' \times N)$ block matrix constructed by repeating the column
-vector $\bvec{s}$ $N$ times in blocks along the main diagonal. 
-%
-Before we solve this equation for $\bvec{y}$, we note that in practice
-it is convenient to fix the coefficient of the $Y_{0,0}$ spherical
-harmonic, $y_0$, to unity. After all, this coefficient is not directly
-constrained by the data, as it merely sets the baseline intensity on the
-surface of the star and is therefore formally degenerate with the stellar 
-luminosity (which also cannot be directly inferred from the data). This
-choice further ensures a mean baseline of unity for the model 
-vector $\mathbf{f}$. We may therefore write
-%
-\begin{align}
-    \label{eq:inverse:fy1}
-    \bvec{f}
-    &=
-    \Doppler
-    \,
-    \bvec{s}_\bvec{0}
-    \,
-    +
-    \,
-    \Doppler
-    \,
-    \bvec{S_1}
-    \,
-    \bvec{y}_\bvec{1}
-    \quad,
-\end{align}
-%
-where the vector $\bvec{s_0}$ denotes the first column of $\bvec{S}$,
-the matrix $\bvec{S_1}$ denotes the remaining columns of $\bvec{S}$, and
-$\bvec{y_1}$ is the quantity we wish to solve for: the vector of spherical 
-harmonic coefficients of degree $l \ge 1$.
-
-Given prior mean $\boldsymbol{\mu}_\bvec{y_1}$ and covariance
-$\boldsymbol{\Lambda}_\bvec{y_1}$ on $\bvec{y_1}$, the MAP solution
-is given by
-%
-\begin{align}
-    \label{eq:inverse:y1hat}
-    \bvec{\hat{y}_1} &= 
-    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1}
-    \left(
-        \bvec{S_1}^\top\Doppler^\top
-        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
-        \left(\bvec{f} - \Doppler\bvec{s}_\bvec{0}\right)
-        +
-        {\boldsymbol{\Lambda}_\bvec{y_1}}^{-1} \boldsymbol{\mu}_\bvec{y_1}
-    \right)
-    \quad,
-\end{align}
-%
-with covariance
-%
-\begin{align}
-    \label{eq:inverse:y1cov}
-    \boldsymbol{\Sigma}_\bvec{\hat{y}_1} &= 
-    \left(
-        \bvec{S_1}^\top\Doppler^\top
-        {\boldsymbol{\Sigma}_\bvec{f}}^{-1}
-        \Doppler\bvec{S_1}
-        +
-        {\boldsymbol{\Lambda}_\bvec{y_1}}^{-1}
-    \right)^{-1}
-    \quad.
-\end{align}
-%
-If we choose a prior with zero mean ($\boldsymbol{\mu}_\bvec{y_1} = 0$)
-and a diagonal covariance that is constant for each spherical harmonic 
-order $m$,
-%
-\begin{align}
-    \boldsymbol{\Lambda}_\bvec{y_1} &=
-    \mathrm{diag} \left(
-        \sigma_1^2
-        \quad\quad\quad\quad
-        \sigma_1^2
-        \quad\quad\quad\quad
-        \sigma_1^2
-        \quad\quad\quad\quad
-        \sigma_2^2
-        \quad\quad\quad\quad
-        \sigma_2^2
-        \quad\quad\quad\quad
-        \sigma_2^2
-        \quad\quad\quad\quad
-        \sigma_2^2
-        \quad\quad\quad\quad
-        \sigma_2^2
-        \quad\quad\quad\quad
-        \cdots
-    \right)
-    \quad,
-\end{align}
-%
-we are in fact imposing an isotropic prior with an angular power spectrum
-given by $C_l = \sigma_l^2$
-\citep[e.g.,][]{Baldi2006}. This is especially useful if the typical
-angular scale of features on the surface of the star is known or if
-a Gaussian prior can be placed on it.
-
-\subsection{Solution for the spectrum}
-\label{sec:solve_s}
-If, on the other hand, the spatial intensity profile is known, the
-model for the flux vector may be written in terms of the spectrum $\bvec{s}$
-as
-%
-\begin{align}
-    \label{eq:inverse:fs}
-    \bvec{f}
-    &=
-    \Doppler
-    \,
-    \bvec{Y}
-    \,
-    \bvec{s}
-    \quad,
-\end{align}
-%
-where
-%
-\begin{align}
-    \label{eq:inverse:Y}
-    \setstackgap{L}{1.25\baselineskip}
-    \bvec{Y} =
-        \begin{pmatrix}
-            y_0\, \bvec{I}_{K'} \\
-            y_1\, \bvec{I}_{K'} \\
-            y_2\, \bvec{I}_{K'} \\
-            y_3\, \bvec{I}_{K'} \\
-            \cdots
-        \end{pmatrix}
-\end{align}
-%
-is a $(NK' \times K')$ matrix constructed by vertically stacking
-$N$ $(K' \times K')$ identity matrices, each multiplied by the
-corresponding coefficient of $\bvec{y}$. Given
-prior mean $\boldsymbol{\mu}_\mathbf{s}$ and covariance
-$\boldsymbol{\Lambda}_\mathbf{s}$ on $\mathbf{s}$, the MAP solution
-is given by
-%
-\begin{align}
-    \label{eq:inverse:shat}
-    \bvec{\hat{s}} &= 
-    \boldsymbol{\Sigma}_\mathbf{\hat{s}}
-    \left(
-        \bvec{Y}^\top\Doppler^\top
-        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
-        \bvec{f}
-        +
-        {\boldsymbol{\Lambda}_\mathbf{s}}^{-1} \boldsymbol{\mu}_\mathbf{s}
-    \right)
-    \quad,
-\end{align}
-%
-with covariance
-%
-\begin{align}
-    \label{eq:inverse:scov}
-    \boldsymbol{\Sigma}_\mathbf{\hat{s}} &= 
-    \left(
-        \bvec{Y}^\top\Doppler^\top
-        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
-        \Doppler\bvec{Y}
-        +
-        {\boldsymbol{\Lambda}_\mathbf{s}}^{-1}
-    \right)^{-1}
-    \quad.
-\end{align}
-
-\subsection{The full solution}
-In the previous two sections we showed how, if the stellar
-rest-frame spectrum is spatially constant and known \emph{a priori} 
-(from, say, a template spectrum), the posterior distribution
-for the surface map $\bvec{y}$ is \emph{analytic} 
-(Equations~\ref{eq:inverse:y1hat}
-and \ref{eq:inverse:y1cov}). Conversely, if the surface map is known,
-the posterior for the spectrum is also analytic 
-(Equations~\ref{eq:inverse:shat} and \ref{eq:inverse:scov}). Both sets of
-solutions require Gaussian priors on the quantities of interest, but these
-are easily interpretable. A Gaussian prior on
-the spherical harmonic coefficients of the surface map corresponds 
-to the angular power spectrum of the surface features, whereas a Gaussian
-prior on the spectrum can be used to correctly propagate uncertainties in
-the stellar spectrum from observational uncertainties on the stellar
-metallicity, temperature, etc.
-
-Importantly, the framework developed here allows one to analytically
-compute not only the ``optimal'' solution to the Doppler imaging problem,
-but also its uncertainty. The problem of re-constructing surface images
-of stars from spectra and/or light curves is fundamentally ill-posed because
-of intrinsic degeneracies and a large null space
-\citep[e.g.,][]{Luger2019} \xxx{more cites}. Coupled to uncertainties in
-the observations themselves, this makes the process of searching for the
-``optimal'' solution flawed at best, and meaningless at worst. Access to the
-full covariance matrix of the solution is therefore essential to assessing our
-confidence in the various features of the inferred surface maps.
-
-However, as we mentioned above, the Doppler imaging problem can be solved
-analytically for either the surface map or the spectrum, but not both. If
-neither are known exactly \emph{a priori}, which is quite often the case,
-we can still find the MAP solution quickly by guessing at an initial
-spectrum $\bvec{s}$ and iterating between optimizing for $\bvec{y}$ and
-optimizing for $\bvec{s}$. This bi-linear problem is not generally convex,
-but given a good starting point for $\bvec{s}$ and sufficient regularization
-on $\bvec{y}$, we find that it typically converges to the correct solution,
-especially after refinement with a non-linear solver;
-we discuss this in detail below.
-
-Once the MAP solution has been found for both $\bvec{s}$ and $\bvec{y}$,
-the covariance of one conditioned on the other can be computed from the
-formulae above. However, this is necessarily a lower bound on the true
-covariance of the solution, since it neglects any covariance \emph{between}
-$\bvec{s}$ and $\bvec{y}$. To \emph{correctly} account for this, one must
-resort to Monte Carlo methods or other sampling techniques. We discuss
-this further below.
-
-\section{Further considerations}
-\label{sec:bellswhistles}
-
-Before we demonstrate our formalism in practice, we consider three
-modifications to our model that are often required when modeling real
-data. Below we discuss what to do when the relative brightness of the
-star across different observations is unknown (\S\ref{sec:norm}), how
-to account for the effects of limb darkening (\S\ref{sec:ld}), and how
-to model stars whose local spectra differ within and outside of starspots
-(\S\ref{sec:eigen}).
-
-\subsection{Unknown continuum normalization}
-\label{sec:norm}
-%
-Consider the star depicted in Figure~\ref{fig:spot}. When the spot is in
-view, absorption lines become distorted due to the suppression of either
-blueshifted or redshifted light. However, what is not shown in the figure
-is the fact that overall, the star also gets \emph{dimmer}: the 
-continuum level drops in the presence of the spot. Unfortunately, 
-spectrographs are not usually designed to measure this, since the
-change in the star's overall brightness from one observation to the next
-is often dwarfed by (unknown) changes in the spectrograph sensitivity. 
-For this reason, the spectra are usually normalized to have a
-fixed baseline continuum, and Equation~\ref{eq:linear:f} is no longer
-a good model for the data.
-
-One option is to collect simultaneous photometry on the target in a band
-similar to the wavelength range observed, and use this light curve to
-(un-)normalize the spectral timeseries $\bvec{f}$. However, when this is
-not an option, our model for $\bvec{f}$ (Equation~\ref{eq:linear:f}) must
-be amended.
-
-%
-\begin{align}
-    \label{eq:norm:f}
-    \bvec{f}
-    &=
-    \frac{
-        \Doppler
-        \,
-        \azero
-    } {
-        \bvec{b}
-    }
-    \quad,
-\end{align}
-%
-where $\bvec{b}$ is the baseline and the vector division is
-performed elementwise. When $\azero$ is given by Equation~(\ref{eq:inverse:azero}),
-the baseline $\bvec{b}$ is simply the total (wavelength-integrated) flux
-at each epoch, repeated for every element in each spectrum. 
-Based on \citet{Luger2019}, this can be computed as a purely linear operation 
-on the spherical harmonic vector $\bvec{y}$:
-%
-\begin{align}
-    \label{eq:norm:b}
-    \bvec{b}
-    &=
-    %
-    \begin{pmatrix}
-        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_0) \\
-        \cdots \\
-        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_0) \\
-        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_1) \\
-        \cdots \\
-        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_1) \\
-        \cdots \\
-        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_{M-1}) \\
-        \cdots \\
-        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_{M-1})
-    \end{pmatrix}
-    \bvec{y}
-    %
-    \nonumber \\[0.5em]
-    &\equiv
-    \bvec{B} \, \bvec{y}
-\end{align}
-%
-where $\bvec{r}$ is given by Equation~(18) in \citet{Luger2019},
-$\bvec{A_1}$ is given in Appendix B of \citet{Luger2019}, and $\bvec{R}(t)$
-is the rotation matrix defined previously.
-
-Given this new equation, we must change how we approach the inverse problem
-(\S\ref{sec:inverse}). When solving for the spectrum given the spherical 
-harmonic vector (\S\ref{sec:solve_s}), we need only make the replacements
-$\bvec{f} \rightarrow \nicefrac{\bvec{f}}{\bvec{B}\, \bvec{y}}$
-and 
-$\boldsymbol{\Sigma}_\mathbf{f} \rightarrow \nicefrac{\boldsymbol{\Sigma}_\mathbf{f}}{(\bvec{B}\, \bvec{y})^2}$ 
-in Equations~(\ref{eq:inverse:shat}) and (\ref{eq:inverse:scov}).
-However, when solving for the spherical harmonic vector given the spectrum
-(\ref{sec:solve_y}), the problem is no longer linear in $\bvec{y}$, as the
-vector of interest appears in both the numerator and the denominator:
-%
-\begin{align}
-    \label{eq:norm:fy}
-    \bvec{f}
-    &=
-    \frac{
-        \bvec{D}
-        \,
-        \bvec{S}
-        \,
-        \bvec{y}
-    }{
-        \bvec{B}
-        \,
-        \bvec{y}
-    }
-    \quad.
-\end{align}
-%
-While we can solve for $\bvec{y}$ using a non-linear optimizer, it is
-often the case that the denominator in Equation~(\ref{eq:norm:fy}) is close
-to unity; i.e., the total flux from the star typically varies by only a
-few percent. When this is the case, it is straightforward to linearize
-this equation.
-Following the notation from \S\ref{sec:solve_y}, we may therefore write
-%
-\begin{align}
-    \bvec{f}
-    &=
-    \frac{
-        \bvec{D} \, \bvec{s_0}
-        \,
-        + 
-        \,
-        \bvec{D}\bvec{S_1}
-        \,
-        \bvec{y_1}
-    }{
-        \bvec{B_0}
-        \,
-        +
-        \bvec{B_1}
-        \,
-        \bvec{y_1}
-    }
-    \quad,
-\end{align}
-%
-where $\bvec{B_0} = \bvec{1}$ is the first column of $\bvec{B}$
-and $\bvec{B}_\bvec{1}$ denotes the
-matrix composed from the remaining $N - 1$ columns of $\bvec{B}$.
-Expanding the expression above about 
-$\bvec{B_1} \bvec{y_1} = \bvec{0}$ and keeping only terms up to
-first order, we have
-%
-\begin{align}
-    \label{eq:norm:fapprox}
-    \bvec{f}
-    &\approx
-    \left(
-        \bvec{D} \, \bvec{s_0}
-        \,
-        + 
-        \,
-        \bvec{D}\bvec{S_1}
-        \,
-        \bvec{y_1}
-    \right)
-    \circ
-    \left(
-        \bvec{1}
-        \,
-        -
-        \bvec{B_1}
-        \,
-        \bvec{y_1}
-    \right)
-    \nonumber \\
-    &\approx
-    \left(
-        \bvec{D}\bvec{S_1}
-        \,
-        -
-        \bvec{C}
-    \right)
-    \bvec{y_1}
-    \,
-    +
-    \,
-    \bvec{D} \, \bvec{s_0}
-    \quad,
-\end{align}
-%
-where $\circ$ denotes an elementwise product and $\bvec{C}$ is a matrix
-constructed by multiplying each row of $\bvec{B_1}$ by the
-corresponding element of $\bvec{D}\bvec{s_0}$.
-%
-This equation is now
-linear in $\bvec{y}_\bvec{1}$, so we may solve the least-squares problem
-as before:
-%
-\begin{align}
-    \label{eq:norm:yhat}
-    \bvec{\hat{y}_1} &= 
-    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1}
-    \left(
-        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
-        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
-        (\bvec{f} - \bvec{D}\bvec{s_0})
-        +
-        {\boldsymbol{\Lambda}_{\mathbf{y}_\bvec{1}}}^{-1} \boldsymbol{\mu}_{\mathbf{y}_\bvec{1}}
-    \right)
-    \quad,
-\end{align}
-%
-with covariance
-%
-\begin{align}
-    \label{eq:norm:ycov}
-    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1} &= 
-    \left(
-        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
-        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
-        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)
-        +
-        {\boldsymbol{\Lambda}_{\mathbf{y}_1}}^{-1}
-    \right)^{-1}
-    \quad.
-\end{align}
-%
-Note, importantly, that these equations are valid only in the limit that the
-change in the total flux from the star is small. Nevertheless, even in the 
-general case, we find that solving this linear problem yields a good
-starting point for a non-linear optimization, which we revisit in more
-detail below.
-
-\subsection{Limb darkening}
-\label{sec:ld}
-Thus far we have avoided mention of limb darkening, whose effect
-on the observed spectrum can often be significant. A proper treatment of
-limb darkening requires solution of radiative transfer equations and
-should account for the temperature and composition gradients in the
-stellar atmosphere. However, in the spirit of data-driven inference, we 
-can approximate the effect of limb darkening by weighting the spatial
-component of our map by the limb darkening profile of the star, which can 
-either be imposed or learned from the data. For a polynomial limb darkening
-law of the form
-%
-\begin{align}
-    \label{eq:ld:I}
-    \frac{I(\mu)}{I(\mu = 1)} = 1 - \sum_{n=1}^{n_\mathrm{max}} u_n(1 - \mu)^n
-    \quad,
-\end{align}
-%
-where $\mu = z = \sqrt{1 - x^2 - y^2}$ is the radial coordinate on the 
-projected disk and $u_n$ is a limb darkening coefficient, the effect of 
-limb darkening on the stellar map can be expressed exactly as a linear 
-operation on the spherical harmonic coefficient vector 
-\citep{Luger2019,Agol2019}. This can be understood by noting that all terms
-in Equation~(\ref{eq:ld:I}) are strictly polynomials in $x$, $y$, and $z$,
-all of which can be expressed exactly as sums of spherical harmonics
-\citep{Luger2019}. When weighting the surface intensity by the limb darkening
-profile, the resulting intensity is simply a product of spherical harmonics,
-which is itself a sum of spherical harmonics. Given a limb darkening law
-of degree $n_\mathrm{max}$, we can always construct a matrix $\bvec{L}$
-that transforms a spherical harmonic vector $\bvec{y}$ of degree
-$l_\mathrm{max}$ to a limb-darkened spherical harmonic vector $\bvec{y'}$
-of degree $l_\mathrm{max} + n_\mathrm{max}$. As an example, consider 
-a map of degree $l_\mathrm{max} = 1$ and the linear limb darkening law
-($n_\mathrm{max} = 1$).
-The transformation matrix from $\bvec{y}$ to $\bvec{y'}$ is
-%
-\begin{align}
-    \label{eq:ld:L}
-    \setstackgap{L}{1.5\baselineskip}
-    \bvec{L} =
-        \frac{1}{1 - \frac{u_1}{3}}
-        \begin{pmatrix}
-        \quadquad1-u_1\quadquad & 0                         & \frac{u_1}{\sqrt{3}}      & 0                         \\
-        0                       & \quadquad1-u_1\quadquad   & 0                         & 0                         \\
-        \frac{u_1}{\sqrt{3}}    & 0                         & \quadquad1-u_1\quadquad   & 0                         \\
-        0                       & 0                         & 0                         & \quadquad1-u_1\quadquad   \\
-        0                       & 0                         & 0                         & 0                         \\
-        0                       & \frac{u_1}{\sqrt{5}}      & 0                         & 0                         \\
-        0                       & 0                         & \frac{2u_1}{\sqrt{15}}    & 0                         \\
-        0                       & 0                         & 0                         & \frac{u_1}{\sqrt{5}}      \\
-        0                       & 0                         & 0                         & 0          
-        \end{pmatrix}
-        \quad.
-\end{align}
-%
-The columns of $\bvec{L}$ are constructed from the coefficient vectors of
-each transformed spherical harmonic, which are in turn computed by 
-multiplying each spherical harmonic by the spherical harmonic decomposition 
-of the particular limb darkening law.
-Figure~\ref{fig:ld} shows this transformation with $u_1 = 1$ applied to each
-of the first four spherical harmonics.
-%
-\begin{figure}[t!]
-    \begin{centering}
-    \includegraphics[width=0.6\linewidth]{figures/ld.pdf}
-    \oscaption{ld}{%
-        Illustration of the limb darkening transformation given by
-        Equation~(\ref{eq:ld:L}) for a linear limb darkening law with
-        $u_1 = 1$. Each row shows a spherical harmonic before
-        (left) and after (right) transformation by $\bvec{L}$.
-        \label{fig:ld}
-    }
-    \end{centering}
-\end{figure}
-%
-
-Now, to incorporate limb darkening into our model, we must modify how we
-compute the Doppler design matrix $\Doppler$
-(Equation~\ref{eq:linear:D} and Figure~\ref{fig:linalg}). Recall that
-this matrix is constructed by vertically stacking the submatrices 
-$\Doppler_m$ given by Equation~(\ref{eq:linear:Dm}), which we now compute
-as
-%
-\begin{align}
-    \label{eq:ld:Dm}
-    \Doppler_m =
-    \begin{pmatrix}
-        \quad
-        \bvec{T}(\kT_0)
-        \quad
-        &
-        \quad
-        \bvec{T}(\kT_1)
-        \quad
-        &
-        \quad
-        \cdots
-        \quad
-        &
-        \quad
-        \bvec{T}(\kT_{N'})
-        \quad
-    \end{pmatrix}
-    (\bvec{L} \, \bvec{R}(t_m) \otimes \bvec{I}_{K'})
-    \quad,
-\end{align}
-%
-where we have replaced the rotation matrix $\bvec{R}(t_m)$ with
-the linear transformation $\bvec{L}\,\bvec{R}(t_m)$, which first rotates the
-input spherical harmonic coefficient vector to the correct phase then
-limb darkens it. Note also that the terms in the convolution kernel $\kT$
-are now indexed from 0 to $N' = (l_\mathrm{max} + n_\mathrm{max} + 1)^2$,
-where $n_\mathrm{max}$ is the degree of the limb darkening operator.
-
-Note that it is also possible to model wavelength-dependent limb darkening
-in this fashion. The procedure is similar, except that the limb darkening
-coefficients $u_n$ are now functions of $\lnlam$, and each element of the
-matrix $\bvec{L}$ is now a vector of length $K'$. The submatrices
-$\Doppler_m$ may be written as
-%
-\begin{align}
-    \label{eq:ld:Dmwav}
-    \resizebox{0.91\textwidth}{!}{
-    $
-    \Doppler_m =
-    \begin{pmatrix}
-        \quad
-        \bvec{T}(\kT_0)
-        \quad
-        &
-        \quad
-        \bvec{T}(\kT_1)
-        \quad
-        &
-        \quad
-        \cdots
-        \quad
-        &
-        \quad
-        \bvec{T}(\kT_{N'})
-        \quad
-    \end{pmatrix}
-    \begin{pmatrix}
-        \mathrm{diag}(\bvec{L}_{0,0})
-        &
-        \mathrm{diag}(\bvec{L}_{0,1})
-        &
-        \cdots
-        &
-        \mathrm{diag}(\bvec{L}_{0,N})
-        \\
-        \mathrm{diag}(\bvec{L}_{1,0})
-        &
-        \mathrm{diag}(\bvec{L}_{1,1})
-        &
-        \cdots
-        &
-        \mathrm{diag}(\bvec{L}_{1,N})
-        \\
-        \cdots
-        &
-        \cdots
-        &
-        \ddots
-        &
-        \cdots
-        \\
-        \mathrm{diag}(\bvec{L}_{N',0})
-        &
-        \mathrm{diag}(\bvec{L}_{N',1})
-        &
-        \cdots
-        &
-        \mathrm{diag}(\bvec{L}_{N',N})
-    \end{pmatrix}
-    (\bvec{R}(t_m) \otimes \bvec{I}_{K'})
-    $
-    }
-    \quad,
-\end{align}
-%
-where $\mathrm{diag}(\bvec{v})$ denotes the $(K' \times K')$ diagonal matrix
-constructed by placing the vector $\bvec{v}$ along the main diagonal.
-
-\subsection{Multiple spectral components}
-\label{sec:eigen}
-%
-In our discussion so far we have focused on the particular case where the
-spectral/spatial decomposition of the stellar surface can be expressed as 
-the outer product of two vectors (Equation~\ref{eq:inverse:azero}). As we
-mentioned previously, this corresponds to the case where the spectrum is
-constant across the surface of the star except for a spatially-variable 
-amplitude: i.e., spots have the same spectrum as the rest of the star, but
-emit less flux overall. However, most of the formalism developed here also
-applies to the more general case where the spectrum at a particular point
-on the surface of the star is a linear combination of several different
-spectral components. In this case, the map vector $\azero$
-may be written as the sum over $J$ spectra $\bvec{s}_j$, each of which is dotted into
-a different vector of spherical harmonic coefficients $\bvec{y}_j^\top$:
-%
-\begin{align}
-    \label{eq:eigen:azero}
-    \azero 
-        &= 
-        \sum_{j=0}^{J-1}\mathrm{vec}\left( \bvec{s}_j \, \bvec{y}_j^\top \right) \\
-        &=
-        \mathrm{vec}\left( \boldsymbol{\mathbb{S}} \, \boldsymbol{\mathbb{Y}}^\top \right) \quad,
-\end{align}
-%
-where $\boldsymbol{\mathbb{S}}$ is the $(K' \times J)$ matrix whose columns are
-the $J$ spectral components and $\boldsymbol{\mathbb{Y}}^\top$ is the
-$(J \times N)$ matrix whose rows are the corresponding $J$ spherical harmonic
-coefficient vectors.
-
-The model remains linear in both the spherical harmonic coefficients and the
-spectral components, and the procedures outlined in \S\ref{sec:inverse} may
-still be followed to solve the inverse problem, provided we unroll these
-matrices into vectors, letting
-$\mathbf{s} = \mathrm{vec}(\boldsymbol{\mathbb{S}})$
-and
-$\mathbf{y} = \mathrm{vec}(\boldsymbol{\mathbb{Y}})$.
-A detailed discussion of this general case is deferred to future work,
-but we present an example of a two-component stellar spectrum in the
-following section.
-
-\section{Application to a spotted star}
-\label{sec:spotstar}
-
-In this section we apply the formalism developed in \S\ref{sec:inverse}
-and \S\ref{sec:bellswhistles} to a synthetic dataset of a rapidly
-rotating spotted star. This section is motivated by the
-examples in \cite{Vogt1987}, who generated rotationally-broadened spectra
-of a rapidly-rotating star with the letters ``VOGT'' painted across 
-the northern hemisphere. In that paper, the authors
-generated synthetic line profiles of the Fe I 
-$\lambda 6430$ absorption line with equivalent width $W \approx 10$~km/s
-and from these computed rotationally broadened spectra for a star at an 
-inclination $i=40^\circ$ rotating at projected velocity $v\sin i = 40$~km/s.
-The spectra were computed at 16 equally spaced rotational phases and
-downsampled to 32 wavelength bins per epoch, for a total of 512 data
-points.
-
-\begin{figure}[t!]
-    \begin{centering} 
-    \includegraphics[width=0.85\linewidth]{figures/spot_setup.pdf}
-    \oscaption{spot_setup}{%
-        The basic setup for the \spot problem. We compute the 
-        $l_\mathrm{max} = 15$ spherical harmonic expansion of 
-        a map where the word ``SPOT'' has been placed across the northern 
-        hemisphere (top left). Each point on the surface is
-        given the same spectrum, composed of a sum of synthetic 
-        Gaussian absorption lines (blue curve in the bottom panel). 
-        The specific intensity
-        at each point on the surface is equal to this spectrum weighted
-        by the intensity of the map, which is close to zero within the
-        spot (point labeled \texttt{B}) and close ot unity 
-        outside the spot (point labeled \texttt{A}).
-        %
-        To generate the synthetic dataset (orange curves in the bottom
-        panel), the star is inclined at
-        $40^\circ$ with respect to the line of sight and the disk-integrated
-        spectrum is computed at 16 equally-spaced phases between
-        $-180^\circ$ and $180^\circ$ (middle panel).
-        %
-        The grey regions indicate wavelength
-        regions outside the observation window, but whose features still
-        contribute to the observed spectrum due to rotational broadening.
-        \label{fig:spot_setup}
-    }
-    \end{centering}
-\end{figure}
-
-We repeat the same experiment here using our new formalism, except we
-instead generate a stellar surface with the word ``SPOT'' written across
-the northern hemisphere (top left panel of Figure~\ref{fig:spot_setup}).
-We do this by computing the $l_\mathrm{max} = 15$ spherical harmonic
-decomposition of an image of the word, generating a set of 
-$N = (l_\mathrm{max} + 1)^2 = 256$ spherical harmonic coefficients 
-$\bvec{y} = (1 \quadquad \bvec{y_1})$.
-
-Our input spectrum $\bvec{s}$ was generated at high resolution 
-($R \equiv \frac{\lambda}{\Delta\lambda} = 300,000$)
-centered at a reference wavelength $\lambda_\mathrm{r} = 6430$ nm
-(blue curve in the bottom panel of Figure~\ref{fig:spot_setup}).
-The spectrum consists of a Gaussian absorption line in log-wavelength
-($\lnlam$) space with amplitude $0.5$ and standard deviation 
-$\sigma_{\lnlam} = 1.4\times 10^{-5}$. This corresponds to a FWHM of about
-$2.355~\sigma_{\lnlam}~\lambda_\mathrm{r}~\approx~0.2$ nm or, in velocity space,
-$2.355~\sigma_{\lnlam}~c~\approx~10$~km/s, equal to the value used in
-\citet{Vogt1987}. Unlike \citet{Vogt1987}, we add 20 additional small
-absorption lines at random positions throughout the spectrum, all of 
-the same FWHM but of varying depths, including some line blends. In total,
-the rest frame spectrum $\bvec{s}$ consists of $K = 201$ log-wavelength bins in the range
-$-\Delta\lnlam < \lnlam < \Delta\lnlam$ for $\Delta\lnlam = 3.3\times 10^{-4}$ plus an additional 
-%
-\begin{align}
-    W - 1 &= \frac{v\sin i}{c} \frac{K}{\Delta\lnlam} - 1 \nonumber \\
-          &= \left(\frac{40~\mathrm{km/s}}{3\times 10^5~\mathrm{km/s}}\right)
-          \left(\frac{201}{3.3 \times 10^{-4}}\right)  - 1 \nonumber \\ 
-          &= 80
-\end{align}
-%
-log-wavelength bins of padding (40 on either side) to eliminate edge
-effects due to the convolution, for a total of 
-$K' = 281$ wavelength bins. As in \citet{Vogt1987},
-we assume a projected velocity of $v\sin i = 40$ km/s and an inclination
-$i = 40^\circ$.
-
-\xxx{note on the intensities at A and B.}
-
-Given $\bvec{y_1}$ and $\bvec{s}$, we use Equation~(\ref{eq:deconv:F}) to
-compute the data vector $\bvec{f}$
-at $M = 16$ equally spaced rotational phases; these phases are shown in orthographic
-projection (as an observer would see the star) in the center
-panel of Figure~\ref{fig:spot_setup}. The synthetic spectra for each phase
-are shown as the orange curves in the bottom panel of the figure (note the
-different scaling, as all spectral lines become shallower due to the
-broadening). We assume a wavelength-independent,
-quadratic limb darkening law with $u_1 = 0.5$ and $u_2 = 0.25$. Finally,
-we divide the flux by the baseline at each epoch (Equation~\ref{eq:norm:b})
-and add random Gaussian noise with amplitude $\sigma_\bvec{f} = 10^{-4}$ to
-simulate a very high signal-to-noise ratio (SNR) spectrum. The mean
-standard deviation in each wavelength bin across all 16 epochs in the
-noiseless data vector is about $10^{-2}$, so our choice of $\sigma_\bvec{f}$
-corresponds to SNR $\sim$ 100 in each of the 201 wavelength bins of $\bvec{f}$.
-%
-%For reference, \citet{Vogt1987} report SNRs per 60 m\AA\, pixel, while our
-%resolution elements are approximately $\lambda_r\Delta\lnlam/K \approx 100$ m\AA\,
-%across, so our SNR in the same units as \citet{Vogt1987} is about 80.
-%
-% TODO: Perhaps Vogt computes the "signal" as the line depth, rather than
-% as the amplitude of the perturbations? Check this.
-
-% We Recover images with an effective resolution of $12^\circ$.
-
-In the following sections we discuss various approaches to 
-solving the Doppler imaging problem for this dataset.
-Unless otherwise noted, in all experiments we adopt a Gaussian prior
-for the spherical harmonic coefficients $\bvec{y_1}$ with mean
-$\boldsymbol{\mu}_\bvec{y_1} = \bvec{0}$ and covariance
-$\boldsymbol{\Lambda}_\bvec{y_1} = (10^{-2})^2\bvec{I}$,
-corresponding to a flat power spectrum prior.
-We place a Gaussian process prior on the spectrum $\bvec{s}$ with mean
-$\boldsymbol{\mu}_\bvec{s} = \bvec{1}$ and a covariance matrix
-$\boldsymbol{\Lambda}_\bvec{s}$ computed from
- a Mat\'ern-3/2 kernel with amplitude $\sigma_\bvec{s} = 0.3$
-and lengthscale $\rho_\bvec{s} = 3\times 10^{-5}$.
-
-\subsection{Known baseline and spectrum}
-%
-In our first experiment, we attempt to infer the stellar map assuming
-we have perfect knowledge of the rest frame spectrum $\bvec{s}$ and
-the baseline $\bvec{b}$ (Equation~\ref{eq:norm:b}). 
-This is analogous to the case where a good physical model exists for
-the stellar spectrum and simultaneous photometry is available to
-constrain the baseline variations.
-As we showed in
-\S\ref{sec:solve_y}, the posterior distribution for the map coefficients 
-$\bvec{y_1}$ is analytic in this case, with mean given by Equation~(\ref{eq:inverse:y1hat})
-and covariance given by Equation~(\ref{eq:inverse:y1cov}). Note that
-we must first scale the data vector $\bvec{f}$ by $\bvec{b}$ (which in this
-case is known).
-
-\begin{figure}[p!]
-    \begin{centering}
-    \includegraphics[width=0.49\linewidth]{figures/spot_y1_timeseries.pdf}
-    \includegraphics[width=0.49\linewidth]{figures/spot_y1_rect.pdf}
-    \oscaption{spot_y1}{%
-        The solution to the \spot problem at high SNR when both 
-        the rest frame spectrum and the baseline are known.
-        The panel on the left shows the inferred map at each of the 16
-        epochs, alongside the observed spectrum (black points) and the
-        best-fit model (orange lines). The rectangular projection of the
-        original map is shown at the top right; the inferred map is
-        displayed below it. The bottom panel shows the posterior uncertainty
-        as a function of latitude and longitude, ranging from close to zero
-        in the northern hemisphere to $\sigma_\mathrm{prior} \approx 10\%$
-        below a latitude of $-30^\circ$. The latter is the uncertainty
-        associated with our particular choice of prior, as the southernmost
-        latitudes of the star are never visible to the observer.
-        \label{fig:spot_y1}
-    }
-    \end{centering}
-\end{figure}
-
-The results are shown in Figure~\ref{fig:spot_y1}. The left hand panel
-shows the inferred map alongside the data
-(black points) and best fit model (orange curves) at each of the 16 epochs.
-The panels on the right show the true map (top), the inferred map (center)
-and the posterior pointwise uncertainty (bottom) on a rectangular
-latitude-longitude grid. The uncertainty on the vector of pixels $\bvec{p}$ where
-we evaluate the map is equal to the square root of the diagonal of
-the posterior covariance matrix for the pixel values, computed from
-%
-\begin{align}
-    \label{eq:spotstar:uncert}
-    \boldsymbol{\Sigma}_\bvec{p} = \bvec{P} \boldsymbol{\Sigma}_\bvec{\hat{y}_1}^{-1} \bvec{P}^\top
-\end{align}
-%
-where $\bvec{P}$ is the change-of-basis matrix from spherical harmonic 
-coefficients to pixels on the grid.
-
-The inferred map is nearly indistinguishable from the true map, save for a
-few small differences, particularly below the stellar equator. This is 
-captured by the uncertainty, which increases
-south of $+30^\circ$ latitude, reaching a maximum at $-30^\circ$, below
-which the uncertainty is constant at about 10\%. This is due to the fact
-that regions below $-40^\circ$ latitude are never in view from the
-observer's perspective, while regions between about $-30^\circ$ and
-$-40^\circ$ are so strongly limb-darkened that the data contains little
-information about them. The particular value of the uncertainty in this
-region---10\%---is the uncertainty associated with the prior, which can
-be computed by replacing $\boldsymbol{\Sigma}_\bvec{\hat{y}_1}$ with 
-$\boldsymbol{\Lambda}_\bvec{y_1}$ in Equation~(\ref{eq:spotstar:uncert}).
-
-\subsection{Known spectrum, unknown baseline}
-%
-We next investigate the case where the spectrum is known exactly, but
-the baseline is not.
-
-\begin{figure}[p!]
-    \begin{centering}
-    \includegraphics[width=0.49\linewidth]{figures/spot_y1b_timeseries.pdf}
-    \includegraphics[width=0.49\linewidth]{figures/spot_y1b_rect.pdf}
-    \\[0.5em]
-    \includegraphics[width=0.405\linewidth]{figures/spot_y1b_baseline.pdf}
-    \includegraphics[width=0.575\linewidth]{figures/spot_y1b_coeffs.pdf}
-    \oscaption{spot_y1b}{%
-        Similar to Figure~\ref{fig:spot_y1}, but assuming the baseline
-        is not known. The panel at the bottom left shows the true baseline
-        (blue) and the inferred baseline (orange), along with its $1\sigma$
-        uncertainty. The large offset between the two highlights one of the
-        fundamental degeneracies of the problem: since most of the southern
-        hemisphere of the star is never visible, the coefficient of the
-        $Y_{1,-1}$
-        (\raisebox{-0.2em}{\includegraphics[width=1em]{figures/Y1m1.pdf}})
-        spherical harmonic is not constrained by the data, resulting in 
-        an unknowable additive offset in the baseline.
-        This effect can be seen also in (\emph{a}) the inferred map, 
-        where the background 
-        intensity in the northern hemisphere is significantly larger than 
-        that in the southern hemisphere, and (\emph{b}) the spherical
-        harmonic coefficients (bottom right), where a large discrepancy is
-        visible between the true and inferred values of the first two
-        coefficients.
-        \label{fig:spot_y1b}
-    }
-    \end{centering}
-\end{figure}
-
-\begin{figure}[p!]
-    \begin{centering}
-    \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_timeseries.pdf}
-    \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_rect.pdf}
-    \\[0.5em]
-    \includegraphics[width=0.405\linewidth]{figures/spot_y1bs_baseline.pdf}
-    \includegraphics[width=0.575\linewidth]{figures/spot_y1bs_coeffs.pdf}
-    \\[0.5em]
-    \includegraphics[width=0.98\linewidth]{figures/spot_y1bs_spectrum.pdf}
-    \oscaption{spot_y1bs}{%
-        Similar to Figure~\ref{fig:spot_y1}, but assuming we have no
-        information about either the spectrum, the baseline, or the map
-        coefficients. The bottommost panel now shows the true rest frame
-        spectrum (blue line), the initial guess based on a deconvolution
-        (dotted orange line), and the inferred spectrum (orange line, with
-        shaded $1\sigma$ uncertainty).
-        \label{fig:spot_y1bs}
-    }
-    \end{centering}
-\end{figure}
-
-\begin{figure}[p!]
-    \begin{centering}
-    \includegraphics[width=0.98\linewidth]{figures/inclinations.pdf}
-    \oscaption{inclinations}{%
-        Recovered \spot map as a function of stellar inclination. The
-        rest frame spectrum is assumed to be known exactly, but the
-        baseline is not. At very low inclinations, the small
-        projected velocities begin to degrade the spatial resolution of
-        the inferred map, while at inclinations close to $90^\circ$ there
-        is a degeneracy between the northern and southern hemispheres.
-        \label{fig:inclinations}
-    }
-    \end{centering}
-\end{figure}
-
-\begin{figure}[p!]
-    \begin{centering}
-    \includegraphics[width=0.98\linewidth]{figures/snr.pdf}
-    \oscaption{snr}{%
-        Recovered \spot map as a function of SNR per resolution element.
-        The quality of the inferred map in the northern hemisphere improves
-        with SNR, but at very high SNR the region surrounding the global
-        optimum becomes so small that our optimization methods struggle to
-        converge on the correct solution.
-        \label{fig:snr}
-    }
-    \end{centering}
-\end{figure}
-
-\begin{figure}[t!]
-    \begin{centering}
-    \includegraphics[width=\linewidth]{figures/twospec.pdf}
-    \oscaption{twospec}{%
-        An example of a star whose spectrum is different within the spot
-        (\texttt{B}) and outside of the spot (\texttt{A}). Everywhere on 
-        the surface, the spectrum is a linear combination of two
-        ``eigenspectra'' ($s_1$ and $s_2$).
-        As in Figure~\ref{fig:spot_y1bs}, we assume
-        we do not know the map, the baseline, or either of the eigenspectra.
-        The top row shows the true values for the map and the spectra, and
-        the bottom row shows our inferred values.
-        \label{fig:twospec}
-    }
-    \end{centering}
-\end{figure}
-
-\section{Discussion}
-\label{sec:discussion}
-%
-\xxx{In progress...}
-Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires 
-first the rotation of the $(\lmax + 1)^2$
-$\kT$ kernels (each of length $W$) to the correct stellar 
-rotational phase, an operation that scales approximately
-as $W \lmax^3$,
-followed by $(\lmax + 1)^2$
-linear convolutions of the rotated $\kT$ kernels with the 
-spectral components (each of length $K$), which scales
-approximately as $W K \lmax^2$. Since typically $K \gg \lmax$,
-the latter computation dominates and the entire evaluation 
-takes $\mathcal{O}(W K \lmax^2)$ operations.
-
-\xxx{We are not addressing differential rotation and convective blueshift.}
-\xxx{Telluric lines could be treated much as in Figure~\ref{fig:twospec}.}
-\xxx{Instrumental profile is another Toeplitz matrix.}
-
-\section{Conclusions}
-\label{sec:conclusions}
-\xxx{Hello.}
-
-%
-%
-%
-%
-\clearpage
-\appendix
-%
-%
-%
-%
-
-\section{Solving the $\kT$ integral}
-%
-In this section we will show how to compute the integral in
-Equation~(\ref{eq:kT:kT}), yielding the terms of the convolution
-kernel $\kT$. It is convenient to first change basis from spherical harmonics to 
-polynomials on the sphere:
-%
-\begin{align}
-    \label{eq:appendix:kT}
-    \kT(\lnlam, \Dargs) 
-    &=    
-    \int\limits_{-\sqrt{1 - x^2}}^
-                {\sqrt{1 - x^2}}
-    \pbasis
-    \Big(x, y\Big)
-    \mathrm{d}y
-    \,
-    \AOne
-    \nonumber \\[0.5em]
-    &\equiv
-    \rhoT(\lnlam, \Dargs) 
-    \,
-    \AOne
-    \quad,
-\end{align}
-%
-where $\AOne$ is the change of basis matrix from spherical harmonics
-to polynomials \citep[Equation B11 in][]{Luger2019} and
-%
-\begin{align}
-    \pbasis(\x) \equiv 
-\Big( 
-    1 \quad\quad\quad\quad\quad\quad 
-    x \quad\quad\quad\quad\quad\quad 
-    z \quad\quad\quad\quad\quad\quad 
-    y \quad\quad\quad\quad\quad\quad 
-    x^2 \quad\quad\quad\quad\quad\quad 
-    xz \quad\quad\quad\quad\quad\quad 
-    xy \quad\quad\quad\quad\quad\quad
-    yz \quad\quad\quad\quad\quad\quad 
-    y^2 \quad\quad\quad\quad\quad\quad
-    ... 
-\Big)^\top
-\quad,
-\end{align}
-%
-is the polynomial basis \citep[Equation 7][]{Luger2019}. 
-The $n^\mathrm{th}$ term of the polynomial basis
-is a polynomial in $x$, $y$, and $z = \sqrt{1 - x^2 - y^2}$:
-%
-\begin{proof}{PolynomialBasis}
-    \pbasisn
-    &=
-    x^i y^j z^k
-\end{proof}
-%
-where $i, j, k$ are integers given by
-%
-\begin{proof}{PolynomialBasis}
-    \label{eq:kT:lm}
-    i &= \floor*{\Lambda - \Delta}
-    \nonumber \\[0.5em]
-    j &= \floor*{\Delta}
-    \nonumber \\[0.5em]
-    k &= \ceil*{\Delta} - \floor*{\Delta}
-\end{proof}
-%
-with
-%
-\begin{proof}{PolynomialBasis}
-    \Lambda &= \floor*{\sqrt{n}}
-    \nonumber \\[0.5em]
-    \Delta &= \frac{n - \Lambda^2}{2}
-    \quad .
-\end{proof}
-%
-We may now explicitly write down the $n^\mathrm{th}$ term of 
-the vector $\rhoT(\lnlam, \Dargs)$ in Equation~(\ref{eq:appendix:kT}),
-%
-\begin{align}
-    \label{eq:kT:sTexpression}
-    \rho_n(\lnlam, \Dargs) 
-    &=    
-    \rho_{i,\,j,\,k}(\lnlam, \Dargs) 
-    =    
-    x^i
-    \int\limits_{-\sqrt{1 - x^2}}^
-                {\sqrt{1 - x^2}}
-        y^j
-        \left(1 - x^2 - y^2\right)^{\frac{k}{2}} \,
-    \mathrm{d}y 
-    \quad .
-\end{align}
-%
-When $i = k = 0$, the integral is easy to evaluate:
-%
-\begin{align}
-    \rho_{i,\,j,\,0}(\lnlam_0) 
-    &=    
-    \begin{cases}
-        2 \left( 1 - x^2 \right)^\frac{j + 1}{2} 
-        \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad 
-        &  j \, \mathrm{even} \\
-        0 & j \, \mathrm{odd} \quad .
-    \end{cases}
-\end{align}
-%
-The general term may be computed from the recurrence relation
-%
-\begin{align}
-    \rho_{0,\,j,\,0}(\lnlam_0) = \frac{j - 1}{j + 1} \big(1 - x^2\big) \rho_{0,\,j-2,\,0}
-\end{align}
-%
-provided 
-%
-\begin{align}
-    \rho_{0,\,0,\,0} &= 2 \sqrt{1-x^2} \nonumber \\
-    \rho_{0,\,1,\,0} &= 0 \quad.
-\end{align}
-%
-When $i = 0$ and $k = 1$, we may substitute $y = \sin\psi\sqrt{1 - x^2}$ in
-the integrand to obtain
-%
-\begin{align}
-    \rho_{0,\,j,\,1}(\lnlam_0)
-    &=
-    (1 - x^2)^{\frac{j + 2}{2}}
-    \int\limits_{-\frac{\pi}{2}}^{\frac{\pi}{2}}
-        \sin^j\psi
-        \cos^2\psi \,
-    \mathrm{d}\psi
-    \quad.
-\end{align}
-%
-We may solve this integral using the recurrence relation
-%
-\begin{align}
-    \int
-        \sin^j\psi
-        \cos^m\psi \,
-    \mathrm{d}\psi
-    &=
-    -\frac{\sin^{j-1}\psi \cos^{m+1}\psi}{j + m}
-    +
-    \frac{j - 1}{j + m}\int\sin^{j-2}\psi \cos^m\psi \mathrm{d}\psi
-    \quad ,
-\end{align}
-%
-which, in our case, simplifies to
-%
-\begin{align}
-    \int\limits_{-\frac{\pi}{2}}^{\frac{\pi}{2}}
-        \sin^j\psi
-        \cos^2\psi \,
-    \mathrm{d}\psi
-    &=
-    \frac{j - 1}{j + 2}\int\limits_{-\frac{\pi}{2}}^
-        {\frac{\pi}{2}}\sin^{j-2}\psi \cos^2\psi \mathrm{d}\psi
-    \quad.
-\end{align}
-%
-We thus arrive at the recurrence relation
-%
-\begin{align}
-    \rho_{0,\,j,\,1} &= \frac{j - 1}{j + 2} \big(1 - x^2\big) \rho_{0,\,j-2,\,1}
-\end{align}
-%
-with initial conditions
-%
-\begin{align}
-    \rho_{0,\,0,\,1} &= \frac{\pi}{2} \big(1-x^2\big) \nonumber \\
-    \rho_{0,\,1,\,1} &= 0 \quad.
-\end{align}
-%
-Given these expressions, recursing upward in $i$ is easy:
-%
-\begin{align}
-    \rho_{i,\,j,\,k} &= x \, \rho_{i-1,\,j,\,k} \quad.
-\end{align}
-%
-This completes our derivation. To summarize, given the boundary conditions
-%
-\begin{align}
-    \rho_{0,\,0,\,0} &= 2 \sqrt{1-x^2} \nonumber \\
-    \rho_{0,\,0,\,1} &= \frac{\pi}{2} \big(1-x^2\big) \nonumber \\
-    \rho_{0,\,1,\,k} &= 0 \quad ,
-\end{align}
-%
-we may compute any term in $\rhoT$ via the expressions
-%
-\begin{align}
-    \label{eq:kT:sTrecurrence}
-    \rho_{0,\,j,\,k} &= \frac{j - 1}{j + 1 + k} \big(1 - x^2\big) \rho_{0,\,j-2,\,k} \nonumber \\
-    \rho_{i,\,j,\,k} &= x \, \rho_{i-1,\,j,\,k} \quad.
-\end{align}
-%
-The terms of the convolution kernel $\kT$ are then obtained by dotting
-this vector into the change of basis matrix $\AOne$, as discussed above.
-
-% Table
-\clearpage
-\begin{center}
-    \begin{longtable}{cll}
-    \caption{Common notation used in this paper} 
-    \label{tab:notation} \\
-    %
-    \toprule
-    \multicolumn{1}{c}{\textbf{Symbol}} &
-    \multicolumn{1}{c}{\textbf{Description}} &
-    \multicolumn{1}{c}{\textbf{Reference}} \\
-    \midrule
-    \endfirsthead
-    %
-    \multicolumn{3}{c}%
-    {{\bfseries \tablename\ \thetable{}}. (continued from previous page)} \\[0.5em]
-    \toprule
-    \multicolumn{1}{c}{\textbf{Symbol}} &
-    \multicolumn{1}{c}{\textbf{Definition}} &
-    \multicolumn{1}{c}{\textbf{Reference}} \\
-    \midrule
-    \endhead
-    \bottomrule
-    %
-    \endfoot
-    %
-    \endlastfoot
-    %
-    \midrule
-    \multicolumn{3}{c}{\emph{Dimensions}}\\
-    \midrule
-    %
-    $J$                      & \# of spectral components                             & \S\ref{sec:eigen} \\
-    $K$                      & \# of wavelength bins in the observed spectrum        & \S\ref{sec:linear} \\
-    $K'$                     & \# of wavelength bins in the latent spectrum          & \S\ref{sec:linear}\\
-    $M$                      & \# of epochs observed                                 & \S\ref{sec:linear}\\
-    $N$                      & \# of spherical harmonic coefficients                 & \S\ref{sec:linear}\\
-    $N'$                     & \# of spherical harmonic coefficients after limb darkening & \S\ref{sec:ld}\\
-    $W$                      & \# of wavelength bins in the convolution kernel       & \S\ref{sec:linear}\\
-    %
-    \midrule
-    \multicolumn{3}{c}{\emph{Variables}}\\
-    \midrule
-    %
-    $a_{lm}$                 & spectral spherical harmonic coefficient               & Equation~(\ref{eq:deconv:Ixi0})\\
-    $\alm$                   & vector of spectral spherical harmonic coefficients    & Equation~(\ref{eq:deconv:alm})\\
-    $\bvec{a_0}$             & $\alm$ at reference time $t = t_0$                    & Equation~(\ref{eq:deconv:R})\\
-    $\bvec{A_0}$             & matrix form of $\bvec{a_0}$                           & Equation~(\ref{eq:inverse:azero})\\
-    $\bvec{b}$               & flux baseline vector                                  & Equation~(\ref{eq:norm:b})\\
-    $\bvec{B}$               & block matrix representation of $\bvec{b}$             & Equation~(\ref{eq:norm:b})\\
-    $c$                      & speed of light                                        & Equation~(\ref{eq:kT:beta})\\
-    $\Curve$                 & curve of constant radial velocity                     & Equation~(\ref{eq:deconv:kT})\\
-    $\Dargs$                 & parameters of the Doppler field                       & \S\ref{sec:the_problem}\\
-    $\D$                     & logarithmic Doppler shift                             & Equation~(\ref{eq:the_problem:D})\\
-    $\Doppler$               & Doppler design matrix                                 & Equation~(\ref{eq:linear:f})\\
-    $\bvec{f}$               & vector of observed flux values                        & Equation~(\ref{eq:linear:f})\\
-    $F$                      & flux                                                  & Equation~(\ref{eq:the_problem:F})\\
-    $i$                      & inclination                                           & Equation~(\ref{eq:kT:beta})\\
-    $I$                      & specific intensity                                    & Equation~(\ref{eq:the_problem:Ixi})\\
-    $\bvec{I}$               & identity matrix                                       & \\
-    $l$                      & spherical harmonic degree                             & \\
-    $\bvec{L}$               & limb darkening operator                               & Equation~(\ref{eq:ld:L})\\
-    $m$                      & spherical harmonic order                              & \\
-    $\bvec{R}$               & Wigner rotation matrix                                & Equation~(\ref{eq:deconv:R})\\
-    $\bvec{s}$               & vector representation of the spectrum                 & Equation~(\ref{eq:inverse:azero})\\
-    $\bvec{S}$               & block matrix representation of $\bvec{s}$             & Equation~(\ref{eq:inverse:S})\\
-    $\boldsymbol{\mathbb{S}}$& matrix of $J$ spectral components                     & Equation~(\ref{eq:eigen:azero})\\
-    $\Surf$                  & projected visible area of the star                    & Equation~(\ref{eq:the_problem:F})\\
-    $t$                      & time                                                  & \S\ref{sec:the_problem}\\
-    $u$                      & limb darkening coefficient                            & \S\ref{sec:ld}\\
-    $\x$                     & Cartesian position on the sky                         & \S\ref{sec:the_problem}\\
-    $y_{lm}$                 & spherical harmonic coefficient                        & \S\ref{sec:inverse}\\
-    $\bvec{y}$               & vector of spherical harmonic coefficients             & Equation~(\ref{eq:inverse:azero})\\
-    $Y_{lm}$                 & spherical harmonic                                    & Equation~(\ref{eq:deconv:Ixi0})\\
-    $\bvec{Y}$               & block matrix representation of $\bvec{y}$             & Equation~(\ref{eq:inverse:Y})\\
-    $\boldsymbol{\mathbb{Y}}$& matrix of $J$ spherical harmonic components           & Equation~(\ref{eq:eigen:azero})\\
-    %
-    \pagebreak
-    \midrule
-    \multicolumn{3}{c}{\emph{Variables (Greek)}}\\
-    \midrule
-    %
-    $\beta$                  & relativistic parameter                                & Equation~(\ref{eq:the_problem:D})\\
-    $\delta$                 & Dirac delta function                                  & Equation~(\ref{eq:deconv:convolution})\\
-    $\kT$                    & convolution kernel basis vector                       & Equation~(\ref{eq:deconv:kT})\\
-    $\lambda$                & wavelength                                            & \S\ref{sec:the_problem}\\
-    $\lambda_\mathrm{r}$     & reference wavelength                                  & \S\ref{sec:the_problem}\\
-    $\lnlam$                 & $\ln\nicefrac{\lambda}{\lambda_\mathrm{r}}$ (observer frame)  & \S\ref{sec:the_problem}\\
-    $\lnlam_0$               & $\ln\nicefrac{\lambda}{\lambda_\mathrm{r}}$ (rest frame)      & \S\ref{sec:the_problem}\\
-    $\boldsymbol{\Lambda}$   & prior covariance matrix                               & \\
-    $\boldsymbol{\mu}$       & prior mean vector                                     & \\
-    $\ylmbasis$              & spherical harmonic basis vector                       & Equation~(\ref{eq:deconv:ylmbasis})\\
-    $\boldsymbol{\Sigma}$    & covariance matrix                                     & \\
-    $\omega$                 & angular velocity                                      & Equation~(\ref{eq:kT:beta})\\
-    %
-    \midrule
-    \multicolumn{3}{c}{\emph{Operators}}\\
-    \midrule
-    %
-    $\mathrm{diag}$          & diagonal matricization                                & Equation~(\ref{eq:ld:Dmwav})\\
-    $\mathrm{vec}$           & vectorization                                         & Equation~(\ref{eq:inverse:azero})\\
-    $*$                      & convolution                                           & Equation~(\ref{eq:deconv:convolution_def})\\
-    $\circ$                  & element-wise product                                  & Equation~(\ref{eq:norm:fapprox})\\
-    $\otimes$                & Kronecker product                                     & Equation~(\ref{eq:linear:Dm})\\
-    $\ceil*{\,}$             & ceiling                                               & Equation~(\ref{eq:kT:lm})\\
-    $\floor*{\,}$            & floor                                                 & Equation~(\ref{eq:kT:lm})
-\end{longtable}
-\end{center}
-
-% Bibliography
-\clearpage
-\bibliography{bib}
+The paper is organized as follows: in \S\ref{sec:the_problem}~and~\S\ref{sec:the_solution} we introduce the math behind the Doppler imaging problem and derive a closed form expression for the model. 
+In \S\ref{sec:linear},~\S\ref{sec:inverse},~and~\S\ref{sec:bellswhistles} we demonstrate how to re-express the model as a linear operation on the input spectrum and stellar map and derive closed form expressions for the two conditioned on the data and priors.
+In \S\ref{sec:spotstar} we apply our techniques to a mock problem. 
+We further discuss and summarize our results in \S\ref{sec:discussion}~and~\S\ref{sec:conclusions}. 
+Finally, auxiliary derivations are presented in the Appendix.
 

### 2021-08-12 tex/ms_old.tex
showyourwork

% !TeX root = ./ms.tex
\documentclass[modern]{aastex62}

% Load the corTeX style definitions
\input{cortex}
\input{style}

% Bibliography stuff
\bibliographystyle{aasjournal}

% Begin!
\begin{document}

% Title
\title{A Closed-Form Solution to the Doppler Imaging Problem}

% Author list
\author[0000-0002-0296-3826]{Rodrigo Luger}
\email{rluger@flatironinstitute.org}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
%
\author{Megan Bedell}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
%
\author{Daniel Foreman-Mackey}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
%
\author{David W. Hogg}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}

\begin{abstract}
    We derive a closed form, analytic solution to the problem of Doppler imaging
    of stellar surfaces in the limit of negligible differential rotation and
    convective blueshift. The model for the observed spectrum is linear in the
    coefficients of the spherical harmonic expansion of the specific intensity
    distribution on the surface and, in certain limits, the posterior over surface maps
    has a closed form, analytic solution that is computationally trivial to
    evaluate. The model is also linear in the local (rest frame) stellar spectrum,
    which may itself be spatially variable. This allows one to perform Doppler
    imaging without knowledge of the local stellar spectrum and therefore works
    on blended lines or regions of the spectrum where line formation mechanisms
    are not well understood. Finally, the model is fast, differentiable, and allows
    one to calculate uncertainties on the inferred surface map.
    %
    \href{https://github.com/rodluger/paparazzi}{\color{linkcolor}\faGithub}
\end{abstract}

%
\section{Introduction}
%
\xxx{%
    \noindent Introduce the problem of Doppler imaging. Then cite the following papers:\\[0.5em]
    \noindent\textbf{Misc.} \\
    \noindent\citet{Luger2019} --- Surface modeling with spherical harmonics: \starry \\
    \noindent\citet{Bedell2019} --- Data-driven spectral inference: \texttt{wobble} \\[0.5em]
    %
    \noindent\textbf{Theory} \\
    \noindent\citet{Khokhlova1976,Goncharskii1977} --- Local line profile from observed spectrum\\
    \noindent\citet{Vogt1983,Vogt1987} --- Seminal papers on Doppler imaging \\
    \noindent\citet{Rice1989} ---  Another seminal paper\\
    \noindent\citet{Deutsch1958,Deutsch1970,Falk1974} ---  Ylms + Doppler imaging\\
    \noindent\citet{Unruh1995} --- sensitivity to line profile models\\
    \noindent\citet{Piskunov1990} --- notes on regularization \\[0.5em]
    %
    \noindent\textbf{Application} \\
    \noindent\citet{Crossfield2014} --- Global cloud map of Luhman 16B \\
    \noindent\citet{Roettenbacher2017} --- Doppler imaging of $\sigma$ Geminorum \\
}
%

The paper is organized as follows: in \S\ref{sec:the_problem}~and~%
\S\ref{sec:the_solution} we introduce the math behind the Doppler imaging
problem and derive a closed form expression for the model. In
\S\ref{sec:linear},~\S\ref{sec:inverse},~and~\S\ref{sec:bellswhistles}
we demonstrate how to re-express
the model as a linear operation on the input spectrum and stellar map and
derive closed form expressions for the two conditioned on the data and priors.
In \S\ref{sec:spotstar} we apply our techniques to a mock problem. We
further discuss and summarize our results in
\S\ref{sec:discussion}~and~\S\ref{sec:conclusions}. Finally, auxiliary
derivations are presented in the Appendix.

%

All figures in this paper include links {\color{linkcolor}\faFileCodeO}
to the \Python scripts that generated them. The figures were auto-generated
using the
\href{https://dev.azure.com/rodluger/paparazzi/_build}{Azure Pipelines}
continuous integration (CI) service, running on
a two-core 2.3 GHz \texttt{Standard\_DS2\_v2} virtual machine with 6 GiB physical memory.
% https://docs.microsoft.com/en-us/azure/virtual-machines/windows/sizes-general#dsv2-series

%
\section{The problem}
\label{sec:the_problem}
%
Let $I(\lnlam, \x, t, \Dargs)$ be the specific
intensity observed
at log wavelength $\lnlam \equiv \ln\nicefrac{\lambda}{\lambda_\mathrm{r}}$
and at sky-projected
Cartesian position $\x = (x, y, z)$ on the surface of the
star at time $t$, where
$\Dargs$ is a set of arbitrary parameters of the Doppler field
and $\lambda_\mathrm{r}$ is a reference wavelength.
We may express this intensity as
%
\begin{align}
    \label{eq:the_problem:Ixi}
    I(\lnlam, \x, t, \Dargs) & =
    I\Big(\lnlam_0 + \D(\x, \Dargs), \x, t\Big)
\end{align}
%
where $\lnlam_0$ is the log wavelength in the rest frame and $\D$ is
the Doppler shift in log wavelength space:
%
\begin{align}
    \label{eq:the_problem:D}
    \D(\x, \Dargs)
     & =
    \frac{1}{2}\ln\left(
    \frac{1 + \beta(\x, \Dargs)}{1 - \beta(\x,
            \Dargs)}
    \right)
\end{align}
%
where $\beta = v(\x, \Dargs) / c$ is the ratio of the
radial velocity at a point on the surface of the star to the speed of light.
In keeping with the literature, we take positive values of $v$ (and
$\D$) to mean redshifts.

A common approach to computing the Doppler-shifted spectrum is to
evaluate the spectrum at the rest frame wavelength $\lnlam_0$
and interpolate back to the grid in $\lnlam$. This is practical when
computing the spectrum at a single \emph{point} on the surface, but not
ideal when one is interested in the \emph{integral} over the visible
surface of the star $\Surf$, which is typically all we can observe:
%
\begin{align}
    \label{eq:the_problem:F}
    F(\lnlam, t, \Dargs)
     & \equiv
    \iint\limits_{\Surf(\x)}
    I(\lnlam, \x, t, \Dargs)
    \mathrm{d}{\Surf(\x)}
    \quad ,
\end{align}
%
The difficulty in solving Equation~(\ref{eq:the_problem:F}) stems from the fact
that $I(\lnlam, \x, t, \Dargs)$ is difficult to write down in
closed form, given
the nonlinearity of the Doppler shift.
The standard approach to solving this integral is therefore
to discretize the surface of the star with a fine grid, evaluate the
Doppler-shifted spectrum in each cell, and sum over the spatial axes
to approximate the integral. Depending on the resolution of the grid,
this is either numerically inaccurate or computationally inefficient
(and often both).

\section{The Solution}
\label{sec:the_solution}

\subsection{Doppler Deconvolution}

The observed spectrum is a complex function
of spatial, spectral, temporal, and velocity terms. The goal in this
section is to deconvolve each of these terms to make solving the integral
in Equation~(\ref{eq:the_problem:F}) easier.
%
The first thing we will do is to express Equation~(\ref{eq:the_problem:Ixi})
as a convolution:
%
\begin{align}
    \label{eq:deconv:convolution}
    I(\lnlam, \x, t, \Dargs) & =
    I(\lnlam_0, \x, t)
    *
    \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
\end{align}
%
where $\delta$ is the
Dirac delta function and
$*$ denotes the linear convolution operator, defined for
two arbitrary functions $g$ and $h$ as the integral
%
\begin{align}
    \label{eq:deconv:convolution_def}
    (g * h)(t) \equiv \int_{-\infty}^\infty g(\tau) h(t - \tau) d\tau
\end{align}
%
for some independent coordinate $t$ and dummy parameter $\tau$.
%
The convolution of $I(\lnlam_0)$ with a delta function
has the effect of shifting the spectrum by an amount $\D$, returning
a function of the shifted (observed) log wavelength,
$\lnlam = \lnlam_0 + \D$.

Next, we expand the spatial dependence of the
specific intensity at the rest frame wavelength
in terms of spherical harmonics on the unit disk:
%
\begin{align}
    \label{eq:deconv:Ixi0}
    I(\lnlam_0, \x, t)
     & =
    \sum_{l=0}^{l_\mathrm{max}}\sum_{m=-l}^{l} a_{lm}(\lnlam_0, t) Y_{lm}(\x)
    \quad ,
\end{align}
%
where $Y_{lm}(\x)$ is a spherical harmonic on the projected disk
and $a_{lm}(\lnlam_0, t)$ is the corresponding spherical harmonic
coefficient at log wavelength in the rest frame $\lnlam_0$ and time $t$. For
convenience, we may write this equation in vector form:
%
\begin{align}
    \label{eq:deconv:Ivec}
    I(\lnlam_0, \x, t) & =
    \ylmbasis(\x) \,
    \alm(\lnlam_0, t)
    \quad ,
\end{align}
%
where
%
\begin{align}
    \label{eq:deconv:alm}
    \alm(\lnlam_0, t) \equiv
    \Big(
    a_{0,0}(\lnlam_0, t) \quad\quad\quad\quad\quad\quad
    a_{1,-1}(\lnlam_0, t) \quad\quad\quad\quad\quad\quad
    a_{1,0}(\lnlam_0, t) \quad\quad\quad\quad\quad\quad
    a_{1,1}(\lnlam_0, t) \quad\quad\quad\quad\quad\quad
    ...
    \Big)^\top
\end{align}
%
is the vector of $N = (l_\mathrm{max} + 1)^2$ spherical harmonic coefficients and
%
\begin{align}
    \label{eq:deconv:ylmbasis}
    \ylmbasis(\x) \equiv
    \Big(
    Y_{0,0}(\x) \quad\quad\quad\quad\quad\quad
    Y_{1,-1}(\x) \quad\quad\quad\quad\quad\quad
    Y_{1,0}(\x) \quad\quad\quad\quad\quad\quad
    Y_{1,1}(\x) \quad\quad\quad\quad\quad\quad
    ...
    \Big)
\end{align}
%
is the corresponding vector of $N$ spherical harmonics. We may further
decompose our expression by linearizing the time dependence of the
spherical harmonic coefficients:
%
\begin{align}
    \label{eq:deconv:R}
    \alm(\lnlam_0, t) = \R(t) \, \azero(\lnlam_0)
    \quad ,
\end{align}
%
where $\azero(\lnlam_0) = \bvec{a}(\lnlam_0, t=t_0)$
for some reference time $t_0$.
For rigid body rotation, the result is exact and $\R(t)$ is the $(N \times N)$ Wigner
rotation matrix for real spherical harmonics
\citep[e.g.][]{AlvarezCollado1989}, which is implicitly a
function of the inclination, obliquity, and rotation period of the star.
%In the case that other processes such as differential rotation or spot 
%evolution are significant
%over the course of an observation, Equation~(\ref{eq:deconv:R}) can be
%made to hold approximately for some effective rotation matrix 
%$\R(t)$; we discuss this later.

The equation for the specific intensity in the rest frame now reads
%
\begin{align}
    \label{eq:deconv:Ivecfull}
    I(\lnlam_0, \x, t) & =
    \ylmbasis(\x)
    \,
    \R(t)
    \,
    \azero(\lnlam_0)
    \quad ,
\end{align}
%
where it is clear that we have fully separated the spatial, temporal, and
spectral terms. Inserting this into Equation~(\ref{eq:deconv:convolution})
and integrating
over the visible portion of the star, we arrive at the expression for the
observed spectrum:
%
%
\begin{align}
    \label{eq:deconv:F2d}
    F(\lnlam, t, \Dargs) & =
    \iint\limits_{\Surf(\x)}
    \ylmbasis(\x)
    \,
    \R(t)
    \,
    \alm(\lnlam_0)
    * \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
    \mathrm{d}\Surf(\x)
    \nonumber                \\[0.5em]
                         & =
    \iint\limits_{\Surf(\x)}
    \ylmbasis(\x)
    \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
    \mathrm{d}\Surf(\x)
    \,
    \R(t)
    \,
    *
    \,
    \azero(\lnlam_0)
    \quad ,
\end{align}
%
%
where we made use of the commutativity of the convolution operator and
the fact that the integral is taken only over the spatial dimensions.
Note, importantly, that the convolution operation
above is implicitly a vector operation---i.e., the
convolution is taken for each spherical harmonic term individually
and then summed over all terms.

Finally, we can simplify Equation~(\ref{eq:deconv:F2d}) by noting that the
delta function in the integrand allows us to reduce the double integral
to a line integral:
%
\begin{align}
    \label{eq:deconv:kT}
    \iint\limits_{\Surf(\x)}
    \ylmbasis(\x)
    \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
    \mathrm{d}\Surf(\x)
    \, \,
     & =
    \int\limits_{\Curve(\lnlam, \x, \Dargs)}
    \hspace*{-0.6em}\ylmbasis(\x)
    \mathrm{d}\Curve(\lnlam, \x, \Dargs)
    \nonumber                     \\[0.5em]
     & \equiv \kT(\lnlam, \Dargs)
    \quad.
\end{align}
%
where the path $\Curve(\lnlam, \x, \Dargs)$ corresponds to the
set of all points on the visible disk where
$\lnlam_0 + \D(\x, \Dargs) = 0$.
%
We thus have
%
\begin{align}
    \label{eq:deconv:F}
    F(\lnlam, t, \Dargs)
     & =
    \kT(\lnlam, \Dargs) \, \R(t)
    *
    \azero(\lnlam_0)
    \quad.
\end{align}
%
Equation~(\ref{eq:deconv:F}) is the deconvolution of the
observed spectrum into velocity terms, temporal terms, and spectral/spatial
terms, respectively. In the next section, we will discuss how to
efficiently solve the line integral in Equation~(\ref{eq:deconv:kT}).

\subsection{Computing the kernel $\kT$}
\label{sec:kT}
%
In the case that the star's rotation is rigid (i.e., differential rotation
is negligible) and other effects such as convective blueshift
may be ignored, the radial velocity at any point on the surface is
simply proportional to the distance to the axis of rotation. Without loss
of generality, if we assume the axis of rotation lies along the $y-z$ plane,
we have
%
\begin{align}
    \label{eq:kT:beta}
    \beta(\x, \Dargs) = \frac{\omega \sin i \, x}{c}
\end{align}
%
and
%
\begin{align}
    \label{eq:kT:D}
    \D(\x, \Dargs) & =
    \frac{1}{2}\ln\left(
    \dfrac{1 + \dfrac{\omega \sin i \, x}{c}}
    {1 - \dfrac{\omega \sin i \, x}{c}}
    \right)
    \quad ,
\end{align}
%
where the parameters $\Dargs$ of the Doppler field are the
angular velocity, $\omega$, and the inclination of the star with
respect to $\hat{y}$, $i$.

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/placeholder.pdf} % kT.pdf
        \oscaption{kT}{%
            The Doppler $\kT$ basis for a rigidly rotating star
            computed from Equation~(\ref{eq:kT:kT}) and
            Equation~(\ref{eq:kT:sTrecurrence}) up to spherical
            harmonic degree $l_\mathrm{max}=10$. Rows correspond to the degree $l$ and
            columns correspond to the order $m$. These functions encode
            the contribution of each spherical harmonic to the rotational
            broadening of features in the stellar spectrum. Because the
            rotational axis is chosen to be aligned with $\hat{y}$,
            none of the $m < 0$ harmonics contribute to the observed
            spectrum.
            \label{fig:kT}
        }
    \end{centering}
\end{figure}

If we assume the star is unocculted, the region of integration $\Surf(\x)$
in Equation~(\ref{eq:deconv:kT}) is simply the unit disk,
so $\Curve(\lnlam, \x, \Dargs)$
is the set of all points
that satisfy both $\lnlam_0 + \D(\x, \Dargs) = 0$ and
$x^2 + y^2 \le 1$.
Solving Equation~(\ref{eq:kT:D}) for $x$, we find that
the curves $\Curve(\lnlam, \x, \Dargs)$
are simply vertical lines on the unit disk given by
%
\begin{align}
    x & =
    \Bigg(\frac{c}{\omega\sin i}\Bigg)
    \Bigg(\frac{\mathrm{e}^{-2{\lnlam_0}} - 1}
    {\mathrm{e}^{-2{\lnlam_0}} + 1}\Bigg)
    \quad .
\end{align}
%
The integral in Equation~(\ref{eq:deconv:kT}) is therefore just the line integral
of the spherical harmonic basis over $y$:
%
\begin{align}
    \label{eq:kT:kT}
    \kT(\lnlam, \Dargs)
     & =
    \int\limits_{-\sqrt{1 - x^2}}^
    {\sqrt{1 - x^2}}
    \ylmbasis
    \Big(x, y\Big)
    \mathrm{d}y
    \quad .
\end{align}
%
In the Appendix we derive an analytic solution to this integral and show
how to recursively solve it for all terms in the spherical harmonic basis.
%
Figure~\ref{fig:kT} shows the $\kT$ basis computed from
the formulae above and Equation~(\ref{eq:kT:kT}) up to spherical
harmonic degree $l_\mathrm{max}=10$.

This completes our derivation of the analytic expression for the
observed spectrum (Equation~\ref{eq:deconv:F}).

\subsection{Example}
%
Figure~\ref{fig:spot} shows an example application of the formulae derived
in this section. We used \starry to generate a synthetic stellar surface with a
single large Gaussian spot at a latitude of $30^\circ$, yielding a vector of
spherical harmonic coefficients $\bvec{y}$.
The stellar rest frame spectrum $I(\lnlam_0)$ is taken to be a single Gaussian
absorption line that is spatially constant
everywhere save for a multiplicative factor equal to the local spot intensity.
This corresponds to a spectral/spatial expansion vector $\azero(\lnlam_0)$
whose coefficient at degree $l$ and order $m$ is equal to $y_{lm} I(\lnlam_0)$.
In the Figure, we rotated the star about an axis perpendicular to the line
of sight (left panel) and computed the observed spectrum using
Equation~(\ref{eq:deconv:F}) (center panel). The right panel shows the difference
between the observed spectrum and the spectrum when the spot is not in view.
The effect of the spot on the absorption line is evident: a ``bump'' that
travels from the blueshifted side of to the redshifted side of the line
in sync with the change in longitude of the spot. This correspondence between
line shape residuals and spot location is the cornerstone of the Doppler
imaging technique \citep[compare to, e.g., Figures 1 and 4 in][]{Vogt1983}.

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=0.6\linewidth]{figures/placeholder.pdf} % spot.pdf
        \oscaption{spot}{%
            Time evolution of a Gaussian absorption line on a rigidly rotating,
            spotted star computed from the analytic formulae in \S\ref{sec:kT}.
            The stellar surface is modeled as a spherical harmonic expansion
            up to $l_\mathrm{max}=20$, and the line shape is assumed to be the same everywhere;
            the spot simply downweights the local intensity at all wavelengths.
            As the spot rotates into view (left panel), the line shape changes
            slightly (center panel). The residuals between the line when the
            spot is in view (solid) and when it is on the backside of the star
            (dotted) are shown in the right panel, where
            a Gaussian-like feature can be seen tracking the spot as it rotates
            from the blueshifted hemisphere to the redshifted hemisphere of
            the star.
            \label{fig:spot}
        }
    \end{centering}
\end{figure}

Figure~\ref{fig:compare} shows one of the spectra in Figure~\ref{fig:spot},
this time computed using both our formulae (blue line) and the traditional
technique of discretizing the stellar surface, Doppler-shifting the spectrum
in each grid cell according to the local radial velocity, interpolating back
to a uniform wavelength grid, and summing over the spatial dimension
(dotted orange line). We show the residuals in the lower panel, where it
is clear that as the number of grid cells increases from 2,000 (light grey)
to 71,000 (dark grey), the numerical solution approaches the solution
obtained using our approach.

%Understand---and comment on---the fundamental
%differences between a discrete linear convolution and traditional linear 
%interpolation. Should we expect the numerical solution to actually \emph{converge}
%to the \starry solution, or is the way the two are interpolating fundamentally
%different?

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=0.65\linewidth]{figures/placeholder.pdf} % compare.pdf
        \oscaption{compare}{%
            The observed spectrum when the spot is in view computed with
            \starry (blue) and numerically (orange). The problem setup
            is the same as that in Figure~\ref{fig:spot}. The bottom
            panel shows the absolute value of the difference between the
            two spectra for different number of grid points in the
            numerical solution.
            As the number of grid points increases, the numerical solution
            approaches the \starry solution.
            \label{fig:compare}
        }
    \end{centering}
\end{figure}

\section{Linearization}
\label{sec:linear}

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=0.8\linewidth]{figures/placeholder.pdf} % linalg.pdf
        \oscaption{linalg}{%
            The Doppler design matrix $\Doppler$ (Equation~\ref{eq:linear:f}),
            constructed from a grid of Toeplitz
            matrices, each of shape $K \times K'$, where $K$
            is the number of wavelength bins in the observed spectrum and
            $K' = K + W - 1$ is the number of bins in the model spectrum,
            where $W$ is the width of the convolution kernel.
            The $N$ columns of $\Doppler$ correspond
            to the Toeplitz matrices for each of the $N$ spherical harmonics
            (shown at the top);
            the $M$ rows correspond to the Toeplitz matrices rotated to each
            of the $M$ stellar phases observed (indicated graphically
            to the left of $\Doppler$).
            \label{fig:linalg}
        }
    \end{centering}
\end{figure}

Although the convolution operator (Equation~\ref{eq:deconv:convolution_def})
is defined for continuous functions, the problem of Doppler imaging deals with
discrete measurements of a spectrum in bins of log wavelength. Provided our
wavelength grid is fine enough, we may therefore approximate
Equation~(\ref{eq:deconv:convolution_def}) with a discrete convolution.
For discrete arrays $\bvec{g}$ and $\bvec{h}$, we have
%
\begin{align}
    \label{eq:linear:convolution_def}
    \bvec{g} * \bvec{h} = \bvec{T(g)} \, \bvec{h}
\end{align}
%
where $\bvec{T}$ is a Toeplitz matrix, a matrix whose diagonals
are constant from top left to bottom right. In this case, the diagonals
are constructed from the values of $\bvec{g}$. If $\bvec{g}$ has length
$L$, element $g_n$ is placed everywhere along the $k^\mathrm{th}$ diagonal
of $\bvec{T}$ for $k = -L / 2 + n$; all other entries of $\bvec{T}$ are
set to zero. Note that the matrix $\bvec{T}$ need not be square; in fact,
for our purposes, it is a $(K \times K')$ matrix, where $K$ is the
size of the observed wavelength grid and $K' = K + W - 1$ is the size of the
wavelength grid in the rest frame, where $W$ is the width of the convolution
kernel.

Given this formulation, we may re-write Equation~(\ref{eq:deconv:F}) as a
purely linear operation on $\azero(\lnlam_0)$:
%
\begin{align}
    \label{eq:linear:ft}
    \bvec{f}_m
     & =
    \Doppler_m
    \,
    \azero
    \quad,
\end{align}
%
where $\Doppler_m$ is a $(K \times N K')$ matrix constructed
by horizontally concatenating the Toeplitz matrices for each of the $N$
components of the convolution kernel $\kT(\lnlam, \Dargs)$
transformed by the rotation matrix $\bvec{R}(t)$ evaluated at time $t = t_m$:
%
\begin{align}
    \label{eq:linear:Dm}
    \Doppler_m =
    \begin{pmatrix}
        \quad
        \bvec{T}(\kT_0)
        \quad
         &
        \quad
        \bvec{T}(\kT_1)
        \quad
         &
        \quad
        \cdots
        \quad
         &
        \quad
        \bvec{T}(\kT_N)
        \quad
    \end{pmatrix}
    (\bvec{R}(t_m) \otimes \bvec{I}_{K'})
    \quad.
\end{align}
%
where $\bvec{I}_{K'}$ is the $(K' \times K')$ identity matrix and
$\otimes$ denotes the Kronecker product.
%
The $(K \times 1)$ vector $\mathbf{f}_m$ is the model for
the flux observed at each wavelength at time $t = t_m$, and the
$(N K' \times 1)$ vector $\azero$ is the vector representation of the
spatially-dependent spectrum of the star. The latter is constructed
by flattening the spherical harmonic expansion of the star
such that the first $K'$ terms in $\azero$ correspond
to the the values of $(a_0)_{0,0}$ at each wavelength $\lnlam_0$,
followed by the values of $(a_0)_{1,-1}$ at each wavelength, and so forth.

In general, our data will consist of observations made at several
epochs, corresponding to different rotational phases of the star.
If we concatenate all $M$ spectra $\bvec{f}_m$ into the $(MK \times 1)$
vector $\bvec{f}$, we may write
%
\begin{align}
    \label{eq:linear:f}
    \bvec{f}
     & =
    \Doppler
    \,
    \azero
    \quad,
\end{align}
%
where $\Doppler$ is the full $(MK \times N K')$ Doppler design matrix,
constructed by vertically concatenating the individual matrices $\Doppler_m$:
%
%
\begin{align}
    \label{eq:linear:D}
    \Doppler =
    \begin{pmatrix}
        \Doppler_0
        \\
        \Doppler_1
        \\
        \cdots
        \\
        \Doppler_m
    \end{pmatrix}
    \quad.
\end{align}
%
%
Equation~(\ref{eq:linear:f}) represents the full linearization of the problem,
where we
have expressed the quantity we can observe, $\bvec{f}$, as a linear
operation on the quantity of interest, the spectral/spatial decomposition
of the stellar surface, $\azero$. Figure~\ref{fig:linalg} shows an
example of $\Doppler$.

\section{The inverse problem}
\label{sec:inverse}
%
In the previous section we showed how to express the data vector $\bvec{f}$,
a series of spectra obtained at different epochs, as a purely linear
operation on the map vector $\azero$, the spherical harmonic decomposition of
the specific intensity on the surface of the star. The advantage of this
linearity is that, given suitable priors, it allows one to compute both
the maximum likelihood solution for $\azero$ and its uncertainty
\emph{analytically}. In particular, if one places a (multidimensional)
Gaussian prior on $\azero$ with mean $\boldsymbol{\mu}_\mathbf{a_0}$ and
covariance $\boldsymbol{\Lambda}_\mathbf{a_0}$, the maximum \emph{a posteriori} (MAP)
solution for $\azero$ is
%
\begin{align}
    \label{eq:inverse:ahat}
    \bvec{\hat{a}_0} & =
    \boldsymbol{\Sigma}_\mathbf{\hat{a}_0}
    \left(
    \Doppler^\top
    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
    \bvec{f}
    +
    {\boldsymbol{\Lambda}_{\azero}}^{-1} \boldsymbol{\mu}_\mathbf{a_0}
    \right)
    \quad,
\end{align}
%
with posterior covariance given by
%
\begin{align}
    \label{eq:inverse:acov}
    \boldsymbol{\Sigma}_\mathbf{\hat{a}_0} & =
    \left(
    \Doppler^\top
    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
    \Doppler
    +
    {\boldsymbol{\Lambda}_{\azero}}^{-1}
    \right)^{-1}
    \quad,
\end{align}
%
where $\boldsymbol{\Sigma}_\mathbf{f}$ is the data covariance
matrix. These equations require the inversion of a few fairly
large matrices, but as we will see later, it allows one to obtain
the map of the star ($\bvec{\hat{a}_0}$) and its uncertainty
($\boldsymbol{\Sigma}_{\mathbf{\hat{a}_0}}$) in under a second for
a typical dataset.

There is, however, a catch: for most practical purposes, it is
difficult to find a good Gaussian prior for $\bvec{a_0}$. Usually
we will have some prior information on what the spectrum of the
star is, and perhaps some prior information on the distribution
of surface features such as starspots. The problem is that
even if these priors are Gaussian, the corresponding prior
on $\bvec{a_0}$ is \emph{not}. To understand this, consider the
case where the stellar rest frame spectrum is spatially constant,
save for an amplitude that is spatially variable. We can then
describe the rest frame spectrum by the $(K' \times 1)$ vector
$\bvec{s}$ and the amplitude by the $(N \times 1)$ vector
$\bvec{y}$ representing the spherical harmonic expansion of the
intensity profile of the star. The vector $\azero$ is then
given by the (flattened) outer product of the two vectors:
%
\begin{align}
    \label{eq:inverse:azero}
    \azero & = \mathrm{vec}\left( \bvec{A_0} \right) \nonumber             \\
           & = \mathrm{vec}\left( \bvec{s} \, \bvec{y}^\top \right) \quad,
\end{align}
%
where $\mathrm{vec}$ denotes the vectorization operation, which in this case
transforms the $(K' \times N)$ matrix $\bvec{A_0}$ into the $(N K' \times 1)$
column vector $\azero$ by vertically stacking all of its columns. In other
words, the vector $\azero$ consists of the set of $K'$ intensities in
each wavelength bin repeated $N$ times, each time multiplied by the
$n^\mathrm{th}$ spherical harmonic coefficient in the expansion of the
surface intensity. Returning to our point about priors, note that all of the
entries of $\azero$ are the product of two independent random variables. Since
the product of two random variables is generally non-Gaussian, even
when the variables themselves are Gaussian%
\footnote{see, e.g., \url{http://mathworld.wolfram.com/NormalProductDistribution.html}}%
, so too is the prior on $\azero$. This point makes
Equation~(\ref{eq:inverse:ahat}) of little practical use, since a
multivariate Gaussian will not
generally be a suitable prior for $\azero$.

That said, a Gaussian prior \emph{is} typically suitable for both the spectrum
$\bvec{s}$ and the intensity $\bvec{y}$ (just not their product). It is
straightforward to show that because Equation~(\ref{eq:linear:f}) is linear
in $\azero$, it is also linear in both $\bvec{s}$ and $\bvec{y}$, so
MAP solutions can be found analytically for $\bvec{s}$
(conditioned on $\bvec{y}$) and $\bvec{y}$ (conditioned on $\bvec{s}$). We
investigate these solutions below.

\subsection{Solution for the map}
\label{sec:solve_y}
For a fixed, spatially constant rest-frame spectrum $\bvec{s}$, the model
for the flux vector may be written as
%
\begin{align}
    \label{eq:inverse:fy}
    \bvec{f}
     & =
    \Doppler
    \,
    \bvec{S}
    \,
    \bvec{y}
    \quad,
\end{align}
%
where
%
\begin{align}
    \label{eq:inverse:S}
    \setstackgap{L}{1.25\baselineskip}
    \bvec{S} =
    \begin{pmatrix}
        \quadquad\bvec{s}\quadquad &                            &                            &                            &        \\
                                   & \quadquad\bvec{s}\quadquad &                            &                            &        \\
                                   &                            & \quadquad\bvec{s}\quadquad &                            &        \\
                                   &                            &                            & \quadquad\bvec{s}\quadquad &        \\
                                   &                            &                            &                            & \ddots
    \end{pmatrix}
\end{align}
%
is a $(NK' \times N)$ block matrix constructed by repeating the column
vector $\bvec{s}$ $N$ times in blocks along the main diagonal.
%
Before we solve this equation for $\bvec{y}$, we note that in practice
it is convenient to fix the coefficient of the $Y_{0,0}$ spherical
harmonic, $y_0$, to unity. After all, this coefficient is not directly
constrained by the data, as it merely sets the baseline intensity on the
surface of the star and is therefore formally degenerate with the stellar
luminosity (which also cannot be directly inferred from the data). This
choice further ensures a mean baseline of unity for the model
vector $\mathbf{f}$. We may therefore write
%
\begin{align}
    \label{eq:inverse:fy1}
    \bvec{f}
     & =
    \Doppler
    \,
    \bvec{s}_\bvec{0}
    \,
    +
    \,
    \Doppler
    \,
    \bvec{S_1}
    \,
    \bvec{y}_\bvec{1}
    \quad,
\end{align}
%
where the vector $\bvec{s_0}$ denotes the first column of $\bvec{S}$,
the matrix $\bvec{S_1}$ denotes the remaining columns of $\bvec{S}$, and
$\bvec{y_1}$ is the quantity we wish to solve for: the vector of spherical
harmonic coefficients of degree $l \ge 1$.

Given prior mean $\boldsymbol{\mu}_\bvec{y_1}$ and covariance
$\boldsymbol{\Lambda}_\bvec{y_1}$ on $\bvec{y_1}$, the MAP solution
is given by
%
\begin{align}
    \label{eq:inverse:y1hat}
    \bvec{\hat{y}_1} & =
    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1}
    \left(
    \bvec{S_1}^\top\Doppler^\top
    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
    \left(\bvec{f} - \Doppler\bvec{s}_\bvec{0}\right)
    +
    {\boldsymbol{\Lambda}_\bvec{y_1}}^{-1} \boldsymbol{\mu}_\bvec{y_1}
    \right)
    \quad,
\end{align}
%
with covariance
%
\begin{align}
    \label{eq:inverse:y1cov}
    \boldsymbol{\Sigma}_\bvec{\hat{y}_1} & =
    \left(
    \bvec{S_1}^\top\Doppler^\top
    {\boldsymbol{\Sigma}_\bvec{f}}^{-1}
    \Doppler\bvec{S_1}
    +
    {\boldsymbol{\Lambda}_\bvec{y_1}}^{-1}
    \right)^{-1}
    \quad.
\end{align}
%
If we choose a prior with zero mean ($\boldsymbol{\mu}_\bvec{y_1} = 0$)
and a diagonal covariance that is constant for each spherical harmonic
order $m$,
%
\begin{align}
    \boldsymbol{\Lambda}_\bvec{y_1} & =
    \mathrm{diag} \left(
    \sigma_1^2
    \quad\quad\quad\quad
    \sigma_1^2
    \quad\quad\quad\quad
    \sigma_1^2
    \quad\quad\quad\quad
    \sigma_2^2
    \quad\quad\quad\quad
    \sigma_2^2
    \quad\quad\quad\quad
    \sigma_2^2
    \quad\quad\quad\quad
    \sigma_2^2
    \quad\quad\quad\quad
    \sigma_2^2
    \quad\quad\quad\quad
    \cdots
    \right)
    \quad,
\end{align}
%
we are in fact imposing an isotropic prior with an angular power spectrum
given by $C_l = \sigma_l^2$
\citep[e.g.,][]{Baldi2006}. This is especially useful if the typical
angular scale of features on the surface of the star is known or if
a Gaussian prior can be placed on it.

\subsection{Solution for the spectrum}
\label{sec:solve_s}
If, on the other hand, the spatial intensity profile is known, the
model for the flux vector may be written in terms of the spectrum $\bvec{s}$
as
%
\begin{align}
    \label{eq:inverse:fs}
    \bvec{f}
     & =
    \Doppler
    \,
    \bvec{Y}
    \,
    \bvec{s}
    \quad,
\end{align}
%
where
%
\begin{align}
    \label{eq:inverse:Y}
    \setstackgap{L}{1.25\baselineskip}
    \bvec{Y} =
    \begin{pmatrix}
        y_0\, \bvec{I}_{K'} \\
        y_1\, \bvec{I}_{K'} \\
        y_2\, \bvec{I}_{K'} \\
        y_3\, \bvec{I}_{K'} \\
        \cdots
    \end{pmatrix}
\end{align}
%
is a $(NK' \times K')$ matrix constructed by vertically stacking
$N$ $(K' \times K')$ identity matrices, each multiplied by the
corresponding coefficient of $\bvec{y}$. Given
prior mean $\boldsymbol{\mu}_\mathbf{s}$ and covariance
$\boldsymbol{\Lambda}_\mathbf{s}$ on $\mathbf{s}$, the MAP solution
is given by
%
\begin{align}
    \label{eq:inverse:shat}
    \bvec{\hat{s}} & =
    \boldsymbol{\Sigma}_\mathbf{\hat{s}}
    \left(
    \bvec{Y}^\top\Doppler^\top
    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
    \bvec{f}
    +
    {\boldsymbol{\Lambda}_\mathbf{s}}^{-1} \boldsymbol{\mu}_\mathbf{s}
    \right)
    \quad,
\end{align}
%
with covariance
%
\begin{align}
    \label{eq:inverse:scov}
    \boldsymbol{\Sigma}_\mathbf{\hat{s}} & =
    \left(
    \bvec{Y}^\top\Doppler^\top
    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
    \Doppler\bvec{Y}
    +
    {\boldsymbol{\Lambda}_\mathbf{s}}^{-1}
    \right)^{-1}
    \quad.
\end{align}

\subsection{The full solution}
\label{sec:full_solve}
In the previous two sections we showed how, if the stellar
rest-frame spectrum is spatially constant and known \emph{a priori}
(from, say, a template spectrum), the posterior distribution
for the surface map $\bvec{y}$ is \emph{analytic}
(Equations~\ref{eq:inverse:y1hat}
and \ref{eq:inverse:y1cov}). Conversely, if the surface map is known,
the posterior for the spectrum is also analytic
(Equations~\ref{eq:inverse:shat} and \ref{eq:inverse:scov}). Both sets of
solutions require Gaussian priors on the quantities of interest, but these
are easily interpretable. A Gaussian prior on
the spherical harmonic coefficients of the surface map corresponds
to the angular power spectrum of the surface features, whereas a Gaussian
prior on the spectrum can be used to correctly propagate uncertainties in
the stellar spectrum from observational uncertainties on the stellar
metallicity, temperature, etc.

Importantly, the framework developed here allows one to analytically
compute not only the ``optimal'' solution to the Doppler imaging problem,
but also its uncertainty. The problem of re-constructing surface images
of stars from spectra and/or light curves is fundamentally ill-posed because
of intrinsic degeneracies and a large null space
\citep[e.g.,][]{Cowan2017,Luger2019}. Coupled to uncertainties in
the observations themselves, this makes the process of searching for the
``optimal'' solution flawed at best, and meaningless at worst. Access to the
full covariance matrix of the solution is therefore essential to assessing our
confidence in the various features of the inferred surface maps.

However, as we mentioned above, the Doppler imaging problem can be solved
analytically for either the surface map or the spectrum, but not both. If
neither are known exactly \emph{a priori}, which is quite often the case,
we can still find the MAP solution quickly by guessing at an initial
spectrum $\bvec{s}$ and iterating between optimizing for $\bvec{y}$ and
optimizing for $\bvec{s}$. This bilinear problem is not generally convex,
but given a good starting point for $\bvec{s}$ and sufficient regularization
on $\bvec{y}$, we find that it typically converges to the correct solution,
especially after refinement with a nonlinear solver;
we discuss this in detail below.

Once the MAP solution has been found for both $\bvec{s}$ and $\bvec{y}$,
the covariance of one conditioned on the other can be computed from the
formulae above. However, this is necessarily a lower bound on the true
covariance of the solution, since it neglects any covariance \emph{between}
$\bvec{s}$ and $\bvec{y}$. To \emph{correctly} account for this, one must
resort to Monte Carlo methods or other sampling techniques. We discuss
this further below.

\section{Further considerations}
\label{sec:bellswhistles}

Before we demonstrate our formalism in practice, we consider three
modifications to our model that are often required when modeling real
data. Below we discuss what to do when the relative brightness of the
star across different observations is unknown (\S\ref{sec:norm}), how
to account for the effects of limb darkening (\S\ref{sec:ld}), and how
to model stars whose local spectra differ within and outside of starspots
(\S\ref{sec:eigen}).

\subsection{Unknown continuum normalization}
\label{sec:norm}
%
Consider the star depicted in Figure~\ref{fig:spot}. When the spot is in
view, absorption lines become distorted due to the suppression of either
blueshifted or redshifted light. However, what is not shown in the figure
is the fact that overall, the star also gets \emph{dimmer}: the
continuum level drops in the presence of the spot. Unfortunately,
spectrographs are not usually designed to measure this, since the
change in the star's overall brightness from one observation to the next
is often dwarfed by (unknown) changes in the spectrograph sensitivity.
For this reason, the spectra are usually normalized to have a
fixed baseline continuum, and Equation~\ref{eq:linear:f} is no longer
a good model for the data.

One option is to collect simultaneous photometry on the target in a band
similar to the wavelength range observed, and use this light curve to
(un-)normalize the spectral timeseries $\bvec{f}$. However, when this is
not an option, our model for $\bvec{f}$ (Equation~\ref{eq:linear:f}) must
be amended.

%
\begin{align}
    \label{eq:norm:f}
    \bvec{f}
     & =
    \frac{
        \Doppler
        \,
        \azero
    } {
        \bvec{b}
    }
    \quad,
\end{align}
%
where $\bvec{b}$ is the baseline and the vector division is
performed elementwise. When $\azero$ is given by Equation~(\ref{eq:inverse:azero}),
the baseline $\bvec{b}$ is simply the total (wavelength-integrated) flux
at each epoch, repeated for every element in each spectrum.
Based on \citet{Luger2019}, this can be computed as a purely linear operation
on the spherical harmonic vector $\bvec{y}$:
%
\begin{align}
    \label{eq:norm:b}
    \bvec{b}
     & =
    %
    \begin{pmatrix}
        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_0)     \\
        \cdots                                     \\
        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_0)     \\
        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_1)     \\
        \cdots                                     \\
        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_1)     \\
        \cdots                                     \\
        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_{M-1}) \\
        \cdots                                     \\
        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_{M-1})
    \end{pmatrix}
    \bvec{y}
    %
    \nonumber \\[0.5em]
     & \equiv
    \bvec{B} \, \bvec{y}
\end{align}
%
where $\bvec{r}$ is given by Equation~(18) in \citet{Luger2019},
$\bvec{A_1}$ is given in Appendix B of \citet{Luger2019}, and $\bvec{R}(t)$
is the rotation matrix defined previously.

Given this new equation, we must change how we approach the inverse problem
(\S\ref{sec:inverse}). When solving for the spectrum given the spherical
harmonic vector (\S\ref{sec:solve_s}), we need only make the replacements
$\bvec{f} \rightarrow \nicefrac{\bvec{f}}{\bvec{B}\, \bvec{y}}$
and
$\boldsymbol{\Sigma}_\mathbf{f} \rightarrow \nicefrac{\boldsymbol{\Sigma}_\mathbf{f}}{(\bvec{B}\, \bvec{y})^2}$
in Equations~(\ref{eq:inverse:shat}) and (\ref{eq:inverse:scov}).
However, when solving for the spherical harmonic vector given the spectrum
(\ref{sec:solve_y}), the problem is no longer linear in $\bvec{y}$, as the
vector of interest appears in both the numerator and the denominator:
%
\begin{align}
    \label{eq:norm:fy}
    \bvec{f}
     & =
    \frac{
        \bvec{D}
        \,
        \bvec{S}
        \,
        \bvec{y}
    }{
        \bvec{B}
        \,
        \bvec{y}
    }
    \quad.
\end{align}
%
While we can solve for $\bvec{y}$ using a nonlinear optimizer, it is
often the case that the denominator in Equation~(\ref{eq:norm:fy}) is close
to unity; i.e., the total flux from the star typically varies by only a
few percent. When this is the case, it is straightforward to linearize
this equation.
Following the notation from \S\ref{sec:solve_y}, we may therefore write
%
\begin{align}
    \bvec{f}
     & =
    \frac{
        \bvec{D} \, \bvec{s_0}
        \,
        +
        \,
        \bvec{D}\bvec{S_1}
        \,
        \bvec{y_1}
    }{
        \bvec{B_0}
        \,
        +
        \bvec{B_1}
        \,
        \bvec{y_1}
    }
    \quad,
\end{align}
%
where $\bvec{B_0} = \bvec{1}$ is the first column of $\bvec{B}$
and $\bvec{B}_\bvec{1}$ denotes the
matrix composed from the remaining $N - 1$ columns of $\bvec{B}$.
Expanding the expression above about
$\bvec{B_1} \bvec{y_1} = \bvec{0}$ and keeping only terms up to
first order, we have
%
\begin{align}
    \label{eq:norm:fapprox}
    \bvec{f}
     & \approx
    \left(
    \bvec{D} \, \bvec{s_0}
    \,
    +
    \,
    \bvec{D}\bvec{S_1}
    \,
    \bvec{y_1}
    \right)
    \circ
    \left(
    \bvec{1}
    \,
    -
    \bvec{B_1}
    \,
    \bvec{y_1}
    \right)
    \nonumber  \\
     & \approx
    \left(
    \bvec{D}\bvec{S_1}
    \,
    -
    \bvec{C}
    \right)
    \bvec{y_1}
    \,
    +
    \,
    \bvec{D} \, \bvec{s_0}
    \quad,
\end{align}
%
where $\circ$ denotes an elementwise product and $\bvec{C}$ is a matrix
constructed by multiplying each row of $\bvec{B_1}$ by the
corresponding element of $\bvec{D}\bvec{s_0}$.
%
This equation is now
linear in $\bvec{y}_\bvec{1}$, so we may solve the least-squares problem
as before:
%
\begin{align}
    \label{eq:norm:yhat}
    \bvec{\hat{y}_1} & =
    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1}
    \left(
    \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
    (\bvec{f} - \bvec{D}\bvec{s_0})
    +
    {\boldsymbol{\Lambda}_{\mathbf{y}_\bvec{1}}}^{-1} \boldsymbol{\mu}_{\mathbf{y}_\bvec{1}}
    \right)
    \quad,
\end{align}
%
with covariance
%
\begin{align}
    \label{eq:norm:ycov}
    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1} & =
    \left(
    \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
    \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)
    +
    {\boldsymbol{\Lambda}_{\mathbf{y}_1}}^{-1}
    \right)^{-1}
    \quad.
\end{align}
%
Note, importantly, that these equations are valid only in the limit that the
change in the total flux from the star is small. Nevertheless, even in the
general case, we find that solving this linear problem yields a good
starting point for a nonlinear optimization, which we revisit in more
detail below.

\subsection{Limb darkening}
\label{sec:ld}
Thus far we have avoided mention of limb darkening, whose effect
on the observed spectrum can often be significant. A proper treatment of
limb darkening requires solution of radiative transfer equations and
should account for the temperature and composition gradients in the
stellar atmosphere. However, in the spirit of data-driven inference, we
can approximate the effect of limb darkening by weighting the spatial
component of our map by the limb darkening profile of the star, which can
either be imposed or learned from the data. For a polynomial limb darkening
law of the form
%
\begin{align}
    \label{eq:ld:I}
    \frac{I(\mu)}{I(\mu = 1)} = 1 - \sum_{n=1}^{n_\mathrm{max}} u_n(1 - \mu)^n
    \quad,
\end{align}
%
where $\mu = z = \sqrt{1 - x^2 - y^2}$ is the radial coordinate on the
projected disk and $u_n$ is a limb darkening coefficient, the effect of
limb darkening on the stellar map can be expressed exactly as a linear
operation on the spherical harmonic coefficient vector
\citep{Luger2019,Agol2019}. This can be understood by noting that all terms
in Equation~(\ref{eq:ld:I}) are strictly polynomials in $x$, $y$, and $z$,
all of which can be expressed exactly as sums of spherical harmonics
\citep{Luger2019}. When weighting the surface intensity by the limb darkening
profile, the resulting intensity is simply a product of spherical harmonics,
which is itself a sum of spherical harmonics. Given a limb darkening law
of degree $n_\mathrm{max}$, we can always construct a matrix $\bvec{L}$
that transforms a spherical harmonic vector $\bvec{y}$ of degree
$l_\mathrm{max}$ to a limb-darkened spherical harmonic vector $\bvec{y'}$
of degree $l_\mathrm{max} + n_\mathrm{max}$. As an example, consider
a map of degree $l_\mathrm{max} = 1$ and the linear limb darkening law
($n_\mathrm{max} = 1$).
The transformation matrix from $\bvec{y}$ to $\bvec{y'}$ is
%
\begin{align}
    \label{eq:ld:L}
    \setstackgap{L}{1.5\baselineskip}
    \bvec{L} =
    \frac{1}{1 - \frac{u_1}{3}}
    \begin{pmatrix}
        \quadquad1-u_1\quadquad & 0                       & \frac{u_1}{\sqrt{3}}    & 0                       \\
        0                       & \quadquad1-u_1\quadquad & 0                       & 0                       \\
        \frac{u_1}{\sqrt{3}}    & 0                       & \quadquad1-u_1\quadquad & 0                       \\
        0                       & 0                       & 0                       & \quadquad1-u_1\quadquad \\
        0                       & 0                       & 0                       & 0                       \\
        0                       & \frac{u_1}{\sqrt{5}}    & 0                       & 0                       \\
        0                       & 0                       & \frac{2u_1}{\sqrt{15}}  & 0                       \\
        0                       & 0                       & 0                       & \frac{u_1}{\sqrt{5}}    \\
        0                       & 0                       & 0                       & 0
    \end{pmatrix}
    \quad.
\end{align}
%
The columns of $\bvec{L}$ are constructed from the coefficient vectors of
each transformed spherical harmonic, which are in turn computed by
multiplying each spherical harmonic by the spherical harmonic decomposition
of the particular limb darkening law.
Figure~\ref{fig:ld} shows this transformation with $u_1 = 1$ applied to each
of the first four spherical harmonics.
%
\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=0.5\linewidth]{figures/placeholder.pdf} % ld.pdf
        \oscaption{ld}{%
            Illustration of the limb darkening transformation given by
            Equation~(\ref{eq:ld:L}) for a linear limb darkening law with
            $u_1 = 1$. Each row shows a spherical harmonic before
            (left) and after (right) transformation by $\bvec{L}$.
            \label{fig:ld}
        }
    \end{centering}
\end{figure}
%

Now, to incorporate limb darkening into our model, we must modify how we
compute the Doppler design matrix $\Doppler$
(Equation~\ref{eq:linear:D} and Figure~\ref{fig:linalg}). Recall that
this matrix is constructed by vertically stacking the submatrices
$\Doppler_m$ given by Equation~(\ref{eq:linear:Dm}), which we now compute
as
%
\begin{align}
    \label{eq:ld:Dm}
    \Doppler_m =
    \begin{pmatrix}
        \quad
        \bvec{T}(\kT_0)
        \quad
         &
        \quad
        \bvec{T}(\kT_1)
        \quad
         &
        \quad
        \cdots
        \quad
         &
        \quad
        \bvec{T}(\kT_{N'})
        \quad
    \end{pmatrix}
    (\bvec{L} \, \bvec{R}(t_m) \otimes \bvec{I}_{K'})
    \quad,
\end{align}
%
where we have replaced the rotation matrix $\bvec{R}(t_m)$ with
the linear transformation $\bvec{L}\,\bvec{R}(t_m)$, which first rotates the
input spherical harmonic coefficient vector to the correct phase then
limb darkens it. Note also that the terms in the convolution kernel $\kT$
are now indexed from 0 to $N' = (l_\mathrm{max} + n_\mathrm{max} + 1)^2$,
where $n_\mathrm{max}$ is the degree of the limb darkening operator.

Note that it is also possible to model wavelength-dependent limb darkening
in this fashion. The procedure is similar, except that the limb darkening
coefficients $u_n$ are now functions of $\lnlam$, and each element of the
matrix $\bvec{L}$ is now a vector of length $K'$. The submatrices
$\Doppler_m$ may be written as
%
\begin{align}
    \label{eq:ld:Dmwav}
    \resizebox{0.91\textwidth}{!}{
        $
            \Doppler_m =
            \begin{pmatrix}
                \quad
                \bvec{T}(\kT_0)
                \quad
                 &
                \quad
                \bvec{T}(\kT_1)
                \quad
                 &
                \quad
                \cdots
                \quad
                 &
                \quad
                \bvec{T}(\kT_{N'})
                \quad
            \end{pmatrix}
            \begin{pmatrix}
                \mathrm{diag}(\bvec{L}_{0,0})
                 &
                \mathrm{diag}(\bvec{L}_{0,1})
                 &
                \cdots
                 &
                \mathrm{diag}(\bvec{L}_{0,N})
                \\
                \mathrm{diag}(\bvec{L}_{1,0})
                 &
                \mathrm{diag}(\bvec{L}_{1,1})
                 &
                \cdots
                 &
                \mathrm{diag}(\bvec{L}_{1,N})
                \\
                \cdots
                 &
                \cdots
                 &
                \ddots
                 &
                \cdots
                \\
                \mathrm{diag}(\bvec{L}_{N',0})
                 &
                \mathrm{diag}(\bvec{L}_{N',1})
                 &
                \cdots
                 &
                \mathrm{diag}(\bvec{L}_{N',N})
            \end{pmatrix}
            (\bvec{R}(t_m) \otimes \bvec{I}_{K'})
        $
    }
    \quad,
\end{align}
%
where $\mathrm{diag}(\bvec{v})$ denotes the $(K' \times K')$ diagonal matrix
constructed by placing the vector $\bvec{v}$ along the main diagonal.

\subsection{Multiple spectral components}
\label{sec:eigen}
%
In our discussion so far we have focused on the particular case where the
spectral/spatial decomposition of the stellar surface can be expressed as
the outer product of two vectors (Equation~\ref{eq:inverse:azero}). As we
mentioned previously, this corresponds to the case where the spectrum is
constant across the surface of the star except for a spatially-variable
amplitude: i.e., spots have the same spectrum as the rest of the star, but
emit less flux overall. However, most of the formalism developed here also
applies to the more general case where the spectrum at a particular point
on the surface of the star is a linear combination of several different
spectral components. In this case, the map vector $\azero$
may be written as the sum over $J$ spectra $\bvec{s}_j$, each of which is dotted into
a different vector of spherical harmonic coefficients $\bvec{y}_j^\top$:
%
\begin{align}
    \label{eq:eigen:azero}
    \azero
     & =
    \sum_{j=0}^{J-1}\mathrm{vec}\left( \bvec{s}_j \, \bvec{y}_j^\top \right) \\
     & =
    \mathrm{vec}\left( \boldsymbol{\mathbb{S}} \, \boldsymbol{\mathbb{Y}}^\top \right) \quad,
\end{align}
%
where $\boldsymbol{\mathbb{S}}$ is the $(K' \times J)$ matrix whose columns are
the $J$ spectral components and $\boldsymbol{\mathbb{Y}}^\top$ is the
$(J \times N)$ matrix whose rows are the corresponding $J$ spherical harmonic
coefficient vectors.

The model remains linear in both the spherical harmonic coefficients and the
spectral components, and the procedures outlined in \S\ref{sec:inverse} may
still be followed to solve the inverse problem, provided we unroll these
matrices into vectors, letting
$\mathbf{s} = \mathrm{vec}(\boldsymbol{\mathbb{S}})$
and
$\mathbf{y} = \mathrm{vec}(\boldsymbol{\mathbb{Y}})$.
A detailed discussion of this general case is deferred to future work,
but we present an example of a two-component stellar spectrum in \S\ref{sec:eigen}
below.

\section{Application to a spotted star}
\label{sec:spotstar}

In this section we apply the formalism developed in \S\ref{sec:inverse}
and \S\ref{sec:bellswhistles} to a synthetic dataset of a rapidly
rotating spotted star. This section is motivated by the
examples in \cite{Vogt1987}, who generated rotationally-broadened spectra
of a rapidly-rotating star with the letters ``VOGT'' painted across
the northern hemisphere. In that paper, the authors
generated synthetic line profiles of the Fe I
$\lambda 6430$ absorption line with equivalent width $W \approx 10$~km/s
and from these computed rotationally broadened spectra for a star at an
inclination $i=40^\circ$ rotating at projected velocity $v\sin i = 40$~km/s.
The spectra were computed at 16 equally spaced rotational phases and
downsampled to 32 wavelength bins per epoch, for a total of 512 data
points.

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=0.85\linewidth]{figures/placeholder.pdf} % spot_setup.pdf
        \oscaption{spot_setup}{%
            The basic setup for the \spot problem. We compute the
            $l_\mathrm{max} = 15$ spherical harmonic expansion of
            a map where the word ``SPOT'' has been placed across the northern
            hemisphere (top left). Each point on the surface is
            given the same spectrum, composed of a sum of synthetic
            Gaussian absorption lines (blue curve in the bottom panel).
            The specific intensity
            at each point on the surface is equal to this spectrum weighted
            by the intensity of the map, which is close to zero within the
            spot (point labeled \texttt{B}) and close ot unity
            outside the spot (point labeled \texttt{A}).
            %
            To generate the synthetic dataset (orange curves in the bottom
            panel), the star is inclined at
            $40^\circ$ with respect to the line of sight and the disk-integrated
            spectrum is computed at 16 equally-spaced phases between
            $-180^\circ$ and $180^\circ$ (middle panel).
            %
            The grey regions indicate wavelength
            regions outside the observation window, but whose features still
            contribute to the observed spectrum due to rotational broadening.
            \label{fig:spot_setup}
        }
    \end{centering}
\end{figure}

We repeat the same experiment here using our new formalism, except we
instead generate a stellar surface with the word ``SPOT'' written across
the northern hemisphere (top left panel of Figure~\ref{fig:spot_setup}).
We do this by computing the $l_\mathrm{max} = 15$ spherical harmonic
decomposition of an image of the word, generating a set of
$N = (l_\mathrm{max} + 1)^2 = 256$ spherical harmonic coefficients
$\bvec{y} = (1 \quadquad \bvec{y_1})$.

Our input spectrum $\bvec{s}$ was generated at high resolution
($R \equiv \frac{\lambda}{\Delta\lambda} = 300,000$)
centered at a reference wavelength $\lambda_\mathrm{r} = 6430$ nm
(blue curve in the bottom panel of Figure~\ref{fig:spot_setup}).
The spectrum consists of a Gaussian absorption line in log-wavelength
($\lnlam$) space with amplitude $0.5$ and standard deviation
$\sigma_{\lnlam} = 1.4\times 10^{-5}$. This corresponds to a FWHM of about
$2.355~\sigma_{\lnlam}~\lambda_\mathrm{r}~\approx~0.2$ nm or, in velocity space,
$2.355~\sigma_{\lnlam}~c~\approx~10$~km/s, equal to the value used in
\citet{Vogt1987}. Unlike \citet{Vogt1987}, we add 20 additional small
absorption lines at random positions throughout the spectrum, all of
the same FWHM but of varying depths, including some line blends. In total,
the rest frame spectrum $\bvec{s}$ consists of $K = 201$ log-wavelength bins in the range
$-\Delta\lnlam < \lnlam < \Delta\lnlam$ for $\Delta\lnlam = 3.3\times 10^{-4}$ plus an additional
%
\begin{align}
    W - 1 & = \frac{v\sin i}{c} \frac{K}{\Delta\lnlam} - 1 \nonumber           \\
          & = \left(\frac{40~\mathrm{km/s}}{3\times 10^5~\mathrm{km/s}}\right)
    \left(\frac{201}{3.3 \times 10^{-4}}\right)  - 1 \nonumber                 \\
          & = 80
\end{align}
%
log-wavelength bins of padding (40 on either side) to eliminate edge
effects due to the convolution, for a total of
$K' = 281$ wavelength bins. As in \citet{Vogt1987},
we assume a projected velocity of $v\sin i = 40$ km/s and an inclination
$i = 40^\circ$.

Given $\bvec{y_1}$ and $\bvec{s}$, we use Equations~(\ref{eq:deconv:F}) and~%
(\ref{eq:inverse:azero}) to
compute the data vector $\bvec{f}$
at $M = 16$ equally spaced rotational phases; these phases are shown in orthographic
projection (as an observer would see the star) in the center
panel of Figure~\ref{fig:spot_setup}. The synthetic spectra for each phase
are shown as the orange curves in the bottom panel of the figure (note the
different scaling, as all spectral lines become shallower due to the
broadening). We assume a wavelength-independent,
quadratic limb darkening law with $u_1 = 0.5$ and $u_2 = 0.25$. Finally,
we divide the flux by the baseline at each epoch (Equation~\ref{eq:norm:b})
and add random Gaussian noise with amplitude $\sigma_\bvec{f} = 10^{-4}$ to
simulate a very high signal-to-noise ratio (SNR) spectrum. The mean
standard deviation in each wavelength bin across all 16 epochs in the
noiseless data vector is about $10^{-2}$, so our choice of $\sigma_\bvec{f}$
corresponds to SNR $\sim$ 100 in each of the 201 wavelength bins of $\bvec{f}$.
%
%For reference, \citet{Vogt1987} report SNRs per 60 m\AA\, pixel, while our
%resolution elements are approximately $\lambda_r\Delta\lnlam/K \approx 100$ m\AA\,
%across, so our SNR in the same units as \citet{Vogt1987} is about 80.
%
% TODO: Perhaps Vogt computes the "signal" as the line depth, rather than
% as the amplitude of the perturbations? Check this.

% We Recover images with an effective resolution of $12^\circ$.

In the following sections we discuss various approaches to
solving the Doppler imaging problem for this dataset.
Unless otherwise noted, in all experiments we adopt a Gaussian prior
for the spherical harmonic coefficients $\bvec{y_1}$ with mean
$\boldsymbol{\mu}_\bvec{y_1} = \bvec{0}$ and covariance
$\boldsymbol{\Lambda}_\bvec{y_1} = (10^{-2})^2\bvec{I}$,
corresponding to a flat power spectrum prior.
We place a Gaussian process prior on the spectrum $\bvec{s}$ with mean
$\boldsymbol{\mu}_\bvec{s} = \bvec{1}$ and a covariance matrix
$\boldsymbol{\Lambda}_\bvec{s}$ computed from
a Mat\'ern-3/2 kernel with amplitude $\sigma_\bvec{s} = 0.3$
and lengthscale $\rho_\bvec{s} = 3\times 10^{-5}$.

\subsection{Known baseline and spectrum}
\label{sec:spot_y1}
%
In our first experiment, we attempt to infer the stellar map assuming
we have perfect knowledge of the rest frame spectrum $\bvec{s}$ and
the baseline $\bvec{b}$ (Equation~\ref{eq:norm:b}).
This is analogous to the case where a good physical model exists for
the stellar spectrum and simultaneous photometry is available to
constrain the baseline variations.
As we showed in
\S\ref{sec:solve_y}, the posterior distribution for the map coefficients
$\bvec{y_1}$ is analytic in this case, with mean given by Equation~(\ref{eq:inverse:y1hat})
and covariance given by Equation~(\ref{eq:inverse:y1cov}). Note that
we must first scale the data vector $\bvec{f}$ by $\bvec{b}$ (which in this
case is known).

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=0.49\linewidth]{figures/placeholder.pdf} % spot_y1_timeseries.pdf
        \includegraphics[width=0.49\linewidth]{figures/placeholder.pdf} % spot_y1_rect.pdf
        \oscaption{spot_y1}{%
            The solution to the \spot problem at high SNR when both
            the rest frame spectrum and the baseline are known.
            The panel on the left shows the inferred map at each of the 16
            epochs, alongside the observed spectrum (black points) and the
            best-fit model (orange lines). The rectangular projection of the
            original map is shown at the top right; the inferred map is
            displayed below it. The bottom panel shows the posterior uncertainty
            as a function of latitude and longitude, ranging from close to zero
            in the northern hemisphere to $\sigma_\mathrm{prior} \approx 10\%$
            below a latitude of $-30^\circ$. The latter is the uncertainty
            associated with our particular choice of prior, as the southernmost
            latitudes of the star are never visible to the observer.
            \label{fig:spot_y1}
        }
    \end{centering}
\end{figure}

The results are shown in Figure~\ref{fig:spot_y1}. The left hand panel
shows the inferred map alongside the data
(black points) and best fit model (orange curves) at each of the 16 epochs.
The panels on the right show the true map (top), the inferred map (center)
and the posterior pointwise uncertainty (bottom) on a rectangular
latitude-longitude grid. The uncertainty on the vector of pixels $\bvec{p}$ where
we evaluate the map is equal to the square root of the diagonal of
the posterior covariance matrix for the pixel values, computed from
%
\begin{align}
    \label{eq:spotstar:uncert}
    \boldsymbol{\Sigma}_\bvec{p} = \bvec{P} \boldsymbol{\Sigma}_\bvec{\hat{y}_1}^{-1} \bvec{P}^\top
\end{align}
%
where $\bvec{P}$ is the change-of-basis matrix from spherical harmonic
coefficients to pixels on the grid.

The inferred map is nearly indistinguishable from the true map, save for a
few small differences, particularly below the stellar equator. This is
captured by the uncertainty, which increases
south of $+30^\circ$ latitude, reaching a maximum at $-30^\circ$, below
which the uncertainty is constant at about 10\%. This is due to the fact
that regions below $-40^\circ$ latitude are never in view from the
observer's perspective, while regions between about $-30^\circ$ and
$-40^\circ$ are so strongly limb-darkened that the data contains little
information about them. The particular value of the uncertainty in this
region---10\%---is the uncertainty associated with the prior, which can
be computed by replacing $\boldsymbol{\Sigma}_\bvec{\hat{y}_1}$ with
$\boldsymbol{\Lambda}_\bvec{y_1}$ in Equation~(\ref{eq:spotstar:uncert}).

\subsection{Known spectrum, unknown baseline}
\label{sec:spot_y1b}
%
We next investigate the case where the spectrum is known exactly, but
the baseline is not. This corresponds to the case discussed in
\S\ref{sec:norm}. We use the solution to the linearized problem,
Equation~(\ref{eq:norm:yhat}), to obtain an initial guess for
$\bvec{y_1}$. We then repeatedly solve
Equation~(\ref{eq:inverse:y1hat}) for $\bvec{y_1}$, given the baseline
computed from the previous value of $\bvec{y_1}$ from Equation~(\ref{eq:norm:b}).
Because of the high SNR of our data, we find that it is necessary to employ
a simple tempering procedure to avoid getting stuck in local minima. We
introduce an artificial temperature $T$ that decreases every iteration
in equally spaced logarithmic steps $\Delta \log T$ from an initial temperature
$T=T_0$ to $T=1$. This temperature is used to scale the data covariance
$\boldsymbol{\Sigma}_\bvec{f}$; in practice, we simply replace
$\boldsymbol{\Sigma}_\bvec{f}$ with $T \boldsymbol{\Sigma}_\bvec{f}$
in Equation~(\ref{eq:inverse:y1hat}). This has the effect of smoothing
out the likelihood space, reducing the likelihood that the solver
will get stuck in a local minimum. For this particular experiment, we
set $T_0 = 100$ and $\Delta \log T = -0.25$, for a total of $9$ steps of
the bilinear solver.
%
In a final step, we run a gradient-descent optimizer, initializing it
at the solution obtained with the bilinear solver. We use
the \texttt{Keras} \citep{Keras} implementation of the
Nesterov momentum-enhanced Adam solver \citep[\texttt{NAdam};][]{NAdam},
running it for $N_\mathrm{nadam} = 80$ iterations at a learning rate
$L_\mathrm{nadam} = 10^{-4}$. Our loss function is simply the (negative)
log probability, equal to the sum of the log likelihood and log prior:
%
\begin{align}
    \label{eq:spotstar:logP}
    -\ln P & =
    \frac{1}{2}
    \Big(
    \bvec{r}^\top \boldsymbol{\Sigma}_\bvec{f}^{-1} \bvec{r} \, + \,
    \bvec{y_1}^\top \boldsymbol{\Lambda}_\bvec{y_1}^{-1} \bvec{y_1} \, + \,
    (\bvec{b - 1})^\top \boldsymbol{\Lambda}_\bvec{b}^{-1} (\bvec{b - 1})
    \Big)
\end{align}
%
where $\bvec{r}$ is the residual (data minus model) vector and the last term
is a prior we include on the baseline $\bvec{b}$, which we force to be close
to a mean of unity with covariance $\boldsymbol{\Lambda}_\bvec{b} = (0.1)^2\bvec{I}$.

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=0.49\linewidth]{figures/placeholder.pdf} % spot_y1b_timeseries.pdf
        \includegraphics[width=0.49\linewidth]{figures/placeholder.pdf} % spot_y1b_rect.pdf
        \\[0.5em]
        \includegraphics[width=0.405\linewidth]{figures/placeholder.pdf} % spot_y1b_baseline.pdf
        \includegraphics[width=0.575\linewidth]{figures/placeholder.pdf} % spot_y1b_coeffs.pdf
        \oscaption{spot_y1b}{%
            Similar to Figure~\ref{fig:spot_y1}, but assuming the baseline
            is not known. The panel at the bottom left shows the true baseline
            (blue) and the inferred baseline (orange), along with its $1\sigma$
            uncertainty. The large offset between the two highlights one of the
            fundamental degeneracies of the problem: since most of the southern
            hemisphere of the star is never visible, the coefficient of the
            $Y_{1,-1}$
            (\raisebox{-0.2em}{\includegraphics[width=1em]{figures/placeholder.pdf}}) % Y1m1.pdf
            spherical harmonic is not constrained by the data, resulting in
            an unknowable additive offset in the baseline.
            This effect can be seen also in (\emph{a}) the inferred map,
            where the background
            intensity in the northern hemisphere is significantly larger than
            that in the southern hemisphere, and (\emph{b}) the spherical
            harmonic coefficients (bottom right), where a large discrepancy is
            visible between the true and inferred values of the first two
            coefficients.
            \label{fig:spot_y1b}
        }
    \end{centering}
\end{figure}

Our results are shown in
Figure~\ref{fig:spot_y1b}. The panels at the top are the same as those
in Figure~\ref{fig:spot_y1}, but now we also plot the inferred baseline
(lower left) and spherical harmonic coefficients (lower right) next to
the true values. We recover the \texttt{SPOT} map just as well as before,
except for the presence of a strong dipolar artifact; the background
intensity level is higher in the northern hemisphere and lower in the
southern hemisphere. This effect is closely related to the fact that
we do not know the true baseline. While we are able to infer the
shape of the baseline exceedingly well (lower left panel), there is a large
offset between the true value and our inferred value. This is due to
a fundamental degeneracy involving the
$Y_{1,-1}$ (\raisebox{-0.2em}{\includegraphics[width=1em]{figures/placeholder.pdf}})  % Y1m1.pdf
spherical harmonic coefficient, which, because a large portion of the southern
hemisphere is never in view, cannot be constrained by the data. The
magnitude of the true value of the coefficient is quite large (lower right
panel), since the northern hemisphere \emph{is} significantly darker than
the southern hemisphere; however, the data do not constrain this, and
our prior shrinks all coefficients toward zero. The net effect is that the
region surrounding the spot in the northern hemisphere gets brighter to
even out the difference between the two hemispheres. This causes the
visible portion of the star to get brighter, raising the baseline
relative to the true value.

Note, importantly, that even in cases where the baseline is known (from, say,
simultaneous photometry), it is typically only known in a \emph{relative}
sense. This degeneracy will typically apply in that case as well, so in
principle the dipole term will always be unconstrained for stars at
similar inclinations. For inclinations closer to $90^\circ$ this is much
less of an issue, although (as we will see below) other degeneracies show up.

Finally, we note that the pixelwise uncertainty shown is a strict
\emph{lower bound} on the map uncertainty, since it is the uncertainty
conditioned on the inferred value of the baseline. Sampling methods
such as MCMC are required to obtain the \emph{true} uncertainty on the
map. We discuss this further in \S\ref{sec:discussion}.

\subsection{Unknown spectrum, unknown baseline}
\label{sec:spot_y1bs}
%
Suppose we are handed a series of spectra in a wavelength regime where
we do not have a good physical model for the line generation mechanisms,
or a wavelength regime with many line blends for which we do not have
reliable templates. Or perhaps the spectra are of a star whose
rotational broadening does not dominate over other broadening mechanisms,
in which case our template might not be accurate enough to allow us to
tease out the small Doppler signals. In these cases, we may want to relax
the assumption that we know the rest frame spectrum $\bvec{s}$ exactly,
and instead try to \emph{learn} it from the data.

Given the same data as before, we now try to learn both the stellar map
and the stellar spectrum, conditioned only on the wide Gaussian priors
discussed above. We must follow the iterative procedure presented in
\S\ref{sec:full_solve}, adjusting for the fact that we do not know
the true baseline, either (\S\ref{sec:norm}).

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=0.49\linewidth]{figures/placeholder.pdf} % spot_y1bs_timeseries.pdf
        \includegraphics[width=0.49\linewidth]{figures/placeholder.pdf} % spot_y1bs_rect.pdf
        \\[0.5em]
        \includegraphics[width=0.405\linewidth]{figures/placeholder.pdf} % spot_y1bs_baseline.pdf
        \includegraphics[width=0.575\linewidth]{figures/placeholder.pdf} % spot_y1bs_coeffs.pdf
        \\[0.5em]
        \includegraphics[width=0.98\linewidth]{figures/placeholder.pdf} % spot_y1bs_spectrum.pdf
        \oscaption{spot_y1bs}{%
            Similar to Figure~\ref{fig:spot_y1}, but assuming we have no
            information about either the spectrum, the baseline, or the map
            coefficients. The bottommost panel now shows the true rest frame
            spectrum (blue line), the initial guess based on a deconvolution
            (dashed orange line), and the inferred spectrum (orange line, with
            shaded $1\sigma$ uncertainty).
            \label{fig:spot_y1bs}
        }
    \end{centering}
\end{figure}

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=0.49\linewidth]{figures/placeholder.pdf} % spot_y1bs_low_snr_timeseries.pdf
        \includegraphics[width=0.49\linewidth]{figures/placeholder.pdf} % spot_y1bs_low_snr_rect.pdf
        \\[0.5em]
        \includegraphics[width=0.405\linewidth]{figures/placeholder.pdf} % spot_y1bs_low_snr_baseline.pdf
        \includegraphics[width=0.575\linewidth]{figures/placeholder.pdf} % spot_y1bs_low_snr_coeffs.pdf
        \\[0.5em]
        \includegraphics[width=0.98\linewidth]{figures/placeholder.pdf} % spot_y1bs_low_snr_spectrum.pdf
        \oscaption{spot_y1bs_low_snr}{%
            Same as Figure~\ref{fig:spot_y1bs}, but for $10\times$ lower SNR.
            We still recover the \spot map and the input spectrum, albeit with
            higher uncertainty, as expected.
            \label{fig:spot_y1bs_low_snr}
        }
    \end{centering}
\end{figure}

Because the problem is generally not convex, we need a good starting
guess for either the spectrum or the map coefficients. We note that
we can very crudely approximate the rest frame spectrum by deconvolving the
average observed spectrum with the first term of the convolution kernel
$\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{figures/placeholder.pdf}}). % kT00.pdf
This is equivalent to assuming the average map of the star
across all observations is featureless, and the average spectrum is equal
to the (symmetrically) rotationally-broadened version of the rest frame
spectrum. In practice, this is a fairly poor approximation, but we find that it
suffices as an initial guess. Given this starting value of $\bvec{s}$, we
compute an initial guess for $\bvec{y_1}$ using the linear baseline
approximation. We then iterate between solving for $\bvec{s}$ and
solving for $\bvec{y_1}$, always using the previous value of the
baseline to compute $\bvec{y_1}$. As in the previous section, we find it
necessary to implement a tempering scheme, except with a much higher
starting temperature $T_0 = 5,000$ and a slower decay $\Delta\log T = -0.04$.
We again refine our solution with \texttt{NAdam}, this time setting
$N_\mathrm{nadam} = 3,000$ and $L_\mathrm{nadam} = 2.5\times 10^{-5}$. Since
we are now solving for the spectrum as well, we include the negative log prior
term for the spectrum,
$\frac{1}{2}(\bvec{s - 1})^\top \boldsymbol{\Lambda}_\bvec{s}^{-1}(\bvec{s - 1})$,
in Equation~(\ref{eq:spotstar:logP}).

Figure~\ref{fig:spot_y1bs} shows the results. The top portion of the figure is
the same as before. A panel at the bottom has been added showing the true
rest frame spectrum (blue), the initial guess based on the deconvolution
(dashed orange), and the inferred spectrum (orange). We recover the \spot
feature as before, albeit with more noise, particularly south of about
$+30^\circ$ latitude. Our uncertainties are somewhat underestimated, as
expected, since they are computed conditioned on the optimum value of
the spectrum. On the other hand, we recover the spectrum exceedingly well,
with low uncertainty and virtually no bias anywhere.

To test our technique on more realistic data, in Figure~\ref{fig:spot_y1bs_low_snr}
we repeat the experiment on data with $10$ times higher uncertainty,
setting $\sigma_\bvec{f} = 10^{-3}$. Because the higher uncertainty increases
the volume of the region surrounding the global optimum, it is
actually significantly \emph{easier} for the algorithm to converge on the
best solution, so we set $T_0 = 500$, $\Delta\log T = -0.05$,
$N_\mathrm{nadam} = 500$, and $R_\mathrm{nadam} = 10^{-4}$. Interestingly,
while the uncertainty on the spectrum increased, the quality of the
recovered \spot map did not noticeably degrade. This suggests we did not
quite find the global optimum in Figure~\ref{fig:spot_y1bs}. We discuss
this further in \S\ref{sec:discussion}.

\subsection{Spatially-variable spectrum}
\label{sec:twospec}
%
In our final experiment, we relax the assumption that the stellar
rest frame spectrum is spatially constant, allowing for different
spectral features inside and outside of the \spot. This is the case
for, say, chemically peculiar Ap stars, whose abundance of certain
elements is significantly different within spotted regions on their
surfaces. It is also the case in general for spots that are significantly
cooler than the rest of the photosphere, where the relative abundance
of different ionization states or molecular features may be different
than in the hotter, unspotted regions.

The problem setup is the same as that discussed in \S\ref{sec:eigen}, where
our full map vector $\bvec{a_0}$ is the outer product of a spectral matrix
$\mathbb{S}$, whose $J$ columns are the different spectral components, and
a spherical harmonic coefficient matrix $\mathbb{Y}^\top$, whose $J$ rows
are the corresponding coefficient vectors. For simplicity, in this experiment
we consider only $J = 2$ spectral components and further require that the
first component is spatially constant, i.e., the first row of
$\mathbb{Y}^\top$ is the vector $(1 \quadquad \bvec{0}^\top)$. The second
row of $\mathbb{Y}^\top$ is the vector $(1 \quadquad \bvec{y_1}^\top)$, where
$\bvec{y_1}$ is the (unknown) spherical harmonic expansion of the spot. The
two columns of $\mathbb{S}$ are $\bvec{s_1}$ and $\bvec{s_2}$, the unknown
spectral components.

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/placeholder.pdf} % twospec.pdf
        \oscaption{twospec}{%
            An example of a star whose spectrum is different within the spot
            (\texttt{B}) and outside of the spot (\texttt{A}). Everywhere on
            the surface, the spectrum is a linear combination of two
            spectral components ($s_1$ and $s_2$).
            As in Figure~\ref{fig:spot_y1bs}, we assume
            we do not know the map, the baseline, or either of the spectra.
            The top row shows the true values for the map and the spectra, and
            the bottom row shows our inferred values.
            \label{fig:twospec}
        }
    \end{centering}
\end{figure}
%
We set \bvec{s_1} equal to a flat spectrum with two absorption lines of
different depths, and \bvec{s_2} to the same spectrum, except we make the
second line an emission feature. The local rest-frame spectrum everywhere on the
surface is a linear combination of these two spectra. In our simple problem,
the weight given to the first spectrum is the same everywhere (encoded in
the first row of $\mathbb{Y}^\top$), and the weight
given to the second spectrum is large outside of the spot and small within
the spot (encoded in the second row of $\mathbb{Y}^\top$, which we set equal
to the spherical harmonic expansion of the \spot feature).
The first row of Figure ~\ref{fig:twospec} shows the problem setup. The two
spectral components are shown as the blue ($\bvec{s_1}$) and green
($\bvec{s_2}$) curves at the right. Point \texttt{A} on the map (left panel)
is outside the spot feature, so its local spectrum has nearly equal
contributions from $\bvec{s_1}$ and $\bvec{s_2}$, and the second spectral
line is absent (center panel). Point \texttt{B} is inside the spot, so
it receives a contribution from $\bvec{s_1}$ only.

In our inference step, we again assume we have no knowledge of the map,
the baseline, or either of the spectral components. As before, we initialize
$\bvec{s_1}$ to the deconvolved mean spectrum and $\bvec{s_2}$ to the
deconvolved mean spectrum after subtracting $\bvec{s_1}$. In practice this
leads to a decent approximation to $\bvec{s_1}$ but a rather featureless
guess for $\bvec{s_2}$. We use the same priors as before, except we
set $\sigma_\bvec{s_1} = \sigma_\bvec{s_2} = 0.01$ to force the continuum
to be flatter. We run our bilinear solver with $T_0 = 5,000$ and
$\Delta\log T = -0.025$ followed by the nonlinear solver with
$N_\mathrm{nadam} = 2,000$ and $L_\mathrm{nadam} = 3\times 10^{-4}$.

The results are shown in the bottom panel of Figure~\ref{fig:twospec}.
We recover the \spot feature reasonably well, although with more artifacts
than in the previous experiments. We also recover the two spectral components,
although our solution for $\bvec{s_2}$ is significantly better than that for
$\bvec{s_1}$. This is due to the fact that the only information
about $\bvec{s_1}$ that makes it into our dataset is the convolution of
$\bvec{s_1}$ with the first term of the convolution kernel
$\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{figures/placeholder.pdf}}), % kT00.pdf
since this spectral component has no spatial variability.
Since the deconvolution operation is in general ill-posed, there is no
unique solution for $\bvec{s_1}$. On the other hand, the other spectral
component projects into the data via convolutions with all other
terms of the kernel and is therefore very well constrained.
Finally, we can estimate the spectra at points \texttt{A} and \texttt{B}
as before (center panel). We recover the single spectral line at \texttt{A}
and the two lines at \texttt{B}, albeit rather noisily due to the uncertainty
in $\bvec{s_1}$.

\section{Discussion}
\label{sec:discussion}
%

\xxx{%
    \begin{enumerate}
        %
        \item%
              A gaussian prior with unit mean is a pretty bad prior for the spectrum.
              In a more realistic scenario, we'd know a lot more information about the
              spectrum---such as where the lines are and some estimate of their shapes
              and depths---so the fidelity of our maps would be higher.
              %
        \item We are not addressing differential rotation and convective blueshift.
              These make the integral in Equation~(\ref{eq:deconv:kT}) very difficult
              to solve. We will tackle this in the next paper.
              %
        \item Telluric lines could be treated much as in Figure~\ref{fig:twospec},
              and marginalized over as in \citet{Bedell2019}.
              %
        \item The instrumental profile is another Toeplitz matrix that can be
              dotted into Equation~(\ref{eq:linear:f}).
              %
        \item Discuss the case where the inclination/period/velocity is unknown.
              The problem is not linear in these variables, so we need MCMC. But our
              model is differentiable, so we can easily use HMC. Discuss.
              %
        \item%
              Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires
              first the rotation of the $(\lmax + 1)^2$
              $\kT$ kernels (each of length $W$) to the correct stellar
              rotational phase, an operation that scales approximately
              as $W \lmax^3$,
              followed by $(\lmax + 1)^2$
              linear convolutions of the rotated $\kT$ kernels with the
              spectral components (each of length $K$), which scales
              approximately as $W K \lmax^2$. Since typically $K \gg \lmax$,
              the latter computation dominates and the entire evaluation
              takes $\mathcal{O}(W K \lmax^2)$ operations.
    \end{enumerate}
}

\subsection{Dependence on SNR}
\label{sec:snr}
%
Most of the examples in this paper considered very high SNR spectra.
Figure~\ref{fig:snr} shows the effect of different SNR on the quality
of the inferred map. As before, the SNR we report is the ratio of the
standard deviation of the true model in each wavelength bin across
all epochs, averaged over all wavelength bins (i.e., the ``signal'') to the
standard deviation of the added noise term, $\sigma_\bvec{f}$ (the ``noise'').
The panels in Figure~\ref{fig:snr} show the inferred map for SNR in the range
1---1000, where SNR $\sim 100$ is the fiducial case considered in the
examples so far. The setup is the same as that in \S\ref{sec:spot_y1b}, where
the spectrum is known exactly but the map coefficients and the baseline are
not.

As may be expected, the quality of the map decreases with lower SNR, but
a reduction of the SNR by $\sim 20\times$ still allows for reasonable
recovery of the \spot feature. In general, as the SNR decreases further,
two things happen: the \spot contrast decreases, and the features begin to
blur out, especially south of about $+30^\circ$ latitude, where features
are more limb-darkened
at this inclination and in view for a smaller fraction of the time.

As the SNR incraeses, however, the quality of the \spot feature does not
improve appreciably, since a SNR of 100 is more than sufficient to recover
a $l_\mathrm{max} = 15$ band-limited map. Interestingly, south of the equator,
the map quality actually begins to degrade with higher SNR. This is due to
the fact that finding the global optimum becomes exponentially more difficult
with higher SNR, as the posterior volume becomes ever smaller. Even with
aggressive tempering, we were unable to converge on the best solution for
SNR $\gtrsim 500$ given our standard, conservative priors and initial
guesses (\S\ref{sec:spotstar}).
%
\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=0.98\linewidth]{figures/placeholder.pdf} % snr.pdf
        \oscaption{snr}{%
            Recovered \spot map as a function of SNR per resolution element.
            The quality of the inferred map in the northern hemisphere improves
            with SNR, but at very high SNR the region surrounding the global
            optimum becomes so small that our optimization methods struggle to
            converge on the correct solution.
            \label{fig:snr}
        }
    \end{centering}
\end{figure}
%
\subsection{Dependence on inclination}
\label{sec:inc}
%
\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=0.98\linewidth]{figures/placeholder.pdf} % inclinations.pdf
        \oscaption{inclinations}{%
            Recovered \spot map as a function of stellar inclination. The
            rest frame spectrum is assumed to be known exactly, but the
            baseline is not. At very low inclinations, the small
            projected velocities begin to degrade the spatial resolution of
            the inferred map, while at inclinations close to $90^\circ$ there
            is a degeneracy between the northern and southern hemispheres.
            \label{fig:inclinations}
        }
    \end{centering}
\end{figure}
As in \citet{Vogt1987},
we also investigate the dependence of the solution on the inclination
of the star.
Figure~\ref{fig:inclinations} shows the inferred map for the same problem
setup as before (with SNR $\sim 100$), but this time varying the
inclination between $10^\circ$ (nearly face-on) and $90^\circ$ (perfectly
edge-on). As before, the inclination is assumed to be known exactly. We
further keep the true equatorial velocity of the star constant across
all panels, so that the figure corresponds to the same star viewed at
different orientations. Because of this, decreasing the inclination
decreases $v\sin i$, reducing the width of the convolution kernel and
therefore the spatial resolution of our inferred map. Increasing the
inclination does not result in appreciable changes until an inclination of
$\sim 80^\circ$, above which it becomes difficult to differentiate between
features in the northern and southern hemispheres, whose projected
velocities are nearly equal. At $i = 90^\circ$, there is a formal
degeneracy between the two hemispheres, which can be seen from the
mirror-image symmetry in the inferred map. These results are broadly consistent
with those of \citet{Vogt1987}.

\section{Conclusions}
\label{sec:conclusions}
\xxx{%
    \begin{enumerate}
        \item Advantages of data-driven modeling
        \item Interpretable priors
        \item Works on blended lines
        \item Uses the whole spectrum
        \item Yields uncertainties!
        \item Probably works on slow rotators
        \item Differentiable!
        \item Fast!
        \item Use in MCMC to marginalize over inclination and stuff
    \end{enumerate}
}

%
%
%
%
\clearpage
\appendix
%
%
%
%

\section{Solving the $\kT$ integral}
%
In this section we will show how to compute the integral in
Equation~(\ref{eq:kT:kT}), yielding the terms of the convolution
kernel $\kT$. It is convenient to first change basis from spherical harmonics to
polynomials on the sphere:
%
\begin{align}
    \label{eq:appendix:kT}
    \kT(\lnlam, \Dargs)
     & =
    \int\limits_{-\sqrt{1 - x^2}}^
    {\sqrt{1 - x^2}}
    \pbasis
    \Big(x, y\Big)
    \mathrm{d}y
    \,
    \AOne
    \nonumber \\[0.5em]
     & \equiv
    \rhoT(\lnlam, \Dargs)
    \,
    \AOne
    \quad,
\end{align}
%
where $\AOne$ is the change of basis matrix from spherical harmonics
to polynomials \citep[Equation B11 in][]{Luger2019} and
%
\begin{align}
    \pbasis(\x) \equiv
    \Big(
    1 \quad\quad\quad\quad\quad\quad
    x \quad\quad\quad\quad\quad\quad
    z \quad\quad\quad\quad\quad\quad
    y \quad\quad\quad\quad\quad\quad
    x^2 \quad\quad\quad\quad\quad\quad
    xz \quad\quad\quad\quad\quad\quad
    xy \quad\quad\quad\quad\quad\quad
    yz \quad\quad\quad\quad\quad\quad
    y^2 \quad\quad\quad\quad\quad\quad
    ...
    \Big)^\top
    \quad,
\end{align}
%
is the polynomial basis \citep[Equation 7][]{Luger2019}.
The $n^\mathrm{th}$ term of the polynomial basis
is a polynomial in $x$, $y$, and $z = \sqrt{1 - x^2 - y^2}$:
%
\begin{align}
    \pbasisn
    &=
    x^i y^j z^k
\end{align}
%
where $i, j, k$ are integers given by
%
\begin{align}
    \label{eq:kT:lm}
    i &= \floor*{\Lambda - \Delta}
    \nonumber \\[0.5em]
    j &= \floor*{\Delta}
    \nonumber \\[0.5em]
    k &= \ceil*{\Delta} - \floor*{\Delta}
\end{align}
%
with
%
\begin{align}
    \Lambda &= \floor*{\sqrt{n}}
    \nonumber \\[0.5em]
    \Delta &= \frac{n - \Lambda^2}{2}
    \quad .
\end{align}
%
We may now explicitly write down the $n^\mathrm{th}$ term of
the vector $\rhoT(\lnlam, \Dargs)$ in Equation~(\ref{eq:appendix:kT}),
%
\begin{align}
    \label{eq:kT:sTexpression}
    \rho_n(\lnlam, \Dargs)
     & =
    \rho_{i,\,j,\,k}(\lnlam, \Dargs)
    =
    x^i
    \int\limits_{-\sqrt{1 - x^2}}^
    {\sqrt{1 - x^2}}
    y^j
    \left(1 - x^2 - y^2\right)^{\frac{k}{2}} \,
    \mathrm{d}y
    \quad .
\end{align}
%
When $i = k = 0$, the integral is easy to evaluate:
%
\begin{align}
    \rho_{i,\,j,\,0}(\lnlam_0)
     & =
    \begin{cases}
        2 \left( 1 - x^2 \right)^\frac{j + 1}{2}
        \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
          & j \, \mathrm{even}        \\
        0 & j \, \mathrm{odd} \quad .
    \end{cases}
\end{align}
%
The general term may be computed from the recurrence relation
%
\begin{align}
    \rho_{0,\,j,\,0}(\lnlam_0) = \frac{j - 1}{j + 1} \big(1 - x^2\big) \rho_{0,\,j-2,\,0}
\end{align}
%
provided
%
\begin{align}
    \rho_{0,\,0,\,0} & = 2 \sqrt{1-x^2} \nonumber \\
    \rho_{0,\,1,\,0} & = 0 \quad.
\end{align}
%
When $i = 0$ and $k = 1$, we may substitute $y = \sin\psi\sqrt{1 - x^2}$ in
the integrand to obtain
%
\begin{align}
    \rho_{0,\,j,\,1}(\lnlam_0)
     & =
    (1 - x^2)^{\frac{j + 2}{2}}
    \int\limits_{-\frac{\pi}{2}}^{\frac{\pi}{2}}
    \sin^j\psi
    \cos^2\psi \,
    \mathrm{d}\psi
    \quad.
\end{align}
%
We may solve this integral using the recurrence relation
%
\begin{align}
    \int
    \sin^j\psi
    \cos^m\psi \,
    \mathrm{d}\psi
     & =
    -\frac{\sin^{j-1}\psi \cos^{m+1}\psi}{j + m}
    +
    \frac{j - 1}{j + m}\int\sin^{j-2}\psi \cos^m\psi \mathrm{d}\psi
    \quad ,
\end{align}
%
which, in our case, simplifies to
%
\begin{align}
    \int\limits_{-\frac{\pi}{2}}^{\frac{\pi}{2}}
    \sin^j\psi
    \cos^2\psi \,
    \mathrm{d}\psi
     & =
    \frac{j - 1}{j + 2}\int\limits_{-\frac{\pi}{2}}^
    {\frac{\pi}{2}}\sin^{j-2}\psi \cos^2\psi \mathrm{d}\psi
    \quad.
\end{align}
%
We thus arrive at the recurrence relation
%
\begin{align}
    \rho_{0,\,j,\,1} & = \frac{j - 1}{j + 2} \big(1 - x^2\big) \rho_{0,\,j-2,\,1}
\end{align}
%
with initial conditions
%
\begin{align}
    \rho_{0,\,0,\,1} & = \frac{\pi}{2} \big(1-x^2\big) \nonumber \\
    \rho_{0,\,1,\,1} & = 0 \quad.
\end{align}
%
Given these expressions, recursing upward in $i$ is easy:
%
\begin{align}
    \rho_{i,\,j,\,k} & = x \, \rho_{i-1,\,j,\,k} \quad.
\end{align}
%
This completes our derivation. To summarize, given the boundary conditions
%
\begin{align}
    \rho_{0,\,0,\,0} & = 2 \sqrt{1-x^2} \nonumber                \\
    \rho_{0,\,0,\,1} & = \frac{\pi}{2} \big(1-x^2\big) \nonumber \\
    \rho_{0,\,1,\,k} & = 0 \quad ,
\end{align}
%
we may compute any term in $\rhoT$ via the expressions
%
\begin{align}
    \label{eq:kT:sTrecurrence}
    \rho_{0,\,j,\,k} & = \frac{j - 1}{j + 1 + k} \big(1 - x^2\big) \rho_{0,\,j-2,\,k} \nonumber \\
    \rho_{i,\,j,\,k} & = x \, \rho_{i-1,\,j,\,k} \quad.
\end{align}
%
The terms of the convolution kernel $\kT$ are then obtained by dotting
this vector into the change of basis matrix $\AOne$, as discussed above.

% Table
\clearpage
\begin{center}
    \begin{longtable}{cll}
        \caption{Common notation used in this paper}
        \label{tab:notation}                                                                                                                                            \\
        %
        \toprule
        \multicolumn{1}{c}{\textbf{Symbol}}                 &
        \multicolumn{1}{c}{\textbf{Description}}            &
        \multicolumn{1}{c}{\textbf{Reference}}                                                                                                                          \\
        \midrule
        \endfirsthead
        %
        \multicolumn{3}{c}%
        {{\bfseries \tablename\ \thetable{}}. (continued from previous page)}                                                                                           \\[0.5em]
        \toprule
        \multicolumn{1}{c}{\textbf{Symbol}}                 &
        \multicolumn{1}{c}{\textbf{Definition}}             &
        \multicolumn{1}{c}{\textbf{Reference}}                                                                                                                          \\
        \midrule
        \endhead
        \bottomrule
        %
        \endfoot
        %
        \endlastfoot
        %
        \midrule
        \multicolumn{3}{c}{\emph{Variables}}                                                                                                                            \\
        \midrule
        %
        $a_{lm}$                                            & spectral spherical harmonic coefficient                      & Equation~(\ref{eq:deconv:Ixi0})            \\
        $\alm$                                              & vector of spectral spherical harmonic coefficients           & Equation~(\ref{eq:deconv:alm})             \\
        $\bvec{a_0}$                                        & $\alm$ at reference time $t = t_0$                           & Equation~(\ref{eq:deconv:R})               \\
        $\bvec{A_0}$                                        & matrix form of $\bvec{a_0}$                                  & Equation~(\ref{eq:inverse:azero})          \\
        $\bvec{b}$                                          & flux baseline vector                                         & Equation~(\ref{eq:norm:b})                 \\
        $\bvec{B}$                                          & block matrix representation of $\bvec{b}$                    & Equation~(\ref{eq:norm:b})                 \\
        $c$                                                 & speed of light                                               & Equation~(\ref{eq:kT:beta})                \\
        $\Curve$                                            & curve of constant radial velocity                            & Equation~(\ref{eq:deconv:kT})              \\
        $\Dargs$                                            & parameters of the Doppler field                              & \S\ref{sec:the_problem}                    \\
        $\D$                                                & logarithmic Doppler shift                                    & Equation~(\ref{eq:the_problem:D})          \\
        $\Doppler$                                          & Doppler design matrix                                        & Equation~(\ref{eq:linear:f})               \\
        $\bvec{f}$                                          & vector of observed flux values                               & Equation~(\ref{eq:linear:f})               \\
        $F$                                                 & flux                                                         & Equation~(\ref{eq:the_problem:F})          \\
        $i$                                                 & inclination                                                  & Equation~(\ref{eq:kT:beta})                \\
        $I$                                                 & specific intensity                                           & Equation~(\ref{eq:the_problem:Ixi})        \\
        $\bvec{I}$                                          & identity matrix                                              &                                            \\
        $l$                                                 & spherical harmonic degree                                    &                                            \\
        $L_\mathrm{nadam}$                                  & \texttt{NAdam} learning rate                                 & \S\ref{sec:spotstar}                       \\
        $\bvec{L}$                                          & limb darkening operator                                      & Equation~(\ref{eq:ld:L})                   \\
        $m$                                                 & spherical harmonic order                                     &                                            \\
        $N_\mathrm{nadam}$                                  & number of \texttt{NAdam} iterations                          & \S\ref{sec:spotstar}                       \\
        $\bvec{P}$                                          & Change of basis matrix from $Y_{lm}$ to pixels               & Equation~(\ref{eq:spotstar:uncert})        \\
        $\bvec{R}$                                          & Wigner rotation matrix                                       & Equation~(\ref{eq:deconv:R})               \\
        $\bvec{s}$                                          & vector representation of the spectrum                        & Equation~(\ref{eq:inverse:azero})          \\
        $\bvec{S}$                                          & block matrix representation of $\bvec{s}$                    & Equation~(\ref{eq:inverse:S})              \\
        $\boldsymbol{\mathbb{S}}$                           & matrix of $J$ spectral components                            & Equation~(\ref{eq:eigen:azero})            \\
        $\Surf$                                             & projected visible area of the star                           & Equation~(\ref{eq:the_problem:F})          \\
        $t$                                                 & time                                                         & \S\ref{sec:the_problem}                    \\
        $T$                                                 & artificial temperature in bilinear solver                    & \S\ref{sec:spotstar}                       \\
        $T_0$                                               & initial artificial temperature setting                       & \S\ref{sec:spotstar}                       \\
        $\Delta\log T$                                      & artificial temperature step size                             & \S\ref{sec:spotstar}                       \\
        $u$                                                 & limb darkening coefficient                                   & \S\ref{sec:ld}                             \\
        $\x$                                                & Cartesian position on the sky                                & \S\ref{sec:the_problem}                    \\
        $y_{lm}$                                            & spherical harmonic coefficient                               & \S\ref{sec:inverse}                        \\
        $\bvec{y}$                                          & vector of spherical harmonic coefficients                    & Equation~(\ref{eq:inverse:azero})          \\
        $Y_{lm}$                                            & spherical harmonic                                           & Equation~(\ref{eq:deconv:Ixi0})            \\
        $\bvec{Y}$                                          & block matrix representation of $\bvec{y}$                    & Equation~(\ref{eq:inverse:Y})              \\
        $\boldsymbol{\mathbb{Y}}$                           & matrix of $J$ spherical harmonic components                  & Equation~(\ref{eq:eigen:azero})            \\
        %
        \pagebreak
        \midrule
        \multicolumn{3}{c}{\emph{Variables (Greek)}}                                                                                                                    \\
        \midrule
        %
        $\beta$                                             & relativistic parameter                                       & Equation~(\ref{eq:the_problem:D})          \\
        $\delta$                                            & Dirac delta function                                         & Equation~(\ref{eq:deconv:convolution})     \\
        $\kT$                                               & convolution kernel basis vector                              & Equation~(\ref{eq:deconv:kT})              \\
        $\lambda$                                           & wavelength                                                   & \S\ref{sec:the_problem}                    \\
        $\lambda_\mathrm{r}$                                & reference wavelength                                         & \S\ref{sec:the_problem}                    \\
        $\lnlam$                                            & $\ln\nicefrac{\lambda}{\lambda_\mathrm{r}}$ (observer frame) & \S\ref{sec:the_problem}                    \\
        $\lnlam_0$                                          & $\ln\nicefrac{\lambda}{\lambda_\mathrm{r}}$ (rest frame)     & \S\ref{sec:the_problem}                    \\
        $\boldsymbol{\Lambda}$                              & prior covariance matrix                                      &                                            \\
        $\boldsymbol{\mu}$                                  & prior mean vector                                            &                                            \\
        $\ylmbasis$                                         & spherical harmonic basis vector                              & Equation~(\ref{eq:deconv:ylmbasis})        \\
        $\boldsymbol{\Sigma}$                               & covariance matrix                                            &                                            \\
        $\omega$                                            & angular velocity                                             & Equation~(\ref{eq:kT:beta})                \\
        %
        \midrule
        \multicolumn{3}{c}{\emph{Dimensions}}                                                                                                                           \\
        \midrule
        %
        $J$                                                 & \# of spectral components                                    & \S\ref{sec:eigen}                          \\
        $K$                                                 & \# of wavelength bins in the observed spectrum               & \S\ref{sec:linear}                         \\
        $K'$                                                & \# of wavelength bins in the latent spectrum                 & \S\ref{sec:linear}                         \\
        $M$                                                 & \# of epochs observed                                        & \S\ref{sec:linear}                         \\
        $N$                                                 & \# of spherical harmonic coefficients                        & \S\ref{sec:linear}                         \\
        $N'$                                                & \# of spherical harmonic coefficients after limb darkening   & \S\ref{sec:ld}                             \\
        $W$                                                 & \# of wavelength bins in the convolution kernel              & \S\ref{sec:linear}                         \\
        %
        \midrule
        \multicolumn{3}{c}{\emph{Operators \& Other symbols}}                                                                                                           \\
        \midrule
        %
        $\mathrm{diag}$                                     & diagonal matricization                                       & Equation~(\ref{eq:ld:Dmwav})               \\
        $\mathrm{vec}$                                      & vectorization                                                & Equation~(\ref{eq:inverse:azero})          \\
        $*$                                                 & convolution                                                  & Equation~(\ref{eq:deconv:convolution_def}) \\
        $\circ$                                             & element-wise product                                         & Equation~(\ref{eq:norm:fapprox})           \\
        $\otimes$                                           & Kronecker product                                            & Equation~(\ref{eq:linear:Dm})              \\
        $\ceil*{\,}$                                        & ceiling                                                      & Equation~(\ref{eq:kT:lm})                  \\
        $\floor*{\,}$                                       & floor                                                        & Equation~(\ref{eq:kT:lm})                  \\
        $\bvec{0}$                                          & the zero vector,
        $(0 \quadquad 0 \quadquad \cdots \quadquad 0)^\top$ &                                                                                                           \\
        $\bvec{1}$                                          & the one vector,
        $(1 \quadquad 1 \quadquad \cdots \quadquad 1)^\top$ &                                                                                                           \\
    \end{longtable}
\end{center}

% Bibliography
\clearpage
\bibliography{bib}

\end{document}

### 2021-08-12 figures/kT.py

@@ -1,0 +1,48 @@
+# -*- coding: utf-8 -*-
+"""
+Plots the basis of `g` kernels.
+
+"""
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import paparazzi as pp
+
+
+# Get the `kT` functions at high res
+ydeg = 10
+dop = pp.Doppler(ydeg=ydeg)
+dop.generate_data(R=1e6, nlam=99, y1=np.zeros(dop.N - 1))
+kT = dop.kT()
+
+# Set up the plot
+fig, ax = plt.subplots(
+    ydeg + 1, 2 * ydeg + 1, figsize=(16, 10), sharex=True, sharey=True
+)
+fig.subplots_adjust(hspace=0)
+for axis in ax.flatten():
+    axis.spines["top"].set_visible(False)
+    axis.spines["right"].set_visible(False)
+    axis.spines["bottom"].set_visible(False)
+    axis.spines["left"].set_visible(False)
+    axis.set_xticks([])
+    axis.set_yticks([])
+
+# Loop over the orders and degrees
+n = 0
+for i, l in enumerate(range(ydeg + 1)):
+    for j, m in enumerate(range(-l, l + 1)):
+        j += ydeg - l
+        ax[i, j].plot(kT[n])
+        n += 1
+
+# Labels
+for j, m in enumerate(range(-ydeg, ydeg + 1)):
+    ax[-1, j].set_xlabel("%d" % m, fontsize=14, alpha=0.5)
+for i, l in enumerate(range(ydeg + 1)):
+    ax[i, ydeg - l].set_ylabel(
+        "%d" % l, fontsize=14, rotation=45, labelpad=20, alpha=0.5
+    )
+
+# Save
+fig.savefig("kT.pdf", bbox_inches="tight")

### 2021-08-12 figures/linalg.py

@@ -1,0 +1,247 @@
+# -*- coding: utf-8 -*-
+"""
+Plots an image of the Doppler design matrix for a low
+degree inference problem.
+
+"""
+import matplotlib.pyplot as plt
+import numpy as np
+import paparazzi as pp
+from scipy.sparse import hstack, vstack, csr_matrix, block_diag, diags
+import starry
+
+np.random.seed(11)
+
+
+def RAxisAngle(axis=[0, 1, 0], theta=0):
+    """
+    Rotate an arbitrary point by an axis and an angle.
+
+    """
+    cost = np.cos(theta)
+    sint = np.sin(theta)
+
+    return np.reshape(
+        [
+            cost + axis[0] * axis[0] * (1 - cost),
+            axis[0] * axis[1] * (1 - cost) - axis[2] * sint,
+            axis[0] * axis[2] * (1 - cost) + axis[1] * sint,
+            axis[1] * axis[0] * (1 - cost) + axis[2] * sint,
+            cost + axis[1] * axis[1] * (1 - cost),
+            axis[1] * axis[2] * (1 - cost) - axis[0] * sint,
+            axis[2] * axis[0] * (1 - cost) - axis[1] * sint,
+            axis[2] * axis[1] * (1 - cost) + axis[0] * sint,
+            cost + axis[2] * axis[2] * (1 - cost),
+        ],
+        [3, 3],
+    )
+
+
+def get_ortho_latitude_lines(inc=np.pi / 2, obl=0, dlat=np.pi / 6, npts=1000):
+    """
+    Return the lines of constant latitude on an orthographic projection.
+
+    """
+    # Angular quantities
+    ci = np.cos(inc)
+    si = np.sin(inc)
+    co = np.cos(obl)
+    so = np.sin(obl)
+
+    # Latitude lines
+    res = []
+    latlines = np.arange(-np.pi / 2, np.pi / 2, dlat)[1:]
+    for lat in latlines:
+
+        # Figure out the equation of the ellipse
+        y0 = np.sin(lat) * si
+        a = np.cos(lat)
+        b = a * ci
+        x = np.linspace(-a, a, npts)
+        y1 = y0 - b * np.sqrt(1 - (x / a) ** 2)
+        y2 = y0 + b * np.sqrt(1 - (x / a) ** 2)
+
+        # Mask lines on the backside
+        if si != 0:
+            if inc > np.pi / 2:
[…]

### 2021-08-12 figures/spot_setup.py

@@ -1,0 +1,169 @@
+# -*- coding: utf-8 -*-
+"""
+Setup for the SPOT problem.
+
+"""
+
+# DEBUG
+import theano
+
+theano.config.optimizer = "None"
+theano.config.exception_verbosity = "high"
+
+import paparazzi as pp
+import numpy as np
+import matplotlib.pyplot as plt
+
+# Generate the data
+np.random.seed(13)
+dop = pp.Doppler(ydeg=15, u=[0.5, 0.25])
+dop.generate_data(ferr=0)
+
+# Render the map
+dop.s = dop.s_true
+dop.y1 = dop.y1_true
+map = dop._map
+res = 300
+img = map.render(projection="rect", res=res).eval()
+img_ortho = map.render(theta=dop.theta, projection="ortho", res=res).eval()
+
+# Set up the plot
+fig = plt.figure(figsize=(11, 9))
+fig.subplots_adjust(hspace=0.75)
+ax = [
+    plt.subplot2grid((33, 8), (0, 0), rowspan=12, colspan=5),
+    plt.subplot2grid((33, 8), (0, 5), rowspan=12, colspan=3),
+]
+ax_ortho = [
+    plt.subplot2grid((33, 8), (14, n), rowspan=4, colspan=1) for n in range(8)
+]
+ax_ortho += [
+    plt.subplot2grid((33, 8), (18, n), rowspan=4, colspan=1) for n in range(8)
+]
+ax_data = plt.subplot2grid((33, 8), (23, 0), rowspan=10, colspan=8)
+
+# Show the rect image
+ax[0].imshow(img, origin="lower", extent=(-180, 180, -90, 90), cmap="plasma")
+latlines = np.linspace(-90, 90, 7)[1:-1]
+lonlines = np.linspace(-180, 180, 13)
+for lat in latlines:
+    ax[0].axhline(lat, color="k", lw=0.5, alpha=0.5, zorder=100)
+for lon in lonlines:
+    ax[0].axvline(lon, color="k", lw=0.5, alpha=0.5, zorder=100)
+ax[0].set_xticks(lonlines)
+ax[0].set_yticks(latlines)
+for tick in ax[0].xaxis.get_major_ticks() + ax[0].yaxis.get_major_ticks():
+    tick.label.set_fontsize(10)
+ax[0].set_xlabel("Longitude [deg]", fontsize=10)
+ax[0].set_ylabel("Latitude [deg]", fontsize=10)
+
+# Show the ortho images
+vmin = np.nanmin(img_ortho)
[…]

### 2021-08-12 figures/spot_y1b.py

@@ -1,0 +1,50 @@
+# -*- coding: utf-8 -*-
+"""
+Solve the SPOT problem.
+
+In this case, we know the rest frame spectrum, but we don't
+know the map coefficients or the baseline flux. The problem
+can be linearized to solve for the coefficients, and then
+refined with the non-linear solver.
+
+"""
+import paparazzi as pp
+import numpy as np
+from utils.spot import plot_results
+
+np.random.seed(13)
+
+# Let's plot the high SNR case for the paper
+high_snr = True
+
+# High or low SNR?
+if high_snr:
+    # At high SNR, we need to do a bit of refinement
+    # with the non-linear solver.
+    ferr = 1e-4
+    niter = 80
+    lr = 1e-4
+    T = 100.0
+    dlogT = -0.25
+else:
+    # At low SNR, a single run of the bi-linear solver
+    # gets us to the optimum!
+    ferr = 1e-3
+    niter = 0
+    lr = None
+    T = 1.0
+    dlogT = -0.25
+
+# Generate data
+dop = pp.Doppler(ydeg=15, u=[0.5, 0.25])
+dop.generate_data(ferr=ferr)
+
+# Reset all coefficients
+dop.s = dop.s_true
+dop.y1 = None
+
+# Solve!
+loss, cho_y1, cho_s = dop.solve(s=dop.s, niter=niter, lr=lr, T=T, dlogT=dlogT)
+
+# Plot the results
+plot_results(dop, name="spot_y1b", loss=loss, cho_y1=cho_y1, cho_s=cho_s)

### 2021-08-12 figures/spot_y1bs.py

@@ -1,0 +1,38 @@
+# -*- coding: utf-8 -*-
+"""
+Solve the SPOT problem.
+
+In this case, we know nothing: we're going to learn
+both the map and the spectrum. We're not giving the
+algorithm an initial guess, either: the spectrum is
+learned by deconvolving the data, and the initial
+guess for the map is computed via the linearized
+problem.
+
+"""
+import paparazzi as pp
+import numpy as np
+from utils.spot import plot_results
+
+np.random.seed(13)
+
+# Let's plot the high SNR case for the paper
+ferr = 1e-4
+T = 5000.0
+niter = 3000
+lr = 2.5e-5
+dlogT = -0.04
+
+# Generate data
+dop = pp.Doppler(ydeg=15, u=[0.5, 0.25])
+dop.generate_data(ferr=ferr)
+
+# Reset all coefficients
+dop.y1 = None
+dop.s = None
+
+# Solve!
+loss, cho_y1, cho_s = dop.solve(niter=niter, lr=lr, T=T, dlogT=dlogT)
+
+# Plot the results
+plot_results(dop, name="spot_y1bs", loss=loss, cho_y1=cho_y1, cho_s=cho_s)

### 2021-08-12 figures/twospec.py

@@ -1,0 +1,535 @@
+"""
+Show that we can solve the Doppler imaging problem
+when the stellar spectrum is a linear combination
+of two different "eigenspectra".
+
+Specifically, there is one spectral component (s0) that
+is present everywhere at the same intensity, and one
+component (s1) whose weight varies spatially with the
+spot. This has the effect of causing the spot to have
+one spectrum and the rest of the star to have a
+different one.
+
+"""
+import paparazzi as pp
+import numpy as np
+import matplotlib.pyplot as plt
+import starry
+from scipy.linalg import cho_factor, cho_solve
+from scipy.linalg import block_diag as dense_block_diag
+from scipy.sparse import block_diag as sparse_block_diag
+from scipy.sparse import diags
+import theano
+import theano.tensor as tt
+import theano.sparse as ts
+from tqdm import tqdm
+from inspect import getmro
+import celerite
+from matplotlib.patches import Rectangle
+
+
+def is_theano(*objs):
+    """
+    Return ``True`` if any of ``objs`` is a ``Theano`` object.
+
+    """
+    for obj in objs:
+        for c in getmro(type(obj)):
+            if c is theano.gof.graph.Node:
+                return True
+    return False
+
+
+# Initialize some stuff. We'll instantiate a ``Doppler``
+# object so we can use its properties (mostly the convolution
+# kernels & Doppler design matrix) later on. We're going
+# to re-generate the data below, but we call ``generate_data``
+# to force computation of the various things we'll need.
+np.random.seed(13)
+ferr = 1.0e-4
+res = 300
+dop = pp.Doppler(ydeg=15, u=[0.5, 0.25])
+dop.generate_data(ferr=ferr)
+D = dop.D()
+kT = dop.kT()
+theta = dop.theta
+K = dop.K
+Kp = dop.Kp
+W = dop.W
+N = dop.N
+M = dop.M
+lnlam = dop.lnlam
+lnlam_padded = dop.lnlam_padded
[…]

### 2021-08-12 figures/utils/spot.py

@@ -1,0 +1,373 @@
+import paparazzi as pp
+import numpy as np
+import matplotlib.pyplot as plt
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+import starry
+import subprocess
+from scipy.linalg import cho_solve
+import theano.tensor as tt
+import theano.sparse as ts
+
+__all__ = ["plot_results"]
+
+
+def plot_results(
+    doppler,
+    loss=[],
+    cho_y1=None,
+    cho_s=None,
+    name="vogtstar",
+    nframes=None,
+    render_movies=False,
+    open_plots=False,
+    overlap=2.0,
+    res=300,
+):
+    """
+    Plot the results of the Doppler imaging problem for the SPOT star.
+
+    """
+    # Get the values we'll need for plotting
+    ydeg = doppler.ydeg
+    udeg = doppler._udeg
+    u = doppler.u
+    theta = doppler.theta
+    y1_true = doppler.y1_true
+    s_true = doppler.s_true
+    s_deconv = doppler.s_deconv
+    baseline_true = doppler.baseline_true
+    y1 = np.array(doppler.y1)
+    s = np.array(doppler.s)
+    baseline = doppler.baseline().reshape(-1)
+    model = doppler.model()
+    F = doppler.F
+    lnlam = doppler.lnlam
+    lnlam_padded = doppler.lnlam_padded
+    M = doppler.M
+    inc = doppler.inc
+
+    # List of figure files we're generating
+    files = []
+
+    # Plot the baseline
+    # HACK: Append the first measurement to the last to get
+    # a plot going from -180 to 180 (endpoints included)
+    theta_ = np.append(theta, [180.0])
+    baseline_true_ = np.append(baseline_true, [baseline_true[0]])
+    baseline_ = np.append(baseline, [baseline[0]])
+    fig, ax = plt.subplots(1, figsize=(8, 5))
+    ax.plot(theta_, baseline_true_, label="true")
+    ax.plot(theta_, baseline_, label="inferred")
+    if cho_y1 is not None:
+        U = np.triu(cho_y1[0])
+        B = doppler._map.design_matrix(theta=doppler.theta).eval()[:, 1:]
+        A = np.linalg.solve(U.T, B.T)
+        baseline_sig = np.sqrt(np.sum(A ** 2, axis=0))
+        baseline_sig_ = np.append(baseline_sig, [baseline_sig[0]])
[…]

### 2021-08-12 paparazzi/doppler.py

@@ -1,1055 +1,0 @@
-# -*- coding: utf-8 -*-
-import numpy as np
-import starry
-from scipy.sparse import csr_matrix, hstack, vstack, diags
-from scipy.sparse import block_diag as sparse_block_diag
-from scipy.linalg import block_diag as dense_block_diag
-from scipy.linalg import cho_factor, cho_solve
-import celerite
-import theano
-import theano.tensor as tt
-import theano.sparse as ts
-from tqdm import tqdm
-import os
-from .utils import Adam, NAdam
-
-CLIGHT = 3.0e5
-
-
-__all__ = ["Doppler"]
-
-
-class Doppler(object):
-    """
-    Doppler imaging solver class.
-
-    Args:
-        ydeg (int, optional): Spherical harmonic degree. Defaults to 15.
-        vsini (int, optional): Projected equatorial velocity in km/s. 
-            Defaults to 40.
-        inc (float, optional): Inclination in degrees. Defaults to 40.0.
-        u (ndarray, optional): Limb darkening coefficients. Defaults to ``[]``.
-        y1_mu (float or ndarray, optional): Prior mean on the spherical 
-            harmonic coefficients. Defaults to 0.0.
-        y1_sig (float or ndarray, optional): Prior standard deviation on 
-            the spherical harmonic coefficients. Defaults to 0.01.
-        s_mu (float or ndarray, optional): Prior mean on the spectrum. 
-            Defaults to 1.0.
-        s_sig (float, optional): Prior standard deviation on
-            the spectrum. Defaults to 0.3.
-        s_rho (float, optional): Prior lengthscale on the Gaussian Process
-            prior on the spectrum. Set to zero to disable the GP.
-            Defaults to 3.e-5.
-        baseline_mu (float or ndarray, optional): Prior mean on the 
-            baseline. Defaults to 1.0.
-        baseline_sig (float or ndarray, optional): Prior standard 
-            deviation on the baseline. Defaults to 0.1.
-    """
-
-    def __init__(
-        self,
-        ydeg=15,
-        vsini=40,
-        inc=40.0,
-        u=[],
-        y1_mu=0.0,
-        y1_sig=0.01,
-        s_mu=1.0,
-        s_sig=0.3,
-        s_rho=3.0e-5,
-        baseline_mu=1.0,
-        baseline_sig=0.1,
-    ):
-        # Stellar params
-        self._udeg = len(u)
-        self.ydeg = ydeg
-        self.inc = inc
-        self.vsini = vsini
-        self.u = u
-
[…]

### 2021-08-12 scratch/old/vogstar_hmc.py

@@ -1,258 +1,0 @@
-# -*- coding: utf-8 -*-
-import matplotlib.pyplot as plt
-import numpy as np
-import starry
-from utils import RigidRotationSolver
-from tqdm import tqdm
-import exoplanet as xo
-from scipy.sparse import block_diag, diags
-import theano.tensor as tt
-import theano.sparse as ts
-import pymc3 as pm
-import os
-np.random.seed(13)
-
-
-# The save file
-filename = "output/vogtstar_new"
-clobber = False
-
-# Run?
-if (clobber) or (not os.path.exists("%s.npz" % filename)):
-
-    # Params
-    params = dict(
-        ydeg = 14,
-        niter = 200,
-        lam_max = 2e-5,
-        K = 399,                    # Number of wavs observed
-        inc = 60.0,
-        beta = 2.e-6,
-        line_sigma = 2.e-7,
-        P = 1.0,
-        ferr = 1.0e-4,
-        sig_vT = 0.3,
-        sig_u = 0.01,
-        sig_u0 = 1e-5,
-        M = 11,                      # Number of observations
-        ntheta = 12                  # Number of images to display
-    )
-    locals().update(params)
-
-    # Instantiate a map
-    N = (ydeg + 1) ** 2
-    map = starry.Map(ydeg, lazy=False)
-    map.inc = inc
-    map.load("vogtstar.jpg")
-    ylms = np.array(map.y)
-    img = map.render(theta=np.linspace(-180, 180, ntheta + 1)[:-1])
-    map.show(theta=np.linspace(-180, 180, 50), mp4="%s_true.mp4" % filename)
-
-    # Log wavelength array
-    lam = np.linspace(-lam_max, lam_max, K)
-
-    # Instantiate the solver
-    solver = RigidRotationSolver(lam, ydeg=ydeg, beta=beta, inc=inc, P=P)
-
-    # Create a fake spectrum w/ a bunch of lines
-    # Note that we generate it on a *padded* wavelength grid
-    # so we can control the behavior at the edges
-    lam_padded = solver.lam_padded
-    Kp = len(lam_padded)
-    I0_padded = np.ones_like(lam_padded)
-    for i in range(30):
[…]

### 2021-08-12 scratch/vogtstar.py

@@ -1,473 +1,0 @@
-import paparazzi as pp
-import numpy as np
-import matplotlib.pyplot as plt
-from mpl_toolkits.axes_grid1 import make_axes_locatable
-import starry
-import subprocess
-from scipy.linalg import cho_solve
-import theano.sparse as ts
-
-np.random.seed(13)
-
-
-def plot_results(
-    doppler,
-    loss=[],
-    cho_u=None,
-    cho_vT=None,
-    name="vogtstar",
-    nframes=None,
-    render_movies=False,
-    open_plots=False,
-    overlap=2.0,
-    res=300,
-):
-    """
-    Plot the results of the Doppler imaging problem for the Vogtstar.
-
-    """
-    # Get the values we'll need for plotting
-    ydeg = doppler.ydeg
-    theta = doppler.theta
-    u_true = doppler.u_true
-    vT_true = doppler.vT_true
-    baseline_true = doppler.baseline_true
-    u = np.array(doppler.u)
-    vT = np.array(doppler.vT)
-    baseline = doppler.baseline().reshape(-1)
-    model = doppler.model()
-    F = doppler.F
-    lnlam = doppler.lnlam
-    lnlam_padded = doppler.lnlam_padded
-    M = doppler.M
-    inc = doppler.inc
-
-    # List of figure files we're generating
-    files = []
-
-    # Plot the baseline
-    # HACK: Append the first measurement to the last to get
-    # a plot going from -180 to 180 (endpoints included)
-    theta_ = np.append(theta, [180.0])
-    baseline_true_ = np.append(baseline_true, [baseline_true[0]])
-    baseline_ = np.append(baseline, [baseline[0]])
-    fig, ax = plt.subplots(1, figsize=(8, 5))
-    ax.plot(theta_, baseline_true_, label="true")
-    ax.plot(theta_, baseline_, label="inferred")
-    if cho_u is not None:
-        U = np.triu(cho_u[0])
-        B = doppler._map.X(theta=doppler.theta).eval()[:, 1:]
-        A = np.linalg.solve(U.T, B.T)
-        baseline_sig = np.sqrt(np.sum(A ** 2, axis=0))
-        baseline_sig_ = np.append(baseline_sig, [baseline_sig[0]])
-        ax.fill_between(
-            theta,
-            baseline - baseline_sig,
-            baseline + baseline_sig,
-            color="C1",
[…]

### 2021-08-12 tests/test_placeholder.py

@@ -1,6 +1,0 @@
-"""A placeholder file for unit tests."""
-
-
-def test_commutation():
-    """Test that math still works."""
-    assert 1 + 2 == 2 + 1

### 2021-08-12 tex/figures/ld.py

@@ -1,110 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Limb darkening operator illustration.
-
-"""
-import starry
-import matplotlib.pyplot as plt
-import numpy as np
-import theano.tensor as tt
-
-
-# Compute the limb-darkening matrix, `L`
-ydeg = 1
-udeg = 1
-u1 = 1
-L = np.array(
-    [
-        [1 - u1, 0, u1 / np.sqrt(3), 0],
-        [0, 1 - u1, 0, 0],
-        [u1 / np.sqrt(3), 0, 1 - u1, 0],
-        [0, 0, 0, 1 - u1],
-        [0, 0, 0, 0],
-        [0, u1 / np.sqrt(5), 0, 0],
-        [0, 0, (2 * u1) / np.sqrt(15), 0],
-        [0, 0, 0, u1 / np.sqrt(5)],
-        [0, 0, 0, 0],
-    ]
-) / (1 - u1 / 3)
-
-# Go under the hood with `starry` to manually render
-# the limb-darkened map. This is super hacky, sorry.
-res = 300
-map = starry.Map(ydeg + udeg)
-render = (
-    lambda y: map.ops.render(
-        res,
-        0,
-        tt.as_tensor_variable([0.0, 0.0]).astype(tt.config.floatX),
-        map._inc,
-        map._obl,
-        tt.as_tensor_variable(y).astype(tt.config.floatX),
-        map._u,
-        map._f,
-        map._alpha,
-    )[0]
-    .eval()
-    .reshape(res, res)
-)
-
-fig, ax = plt.subplots((ydeg + 1) ** 2, 2, figsize=(8, 8))
-fig.subplots_adjust(wspace=0.75)
-for axis in ax.flatten():
-    axis.spines["top"].set_visible(False)
-    axis.spines["right"].set_visible(False)
-    axis.spines["bottom"].set_visible(False)
-    axis.spines["left"].set_visible(False)
-    axis.set_xticks([])
-    axis.set_yticks([])
-
-# Plot the transformation of each Ylm
-n = 0
-for l in range(ydeg + 1):
-    for m in range(-l, l + 1):
-
-        y = np.zeros((ydeg + udeg + 1) ** 2)
-        y[n] = 1.0
[…]

### 2021-08-12 tex/figures/spot_y1.py

@@ -1,41 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Solve the SPOT problem.
-
-In this case, we know the spectrum and the baseline
-perfectly. The problem is linear in the map, so solving
-the Doppler problem is easy!
-
-"""
-import paparazzi as pp
-import numpy as np
-from utils.spot import plot_results
-
-np.random.seed(13)
-
-# Let's plot the high SNR case for the paper
-high_snr = True
-
-# High or low SNR?
-if high_snr:
-    ferr = 1e-4
-else:
-    ferr = 1e-3
-
-# Generate data at high SNR
-dop = pp.Doppler(ydeg=15, u=[0.5, 0.25])
-dop.generate_data(ferr=ferr)
-
-# Compute the true baseline (assumed to be known exactly)
-dop.y1 = dop.y1_true
-baseline = dop.baseline()
-
-# Reset all coefficients
-dop.s = dop.s_true
-dop.y1 = None
-
-# Solve!
-loss, cho_y1, cho_s = dop.solve(s=dop.s, baseline=baseline)
-
-# Plot the results
-plot_results(dop, name="spot_y1", loss=loss, cho_y1=cho_y1, cho_s=cho_s)

### 2021-08-12 tex/figures/spot_y1b.py

@@ -1,50 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Solve the SPOT problem.
-
-In this case, we know the rest frame spectrum, but we don't
-know the map coefficients or the baseline flux. The problem
-can be linearized to solve for the coefficients, and then
-refined with the non-linear solver.
-
-"""
-import paparazzi as pp
-import numpy as np
-from utils.spot import plot_results
-
-np.random.seed(13)
-
-# Let's plot the high SNR case for the paper
-high_snr = True
-
-# High or low SNR?
-if high_snr:
-    # At high SNR, we need to do a bit of refinement
-    # with the non-linear solver.
-    ferr = 1e-4
-    niter = 80
-    lr = 1e-4
-    T = 100.0
-    dlogT = -0.25
-else:
-    # At low SNR, a single run of the bi-linear solver
-    # gets us to the optimum!
-    ferr = 1e-3
-    niter = 0
-    lr = None
-    T = 1.0
-    dlogT = -0.25
-
-# Generate data
-dop = pp.Doppler(ydeg=15, u=[0.5, 0.25])
-dop.generate_data(ferr=ferr)
-
-# Reset all coefficients
-dop.s = dop.s_true
-dop.y1 = None
-
-# Solve!
-loss, cho_y1, cho_s = dop.solve(s=dop.s, niter=niter, lr=lr, T=T, dlogT=dlogT)
-
-# Plot the results
-plot_results(dop, name="spot_y1b", loss=loss, cho_y1=cho_y1, cho_s=cho_s)

### 2021-08-12 tex/figures/twospec.py

@@ -1,535 +1,0 @@
-"""
-Show that we can solve the Doppler imaging problem
-when the stellar spectrum is a linear combination
-of two different "eigenspectra".
-
-Specifically, there is one spectral component (s0) that
-is present everywhere at the same intensity, and one
-component (s1) whose weight varies spatially with the
-spot. This has the effect of causing the spot to have
-one spectrum and the rest of the star to have a
-different one.
-
-"""
-import paparazzi as pp
-import numpy as np
-import matplotlib.pyplot as plt
-import starry
-from scipy.linalg import cho_factor, cho_solve
-from scipy.linalg import block_diag as dense_block_diag
-from scipy.sparse import block_diag as sparse_block_diag
-from scipy.sparse import diags
-import theano
-import theano.tensor as tt
-import theano.sparse as ts
-from tqdm import tqdm
-from inspect import getmro
-import celerite
-from matplotlib.patches import Rectangle
-
-
-def is_theano(*objs):
-    """
-    Return ``True`` if any of ``objs`` is a ``Theano`` object.
-
-    """
-    for obj in objs:
-        for c in getmro(type(obj)):
-            if c is theano.gof.graph.Node:
-                return True
-    return False
-
-
-# Initialize some stuff. We'll instantiate a ``Doppler``
-# object so we can use its properties (mostly the convolution
-# kernels & Doppler design matrix) later on. We're going
-# to re-generate the data below, but we call ``generate_data``
-# to force computation of the various things we'll need.
-np.random.seed(13)
-ferr = 1.0e-4
-res = 300
-dop = pp.Doppler(ydeg=15, u=[0.5, 0.25])
-dop.generate_data(ferr=ferr)
-D = dop.D()
-kT = dop.kT()
-theta = dop.theta
-K = dop.K
-Kp = dop.Kp
-W = dop.W
-N = dop.N
-M = dop.M
-lnlam = dop.lnlam
-lnlam_padded = dop.lnlam_padded
[…]

### 2021-08-12 tex/gen_links.py

@@ -1,44 +1,0 @@
-from __future__ import print_function
-import subprocess
-import os
-import glob
-import time
-import re
-
-# Generate the github links
-hash = subprocess.check_output(["git", "rev-parse", "HEAD"]).decode("utf-8")[
-    :-1
-]
-slug = os.getenv("TRAVIS_REPO_SLUG", "user/repo")
-with open("gitlinks.tex", "w") as f:
-    print(
-        r"\newcommand{\codelink}[1]{\href{https://github.com/%s/blob/%s/tex/figures/#1.py}{\codeicon}\,\,}"
-        % (slug, hash),
-        file=f,
-    )
-    print(
-        r"\newcommand{\animlink}[1]{\href{https://github.com/%s/blob/%s/tex/figures/#1.gif}{\animicon}\,\,}"
-        % (slug, hash),
-        file=f,
-    )
-    print(
-        r"\newcommand{\prooflink}[1]{\href{https://github.com/%s/blob/%s/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}"
-        % (slug, hash),
-        file=f,
-    )
-    print(
-        r"\newcommand{\cilink}[1]{\href{https://dev.azure.com/%s/_build}{#1}}"
-        % (slug),
-        file=f,
-    )
-
-# Tally up the total figure runtime
-files = glob.glob("figures/*.figtime")
-seconds = 0
-for file in files:
-    with open(file, "r") as f:
-        line = f.readline()
-    m, s = re.match("([0-9]*?)m([0-9]*?)s", line).groups()
-    seconds += 60 * int(m) + int(s)
-with open("figures/allfigures.figtime", "w") as f:
-    print(time.strftime("%Mm%Ss", time.gmtime(seconds)), file=f)

### 2021-08-16 tex/ms.tex
slowly getting there

@@
+% Replace "([a-z$,])\n(\s*)([$\(a-z])" with "$1 $3"
+% Replace "\.\s([a-z])" with ". \n$1"
 % Define document class & import showyourwork
 \documentclass[modern]{aastex631}
+
+\include{style}
 
@@
 
+\section{The problem}
+\label{sec:the_problem}
+%
+Let $I(\lnlam, \x, t, \Dargs)$ be the specific intensity observed at log wavelength $\lnlam \equiv \ln\frac{\lambda}{\lambda_\mathrm{r}}$ and at sky-projected Cartesian position $\x = (x, y, z)$ on the surface of the star at time $t$, where $\Dargs$ is a set of arbitrary parameters of the Doppler field and $\lambda_\mathrm{r}$ is a reference wavelength.
+We may express this intensity as
+%
+\begin{align}
+    \label{eq:the_problem:Ixi}
+    I(\lnlam, \x, t, \Dargs) & =
+    I\Big(\lnlam_0 + \D(\x, \Dargs), \x, t\Big)
+\end{align}
+%
+where $\lnlam_0$ is the log wavelength in the rest frame and $\D$ is the Doppler shift in log wavelength space:
+%
+\begin{align}
+    \label{eq:the_problem:D}
+    \D(\x, \Dargs)
+     & =
+    \frac{1}{2}\ln\left(
+    \frac{1 + \beta(\x, \Dargs)}{1 - \beta(\x,
+            \Dargs)}
+    \right)
+\end{align}
+%
+where $\beta = v(\x, \Dargs) / c$ is the ratio of the radial velocity at a point on the surface of the star to the speed of light.
+In keeping with the literature, we take positive values of $v$ (and $\D$) to mean redshifts.
+
+A common approach to computing the Doppler-shifted spectrum is to evaluate the spectrum at the rest frame wavelength $\lnlam_0$ and interpolate back to the grid in $\lnlam$. 
+This is practical when computing the spectrum at a single \emph{point} on the surface, but not ideal when one is interested in the \emph{integral} over the visible surface of the star $\Surf$, which is typically all we can observe:
+%
+\begin{align}
+    \label{eq:the_problem:F}
+    F(\lnlam, t, \Dargs)
+     & \equiv
+    \iint\limits_{\Surf(\x)}
+    I(\lnlam, \x, t, \Dargs)
+    \mathrm{d}{\Surf(\x)}
+    \quad ,
+\end{align}
+%
+The difficulty in solving Equation~(\ref{eq:the_problem:F}) stems from the fact that $I(\lnlam, \x, t, \Dargs)$ is difficult to write down in closed form, given the nonlinearity of the Doppler shift.
+The standard approach to solving this integral is therefore to discretize the surface of the star with a fine grid, evaluate the Doppler-shifted spectrum in each cell, and sum over the spatial axes to approximate the integral.
+Depending on the resolution of the grid, this is either numerically inaccurate or computationally inefficient (and often both).
+
+\section{The Solution}
+\label{sec:the_solution}
+
+\subsection{Doppler Deconvolution}
+
+The observed spectrum is a complex function of spatial, spectral, temporal, and velocity terms. 
+The goal in this section is to deconvolve each of these terms to make solving the integral in Equation~(\ref{eq:the_problem:F}) easier.
+%
+The first thing we will do is to express Equation~(\ref{eq:the_problem:Ixi})
+as a convolution:
+%
+\begin{align}
+    \label{eq:deconv:convolution}
+    I(\lnlam, \x, t, \Dargs) & =
+    I(\lnlam_0, \x, t)
+    *
+    \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
+\end{align}
+%
+where $\delta$ is the Dirac delta function and $*$ denotes the linear convolution operator, defined for two arbitrary functions $g$ and $h$ as the integral
+%
+\begin{align}
+    \label{eq:deconv:convolution_def}
+    (g * h)(t) \equiv \int_{-\infty}^\infty g(\tau) h(t - \tau) d\tau
+\end{align}
+%
+for some independent coordinate $t$ and dummy parameter $\tau$.
+%
+The convolution of $I(\lnlam_0)$ with a delta function has the effect of shifting the spectrum by an amount $\D$, returning a function of the shifted (observed) log wavelength, $\lnlam = \lnlam_0 + \D$.
+
+Next, we expand the spatial dependence of the specific intensity at the rest frame wavelength in terms of spherical harmonics on the unit disk:
+%
+\begin{align}
+    \label{eq:deconv:Ixi0}
+    I(\lnlam_0, \x, t)
+     & =
+    \sum_{l=0}^{l_\mathrm{max}}\sum_{m=-l}^{l} a_{lm}(\lnlam_0, t) Y_{lm}(\x)
+    \quad ,
+\end{align}
+%
+where $Y_{lm}(\x)$ is a spherical harmonic on the projected disk and $a_{lm}(\lnlam_0, t)$ is the corresponding spherical harmonic coefficient at log wavelength in the rest frame $\lnlam_0$ and time $t$.
+For convenience, we may write this equation in vector form:
+%
+\begin{align}
+    \label{eq:deconv:Ivec}
+    I(\lnlam_0, \x, t) & =
+    \ylmbasis(\x) \,
+    \alm(\lnlam_0, t)
+    \quad ,
+\end{align}
+%
+where
+%
+\begin{align}
+    \label{eq:deconv:alm}
+    \alm(\lnlam_0, t) \equiv
+    \Big(
+    a_{0,0}(\lnlam_0, t) \quad 
+    a_{1,-1}(\lnlam_0, t) \quad 
+    a_{1,0}(\lnlam_0, t) \quad 
+    a_{1,1}(\lnlam_0, t) \quad
+    ...
+    \Big)^\top
+\end{align}
+%
+is the vector of $N = (l_\mathrm{max} + 1)^2$ spherical harmonic coefficients and
+%
+\begin{align}
+    \label{eq:deconv:ylmbasis}
+    \ylmbasis(\x) \equiv
+    \Big(
+    Y_{0,0}(\x) \quad 
+    Y_{1,-1}(\x) \quad 
+    Y_{1,0}(\x) \quad 
+    Y_{1,1}(\x) \quad
+    ...
+    \Big)
+\end{align}
+%
+is the corresponding vector of $N$ spherical harmonics. 
+We may further decompose our expression by linearizing the time dependence of the spherical harmonic coefficients:
+%
+\begin{align}
+    \label{eq:deconv:R}
+    \alm(\lnlam_0, t) = \R(t) \, \azero(\lnlam_0)
+    \quad ,
+\end{align}
+%
+where $\azero(\lnlam_0) = \bvec{a}(\lnlam_0, t=t_0)$ for some reference time $t_0$.
+For rigid body rotation, the result is exact and $\R(t)$ is the $(N \times N)$ Wigner rotation matrix for real spherical harmonics
+\citep[e.g.][]{AlvarezCollado1989}, which is implicitly a function of the inclination, obliquity, and rotation period of the star.
+%In the case that other processes such as differential rotation or spot 
+%evolution are significant
+%over the course of an observation, Equation~(\ref{eq:deconv:R}) can be
+%made to hold approximately for some effective rotation matrix 
+%$\R(t)$; we discuss this later.
+
+The equation for the specific intensity in the rest frame now reads
+%
+\begin{align}
+    \label{eq:deconv:Ivecfull}
+    I(\lnlam_0, \x, t) & =
+    \ylmbasis(\x)
+    \,
+    \R(t)
+    \,
+    \azero(\lnlam_0)
+    \quad ,
+\end{align}
+%
+where it is clear that we have fully separated the spatial, temporal, and spectral terms. 
+Inserting this into Equation~(\ref{eq:deconv:convolution})
+and integrating over the visible portion of the star, we arrive at the expression for the observed spectrum:
+%
+%
+\begin{align}
+    \label{eq:deconv:F2d}
+    F(\lnlam, t, \Dargs) & =
+    \iint\limits_{\Surf(\x)}
+    \ylmbasis(\x)
+    \,
+    \R(t)
+    \,
+    \alm(\lnlam_0)
+    * \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
+    \mathrm{d}\Surf(\x)
+    \nonumber                \\[0.5em]
+                         & =
+    \iint\limits_{\Surf(\x)}
+    \ylmbasis(\x)
+    \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
+    \mathrm{d}\Surf(\x)
+    \,
+    \R(t)
+    \,
+    *
+    \,
+    \azero(\lnlam_0)
+    \quad ,
+\end{align}
+%
+%
+where we made use of the commutativity of the convolution operator and the fact that the integral is taken only over the spatial dimensions.
+Note, importantly, that the convolution operation above is implicitly a vector operation---i.e., the convolution is taken for each spherical harmonic term individually and then summed over all terms.
+
+Finally, we can simplify Equation~(\ref{eq:deconv:F2d}) by noting that the delta function in the integrand allows us to reduce the double integral to a line integral:
+%
+\begin{align}
+    \label{eq:deconv:kT}
+    \iint\limits_{\Surf(\x)}
+    \ylmbasis(\x)
+    \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
+    \mathrm{d}\Surf(\x)
+    \, \,
+     & =
+    \int\limits_{\Curve(\lnlam, \x, \Dargs)}
+    \hspace*{-0.6em}\ylmbasis(\x)
+    \mathrm{d}\Curve(\lnlam, \x, \Dargs)
+    \nonumber                     \\[0.5em]
+     & \equiv \kT(\lnlam, \Dargs)
+    \quad.
+\end{align}
+%
+where the path $\Curve(\lnlam, \x, \Dargs)$ corresponds to the set of all points on the visible disk where $\lnlam_0 + \D(\x, \Dargs) = 0$.
+%
+We thus have
+%
+\begin{align}
+    \label{eq:deconv:F}
+    F(\lnlam, t, \Dargs)
+     & =
+    \kT(\lnlam, \Dargs) \, \R(t)
+    *
+    \azero(\lnlam_0)
+    \quad.
+\end{align}
+%
+Equation~(\ref{eq:deconv:F}) is the deconvolution of the observed spectrum into velocity terms, temporal terms, and spectral/spatial terms, respectively. 
+In the next section, we will discuss how to efficiently solve the line integral in Equation~(\ref{eq:deconv:kT}).
+
+\subsection{Computing the kernel $\kT$}
+\label{sec:kT}
+%
+In the case that the star's rotation is rigid (i.e., differential rotation is negligible) and other effects such as convective blueshift may be ignored, the radial velocity at any point on the surface is simply proportional to the distance to the axis of rotation.
+Without loss of generality, if we assume the axis of rotation lies along the $y-z$ plane, we have
+%
+\begin{align}
+    \label{eq:kT:beta}
+    \beta(\x, \Dargs) = \frac{\omega \sin i \, x}{c}
+\end{align}
+%
+and
+%
+\begin{align}
+    \label{eq:kT:D}
+    \D(\x, \Dargs) & =
+    \frac{1}{2}\ln\left(
+    \dfrac{1 + \dfrac{\omega \sin i \, x}{c}}
+    {1 - \dfrac{\omega \sin i \, x}{c}}
+    \right)
+    \quad ,
+\end{align}
+%
+where the parameters $\Dargs$ of the Doppler field are the angular velocity, $\omega$, and the inclination of the star with respect to $\hat{y}$, $i$.
+
+\begin{figure}[t!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{kT.pdf}
+        \caption{%
+            The Doppler $\kT$ basis for a rigidly rotating star computed from Equation~(\ref{eq:kT:kT}) and Equation~(\ref{eq:kT:sTrecurrence}) up to spherical harmonic degree $l_\mathrm{max}=10$. 
+            Rows correspond to the degree $l$ and columns correspond to the order $m$. 
+            These functions encode the contribution of each spherical harmonic to the rotational broadening of features in the stellar spectrum. 
+            Because the rotational axis is chosen to be aligned with $\hat{y}$, none of the $m < 0$ harmonics contribute to the observed spectrum.
+        }
+        \label{fig:kT}
+    \end{centering}
+\end{figure}
+
+If we assume the star is unocculted, the region of integration $\Surf(\x)$ in Equation~(\ref{eq:deconv:kT}) is simply the unit disk, so $\Curve(\lnlam, \x, \Dargs)$ is the set of all points that satisfy both $\lnlam_0 + \D(\x, \Dargs) = 0$ and $x^2 + y^2 \le 1$.
+Solving Equation~(\ref{eq:kT:D}) for $x$, we find that the curves $\Curve(\lnlam, \x, \Dargs)$ are simply vertical lines on the unit disk given by
+%
+\begin{align}
+    x & =
+    \Bigg(\frac{c}{\omega\sin i}\Bigg)
+    \Bigg(\frac{\mathrm{e}^{-2{\lnlam_0}} - 1}
+    {\mathrm{e}^{-2{\lnlam_0}} + 1}\Bigg)
+    \quad .
+\end{align}
+%
+The integral in Equation~(\ref{eq:deconv:kT}) is therefore just the line integral of the spherical harmonic basis over $y$:
+%
+\begin{align}
+    \label{eq:kT:kT}
+    \kT(\lnlam, \Dargs)
+     & =
+    \int\limits_{-\sqrt{1 - x^2}}^
+    {\sqrt{1 - x^2}}
+    \ylmbasis
+    \Big(x, y\Big)
+    \mathrm{d}y
+    \quad .
+\end{align}
+%
+In the Appendix we derive an analytic solution to this integral and show how to recursively solve it for all terms in the spherical harmonic basis.
+Figure~\ref{fig:kT} shows the $\kT$ basis computed from the formulae above and Equation~(\ref{eq:kT:kT}) up to spherical harmonic degree $l_\mathrm{max}=10$.
+
+This completes our derivation of the analytic expression for the observed spectrum (Equation~\ref{eq:deconv:F}).
+
+\subsection{Example}
+%
+Figure~\ref{fig:spot} shows an example application of the formulae derived in this section. 
+We used \starry to generate a synthetic stellar surface with a single large Gaussian spot at a latitude of $30^\circ$, yielding a vector of spherical harmonic coefficients $\bvec{y}$.
+The stellar rest frame spectrum $I(\lnlam_0)$ is taken to be a single Gaussian absorption line that is spatially constant everywhere save for a multiplicative factor equal to the local spot intensity.
+This corresponds to a spectral/spatial expansion vector $\azero(\lnlam_0)$ whose coefficient at degree $l$ and order $m$ is equal to $y_{lm} I(\lnlam_0)$.
+In the Figure, we rotated the star about an axis perpendicular to the line of sight (left panel) and computed the observed spectrum using Equation~(\ref{eq:deconv:F}) (center panel). 
+The right panel shows the difference between the observed spectrum and the spectrum when the spot is not in view.
+The effect of the spot on the absorption line is evident: a ``bump'' that travels from the blueshifted side of to the redshifted side of the line in sync with the change in longitude of the spot. 
+This correspondence between line shape residuals and spot location is the cornerstone of the Doppler imaging technique \citep[compare to, e.g., Figures 1 and 4 in][]{Vogt1983}.
+
+\begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=0.6\linewidth]{spot.pdf}
+        \caption{%
+            Time evolution of a Gaussian absorption line on a rigidly rotating, spotted star computed from the analytic formulae in \S\ref{sec:kT}.
+            The stellar surface is modeled as a spherical harmonic expansion up to $l_\mathrm{max}=20$, and the line shape is assumed to be the same everywhere;
+            the spot simply downweights the local intensity at all wavelengths.
+            As the spot rotates into view (left panel), the line shape changes slightly (center panel). 
+            The residuals between the line when the spot is in view (solid) and when it is on the backside of the star (dotted) are shown in the right panel, where a Gaussian-like feature can be seen tracking the spot as it rotates from the blueshifted hemisphere to the redshifted hemisphere of the star.
+        }
+        \label{fig:spot}
+    \end{centering}
+\end{figure}
+
+Figure~\ref{fig:compare} shows one of the spectra in Figure~\ref{fig:spot}, this time computed using both our formulae (blue line) and the traditional technique of discretizing the stellar surface, Doppler-shifting the spectrum in each grid cell according to the local radial velocity, interpolating back to a uniform wavelength grid, and summing over the spatial dimension (dotted orange line).
+We show the residuals in the lower panel, where it is clear that as the number of grid cells increases from 2,000 (light grey) to 71,000 (dark grey), the numerical solution approaches the solution obtained using our approach.
+
+%Understand---and comment on---the fundamental
+%differences between a discrete linear convolution and traditional linear 
+%interpolation. Should we expect the numerical solution to actually \emph{converge}
+%to the \starry solution, or is the way the two are interpolating fundamentally
+%different?
+
+\begin{figure}[t!]
+    \begin{centering}
+        \includegraphics[width=0.65\linewidth]{compare.pdf}
+        \caption{%
+            The observed spectrum when the spot is in view computed with
+            \starry (blue) and numerically (orange). 
+            The problem setup is the same as that in Figure~\ref{fig:spot}. 
+            The bottom panel shows the absolute value of the difference between the two spectra for different number of grid points in the numerical solution.
+            As the number of grid points increases, the numerical solution approaches the \starry solution.
+        }
+        \label{fig:compare}
+    \end{centering}
+\end{figure}
+
 \end{document}

### 2021-08-17 tex/ms.tex
more text

@@
 %
-\author{David W. Hogg}
+\author{David W. 
+Hogg}
 \affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
@@
 %differences between a discrete linear convolution and traditional linear 
-%interpolation. Should we expect the numerical solution to actually \emph{converge}
+%interpolation. 
+Should we expect the numerical solution to actually \emph{converge}
 %to the \starry solution, or is the way the two are interpolating fundamentally
@@
             The problem setup is the same as that in Figure~\ref{fig:spot}. 
-            The bottom panel shows the absolute value of the difference between the two spectra for different number of grid points in the numerical solution.
+            The boottom panel shows the absolute value of the difference between the two spectra for different number of grid points in the numerical solution.
             As the number of grid points increases, the numerical solution approaches the \starry solution.
@@
 
+\section{Linearization}
+\label{sec:linear}
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=0.8\linewidth]{linalg.pdf}
+        \caption{%
+            The Doppler design matrix $\Doppler$ (Equation~\ref{eq:linear:f}), constructed from a grid of Toeplitz matrices, each of shape $K \times K'$, where $K$ is the number of wavelength bins in the observed spectrum and $K' = K + W - 1$ is the number of bins in the model spectrum, where $W$ is the width of the convolution kernel.
+            The $N$ columns of $\Doppler$ correspond to the Toeplitz matrices for each of the $N$ spherical harmonics (shown at the top);
+            the $M$ rows correspond to the Toeplitz matrices rotated to each of the $M$ stellar phases observed (indicated graphically to the left of $\Doppler$).
+        }
+        \label{fig:linalg}
+    \end{centering}
+\end{figure}
+
+Although the convolution operator (Equation~\ref{eq:deconv:convolution_def})
+is defined for continuous functions, the problem of Doppler imaging deals with discrete measurements of a spectrum in bins of log wavelength. 
+Provided our wavelength grid is fine enough, we may therefore approximate Equation~(\ref{eq:deconv:convolution_def}) with a discrete convolution.
+For discrete arrays $\bvec{g}$ and $\bvec{h}$, we have
+%
+\begin{align}
+    \label{eq:linear:convolution_def}
+    \bvec{g} * \bvec{h} = \bvec{T(g)} \, \bvec{h}
+\end{align}
+%
+where $\bvec{T}$ is a Toeplitz matrix, a matrix whose diagonals are constant from top left to bottom right. 
+In this case, the diagonals are constructed from the values of $\bvec{g}$. 
+If $\bvec{g}$ has length $L$, element $g_n$ is placed everywhere along the $k^\mathrm{th}$ diagonal of $\bvec{T}$ for $k = -L / 2 + n$; all other entries of $\bvec{T}$ are set to zero. 
+Note that the matrix $\bvec{T}$ need not be square; in fact, for our purposes, it is a $(K \times K')$ matrix, where $K$ is the size of the observed wavelength grid and $K' = K + W - 1$ is the size of the wavelength grid in the rest frame, where $W$ is the width of the convolution kernel.
+
+Given this formulation, we may re-write Equation~(\ref{eq:deconv:F}) as a purely linear operation on $\azero(\lnlam_0)$:
+%
+\begin{align}
+    \label{eq:linear:ft}
+    \bvec{f}_m
+     & =
+    \Doppler_m
+    \,
+    \azero
+    \quad,
+\end{align}
+%
+where $\Doppler_m$ is a $(K \times N K')$ matrix constructed by horizontally concatenating the Toeplitz matrices for each of the $N$ components of the convolution kernel $\kT(\lnlam, \Dargs)$ transformed by the rotation matrix $\bvec{R}(t)$ evaluated at time $t = t_m$:
+%
+\begin{align}
+    \label{eq:linear:Dm}
+    \Doppler_m =
+    \begin{pmatrix}
+        \quad
+        \bvec{T}(\kT_0)
+        \quad
+         &
+        \quad
+        \bvec{T}(\kT_1)
+        \quad
+         &
+        \quad
+        \cdots
+        \quad
+         &
+        \quad
+        \bvec{T}(\kT_N)
+        \quad
+    \end{pmatrix}
+    (\bvec{R}(t_m) \otimes \bvec{I}_{K'})
+    \quad.
+\end{align}
+%
+where $\bvec{I}_{K'}$ is the $(K' \times K')$ identity matrix and $\otimes$ denotes the Kronecker product.
+%
+The $(K \times 1)$ vector $\mathbf{f}_m$ is the model for the flux observed at each wavelength at time $t = t_m$, and the $(N K' \times 1)$ vector $\azero$ is the vector representation of the spatially-dependent spectrum of the star.
+The latter is constructed by flattening the spherical harmonic expansion of the star such that the first $K'$ terms in $\azero$ correspond to the the values of $(a_0)_{0,0}$ at each wavelength $\lnlam_0$, followed by the values of $(a_0)_{1,-1}$ at each wavelength, and so forth.
+
+In general, our data will consist of observations made at several epochs, corresponding to different rotational phases of the star.
+If we concatenate all $M$ spectra $\bvec{f}_m$ into the $(MK \times 1)$ vector $\bvec{f}$, we may write
+%
+\begin{align}
+    \label{eq:linear:f}
+    \bvec{f}
+     & =
+    \Doppler
+    \,
+    \azero
+    \quad,
+\end{align}
+%
+where $\Doppler$ is the full $(MK \times N K')$ Doppler design matrix, constructed by vertically concatenating the individual matrices $\Doppler_m$:
+%
+%
+\begin{align}
+    \label{eq:linear:D}
+    \Doppler =
+    \begin{pmatrix}
+        \Doppler_0
+        \\
+        \Doppler_1
+        \\
+        \cdots
+        \\
+        \Doppler_m
+    \end{pmatrix}
+    \quad.
+\end{align}
+%
+%
+Equation~(\ref{eq:linear:f}) represents the full linearization of the problem, where we have expressed the quantity we can observe, $\bvec{f}$, as a linear operation on the quantity of interest, the spectral/spatial decomposition of the stellar surface, $\azero$.
+Figure~\ref{fig:linalg} shows an example of $\Doppler$.
+
+\section{The inverse problem}
+\label{sec:inverse}
+%
+In the previous section we showed how to express the data vector $\bvec{f}$, a series of spectra obtained at different epochs, as a purely linear operation on the map vector $\azero$, the spherical harmonic decomposition of the specific intensity on the surface of the star.
+The advantage of this linearity is that, given suitable priors, it allows one to compute both the maximum likelihood solution for $\azero$ and its uncertainty \emph{analytically}. 
+In particular, if one places a (multidimensional) Gaussian prior on $\azero$ with mean $\boldsymbol{\mu}_\mathbf{a_0}$ and covariance $\boldsymbol{\Lambda}_\mathbf{a_0}$, the maximum \emph{a posteriori} (MAP)
+solution for $\azero$ is
+%
+\begin{align}
+    \label{eq:inverse:ahat}
+    \bvec{\hat{a}_0} & =
+    \boldsymbol{\Sigma}_\mathbf{\hat{a}_0}
+    \left(
+    \Doppler^\top
+    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
+    \bvec{f}
+    +
+    {\boldsymbol{\Lambda}_{\azero}}^{-1} \boldsymbol{\mu}_\mathbf{a_0}
+    \right)
+    \quad,
+\end{align}
+%
+with posterior covariance given by
+%
+\begin{align}
+    \label{eq:inverse:acov}
+    \boldsymbol{\Sigma}_\mathbf{\hat{a}_0} & =
+    \left(
+    \Doppler^\top
+    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
+    \Doppler
+    +
+    {\boldsymbol{\Lambda}_{\azero}}^{-1}
+    \right)^{-1}
+    \quad,
+\end{align}
+%
+where $\boldsymbol{\Sigma}_\mathbf{f}$ is the data covariance matrix. 
+These equations require the inversion of a few fairly large matrices, but as we will see later, it allows one to obtain the map of the star ($\bvec{\hat{a}_0}$) and its uncertainty ($\boldsymbol{\Sigma}_{\mathbf{\hat{a}_0}}$) in under a second for a typical dataset.
+
+There is, however, a catch: for most practical purposes, it is difficult to find a good Gaussian prior for $\bvec{a_0}$. 
+Usually we will have some prior information on what the spectrum of the star is, and perhaps some prior information on the distribution of surface features such as starspots. 
+The problem is that even if these priors are Gaussian, the corresponding prior on $\bvec{a_0}$ is \emph{not}. 
+To understand this, consider the case where the stellar rest frame spectrum is spatially constant, save for an amplitude that is spatially variable. 
+We can then describe the rest frame spectrum by the $(K' \times 1)$ vector $\bvec{s}$ and the amplitude by the $(N \times 1)$ vector $\bvec{y}$ representing the spherical harmonic expansion of the intensity profile of the star.
+The vector $\azero$ is then given by the (flattened) outer product of the two vectors:
+%
+\begin{align}
+    \label{eq:inverse:azero}
+    \azero & = \mathrm{vec}\left( \bvec{A_0} \right) \nonumber             \\
+           & = \mathrm{vec}\left( \bvec{s} \, \bvec{y}^\top \right) \quad,
+\end{align}
+%
+where $\mathrm{vec}$ denotes the vectorization operation, which in this case transforms the $(K' \times N)$ matrix $\bvec{A_0}$ into the $(N K' \times 1)$ column vector $\azero$ by vertically stacking all of its columns.
+In other words, the vector $\azero$ consists of the set of $K'$ intensities in each wavelength bin repeated $N$ times, each time multiplied by the $n^\mathrm{th}$ spherical harmonic coefficient in the expansion of the surface intensity.
+Returning to our point about priors, note that all of the entries of $\azero$ are the product of two independent random variables. 
+Since the product of two random variables is generally non-Gaussian, even when the variables themselves are Gaussian%
+\footnote{see, e.g., \url{http://mathworld.wolfram.com/NormalProductDistribution.html}}%
+, so too is the prior on $\azero$. 
+This point makes Equation~(\ref{eq:inverse:ahat}) of little practical use, since a multivariate Gaussian will not generally be a suitable prior for $\azero$.
+
+That said, a Gaussian prior \emph{is} typically suitable for both the spectrum $\bvec{s}$ and the intensity $\bvec{y}$ (just not their product). 
+It is straightforward to show that because Equation~(\ref{eq:linear:f}) is linear in $\azero$, it is also linear in both $\bvec{s}$ and $\bvec{y}$, so MAP solutions can be found analytically for $\bvec{s}$ (conditioned on $\bvec{y}$) and $\bvec{y}$ (conditioned on $\bvec{s}$).
+We investigate these solutions below.
+
+\subsection{Solution for the map}
+\label{sec:solve_y}
+%
+For a fixed, spatially constant rest-frame spectrum $\bvec{s}$, the model for the flux vector may be written as
+%
+\begin{align}
+    \label{eq:inverse:fy}
+    \bvec{f}
+     & =
+    \Doppler
+    \,
+    \bvec{S}
+    \,
+    \bvec{y}
+    \quad,
+\end{align}
+%
+where
+%
+\begin{align}
+    \label{eq:inverse:S}
+    \bvec{S} =
+    \begin{pmatrix}
+        \quadquad\bvec{s}\quadquad &                            &                            &                            &        \\
+                                   & \quadquad\bvec{s}\quadquad &                            &                            &        \\
+                                   &                            & \quadquad\bvec{s}\quadquad &                            &        \\
+                                   &                            &                            & \quadquad\bvec{s}\quadquad &        \\
+                                   &                            &                            &                            & \ddots
+    \end{pmatrix}
+\end{align}
+%
+is a $(NK' \times N)$ block matrix constructed by repeating the column vector $\bvec{s}$ $N$ times in blocks along the main diagonal.
+Before we solve this equation for $\bvec{y}$, we note that in practice it is convenient to fix the coefficient of the $Y_{0,0}$ spherical harmonic, $y_0$, to unity. 
+After all, this coefficient is not directly constrained by the data, as it merely sets the baseline intensity on the surface of the star and is therefore formally degenerate with the stellar luminosity (which also cannot be directly inferred from the data).
+This choice further ensures a mean baseline of unity for the model vector $\mathbf{f}$. 
+We may therefore write
+%
+\begin{align}
+    \label{eq:inverse:fy1}
+    \bvec{f}
+     & =
+    \Doppler
+    \,
+    \bvec{s}_\bvec{0}
+    \,
+    +
+    \,
+    \Doppler
+    \,
+    \bvec{S_1}
+    \,
+    \bvec{y}_\bvec{1}
+    \quad,
+\end{align}
+%
+where the vector $\bvec{s_0}$ denotes the first column of $\bvec{S}$, the matrix $\bvec{S_1}$ denotes the remaining columns of $\bvec{S}$, and $\bvec{y_1}$ is the quantity we wish to solve for: the vector of spherical harmonic coefficients of degree $l \ge 1$.
+
+Given prior mean $\boldsymbol{\mu}_\bvec{y_1}$ and covariance $\boldsymbol{\Lambda}_\bvec{y_1}$ on $\bvec{y_1}$, the MAP solution is given by
+%
+\begin{align}
+    \label{eq:inverse:y1hat}
+    \bvec{\hat{y}_1} & =
+    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1}
+    \left(
+    \bvec{S_1}^\top\Doppler^\top
+    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
+    \left(\bvec{f} - \Doppler\bvec{s}_\bvec{0}\right)
+    +
+    {\boldsymbol{\Lambda}_\bvec{y_1}}^{-1} \boldsymbol{\mu}_\bvec{y_1}
+    \right)
+    \quad,
+\end{align}
+%
+with covariance
+%
+\begin{align}
+    \label{eq:inverse:y1cov}
+    \boldsymbol{\Sigma}_\bvec{\hat{y}_1} & =
+    \left(
+    \bvec{S_1}^\top\Doppler^\top
+    {\boldsymbol{\Sigma}_\bvec{f}}^{-1}
+    \Doppler\bvec{S_1}
+    +
+    {\boldsymbol{\Lambda}_\bvec{y_1}}^{-1}
+    \right)^{-1}
+    \quad.
+\end{align}
+%
+If we choose a prior with zero mean ($\boldsymbol{\mu}_\bvec{y_1} = 0$)
+and a diagonal covariance that is constant for each spherical harmonic order $m$,
+%
+\begin{align}
+    \boldsymbol{\Lambda}_\bvec{y_1} & =
+    \mathrm{diag} \left(
+    \sigma_1^2
+    \quad\quad\quad\quad
+    \sigma_1^2
+    \quad\quad\quad\quad
+    \sigma_1^2
+    \quad\quad\quad\quad
+    \sigma_2^2
+    \quad\quad\quad\quad
+    \sigma_2^2
+    \quad\quad\quad\quad
+    \sigma_2^2
+    \quad\quad\quad\quad
+    \sigma_2^2
+    \quad\quad\quad\quad
+    \sigma_2^2
+    \quad\quad\quad\quad
+    \cdots
+    \right)
+    \quad,
+\end{align}
+%
+we are in fact imposing an isotropic prior with an angular power spectrum given by $C_l = \sigma_l^2$
+\citep[e.g.,][]{Baldi2006}. 
+This is especially useful if the typical angular scale of features on the surface of the star is known or if a Gaussian prior can be placed on it.
+
+\subsection{Solution for the spectrum}
+\label{sec:solve_s}
+%
+If, on the other hand, the spatial intensity profile is known, the model for the flux vector may be written in terms of the spectrum $\bvec{s}$ as
+%
+\begin{align}
+    \label{eq:inverse:fs}
+    \bvec{f}
+     & =
+    \Doppler
+    \,
+    \bvec{Y}
+    \,
+    \bvec{s}
+    \quad,
+\end{align}
+%
+where
+%
+\begin{align}
+    \label{eq:inverse:Y}
+    \bvec{Y} =
+    \begin{pmatrix}
+        y_0\, \bvec{I}_{K'} \\
+        y_1\, \bvec{I}_{K'} \\
+        y_2\, \bvec{I}_{K'} \\
+        y_3\, \bvec{I}_{K'} \\
+        \cdots
+    \end{pmatrix}
+\end{align}
+%
+is a $(NK' \times K')$ matrix constructed by vertically stacking $N$ $(K' \times K')$ identity matrices, each multiplied by the corresponding coefficient of $\bvec{y}$. 
+Given prior mean $\boldsymbol{\mu}_\mathbf{s}$ and covariance $\boldsymbol{\Lambda}_\mathbf{s}$ on $\mathbf{s}$, the MAP solution is given by
+%
+\begin{align}
+    \label{eq:inverse:shat}
+    \bvec{\hat{s}} & =
+    \boldsymbol{\Sigma}_\mathbf{\hat{s}}
+    \left(
+    \bvec{Y}^\top\Doppler^\top
+    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
+    \bvec{f}
+    +
+    {\boldsymbol{\Lambda}_\mathbf{s}}^{-1} \boldsymbol{\mu}_\mathbf{s}
+    \right)
+    \quad,
+\end{align}
+%
+with covariance
+%
+\begin{align}
+    \label{eq:inverse:scov}
+    \boldsymbol{\Sigma}_\mathbf{\hat{s}} & =
+    \left(
+    \bvec{Y}^\top\Doppler^\top
+    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
+    \Doppler\bvec{Y}
+    +
+    {\boldsymbol{\Lambda}_\mathbf{s}}^{-1}
+    \right)^{-1}
+    \quad.
+\end{align}
+
+\subsection{The full solution}
+\label{sec:full_solve}
+%
+In the previous two sections we showed how, if the stellar rest-frame spectrum is spatially constant and known \emph{a priori} (from, say, a template spectrum), the posterior distribution for the surface map $\bvec{y}$ is \emph{analytic} (Equations~\ref{eq:inverse:y1hat} and \ref{eq:inverse:y1cov}).
+Conversely, if the surface map is known, the posterior for the spectrum is also analytic (Equations~\ref{eq:inverse:shat} and \ref{eq:inverse:scov}). 
+Both sets of solutions require Gaussian priors on the quantities of interest, but these are easily interpretable. 
+A Gaussian prior on the spherical harmonic coefficients of the surface map corresponds to the angular power spectrum of the surface features, whereas a Gaussian prior on the spectrum can be used to correctly propagate uncertainties in the stellar spectrum from observational uncertainties on the stellar metallicity, temperature, etc.
+
+Importantly, the framework developed here allows one to analytically compute not only the ``optimal'' solution to the Doppler imaging problem, but also its uncertainty. 
+The problem of re-constructing surface images of stars from spectra and/or light curves is fundamentally ill-posed because of intrinsic degeneracies and a large null space \citep[e.g.,][]{Cowan2017,Luger2019}.
+Coupled to uncertainties in the observations themselves, this makes the process of searching for the ``optimal'' solution flawed at best, and meaningless at worst. 
+Access to the full covariance matrix of the solution is therefore essential to assessing our confidence in the various features of the inferred surface maps.
+
+However, as we mentioned above, the Doppler imaging problem can be solved analytically for either the surface map or the spectrum, but not both. 
+If neither are known exactly \emph{a priori}, which is quite often the case, we can still find the MAP solution quickly by guessing at an initial spectrum $\bvec{s}$ and iterating between optimizing for $\bvec{y}$ and optimizing for $\bvec{s}$.
+This bilinear problem is not generally convex, but given a good starting point for $\bvec{s}$ and sufficient regularization on $\bvec{y}$, we find that it typically converges to the correct solution, especially after refinement with a nonlinear solver; we discuss this in detail below.
+
+Once the MAP solution has been found for both $\bvec{s}$ and $\bvec{y}$, the covariance of one conditioned on the other can be computed from the formulae above. 
+However, this is necessarily a lower bound on the true covariance of the solution, since it neglects any covariance \emph{between} $\bvec{s}$ and $\bvec{y}$. 
+To \emph{correctly} account for this, one must resort to Monte Carlo methods or other sampling techniques. 
+We discuss this further below.
+
+\section{Further considerations}
+\label{sec:bellswhistles}
+%
+Before we demonstrate our formalism in practice, we consider three modifications to our model that are often required when modeling real data. 
+Below we discuss what to do when the relative brightness of the star across different observations is unknown (\S\ref{sec:norm}), how to account for the effects of limb darkening (\S\ref{sec:ld}), and how to model stars whose local spectra differ within and outside of starspots (\S\ref{sec:eigen}).
+
+\subsection{Unknown continuum normalization}
+\label{sec:norm}
+%
+Consider the star depicted in Figure~\ref{fig:spot}. 
+When the spot is in view, absorption lines become distorted due to the suppression of either blueshifted or redshifted light. 
+However, what is not shown in the figure is the fact that overall, the star also gets \emph{dimmer}: the continuum level drops in the presence of the spot. 
+Unfortunately, spectrographs are not usually designed to measure this, since the change in the star's overall brightness from one observation to the next is often dwarfed by (unknown) changes in the spectrograph sensitivity.
+For this reason, the spectra are usually normalized to have a fixed baseline continuum, and Equation~\ref{eq:linear:f} is no longer a good model for the data.
+
+One option is to collect simultaneous photometry on the target in a band similar to the wavelength range observed, and use this light curve to (un-)normalize the spectral timeseries $\bvec{f}$. 
+However, when this is not an option, our model for $\bvec{f}$ (Equation~\ref{eq:linear:f}) must be amended.
+%
+\begin{align}
+    \label{eq:norm:f}
+    \bvec{f}
+     & =
+    \frac{
+        \Doppler
+        \,
+        \azero
+    } {
+        \bvec{b}
+    }
+    \quad,
+\end{align}
+%
+where $\bvec{b}$ is the baseline and the vector division is performed elementwise. 
+When $\azero$ is given by Equation~(\ref{eq:inverse:azero}), the baseline $\bvec{b}$ is simply the total (wavelength-integrated) flux at each epoch, repeated for every element in each spectrum.
+Based on \citet{Luger2019}, this can be computed as a purely linear operation on the spherical harmonic vector $\bvec{y}$:
+%
+\begin{align}
+    \label{eq:norm:b}
+    \bvec{b}
+     & =
+    %
+    \begin{pmatrix}
+        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_0)     \\
+        \cdots                                     \\
+        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_0)     \\
+        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_1)     \\
+        \cdots                                     \\
+        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_1)     \\
+        \cdots                                     \\
+        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_{M-1}) \\
+        \cdots                                     \\
+        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_{M-1})
+    \end{pmatrix}
+    \bvec{y}
+    %
+    \nonumber \\[0.5em]
+     & \equiv
+    \bvec{B} \, \bvec{y}
+\end{align}
+%
+where $\bvec{r}$ is given by Equation~(18) in \citet{Luger2019}, $\bvec{A_1}$ is given in Appendix B of \citet{Luger2019}, and $\bvec{R}(t)$ is the rotation matrix defined previously.
+
+Given this new equation, we must change how we approach the inverse problem (\S\ref{sec:inverse}). 
+When solving for the spectrum given the spherical harmonic vector (\S\ref{sec:solve_s}), we need only make the replacements $\bvec{f} \rightarrow \frac{\bvec{f}}{\bvec{B}\, \bvec{y}}$ and $\boldsymbol{\Sigma}_\mathbf{f} \rightarrow \frac{\boldsymbol{\Sigma}_\mathbf{f}}{(\bvec{B}\, \bvec{y})^2}$ in Equations~(\ref{eq:inverse:shat}) and (\ref{eq:inverse:scov}).
+However, when solving for the spherical harmonic vector given the spectrum (\ref{sec:solve_y}), the problem is no longer linear in $\bvec{y}$, as the vector of interest appears in both the numerator and the denominator:
+%
+\begin{align}
+    \label{eq:norm:fy}
+    \bvec{f}
+     & =
+    \frac{
+        \bvec{D}
+        \,
+        \bvec{S}
+        \,
+        \bvec{y}
+    }{
+        \bvec{B}
+        \,
+        \bvec{y}
+    }
+    \quad.
+\end{align}
+%
+While we can solve for $\bvec{y}$ using a nonlinear optimizer, it is often the case that the denominator in Equation~(\ref{eq:norm:fy}) is close to unity; i.e., the total flux from the star typically varies by only a few percent.
+When this is the case, it is straightforward to linearize this equation.
+Following the notation from \S\ref{sec:solve_y}, we may therefore write
+%
+\begin{align}
+    \bvec{f}
+     & =
+    \frac{
+        \bvec{D} \, \bvec{s_0}
+        \,
+        +
+        \,
+        \bvec{D}\bvec{S_1}
+        \,
+        \bvec{y_1}
+    }{
+        \bvec{B_0}
+        \,
+        +
+        \bvec{B_1}
+        \,
+        \bvec{y_1}
+    }
+    \quad,
+\end{align}
+%
+where $\bvec{B_0} = \bvec{1}$ is the first column of $\bvec{B}$ and $\bvec{B}_\bvec{1}$ denotes the matrix composed from the remaining $N - 1$ columns of $\bvec{B}$.
+Expanding the expression above about $\bvec{B_1} \bvec{y_1} = \bvec{0}$ and keeping only terms up to first order, we have
+%
+\begin{align}
+    \label{eq:norm:fapprox}
+    \bvec{f}
+     & \approx
+    \left(
+    \bvec{D} \, \bvec{s_0}
+    \,
+    +
+    \,
+    \bvec{D}\bvec{S_1}
+    \,
+    \bvec{y_1}
+    \right)
+    \circ
+    \left(
+    \bvec{1}
+    \,
+    -
+    \bvec{B_1}
+    \,
+    \bvec{y_1}
+    \right)
+    \nonumber  \\
+     & \approx
+    \left(
+    \bvec{D}\bvec{S_1}
+    \,
+    -
+    \bvec{C}
+    \right)
+    \bvec{y_1}
+    \,
+    +
+    \,
+    \bvec{D} \, \bvec{s_0}
+    \quad,
+\end{align}
+%
+where $\circ$ denotes an elementwise product and $\bvec{C}$ is a matrix constructed by multiplying each row of $\bvec{B_1}$ by the corresponding element of $\bvec{D}\bvec{s_0}$.
+%
+This equation is now linear in $\bvec{y}_\bvec{1}$, so we may solve the least-squares problem as before:
+%
+\begin{align}
+    \label{eq:norm:yhat}
+    \bvec{\hat{y}_1} & =
+    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1}
+    \left(
+    \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
+    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
+    (\bvec{f} - \bvec{D}\bvec{s_0})
+    +
+    {\boldsymbol{\Lambda}_{\mathbf{y}_\bvec{1}}}^{-1} \boldsymbol{\mu}_{\mathbf{y}_\bvec{1}}
+    \right)
+    \quad,
+\end{align}
+%
+with covariance
+%
+\begin{align}
+    \label{eq:norm:ycov}
+    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1} & =
+    \left(
+    \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
+    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
+    \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)
+    +
+    {\boldsymbol{\Lambda}_{\mathbf{y}_1}}^{-1}
+    \right)^{-1}
+    \quad.
+\end{align}
+%
+Note, importantly, that these equations are valid only in the limit that the change in the total flux from the star is small. 
+Nevertheless, even in the general case, we find that solving this linear problem yields a good starting point for a nonlinear optimization, which we revisit in more detail below.
+
+\subsection{Limb darkening}
+\label{sec:ld}
+%
+Thus far we have avoided mention of limb darkening, whose effect on the observed spectrum can often be significant. 
+A proper treatment of limb darkening requires solution of radiative transfer equations and should account for the temperature and composition gradients in the stellar atmosphere. 
+However, in the spirit of data-driven inference, we can approximate the effect of limb darkening by weighting the spatial component of our map by the limb darkening profile of the star, which can either be imposed or learned from the data.
+For a polynomial limb darkening law of the form
+%
+\begin{align}
+    \label{eq:ld:I}
+    \frac{I(\mu)}{I(\mu = 1)} = 1 - \sum_{n=1}^{n_\mathrm{max}} u_n(1 - \mu)^n
+    \quad,
+\end{align}
+%
+where $\mu = z = \sqrt{1 - x^2 - y^2}$ is the radial coordinate on the projected disk and $u_n$ is a limb darkening coefficient, the effect of limb darkening on the stellar map can be expressed exactly as a linear operation on the spherical harmonic coefficient vector \citep{Luger2019,Agol2019}.
+This can be understood by noting that all terms in Equation~(\ref{eq:ld:I}) are strictly polynomials in $x$, $y$, and $z$, all of which can be expressed exactly as sums of spherical harmonics \citep{Luger2019}.
+When weighting the surface intensity by the limb darkening profile, the resulting intensity is simply a product of spherical harmonics, which is itself a sum of spherical harmonics. 
+Given a limb darkening law of degree $n_\mathrm{max}$, we can always construct a matrix $\bvec{L}$ that transforms a spherical harmonic vector $\bvec{y}$ of degree $l_\mathrm{max}$ to a limb-darkened spherical harmonic vector $\bvec{y'}$ of degree $l_\mathrm{max} + n_\mathrm{max}$.
+As an example, consider a map of degree $l_\mathrm{max} = 1$ and the linear limb darkening law ($n_\mathrm{max} = 1$).
+The transformation matrix from $\bvec{y}$ to $\bvec{y'}$ is
+%
+\begin{align}
+    \label{eq:ld:L}
+    \bvec{L} =
+    \frac{1}{1 - \frac{u_1}{3}}
+    \begin{pmatrix}
+        \quadquad1-u_1\quadquad & 0                       & \frac{u_1}{\sqrt{3}}    & 0                       \\
+        0                       & \quadquad1-u_1\quadquad & 0                       & 0                       \\
+        \frac{u_1}{\sqrt{3}}    & 0                       & \quadquad1-u_1\quadquad & 0                       \\
+        0                       & 0                       & 0                       & \quadquad1-u_1\quadquad \\
+        0                       & 0                       & 0                       & 0                       \\
+        0                       & \frac{u_1}{\sqrt{5}}    & 0                       & 0                       \\
+        0                       & 0                       & \frac{2u_1}{\sqrt{15}}  & 0                       \\
+        0                       & 0                       & 0                       & \frac{u_1}{\sqrt{5}}    \\
+        0                       & 0                       & 0                       & 0
+    \end{pmatrix}
+    \quad.
+\end{align}
+%
+The columns of $\bvec{L}$ are constructed from the coefficient vectors of each transformed spherical harmonic, which are in turn computed by multiplying each spherical harmonic by the spherical harmonic decomposition of the particular limb darkening law.
+Figure~\ref{fig:ld} shows this transformation with $u_1 = 1$ applied to each of the first four spherical harmonics.
+%
+\begin{figure}[t!]
+    \begin{centering}
+        \includegraphics[width=0.5\linewidth]{ld.pdf}
+        \caption{%
+            Illustration of the limb darkening transformation given by Equation~(\ref{eq:ld:L}) for a linear limb darkening law with $u_1 = 1$. 
+            Each row shows a spherical harmonic before (left) and after (right) transformation by $\bvec{L}$.
+        }
+        \label{fig:ld}
+    \end{centering}
+\end{figure}
+%
+
+Now, to incorporate limb darkening into our model, we must modify how we compute the Doppler design matrix $\Doppler$ (Equation~\ref{eq:linear:D} and Figure~\ref{fig:linalg}). 
+Recall that this matrix is constructed by vertically stacking the submatrices $\Doppler_m$ given by Equation~(\ref{eq:linear:Dm}), which we now compute as
+%
+\begin{align}
+    \label{eq:ld:Dm}
+    \Doppler_m =
+    \begin{pmatrix}
+        \quad
+        \bvec{T}(\kT_0)
+        \quad
+         &
+        \quad
+        \bvec{T}(\kT_1)
+        \quad
+         &
+        \quad
+        \cdots
+        \quad
+         &
+        \quad
+        \bvec{T}(\kT_{N'})
+        \quad
+    \end{pmatrix}
+    (\bvec{L} \, \bvec{R}(t_m) \otimes \bvec{I}_{K'})
+    \quad,
+\end{align}
+%
+where we have replaced the rotation matrix $\bvec{R}(t_m)$ with the linear transformation $\bvec{L}\,\bvec{R}(t_m)$, which first rotates the input spherical harmonic coefficient vector to the correct phase then limb darkens it.
+Note also that the terms in the convolution kernel $\kT$ are now indexed from 0 to $N' = (l_\mathrm{max} + n_\mathrm{max} + 1)^2$, where $n_\mathrm{max}$ is the degree of the limb darkening operator.
+
+Note that it is also possible to model wavelength-dependent limb darkening in this fashion. 
+The procedure is similar, except that the limb darkening coefficients $u_n$ are now functions of $\lnlam$, and each element of the matrix $\bvec{L}$ is now a vector of length $K'$. 
+The submatrices $\Doppler_m$ may be written as
+%
+\begin{align}
+    \label{eq:ld:Dmwav}
+    \resizebox{0.91\textwidth}{!}{
+        $
+            \Doppler_m =
+            \begin{pmatrix}
+                \quad
+                \bvec{T}(\kT_0)
+                \quad
+                 &
+                \quad
+                \bvec{T}(\kT_1)
+                \quad
+                 &
+                \quad
+                \cdots
+                \quad
+                 &
+                \quad
+                \bvec{T}(\kT_{N'})
+                \quad
+            \end{pmatrix}
+            \begin{pmatrix}
+                \mathrm{diag}(\bvec{L}_{0,0})
+                 &
+                \mathrm{diag}(\bvec{L}_{0,1})
+                 &
+                \cdots
+                 &
+                \mathrm{diag}(\bvec{L}_{0,N})
+                \\
+                \mathrm{diag}(\bvec{L}_{1,0})
+                 &
+                \mathrm{diag}(\bvec{L}_{1,1})
+                 &
+                \cdots
+                 &
+                \mathrm{diag}(\bvec{L}_{1,N})
+                \\
+                \cdots
+                 &
+                \cdots
+                 &
+                \ddots
+                 &
+                \cdots
+                \\
+                \mathrm{diag}(\bvec{L}_{N',0})
+                 &
+                \mathrm{diag}(\bvec{L}_{N',1})
+                 &
+                \cdots
+                 &
+                \mathrm{diag}(\bvec{L}_{N',N})
+            \end{pmatrix}
+            (\bvec{R}(t_m) \otimes \bvec{I}_{K'})
+        $
+    }
+    \quad,
+\end{align}
+%
+where $\mathrm{diag}(\bvec{v})$ denotes the $(K' \times K')$ diagonal matrix constructed by placing the vector $\bvec{v}$ along the main diagonal.
+
+\subsection{Multiple spectral components}
+\label{sec:eigen}
+%
+In our discussion so far we have focused on the particular case where the spectral/spatial decomposition of the stellar surface can be expressed as the outer product of two vectors (Equation~\ref{eq:inverse:azero}).
+As we mentioned previously, this corresponds to the case where the spectrum is constant across the surface of the star except for a spatially-variable amplitude: i.e., spots have the same spectrum as the rest of the star, but emit less flux overall.
+However, most of the formalism developed here also applies to the more general case where the spectrum at a particular point on the surface of the star is a linear combination of several different spectral components.
+In this case, the map vector $\azero$ may be written as the sum over $J$ spectra $\bvec{s}_j$, each of which is dotted into a different vector of spherical harmonic coefficients $\bvec{y}_j^\top$:
+%
+\begin{align}
+    \label{eq:eigen:azero}
+    \azero
+     & =
+    \sum_{j=0}^{J-1}\mathrm{vec}\left( \bvec{s}_j \, \bvec{y}_j^\top \right) \\
+     & =
+    \mathrm{vec}\left( \boldsymbol{\mathbb{S}} \, \boldsymbol{\mathbb{Y}}^\top \right) \quad,
+\end{align}
+%
+where $\boldsymbol{\mathbb{S}}$ is the $(K' \times J)$ matrix whose columns are the $J$ spectral components and $\boldsymbol{\mathbb{Y}}^\top$ is the $(J \times N)$ matrix whose rows are the corresponding $J$ spherical harmonic coefficient vectors.
+
+The model remains linear in both the spherical harmonic coefficients and the spectral components, and the procedures outlined in \S\ref{sec:inverse} may still be followed to solve the inverse problem, provided we unroll these matrices into vectors, letting $\mathbf{s} = \mathrm{vec}(\boldsymbol{\mathbb{S}})$ and $\mathbf{y} = \mathrm{vec}(\boldsymbol{\mathbb{Y}})$.
+A detailed discussion of this general case is deferred to future work, but we present an example of a two-component stellar spectrum in \S\ref{sec:eigen}
+below.
+
+\section{Application to a spotted star}
+\label{sec:spotstar}
+
+In this section we apply the formalism developed in \S\ref{sec:inverse} and \S\ref{sec:bellswhistles} to a synthetic dataset of a rapidly rotating spotted star. 
+This section is motivated by the examples in \cite{Vogt1987}, who generated rotationally-broadened spectra of a rapidly-rotating star with the letters ``VOGT'' painted across the northern hemisphere. 
+In that paper, the authors generated synthetic line profiles of the Fe I $\lambda 6430$ absorption line with equivalent width $W \approx 10$~km/s and from these computed rotationally broadened spectra for a star at an inclination $i=40^\circ$ rotating at projected velocity $v\sin i = 40$~km/s.
+The spectra were computed at 16 equally spaced rotational phases and downsampled to 32 wavelength bins per epoch, for a total of 512 data points.
+
+\begin{figure}[t!]
+    \begin{centering}
+        \includegraphics[width=0.85\linewidth]{spot_setup.pdf}
+        \caption{%
+            The basic setup for the \spot problem. 
+            We compute the $l_\mathrm{max} = 15$ spherical harmonic expansion of a map where the word ``SPOT'' has been placed across the northern hemisphere (top left). 
+            Each point on the surface is given the same spectrum, composed of a sum of synthetic Gaussian absorption lines (blue curve in the bottom panel).
+            The specific intensity at each point on the surface is equal to this spectrum weighted by the intensity of the map, which is close to zero within the spot (point labeled \texttt{B}) and close ot unity outside the spot (point labeled \texttt{A}).
+            To generate the synthetic dataset (orange curves in the bottom panel), the star is inclined at $40^\circ$ with respect to the line of sight and the disk-integrated spectrum is computed at 16 equally-spaced phases between $-180^\circ$ and $180^\circ$ (middle panel).
+            The grey regions indicate wavelength regions outside the observation window, but whose features still contribute to the observed spectrum due to rotational broadening.
+        }
+        \label{fig:spot_setup}
+    \end{centering}
+\end{figure}
+
+We repeat the same experiment here using our new formalism, except we instead generate a stellar surface with the word ``SPOT'' written across the northern hemisphere (top left panel of Figure~\ref{fig:spot_setup}).
+We do this by computing the $l_\mathrm{max} = 15$ spherical harmonic decomposition of an image of the word, generating a set of $N = (l_\mathrm{max} + 1)^2 = 256$ spherical harmonic coefficients $\bvec{y} = (1 \quadquad \bvec{y_1})$.
+
+Our input spectrum $\bvec{s}$ was generated at high resolution ($R \equiv \frac{\lambda}{\Delta\lambda} = 300,000$) centered at a reference wavelength $\lambda_\mathrm{r} = 6430$ nm (blue curve in the bottom panel of Figure~\ref{fig:spot_setup}).
+The spectrum consists of a Gaussian absorption line in log-wavelength ($\lnlam$) space with amplitude $0.5$ and standard deviation $\sigma_{\lnlam} = 1.4\times 10^{-5}$. 
+This corresponds to a FWHM of about $2.355~\sigma_{\lnlam}~\lambda_\mathrm{r}~\approx~0.2$ nm or, in velocity space, $2.355~\sigma_{\lnlam}~c~\approx~10$~km/s, equal to the value used in \citet{Vogt1987}.
+Unlike \citet{Vogt1987}, we add 20 additional small absorption lines at random positions throughout the spectrum, all of the same FWHM but of varying depths, including some line blends. 
+In total, the rest frame spectrum $\bvec{s}$ consists of $K = 201$ log-wavelength bins in the range $-\Delta\lnlam < \lnlam < \Delta\lnlam$ for $\Delta\lnlam = 3.3\times 10^{-4}$ plus an additional
+%
+\begin{align}
+    W - 1 & = \frac{v\sin i}{c} \frac{K}{\Delta\lnlam} - 1 \nonumber           \\
+          & = \left(\frac{40~\mathrm{km/s}}{3\times 10^5~\mathrm{km/s}}\right)
+    \left(\frac{201}{3.3 \times 10^{-4}}\right)  - 1 \nonumber                 \\
+          & = 80
+\end{align}
+%
+log-wavelength bins of padding (40 on either side) to eliminate edge effects due to the convolution, for a total of $K' = 281$ wavelength bins. 
+As in \citet{Vogt1987}, we assume a projected velocity of $v\sin i = 40$ km/s and an inclination $i = 40^\circ$.
+
+Given $\bvec{y_1}$ and $\bvec{s}$, we use Equations~(\ref{eq:deconv:F}) and~%
+(\ref{eq:inverse:azero}) to compute the data vector $\bvec{f}$ at $M = 16$ equally spaced rotational phases; these phases are shown in orthographic projection (as an observer would see the star) in the center panel of Figure~\ref{fig:spot_setup}.
+The synthetic spectra for each phase are shown as the orange curves in the bottom panel of the figure (note the different scaling, as all spectral lines become shallower due to the broadening). 
+We assume a wavelength-independent, quadratic limb darkening law with $u_1 = 0.5$ and $u_2 = 0.25$. 
+Finally, we divide the flux by the baseline at each epoch (Equation~\ref{eq:norm:b})
+and add random Gaussian noise with amplitude $\sigma_\bvec{f} = 10^{-4}$ to simulate a very high signal-to-noise ratio (SNR) spectrum. 
+The mean standard deviation in each wavelength bin across all 16 epochs in the noiseless data vector is about $10^{-2}$, so our choice of $\sigma_\bvec{f}$ corresponds to SNR $\sim$ 100 in each of the 201 wavelength bins of $\bvec{f}$.
+%
+%For reference, \citet{Vogt1987} report SNRs per 60 m\AA\, pixel, while our
+%resolution elements are approximately $\lambda_r\Delta\lnlam/K \approx 100$ m\AA\,
+%across, so our SNR in the same units as \citet{Vogt1987} is about 80.
+%
+% TODO: Perhaps Vogt computes the "signal" as the line depth, rather than
+% as the amplitude of the perturbations? Check this.
+
+% We Recover images with an effective resolution of $12^\circ$.
+
+In the following sections we discuss various approaches to solving the Doppler imaging problem for this dataset.
+Unless otherwise noted, in all experiments we adopt a Gaussian prior for the spherical harmonic coefficients $\bvec{y_1}$ with mean $\boldsymbol{\mu}_\bvec{y_1} = \bvec{0}$ and covariance $\boldsymbol{\Lambda}_\bvec{y_1} = (10^{-2})^2\bvec{I}$, corresponding to a flat power spectrum prior.
+We place a Gaussian process prior on the spectrum $\bvec{s}$ with mean $\boldsymbol{\mu}_\bvec{s} = \bvec{1}$ and a covariance matrix $\boldsymbol{\Lambda}_\bvec{s}$ computed from a Mat\'ern-3/2 kernel with amplitude $\sigma_\bvec{s} = 0.3$ and lengthscale $\rho_\bvec{s} = 3\times 10^{-5}$.
+
 \end{document}

### 2021-08-17 figures/linalg.py

@@ -6,11 +6,8 @@ degree inference problem.
 """
 import matplotlib.pyplot as plt
 import numpy as np
-import paparazzi as pp
 from scipy.sparse import hstack, vstack, csr_matrix, block_diag, diags
 import starry
-
-np.random.seed(11)
 
 
 def RAxisAngle(axis=[0, 1, 0], theta=0):
@@ -164,27 +161,25 @@ def get_ortho_longitude_lines(
 
 # Settings for this figure
 ydeg = 2
-ntheta = 11
+nt = 11
 inc = 40.0
-vsini = 35.0
-nlam = 151
-u = []
+veq = 100000
 
 #
 # Compute stuff!
 #
 
 # Compute the `D` matrix
-theta = np.linspace(0, 360, ntheta)
+theta = np.linspace(0, 360, nt)
 theta[-1] = 0.0
-dop = pp.Doppler(ydeg=ydeg, vsini=vsini, inc=inc, u=u)
-dop.generate_data(theta=theta, nlam=nlam)
-D = dop.D().todense()
+vsini = veq * np.sin(inc * np.pi / 180)
+map = starry.DopplerMap(ydeg=ydeg, nt=nt, veq=veq, vsini_max=vsini, inc=inc, lazy=False)
+D = np.array(map.design_matrix(theta=theta).todense())
 
 # Plot it
 fig, ax = plt.subplots(1, figsize=(11, 9.25))
 fig.subplots_adjust(left=0, right=1, bottom=0, top=1)
-cmap = plt.get_cmap("inferno")
+cmap = plt.get_cmap("inferno").copy()
 vmax = np.nanmax(np.abs(D))
 D[D == 0] = -99
 cmap.set_under((0.9, 0.9, 0.9))
@@ -197,7 +192,7 @@ width = 1.0 / 9.0
 pad = 0.0
 y0 = 1.0
 height = 1.0 / 9.0
-map = starry.Map(ydeg=2)
+map = starry.Map(ydeg=ydeg)
 n = 0
 for l in range(ydeg + 1):
     for m in range(-l, l + 1):
@@ -207,6 +202,10 @@ for l in range(ydeg + 1):
             map[l, m] = 1.0
         img = map.render(res=500).eval()
         axins.imshow(img, origin="lower", cmap=cmap, extent=(-1, 1, -1, 1))
+        x = np.linspace(-1, 1, 10000)
+        y = np.sqrt(1 - x ** 2)
[…]

### 2021-08-18 tex/ms.tex
updates

@@
-% Replace "([a-z$,])\n(\s*)([$\(a-z])" with "$1 $3"
-% Replace "\.\s([a-z])" with ". \n$1"
 % Define document class & import showyourwork
@@
 
+% Custom defs
 \include{style}
@@
 The mean standard deviation in each wavelength bin across all 16 epochs in the noiseless data vector is about $10^{-2}$, so our choice of $\sigma_\bvec{f}$ corresponds to SNR $\sim$ 100 in each of the 201 wavelength bins of $\bvec{f}$.
-%
+
 %For reference, \citet{Vogt1987} report SNRs per 60 m\AA\, pixel, while our
@@
 % as the amplitude of the perturbations? Check this.
-
 % We Recover images with an effective resolution of $12^\circ$.
@@
 
+\subsection{Known baseline and spectrum}
+\label{sec:spot_y1}
+%
+In our first experiment, we attempt to infer the stellar map assuming we have perfect knowledge of the rest frame spectrum $\bvec{s}$ and the baseline $\bvec{b}$ (Equation~\ref{eq:norm:b}).
+This is analogous to the case where a good physical model exists for the stellar spectrum and simultaneous photometry is available to constrain the baseline variations.
+As we showed in \S\ref{sec:solve_y}, the posterior distribution for the map coefficients $\bvec{y_1}$ is analytic in this case, with mean given by Equation~(\ref{eq:inverse:y1hat})
+and covariance given by Equation~(\ref{eq:inverse:y1cov}). 
+Note that we must first scale the data vector $\bvec{f}$ by $\bvec{b}$ (which in this case is known).
+
+% \begin{figure}[p!]
+%     \begin{centering}
+%         \includegraphics[width=0.49\linewidth]{spot_y1_timeseries.pdf}
+%         \includegraphics[width=0.49\linewidth]{spot_y1_rect.pdf}
+%         \caption{%
+%             The solution to the \spot problem at high SNR when both the rest frame spectrum and the baseline are known.
+%             The panel on the left shows the inferred map at each of the 16
+%             epochs, alongside the observed spectrum (black points) and the best-fit model (orange lines). 
+%             The rectangular projection of the original map is shown at the top right; the inferred map is displayed below it. 
+%             The bottom panel shows the posterior uncertainty as a function of latitude and longitude, ranging from close to zero in the northern hemisphere to $\sigma_\mathrm{prior} \approx 10\%$ below a latitude of $-30^\circ$.
+%             The latter is the uncertainty associated with our particular choice of prior, as the southernmost latitudes of the star are never visible to the observer.
+%         }
+%         \label{fig:spot_y1}
+%     \end{centering}
+% \end{figure}
+
+The results are shown in Figure~\ref{fig:spot_y1}. 
+The left hand panel shows the inferred map alongside the data (black points) and best fit model (orange curves) at each of the 16 epochs.
+The panels on the right show the true map (top), the inferred map (center)
+and the posterior pointwise uncertainty (bottom) on a rectangular latitude-longitude grid. 
+The uncertainty on the vector of pixels $\bvec{p}$ where we evaluate the map is equal to the square root of the diagonal of the posterior covariance matrix for the pixel values, computed from
+%
+\begin{align}
+    \label{eq:spotstar:uncert}
+    \boldsymbol{\Sigma}_\bvec{p} = \bvec{P} \boldsymbol{\Sigma}_\bvec{\hat{y}_1}^{-1} \bvec{P}^\top
+\end{align}
+%
+where $\bvec{P}$ is the change-of-basis matrix from spherical harmonic coefficients to pixels on the grid.
+
+The inferred map is nearly indistinguishable from the true map, save for a few small differences, particularly below the stellar equator. 
+This is captured by the uncertainty, which increases south of $+30^\circ$ latitude, reaching a maximum at $-30^\circ$, below which the uncertainty is constant at about 10\%. 
+This is due to the fact that regions below $-40^\circ$ latitude are never in view from the observer's perspective, while regions between about $-30^\circ$ and $-40^\circ$ are so strongly limb-darkened that the data contains little information about them.
+The particular value of the uncertainty in this region---10\%---is the uncertainty associated with the prior, which can be computed by replacing $\boldsymbol{\Sigma}_\bvec{\hat{y}_1}$ with $\boldsymbol{\Lambda}_\bvec{y_1}$ in Equation~(\ref{eq:spotstar:uncert}).
+
+\subsection{Known spectrum, unknown baseline}
+\label{sec:spot_y1b}
+%
+We next investigate the case where the spectrum is known exactly, but the baseline is not. 
+This corresponds to the case discussed in
+\S\ref{sec:norm}. 
+We use the solution to the linearized problem, Equation~(\ref{eq:norm:yhat}), to obtain an initial guess for $\bvec{y_1}$. 
+We then repeatedly solve Equation~(\ref{eq:inverse:y1hat}) for $\bvec{y_1}$, given the baseline computed from the previous value of $\bvec{y_1}$ from Equation~(\ref{eq:norm:b}).
+Because of the high SNR of our data, we find that it is necessary to employ a simple tempering procedure to avoid getting stuck in local minima. 
+We introduce an artificial temperature $T$ that decreases every iteration in equally spaced logarithmic steps $\Delta \log T$ from an initial temperature $T=T_0$ to $T=1$. 
+This temperature is used to scale the data covariance $\boldsymbol{\Sigma}_\bvec{f}$; in practice, we simply replace $\boldsymbol{\Sigma}_\bvec{f}$ with $T \boldsymbol{\Sigma}_\bvec{f}$ in Equation~(\ref{eq:inverse:y1hat}).
+This has the effect of smoothing out the likelihood space, reducing the likelihood that the solver will get stuck in a local minimum. 
+For this particular experiment, we set $T_0 = 100$ and $\Delta \log T = -0.25$, for a total of $9$ steps of the bilinear solver.
+%
+In a final step, we run a gradient-descent optimizer, initializing it at the solution obtained with the bilinear solver. 
+We use the \texttt{Keras} \citep{Keras} implementation of the Nesterov momentum-enhanced Adam solver \citep[\texttt{NAdam};][]{NAdam}, running it for $N_\mathrm{nadam} = 80$ iterations at a learning rate $L_\mathrm{nadam} = 10^{-4}$.
+Our loss function is simply the (negative) log probability, equal to the sum of the log likelihood and log prior:
+%
+\begin{align}
+    \label{eq:spotstar:logP}
+    -\ln P & =
+    \frac{1}{2}
+    \Big(
+    \bvec{r}^\top \boldsymbol{\Sigma}_\bvec{f}^{-1} \bvec{r} \, + \,
+    \bvec{y_1}^\top \boldsymbol{\Lambda}_\bvec{y_1}^{-1} \bvec{y_1} \, + \, (\bvec{b - 1})^\top \boldsymbol{\Lambda}_\bvec{b}^{-1} (\bvec{b - 1})
+    \Big)
+\end{align}
+%
+where $\bvec{r}$ is the residual (data minus model) vector and the last term is a prior we include on the baseline $\bvec{b}$, which we force to be close to a mean of unity with covariance $\boldsymbol{\Lambda}_\bvec{b} = (0.1)^2\bvec{I}$.
+
+% \begin{figure}[p!]
+%     \begin{centering}
+%         \includegraphics[width=0.49\linewidth]{spot_y1b_timeseries.pdf.pdf}
+%         \includegraphics[width=0.49\linewidth]{spot_y1b_rect.pdf}
+%         \\[0.5em]
+%         \includegraphics[width=0.405\linewidth]{spot_y1b_baseline.pdf}
+%         \includegraphics[width=0.575\linewidth]{spot_y1b_coeffs.pdf}
+%         \caption{%
+%             Similar to Figure~\ref{fig:spot_y1}, but assuming the baseline is not known. 
+%             The panel at the bottom left shows the true baseline (blue) and the inferred baseline (orange), along with its $1\sigma$ uncertainty. 
+%             The large offset between the two highlights one of the fundamental degeneracies of the problem: since most of the southern hemisphere of the star is never visible, the coefficient of the $Y_{1,-1}$ (\raisebox{-0.2em}{\includegraphics[width=1em]{Y1m1.pdf}}) spherical harmonic is not constrained by the data, resulting in an unknowable additive offset in the baseline.
+%             This effect can be seen also in (\emph{a}) the inferred map, where the background intensity in the northern hemisphere is significantly larger than that in the southern hemisphere, and (\emph{b}) the spherical harmonic coefficients (bottom right), where a large discrepancy is visible between the true and inferred values of the first two coefficients.
+%         }
+%         \label{fig:spot_y1b}
+%     \end{centering}
+% \end{figure}
+
+Our results are shown in Figure~\ref{fig:spot_y1b}. 
+The panels at the top are the same as those in Figure~\ref{fig:spot_y1}, but now we also plot the inferred baseline (lower left) and spherical harmonic coefficients (lower right) next to the true values.
+We recover the \texttt{SPOT} map just as well as before, except for the presence of a strong dipolar artifact; the background intensity level is higher in the northern hemisphere and lower in the southern hemisphere.
+This effect is closely related to the fact that we do not know the true baseline. 
+While we are able to infer the shape of the baseline exceedingly well (lower left panel), there is a large offset between the true value and our inferred value. 
+This is due to a fundamental degeneracy involving the $Y_{1,-1}$ (\raisebox{-0.2em}{\includegraphics[width=1em]{Y1m1.pdf}}) spherical harmonic coefficient, which, because a large portion of the southern hemisphere is never in view, cannot be constrained by the data.
+The magnitude of the true value of the coefficient is quite large (lower right panel), since the northern hemisphere \emph{is} significantly darker than the southern hemisphere; however, the data do not constrain this, and our prior shrinks all coefficients toward zero.
+The net effect is that the region surrounding the spot in the northern hemisphere gets brighter to even out the difference between the two hemispheres. 
+This causes the visible portion of the star to get brighter, raising the baseline relative to the true value.
+
+Note, importantly, that even in cases where the baseline is known (from, say, simultaneous photometry), it is typically only known in a \emph{relative} sense. 
+This degeneracy will typically apply in that case as well, so in principle the dipole term will always be unconstrained for stars at similar inclinations. 
+For inclinations closer to $90^\circ$ this is much less of an issue, although (as we will see below) other degeneracies show up.
+
+Finally, we note that the pixelwise uncertainty shown is a strict \emph{lower bound} on the map uncertainty, since it is the uncertainty conditioned on the inferred value of the baseline. 
+Sampling methods such as MCMC are required to obtain the \emph{true} uncertainty on the map. 
+We discuss this further in \S\ref{sec:discussion}.
+
+\subsection{Unknown spectrum, unknown baseline}
+\label{sec:spot_y1bs}
+%
+Suppose we are handed a series of spectra in a wavelength regime where we do not have a good physical model for the line generation mechanisms, or a wavelength regime with many line blends for which we do not have reliable templates.
+Or perhaps the spectra are of a star whose rotational broadening does not dominate over other broadening mechanisms, in which case our template might not be accurate enough to allow us to tease out the small Doppler signals.
+In these cases, we may want to relax the assumption that we know the rest frame spectrum $\bvec{s}$ exactly, and instead try to \emph{learn} it from the data.
+
+Given the same data as before, we now try to learn both the stellar map and the stellar spectrum, conditioned only on the wide Gaussian priors discussed above. 
+We must follow the iterative procedure presented in
+\S\ref{sec:full_solve}, adjusting for the fact that we do not know the true baseline, either (\S\ref{sec:norm}).
+
+% \begin{figure}[p!]
+%     \begin{centering}
+%         \includegraphics[width=0.49\linewidth]{spot_y1bs_timeseries.pdf}
+%         \includegraphics[width=0.49\linewidth]{spot_y1bs_rect.pdf}
+%         \\[0.5em]
+%         \includegraphics[width=0.405\linewidth]{spot_y1bs_baseline.pdf}
+%         \includegraphics[width=0.575\linewidth]{spot_y1bs_coeffs.pdf}
+%         \\[0.5em]
+%         \includegraphics[width=0.98\linewidth]{spot_y1bs_spectrum.pdf}
+%         \caption{%
+%             Similar to Figure~\ref{fig:spot_y1}, but assuming we have no information about either the spectrum, the baseline, or the map coefficients. 
+%             The bottommost panel now shows the true rest frame spectrum (blue line), the initial guess based on a deconvolution (dashed orange line), and the inferred spectrum (orange line, with shaded $1\sigma$ uncertainty).
+%         }
+%         \label{fig:spot_y1bs}
+%     \end{centering}
+% \end{figure}
+
+% \begin{figure}[p!]
+%     \begin{centering}
+%         \includegraphics[width=0.49\linewidth]{spot_y1bs_low_snr_timeseries.pdf}
+%         \includegraphics[width=0.49\linewidth]{spot_y1bs_low_snr_rect.pdf}
+%         \\[0.5em]
+%         \includegraphics[width=0.405\linewidth]{spot_y1bs_low_snr_baseline.pdf}
+%         \includegraphics[width=0.575\linewidth]{spot_y1bs_low_snr_coeffs.pdf}
+%         \\[0.5em]
+%         \includegraphics[width=0.98\linewidth]{spot_y1bs_low_snr_spectrum.pdf}
+%         \caption{%
+%             Same as Figure~\ref{fig:spot_y1bs}, but for $10\times$ lower SNR.
+%             We still recover the \spot map and the input spectrum, albeit with higher uncertainty, as expected.
+%         }
+%         \label{fig:spot_y1bs_low_snr}
+%     \end{centering}
+% \end{figure}
+
+Because the problem is generally not convex, we need a good starting guess for either the spectrum or the map coefficients. 
+We note that we can very crudely approximate the rest frame spectrum by deconvolving the average observed spectrum with the first term of the convolution kernel $\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{kT00.pdf}}).
+In practice, this is a fairly poor approximation, but we find that it suffices as an initial guess. 
+Given this starting value of $\bvec{s}$, we compute an initial guess for $\bvec{y_1}$ using the linear baseline approximation. 
+We then iterate between solving for $\bvec{s}$ and solving for $\bvec{y_1}$, always using the previous value of the baseline to compute $\bvec{y_1}$. 
+As in the previous section, we find it necessary to implement a tempering scheme, except with a much higher starting temperature $T_0 = 5,000$ and a slower decay $\Delta\log T = -0.04$.
+We again refine our solution with \texttt{NAdam}, this time setting $N_\mathrm{nadam} = 3,000$ and $L_\mathrm{nadam} = 2.5\times 10^{-5}$. 
+Since we are now solving for the spectrum as well, we include the negative log prior term for the spectrum, $\frac{1}{2}(\bvec{s - 1})^\top \boldsymbol{\Lambda}_\bvec{s}^{-1}(\bvec{s - 1})$, in Equation~(\ref{eq:spotstar:logP}).
+
+Figure~\ref{fig:spot_y1bs} shows the results. 
+The top portion of the figure is the same as before. 
+A panel at the bottom has been added showing the true rest frame spectrum (blue), the initial guess based on the deconvolution (dashed orange), and the inferred spectrum (orange). 
+We recover the \spot feature as before, albeit with more noise, particularly south of about $+30^\circ$ latitude. 
+Our uncertainties are somewhat underestimated, as expected, since they are computed conditioned on the optimum value of the spectrum. 
+On the other hand, we recover the spectrum exceedingly well, with low uncertainty and virtually no bias anywhere.
+
+To test our technique on more realistic data, in Figure~\ref{fig:spot_y1bs_low_snr} we repeat the experiment on data with $10$ times higher uncertainty, setting $\sigma_\bvec{f} = 10^{-3}$. 
+Because the higher uncertainty increases the volume of the region surrounding the global optimum, it is actually significantly \emph{easier} for the algorithm to converge on the best solution, so we set $T_0 = 500$, $\Delta\log T = -0.05$, $N_\mathrm{nadam} = 500$, and $R_\mathrm{nadam} = 10^{-4}$.
+Interestingly, while the uncertainty on the spectrum increased, the quality of the recovered \spot map did not noticeably degrade. 
+This suggests we did not quite find the global optimum in Figure~\ref{fig:spot_y1bs}. 
+We discuss this further in \S\ref{sec:discussion}.
+
+\subsection{Spatially-variable spectrum}
+\label{sec:twospec}
+%
+In our final experiment, we relax the assumption that the stellar rest frame spectrum is spatially constant, allowing for different spectral features inside and outside of the \spot. 
+This is the case for, say, chemically peculiar Ap stars, whose abundance of certain elements is significantly different within spotted regions on their surfaces. 
+It is also the case in general for spots that are significantly cooler than the rest of the photosphere, where the relative abundance of different ionization states or molecular features may be different than in the hotter, unspotted regions.
+
+The problem setup is the same as that discussed in \S\ref{sec:eigen}, where our full map vector $\bvec{a_0}$ is the outer product of a spectral matrix $\mathbb{S}$, whose $J$ columns are the different spectral components, and a spherical harmonic coefficient matrix $\mathbb{Y}^\top$, whose $J$ rows are the corresponding coefficient vectors.
+For simplicity, in this experiment we consider only $J = 2$ spectral components and further require that the first component is spatially constant, i.e., the first row of $\mathbb{Y}^\top$ is the vector $(1 \quadquad \bvec{0}^\top)$.
+The second row of $\mathbb{Y}^\top$ is the vector $(1 \quadquad \bvec{y_1}^\top)$, where $\bvec{y_1}$ is the (unknown) spherical harmonic expansion of the spot. 
+The two columns of $\mathbb{S}$ are $\bvec{s_1}$ and $\bvec{s_2}$, the unknown spectral components.
+
+% \begin{figure}[t!]
+%     \begin{centering}
+%         \includegraphics[width=\linewidth]{twospec.pdf}
+%         \caption{%
+%             An example of a star whose spectrum is different within the spot (\texttt{B}) and outside of the spot (\texttt{A}). 
+%             Everywhere on the surface, the spectrum is a linear combination of two spectral components ($s_1$ and $s_2$).
+%             As in Figure~\ref{fig:spot_y1bs}, we assume we do not know the map, the baseline, or either of the spectra.
+%             The top row shows the true values for the map and the spectra, and the bottom row shows our inferred values. 
+%         }
+%         \label{fig:twospec}
+%     \end{centering}
+% \end{figure}
+
+We set \bvec{s_1} equal to a flat spectrum with two absorption lines of different depths, and \bvec{s_2} to the same spectrum, except we make the second line an emission feature. 
+The local rest-frame spectrum everywhere on the surface is a linear combination of these two spectra. 
+In our simple problem, the weight given to the first spectrum is the same everywhere (encoded in the first row of $\mathbb{Y}^\top$), and the weight given to the second spectrum is large outside of the spot and small within the spot (encoded in the second row of $\mathbb{Y}^\top$, which we set equal to the spherical harmonic expansion of the \spot feature).
+The first row of Figure ~\ref{fig:twospec} shows the problem setup. 
+The two spectral components are shown as the blue ($\bvec{s_1}$) and green ($\bvec{s_2}$) curves at the right. 
+Point \texttt{A} on the map (left panel) is outside the spot feature, so its local spectrum has nearly equal contributions from $\bvec{s_1}$ and $\bvec{s_2}$, and the second spectral line is absent (center panel).
+Point \texttt{B} is inside the spot, so it receives a contribution from $\bvec{s_1}$ only.
+
+In our inference step, we again assume we have no knowledge of the map, the baseline, or either of the spectral components. 
+As before, we initialize $\bvec{s_1}$ to the deconvolved mean spectrum and $\bvec{s_2}$ to the deconvolved mean spectrum after subtracting $\bvec{s_1}$. 
+In practice this leads to a decent approximation to $\bvec{s_1}$ but a rather featureless guess for $\bvec{s_2}$. 
+We use the same priors as before, except we set $\sigma_\bvec{s_1} = \sigma_\bvec{s_2} = 0.01$ to force the continuum to be flatter. 
+We run our bilinear solver with $T_0 = 5,000$ and $\Delta\log T = -0.025$ followed by the nonlinear solver with $N_\mathrm{nadam} = 2,000$ and $L_\mathrm{nadam} = 3\times 10^{-4}$.
+
+The results are shown in the bottom panel of Figure~\ref{fig:twospec}.
+We recover the \spot feature reasonably well, although with more artifacts than in the previous experiments. 
+We also recover the two spectral components, although our solution for $\bvec{s_2}$ is significantly better than that for $\bvec{s_1}$. 
+This is due to the fact that the only information about $\bvec{s_1}$ that makes it into our dataset is the convolution of $\bvec{s_1}$ with the first term of the convolution kernel $\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{kT00.pdf}}), since this spectral component has no spatial variability.
+Since the deconvolution operation is in general ill-posed, there is no unique solution for $\bvec{s_1}$. 
+On the other hand, the other spectral component projects into the data via convolutions with all other terms of the kernel and is therefore very well constrained.
+Finally, we can estimate the spectra at points \texttt{A} and \texttt{B} as before (center panel). 
+We recover the single spectral line at \texttt{A} and the two lines at \texttt{B}, albeit rather noisily due to the uncertainty in $\bvec{s_1}$.
+
+\section{Discussion}
+\label{sec:discussion}
+%
+
+\xxx{%
+    \begin{enumerate}
+        %
+        \item%
+              A gaussian prior with unit mean is a pretty bad prior for the spectrum.
+              In a more realistic scenario, we'd know a lot more information about the spectrum---such as where the lines are and some estimate of their shapes and depths---so the fidelity of our maps would be higher.
+              %
+        \item%
+              We are not addressing differential rotation and convective blueshift.
+              These make the integral in Equation~(\ref{eq:deconv:kT}) very difficult to solve. 
+              We will tackle this in the next paper.
+              %
+        \item%
+              Telluric lines could be treated much as in Figure~\ref{fig:twospec}, and marginalized over as in \citet{Bedell2019}.
+              %
+        \item% 
+              The instrumental profile is another Toeplitz matrix that can be dotted into Equation~(\ref{eq:linear:f}).
+              %
+        \item Discuss the case where the inclination/period/velocity is unknown.
+              The problem is not linear in these variables, so we need MCMC. 
+              But our model is differentiable, so we can easily use HMC. 
+              Discuss.
+              %
+        \item%
+              Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires first the rotation of the $(\lmax + 1)^2$ $\kT$ kernels (each of length $W$) to the correct stellar rotational phase, an operation that scales approximately as $W \lmax^3$, followed by $(\lmax + 1)^2$ linear convolutions of the rotated $\kT$ kernels with the spectral components (each of length $K$), which scales approximately as $W K \lmax^2$.
+              Since typically $K \gg \lmax$, the latter computation dominates and the entire evaluation takes $\mathcal{O}(W K \lmax^2)$ operations.
+    \end{enumerate}
+}
+
+\subsection{Dependence on SNR}
+\label{sec:snr}
+%
+Most of the examples in this paper considered very high SNR spectra.
+Figure~\ref{fig:snr} shows the effect of different SNR on the quality of the inferred map. 
+As before, the SNR we report is the ratio of the standard deviation of the true model in each wavelength bin across all epochs, averaged over all wavelength bins (i.e., the ``signal'') to the standard deviation of the added noise term, $\sigma_\bvec{f}$ (the ``noise'').
+The panels in Figure~\ref{fig:snr} show the inferred map for SNR in the range 1---1000, where SNR $\sim 100$ is the fiducial case considered in the examples so far. 
+The setup is the same as that in \S\ref{sec:spot_y1b}, where the spectrum is known exactly but the map coefficients and the baseline are not.
+
+As may be expected, the quality of the map decreases with lower SNR, but a reduction of the SNR by $\sim 20\times$ still allows for reasonable recovery of the \spot feature. 
+In general, as the SNR decreases further, two things happen: the \spot contrast decreases, and the features begin to blur out, especially south of about $+30^\circ$ latitude, where features are more limb-darkened at this inclination and in view for a smaller fraction of the time.
+
+As the SNR incraeses, however, the quality of the \spot feature does not improve appreciably, since a SNR of 100 is more than sufficient to recover a $l_\mathrm{max} = 15$ band-limited map. 
+Interestingly, south of the equator, the map quality actually begins to degrade with higher SNR. 
+This is due to the fact that finding the global optimum becomes exponentially more difficult with higher SNR, as the posterior volume becomes ever smaller. 
+Even with aggressive tempering, we were unable to converge on the best solution for SNR $\gtrsim 500$ given our standard, conservative priors and initial guesses (\S\ref{sec:spotstar}).
+%
+% \begin{figure}[p!]
+%     \begin{centering}
+%         \includegraphics[width=0.98\linewidth]{snr.pdf}
+%         \caption{%
+%             Recovered \spot map as a function of SNR per resolution element.
+%             The quality of the inferred map in the northern hemisphere improves with SNR, but at very high SNR the region surrounding the global optimum becomes so small that our optimization methods struggle to converge on the correct solution.
+%         }
+%         \label{fig:snr}
+%     \end{centering}
+% \end{figure}
+
+\subsection{Dependence on inclination}
+\label{sec:inc}
+%
+% \begin{figure}[p!]
+%     \begin{centering}
+%         \includegraphics[width=0.98\linewidth]{inclinations.pdf} % 
+%         \caption{%
+%             Recovered \spot map as a function of stellar inclination. 
+%             The rest frame spectrum is assumed to be known exactly, but the baseline is not. 
+%             At very low inclinations, the small projected velocities begin to degrade the spatial resolution of the inferred map, while at inclinations close to $90^\circ$ there is a degeneracy between the northern and southern hemispheres.
+%         }
+%         \label{fig:inclinations}
+%     \end{centering}
+% \end{figure}
+%
+As in \citet{Vogt1987}, we also investigate the dependence of the solution on the inclination of the star.
+Figure~\ref{fig:inclinations} shows the inferred map for the same problem setup as before (with SNR $\sim 100$), but this time varying the inclination between $10^\circ$ (nearly face-on) and $90^\circ$ (perfectly edge-on).
+As before, the inclination is assumed to be known exactly. 
+We further keep the true equatorial velocity of the star constant across all panels, so that the figure corresponds to the same star viewed at different orientations. 
+Because of this, decreasing the inclination decreases $v\sin i$, reducing the width of the convolution kernel and therefore the spatial resolution of our inferred map. 
+Increasing the inclination does not result in appreciable changes until an inclination of $\sim 80^\circ$, above which it becomes difficult to differentiate between features in the northern and southern hemispheres, whose projected velocities are nearly equal.
+At $i = 90^\circ$, there is a formal degeneracy between the two hemispheres, which can be seen from the mirror-image symmetry in the inferred map. 
+These results are broadly consistent with those of \citet{Vogt1987}.
+
+\section{Conclusions}
+\label{sec:conclusions}
+%
+\xxx{%
+    \begin{enumerate}
+        \item Advantages of data-driven modeling
+        \item Interpretable priors
+        \item Works on blended lines
+        \item Uses the whole spectrum
+        \item Yields uncertainties!
+        \item Probably works on slow rotators
+        \item Differentiable!
+        \item Fast!
+        \item Use in MCMC to marginalize over inclination and stuff
+    \end{enumerate}
+}
+
+%
+%
+%
+%
+\clearpage
+\appendix
+%
+%
+%
+%
+
+\section{Solving the $\kT$ integral}
+%
+In this section we will show how to compute the integral in Equation~(\ref{eq:kT:kT}), yielding the terms of the convolution kernel $\kT$. 
+It is convenient to first change basis from spherical harmonics to polynomials on the sphere:
+%
+\begin{align}
+    \label{eq:appendix:kT}
+    \kT(\lnlam, \Dargs)
+     & =
+    \int\limits_{-\sqrt{1 - x^2}}^
+    {\sqrt{1 - x^2}}
+    \pbasis
+    \Big(x, y\Big)
+    \mathrm{d}y
+    \,
+    \AOne
+    \nonumber \\[0.5em]
+     & \equiv
+    \rhoT(\lnlam, \Dargs)
+    \,
+    \AOne
+    \quad,
+\end{align}
+%
+where $\AOne$ is the change of basis matrix from spherical harmonics to polynomials \citep[Equation B11 in][]{Luger2019} and
+%
+\begin{align}
+    \pbasis(\x) \equiv
+    \Big(
+    1 \quad\quad\quad\quad\quad\quad x \quad\quad\quad\quad\quad\quad z \quad\quad\quad\quad\quad\quad y \quad\quad\quad\quad\quad\quad x^2 \quad\quad\quad\quad\quad\quad xz \quad\quad\quad\quad\quad\quad xy \quad\quad\quad\quad\quad\quad yz \quad\quad\quad\quad\quad\quad y^2 \quad\quad\quad\quad\quad\quad
+    ...
+    \Big)^\top
+    \quad,
+\end{align}
+%
+is the polynomial basis \citep[Equation 7][]{Luger2019}.
+The $n^\mathrm{th}$ term of the polynomial basis is a polynomial in $x$, $y$, and $z = \sqrt{1 - x^2 - y^2}$:
+%
+\begin{align}
+    \pbasisn
+    &=
+    x^i y^j z^k
+\end{align}
+%
+where $i, j, k$ are integers given by
+%
+\begin{align}
+    \label{eq:kT:lm}
+    i &= \floor*{\Lambda - \Delta}
+    \nonumber \\[0.5em]
+    j &= \floor*{\Delta}
+    \nonumber \\[0.5em]
+    k &= \ceil*{\Delta} - \floor*{\Delta}
+\end{align}
+%
+with
+%
+\begin{align}
+    \Lambda &= \floor*{\sqrt{n}}
+    \nonumber \\[0.5em]
+    \Delta &= \frac{n - \Lambda^2}{2}
+    \quad .
+\end{align}
+%
+We may now explicitly write down the $n^\mathrm{th}$ term of the vector $\rhoT(\lnlam, \Dargs)$ in Equation~(\ref{eq:appendix:kT}),
+%
+\begin{align}
+    \label{eq:kT:sTexpression}
+    \rho_n(\lnlam, \Dargs)
+     & =
+    \rho_{i,\,j,\,k}(\lnlam, \Dargs)
+    =
+    x^i
+    \int\limits_{-\sqrt{1 - x^2}}^
+    {\sqrt{1 - x^2}}
+    y^j
+    \left(1 - x^2 - y^2\right)^{\frac{k}{2}} \,
+    \mathrm{d}y
+    \quad .
+\end{align}
+%
+When $i = k = 0$, the integral is easy to evaluate:
+%
+\begin{align}
+    \rho_{i,\,j,\,0}(\lnlam_0)
+     & =
+    \begin{cases}
+        2 \left( 1 - x^2 \right)^\frac{j + 1}{2}
+        \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
+          & j \, \mathrm{even}        \\
+        0 & j \, \mathrm{odd} \quad .
+    \end{cases}
+\end{align}
+%
+The general term may be computed from the recurrence relation
+%
+\begin{align}
+    \rho_{0,\,j,\,0}(\lnlam_0) = \frac{j - 1}{j + 1} \big(1 - x^2\big) \rho_{0,\,j-2,\,0}
+\end{align}
+%
+provided
+%
+\begin{align}
+    \rho_{0,\,0,\,0} & = 2 \sqrt{1-x^2} \nonumber \\
+    \rho_{0,\,1,\,0} & = 0 \quad.
+\end{align}
+%
+When $i = 0$ and $k = 1$, we may substitute $y = \sin\psi\sqrt{1 - x^2}$ in the integrand to obtain
+%
+\begin{align}
+    \rho_{0,\,j,\,1}(\lnlam_0)
+     & =
+    (1 - x^2)^{\frac{j + 2}{2}}
+    \int\limits_{-\frac{\pi}{2}}^{\frac{\pi}{2}}
+    \sin^j\psi
+    \cos^2\psi \,
+    \mathrm{d}\psi
+    \quad.
+\end{align}
+%
+We may solve this integral using the recurrence relation
+%
+\begin{align}
+    \int
+    \sin^j\psi
+    \cos^m\psi \,
+    \mathrm{d}\psi
+     & =
+    -\frac{\sin^{j-1}\psi \cos^{m+1}\psi}{j + m}
+    +
+    \frac{j - 1}{j + m}\int\sin^{j-2}\psi \cos^m\psi \mathrm{d}\psi
+    \quad ,
+\end{align}
+%
+which, in our case, simplifies to
+%
+\begin{align}
+    \int\limits_{-\frac{\pi}{2}}^{\frac{\pi}{2}}
+    \sin^j\psi
+    \cos^2\psi \,
+    \mathrm{d}\psi
+     & =
+    \frac{j - 1}{j + 2}\int\limits_{-\frac{\pi}{2}}^
+    {\frac{\pi}{2}}\sin^{j-2}\psi \cos^2\psi \mathrm{d}\psi
+    \quad.
+\end{align}
+%
+We thus arrive at the recurrence relation
+%
+\begin{align}
+    \rho_{0,\,j,\,1} & = \frac{j - 1}{j + 2} \big(1 - x^2\big) \rho_{0,\,j-2,\,1}
+\end{align}
+%
+with initial conditions
+%
+\begin{align}
+    \rho_{0,\,0,\,1} & = \frac{\pi}{2} \big(1-x^2\big) \nonumber \\
+    \rho_{0,\,1,\,1} & = 0 \quad.
+\end{align}
+%
+Given these expressions, recursing upward in $i$ is easy:
+%
+\begin{align}
+    \rho_{i,\,j,\,k} & = x \, \rho_{i-1,\,j,\,k} \quad.
+\end{align}
+%
+This completes our derivation. 
+To summarize, given the boundary conditions
+%
+\begin{align}
+    \rho_{0,\,0,\,0} & = 2 \sqrt{1-x^2} \nonumber                \\
+    \rho_{0,\,0,\,1} & = \frac{\pi}{2} \big(1-x^2\big) \nonumber \\
+    \rho_{0,\,1,\,k} & = 0 \quad ,
+\end{align}
+%
+we may compute any term in $\rhoT$ via the expressions
+%
+\begin{align}
+    \label{eq:kT:sTrecurrence}
+    \rho_{0,\,j,\,k} & = \frac{j - 1}{j + 1 + k} \big(1 - x^2\big) \rho_{0,\,j-2,\,k} \nonumber \\
+    \rho_{i,\,j,\,k} & = x \, \rho_{i-1,\,j,\,k} \quad.
+\end{align}
+%
+The terms of the convolution kernel $\kT$ are then obtained by dotting this vector into the change of basis matrix $\AOne$, as discussed above.
+
+% Table
+\clearpage
+\begin{center}
+    \begin{longtable}{cll}
+        \caption{Common notation used in this paper}
+        \label{tab:notation}                                                                                                                                            \\
+        %
+        \toprule
+        \multicolumn{1}{c}{\textbf{Symbol}}                 &
+        \multicolumn{1}{c}{\textbf{Description}}            &
+        \multicolumn{1}{c}{\textbf{Reference}}                                                                                                                          \\
+        \midrule
+        \endfirsthead
+        %
+        \multicolumn{3}{c}%
+        {{\bfseries \tablename\ \thetable{}}. (continued from previous page)}                                                                                           \\[0.5em]
+        \toprule
+        \multicolumn{1}{c}{\textbf{Symbol}}                 &
+        \multicolumn{1}{c}{\textbf{Definition}}             &
+        \multicolumn{1}{c}{\textbf{Reference}}                                                                                                                          \\
+        \midrule
+        \endhead
+        \bottomrule
+        %
+        \endfoot
+        %
+        \endlastfoot
+        %
+        \midrule
+        \multicolumn{3}{c}{\emph{Variables}}                                                                                                                            \\
+        \midrule
+        %
+        $a_{lm}$                                            & spectral spherical harmonic coefficient                      & Equation~(\ref{eq:deconv:Ixi0})            \\
+        $\alm$                                              & vector of spectral spherical harmonic coefficients           & Equation~(\ref{eq:deconv:alm})             \\
+        $\bvec{a_0}$                                        & $\alm$ at reference time $t = t_0$                           & Equation~(\ref{eq:deconv:R})               \\
+        $\bvec{A_0}$                                        & matrix form of $\bvec{a_0}$                                  & Equation~(\ref{eq:inverse:azero})          \\
+        $\bvec{b}$                                          & flux baseline vector                                         & Equation~(\ref{eq:norm:b})                 \\
+        $\bvec{B}$                                          & block matrix representation of $\bvec{b}$                    & Equation~(\ref{eq:norm:b})                 \\
+        $c$                                                 & speed of light                                               & Equation~(\ref{eq:kT:beta})                \\
+        $\Curve$                                            & curve of constant radial velocity                            & Equation~(\ref{eq:deconv:kT})              \\
+        $\Dargs$                                            & parameters of the Doppler field                              & \S\ref{sec:the_problem}                    \\
+        $\D$                                                & logarithmic Doppler shift                                    & Equation~(\ref{eq:the_problem:D})          \\
+        $\Doppler$                                          & Doppler design matrix                                        & Equation~(\ref{eq:linear:f})               \\
+        $\bvec{f}$                                          & vector of observed flux values                               & Equation~(\ref{eq:linear:f})               \\
+        $F$                                                 & flux                                                         & Equation~(\ref{eq:the_problem:F})          \\
+        $i$                                                 & inclination                                                  & Equation~(\ref{eq:kT:beta})                \\
+        $I$                                                 & specific intensity                                           & Equation~(\ref{eq:the_problem:Ixi})        \\
+        $\bvec{I}$                                          & identity matrix                                              &                                            \\
+        $l$                                                 & spherical harmonic degree                                    &                                            \\
+        $L_\mathrm{nadam}$                                  & \texttt{NAdam} learning rate                                 & \S\ref{sec:spotstar}                       \\
+        $\bvec{L}$                                          & limb darkening operator                                      & Equation~(\ref{eq:ld:L})                   \\
+        $m$                                                 & spherical harmonic order                                     &                                            \\
+        $N_\mathrm{nadam}$                                  & number of \texttt{NAdam} iterations                          & \S\ref{sec:spotstar}                       \\
+        $\bvec{P}$                                          & Change of basis matrix from $Y_{lm}$ to pixels               & Equation~(\ref{eq:spotstar:uncert})        \\
+        $\bvec{R}$                                          & Wigner rotation matrix                                       & Equation~(\ref{eq:deconv:R})               \\
+        $\bvec{s}$                                          & vector representation of the spectrum                        & Equation~(\ref{eq:inverse:azero})          \\
+        $\bvec{S}$                                          & block matrix representation of $\bvec{s}$                    & Equation~(\ref{eq:inverse:S})              \\
+        $\boldsymbol{\mathbb{S}}$                           & matrix of $J$ spectral components                            & Equation~(\ref{eq:eigen:azero})            \\
+        $\Surf$                                             & projected visible area of the star                           & Equation~(\ref{eq:the_problem:F})          \\
+        $t$                                                 & time                                                         & \S\ref{sec:the_problem}                    \\
+        $T$                                                 & artificial temperature in bilinear solver                    & \S\ref{sec:spotstar}                       \\
+        $T_0$                                               & initial artificial temperature setting                       & \S\ref{sec:spotstar}                       \\
+        $\Delta\log T$                                      & artificial temperature step size                             & \S\ref{sec:spotstar}                       \\
+        $u$                                                 & limb darkening coefficient                                   & \S\ref{sec:ld}                             \\
+        $\x$                                                & Cartesian position on the sky                                & \S\ref{sec:the_problem}                    \\
+        $y_{lm}$                                            & spherical harmonic coefficient                               & \S\ref{sec:inverse}                        \\
+        $\bvec{y}$                                          & vector of spherical harmonic coefficients                    & Equation~(\ref{eq:inverse:azero})          \\
+        $Y_{lm}$                                            & spherical harmonic                                           & Equation~(\ref{eq:deconv:Ixi0})            \\
+        $\bvec{Y}$                                          & block matrix representation of $\bvec{y}$                    & Equation~(\ref{eq:inverse:Y})              \\
+        $\boldsymbol{\mathbb{Y}}$                           & matrix of $J$ spherical harmonic components                  & Equation~(\ref{eq:eigen:azero})            \\
+        %
+        \pagebreak
+        \midrule
+        \multicolumn{3}{c}{\emph{Variables (Greek)}}                                                                                                                    \\
+        \midrule
+        %
+        $\beta$                                             & relativistic parameter                                       & Equation~(\ref{eq:the_problem:D})          \\
+        $\delta$                                            & Dirac delta function                                         & Equation~(\ref{eq:deconv:convolution})     \\
+        $\kT$                                               & convolution kernel basis vector                              & Equation~(\ref{eq:deconv:kT})              \\
+        $\lambda$                                           & wavelength                                                   & \S\ref{sec:the_problem}                    \\
+        $\lambda_\mathrm{r}$                                & reference wavelength                                         & \S\ref{sec:the_problem}                    \\
+        $\lnlam$                                            & $\ln\frac{\lambda}{\lambda_\mathrm{r}}$ (observer frame) & \S\ref{sec:the_problem}                    \\
+        $\lnlam_0$                                          & $\ln\frac{\lambda}{\lambda_\mathrm{r}}$ (rest frame)     & \S\ref{sec:the_problem}                    \\
+        $\boldsymbol{\Lambda}$                              & prior covariance matrix                                      &                                            \\
+        $\boldsymbol{\mu}$                                  & prior mean vector                                            &                                            \\
+        $\ylmbasis$                                         & spherical harmonic basis vector                              & Equation~(\ref{eq:deconv:ylmbasis})        \\
+        $\boldsymbol{\Sigma}$                               & covariance matrix                                            &                                            \\
+        $\omega$                                            & angular velocity                                             & Equation~(\ref{eq:kT:beta})                \\
+        %
+        \midrule
+        \multicolumn{3}{c}{\emph{Dimensions}}                                                                                                                           \\
+        \midrule
+        %
+        $J$                                                 & \# of spectral components                                    & \S\ref{sec:eigen}                          \\
+        $K$                                                 & \# of wavelength bins in the observed spectrum               & \S\ref{sec:linear}                         \\
+        $K'$                                                & \# of wavelength bins in the latent spectrum                 & \S\ref{sec:linear}                         \\
+        $M$                                                 & \# of epochs observed                                        & \S\ref{sec:linear}                         \\
+        $N$                                                 & \# of spherical harmonic coefficients                        & \S\ref{sec:linear}                         \\
+        $N'$                                                & \# of spherical harmonic coefficients after limb darkening   & \S\ref{sec:ld}                             \\
+        $W$                                                 & \# of wavelength bins in the convolution kernel              & \S\ref{sec:linear}                         \\
+        %
+        \midrule
+        \multicolumn{3}{c}{\emph{Operators \& Other symbols}}                                                                                                           \\
+        \midrule
+        %
+        $\mathrm{diag}$                                     & diagonal matricization                                       & Equation~(\ref{eq:ld:Dmwav})               \\
+        $\mathrm{vec}$                                      & vectorization                                                & Equation~(\ref{eq:inverse:azero})          \\
+        $*$                                                 & convolution                                                  & Equation~(\ref{eq:deconv:convolution_def}) \\
+        $\circ$                                             & element-wise product                                         & Equation~(\ref{eq:norm:fapprox})           \\
+        $\otimes$                                           & Kronecker product                                            & Equation~(\ref{eq:linear:Dm})              \\
+        $\ceil*{\,}$                                        & ceiling                                                      & Equation~(\ref{eq:kT:lm})                  \\
+        $\floor*{\,}$                                       & floor                                                        & Equation~(\ref{eq:kT:lm})                  \\
+        $\bvec{0}$                                          & the zero vector, $(0 \quadquad 0 \quadquad \cdots \quadquad 0)^\top$ &                                                                                                           \\
+        $\bvec{1}$                                          & the one vector, $(1 \quadquad 1 \quadquad \cdots \quadquad 1)^\top$ &                                                                                                           \\
+    \end{longtable}
+\end{center}
+
+% Bibliography
+\clearpage
+\bibliography{bib}
+
 \end{document}

### 2021-08-18 figures/kT00.py

@@ -4,11 +4,15 @@ Plots the first term of the convolution kernel.
 
 """
 import matplotlib.pyplot as plt
-import paparazzi as pp
+import starry
 
-dop = pp.Doppler(ydeg=1)
-dop.generate_data(R=1e6, nlam=99, y1=[0, 0, 0])
-kT00 = dop.kT()[0]
+# Get the first term in the kernel
+map = starry.DopplerMap(1)
+vsini = map.ops.vsini_max
+x = map.ops.get_x(vsini)
+rT = map.ops.get_rT(x)
+kT = map.ops.get_kT0(rT)
+kT00 = kT[0]
 
 fig, ax = plt.subplots(1, figsize=(0.5, 0.25))
 fig.subplots_adjust(left=0, right=1, bottom=0, top=1)

### 2021-08-18 figures/ld.py

@@ -40,7 +40,7 @@ render = (
         map._obl,
         tt.as_tensor_variable(y).astype(tt.config.floatX),
         map._u,
-        map._f
+        map._f,
     )[0]
     .eval()
     .reshape(res, res)
@@ -67,8 +67,15 @@ for l in range(ydeg + 1):
         y[n] = 1.0
         yprime = L.dot(y[: (ydeg + 1) ** 2])
 
-        ax[n, 0].imshow(render(y), origin="lower", cmap="plasma", extent=(-1, 1, -1, 1))
-        ax[n, 1].imshow(render(yprime), origin="lower", cmap="plasma", extent=(-1, 1, -1, 1))
+        ax[n, 0].imshow(
+            render(y), origin="lower", cmap="plasma", extent=(-1, 1, -1, 1)
+        )
+        ax[n, 1].imshow(
+            render(yprime),
+            origin="lower",
+            cmap="plasma",
+            extent=(-1, 1, -1, 1),
+        )
 
         for k in [0, 1]:
             ax[n, k].plot(xc, yc, "k-")
@@ -77,7 +84,9 @@ for l in range(ydeg + 1):
             ax[n, k].set_xlim(-1.02, 1.02)
             ax[n, k].set_ylim(-1.02, 1.02)
 
-        ax[n, 0].set_ylabel(r"$Y_{{%d},{%d}}$" % (l, m), rotation=0, fontsize=20)
+        ax[n, 0].set_ylabel(
+            r"$Y_{{%d},{%d}}$" % (l, m), rotation=0, fontsize=20
+        )
         ax[n, 0].yaxis.set_label_coords(-0.35, 0.4)
 
         n += 1

### 2021-08-18 figures/spot_setup.py

@@ -3,6 +3,7 @@
 Setup for the SPOT problem.
 
 """
+from generate import generate_data
 import numpy as np
 import matplotlib.pyplot as plt
 import starry
@@ -10,39 +11,27 @@ import starry
 # Generate the data
 np.random.seed(13)
 
-
 # Instantiate the Doppler map
 ydeg = 15
-u = [0.5, 0.25]
-udeg = len(u)
-inc = 40.0
-veq = 60000
+nc = 1
 nt = 16
-map = starry.DopplerMap(ydeg=ydeg, udeg=udeg, nt=nt, inc=inc, veq=veq, lazy=False)
-map[1:] = u
-map.load(map="spot")
-map.spectrum = (
-    1.0
-    - 0.55 * np.exp(-0.5 * (map.wav0 - 643.0) ** 2 / 0.0085 ** 2)
-    - 0.02 * np.exp(-0.5 * (map.wav0 - 642.895) ** 2 / 0.0085 ** 2)
-    - 0.10 * np.exp(-0.5 * (map.wav0 - 642.97) ** 2 / 0.0085 ** 2)
-    - 0.04 * np.exp(-0.5 * (map.wav0 - 643.1) ** 2 / 0.0085 ** 2)
-    - 0.12 * np.exp(-0.5 * (map.wav0 - 643.4) ** 2 / 0.0085 ** 2)
-    - 0.08 * np.exp(-0.5 * (map.wav0 - 643.25) ** 2 / 0.0085 ** 2)
-    - 0.06 * np.exp(-0.5 * (map.wav0 - 642.79) ** 2 / 0.0085 ** 2)
-    - 0.03 * np.exp(-0.5 * (map.wav0 - 642.81) ** 2 / 0.0085 ** 2)
-    - 0.18 * np.exp(-0.5 * (map.wav0 - 642.63) ** 2 / 0.0085 ** 2)
-    - 0.04 * np.exp(-0.5 * (map.wav0 - 642.60) ** 2 / 0.0085 ** 2)
-)
-
-# Render the surface map for plotting
-res = 300
+inc = 40
+veq = 60000
+wav = np.linspace(642.85, 643.15, 200)
 theta = np.linspace(-180, 180, nt, endpoint=False)
-tmp = starry.Map(ydeg=ydeg, udeg=udeg, inc=inc, lazy=False)
-tmp[1:] = u
-tmp.load("spot", smoothing=0.05, force_psd=True, oversample=2)
[…]

### 2021-09-08 src/ms.tex
new structure

--- 2021-08-18 tex/ms.tex
@@
-% Define document class & import showyourwork
+% Define document class
 \documentclass[modern]{aastex631}
@@
     \begin{centering}
-        \includegraphics[width=\linewidth]{kT.pdf}
+        \includegraphics[width=\linewidth]{figures/kT.pdf}
         \caption{%
@@
     \begin{centering}
-        \includegraphics[width=0.6\linewidth]{spot.pdf}
+        \includegraphics[width=0.6\linewidth]{figures/spot.pdf}
         \caption{%
@@
     \begin{centering}
-        \includegraphics[width=0.65\linewidth]{compare.pdf}
+        \includegraphics[width=0.65\linewidth]{figures/compare.pdf}
         \caption{%
@@
     \begin{centering}
-        \includegraphics[width=0.8\linewidth]{linalg.pdf}
+        \includegraphics[width=0.8\linewidth]{figures/linalg.pdf}
         \caption{%
@@
     \begin{centering}
-        \includegraphics[width=0.5\linewidth]{ld.pdf}
+        \includegraphics[width=0.5\linewidth]{figures/ld.pdf}
         \caption{%
@@
     \begin{centering}
-        \includegraphics[width=0.85\linewidth]{spot_setup.pdf}
+        \includegraphics[width=0.85\linewidth]{figures/spot_setup.pdf}
         \caption{%
@@
 %     \begin{centering}
-%         \includegraphics[width=0.49\linewidth]{spot_y1_timeseries.pdf}
-%         \includegraphics[width=0.49\linewidth]{spot_y1_rect.pdf}
+%         \includegraphics[width=0.49\linewidth]{figures/spot_y1_timeseries.pdf}
+%         \includegraphics[width=0.49\linewidth]{figures/spot_y1_rect.pdf}
 %         \caption{%
@@
 %     \begin{centering}
-%         \includegraphics[width=0.49\linewidth]{spot_y1b_timeseries.pdf.pdf}
-%         \includegraphics[width=0.49\linewidth]{spot_y1b_rect.pdf}
+%         \includegraphics[width=0.49\linewidth]{figures/spot_y1b_timeseries.pdf.pdf}
+%         \includegraphics[width=0.49\linewidth]{figures/spot_y1b_rect.pdf}
 %         \\[0.5em]
-%         \includegraphics[width=0.405\linewidth]{spot_y1b_baseline.pdf}
-%         \includegraphics[width=0.575\linewidth]{spot_y1b_coeffs.pdf}
+%         \includegraphics[width=0.405\linewidth]{figures/spot_y1b_baseline.pdf}
+%         \includegraphics[width=0.575\linewidth]{figures/spot_y1b_coeffs.pdf}
 %         \caption{%
@@
 While we are able to infer the shape of the baseline exceedingly well (lower left panel), there is a large offset between the true value and our inferred value. 
-This is due to a fundamental degeneracy involving the $Y_{1,-1}$ (\raisebox{-0.2em}{\includegraphics[width=1em]{Y1m1.pdf}}) spherical harmonic coefficient, which, because a large portion of the southern hemisphere is never in view, cannot be constrained by the data.
+This is due to a fundamental degeneracy involving the $Y_{1,-1}$ (\raisebox{-0.2em}{\includegraphics[width=1em]{figures/Y1m1.pdf}}) spherical harmonic coefficient, which, because a large portion of the southern hemisphere is never in view, cannot be constrained by the data.
 The magnitude of the true value of the coefficient is quite large (lower right panel), since the northern hemisphere \emph{is} significantly darker than the southern hemisphere; however, the data do not constrain this, and our prior shrinks all coefficients toward zero.
@@
 %     \begin{centering}
-%         \includegraphics[width=0.49\linewidth]{spot_y1bs_timeseries.pdf}
-%         \includegraphics[width=0.49\linewidth]{spot_y1bs_rect.pdf}
+%         \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_timeseries.pdf}
+%         \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_rect.pdf}
 %         \\[0.5em]
-%         \includegraphics[width=0.405\linewidth]{spot_y1bs_baseline.pdf}
-%         \includegraphics[width=0.575\linewidth]{spot_y1bs_coeffs.pdf}
+%         \includegraphics[width=0.405\linewidth]{figures/spot_y1bs_baseline.pdf}
+%         \includegraphics[width=0.575\linewidth]{figures/spot_y1bs_coeffs.pdf}
 %         \\[0.5em]
-%         \includegraphics[width=0.98\linewidth]{spot_y1bs_spectrum.pdf}
+%         \includegraphics[width=0.98\linewidth]{figures/spot_y1bs_spectrum.pdf}
 %         \caption{%
@@
 %     \begin{centering}
-%         \includegraphics[width=0.49\linewidth]{spot_y1bs_low_snr_timeseries.pdf}
-%         \includegraphics[width=0.49\linewidth]{spot_y1bs_low_snr_rect.pdf}
+%         \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_low_snr_timeseries.pdf}
+%         \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_low_snr_rect.pdf}
 %         \\[0.5em]
-%         \includegraphics[width=0.405\linewidth]{spot_y1bs_low_snr_baseline.pdf}
-%         \includegraphics[width=0.575\linewidth]{spot_y1bs_low_snr_coeffs.pdf}
+%         \includegraphics[width=0.405\linewidth]{figures/spot_y1bs_low_snr_baseline.pdf}
+%         \includegraphics[width=0.575\linewidth]{figures/spot_y1bs_low_snr_coeffs.pdf}
 %         \\[0.5em]
-%         \includegraphics[width=0.98\linewidth]{spot_y1bs_low_snr_spectrum.pdf}
+%         \includegraphics[width=0.98\linewidth]{figures/spot_y1bs_low_snr_spectrum.pdf}
 %         \caption{%
@@
 Because the problem is generally not convex, we need a good starting guess for either the spectrum or the map coefficients. 
-We note that we can very crudely approximate the rest frame spectrum by deconvolving the average observed spectrum with the first term of the convolution kernel $\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{kT00.pdf}}).
+We note that we can very crudely approximate the rest frame spectrum by deconvolving the average observed spectrum with the first term of the convolution kernel $\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{figures/kT00.pdf}}).
 In practice, this is a fairly poor approximation, but we find that it suffices as an initial guess. 
@@
 %     \begin{centering}
-%         \includegraphics[width=\linewidth]{twospec.pdf}
+%         \includegraphics[width=\linewidth]{figures/twospec.pdf}
 %         \caption{%
@@
 We also recover the two spectral components, although our solution for $\bvec{s_2}$ is significantly better than that for $\bvec{s_1}$. 
-This is due to the fact that the only information about $\bvec{s_1}$ that makes it into our dataset is the convolution of $\bvec{s_1}$ with the first term of the convolution kernel $\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{kT00.pdf}}), since this spectral component has no spatial variability.
+This is due to the fact that the only information about $\bvec{s_1}$ that makes it into our dataset is the convolution of $\bvec{s_1}$ with the first term of the convolution kernel $\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{figures/kT00.pdf}}), since this spectral component has no spatial variability.
 Since the deconvolution operation is in general ill-posed, there is no unique solution for $\bvec{s_1}$. 
@@
 %     \begin{centering}
-%         \includegraphics[width=0.98\linewidth]{snr.pdf}
+%         \includegraphics[width=0.98\linewidth]{figures/snr.pdf}
 %         \caption{%
@@
 %     \begin{centering}
-%         \includegraphics[width=0.98\linewidth]{inclinations.pdf} % 
+%         \includegraphics[width=0.98\linewidth]{figures/inclinations.pdf} % 
 %         \caption{%

### 2021-09-08 figures/todo/spot_y1bs.py

@@ -1,38 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Solve the SPOT problem.
-
-In this case, we know nothing: we're going to learn
-both the map and the spectrum. We're not giving the
-algorithm an initial guess, either: the spectrum is
-learned by deconvolving the data, and the initial
-guess for the map is computed via the linearized
-problem.
-
-"""
-import paparazzi as pp
-import numpy as np
-from utils.spot import plot_results
-
-np.random.seed(13)
-
-# Let's plot the high SNR case for the paper
-ferr = 1e-4
-T = 5000.0
-niter = 3000
-lr = 2.5e-5
-dlogT = -0.04
-
-# Generate data
-dop = pp.Doppler(ydeg=15, u=[0.5, 0.25])
-dop.generate_data(ferr=ferr)
-
-# Reset all coefficients
-dop.y1 = None
-dop.s = None
-
-# Solve!
-loss, cho_y1, cho_s = dop.solve(niter=niter, lr=lr, T=T, dlogT=dlogT)
-
-# Plot the results
-plot_results(dop, name="spot_y1bs", loss=loss, cho_y1=cho_y1, cho_s=cho_s)

### 2021-09-08 src/ms.tex
working on ms

@@
 %
-Let $I(\lnlam, \x, t, \Dargs)$ be the specific intensity observed at log wavelength $\lnlam \equiv \ln\frac{\lambda}{\lambda_\mathrm{r}}$ and at sky-projected Cartesian position $\x = (x, y, z)$ on the surface of the star at time $t$, where $\Dargs$ is a set of arbitrary parameters of the Doppler field and $\lambda_\mathrm{r}$ is a reference wavelength.
+Let $I(\lnlam, \x, t)$ be the specific intensity observed at log wavelength $\lnlam \equiv \ln\frac{\lambda}{\lambda_\mathrm{r}}$ and at sky-projected Cartesian position $\x = (x, y, z)$ on the surface of the star at time $t$, where $\lambda_\mathrm{r}$ is a reference wavelength.
 We may express this intensity as
@@
     \label{eq:the_problem:Ixi}
-    I(\lnlam, \x, t, \Dargs) & =
-    I\Big(\lnlam_0 + \D(\x, \Dargs), \x, t\Big)
+    I(\lnlam, \x, t) & =
+    I\Big(\lnlam_0 + \D(\x), \x, t\Big)
 \end{align}
@@
     \label{eq:the_problem:D}
-    \D(\x, \Dargs)
+    \D(\x)
      & =
     \frac{1}{2}\ln\left(
-    \frac{1 + \beta(\x, \Dargs)}{1 - \beta(\x,
-            \Dargs)}
+    \frac{1 + \beta(\x)}{1 - \beta(\x)}
     \right)
@@
 %
-where $\beta = v(\x, \Dargs) / c$ is the ratio of the radial velocity at a point on the surface of the star to the speed of light.
+where $\beta = v(\x) / c$ is the ratio of the radial velocity at a point on the surface of the star to the speed of light.
 In keeping with the literature, we take positive values of $v$ (and $\D$) to mean redshifts.
@@
     \label{eq:the_problem:F}
-    F(\lnlam, t, \Dargs)
+    F(\lnlam, t)
      & \equiv
     \iint\limits_{\Surf(\x)}
-    I(\lnlam, \x, t, \Dargs)
+    I(\lnlam, \x, t)
     \mathrm{d}{\Surf(\x)}
-    \quad ,
-\end{align}
-%
-The difficulty in solving Equation~(\ref{eq:the_problem:F}) stems from the fact that $I(\lnlam, \x, t, \Dargs)$ is difficult to write down in closed form, given the nonlinearity of the Doppler shift.
+    \quad,
+\end{align}
+%
+The difficulty in solving Equation~(\ref{eq:the_problem:F}) stems from the fact that $I(\lnlam, \x, t)$ is difficult to write down in closed form, given the nonlinearity of the Doppler shift.
 The standard approach to solving this integral is therefore to discretize the surface of the star with a fine grid, evaluate the Doppler-shifted spectrum in each cell, and sum over the spatial axes to approximate the integral.
@@
     \label{eq:deconv:convolution}
-    I(\lnlam, \x, t, \Dargs) & =
+    I(\lnlam, \x, t) & =
     I(\lnlam_0, \x, t)
     *
-    \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
+    \delta\big(\lnlam_0 + \D(\x)\big)
 \end{align}
@@
     \ylmbasis(\x) \,
-    \alm(\lnlam_0, t)
+    \almt(\lnlam_0, t)
     \quad ,
@@
 \begin{align}
-    \label{eq:deconv:alm}
-    \alm(\lnlam_0, t) \equiv
+    \label{eq:deconv:almt}
+    \almt(\lnlam_0, t) \equiv
     \Big(
@@
     \label{eq:deconv:R}
-    \alm(\lnlam_0, t) = \R(t) \, \azero(\lnlam_0)
+    \almt(\lnlam_0, t) = \R(t) \, \alm(\lnlam_0)
     \quad ,
@@
 %
-where $\azero(\lnlam_0) = \bvec{a}(\lnlam_0, t=t_0)$ for some reference time $t_0$.
+where $\alm(\lnlam_0) = \bvec{a}(\lnlam_0, t=t_0)$ for some reference time $t_0$.
 For rigid body rotation, the result is exact and $\R(t)$ is the $(N \times N)$ Wigner rotation matrix for real spherical harmonics
@@
     \,
-    \azero(\lnlam_0)
+    \alm(\lnlam_0)
     \quad ,
@@
     \label{eq:deconv:F2d}
-    F(\lnlam, t, \Dargs) & =
+    F(\lnlam, t) & =
     \iint\limits_{\Surf(\x)}
@@
     \,
-    \alm(\lnlam_0)
-    * \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
+    \almt(\lnlam_0)
+    * \delta\big(\lnlam_0 + \D(\x)\big)
     \mathrm{d}\Surf(\x)
@@
     \ylmbasis(\x)
-    \delta\big(\lnlam_0 + \D(\x, \Dargs)\big)
+    \delta\big(\lnlam_0 + \D(\x)\big)
     \mathrm{d}\Surf(\x)
@@
      & =
-    \int\limits_{\Curve(\lnlam, \x, \Dargs)}
+    \int\limits_{\Curve(\lnlam, \x)}
     \hspace*{-0.6em}\ylmbasis(\x)
-    \mathrm{d}\Curve(\lnlam, \x, \Dargs)
+    \mathrm{d}\Curve(\lnlam, \x)
     \nonumber                     \\[0.5em]
-     & \equiv \kT(\lnlam, \Dargs)
+     & \equiv \kT(\lnlam)
     \quad.
@@
 %
-where the path $\Curve(\lnlam, \x, \Dargs)$ corresponds to the set of all points on the visible disk where $\lnlam_0 + \D(\x, \Dargs) = 0$.
+where the path $\Curve(\lnlam, \x)$ corresponds to the set of all points on the visible disk where $\lnlam_0 + \D(\x) = 0$.
 %
@@
     \label{eq:deconv:F}
-    F(\lnlam, t, \Dargs)
-     & =
-    \kT(\lnlam, \Dargs) \, \R(t)
+    F(\lnlam, t)
+     & =
+    \kT(\lnlam) \, \R(t)
     *
-    \azero(\lnlam_0)
+    \alm(\lnlam_0)
     \quad.
@@
     \label{eq:kT:beta}
-    \beta(\x, \Dargs) = \frac{\omega \sin i \, x}{c}
+    \beta(\x) = \frac{\omega \sin i \, x}{c}
 \end{align}
@@
     \label{eq:kT:D}
-    \D(\x, \Dargs) & =
+    \D(\x) & =
     \frac{1}{2}\ln\left(
@@
 %
-where the parameters $\Dargs$ of the Doppler field are the angular velocity, $\omega$, and the inclination of the star with respect to $\hat{y}$, $i$.
+where $\omega$ is the stellar angular velocity and $i$ is the stellar inclination with respect to $\hat{y}$.
 
@@
 
-If we assume the star is unocculted, the region of integration $\Surf(\x)$ in Equation~(\ref{eq:deconv:kT}) is simply the unit disk, so $\Curve(\lnlam, \x, \Dargs)$ is the set of all points that satisfy both $\lnlam_0 + \D(\x, \Dargs) = 0$ and $x^2 + y^2 \le 1$.
-Solving Equation~(\ref{eq:kT:D}) for $x$, we find that the curves $\Curve(\lnlam, \x, \Dargs)$ are simply vertical lines on the unit disk given by
+If we assume the star is unocculted, the region of integration $\Surf(\x)$ in Equation~(\ref{eq:deconv:kT}) is simply the unit disk, so $\Curve(\lnlam, \x)$ is the set of all points that satisfy both $\lnlam_0 + \D(\x) = 0$ and $x^2 + y^2 \le 1$.
+Solving Equation~(\ref{eq:kT:D}) for $x$, we find that the curves $\Curve(\lnlam, \x)$ are simply vertical lines on the unit disk given by
 %
@@
     \label{eq:kT:kT}
-    \kT(\lnlam, \Dargs)
+    \kT(\lnlam)
      & =
@@
     \ylmbasis
-    \Big(x, y\Big)
+    (x, y)
     \mathrm{d}y
@@
 The stellar rest frame spectrum $I(\lnlam_0)$ is taken to be a single Gaussian absorption line that is spatially constant everywhere save for a multiplicative factor equal to the local spot intensity.
-This corresponds to a spectral/spatial expansion vector $\azero(\lnlam_0)$ whose coefficient at degree $l$ and order $m$ is equal to $y_{lm} I(\lnlam_0)$.
+This corresponds to a spectral/spatial expansion vector $\alm(\lnlam_0)$ whose coefficient at degree $l$ and order $m$ is equal to $y_{lm} I(\lnlam_0)$.
 In the Figure, we rotated the star about an axis perpendicular to the line of sight (left panel) and computed the observed spectrum using Equation~(\ref{eq:deconv:F}) (center panel). 
@@
 Figure~\ref{fig:compare} shows one of the spectra in Figure~\ref{fig:spot}, this time computed using both our formulae (blue line) and the traditional technique of discretizing the stellar surface, Doppler-shifting the spectrum in each grid cell according to the local radial velocity, interpolating back to a uniform wavelength grid, and summing over the spatial dimension (dotted orange line).
-We show the residuals in the lower panel, where it is clear that as the number of grid cells increases from 2,000 (light grey) to 71,000 (dark grey), the numerical solution approaches the solution obtained using our approach.
+We show the residuals in the lower panel, where it is clear that as the number of grid cells increases from $10^2$ (light grey) to $10^5$ (dark grey), the numerical solution approaches the solution obtained using our approach.
 
@@
             The problem setup is the same as that in Figure~\ref{fig:spot}. 
-            The boottom panel shows the absolute value of the difference between the two spectra for different number of grid points in the numerical solution.
+            The bottom panel shows the absolute value of the difference between the two spectra for different number of grid points in the numerical solution.
             As the number of grid points increases, the numerical solution approaches the \starry solution.
@@
 
-Given this formulation, we may re-write Equation~(\ref{eq:deconv:F}) as a purely linear operation on $\azero(\lnlam_0)$:
+Given this formulation, we may re-write Equation~(\ref{eq:deconv:F}) as a purely linear operation on $\alm(\lnlam_0)$:
 %
@@
     \,
-    \azero
+    \alm
     \quad,
@@
 %
-where $\Doppler_m$ is a $(K \times N K')$ matrix constructed by horizontally concatenating the Toeplitz matrices for each of the $N$ components of the convolution kernel $\kT(\lnlam, \Dargs)$ transformed by the rotation matrix $\bvec{R}(t)$ evaluated at time $t = t_m$:
+where $\Doppler_m$ is a $(K \times N K')$ matrix constructed by horizontally concatenating the Toeplitz matrices for each of the $N$ components of the convolution kernel $\kT(\lnlam)$ transformed by the rotation matrix $\bvec{R}(t)$ evaluated at time $t = t_m$:
 %
@@
     \begin{pmatrix}
-        \quad
         \bvec{T}(\kT_0)
@@
 %
-The $(K \times 1)$ vector $\mathbf{f}_m$ is the model for the flux observed at each wavelength at time $t = t_m$, and the $(N K' \times 1)$ vector $\azero$ is the vector representation of the spatially-dependent spectrum of the star.
-The latter is constructed by flattening the spherical harmonic expansion of the star such that the first $K'$ terms in $\azero$ correspond to the the values of $(a_0)_{0,0}$ at each wavelength $\lnlam_0$, followed by the values of $(a_0)_{1,-1}$ at each wavelength, and so forth.
+The $(K \times 1)$ vector $\mathbf{f}_m$ is the model for the flux observed at each wavelength at time $t = t_m$, and the $(N K' \times 1)$ vector $\alm$ is the vector representation of the spatially-dependent spectrum of the star.
+The latter is constructed by flattening the spherical harmonic expansion of the star such that the first $K'$ terms in $\alm$ correspond to the the values of $a_{0,0}$ at each wavelength $\lnlam_0$, followed by the values of $a_{1,-1}$ at each wavelength, and so forth.
 
@@
 %
-Equation~(\ref{eq:linear:f}) represents the full linearization of the problem, where we have expressed the quantity we can observe, $\bvec{f}$, as a linear operation on the quantity of interest, the spectral/spatial decomposition of the stellar surface, $\azero$.
+Equation~(\ref{eq:linear:f}) represents the full linearization of the problem, where we have expressed the quantity we can observe, $\bvec{f}$, as a linear operation on the quantity of interest, the spectral/spatial decomposition of the stellar surface, $\alm$.
 Figure~\ref{fig:linalg} shows an example of $\Doppler$.
@@
 %
-In the previous section we showed how to express the data vector $\bvec{f}$, a series of spectra obtained at different epochs, as a purely linear operation on the map vector $\azero$, the spherical harmonic decomposition of the specific intensity on the surface of the star.
-The advantage of this linearity is that, given suitable priors, it allows one to compute both the maximum likelihood solution for $\azero$ and its uncertainty \emph{analytically}. 
-In particular, if one places a (multidimensional) Gaussian prior on $\azero$ with mean $\boldsymbol{\mu}_\mathbf{a_0}$ and covariance $\boldsymbol{\Lambda}_\mathbf{a_0}$, the maximum \emph{a posteriori} (MAP)
-solution for $\azero$ is
+In the previous section we showed how to express the data vector $\bvec{f}$, a series of spectra obtained at different epochs, as a purely linear operation on the map vector $\alm$, the spherical harmonic decomposition of the specific intensity on the surface of the star.
+The advantage of this linearity is that, given suitable priors, it allows one to compute both the maximum likelihood solution for $\alm$ and its uncertainty \emph{analytically}. 
+In particular, if one places a (multidimensional) Gaussian prior on $\alm$ with mean $\boldsymbol{\mu}_\mathbf{a}$ and covariance $\boldsymbol{\Lambda}_\mathbf{a}$, the maximum \emph{a posteriori} (MAP)
+solution for $\alm$ is
 %
@@
     \label{eq:inverse:ahat}
-    \bvec{\hat{a}_0} & =
-    \boldsymbol{\Sigma}_\mathbf{\hat{a}_0}
+    \bvec{\hat{a}} & =
+    \boldsymbol{\Sigma}_\mathbf{\hat{a}}
     \left(
@@
     +
-    {\boldsymbol{\Lambda}_{\azero}}^{-1} \boldsymbol{\mu}_\mathbf{a_0}
+    {\boldsymbol{\Lambda}_{\alm}}^{-1} \boldsymbol{\mu}_\mathbf{a}
     \right)
@@
     \label{eq:inverse:acov}
-    \boldsymbol{\Sigma}_\mathbf{\hat{a}_0} & =
+    \boldsymbol{\Sigma}_\mathbf{\hat{a}} & =
     \left(
@@
     +
-    {\boldsymbol{\Lambda}_{\azero}}^{-1}
+    {\boldsymbol{\Lambda}_{\alm}}^{-1}
     \right)^{-1}
@@
 where $\boldsymbol{\Sigma}_\mathbf{f}$ is the data covariance matrix. 
-These equations require the inversion of a few fairly large matrices, but as we will see later, it allows one to obtain the map of the star ($\bvec{\hat{a}_0}$) and its uncertainty ($\boldsymbol{\Sigma}_{\mathbf{\hat{a}_0}}$) in under a second for a typical dataset.
-
-There is, however, a catch: for most practical purposes, it is difficult to find a good Gaussian prior for $\bvec{a_0}$. 
+These equations require the inversion of a few fairly large matrices, but as we will see later, it allows one to obtain the map of the star ($\bvec{\hat{a}}$) and its uncertainty ($\boldsymbol{\Sigma}_{\mathbf{\hat{a}}}$) in under a second for a typical dataset.
+
+There is, however, a catch: for most practical purposes, it is difficult to find a good Gaussian prior for $\bvec{a}$. 
 Usually we will have some prior information on what the spectrum of the star is, and perhaps some prior information on the distribution of surface features such as starspots. 
-The problem is that even if these priors are Gaussian, the corresponding prior on $\bvec{a_0}$ is \emph{not}. 
+The problem is that even if these priors are Gaussian, the corresponding prior on $\bvec{a}$ is \emph{not}. 
 To understand this, consider the case where the stellar rest frame spectrum is spatially constant, save for an amplitude that is spatially variable. 
 We can then describe the rest frame spectrum by the $(K' \times 1)$ vector $\bvec{s}$ and the amplitude by the $(N \times 1)$ vector $\bvec{y}$ representing the spherical harmonic expansion of the intensity profile of the star.
-The vector $\azero$ is then given by the (flattened) outer product of the two vectors:
-%
-\begin{align}
-    \label{eq:inverse:azero}
-    \azero & = \mathrm{vec}\left( \bvec{A_0} \right) \nonumber             \\
+The vector $\alm$ is then given by the (flattened) outer product of the two vectors:
+%
+\begin{align}
+    \label{eq:inverse:alm}
+    \alm & = \mathrm{vec}\left( \bvec{A} \right) \nonumber             \\
            & = \mathrm{vec}\left( \bvec{s} \, \bvec{y}^\top \right) \quad,
@@
 %
-where $\mathrm{vec}$ denotes the vectorization operation, which in this case transforms the $(K' \times N)$ matrix $\bvec{A_0}$ into the $(N K' \times 1)$ column vector $\azero$ by vertically stacking all of its columns.
-In other words, the vector $\azero$ consists of the set of $K'$ intensities in each wavelength bin repeated $N$ times, each time multiplied by the $n^\mathrm{th}$ spherical harmonic coefficient in the expansion of the surface intensity.
-Returning to our point about priors, note that all of the entries of $\azero$ are the product of two independent random variables. 
+where $\mathrm{vec}$ denotes the vectorization operation, which in this case transforms the $(K' \times N)$ matrix $\bvec{A}$ into the $(N K' \times 1)$ column vector $\alm$ by vertically stacking all of its columns.
+In other words, the vector $\alm$ consists of the set of $K'$ intensities in each wavelength bin repeated $N$ times, each time multiplied by the $n^\mathrm{th}$ spherical harmonic coefficient in the expansion of the surface intensity.
+Returning to our point about priors, note that all of the entries of $\alm$ are the product of two independent random variables. 
 Since the product of two random variables is generally non-Gaussian, even when the variables themselves are Gaussian%
 \footnote{see, e.g., \url{http://mathworld.wolfram.com/NormalProductDistribution.html}}%
-, so too is the prior on $\azero$. 
-This point makes Equation~(\ref{eq:inverse:ahat}) of little practical use, since a multivariate Gaussian will not generally be a suitable prior for $\azero$.
+, so too is the prior on $\alm$. 
+This point makes Equation~(\ref{eq:inverse:ahat}) tricky to use in practice, since a multivariate Gaussian is not generally the most suitable prior for $\alm$.
 
 That said, a Gaussian prior \emph{is} typically suitable for both the spectrum $\bvec{s}$ and the intensity $\bvec{y}$ (just not their product). 
-It is straightforward to show that because Equation~(\ref{eq:linear:f}) is linear in $\azero$, it is also linear in both $\bvec{s}$ and $\bvec{y}$, so MAP solutions can be found analytically for $\bvec{s}$ (conditioned on $\bvec{y}$) and $\bvec{y}$ (conditioned on $\bvec{s}$).
+It is straightforward to show that because Equation~(\ref{eq:linear:f}) is linear in $\alm$, it is also linear in both $\bvec{s}$ and $\bvec{y}$, so MAP solutions can be found analytically for $\bvec{s}$ (conditioned on $\bvec{y}$) and $\bvec{y}$ (conditioned on $\bvec{s}$).
 We investigate these solutions below.
@@
 is a $(NK' \times N)$ block matrix constructed by repeating the column vector $\bvec{s}$ $N$ times in blocks along the main diagonal.
-Before we solve this equation for $\bvec{y}$, we note that in practice it is convenient to fix the coefficient of the $Y_{0,0}$ spherical harmonic, $y_0$, to unity. 
-After all, this coefficient is not directly constrained by the data, as it merely sets the baseline intensity on the surface of the star and is therefore formally degenerate with the stellar luminosity (which also cannot be directly inferred from the data).
-This choice further ensures a mean baseline of unity for the model vector $\mathbf{f}$. 
-We may therefore write
-%
-\begin{align}
-    \label{eq:inverse:fy1}
+%
+Given prior mean $\boldsymbol{\mu}_\bvec{y}$ and covariance $\boldsymbol{\Lambda}_\bvec{y}$ on $\bvec{y}$, the MAP solution is given by
+%
+\begin{align}
+    \label{eq:inverse:y1hat}
+    \bvec{\hat{y}} & =
+    \boldsymbol{\Sigma}_\mathbf{\hat{y}}
+    \left(
+    \bvec{S}^\top\Doppler^\top
+    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
     \bvec{f}
-     & =
-    \Doppler
-    \,
-    \bvec{s}_\bvec{0}
-    \,
     +
-    \,
-    \Doppler
-    \,
-    \bvec{S_1}
-    \,
-    \bvec{y}_\bvec{1}
-    \quad,
-\end{align}
-%
-where the vector $\bvec{s_0}$ denotes the first column of $\bvec{S}$, the matrix $\bvec{S_1}$ denotes the remaining columns of $\bvec{S}$, and $\bvec{y_1}$ is the quantity we wish to solve for: the vector of spherical harmonic coefficients of degree $l \ge 1$.
-
-Given prior mean $\boldsymbol{\mu}_\bvec{y_1}$ and covariance $\boldsymbol{\Lambda}_\bvec{y_1}$ on $\bvec{y_1}$, the MAP solution is given by
-%
-\begin{align}
-    \label{eq:inverse:y1hat}
-    \bvec{\hat{y}_1} & =
-    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1}
-    \left(
-    \bvec{S_1}^\top\Doppler^\top
-    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
-    \left(\bvec{f} - \Doppler\bvec{s}_\bvec{0}\right)
-    +
-    {\boldsymbol{\Lambda}_\bvec{y_1}}^{-1} \boldsymbol{\mu}_\bvec{y_1}
+    {\boldsymbol{\Lambda}_\bvec{y}}^{-1} \boldsymbol{\mu}_\bvec{y}
     \right)
@@
     \label{eq:inverse:y1cov}
-    \boldsymbol{\Sigma}_\bvec{\hat{y}_1} & =
+    \boldsymbol{\Sigma}_\bvec{\hat{y}} & =
     \left(
-    \bvec{S_1}^\top\Doppler^\top
+    \bvec{S}^\top\Doppler^\top
     {\boldsymbol{\Sigma}_\bvec{f}}^{-1}
-    \Doppler\bvec{S_1}
+    \Doppler\bvec{S}
     +
-    {\boldsymbol{\Lambda}_\bvec{y_1}}^{-1}
+    {\boldsymbol{\Lambda}_\bvec{y}}^{-1}
     \right)^{-1}
@@
 %
-If we choose a prior with zero mean ($\boldsymbol{\mu}_\bvec{y_1} = 0$)
+If we choose a prior with zero mean ($\boldsymbol{\mu}_\bvec{y} = 0$)
 and a diagonal covariance that is constant for each spherical harmonic order $m$,
@@
 \begin{align}
-    \boldsymbol{\Lambda}_\bvec{y_1} & =
+    \boldsymbol{\Lambda}_\bvec{y} & =
     \mathrm{diag} \left(
+    \sigma_0^2
+    \quad\quad\quad\quad
     \sigma_1^2
@@
     \begin{pmatrix}
-        y_0\, \bvec{I}_{K'} \\
-        y_1\, \bvec{I}_{K'} \\
-        y_2\, \bvec{I}_{K'} \\
-        y_3\, \bvec{I}_{K'} \\
+        y_{0,0}\, \bvec{I}_{K'} \\
+        y_{1,-1}\, \bvec{I}_{K'} \\
+        y_{1,0}\, \bvec{I}_{K'} \\
+        y_{1,1}\, \bvec{I}_{K'} \\
         \cdots
@@
 
-However, as we mentioned above, the Doppler imaging problem can be solved analytically for either the surface map or the spectrum, but not both. 
+However, as we mentioned above, the Doppler imaging problem can be solved analytically for either the surface map or the spectrum, but not typically both. 
 If neither are known exactly \emph{a priori}, which is quite often the case, we can still find the MAP solution quickly by guessing at an initial spectrum $\bvec{s}$ and iterating between optimizing for $\bvec{y}$ and optimizing for $\bvec{s}$.
@@
 However, what is not shown in the figure is the fact that overall, the star also gets \emph{dimmer}: the continuum level drops in the presence of the spot. 
-Unfortunately, spectrographs are not usually designed to measure this, since the change in the star's overall brightness from one observation to the next is often dwarfed by (unknown) changes in the spectrograph sensitivity.
+Unfortunately, spectrographs are not usually designed to measure this, since the change in the star's overall brightness from one observation to the next is often dwarfed by (unknown) changes in the spectrograph sensitivity, cloud cover, etc.
 For this reason, the spectra are usually normalized to have a fixed baseline continuum, and Equation~\ref{eq:linear:f} is no longer a good model for the data.
@@
 However, when this is not an option, our model for $\bvec{f}$ (Equation~\ref{eq:linear:f}) must be amended.
+
+\xxx{WORK IN PROGRESS BELOW HERE}
+
 %
@@
         \,
-        \azero
+        \alm
     } {
@@
 where $\bvec{b}$ is the baseline and the vector division is performed elementwise. 
-When $\azero$ is given by Equation~(\ref{eq:inverse:azero}), the baseline $\bvec{b}$ is simply the total (wavelength-integrated) flux at each epoch, repeated for every element in each spectrum.
+When $\alm$ is given by Equation~(\ref{eq:inverse:alm}), the baseline $\bvec{b}$ is simply the total (wavelength-integrated) flux at each epoch, repeated for every element in each spectrum.
 Based on \citet{Luger2019}, this can be computed as a purely linear operation on the spherical harmonic vector $\bvec{y}$:
@@
 %
-In our discussion so far we have focused on the particular case where the spectral/spatial decomposition of the stellar surface can be expressed as the outer product of two vectors (Equation~\ref{eq:inverse:azero}).
+In our discussion so far we have focused on the particular case where the spectral/spatial decomposition of the stellar surface can be expressed as the outer product of two vectors (Equation~\ref{eq:inverse:alm}).
 As we mentioned previously, this corresponds to the case where the spectrum is constant across the surface of the star except for a spatially-variable amplitude: i.e., spots have the same spectrum as the rest of the star, but emit less flux overall.
 However, most of the formalism developed here also applies to the more general case where the spectrum at a particular point on the surface of the star is a linear combination of several different spectral components.
-In this case, the map vector $\azero$ may be written as the sum over $J$ spectra $\bvec{s}_j$, each of which is dotted into a different vector of spherical harmonic coefficients $\bvec{y}_j^\top$:
-%
-\begin{align}
-    \label{eq:eigen:azero}
-    \azero
+In this case, the map vector $\alm$ may be written as the sum over $J$ spectra $\bvec{s}_j$, each of which is dotted into a different vector of spherical harmonic coefficients $\bvec{y}_j^\top$:
+%
+\begin{align}
+    \label{eq:eigen:alm}
+    \alm
      & =
@@
 Given $\bvec{y_1}$ and $\bvec{s}$, we use Equations~(\ref{eq:deconv:F}) and~%
-(\ref{eq:inverse:azero}) to compute the data vector $\bvec{f}$ at $M = 16$ equally spaced rotational phases; these phases are shown in orthographic projection (as an observer would see the star) in the center panel of Figure~\ref{fig:spot_setup}.
+(\ref{eq:inverse:alm}) to compute the data vector $\bvec{f}$ at $M = 16$ equally spaced rotational phases; these phases are shown in orthographic projection (as an observer would see the star) in the center panel of Figure~\ref{fig:spot_setup}.
 The synthetic spectra for each phase are shown as the orange curves in the bottom panel of the figure (note the different scaling, as all spectral lines become shallower due to the broadening). 
@@
 
-The problem setup is the same as that discussed in \S\ref{sec:eigen}, where our full map vector $\bvec{a_0}$ is the outer product of a spectral matrix $\mathbb{S}$, whose $J$ columns are the different spectral components, and a spherical harmonic coefficient matrix $\mathbb{Y}^\top$, whose $J$ rows are the corresponding coefficient vectors.
+The problem setup is the same as that discussed in \S\ref{sec:eigen}, where our full map vector $\bvec{a}$ is the outer product of a spectral matrix $\mathbb{S}$, whose $J$ columns are the different spectral components, and a spherical harmonic coefficient matrix $\mathbb{Y}^\top$, whose $J$ rows are the corresponding coefficient vectors.
 For simplicity, in this experiment we consider only $J = 2$ spectral components and further require that the first component is spatially constant, i.e., the first row of $\mathbb{Y}^\top$ is the vector $(1 \quadquad \bvec{0}^\top)$.
@@
     \label{eq:appendix:kT}
-    \kT(\lnlam, \Dargs)
+    \kT(\lnlam)
      & =
@@
      & \equiv
-    \rhoT(\lnlam, \Dargs)
+    \rhoT(\lnlam)
     \,
@@
 %
-We may now explicitly write down the $n^\mathrm{th}$ term of the vector $\rhoT(\lnlam, \Dargs)$ in Equation~(\ref{eq:appendix:kT}),
+We may now explicitly write down the $n^\mathrm{th}$ term of the vector $\rhoT(\lnlam)$ in Equation~(\ref{eq:appendix:kT}),
 %
@@
     \label{eq:kT:sTexpression}
-    \rho_n(\lnlam, \Dargs)
-     & =
-    \rho_{i,\,j,\,k}(\lnlam, \Dargs)
+    \rho_n(\lnlam)
+     & =
+    \rho_{i,\,j,\,k}(\lnlam)
     =
@@
         $a_{lm}$                                            & spectral spherical harmonic coefficient                      & Equation~(\ref{eq:deconv:Ixi0})            \\
-        $\alm$                                              & vector of spectral spherical harmonic coefficients           & Equation~(\ref{eq:deconv:alm})             \\
-        $\bvec{a_0}$                                        & $\alm$ at reference time $t = t_0$                           & Equation~(\ref{eq:deconv:R})               \\
-        $\bvec{A_0}$                                        & matrix form of $\bvec{a_0}$                                  & Equation~(\ref{eq:inverse:azero})          \\
+        $\almt$                                              & vector of spectral spherical harmonic coefficients           & Equation~(\ref{eq:deconv:almt})             \\
+        $\bvec{a}$                                        & $\almt$ at reference time $t = t_0$                           & Equation~(\ref{eq:deconv:R})               \\
+        $\bvec{A}$                                        & matrix form of $\bvec{a}$                                  & Equation~(\ref{eq:inverse:alm})          \\
         $\bvec{b}$                                          & flux baseline vector                                         & Equation~(\ref{eq:norm:b})                 \\
@@
         $\Curve$                                            & curve of constant radial velocity                            & Equation~(\ref{eq:deconv:kT})              \\
-        $\Dargs$                                            & parameters of the Doppler field                              & \S\ref{sec:the_problem}                    \\
         $\D$                                                & logarithmic Doppler shift                                    & Equation~(\ref{eq:the_problem:D})          \\
@@
         $\bvec{R}$                                          & Wigner rotation matrix                                       & Equation~(\ref{eq:deconv:R})               \\
-        $\bvec{s}$                                          & vector representation of the spectrum                        & Equation~(\ref{eq:inverse:azero})          \\
+        $\bvec{s}$                                          & vector representation of the spectrum                        & Equation~(\ref{eq:inverse:alm})          \\
         $\bvec{S}$                                          & block matrix representation of $\bvec{s}$                    & Equation~(\ref{eq:inverse:S})              \\
-        $\boldsymbol{\mathbb{S}}$                           & matrix of $J$ spectral components                            & Equation~(\ref{eq:eigen:azero})            \\
+        $\boldsymbol{\mathbb{S}}$                           & matrix of $J$ spectral components                            & Equation~(\ref{eq:eigen:alm})            \\
         $\Surf$                                             & projected visible area of the star                           & Equation~(\ref{eq:the_problem:F})          \\
@@
         $y_{lm}$                                            & spherical harmonic coefficient                               & \S\ref{sec:inverse}                        \\
-        $\bvec{y}$                                          & vector of spherical harmonic coefficients                    & Equation~(\ref{eq:inverse:azero})          \\
+        $\bvec{y}$                                          & vector of spherical harmonic coefficients                    & Equation~(\ref{eq:inverse:alm})          \\
         $Y_{lm}$                                            & spherical harmonic                                           & Equation~(\ref{eq:deconv:Ixi0})            \\
         $\bvec{Y}$                                          & block matrix representation of $\bvec{y}$                    & Equation~(\ref{eq:inverse:Y})              \\
-        $\boldsymbol{\mathbb{Y}}$                           & matrix of $J$ spherical harmonic components                  & Equation~(\ref{eq:eigen:azero})            \\
+        $\boldsymbol{\mathbb{Y}}$                           & matrix of $J$ spherical harmonic components                  & Equation~(\ref{eq:eigen:alm})            \\
         %
@@
         $\mathrm{diag}$                                     & diagonal matricization                                       & Equation~(\ref{eq:ld:Dmwav})               \\
-        $\mathrm{vec}$                                      & vectorization                                                & Equation~(\ref{eq:inverse:azero})          \\
+        $\mathrm{vec}$                                      & vectorization                                                & Equation~(\ref{eq:inverse:alm})          \\
         $*$                                                 & convolution                                                  & Equation~(\ref{eq:deconv:convolution_def}) \\

### 2021-09-09 src/ms.tex
writing

@@
 %interpolation. 
-Should we expect the numerical solution to actually \emph{converge}
+%Should we expect the numerical solution to actually \emph{converge}
 %to the \starry solution, or is the way the two are interpolating fundamentally
@@
 One option is to collect simultaneous photometry on the target in a band similar to the wavelength range observed, and use this light curve to (un-)normalize the spectral timeseries $\bvec{f}$. 
-However, when this is not an option, our model for $\bvec{f}$ (Equation~\ref{eq:linear:f}) must be amended.
-
-\xxx{WORK IN PROGRESS BELOW HERE}
-
+However, when this is not an option, our model for $\bvec{f}$ (Equation~\ref{eq:linear:f}) must be amended:
 %
@@
     \label{eq:norm:f}
-    \bvec{f}
+    \fnorm
+     & =
+     \frac{
+        \mathbf{f}
+    } {
+        \bvec{B}
+        \,
+        \alm
+    }
+    \nonumber 
+    \\[1em]
     & =
@@
     } {
-        \bvec{b}
+        \bvec{B}
+        \,
+        \alm
     }
@@
 %
-where $\bvec{b}$ is the baseline and the vector division is performed elementwise. 
-When $\alm$ is given by Equation~(\ref{eq:inverse:alm}), the baseline $\bvec{b}$ is simply the total (wavelength-integrated) flux at each epoch, repeated for every element in each spectrum.
-Based on \citet{Luger2019}, this can be computed as a purely linear operation on the spherical harmonic vector $\bvec{y}$:
-%
-\begin{align}
-    \label{eq:norm:b}
-    \bvec{b}
-     & =
-    %
-    \begin{pmatrix}
-        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_0)     \\
-        \cdots                                     \\
-        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_0)     \\
-        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_1)     \\
-        \cdots                                     \\
-        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_1)     \\
-        \cdots                                     \\
-        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_{M-1}) \\
-        \cdots                                     \\
-        \bvec{r}^\top \bvec{A_1} \bvec{R}(t_{M-1})
-    \end{pmatrix}
-    \bvec{y}
-    %
-    \nonumber \\[0.5em]
-     & \equiv
-    \bvec{B} \, \bvec{y}
-\end{align}
-%
-where $\bvec{r}$ is given by Equation~(18) in \citet{Luger2019}, $\bvec{A_1}$ is given in Appendix B of \citet{Luger2019}, and $\bvec{R}(t)$ is the rotation matrix defined previously.
-
-Given this new equation, we must change how we approach the inverse problem (\S\ref{sec:inverse}). 
-When solving for the spectrum given the spherical harmonic vector (\S\ref{sec:solve_s}), we need only make the replacements $\bvec{f} \rightarrow \frac{\bvec{f}}{\bvec{B}\, \bvec{y}}$ and $\boldsymbol{\Sigma}_\mathbf{f} \rightarrow \frac{\boldsymbol{\Sigma}_\mathbf{f}}{(\bvec{B}\, \bvec{y})^2}$ in Equations~(\ref{eq:inverse:shat}) and (\ref{eq:inverse:scov}).
+where $\fnorm$ is the normalized spectral timeseries,
+$\bvec{B}$ is the baseline design matrix, and the vector division is performed
+elementwise. 
+If $c$ is an index in the observed spectrum corresponding to the continuum (at all epochs), the elements of $\bvec{B}$ are computed from
+%
+\begin{align}
+    B_{ij} = D_{i'j}
+\end{align}
+%
+where
+%
+\begin{align}
+    i' = c + \bigg\lfloor\frac{i}{K}\bigg\rfloor K
+    \quad.
+\end{align}
+%
+In other words, the matrix $\bvec{B}$ is constructed by repeating the $c^\mathrm{th}$ row of each epoch block $\Doppler_m$ of $\Doppler$ $K$ times.
+Equation~(\ref{eq:norm:f}) is therefore equivalent to computing the $M$ unnormalized spectra using Equation~(\ref{eq:linear:f}) and dividing each one by the value at index $c$.
+
+Given this new equation, we must change how we approach the inverse problem (\S\ref{sec:inverse}) if our data vector is the normalized spectral timeseries $\fnorm$. 
+When solving for the spectrum given the spherical harmonic vector (\S\ref{sec:solve_s}), we need only make the replacements 
+$\bvec{f} \rightarrow \fnorm \circ (\bvec{B}\, \bvec{a})$ 
+and 
+$\boldsymbol{\Sigma}_\mathbf{f} \rightarrow \boldsymbol{\Sigma}_{\fnorm} \circ (\bvec{B}\, \bvec{a})^2$ 
+in Equations~(\ref{eq:inverse:shat}) and (\ref{eq:inverse:scov}), where $\circ$ denotes the elementwise product.
 However, when solving for the spherical harmonic vector given the spectrum (\ref{sec:solve_y}), the problem is no longer linear in $\bvec{y}$, as the vector of interest appears in both the numerator and the denominator:
@@
     \label{eq:norm:fy}
-    \bvec{f}
+    \fnorm
      & =
@@
         \,
+        \bvec{S}
+        \,
         \bvec{y}
@@
 %
-While we can solve for $\bvec{y}$ using a nonlinear optimizer, it is often the case that the denominator in Equation~(\ref{eq:norm:fy}) is close to unity; i.e., the total flux from the star typically varies by only a few percent.
-When this is the case, it is straightforward to linearize this equation.
-Following the notation from \S\ref{sec:solve_y}, we may therefore write
-%
-\begin{align}
-    \bvec{f}
-     & =
-    \frac{
-        \bvec{D} \, \bvec{s_0}
-        \,
-        +
-        \,
-        \bvec{D}\bvec{S_1}
-        \,
-        \bvec{y_1}
-    }{
-        \bvec{B_0}
-        \,
-        +
-        \bvec{B_1}
-        \,
-        \bvec{y_1}
-    }
-    \quad,
-\end{align}
-%
-where $\bvec{B_0} = \bvec{1}$ is the first column of $\bvec{B}$ and $\bvec{B}_\bvec{1}$ denotes the matrix composed from the remaining $N - 1$ columns of $\bvec{B}$.
-Expanding the expression above about $\bvec{B_1} \bvec{y_1} = \bvec{0}$ and keeping only terms up to first order, we have
-%
-\begin{align}
-    \label{eq:norm:fapprox}
-    \bvec{f}
-     & \approx
-    \left(
-    \bvec{D} \, \bvec{s_0}
-    \,
-    +
-    \,
-    \bvec{D}\bvec{S_1}
-    \,
-    \bvec{y_1}
-    \right)
-    \circ
-    \left(
-    \bvec{1}
-    \,
-    -
-    \bvec{B_1}
-    \,
-    \bvec{y_1}
-    \right)
-    \nonumber  \\
-     & \approx
-    \left(
-    \bvec{D}\bvec{S_1}
-    \,
-    -
-    \bvec{C}
-    \right)
-    \bvec{y_1}
-    \,
-    +
-    \,
-    \bvec{D} \, \bvec{s_0}
-    \quad,
-\end{align}
-%
-where $\circ$ denotes an elementwise product and $\bvec{C}$ is a matrix constructed by multiplying each row of $\bvec{B_1}$ by the corresponding element of $\bvec{D}\bvec{s_0}$.
-%
-This equation is now linear in $\bvec{y}_\bvec{1}$, so we may solve the least-squares problem as before:
-%
-\begin{align}
-    \label{eq:norm:yhat}
-    \bvec{\hat{y}_1} & =
-    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1}
-    \left(
-    \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
-    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
-    (\bvec{f} - \bvec{D}\bvec{s_0})
-    +
-    {\boldsymbol{\Lambda}_{\mathbf{y}_\bvec{1}}}^{-1} \boldsymbol{\mu}_{\mathbf{y}_\bvec{1}}
-    \right)
-    \quad,
-\end{align}
-%
-with covariance
-%
-\begin{align}
-    \label{eq:norm:ycov}
-    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1} & =
-    \left(
-    \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
-    {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
-    \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)
-    +
-    {\boldsymbol{\Lambda}_{\mathbf{y}_1}}^{-1}
-    \right)^{-1}
-    \quad.
-\end{align}
-%
-Note, importantly, that these equations are valid only in the limit that the change in the total flux from the star is small. 
-Nevertheless, even in the general case, we find that solving this linear problem yields a good starting point for a nonlinear optimization, which we revisit in more detail below.
+Unfortunately, this equation does not admit a closed form solution for $\mathbf{y}$. 
+One can, however, still solve for the maximum a posteriori value of $\mathbf{y}$ in an efficient manner by iteratively solving for the baseline and then for the spherical harmonic coefficients.
+We describe a procedure for this in \S\ref{sec:spotstar} below.
 
@@
 %
-where $\mu = z = \sqrt{1 - x^2 - y^2}$ is the radial coordinate on the projected disk and $u_n$ is a limb darkening coefficient, the effect of limb darkening on the stellar map can be expressed exactly as a linear operation on the spherical harmonic coefficient vector \citep{Luger2019,Agol2019}.
+where $\mu = z = \sqrt{1 - x^2 - y^2}$ is the radial coordinate on the projected disk and $u_n$ is a limb darkening coefficient, the effect of limb darkening on the stellar map can be expressed exactly as a linear operation on the spherical harmonic coefficient vector \citep{Luger2019,Agol2020}.
 This can be understood by noting that all terms in Equation~(\ref{eq:ld:I}) are strictly polynomials in $x$, $y$, and $z$, all of which can be expressed exactly as sums of spherical harmonics \citep{Luger2019}.
@@
 The model remains linear in both the spherical harmonic coefficients and the spectral components, and the procedures outlined in \S\ref{sec:inverse} may still be followed to solve the inverse problem, provided we unroll these matrices into vectors, letting $\mathbf{s} = \mathrm{vec}(\boldsymbol{\mathbb{S}})$ and $\mathbf{y} = \mathrm{vec}(\boldsymbol{\mathbb{Y}})$.
-A detailed discussion of this general case is deferred to future work, but we present an example of a two-component stellar spectrum in \S\ref{sec:eigen}
+We present an example of inference on a two-component stellar spectrum in \S\ref{sec:twospec}
 below.
@@
             To generate the synthetic dataset (orange curves in the bottom panel), the star is inclined at $40^\circ$ with respect to the line of sight and the disk-integrated spectrum is computed at 16 equally-spaced phases between $-180^\circ$ and $180^\circ$ (middle panel).
-            The grey regions indicate wavelength regions outside the observation window, but whose features still contribute to the observed spectrum due to rotational broadening.
+            The grey regions indicate wavelength regions outside the observation window, but whose features can still contribute to the observed spectrum due to rotational broadening.
         }
@@
 We repeat the same experiment here using our new formalism, except we instead generate a stellar surface with the word ``SPOT'' written across the northern hemisphere (top left panel of Figure~\ref{fig:spot_setup}).
-We do this by computing the $l_\mathrm{max} = 15$ spherical harmonic decomposition of an image of the word, generating a set of $N = (l_\mathrm{max} + 1)^2 = 256$ spherical harmonic coefficients $\bvec{y} = (1 \quadquad \bvec{y_1})$.
-
-Our input spectrum $\bvec{s}$ was generated at high resolution ($R \equiv \frac{\lambda}{\Delta\lambda} = 300,000$) centered at a reference wavelength $\lambda_\mathrm{r} = 6430$ nm (blue curve in the bottom panel of Figure~\ref{fig:spot_setup}).
-The spectrum consists of a Gaussian absorption line in log-wavelength ($\lnlam$) space with amplitude $0.5$ and standard deviation $\sigma_{\lnlam} = 1.4\times 10^{-5}$. 
-This corresponds to a FWHM of about $2.355~\sigma_{\lnlam}~\lambda_\mathrm{r}~\approx~0.2$ nm or, in velocity space, $2.355~\sigma_{\lnlam}~c~\approx~10$~km/s, equal to the value used in \citet{Vogt1987}.
+We do this by computing the $l_\mathrm{max} = 15$ spherical harmonic decomposition of an image of the word, generating a set of $N = (l_\mathrm{max} + 1)^2 = 256$ spherical harmonic coefficients $\bvec{y}$.
+We assume an equatorial velocity $v = 60$ km/s and an inclination $i = 40^\circ$, such that $v \sin i = 38.6$~km/s (compare to $i = 40^\circ$ and $v \sin i = 40$~km/s in \citealt{Vogt1987}).
+
+Our input spectrum $\bvec{s}$ was generated at high resolution ($R \equiv \frac{\lambda}{\Delta\lambda} = 430,000$) centered on the Fe I $\lambda 6430$ absorption line (blue curve in the bottom panel of Figure~\ref{fig:spot_setup}).
+%
+The spectrum consists of a (purely synthetic) Gaussian absorption line of fractional depth 50\% centered at $\lambda = 643$~nm with FWHM of $0.02$~nm, or, in velocity space, $\Delta v = \mathrm{FWHM} \times c / \lambda \approx~10$~km/s, equal to the value used in \citet{Vogt1987}.
+%
 Unlike \citet{Vogt1987}, we add 20 additional small absorption lines at random positions throughout the spectrum, all of the same FWHM but of varying depths, including some line blends. 
-In total, the rest frame spectrum $\bvec{s}$ consists of $K = 201$ log-wavelength bins in the range $-\Delta\lnlam < \lnlam < \Delta\lnlam$ for $\Delta\lnlam = 3.3\times 10^{-4}$ plus an additional
-%
-\begin{align}
-    W - 1 & = \frac{v\sin i}{c} \frac{K}{\Delta\lnlam} - 1 \nonumber           \\
-          & = \left(\frac{40~\mathrm{km/s}}{3\times 10^5~\mathrm{km/s}}\right)
-    \left(\frac{201}{3.3 \times 10^{-4}}\right)  - 1 \nonumber                 \\
-          & = 80
-\end{align}
-%
-log-wavelength bins of padding (40 on either side) to eliminate edge effects due to the convolution, for a total of $K' = 281$ wavelength bins. 
-As in \citet{Vogt1987}, we assume a projected velocity of $v\sin i = 40$ km/s and an inclination $i = 40^\circ$.
-
-Given $\bvec{y_1}$ and $\bvec{s}$, we use Equations~(\ref{eq:deconv:F}) and~%
-(\ref{eq:inverse:alm}) to compute the data vector $\bvec{f}$ at $M = 16$ equally spaced rotational phases; these phases are shown in orthographic projection (as an observer would see the star) in the center panel of Figure~\ref{fig:spot_setup}.
+In total, the rest frame spectrum $\bvec{s}$ consists of $K = 200$ wavelength bins in the range $642.85~\mathrm{nm} \leq \lambda \leq 643.15~\mathrm{nm}$ plus an additional
+%
+\begin{align}
+    W & = 2 \bigg\lceil \frac{(v\sin i)_\mathrm{max}R}{c} \bigg\rceil \nonumber  \\
+      & = 144
+\end{align}
+%
+bins of padding (72 on either side) to eliminate edge effects due to the convolution, for a total of $K' = 344$ wavelength bins. 
+In the expression above, $(v\sin i)_\mathrm{max}$ is the maximum value of $v\sin i$ we can model with a given value of $W$; for this experiment, we set $(v\sin i)_\mathrm{max}=50$~km/s, which is larger than the actual value of $v\sin i$ we used to generate the data (see above).
+Finally, we linearly interpolate this spectrum to a wavelength grid uniform in log space to obtain the vector $\bvec{s}$ evaluated at each $\lnlam$.
+
+Given $\bvec{y}$ and $\bvec{s}$, we use Equations~(\ref{eq:deconv:F}) and~(\ref{eq:inverse:alm}) to compute the data vector $\bvec{f}$ at $M = 16$ equally spaced rotational phases; these phases are shown in orthographic projection (as an observer would see the star) in the center panel of Figure~\ref{fig:spot_setup}.
 The synthetic spectra for each phase are shown as the orange curves in the bottom panel of the figure (note the different scaling, as all spectral lines become shallower due to the broadening). 
 We assume a wavelength-independent, quadratic limb darkening law with $u_1 = 0.5$ and $u_2 = 0.25$. 
-Finally, we divide the flux by the baseline at each epoch (Equation~\ref{eq:norm:b})
-and add random Gaussian noise with amplitude $\sigma_\bvec{f} = 10^{-4}$ to simulate a very high signal-to-noise ratio (SNR) spectrum. 
-The mean standard deviation in each wavelength bin across all 16 epochs in the noiseless data vector is about $10^{-2}$, so our choice of $\sigma_\bvec{f}$ corresponds to SNR $\sim$ 100 in each of the 201 wavelength bins of $\bvec{f}$.
+Finally, we divide the flux by the baseline at each epoch (Equation~\ref{eq:norm:f}) and add random Gaussian noise with amplitude $\sigma_\bvec{f} = 10^{-4}$ to simulate a very high signal-to-noise ratio (SNR) spectrum.
+The mean standard deviation in each wavelength bin across all 16 epochs in the noiseless data vector is about $10^{-2}$, so our choice of $\sigma_\bvec{f}$ corresponds to SNR $\sim$ 100 in each of the 200 wavelength bins of $\bvec{f}$.
 
@@
 In the following sections we discuss various approaches to solving the Doppler imaging problem for this dataset.
-Unless otherwise noted, in all experiments we adopt a Gaussian prior for the spherical harmonic coefficients $\bvec{y_1}$ with mean $\boldsymbol{\mu}_\bvec{y_1} = \bvec{0}$ and covariance $\boldsymbol{\Lambda}_\bvec{y_1} = (10^{-2})^2\bvec{I}$, corresponding to a flat power spectrum prior.
-We place a Gaussian process prior on the spectrum $\bvec{s}$ with mean $\boldsymbol{\mu}_\bvec{s} = \bvec{1}$ and a covariance matrix $\boldsymbol{\Lambda}_\bvec{s}$ computed from a Mat\'ern-3/2 kernel with amplitude $\sigma_\bvec{s} = 0.3$ and lengthscale $\rho_\bvec{s} = 3\times 10^{-5}$.
+Unless otherwise noted, in all experiments we adopt a Gaussian prior for the spherical harmonic coefficients $\bvec{y}$ with mean $\boldsymbol{\mu}_\bvec{y} = \bvec{0}$ and covariance $\boldsymbol{\Lambda}_\bvec{y}$, with
+%
+\begin{align}
+    {\Lambda_\bvec{y}}_{i, j} 
+    =
+    \begin{cases}
+        1 & \quad\quad\quad\quad i = j = 0
+        \\
+        10^{-4}\delta_{ij} & \quad\quad\quad\quad \mathrm{otherwise}
+        \quad,
+    \end{cases}
+\end{align}
+%
+corresponding to a flat power spectrum prior.
+We also place a Gaussian prior on the spectrum $\bvec{s}$ with unit mean and covariance $\boldsymbol{\Lambda}_\bvec{s} = (10^{-1})^2\bvec{I}$.
+
+\xxx{WORK IN PROGRESS BELOW THIS LINE}
 
@@
 %
-In our first experiment, we attempt to infer the stellar map assuming we have perfect knowledge of the rest frame spectrum $\bvec{s}$ and the baseline $\bvec{b}$ (Equation~\ref{eq:norm:b}).
+In our first experiment, we attempt to infer the stellar map assuming we have perfect knowledge of the rest frame spectrum $\bvec{s}$ and the baseline.
 This is analogous to the case where a good physical model exists for the stellar spectrum and simultaneous photometry is available to constrain the baseline variations.
@@
         $\bvec{A}$                                          & matrix form of $\bvec{a}$                                    & Equation~(\ref{eq:inverse:alm})          \\
-        $\bvec{b}$                                          & flux baseline vector                                         & Equation~(\ref{eq:norm:b})                 \\
-        $\bvec{B}$                                          & block matrix representation of $\bvec{b}$                    & Equation~(\ref{eq:norm:b})                 \\
+        $\bvec{B}$                                          & baseline design matrix                                       & \S\ref{sec:norm}                 \\
         $c$                                                 & speed of light                                               & Equation~(\ref{eq:kT:beta})                \\
@@
         $*$                                                 & convolution                                                  & Equation~(\ref{eq:deconv:convolution_def}) \\
-        $\circ$                                             & element-wise product                                         & Equation~(\ref{eq:norm:fapprox})           \\
+        $\circ$                                             & element-wise product                                         & \S\ref{sec:norm}           \\
         $\otimes$                                           & Kronecker product                                            & Equation~(\ref{eq:linear:Dm})              \\

### 2021-09-09 src/figures/generate.py

@@ -10,6 +10,7 @@ def generate_data(
     nt=16,
     inc=40,
     veq=60000,
+    vsini_max=50000,
     smoothing=0.075,
     theta=None,
     wav=np.linspace(642.85, 643.15, 200),
@@ -24,6 +25,7 @@ def generate_data(
         nc=nc,
         veq=veq,
         inc=inc,
+        vsini_max=vsini_max,
         nt=nt,
         wav=wav,
     )

### 2021-09-09 src/figures/spot_setup.py

@@ -17,6 +17,7 @@ nc = 1
 nt = 16
 inc = 40
 veq = 60000
+vsini_max = 50000
 wav = np.linspace(642.85, 643.15, 200)
 theta = np.linspace(-180, 180, nt, endpoint=False)
 u = [0.5, 0.25]
@@ -27,6 +28,7 @@ map, _, _ = generate_data(
     nt=nt,
     inc=inc,
     veq=veq,
+    vsini_max=vsini_max,
     wav=wav,
     theta=theta,
     u=u,
@@ -125,7 +127,7 @@ for lon, lat in zip(lons, lats):
 # Tweak
 ax[1].set_ylabel(r"intensity", fontsize=10)
 ax[1].set_xlabel(r"$\lambda$ [nm]", fontsize=10)
-ax[1].set_aspect(0.7)
+ax[1].set_aspect(0.4)
 for tick in ax[1].xaxis.get_major_ticks() + ax[1].yaxis.get_major_ticks():
     tick.label.set_fontsize(10)
 ax[1].margins(0, 0.2)

### 2021-09-10 src/ms.tex
more figs

@@
 \begin{align}
+    \label{eq:Lambday}
     {\Lambda_\bvec{y}}_{i, j} 
@@
 
-\xxx{WORK IN PROGRESS BELOW THIS LINE}
-
 \subsection{Known baseline and spectrum}
@@
 This is analogous to the case where a good physical model exists for the stellar spectrum and simultaneous photometry is available to constrain the baseline variations.
-As we showed in \S\ref{sec:solve_y}, the posterior distribution for the map coefficients $\bvec{y_1}$ is analytic in this case, with mean given by Equation~(\ref{eq:inverse:y1hat})
+As we showed in \S\ref{sec:solve_y}, the posterior distribution for the map coefficients $\bvec{y}$ is analytic in this case, with mean given by Equation~(\ref{eq:inverse:y1hat})
 and covariance given by Equation~(\ref{eq:inverse:y1cov}). 
-Note that we must first scale the data vector $\bvec{f}$ by $\bvec{b}$ (which in this case is known).
-
-% \begin{figure}[p!]
-%     \begin{centering}
-%         \includegraphics[width=0.49\linewidth]{figures/spot_y1_timeseries.pdf}
-%         \includegraphics[width=0.49\linewidth]{figures/spot_y1_rect.pdf}
-%         \caption{%
-%             The solution to the \spot problem at high SNR when both the rest frame spectrum and the baseline are known.
-%             The panel on the left shows the inferred map at each of the 16
-%             epochs, alongside the observed spectrum (black points) and the best-fit model (orange lines). 
-%             The rectangular projection of the original map is shown at the top right; the inferred map is displayed below it. 
-%             The bottom panel shows the posterior uncertainty as a function of latitude and longitude, ranging from close to zero in the northern hemisphere to $\sigma_\mathrm{prior} \approx 10\%$ below a latitude of $-30^\circ$.
-%             The latter is the uncertainty associated with our particular choice of prior, as the southernmost latitudes of the star are never visible to the observer.
-%         }
-%         \label{fig:spot_y1}
-%     \end{centering}
-% \end{figure}
-
-The results are shown in Figure~\ref{fig:spot_y1}. 
+Note that we must first scale the data vector $\fnorm$ by the baseline (which in this case is known) to obtain $\bvec{f}$.
+
+\begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=0.39\linewidth]{figures/spot_infer_y_timeseries.pdf}
+        \includegraphics[width=0.59\linewidth]{figures/spot_infer_y_maps.pdf}
+        \caption{%
+            The solution to the \spot problem at high SNR when both the rest frame spectrum and the baseline are known.
+            The panel on the left shows the inferred map at each of the 16
+            epochs, alongside the observed spectrum (black points) and the best-fit model (orange lines). 
+            The Mollweide projection of the original map is shown at the top right; the inferred map is displayed below it. 
+            The bottom panel shows the posterior uncertainty on the inferred intensity, ranging from close to zero in the northern hemisphere to $\sigma_\mathrm{prior} \approx 13\%$ below a latitude of $-30^\circ$.
+            The latter is the uncertainty associated with our particular choice of prior, as the southernmost latitudes of the star are never visible to the observer.
+        }
+        \label{fig:spot_infer_y}
+    \end{centering}
+\end{figure}
+
+The results are shown in Figure~\ref{fig:spot_infer_y}. 
 The left hand panel shows the inferred map alongside the data (black points) and best fit model (orange curves) at each of the 16 epochs.
@@
     \label{eq:spotstar:uncert}
-    \boldsymbol{\Sigma}_\bvec{p} = \bvec{P} \boldsymbol{\Sigma}_\bvec{\hat{y}_1}^{-1} \bvec{P}^\top
+    \boldsymbol{\Sigma}_\bvec{p} = \bvec{P} \boldsymbol{\Sigma}_\bvec{\hat{y}}\bvec{P}^\top
 \end{align}
@@
 The inferred map is nearly indistinguishable from the true map, save for a few small differences, particularly below the stellar equator. 
-This is captured by the uncertainty, which increases south of $+30^\circ$ latitude, reaching a maximum at $-30^\circ$, below which the uncertainty is constant at about 10\%. 
+This is captured by the uncertainty, which increases south of $+30^\circ$ latitude, reaching a maximum at $-30^\circ$, below which the uncertainty is constant at about 13\%. 
 This is due to the fact that regions below $-40^\circ$ latitude are never in view from the observer's perspective, while regions between about $-30^\circ$ and $-40^\circ$ are so strongly limb-darkened that the data contains little information about them.
-The particular value of the uncertainty in this region---10\%---is the uncertainty associated with the prior, which can be computed by replacing $\boldsymbol{\Sigma}_\bvec{\hat{y}_1}$ with $\boldsymbol{\Lambda}_\bvec{y_1}$ in Equation~(\ref{eq:spotstar:uncert}).
+The particular value of the uncertainty in this region---13\%---is the uncertainty associated with our choice of prior (Equation~\ref{eq:Lambday}).
+
+\xxx{WORK IN PROGRESS BELOW THIS LINE}
 

### 2021-09-10 src/figures/spot_infer_y.py

@@ -1,0 +1,31 @@
+# -*- coding: utf-8 -*-
+"""
+Setup for the SPOT problem.
+
+"""
+from utils.generate import generate_data
+from utils.plot import plot_timeseries, plot_maps
+import numpy as np
+import matplotlib.pyplot as plt
+import starry
+
+# Generate the synthetic dataset
+data = generate_data()
+map = data["map"]
+y = data["y"]
+theta = data["theta"]
+flux0 = data["flux0"]
+flux_err = data["flux_err"]
+
+# Solve
+soln = map.solve(
+    flux0, theta=theta, normalized=False, fix_spectrum=True, flux_err=flux_err
+)
+
+# Plot the maps
+fig = plot_maps(map, y, soln["cho_ycov"])
+fig.savefig("spot_infer_y_maps.pdf", bbox_inches="tight", dpi=300)
+
+# Plot the timeseries
+fig = plot_timeseries(map, theta, flux0, normalized=False)
+fig.savefig("spot_infer_y_timeseries.pdf", bbox_inches="tight", dpi=300)

### 2021-09-10 src/figures/spot_setup.py

@@ -3,37 +3,16 @@
 Setup for the SPOT problem.
 
 """
-from generate import generate_data
+from utils.generate import generate_data
 import numpy as np
 import matplotlib.pyplot as plt
 import starry
 
-# Generate the data
-np.random.seed(13)
 
 # Instantiate the Doppler map
-ydeg = 15
-nc = 1
-nt = 16
-inc = 40
-veq = 60000
-vsini_max = 50000
-wav = np.linspace(642.85, 643.15, 200)
-theta = np.linspace(-180, 180, nt, endpoint=False)
-u = [0.5, 0.25]
-smoothing = 0.075
-map, _, _ = generate_data(
-    ydeg=ydeg,
-    nc=nc,
-    nt=nt,
-    inc=inc,
-    veq=veq,
-    vsini_max=vsini_max,
-    wav=wav,
-    theta=theta,
-    u=u,
-    smoothing=smoothing,
-)
+data = generate_data()
+map = data["map"]
+theta = data["theta"]
 
 # Set up the plot
 fig = plt.figure(figsize=(11, 9))
@@ -67,6 +46,7 @@ for n in range(16):
         fontsize=6,
         color="k",
     )
+    ax_ortho[n].set_rasterization_zorder(100)
 
 # Points where we'll evaluate the spectrum. One corresponds to
 # a place within the spot; the other is outside the spot.
@@ -141,7 +121,11 @@ ax_data_twin = ax_data.twinx()
 label = "observed"
 for n in range(len(flux)):
     ax_data_twin.plot(
-        map.wav, flux[n] / flux[n].max(), color="C1", alpha=0.3, label=label,
+        map.wav,
+        flux[n] / flux[n].max(),
+        color="C1",
+        alpha=0.3,
+        label=label,
     )
     label = None
 ax_data.axvspan(map.wav0[0], map.wav[0], color="k", alpha=0.3)

### 2021-09-12 src/ms.tex
getting there

@@
 
+\begin{algorithm}
+    \begin{spacing}{1.25}
+        \begin{fminipage}{0.98\textwidth}
+            \vspace{1em}
+            \begin{algorithmic}
+                \FUNCTION{solve1}($\bvec{f}$, $\boldsymbol{\Sigma}_\mathbf{f}$, $\boldsymbol{\mu}_\bvec{y}$, $\boldsymbol{\Lambda}_\bvec{y}$, $\bvec{s}$)
+                \STATE
+                $
+                \bvec{S} \gets \mathrm{blockDiag}(\bvec{s})
+                $
+                \STATE 
+                $
+                \boldsymbol{\Sigma}_\bvec{\hat{y}}
+                \gets
+                \left(
+                \bvec{S}^\top\Doppler^\top
+                {\boldsymbol{\Sigma}_\bvec{f}}^{-1}
+                \Doppler\bvec{S}
+                +
+                {\boldsymbol{\Lambda}_\bvec{y}}^{-1}
+                \right)^{-1}
+                $
+                \STATE 
+                $
+                \bvec{\hat{y}} 
+                \gets 
+                \boldsymbol{\Sigma}_\mathbf{\hat{y}}
+                \left(
+                \bvec{S}^\top\Doppler^\top
+                {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
+                \bvec{f}
+                +
+                {\boldsymbol{\Lambda}_\bvec{y}}^{-1} \boldsymbol{\mu}_\bvec{y}
+                \right)
+                $
+                \RETURN ($\bvec{\hat{y}}$, $\boldsymbol{\Sigma}_\mathbf{\hat{y}}$)
+                \ENDFUNCTION
+            \end{algorithmic}
+            \vspace{1em}
+        \end{fminipage}
+    \end{spacing}
+    \label{alg:solve1}
+    \caption{Solution to the L2 linear least squares problem for the spherical harmonic representation $\bvec{y}$ of the stellar surface map.
+Given an unnormalized spectral timeseries $\bvec{f}$, its covariance matrix $\boldsymbol{\Sigma}_\mathbf{f}$, a Gaussian prior on the map (mean $\boldsymbol{\mu}_\bvec{y}$, covariance $\boldsymbol{\Lambda}_\bvec{y}$), and the rest frame spectrum $\bvec{s}$, this function returns the maximum a posteriori (MAP) solution $\bvec{\hat{y}}$ to the surface map as well as its covariance $\boldsymbol{\Sigma}_\mathbf{\hat{y}}$.
+The $\mathrm{blockDiag}$ operation on the second line is given by Equation~(\ref{eq:inverse:S}).}
+\end{algorithm}
+
 \begin{figure}[p!]
@@
 \S\ref{sec:norm}.
+
+\begin{algorithm}
+    \begin{spacing}{1.25}
+        \begin{fminipage}{0.98\textwidth}
+            \vspace{1em}
+            \begin{algorithmic}
+                \FUNCTION{solve2}($\fnorm$, $\boldsymbol{\sigma}_{\fnorm}$, $\boldsymbol{\mu}_\bvec{y}$, $\boldsymbol{\Lambda}_\bvec{y}$, $\bvec{s}$, $\sigma_b$, $\ln T_0$, $\Delta \ln T$)
+                \STATE $\bvec{b} \gets \bvec{1}$
+                \STATE $\ln T \gets \ln T_0$
+                \WHILE{$T > 1$}
+                    \STATE $
+                    \bvec{f} 
+                    \gets 
+                    \fnorm \circ \bvec{b}
+                    $
+                    \STATE $
+                    \boldsymbol{\sigma}_\mathbf{f} 
+                    \gets 
+                    \boldsymbol{\sigma}_{\fnorm} \circ \bvec{b}
+                    $
+                    \STATE $
+                    \boldsymbol{\Sigma}_\mathbf{f} 
+                    \gets 
+                    e^{\ln T} \mathrm{diag}(\boldsymbol{\sigma}_\mathbf{f} ) + \sigma_b^2
+                    $
+                    \STATE 
+                    $
+                    (\bvec{\hat{y}}, \boldsymbol{\Sigma}_\bvec{\hat{y}})
+                    \gets
+                    $
+                    \texttt{\textbf{solve1}}($\bvec{f}$, $\boldsymbol{\Sigma}_\mathbf{f}$, $\boldsymbol{\mu}_\bvec{y}$, $\boldsymbol{\Lambda}_\bvec{y}$, $\bvec{s}$)
+                    \STATE $\bvec{b} \gets \bvec{B} \, \bvec{S} \, \bvec{\hat{y}} $
+                    \STATE $\ln T \gets \ln T - \Delta \ln T$
+                \ENDWHILE
+                \RETURN ($\bvec{\hat{y}}$, $\boldsymbol{\Sigma}_\mathbf{\hat{y}}$)
+                \ENDFUNCTION
+            \end{algorithmic}
+            \vspace{1em}
+        \end{fminipage}
+    \end{spacing}
+    \label{alg:solve2}
+    \caption{Solution to the tempered, iterative problem for the spherical harmonic representation of the stellar surface map when the observed spectra $\fnorm$ have been normalized to the continuum.
+In addition to the data, priors, and model spectrum, this function accepts a baseline standard deviation $\sigma_b$, an initial temperature $\ln T_0$, and a temperature decrement $\Delta \ln T$; see text for details.}
+\end{algorithm}
+
 We use the solution to the linearized problem, Equation~(\ref{eq:norm:yhat}), to obtain an initial guess for $\bvec{y_1}$. 
@@
 For this particular experiment, we set $T_0 = 100$ and $\Delta \log T = -0.25$, for a total of $9$ steps of the bilinear solver.
-%
-In a final step, we run a gradient-descent optimizer, initializing it at the solution obtained with the bilinear solver. 
-We use the \texttt{Keras} \citep{Keras} implementation of the Nesterov momentum-enhanced Adam solver \citep[\texttt{NAdam};][]{NAdam}, running it for $N_\mathrm{nadam} = 80$ iterations at a learning rate $L_\mathrm{nadam} = 10^{-4}$.
-Our loss function is simply the (negative) log probability, equal to the sum of the log likelihood and log prior:
-%
-\begin{align}
-    \label{eq:spotstar:logP}
-    -\ln P & =
-    \frac{1}{2}
-    \Big(
-    \bvec{r}^\top \boldsymbol{\Sigma}_\bvec{f}^{-1} \bvec{r} \, + \,
-    \bvec{y_1}^\top \boldsymbol{\Lambda}_\bvec{y_1}^{-1} \bvec{y_1} \, + \, (\bvec{b - 1})^\top \boldsymbol{\Lambda}_\bvec{b}^{-1} (\bvec{b - 1})
-    \Big)
-\end{align}
-%
-where $\bvec{r}$ is the residual (data minus model) vector and the last term is a prior we include on the baseline $\bvec{b}$, which we force to be close to a mean of unity with covariance $\boldsymbol{\Lambda}_\bvec{b} = (0.1)^2\bvec{I}$.
-
-% \begin{figure}[p!]
-%     \begin{centering}
-%         \includegraphics[width=0.49\linewidth]{figures/spot_y1b_timeseries.pdf.pdf}
-%         \includegraphics[width=0.49\linewidth]{figures/spot_y1b_rect.pdf}
-%         \\[0.5em]
-%         \includegraphics[width=0.405\linewidth]{figures/spot_y1b_baseline.pdf}
-%         \includegraphics[width=0.575\linewidth]{figures/spot_y1b_coeffs.pdf}
-%         \caption{%
-%             Similar to Figure~\ref{fig:spot_y1}, but assuming the baseline is not known. 
-%             The panel at the bottom left shows the true baseline (blue) and the inferred baseline (orange), along with its $1\sigma$ uncertainty. 
-%             The large offset between the two highlights one of the fundamental degeneracies of the problem: since most of the southern hemisphere of the star is never visible, the coefficient of the $Y_{1,-1}$ (\raisebox{-0.2em}{\includegraphics[width=1em]{Y1m1.pdf}}) spherical harmonic is not constrained by the data, resulting in an unknowable additive offset in the baseline.
-%             This effect can be seen also in (\emph{a}) the inferred map, where the background intensity in the northern hemisphere is significantly larger than that in the southern hemisphere, and (\emph{b}) the spherical harmonic coefficients (bottom right), where a large discrepancy is visible between the true and inferred values of the first two coefficients.
-%         }
-%         \label{fig:spot_y1b}
-%     \end{centering}
-% \end{figure}
+
+\begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=0.39\linewidth]{figures/spot_infer_yb_timeseries.pdf}
+        \includegraphics[width=0.59\linewidth]{figures/spot_infer_yb_maps.pdf}
+        \caption{%
+            Similar to Figure~\ref{fig:spot_infer_y}, but assuming the baseline is not known.
+        }
+        \label{fig:spot_infer_yb}
+    \end{centering}
+\end{figure}
 

### 2021-09-14 src/ms.tex
fixed continuum norm

@@
 In particular, if one places a (multidimensional) Gaussian prior on $\alm$ with mean $\boldsymbol{\mu}_\mathbf{a}$ and covariance $\boldsymbol{\Lambda}_\mathbf{a}$, the maximum \emph{a posteriori} (MAP)
-solution for $\alm$ is
+solution for $\alm$ is given by the solution to the L2 regularization problem:
 %
@@
 We assume a wavelength-independent, quadratic limb darkening law with $u_1 = 0.5$ and $u_2 = 0.25$. 
-Finally, we divide the flux by the baseline at each epoch (Equation~\ref{eq:norm:f}) and add random Gaussian noise with amplitude $\sigma_\bvec{f} = 10^{-4}$ to simulate a very high signal-to-noise ratio (SNR) spectrum.
+Finally, we divide the flux by the baseline at each epoch (Equation~\ref{eq:norm:f}) and add random Gaussian noise with covariance matrix $\bvec{\Sigma}_\bvec{f} = \sigma_\bvec{f}^2 \mathbf{I}$, with $\sigma_\bvec{f} = 10^{-4}$ to simulate a very high signal-to-noise ratio (SNR) spectrum.
 The mean standard deviation in each wavelength bin across all 16 epochs in the noiseless data vector is about $10^{-2}$, so our choice of $\sigma_\bvec{f}$ corresponds to SNR $\sim$ 100 in each of the 200 wavelength bins of $\bvec{f}$.
@@
 Note that we must first scale the data vector $\fnorm$ by the baseline (which in this case is known) to obtain $\bvec{f}$.
+The pseudocode for computing the maximum a posteriori (MAP) solution for $\bvec{y}$ and its covariance is given in Algorithm~\ref{alg:solve1}.
 
@@
     \end{spacing}
-    \label{alg:solve1}
-    \caption{Solution to the L2 linear least squares problem for the spherical harmonic representation $\bvec{y}$ of the stellar surface map.
-Given an unnormalized spectral timeseries $\bvec{f}$, its covariance matrix $\boldsymbol{\Sigma}_\mathbf{f}$, a Gaussian prior on the map (mean $\boldsymbol{\mu}_\bvec{y}$, covariance $\boldsymbol{\Lambda}_\bvec{y}$), and the rest frame spectrum $\bvec{s}$, this function returns the maximum a posteriori (MAP) solution $\bvec{\hat{y}}$ to the surface map as well as its covariance $\boldsymbol{\Sigma}_\mathbf{\hat{y}}$.
-The $\mathrm{blockDiag}$ operation on the second line is given by Equation~(\ref{eq:inverse:S}).}
+    \caption{Solution to the L2 linear least squares problem for the spherical harmonic representation $\bvec{\hat{y}}$ of the stellar surface map when the unnormalized spectral timeseries $\bvec{f}$ is known.
+    The $\mathrm{blockDiag}$ operation on the second line is given by Equation~(\ref{eq:inverse:S}).
+    \label{alg:solve1}}
 \end{algorithm}
@@
 
-The results are shown in Figure~\ref{fig:spot_infer_y}. 
+Figure~\ref{fig:spot_infer_y} shows the results.
 The left hand panel shows the inferred map alongside the data (black points) and best fit model (orange curves) at each of the 16 epochs.
 The panels on the right show the true map (top), the inferred map (center)
-and the posterior pointwise uncertainty (bottom) on a rectangular latitude-longitude grid. 
+and the posterior pointwise uncertainty (bottom) on a Mollweide grid. 
 The uncertainty on the vector of pixels $\bvec{p}$ where we evaluate the map is equal to the square root of the diagonal of the posterior covariance matrix for the pixel values, computed from
@@
 
-The inferred map is nearly indistinguishable from the true map, save for a few small differences, particularly below the stellar equator. 
-This is captured by the uncertainty, which increases south of $+30^\circ$ latitude, reaching a maximum at $-30^\circ$, below which the uncertainty is constant at about 13\%. 
-This is due to the fact that regions below $-40^\circ$ latitude are never in view from the observer's perspective, while regions between about $-30^\circ$ and $-40^\circ$ are so strongly limb-darkened that the data contains little information about them.
-The particular value of the uncertainty in this region---13\%---is the uncertainty associated with our choice of prior (Equation~\ref{eq:Lambday}).
-
-\xxx{WORK IN PROGRESS BELOW THIS LINE}
+The inferred map is nearly indistinguishable from the true map north of the equator.
+Regions south of the equator are almost never in view to the observer (below $-40^\circ$, they are \emph{never} in view); our inferred map is therefore informed primarily by our prior in southern latitudes.
+This is well captured by the uncertainty (bottom panel), which increases south of the equator, reaching a maximum at $-30^\circ$, below which the uncertainty is constant at about 13\%, a value associated with our particular choice of prior (Equation~\ref{eq:Lambday}).
 
@@
 This corresponds to the case discussed in
-\S\ref{sec:norm}.
+\S\ref{sec:norm}, and is likely to be the most common application of the methodology presented in this work.
 
@@
                     \gets 
-                    e^{\ln T} \mathrm{diag}(\boldsymbol{\sigma}_\mathbf{f} ) + \sigma_b^2
+                    e^{\ln T} \mathrm{diag}(\boldsymbol{\sigma}_\mathbf{f}^2) + \sigma_b^2
                     $
@@
     \end{spacing}
-    \label{alg:solve2}
     \caption{Solution to the tempered, iterative problem for the spherical harmonic representation of the stellar surface map when the observed spectra $\fnorm$ have been normalized to the continuum.
-In addition to the data, priors, and model spectrum, this function accepts a baseline standard deviation $\sigma_b$, an initial temperature $\ln T_0$, and a temperature decrement $\Delta \ln T$; see text for details.}
+In addition to the data, priors, and model spectrum, this function accepts a baseline standard deviation $\sigma_b$, an initial temperature $\ln T_0$, and a temperature decrement $\Delta \ln T$; see text for details.
+    \label{alg:solve2}}
 \end{algorithm}
 
-We use the solution to the linearized problem, Equation~(\ref{eq:norm:yhat}), to obtain an initial guess for $\bvec{y_1}$. 
-We then repeatedly solve Equation~(\ref{eq:inverse:y1hat}) for $\bvec{y_1}$, given the baseline computed from the previous value of $\bvec{y_1}$ from Equation~(\ref{eq:norm:b}).
-Because of the high SNR of our data, we find that it is necessary to employ a simple tempering procedure to avoid getting stuck in local minima. 
-We introduce an artificial temperature $T$ that decreases every iteration in equally spaced logarithmic steps $\Delta \log T$ from an initial temperature $T=T_0$ to $T=1$. 
-This temperature is used to scale the data covariance $\boldsymbol{\Sigma}_\bvec{f}$; in practice, we simply replace $\boldsymbol{\Sigma}_\bvec{f}$ with $T \boldsymbol{\Sigma}_\bvec{f}$ in Equation~(\ref{eq:inverse:y1hat}).
-This has the effect of smoothing out the likelihood space, reducing the likelihood that the solver will get stuck in a local minimum. 
-For this particular experiment, we set $T_0 = 100$ and $\Delta \log T = -0.25$, for a total of $9$ steps of the bilinear solver.
+Our approach is to iteratively solve Equation~(\ref{eq:norm:fy}) by re-expressing it as
+%
+\begin{align}
+    \fnorm
+     & =
+    \frac{
+        \bvec{D}
+        \,
+        \bvec{S}
+        \,
+        \bvec{y}
+    }{
+        \bvec{b}
+    }
+    \quad.
+\end{align}
+%
+where the baseline $\bvec{b}$ is given by
+%
+\begin{align}
+    \bvec{b}
+    =
+    \bvec{B}
+    \,
+    \bvec{S}
+    \,
+    \bvec{y}
+    \quad.
+\end{align}
+%
+We adopt a simple iterative scheme where we solve the L2 problem for $\bvec{y}$ with $\bvec{b}$ fixed, then update the value of $\bvec{b}$ and repeat.
+Because of the high SNR of our data, we find that it is necessary to employ a simple tempering procedure, in which we artificially inflate the variance of the data by a factor $T$, which we slowly decrease with each step until $T = 1$.
+This has the effect of smoothing out the likelihood surface, effectively preventing the solver from getting stuck in local minima.
+For this particular experiment, we set $\ln T_0 = 2$ and $\Delta \log T = -0.04$, for a total of $50$ steps of the bilinear solver.
+We also add a small variance term $\sigma_b^2 = 10^{-2}$ to all entries of the data covariance $\boldsymbol{\Sigma}_{\bvec{f}}$; this has the effect of marginalizing over an additive model term, which we find improves the convergence of the algorithm.
+The pseudocode for this procedure is presented in Algorithm~\ref{alg:solve2}.
 
@@
         \caption{%
-            Similar to Figure~\ref{fig:spot_infer_y}, but assuming the baseline is not known.
+            Similar to Figure~\ref{fig:spot_infer_y}, but assuming the input spectra are continuum-normalized.
+            We are able to infer the surface map just as
+            well as in the case where the true continuum level
+            is known (Figure~\ref{fig:spot_infer_y}). As before,
+            regions south of the equator are almost never in view, so that portion of our inferred map is dominated by the prior.
         }
@@
 
-Our results are shown in Figure~\ref{fig:spot_y1b}. 
-The panels at the top are the same as those in Figure~\ref{fig:spot_y1}, but now we also plot the inferred baseline (lower left) and spherical harmonic coefficients (lower right) next to the true values.
-We recover the \texttt{SPOT} map just as well as before, except for the presence of a strong dipolar artifact; the background intensity level is higher in the northern hemisphere and lower in the southern hemisphere.
-This effect is closely related to the fact that we do not know the true baseline. 
-While we are able to infer the shape of the baseline exceedingly well (lower left panel), there is a large offset between the true value and our inferred value. 
-This is due to a fundamental degeneracy involving the $Y_{1,-1}$ (\raisebox{-0.2em}{\includegraphics[width=1em]{figures/Y1m1.pdf}}) spherical harmonic coefficient, which, because a large portion of the southern hemisphere is never in view, cannot be constrained by the data.
-The magnitude of the true value of the coefficient is quite large (lower right panel), since the northern hemisphere \emph{is} significantly darker than the southern hemisphere; however, the data do not constrain this, and our prior shrinks all coefficients toward zero.
-The net effect is that the region surrounding the spot in the northern hemisphere gets brighter to even out the difference between the two hemispheres. 
-This causes the visible portion of the star to get brighter, raising the baseline relative to the true value.
-
-Note, importantly, that even in cases where the baseline is known (from, say, simultaneous photometry), it is typically only known in a \emph{relative} sense. 
-This degeneracy will typically apply in that case as well, so in principle the dipole term will always be unconstrained for stars at similar inclinations. 
-For inclinations closer to $90^\circ$ this is much less of an issue, although (as we will see below) other degeneracies show up.
+Our results are shown in Figure~\ref{fig:spot_infer_yb}; compare to Figure~\ref{fig:spot_infer_y}.
+
+\xxx{WORK IN PROGRESS BELOW HERE}
 
@@
 
-% \begin{figure}[p!]
-%     \begin{centering}
-%         \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_timeseries.pdf}
-%         \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_rect.pdf}
-%         \\[0.5em]
-%         \includegraphics[width=0.405\linewidth]{figures/spot_y1bs_baseline.pdf}
-%         \includegraphics[width=0.575\linewidth]{figures/spot_y1bs_coeffs.pdf}
-%         \\[0.5em]
-%         \includegraphics[width=0.98\linewidth]{figures/spot_y1bs_spectrum.pdf}
-%         \caption{%
-%             Similar to Figure~\ref{fig:spot_y1}, but assuming we have no information about either the spectrum, the baseline, or the map coefficients. 
-%             The bottommost panel now shows the true rest frame spectrum (blue line), the initial guess based on a deconvolution (dashed orange line), and the inferred spectrum (orange line, with shaded $1\sigma$ uncertainty).
-%         }
-%         \label{fig:spot_y1bs}
-%     \end{centering}
-% \end{figure}
+\begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=0.39\linewidth]{figures/spot_infer_ybs_timeseries.pdf}
+        \includegraphics[width=0.59\linewidth]{figures/spot_infer_ybs_maps.pdf}
+        %\\[0.5em]
+        \includegraphics[width=\linewidth]{figures/spot_infer_ybs_spectra.pdf}
+        \caption{%
+        Similar to Figure~\ref{fig:spot_y1}, but assuming we have no information about either the spectrum, the baseline, or the map coefficients. 
+        The bottommost panel now shows the true rest frame spectrum (blue line), the initial guess based on a deconvolution (dashed orange line), and the inferred spectrum (orange line, with shaded $1\sigma$ uncertainty).
+        }
+        \label{fig:spot_infer_ybs}
+    \end{centering}
+\end{figure}
 

### 2021-09-14 src/figures/spot_infer_y.py

@@ -5,24 +5,42 @@ Setup for the SPOT problem.
 """
 from utils.generate import generate_data
 from utils.plot import plot_timeseries, plot_maps
+import starry
+import numpy as np
+
 
 # Generate the synthetic dataset
 data = generate_data()
-map = data["map"]
-y = data["y"]
-theta = data["theta"]
-flux0 = data["flux0"]
-flux_err = data["flux0_err"]
+y_true = data["truths"]["y"]
+theta = data["data"]["theta"]
+flux = data["data"]["flux0"]
+flux_err = data["data"]["flux0_err"]
 
-# Solve
+# Instantiate the map
+map = starry.DopplerMap(lazy=False, **data["kwargs"])
+map.spectrum = data["truths"]["spectrum"]
+for n in range(map.udeg):
+    map[1 + n] = data["props"]["u"][n]
+
+# Solve for the Ylm coeffs
 soln = map.solve(
-    flux0, theta=theta, normalized=False, fix_spectrum=True, flux_err=flux_err
+    flux, theta=theta, normalized=False, fix_spectrum=True, flux_err=flux_err
 )
 
+# Get the inferred map
+y_inferred = map.y
+
+# Compute the Ylm expansion of the posterior standard deviation field
+P = map.sht_matrix(inverse=True)
+Q = map.sht_matrix()
+L = np.tril(soln["cho_ycov"])
+W = P @ L
+y_uncert = Q @ np.sqrt(np.diag(W @ W.T))
+
 # Plot the maps
-fig = plot_maps(map, y, soln["cho_ycov"])
+fig = plot_maps(y_true, y_inferred, y_uncert)
 fig.savefig("spot_infer_y_maps.pdf", bbox_inches="tight", dpi=300)
 
 # Plot the timeseries
-fig = plot_timeseries(map, theta, flux0, normalized=False)
+fig = plot_timeseries(data, normalized=False)
 fig.savefig("spot_infer_y_timeseries.pdf", bbox_inches="tight", dpi=300)

### 2021-09-14 src/figures/spot_infer_yb.py

@@ -5,24 +5,42 @@ Setup for the SPOT problem.
 """
 from utils.generate import generate_data
 from utils.plot import plot_timeseries, plot_maps
+import starry
+import numpy as np
+
 
 # Generate the synthetic dataset
 data = generate_data()
-map = data["map"]
-y = data["y"]
-theta = data["theta"]
-flux = data["flux"]
-flux_err = data["flux_err"]
+y_true = data["truths"]["y"]
+theta = data["data"]["theta"]
+flux = data["data"]["flux"]
+flux_err = data["data"]["flux_err"]
 
-# Solve
+# Instantiate the map
+map = starry.DopplerMap(lazy=False, **data["kwargs"])
+map.spectrum = data["truths"]["spectrum"]
+for n in range(map.udeg):
+    map[1 + n] = data["props"]["u"][n]
+
+# Solve for the Ylm coeffs
 soln = map.solve(
     flux, theta=theta, normalized=True, fix_spectrum=True, flux_err=flux_err
 )
 
+# Get the inferred map
+y_inferred = map.y
+
+# Compute the Ylm expansion of the posterior standard deviation field
+P = map.sht_matrix(inverse=True)
+Q = map.sht_matrix()
+L = np.tril(soln["cho_ycov"])
+W = P @ L
+y_uncert = Q @ np.sqrt(np.diag(W @ W.T))
+
 # Plot the maps
-fig = plot_maps(map, y, soln["cho_ycov"])
+fig = plot_maps(y_true, y_inferred, y_uncert)
 fig.savefig("spot_infer_yb_maps.pdf", bbox_inches="tight", dpi=300)
 
 # Plot the timeseries
-fig = plot_timeseries(map, theta, flux, normalized=True, overlap=5.0)
+fig = plot_timeseries(data, normalized=True, overlap=5)
 fig.savefig("spot_infer_yb_timeseries.pdf", bbox_inches="tight", dpi=300)

### 2021-09-14 src/figures/spot_infer_ybs.py

@@ -1,0 +1,58 @@
+# -*- coding: utf-8 -*-
+"""
+Setup for the SPOT problem.
+
+"""
+from utils.generate import generate_data
+from utils.plot import plot_timeseries, plot_maps, plot_spectra
+import starry
+import numpy as np
+
+
+# Generate the synthetic dataset
+data = generate_data()
+y_true = data["truths"]["y"]
+spectrum_true = data["truths"]["spectrum"].reshape(-1)
+theta = data["data"]["theta"]
+flux = data["data"]["flux"]
+flux_err = data["data"]["flux_err"]
+
+# Instantiate the map
+map = starry.DopplerMap(lazy=False, **data["kwargs"])
+for n in range(map.udeg):
+    map[1 + n] = data["props"]["u"][n]
+
+# Solve for the Ylm coeffs and the spectrum
+soln = map.solve(flux, theta=theta, normalized=True, flux_err=flux_err)
+
+# Get the inferred map and spectrum
+y_inferred = map.y
+wav0 = map.wav0
+spectrum_inferred = map.spectrum.reshape(-1)
+
+# Compute the Ylm expansion of the posterior standard deviation field
+P = map.sht_matrix(inverse=True)
+Q = map.sht_matrix()
+L = np.tril(soln["cho_ycov"])
+W = P @ L
+y_uncert = Q @ np.sqrt(np.diag(W @ W.T))
+
+# Get the spectrum guess &  uncertainty
+M = np.array(map._S0i2eTr.todense())  # converts from wav0_ grid to wav0 grid
+spectrum_guess = (soln["spectrum_guess"] @ M).reshape(-1)
+L = np.tril(soln["cho_scov"])
+spectrum_uncert = (np.sqrt(np.diag(L @ L.T)) @ M).reshape(-1)
+
+# Plot the maps
+fig = plot_maps(y_true, y_inferred, y_uncert)
+fig.savefig("spot_infer_ybs_maps.pdf", bbox_inches="tight", dpi=300)
+
+# Plot the spectra
+fig = plot_spectra(
+    wav0, spectrum_true, spectrum_guess, spectrum_inferred, spectrum_uncert
+)
+fig.savefig("spot_infer_ybs_spectra.pdf", bbox_inches="tight", dpi=300)
+
+# Plot the timeseries
+fig = plot_timeseries(data, normalized=True, overlap=5)
+fig.savefig("spot_infer_ybs_timeseries.pdf", bbox_inches="tight", dpi=300)

### 2021-09-14 src/figures/spot_setup.py

@@ -11,8 +11,12 @@ import starry
 
 # Instantiate the Doppler map
 data = generate_data()
-map = data["map"]
-theta = data["theta"]
+map = starry.DopplerMap(lazy=False, **data["kwargs"])
+map[:, :] = data["truths"]["y"]
+map.spectrum = data["truths"]["spectrum"]
+for n in range(map.udeg):
+    map[1 + n] = data["props"]["u"][n]
+theta = data["data"]["theta"]
 
 # Set up the plot
 fig = plt.figure(figsize=(11, 9))
@@ -140,8 +144,8 @@ for axis in [ax_data, ax_data_twin]:
         tick.label1.set_fontsize(10)
         tick.label2.set_fontsize(10)
 ax_data.margins(0, None)
-ax_data.set_ylim(0.35, 1.05)
-ax_data_twin.set_ylim(0.835, 1.0125)
+ax_data.set_ylim(0.05, 1.05)
+ax_data_twin.set_ylim(0.700, 1.0155)
 
 # We're done!
 fig.savefig("spot_setup.pdf", bbox_inches="tight", dpi=300)

### 2021-09-14 src/ms.tex
low snr

@@
         \includegraphics[width=0.59\linewidth]{figures/spot_infer_ybs_maps.pdf}
-        %\\[0.5em]
         \includegraphics[width=\linewidth]{figures/spot_infer_ybs_spectra.pdf}
@@
 
-% \begin{figure}[p!]
-%     \begin{centering}
-%         \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_low_snr_timeseries.pdf}
-%         \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_low_snr_rect.pdf}
-%         \\[0.5em]
-%         \includegraphics[width=0.405\linewidth]{figures/spot_y1bs_low_snr_baseline.pdf}
-%         \includegraphics[width=0.575\linewidth]{figures/spot_y1bs_low_snr_coeffs.pdf}
-%         \\[0.5em]
-%         \includegraphics[width=0.98\linewidth]{figures/spot_y1bs_low_snr_spectrum.pdf}
-%         \caption{%
-%             Same as Figure~\ref{fig:spot_y1bs}, but for $10\times$ lower SNR.
-%             We still recover the \spot map and the input spectrum, albeit with higher uncertainty, as expected.
-%         }
-%         \label{fig:spot_y1bs_low_snr}
-%     \end{centering}
-% \end{figure}
+\begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=0.39\linewidth]{figures/spot_infer_ybs_low_snr_timeseries.pdf}
+        \includegraphics[width=0.59\linewidth]{figures/spot_infer_ybs_low_snr_maps.pdf}
+        \includegraphics[width=\linewidth]{figures/spot_infer_ybs_low_snr_spectra.pdf}
+        \caption{%
+            Same as Figure~\ref{fig:spot_y1bs}, but for $10\times$ lower SNR.
+             We still recover the \spot map and the input spectrum, albeit with higher uncertainty, as expected.
+        }
+        \label{fig:spot_infer_ybs_low_snr}
+    \end{centering}
+\end{figure}
 

### 2021-09-15 src/ms.tex
[skip ci] more text, figs

@@
 %
-In the Appendix we derive an analytic solution to this integral and show how to recursively solve it for all terms in the spherical harmonic basis.
+In Appendix~\ref{app:kT} we derive an analytic solution to this integral and show how to recursively solve it for all terms in the spherical harmonic basis.
 Figure~\ref{fig:kT} shows the $\kT$ basis computed from the formulae above and Equation~(\ref{eq:kT:kT}) up to spherical harmonic degree $l_\mathrm{max}=10$.
@@
 %
-Unlike \citet{Vogt1987}, we add 20 additional small absorption lines at random positions throughout the spectrum, all of the same FWHM but of varying depths, including some line blends. 
+Unlike \citet{Vogt1987}, we add two additional small absorption lines, one of which is blended with the central absorption line.
 In total, the rest frame spectrum $\bvec{s}$ consists of $K = 200$ wavelength bins in the range $642.85~\mathrm{nm} \leq \lambda \leq 643.15~\mathrm{nm}$ plus an additional
@@
 We assume a wavelength-independent, quadratic limb darkening law with $u_1 = 0.5$ and $u_2 = 0.25$. 
-Finally, we divide the flux by the baseline at each epoch (Equation~\ref{eq:norm:f}) and add random Gaussian noise with covariance matrix $\bvec{\Sigma}_\bvec{f} = \sigma_\bvec{f}^2 \mathbf{I}$, with $\sigma_\bvec{f} = 10^{-4}$ to simulate a very high signal-to-noise ratio (SNR) spectrum.
-The mean standard deviation in each wavelength bin across all 16 epochs in the noiseless data vector is about $10^{-2}$, so our choice of $\sigma_\bvec{f}$ corresponds to SNR $\sim$ 100 in each of the 200 wavelength bins of $\bvec{f}$.
+Finally, we divide the flux by the baseline at each epoch (Equation~\ref{eq:norm:f}) and add random Gaussian noise with covariance matrix $\boldsymbol{\Sigma}_\bvec{f} = \sigma_\bvec{f}^2 \mathbf{I}$, with $\sigma_\bvec{f} = 2\times 10^{-4}$ to simulate a very high signal-to-noise ratio (SNR) spectrum.
+The mean standard deviation in each wavelength bin across all 16 epochs in the noiseless data vector is about $2\times 10^{-2}$, so our choice of $\sigma_\bvec{f}$ corresponds to SNR $\sim$ 100 in each of the 200 wavelength bins of $\bvec{f}$.
 
@@
 In the following sections we discuss various approaches to solving the Doppler imaging problem for this dataset.
-Unless otherwise noted, in all experiments we adopt a Gaussian prior for the spherical harmonic coefficients $\bvec{y}$ with mean $\boldsymbol{\mu}_\bvec{y} = \bvec{0}$ and covariance $\boldsymbol{\Lambda}_\bvec{y}$, with
-%
-\begin{align}
-    \label{eq:Lambday}
-    {\Lambda_\bvec{y}}_{i, j} 
-    =
-    \begin{cases}
-        1 & \quad\quad\quad\quad i = j = 0
-        \\
-        10^{-4}\delta_{ij} & \quad\quad\quad\quad \mathrm{otherwise}
-        \quad,
-    \end{cases}
-\end{align}
-%
-corresponding to a flat power spectrum prior.
-We also place a Gaussian prior on the spectrum $\bvec{s}$ with unit mean and covariance $\boldsymbol{\Lambda}_\bvec{s} = (10^{-1})^2\bvec{I}$.
+Unless otherwise noted, in all experiments we adopt a Gaussian prior for the spherical harmonic coefficients $\bvec{y}$ with mean $\boldsymbol{\mu}_\bvec{y} = \left(1 \quad\quad \bvec{0}\right)$ and covariance $\boldsymbol{\Lambda}_\bvec{y} = 10^{-4} \bvec{I}$, corresponding to a flat power spectrum prior.
+When solving for the rest frame spectrum, we also place a Gaussian prior on $\bvec{s}$ with unit mean and covariance $\boldsymbol{\Lambda}_\bvec{s} = 10^{-3}\bvec{I}$.
 
@@
 Note that we must first scale the data vector $\fnorm$ by the baseline (which in this case is known) to obtain $\bvec{f}$.
-The pseudocode for computing the maximum a posteriori (MAP) solution for $\bvec{y}$ and its covariance is given in Algorithm~\ref{alg:solve1}.
-
-\begin{algorithm}
-    \begin{spacing}{1.25}
-        \begin{fminipage}{0.98\textwidth}
-            \vspace{1em}
-            \begin{algorithmic}
-                \FUNCTION{solve1}($\bvec{f}$, $\boldsymbol{\Sigma}_\mathbf{f}$, $\boldsymbol{\mu}_\bvec{y}$, $\boldsymbol{\Lambda}_\bvec{y}$, $\bvec{s}$)
-                \STATE
-                $
-                \bvec{S} \gets \mathrm{blockDiag}(\bvec{s})
-                $
-                \STATE 
-                $
-                \boldsymbol{\Sigma}_\bvec{\hat{y}}
-                \gets
-                \left(
-                \bvec{S}^\top\Doppler^\top
-                {\boldsymbol{\Sigma}_\bvec{f}}^{-1}
-                \Doppler\bvec{S}
-                +
-                {\boldsymbol{\Lambda}_\bvec{y}}^{-1}
-                \right)^{-1}
-                $
-                \STATE 
-                $
-                \bvec{\hat{y}} 
-                \gets 
-                \boldsymbol{\Sigma}_\mathbf{\hat{y}}
-                \left(
-                \bvec{S}^\top\Doppler^\top
-                {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
-                \bvec{f}
-                +
-                {\boldsymbol{\Lambda}_\bvec{y}}^{-1} \boldsymbol{\mu}_\bvec{y}
-                \right)
-                $
-                \RETURN ($\bvec{\hat{y}}$, $\boldsymbol{\Sigma}_\mathbf{\hat{y}}$)
-                \ENDFUNCTION
-            \end{algorithmic}
-            \vspace{1em}
-        \end{fminipage}
-    \end{spacing}
-    \caption{Solution to the L2 linear least squares problem for the spherical harmonic representation $\bvec{\hat{y}}$ of the stellar surface map when the unnormalized spectral timeseries $\bvec{f}$ is known.
-    The $\mathrm{blockDiag}$ operation on the second line is given by Equation~(\ref{eq:inverse:S}).
-    \label{alg:solve1}}
-\end{algorithm}
 
@@
             The latter is the uncertainty associated with our particular choice of prior, as the southernmost latitudes of the star are never visible to the observer.
+            The optimization step in this experiment ran in under 1 second.
         }
@@
 
-The inferred map is nearly indistinguishable from the true map north of the equator.
-Regions south of the equator are almost never in view to the observer (below $-40^\circ$, they are \emph{never} in view); our inferred map is therefore informed primarily by our prior in southern latitudes.
-This is well captured by the uncertainty (bottom panel), which increases south of the equator, reaching a maximum at $-30^\circ$, below which the uncertainty is constant at about 13\%, a value associated with our particular choice of prior (Equation~\ref{eq:Lambday}).
+The inferred map very closely matches the true map, aside from a few small artifacts in the southern hemisphere.
+Note, importantly, that regions south of the equator are almost never in view to the observer (below $-40^\circ$, they are \emph{never} in view); our inferred map is therefore informed primarily by our prior in southern latitudes.
+This is well captured by the uncertainty (bottom panel), which increases south of the equator, reaching a maximum at $-30^\circ$, below which the uncertainty is constant at about 13\%, a value associated with our particular choice of prior.
 
@@
 This corresponds to the case discussed in
-\S\ref{sec:norm}, and is likely to be the most common application of the methodology presented in this work.
-
-\begin{algorithm}
-    \begin{spacing}{1.25}
-        \begin{fminipage}{0.98\textwidth}
-            \vspace{1em}
-            \begin{algorithmic}
-                \FUNCTION{solve2}($\fnorm$, $\boldsymbol{\sigma}_{\fnorm}$, $\boldsymbol{\mu}_\bvec{y}$, $\boldsymbol{\Lambda}_\bvec{y}$, $\bvec{s}$, $\sigma_b$, $\ln T_0$, $\Delta \ln T$)
-                \STATE $\bvec{b} \gets \bvec{1}$
-                \STATE $\ln T \gets \ln T_0$
-                \WHILE{$T > 1$}
-                    \STATE $
-                    \bvec{f} 
-                    \gets 
-                    \fnorm \circ \bvec{b}
-                    $
-                    \STATE $
-                    \boldsymbol{\sigma}_\mathbf{f} 
-                    \gets 
-                    \boldsymbol{\sigma}_{\fnorm} \circ \bvec{b}
-                    $
-                    \STATE $
-                    \boldsymbol{\Sigma}_\mathbf{f} 
-                    \gets 
-                    e^{\ln T} \mathrm{diag}(\boldsymbol{\sigma}_\mathbf{f}^2) + \sigma_b^2
-                    $
-                    \STATE 
-                    $
-                    (\bvec{\hat{y}}, \boldsymbol{\Sigma}_\bvec{\hat{y}})
-                    \gets
-                    $
-                    \texttt{\textbf{solve1}}($\bvec{f}$, $\boldsymbol{\Sigma}_\mathbf{f}$, $\boldsymbol{\mu}_\bvec{y}$, $\boldsymbol{\Lambda}_\bvec{y}$, $\bvec{s}$)
-                    \STATE $\bvec{b} \gets \bvec{B} \, \bvec{S} \, \bvec{\hat{y}} $
-                    \STATE $\ln T \gets \ln T - \Delta \ln T$
-                \ENDWHILE
-                \RETURN ($\bvec{\hat{y}}$, $\boldsymbol{\Sigma}_\mathbf{\hat{y}}$)
-                \ENDFUNCTION
-            \end{algorithmic}
-            \vspace{1em}
-        \end{fminipage}
-    \end{spacing}
-    \caption{Solution to the tempered, iterative problem for the spherical harmonic representation of the stellar surface map when the observed spectra $\fnorm$ have been normalized to the continuum.
-In addition to the data, priors, and model spectrum, this function accepts a baseline standard deviation $\sigma_b$, an initial temperature $\ln T_0$, and a temperature decrement $\Delta \ln T$; see text for details.
-    \label{alg:solve2}}
-\end{algorithm}
+\S\ref{sec:norm}, in which each spectrum is normalized to its continuum, and the true difference in continuum levels across spectral epochs is not precisely known.
+This is likely to be the most common application of the methodology presented in this work.
 
@@
 For this particular experiment, we set $\ln T_0 = 2$ and $\Delta \log T = -0.04$, for a total of $50$ steps of the bilinear solver.
-We also add a small variance term $\sigma_b^2 = 10^{-2}$ to all entries of the data covariance $\boldsymbol{\Sigma}_{\bvec{f}}$; this has the effect of marginalizing over an additive model term, which we find improves the convergence of the algorithm.
-The pseudocode for this procedure is presented in Algorithm~\ref{alg:solve2}.
+We also add a small variance term $\sigma_b^2 = 10^{-2}$ to all entries of the data covariance $\boldsymbol{\Sigma}_{\bvec{f}}$; this has the effect of marginalizing over a small additive model term, which we find improves the convergence of the algorithm.
 
@@
             regions south of the equator are almost never in view, so that portion of our inferred map is dominated by the prior.
+            Note that the uncertainty shown (lower panel) is a strict lower bound on the true uncertainty, as it is conditioned on our point estimate of the baseline level.
+            The optimization step in this experiment ran in about 5 seconds.
         }
@@
 
-Our results are shown in Figure~\ref{fig:spot_infer_yb}; compare to Figure~\ref{fig:spot_infer_y}.
-
-\xxx{WORK IN PROGRESS BELOW HERE}
-
-Finally, we note that the pixelwise uncertainty shown is a strict \emph{lower bound} on the map uncertainty, since it is the uncertainty conditioned on the inferred value of the baseline. 
-Sampling methods such as MCMC are required to obtain the \emph{true} uncertainty on the map. 
+Our results are shown in Figure~\ref{fig:spot_infer_yb}.
+As in the case where the continuum level was known exactly (Figure~\ref{fig:spot_infer_y}), we recover the stellar surface map with high fidelity in the northern hemisphere.
+However, there is now a strong dipolar artifact; the background intensity level is higher in the northern hemisphere than in the southern hemisphere.
+This is due to a degeneracy involving the $Y_{1,-1}$ spherical harmonic (\raisebox{-0.2em}{\includegraphics[width=1em]{figures/Y1m1.pdf}}), which, because a large portion of the southern hemisphere is never in view, cannot be constrained by the data.
+
+Interestingly, while the map uncertainty still increases toward the south pole (bottom panel), its magnitude is smaller than that in Figure~\ref{fig:spot_infer_y}.
+This is counter-intuitive, since the continuum-normalized spectrum should contain \emph{less} information than the unnormalized one.
+Indeed, the uncertainties shown in the figure are conditioned on our estimate of the baseline, so they are actually a strict \emph{lower bound} on the map uncertainty.
+In order to constrain the true uncertainty on the solution to this bilinear problem, we must resort to approximate sampling methods such as MCMC. 
 We discuss this further in \S\ref{sec:discussion}.
@@
         \includegraphics[width=0.59\linewidth]{figures/spot_infer_ybs_maps.pdf}
+        \vspace{1em}
         \includegraphics[width=\linewidth]{figures/spot_infer_ybs_spectra.pdf}
         \caption{%
-            Similar to Figure~\ref{fig:spot_y1}, but assuming we have no information about either the spectrum, the baseline, or the map coefficients. 
+            Similar to Figure~\ref{fig:spot_infer_y}, but assuming we have no information about either the spectrum, the baseline, or the map coefficients. 
             The bottommost panel now shows the true rest frame spectrum (blue line), the initial guess based on a deconvolution (dashed orange line), and the inferred spectrum (orange line, with shaded $1\sigma$ uncertainty).
+            The optimization step in this experiment ran in about 30 seconds.
         }
@@
         \caption{%
-            Same as Figure~\ref{fig:spot_y1bs}, but for $10\times$ lower SNR.
+            Same as Figure~\ref{fig:spot_infer_ybs}, but for $10\times$ lower SNR.
              We still recover the \spot map and the input spectrum, albeit with higher uncertainty, as expected.
+             Once again, the optimization step in this experiment ran in about 30 seconds.
         }
@@
 In practice, this is a fairly poor approximation, but we find that it suffices as an initial guess. 
-Given this starting value of $\bvec{s}$, we compute an initial guess for $\bvec{y_1}$ using the linear baseline approximation. 
-We then iterate between solving for $\bvec{s}$ and solving for $\bvec{y_1}$, always using the previous value of the baseline to compute $\bvec{y_1}$. 
-As in the previous section, we find it necessary to implement a tempering scheme, except with a much higher starting temperature $T_0 = 5,000$ and a slower decay $\Delta\log T = -0.04$.
-We again refine our solution with \texttt{NAdam}, this time setting $N_\mathrm{nadam} = 3,000$ and $L_\mathrm{nadam} = 2.5\times 10^{-5}$. 
-Since we are now solving for the spectrum as well, we include the negative log prior term for the spectrum, $\frac{1}{2}(\bvec{s - 1})^\top \boldsymbol{\Lambda}_\bvec{s}^{-1}(\bvec{s - 1})$, in Equation~(\ref{eq:spotstar:logP}).
-
-Figure~\ref{fig:spot_y1bs} shows the results. 
-The top portion of the figure is the same as before. 
-A panel at the bottom has been added showing the true rest frame spectrum (blue), the initial guess based on the deconvolution (dashed orange), and the inferred spectrum (orange). 
-We recover the \spot feature as before, albeit with more noise, particularly south of about $+30^\circ$ latitude. 
-Our uncertainties are somewhat underestimated, as expected, since they are computed conditioned on the optimum value of the spectrum. 
+We then iterate between solving for $\bvec{y}$ (\S\ref{sec:solve_y}) and solving for $\bvec{s}$ (\S\ref{sec:solve_s}), followed by a step in which we update our estimate of the baseline.
+We adopt the same tempering scheme discussed above.
+
+Figure~\ref{fig:spot_infer_ybs} shows the results; 
+the top portion of the figure is the same as in Figure~\ref{fig:spot_infer_yb}.
+A panel has been added at the bottom showing the true rest frame spectrum (blue), the initial guess based on the deconvolution (dashed orange), and the inferred spectrum with 1-$\sigma$ uncertainty shading (orange).
+We recover the \spot feature as before, albeit with more noise, particularly south of the equator. 
+Once again, our map uncertainties are somewhat underestimated, as expected, since they are computed conditioned on the optimum value of the baseline and the spectrum. 
 On the other hand, we recover the spectrum exceedingly well, with low uncertainty and virtually no bias anywhere.
 
-To test our technique on more realistic data, in Figure~\ref{fig:spot_y1bs_low_snr} we repeat the experiment on data with $10$ times higher uncertainty, setting $\sigma_\bvec{f} = 10^{-3}$. 
-Because the higher uncertainty increases the volume of the region surrounding the global optimum, it is actually significantly \emph{easier} for the algorithm to converge on the best solution, so we set $T_0 = 500$, $\Delta\log T = -0.05$, $N_\mathrm{nadam} = 500$, and $R_\mathrm{nadam} = 10^{-4}$.
-Interestingly, while the uncertainty on the spectrum increased, the quality of the recovered \spot map did not noticeably degrade. 
-This suggests we did not quite find the global optimum in Figure~\ref{fig:spot_y1bs}. 
-We discuss this further in \S\ref{sec:discussion}.
+To test our technique on more realistic data, we repeat the experiment on data with $10$ times higher uncertainty, setting $\sigma_\bvec{f} = 2\times 10^{-3}$.
+%
+After some tuning, we find it necessary to increase our prior variances slightly to get good fits to the data: we set $\boldsymbol{\Lambda}_\bvec{y} = 2.5\times 10^{-4} \bvec{I}$ and $\boldsymbol{\Lambda}_\bvec{s} = 5\times 10^{-3}\bvec{I}$.
+%
+Figure~\ref{fig:spot_infer_ybs_low_snr} shows the results.
+We again correctly infer the \spot feature and the rest frame spectrum, although the surface map is considerably degraded, particularly at high spatial frequencies.
 
@@
 Figure~\ref{fig:snr} shows the effect of different SNR on the quality of the inferred map. 
-As before, the SNR we report is the ratio of the standard deviation of the true model in each wavelength bin across all epochs, averaged over all wavelength bins (i.e., the ``signal'') to the standard deviation of the added noise term, $\sigma_\bvec{f}$ (the ``noise'').
+As before, the SNR we report is the ratio of the standard deviation of the true model in each wavelength bin across all epochs, averaged over all wavelength bins (i.e., the ``signal''), to the standard deviation of the added noise term, $\sigma_\bvec{f}$ (the ``noise'').
 The panels in Figure~\ref{fig:snr} show the inferred map for SNR in the range 1---1000, where SNR $\sim 100$ is the fiducial case considered in the examples so far. 
@@
 As the SNR incraeses, however, the quality of the \spot feature does not improve appreciably, since a SNR of 100 is more than sufficient to recover a $l_\mathrm{max} = 15$ band-limited map. 
-Interestingly, south of the equator, the map quality actually begins to degrade with higher SNR. 
-This is due to the fact that finding the global optimum becomes exponentially more difficult with higher SNR, as the posterior volume becomes ever smaller. 
-Even with aggressive tempering, we were unable to converge on the best solution for SNR $\gtrsim 500$ given our standard, conservative priors and initial guesses (\S\ref{sec:spotstar}).
-%
-% \begin{figure}[p!]
-%     \begin{centering}
-%         \includegraphics[width=0.98\linewidth]{figures/snr.pdf}
-%         \caption{%
-%             Recovered \spot map as a function of SNR per resolution element.
-%             The quality of the inferred map in the northern hemisphere improves with SNR, but at very high SNR the region surrounding the global optimum becomes so small that our optimization methods struggle to converge on the correct solution.
-%         }
-%         \label{fig:snr}
-%     \end{centering}
-% \end{figure}
+Interestingly, at constant spatial prior variance ($\boldsymbol{\Lambda}_\bvec{y} = 10^{-4}\bvec{I}$), the map quality actually begins to degrade with higher SNR south of the equator due to overfitting.
+To circumvent this, we decrease the prior variance by a factor of 10--100 for the highest SNR cases, which penalizes excessive complexity in the solution.
+
+%
+\begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=0.98\linewidth]{figures/snr.pdf}
+        \caption{%
+            Recovered \spot map as a function of SNR per resolution element. The observed spectra are continuum-normalized and the rest frame spectrum is assumed to be known exactly.
+        }
+        \label{fig:snr}
+    \end{centering}
+\end{figure}
 
@@
 %
-% \begin{figure}[p!]
-%     \begin{centering}
-%         \includegraphics[width=0.98\linewidth]{figures/inclinations.pdf} % 
-%         \caption{%
-%             Recovered \spot map as a function of stellar inclination. 
-%             The rest frame spectrum is assumed to be known exactly, but the baseline is not. 
-%             At very low inclinations, the small projected velocities begin to degrade the spatial resolution of the inferred map, while at inclinations close to $90^\circ$ there is a degeneracy between the northern and southern hemispheres.
-%         }
-%         \label{fig:inclinations}
-%     \end{centering}
-% \end{figure}
+\begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=0.98\linewidth]{figures/inclinations.pdf} % 
+        \caption{%
+            Recovered \texttt{STAR SPOT} map as a function of stellar inclination. 
+            The observed spectra are continuum-normalized and the rest frame spectrum is assumed to be known exactly.
+            In general, it is very difficult to infer features in the hemisphere facing away from the observer (in this case, the southern hemisphere).
+At low inclinations, those features are never in view, while at inclinations close to 90$^\circ$, it becomes difficult to differentiate between features above and below the equator.
+        }
+        \label{fig:inclinations}
+    \end{centering}
+\end{figure}
 %
@@
 \section{Solving the $\kT$ integral}
+\label{app:kT}
 %

### 2021-09-15 src/figures/snr.py

@@ -1,0 +1,83 @@
+"""
+Investigate how our recovered map varies with the
+signal to noise ratio of the data.
+
+"""
+from utils.generate import generate_data
+import starry
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.colors import Normalize
+
+# Settings
+ydeg = 15
+smoothing = 0.075
+
+# Compute model at infinite SNR to get the "signal"
+# This is the standard deviation in each wavelength
+# bin across all epochs.
+data = generate_data(flux_err=0, ydeg=ydeg, smoothing=smoothing)
+theta = data["data"]["theta"]
+flux = data["data"]["flux"]
+signal = np.mean(np.std(flux, axis=0))
+
+# Compute the pointwise uncertainty for a given SNR
+snrs = np.array([1.0, 2.0, 5.0, 10.0, 50.0, 100.0, 200.0, 500.0, 1000.0])
+spatial_cov = np.minimum(1e-4, 1e-4 * (100 / snrs) ** 2)
+flux_errs = signal / snrs
+
+# Plot the true map
+fig, ax = plt.subplots(4, 3, figsize=(15, 10))
+ax[0, 0].set_visible(False)
+ax[0, 2].set_visible(False)
+map = starry.Map(ydeg=ydeg)
+map.load("spot", smoothing=smoothing)
+map.show(ax=ax[0, 1], projection="moll")
+ax[0, 1].annotate(
+    r"true",
+    xy=(0, 1),
+    xytext=(7, 7),
+    clip_on=False,
+    xycoords="axes fraction",
+    textcoords="offset points",
+    ha="left",
+    va="top",
+    fontsize=14,
+    color="k",
+    zorder=101,
+)
+
+# Instantiate the map we'll use for inference
+map = starry.DopplerMap(lazy=False, **data["kwargs"])
+map.spectrum = data["truths"]["spectrum"]
+for n in range(map.udeg):
+    map[1 + n] = data["props"]["u"][n]
+
+# Solve & plot
+ax = ax[1:].flatten()
+for i, flux_err in enumerate(flux_errs):
+
+    soln = map.solve(
+        flux + flux_err * np.random.randn(*flux.shape),
+        theta=theta,
+        normalized=True,
+        fix_spectrum=True,
+        flux_err=flux_err,
+        spatial_cov=spatial_cov[i],
+    )
+
+    map.show(ax=ax[i], projection="moll", norm=Normalize(vmin=0, vmax=0.5))
[…]

### 2021-09-15 src/figures/twospec.py

@@ -1,0 +1,188 @@
+import starry
+from pathlib import Path
+import numpy as np
+import matplotlib.pyplot as plt
+import starry
+import george
+import pymc3 as pm
+import pymc3_ext as pmx
+import theano.tensor as tt
+from tqdm.auto import tqdm
+import json
+import sys
+
+# Pass `--clobber` when running this script to force rerun
+if "--clobber" in sys.argv:
+    clobber = True
+else:
+    clobber = False
+
+# Dataset settings
+flux_err = 1e-4
+ydeg = 15
+nt = 16
+inc = 40
+veq = 60000
+wav = np.linspace(642.85, 643.15, 200)
+wav0 = np.linspace(642.75, 643.25, 200)
+u = [0.5, 0.25]
+
+# True maps
+starry_path = Path(starry.__file__).parents[0]
+image1 = np.mean(
+    np.flipud(plt.imread(starry_path / "img" / "spot.png"))[:, :, :3],
+    axis=2,
+)
+image2 = 1 - image1
+
+# True intensity ratio (spot / photosphere)
+ratio = 0.5
+
+# True spectra (photosphere and spot)
+spectrum1 = 1.0 - 0.925 * np.exp(-0.5 * (wav0 - 643.0) ** 2 / 0.0085 ** 2)
+spectrum2 = (
+    1.0
+    - 0.63 * np.exp(-0.5 * (wav0 - 642.97) ** 2 / 0.0085 ** 2)
+    - 0.6 * np.exp(-0.5 * (wav0 - 643.08) ** 2 / 0.0085 ** 2)
+)
+
+# Optimization settings
+niter = 100000
+lr = 1e-4
+
+# Prior on the spectra
+spectral_mean1 = np.ones_like(wav0)
+spectral_mean2 = np.ones_like(wav0)
+spectral_cov1 = 1e-3 * np.ones_like(wav0)
+spectral_cov2 = 1e-3 * np.ones_like(wav0)
+
+# Instantiate the map
+map = starry.DopplerMap(
+    ydeg=ydeg,
+    udeg=len(u),
+    nc=2,
+    veq=veq,
+    inc=inc,
+    nt=nt,
+    wav=wav,
+    wav0=wav0,
+    lazy=False,
+    vsini_max=40000,
+)
+map.load(
+    maps=[image1, image2],
+    spectra=[spectrum1, ratio * spectrum2],
+    smoothing=0.075,
+)
+for n in range(len(u)):
[…]

### 2021-09-16 src/ms.tex
lots of updates

@@
 
-% \begin{figure}[t!]
-%     \begin{centering}
-%         \includegraphics[width=\linewidth]{figures/twospec.pdf}
-%         \caption{%
-%             An example of a star whose spectrum is different within the spot (\texttt{B}) and outside of the spot (\texttt{A}). 
-%             Everywhere on the surface, the spectrum is a linear combination of two spectral components ($s_1$ and $s_2$).
-%             As in Figure~\ref{fig:spot_y1bs}, we assume we do not know the map, the baseline, or either of the spectra.
-%             The top row shows the true values for the map and the spectra, and the bottom row shows our inferred values. 
-%         }
-%         \label{fig:twospec}
-%     \end{centering}
-% \end{figure}
+\begin{figure}[t!]
+    \begin{centering}
+        \includegraphics[width=0.39\linewidth]{figures/twospec_timeseries.pdf}
+        \includegraphics[width=0.59\linewidth]{figures/twospec_maps.pdf}
+        \includegraphics[width=\linewidth]{figures/twospec_spectra1.pdf}
+        \includegraphics[width=\linewidth]{figures/twospec_spectra2.pdf}
+        \caption{%
+            An example of a star whose spectrum is different within the spot and outside of the spot.
+        }
+        \label{fig:twospec}
+    \end{centering}
+\end{figure}
 
@@
 As in \citet{Vogt1987}, we also investigate the dependence of the solution on the inclination of the star.
-Figure~\ref{fig:inclinations} shows the inferred map for the same problem setup as before (with SNR $\sim 100$), but this time varying the inclination between $10^\circ$ (nearly face-on) and $90^\circ$ (perfectly edge-on).
+Figure~\ref{fig:inclinations} shows the inferred map for the same problem setup as before, but this time varying the inclination between $10^\circ$ (nearly face-on) and $90^\circ$ (perfectly edge-on).
+We also use a different surface map, this time with the word \texttt{STAR} in the northern hemisphere and the word \texttt{SPOT} in the southern hemisphere, to assess our ability to infer information across the entire stellar surface.
+\xxx{Given the added complexity of the map, we increase the spherical harmonic degree to} $l_\mathrm{max} = 20$, increase the SNR of our data to 200, and set the covariance of the spatial prior to $\boldsymbol{\Lambda}_\bvec{y} = 3\times 10^{-5}\bvec{I}$.
 As before, the inclination is assumed to be known exactly. 
-We further keep the true equatorial velocity of the star constant across all panels, so that the figure corresponds to the same star viewed at different orientations. 
+\xxx{We further keep the true equatorial velocity of the star constant} across all panels, so that the figure corresponds to the same star viewed at different orientations. 
 Because of this, decreasing the inclination decreases $v\sin i$, reducing the width of the convolution kernel and therefore the spatial resolution of our inferred map. 

### 2021-09-16 src/figures/spot.py

@@ -28,7 +28,7 @@ F0 = flux[0]
 F = flux[1:]
 
 # Render the images
-img = spot_map.render(theta=theta[1:], res=300)
+img = map.render(theta=theta[1:], res=300)
 assert np.nanmin(img) > 0
 
 # Set up the plot

### 2021-09-16 src/figures/utils/plot.py

@@ -86,7 +86,9 @@ def plot_timeseries(
     return fig
 
 
-def plot_maps(y_true, y_inferred, y_uncert, y_uncert_max=0.15, quantile=0.995):
+def plot_maps(
+    y_true, y_inferred, y_uncert=None, y_uncert_max=0.15, quantile=0.995
+):
     # Set up the plot
     fig, ax = plt.subplots(3, figsize=(8, 11.5))
     fig.subplots_adjust(hspace=0.3)
@@ -147,47 +149,51 @@ def plot_maps(y_true, y_inferred, y_uncert, y_uncert_max=0.15, quantile=0.995):
     )
 
     # Plot the pixel uncertainty image
-    map[:, :] = y_uncert
-    image = map.render(projection="moll")
-    image /= max_inf
-    map.show(
-        ax=ax[2],
-        image=image,
-        projection="moll",
-        colorbar=True,
-        colorbar_size="3%",
-        colorbar_pad=0.1,
-        norm=Normalize(vmin=0, vmax=y_uncert_max),
-    )
-    cax = fig.axes[-1]
-    cax.yaxis.set_major_formatter(FormatStrFormatter("%.2f"))
-    ax[2].annotate(
-        "uncert",
-        xy=(0, 1),
-        xycoords="axes fraction",
-        xytext=(10, -5),
-        textcoords="offset points",
-        ha="left",
-        va="top",
-        fontsize=16,
-    )
+    if y_uncert is None:
+        ax[2].axis("off")
+    else:
+        map[:, :] = y_uncert
+        image = map.render(projection="moll")
+        image /= max_inf
+        map.show(
+            ax=ax[2],
+            image=image,
+            projection="moll",
+            colorbar=True,
+            colorbar_size="3%",
+            colorbar_pad=0.1,
+            norm=Normalize(vmin=0, vmax=y_uncert_max),
+        )
+        cax = fig.axes[-1]
+        cax.yaxis.set_major_formatter(FormatStrFormatter("%.2f"))
+        ax[2].annotate(
+            "uncert",
+            xy=(0, 1),
+            xycoords="axes fraction",
+            xytext=(10, -5),
+            textcoords="offset points",
+            ha="left",
+            va="top",
+            fontsize=16,
+        )
 
     return fig
 
 
-def plot_spectra(wav, wav0, s_true, s_guess, s_inferred, s_uncert):
[…]

### 2021-09-17 src/ms.tex
woot

@@
 The problem setup is the same as that discussed in \S\ref{sec:eigen}, where our full map vector $\bvec{a}$ is the outer product of a spectral matrix $\mathbb{S}$, whose $J$ columns are the different spectral components, and a spherical harmonic coefficient matrix $\mathbb{Y}^\top$, whose $J$ rows are the corresponding coefficient vectors.
-For simplicity, in this experiment we consider only $J = 2$ spectral components and further require that the first component is spatially constant, i.e., the first row of $\mathbb{Y}^\top$ is the vector $(1 \quadquad \bvec{0}^\top)$.
-The second row of $\mathbb{Y}^\top$ is the vector $(1 \quadquad \bvec{y_1}^\top)$, where $\bvec{y_1}$ is the (unknown) spherical harmonic expansion of the spot. 
-The two columns of $\mathbb{S}$ are $\bvec{s_1}$ and $\bvec{s_2}$, the unknown spectral components.
-
-\begin{figure}[t!]
+For simplicity, in this experiment we consider only $J = 2$ map components and further require that the surface map for the second component is the complement of the surface map for the first component.
+Specifically, the first component map ($\bvec{y_0}$, the first row of $\mathbb{Y}^\top$) corresponds to the background photosphere, whose value is unity everywhere except within the \texttt{SPOT} feature, where the value is zero.
+The second component map ($\bvec{y_1}$, the second row of $\mathbb{Y}^\top$) corresponds to the spot and is zero in the photosphere and unity within the spot.
+The two columns of $\mathbb{S}$ are $\bvec{s_0}$ and $\bvec{s_1}$, the unknown spectral components corresponding to the photosphere and the spot, repsectively.
+%
+\begin{figure}[p!]
     \begin{centering}
@@
             An example of a star whose spectrum is different within the spot and outside of the spot.
+            We are able to infer both the surface map of the star (upper right) and the two component spectra (lower two panels), assuming virtually no prior knowledge of either.
         }
@@
 \end{figure}
-
-We set \bvec{s_1} equal to a flat spectrum with two absorption lines of different depths, and \bvec{s_2} to the same spectrum, except we make the second line an emission feature. 
-The local rest-frame spectrum everywhere on the surface is a linear combination of these two spectra. 
-In our simple problem, the weight given to the first spectrum is the same everywhere (encoded in the first row of $\mathbb{Y}^\top$), and the weight given to the second spectrum is large outside of the spot and small within the spot (encoded in the second row of $\mathbb{Y}^\top$, which we set equal to the spherical harmonic expansion of the \spot feature).
-The first row of Figure ~\ref{fig:twospec} shows the problem setup. 
-The two spectral components are shown as the blue ($\bvec{s_1}$) and green ($\bvec{s_2}$) curves at the right. 
-Point \texttt{A} on the map (left panel) is outside the spot feature, so its local spectrum has nearly equal contributions from $\bvec{s_1}$ and $\bvec{s_2}$, and the second spectral line is absent (center panel).
-Point \texttt{B} is inside the spot, so it receives a contribution from $\bvec{s_1}$ only.
+%
+We set $\bvec{s_0}$ to unity everywhere, with an absorption feature at $643$~nm similar to the one in the previous experiments.
+The spot spectrum $\bvec{s_1}$ corresponds to two absorption lines on either side of this feature, and the baseline intensity is set to half that of the photospheric background.
+%
+The rest frame spectrum at any point on the surface of the star is then a linear combination of $\bvec{s_0}$ and $\bvec{s_1}$, weighted by the respective surface maps $\bvec{y_0}$ and $\bvec{y_1}$.
+%
+We generate the synthetic dataset in the same way as in \S\ref{sec:spot_y1}: 16 spectra, each with 200 wavelength bins observed with SNR$\sim$100.
 
 In our inference step, we again assume we have no knowledge of the map, the baseline, or either of the spectral components.
-As before, we initialize $\bvec{s_1}$ to the deconvolved mean spectrum and $\bvec{s_2}$ to the deconvolved mean spectrum after subtracting $\bvec{s_1}$. 
-In practice this leads to a decent approximation to $\bvec{s_1}$ but a rather featureless guess for $\bvec{s_2}$. 
-We use the same priors as before, except we set $\sigma_\bvec{s_1} = \sigma_\bvec{s_2} = 0.01$ to force the continuum to be flatter. 
-We run our bilinear solver with $T_0 = 5,000$ and $\Delta\log T = -0.025$ followed by the nonlinear solver with $N_\mathrm{nadam} = 2,000$ and $L_\mathrm{nadam} = 3\times 10^{-4}$.
+While our bilinear method (\S\ref{sec:spot_y1bs}) could in principle work here, we find that in practice it is very difficult to converge on the global optimum without either good priors or a good initial guess.
+We therefore optimize our model using the nonlinear gradient-descent \texttt{Adam} optimizer \citep{Adam} within the \texttt{pymc3} probabilistic modeling framework \citep{Salvatier2016}.
+Since we are no longer restricted to using Gaussian priors on the variables (a requirement of our bilinear method), we place a unit-mean Laplacian (sparsity) prior on the two spectra with scale parameter $b = 10^{-3}$ and bounded to the range $[0, 1]$.
+%
+We further place a Gaussian Process prior on the spectra to enforce smoothness, adopting a squared exponential kernel with amplitude $10^{-1}$ and lengthscale $10^{-2}$~nm.
+%
+We also solve for a single scale parameter $r \sim \mathrm{Uniform}(0, 1)$, equal to the ratio of the continuum levels of the two spectra (whose true value is 0.5).
+Finally, in order to enforce that the two component surface maps sum to unity (as described above), we optimize for the actual \emph{pixel} intensities of the photosphere map, on which we place a simple uniform prior on $[0, 1]$; the spot map is then simply the complement.
+The spherical harmonic coefficients are then computed via a fast, linear spherical harmonic transform (SHT) operation at each step.
+In order to satisfy the Nyquist criterion, our pixel grid consists of twice as many pixels as spherical harmonic coefficients.
+
+We initialize our two maps with uniform intensities and initialize our two spectra at unity, with small random negative deviations to break the symmetry.
+We then take 20,000 steps of the optimizer with a learning rate of $10^{-2}$.
 
 The results are shown in the bottom panel of Figure~\ref{fig:twospec}.
-We recover the \spot feature reasonably well, although with more artifacts than in the previous experiments. 
-We also recover the two spectral components, although our solution for $\bvec{s_2}$ is significantly better than that for $\bvec{s_1}$. 
-This is due to the fact that the only information about $\bvec{s_1}$ that makes it into our dataset is the convolution of $\bvec{s_1}$ with the first term of the convolution kernel $\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{figures/kT00.pdf}}), since this spectral component has no spatial variability.
-Since the deconvolution operation is in general ill-posed, there is no unique solution for $\bvec{s_1}$. 
-On the other hand, the other spectral component projects into the data via convolutions with all other terms of the kernel and is therefore very well constrained.
-Finally, we can estimate the spectra at points \texttt{A} and \texttt{B} as before (center panel). 
-We recover the single spectral line at \texttt{A} and the two lines at \texttt{B}, albeit rather noisily due to the uncertainty in $\bvec{s_1}$.
+Even though we assume no knowledge of the surface map---except its intensity is bounded in $[0, 1]$---we are able to recover the \spot feature just as well as in the previous experiments.
+We also recover the two spectral components quite well.
+Our solution for the photospheric component, however, is noticeably better than that for the spot component, simply because effective SNR of the former is larger due to its greater surface area and higher baseline intensity.
+We also slightly overestimate the baseline level of the spot spectrum, but we correctly recover the locations, shapes, and depths of the two absorption lines.
 

### 2021-09-17 src/figures/twospec.py

@@ -8,7 +8,6 @@ import pymc3 as pm
 import pymc3_ext as pmx
 import theano.tensor as tt
 from tqdm.auto import tqdm
-import json
 
 
 np.random.seed(0)
@@ -49,9 +48,11 @@ spectrum2 = (
 
 
 # Optimization settings
-niter = 20000
-lr = 1e-2
-sb = 1e-3
+niter = 20000  # Number of iterations
+lr = 1e-2  # Adam learning rate
+sb = 1e-3  # Laplacian regularization strength for the spectrum
+wl = 1e-2  # GP lengthscale for the spectrum (nm)
+wa = 1e-1  # GP amplitude for the spectrum
 
 
 # Instantiate the map
@@ -162,6 +163,18 @@ with pm.Model() as model:
         axis=0,
     )
 
+    # Enforce smoothness with a Squared Exponential GP on the spectra
+    kernel = wa ** 2 * pm.gp.cov.ExpQuad(1, wl)
+    cov = kernel(wav0[:, None]).eval() + 1e-6 * np.eye(map.nw0)
+    smoothness1 = pm.Potential(
+        "smoothness1",
+        pm.MvNormal.dist(mu=np.ones(map.nw0), cov=cov).logp(spectrum1),
+    )
+    smoothness2 = pm.Potential(
+        "smoothness2",
+        pm.MvNormal.dist(mu=np.ones(map.nw0), cov=cov).logp(spectrum2),
+    )
+
     # Compute the model
     flux_model = map.flux(theta=theta)
 
@@ -176,52 +189,34 @@ with pm.Model() as model:
     )
 
 
-# TODO: Get rid of this
-# Run the optimizer or load the saved MAP solution
-file = Path("twospec_map_soln.json")
-if True:
+# Optimize!
+loss = []
+best_loss = np.inf
+map_soln = model.test_point
+iterator = tqdm(
+    pmx.optim.optimize_iterator(pmx.optim.Adam(lr=lr), niter, start=map_soln),
+    total=niter,
+)
+with model:
+    for obj, point in iterator:
+        iterator.set_description(
+            "loss: {:.3e} / {:.3e}".format(obj, best_loss)
+        )
+        loss.append(obj)
+        if obj < best_loss:
+            best_loss = obj
+            map_soln = point
 
-    # Optimize!
-    loss = []
-    best_loss = np.inf
-    map_soln = model.test_point
-    with model:
[…]

### 2021-09-17 src/figures/utils/plot.py

@@ -20,7 +20,12 @@ def maxq(x, quantile=None):
 
 
 def plot_timeseries(
-    data, y_inferred, spectrum_inferred, normalized=False, overlap=8.0
+    data,
+    y_inferred,
+    spectrum_inferred,
+    normalized=False,
+    overlap=8.0,
+    figsize=(5, 11.5),
 ):
     # Get the data
     theta = data["data"]["theta"]
@@ -39,7 +44,7 @@ def plot_timeseries(
     model = map.flux(theta, normalize=normalized).reshape(map.nt, -1)
 
     # Plot the "Joy Division" graph
-    fig = plt.figure(figsize=(5, 11.5))
+    fig = plt.figure(figsize=figsize)
     ax_img = [
         plt.subplot2grid((map.nt, 8), (n, 0), rowspan=1, colspan=1)
         for n in range(map.nt)
@@ -87,10 +92,19 @@ def plot_timeseries(
 
 
 def plot_maps(
-    y_true, y_inferred, y_uncert=None, y_uncert_max=0.15, quantile=0.995
+    y_true,
+    y_inferred,
+    y_uncert=None,
+    y_uncert_max=0.15,
+    quantile=0.995,
+    figsize=(8, 11.5),
 ):
     # Set up the plot
-    fig, ax = plt.subplots(3, figsize=(8, 11.5))
+    if y_uncert is None:
+        nrows = 2
+    else:
+        nrows = 3
+    fig, ax = plt.subplots(nrows, figsize=figsize)
     fig.subplots_adjust(hspace=0.3)
     norm01 = Normalize(vmin=0, vmax=1)
 
@@ -149,9 +163,7 @@ def plot_maps(
     )
 
     # Plot the pixel uncertainty image
-    if y_uncert is None:
-        ax[2].axis("off")
-    else:
+    if y_uncert is not None:
         map[:, :] = y_uncert
         image = map.render(projection="moll")
         image /= max_inf
@@ -180,8 +192,10 @@ def plot_maps(
     return fig
 
 
-def plot_spectra(wav, wav0, s_true, s_guess, s_inferred, s_uncert=None):
-    fig, ax = plt.subplots(1, figsize=(8, 2.5))
+def plot_spectra(
+    wav, wav0, s_true, s_guess, s_inferred, s_uncert=None, figsize=(8, 2.5)
+):
+    fig, ax = plt.subplots(1, figsize=figsize)
 
[…]

### 2021-09-17 src/ms.tex
tweaks

@@
 \include{style}
+
+% TIMING RESULTS
+\def\timeInferY{under 1 second}
+\def\timeInferYB{about 5 seconds}
+\def\timeInferYBS{about 30 seconds}
+\def\timeInferYBSLOSNR{about 30 seconds}
+\def\timeInferTwoSpec{about 20 minutes}
 
@@
 %
-\author{David W. 
-Hogg}
+\author{Lily Zhao}
+\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
+%
+\author{David W. Hogg}
 \affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
@@
             The latter is the uncertainty associated with our particular choice of prior, as the southernmost latitudes of the star are never visible to the observer.
-            The optimization step in this experiment ran in under 1 second.
+            The optimization step in this experiment ran in \timeInferY.
         }
@@
             Note that the uncertainty shown (lower panel) is a strict lower bound on the true uncertainty, as it is conditioned on our point estimate of the baseline level.
-            The optimization step in this experiment ran in about 5 seconds.
+            The optimization step in this experiment ran in \timeInferYB.
         }
@@
             The bottommost panel now shows the true rest frame spectrum (blue line), the initial guess based on a deconvolution (dashed orange line), and the inferred spectrum (orange line, with shaded $1\sigma$ uncertainty).
-            The optimization step in this experiment ran in about 30 seconds.
+            The optimization step in this experiment ran in \timeInferYBS.
         }
@@
              We still recover the \spot map and the input spectrum, albeit with higher uncertainty, as expected.
-             Once again, the optimization step in this experiment ran in about 30 seconds.
+             Once again, the optimization step in this experiment ran in \timeInferYBSLOSNR.
         }
@@
             We are able to infer both the surface map of the star (upper right) and the two component spectra (lower two panels), assuming virtually no prior knowledge of either.
+            The optimization step in this experiment ran in \timeInferTwoSpec.
         }
@@
 We also slightly overestimate the baseline level of the spot spectrum, but we correctly recover the locations, shapes, and depths of the two absorption lines.
+Note, importantly, that the nonlinear optimization step does not yield uncertainties (or lower bounds, like the bilinear solver); for this, we must resort to MCMC sampling (see \S\ref{sec:discussion}).
 
@@
 As may be expected, the quality of the map decreases with lower SNR, but a reduction of the SNR by $\sim 20\times$ still allows for reasonable recovery of the \spot feature. 
-In general, as the SNR decreases further, two things happen: the \spot contrast decreases, and the features begin to blur out, especially south of about $+30^\circ$ latitude, where features are more limb-darkened at this inclination and in view for a smaller fraction of the time.
+In general, as the SNR decreases further, the features begin to blur out, especially south of about $+30^\circ$ latitude, where features are more limb-darkened at this inclination and in view for a smaller fraction of the time.
 
@@
 %
-\begin{figure}[p!]
+\begin{figure}[t!]
     \begin{centering}
@@
         \caption{%
-            Recovered \texttt{STAR SPOT} map as a function of stellar inclination. 
+            Recovered \texttt{SPOT} map as a function of stellar inclination. 
             The observed spectra are continuum-normalized and the rest frame spectrum is assumed to be known exactly.
@@
 Figure~\ref{fig:inclinations} shows the inferred map for the same problem setup as before, but this time varying the inclination between $10^\circ$ (nearly face-on) and $90^\circ$ (perfectly edge-on).
-We also use a different surface map, this time with the word \texttt{STAR} in the northern hemisphere and the word \texttt{SPOT} in the southern hemisphere, to assess our ability to infer information across the entire stellar surface.
-\xxx{Given the added complexity of the map, we increase the spherical harmonic degree to} $l_\mathrm{max} = 20$, increase the SNR of our data to 200, and set the covariance of the spatial prior to $\boldsymbol{\Lambda}_\bvec{y} = 3\times 10^{-5}\bvec{I}$.
-As before, the inclination is assumed to be known exactly. 
-\xxx{We further keep the true equatorial velocity of the star constant} across all panels, so that the figure corresponds to the same star viewed at different orientations. 
+We also add four small circular features at $-45^\circ$ latitude to test our ability to infer features in the southern hemisphere (i.e., the side of the star facing away from the observer).
+We set the covariance of the spatial prior to $\boldsymbol{\Lambda}_\bvec{y} = 3\times 10^{-5}\bvec{I}$ and, as before, assume the inclination to be known exactly. 
+We further keep the true equatorial velocity of the star constant at $60$~km/s across all panels, so that the figure corresponds to the same star viewed at different orientations. 
 Because of this, decreasing the inclination decreases $v\sin i$, reducing the width of the convolution kernel and therefore the spatial resolution of our inferred map.
@@
 At $i = 90^\circ$, there is a formal degeneracy between the two hemispheres, which can be seen from the mirror-image symmetry in the inferred map. 
+Finally, as expected, the features in the southern hemisphere are not recovered below inclinations of about $60^\circ$, as they are never actually in view.
+At an inclination of $80^\circ$m tge spots are recovered fairly well, but never with as high fidelity as features in the observer-facing hemisphere.
 These results are broadly consistent with those of \citet{Vogt1987}.
@@
         $\almt$                                              & vector of spectral spherical harmonic coefficients          & Equation~(\ref{eq:deconv:almt})             \\
-        $\bvec{a}$                                          & $\almt$ at reference time $t = t_0$                          & Equation~(\ref{eq:deconv:R})               \\
         $\bvec{A}$                                          & matrix form of $\bvec{a}$                                    & Equation~(\ref{eq:inverse:alm})          \\
@@
         $l$                                                 & spherical harmonic degree                                    &                                            \\
-        $L_\mathrm{nadam}$                                  & \texttt{NAdam} learning rate                                 & \S\ref{sec:spotstar}                       \\
         $\bvec{L}$                                          & limb darkening operator                                      & Equation~(\ref{eq:ld:L})                   \\
         $m$                                                 & spherical harmonic order                                     &                                            \\
-        $N_\mathrm{nadam}$                                  & number of \texttt{NAdam} iterations                          & \S\ref{sec:spotstar}                       \\
         $\bvec{P}$                                          & Change of basis matrix from $Y_{lm}$ to pixels               & Equation~(\ref{eq:spotstar:uncert})        \\

### 2021-09-17 src/ms.tex
syw update

@@
 
-The observed spectrum is a complex function of spatial, spectral, temporal, and velocity terms. 
+The observed spectrum is an intricate function of spatial, spectral, temporal, and velocity terms. 
 The goal in this section is to deconvolve each of these terms to make solving the integral in Equation~(\ref{eq:the_problem:F}) easier.
@@
     \label{eq:kT:beta}
-    \beta(\x) = \frac{\omega \sin i \, x}{c}
+    \beta(\x) = \frac{\omega \, x}{c} \sin i
 \end{align}
@@
     \frac{1}{2}\ln\left(
-    \dfrac{1 + \dfrac{\omega \sin i \, x}{c}}
-    {1 - \dfrac{\omega \sin i \, x}{c}}
+    \dfrac{1 + \dfrac{\omega \, x}{c} \sin i}
+    {1 - \dfrac{\omega \, x}{c} \sin i}
     \right)
@@
 
-If we assume the star is unocculted, the region of integration $\Surf(\x)$ in Equation~(\ref{eq:deconv:kT}) is simply the unit disk, so $\Curve(\lnlam, \x)$ is the set of all points that satisfy both $\lnlam_0 + \D(\x) = 0$ and $x^2 + y^2 \le 1$.
+The region of integration $\Surf(\x)$ in Equation~(\ref{eq:deconv:kT}) is simply the unit disk, so $\Curve(\lnlam, \x)$ is the set of all points that satisfy both $\lnlam_0 + \D(\x) = 0$ and $x^2 + y^2 \le 1$.
 Solving Equation~(\ref{eq:kT:D}) for $x$, we find that the curves $\Curve(\lnlam, \x)$ are simply vertical lines on the unit disk given by
@@
 Figure~\ref{fig:spot} shows an example application of the formulae derived in this section. 
-We used \starry to generate a synthetic stellar surface with a single large Gaussian spot at a latitude of $30^\circ$, yielding a vector of spherical harmonic coefficients $\bvec{y}$.
+We generated a synthetic stellar surface with a large, circular spot at a latitude of $30^\circ$ and computed its spherical harmonic expansion up to $l_\mathrm{max}=20$ in the form of the vector of coefficients $\bvec{y}$.
 The stellar rest frame spectrum $I(\lnlam_0)$ is taken to be a single Gaussian absorption line that is spatially constant everywhere save for a multiplicative factor equal to the local spot intensity.
@@
 The effect of the spot on the absorption line is evident: a ``bump'' that travels from the blueshifted side of to the redshifted side of the line in sync with the change in longitude of the spot. 
-This correspondence between line shape residuals and spot location is the cornerstone of the Doppler imaging technique \citep[compare to, e.g., Figures 1 and 4 in][]{Vogt1983}.
+This correspondence between line shape and spot location is the cornerstone of the Doppler imaging technique \citep[compare to, e.g., Figures 1 and 4 in][]{Vogt1983}.
 
@@
             The observed spectrum when the spot is in view computed with
-            \starry (blue) and numerically (orange). 
+            our algorithm (blue) and numerically (orange). 
             The problem setup is the same as that in Figure~\ref{fig:spot}. 
@@
 
-\section{Linearization}
+\section{The forward problem}
 \label{sec:linear}
@@
             Each point on the surface is given the same spectrum, composed of a sum of synthetic Gaussian absorption lines (blue curve in the bottom panel).
-            The specific intensity at each point on the surface is equal to this spectrum weighted by the intensity of the map, which is close to zero within the spot (point labeled \texttt{B}) and close ot unity outside the spot (point labeled \texttt{A}).
+            The specific intensity at each point on the surface is equal to this spectrum weighted by the intensity of the map, which is close to zero within the spot (point labeled \texttt{B}) and close to unity outside the spot (point labeled \texttt{A}).
             To generate the synthetic dataset (orange curves in the bottom panel), the star is inclined at $40^\circ$ with respect to the line of sight and the disk-integrated spectrum is computed at 16 equally-spaced phases between $-180^\circ$ and $180^\circ$ (middle panel).

### 2021-09-29 src/ms.tex
luhman16b

@@
 %
-\author{Megan Bedell}
+\author[0000-0001-9907-7742]{Megan Bedell}
 \affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
 %
-\author{Daniel Foreman-Mackey}
+\author[0000-0002-9328-5652]{Daniel Foreman-Mackey}
 \affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
 %
-\author{Lily Zhao}
+\author[0000-0002-1835-1891]{Ian Crossfield}
+\affil{Department~of~Physics~and~Astronomy, Kansas University, Lawrence, KS}
+%
+\author[0000-0002-3852-3590]{Lily Zhao}
 \affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
 %
-\author{David W. Hogg}
+\author[0000-0003-2866-9403]{David W. Hogg}
 \affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
@@
 
-Our input spectrum $\bvec{s}$ was generated at high resolution ($R \equiv \frac{\lambda}{\Delta\lambda} = 430,000$) centered on the Fe I $\lambda 6430$ absorption line (blue curve in the bottom panel of Figure~\ref{fig:spot_setup}).
+Our input spectrum $\bvec{s}$ was generated at high resolution ($R \equiv \frac{\lambda}{\Delta\lambda} = 150,000$) centered on the Fe I $\lambda 6430$ absorption line (blue curve in the bottom panel of Figure~\ref{fig:spot_setup}).
 %
@@
 Finally, as expected, the features in the southern hemisphere are not recovered below inclinations of about $60^\circ$, as they are never actually in view. 
-At an inclination of $80^\circ$m tge spots are recovered fairly well, but never with as high fidelity as features in the observer-facing hemisphere.
+At an inclination of $80^\circ$ the spots are recovered fairly well, but never with as high fidelity as features in the observer-facing hemisphere.
 These results are broadly consistent with those of \citet{Vogt1987}.
+
+\section{Application to Luhman 16B}
+\label{sec:luhman16b}
+%
+\begin{figure}[t!]
+    \begin{centering}
+        \includegraphics[width=0.45\linewidth]{figures/luhman16b_map.pdf} % 
+        \includegraphics[width=0.42\linewidth]{static/luhman16b_crossfield.png} % 
+        \caption{%
+            Maximum \emph{a posteriori} surface maps of Luhman 16B inferred from the CRIRES spectra obtained in \citet{Crossfield2014}.
+\emph{Left:} surface map inferred using the algorithm developed in this work.
+\emph{Right}: surface map inferred in \citet{Crossfield2014}, reproduced from Figure~2 in that paper.
+We infer the presence of a bright circumpolar spot, as well as the presence of a few dark features, most of which agree with the map presented in \citet{Crossfield2014}.
+        }
+        \label{fig:luhman16b_maps}
+    \end{centering}
+\end{figure}
+%
 

### 2021-09-29 src/figures/solve_y.py

@@ -1,7 +1,0 @@
-from generate import generate
-import matplotlib.pyplot as plt
-
-
-map, flux0, flux = generate(nc=1)
-
-map.show_components(file="test.pdf")

### 2021-09-29 src/figures/spot_infer_yb.py

@@ -7,6 +7,7 @@ from utils.generate import generate_data
 from utils.plot import plot_timeseries, plot_maps
 import starry
 import numpy as np
+import os
 
 
 # Generate the synthetic dataset
@@ -25,7 +26,12 @@ for n in range(map.udeg):
 
 # Solve for the Ylm coeffs
 soln = map.solve(
-    flux, theta=theta, normalized=True, fix_spectrum=True, flux_err=flux_err
+    flux,
+    theta=theta,
+    normalized=True,
+    fix_spectrum=True,
+    flux_err=flux_err,
+    quiet=os.getenv("CI", "false") == "true",
 )
 
 # Get the inferred map

### 2021-09-29 src/figures/spot_infer_ybs.py

@@ -7,6 +7,7 @@ from utils.generate import generate_data
 from utils.plot import plot_timeseries, plot_maps, plot_spectra
 import starry
 import numpy as np
+import os
 
 
 # Generate the synthetic dataset
@@ -23,7 +24,13 @@ for n in range(map.udeg):
     map[1 + n] = data["props"]["u"][n]
 
 # Solve for the Ylm coeffs and the spectrum
-soln = map.solve(flux, theta=theta, normalized=True, flux_err=flux_err)
+soln = map.solve(
+    flux,
+    theta=theta,
+    normalized=True,
+    flux_err=flux_err,
+    quiet=os.getenv("CI", "false") == "true",
+)
 
 # Get the inferred map and spectrum
 y_inferred = map.y

### 2021-09-30 src/ms.tex
fix syw stuff
working on text

@@
 The standard approach to solving this integral is therefore to discretize the surface of the star with a fine grid, evaluate the Doppler-shifted spectrum in each cell, and sum over the spatial axes to approximate the integral.
-Depending on the resolution of the grid, this is either numerically inaccurate or computationally inefficient (and often both).
+Depending on the resolution of the grid, this is either numerically inaccurate or computationally inefficient.
 
@@
 %
-where $\omega$ is the stellar angular velocity and $i$ is the stellar inclination with respect to $\hat{y}$.
+where $\omega$ is the stellar angular velocity and $i$ is the stellar inclination with respect to $\hat{y}$, where $i = 0^\circ$ corresponds to a pole-on orientation.
 
@@
             These functions encode the contribution of each spherical harmonic to the rotational broadening of features in the stellar spectrum. 
-            Because the rotational axis is chosen to be aligned with $\hat{y}$, none of the $m < 0$ harmonics contribute to the observed spectrum.
+            Because the rotational axis is chosen to be aligned with $\hat{y}$ (along the plane of the sky), none of the $m < 0$ harmonics contribute to the observed spectrum.
         }
@@
         \caption{%
-            The Doppler design matrix $\Doppler$ (Equation~\ref{eq:linear:f}), constructed from a grid of Toeplitz matrices, each of shape $K \times K'$, where $K$ is the number of wavelength bins in the observed spectrum and $K' = K + W - 1$ is the number of bins in the model spectrum, where $W$ is the width of the convolution kernel.
+            The Doppler design matrix $\Doppler$ (Equation~\ref{eq:linear:f}), constructed from a grid of Toeplitz matrices, each of shape $K \times K'$, where $K$ is the number of wavelength bins in the broadened spectrum and $K' = K + W - 1$ is the number of bins in the latent (template) spectrum, where $W$ is the width of the convolution kernel.
             The $N$ columns of $\Doppler$ correspond to the Toeplitz matrices for each of the $N$ spherical harmonics (shown at the top);
             the $M$ rows correspond to the Toeplitz matrices rotated to each of the $M$ stellar phases observed (indicated graphically to the left of $\Doppler$).
+            The color scale ranges from black (negative) to bright yellow (positive); light grey regions correspond to entries in the matrix that are identically zero.
         }
@@
 If $\bvec{g}$ has length $L$, element $g_n$ is placed everywhere along the $k^\mathrm{th}$ diagonal of $\bvec{T}$ for $k = -L / 2 + n$; all other entries of $\bvec{T}$ are set to zero. 
-Note that the matrix $\bvec{T}$ need not be square; in fact, for our purposes, it is a $(K \times K')$ matrix, where $K$ is the size of the observed wavelength grid and $K' = K + W - 1$ is the size of the wavelength grid in the rest frame, where $W$ is the width of the convolution kernel.
+Note that the matrix $\bvec{T}$ need not be square; in fact, for our purposes, it is a $(K \times K')$ matrix, where $K$ is the size of the output wavelength grid and $K' = K + W - 1$ is the size of the input wavelength grid (in the rest frame), where $W$ is the width of the convolution kernel.
 
@@
 In particular, if one places a (multidimensional) Gaussian prior on $\alm$ with mean $\boldsymbol{\mu}_\mathbf{a}$ and covariance $\boldsymbol{\Lambda}_\mathbf{a}$, the maximum \emph{a posteriori} (MAP)
-solution for $\alm$ is given by the solution to the L2 regularization problem:
+solution for $\alm$ is given by the solution to the L2 regularization problem \citep[see, e.g.,][]{Luger2016}:
 %
@@
 That said, a Gaussian prior \emph{is} typically suitable for both the spectrum $\bvec{s}$ and the intensity $\bvec{y}$ (just not their product). 
-It is straightforward to show that because Equation~(\ref{eq:linear:f}) is linear in $\alm$, it is also linear in both $\bvec{s}$ and $\bvec{y}$, so MAP solutions can be found analytically for $\bvec{s}$ (conditioned on $\bvec{y}$) and $\bvec{y}$ (conditioned on $\bvec{s}$).
-We investigate these solutions below.
+Spectral templates can provide us with a physically-motivated mean for the prior on $\bvec{s}$, while the variance can be used to capture our degree of confidence in the model.
+Similarly, a multivariate Gaussian prior on the spherical harmonic coefficients $\bvec{y}$ is flexible enough to capture prior information on the location and properties of starspots \citep{Luger2021b}.
+%
+Given Gaussian priors on these two quantities,
+it is straightforward to show that because Equation~(\ref{eq:linear:f}) is linear in $\alm$, it is also linear in both $\bvec{s}$ and $\bvec{y}$, so MAP solutions can be found analytically for $\bvec{s}$ (conditioned on $\bvec{y}$) and $\bvec{y}$ (conditioned on $\bvec{s}$).
+A solution to the full problem of determining both $\bvec{s}$ and $\bvec{y}$ can then be obtained by iteratively solving these two problems.
+We investigate this procedure below.
 
@@
 %
-For a fixed, spatially constant rest-frame spectrum $\bvec{s}$, the model for the flux vector may be written as
+Given a single rest-frame spectrum $\bvec{s}$, the model for the flux vector may be written as
 %
@@
 This is especially useful if the typical angular scale of features on the surface of the star is known or if a Gaussian prior can be placed on it.
+Alternatively, we may compute $\boldsymbol{\Lambda}_\bvec{y}$ from the Gaussian process formalism in \citet{Luger2021b} to incorporate explicit prior information on the typical latitudes, sizes, and contrasts of spots.
+We discuss this point further in \S\ref{sec:discussion}.
 
@@
 %
-If, on the other hand, the spatial intensity profile is known, the model for the flux vector may be written in terms of the spectrum $\bvec{s}$ as
+Conversely, given a spatial representation of the surface $\bvec{y}$, the model for the flux vector may be written in terms of the spectrum $\bvec{s}$ as
 %
@@
 This section is motivated by the examples in \cite{Vogt1987}, who generated rotationally-broadened spectra of a rapidly-rotating star with the letters ``VOGT'' painted across the northern hemisphere. 
-In that paper, the authors generated synthetic line profiles of the Fe I $\lambda 6430$ absorption line with equivalent width $W \approx 10$~km/s and from these computed rotationally broadened spectra for a star at an inclination $i=40^\circ$ rotating at projected velocity $v\sin i = 40$~km/s.
+In that paper, the authors generated synthetic line profiles of the Fe I $\lambda 6430$ absorption line with equivalent width ${\sim}10$~km/s and from these computed rotationally broadened spectra for a star at an inclination $i=40^\circ$ rotating at projected velocity $v\sin i = 40$~km/s.
 The spectra were computed at 16 equally spaced rotational phases and downsampled to 32 wavelength bins per epoch, for a total of 512 data points.
@@
 
-Our input spectrum $\bvec{s}$ was generated at high resolution ($R \equiv \frac{\lambda}{\Delta\lambda} = 150,000$) centered on the Fe I $\lambda 6430$ absorption line (blue curve in the bottom panel of Figure~\ref{fig:spot_setup}).
+Our input spectrum $\bvec{s}$ was generated at extremely high resolution
+%
+($R \equiv \frac{\lambda}{\Delta\lambda} = 750,000$) 
+%
+centered on the Fe I $\lambda 6430$ absorption line (blue curve in the bottom panel of Figure~\ref{fig:spot_setup}).
 %
@@
 Unlike \citet{Vogt1987}, we add two additional small absorption lines, one of which is blended with the central absorption line.
-In total, the rest frame spectrum $\bvec{s}$ consists of $K = 200$ wavelength bins in the range $642.85~\mathrm{nm} \leq \lambda \leq 643.15~\mathrm{nm}$ plus an additional
-%
-\begin{align}
-    W & = 2 \bigg\lceil \frac{(v\sin i)_\mathrm{max}R}{c} \bigg\rceil \nonumber  \\
-      & = 144
-\end{align}
-%
-bins of padding (72 on either side) to eliminate edge effects due to the convolution, for a total of $K' = 344$ wavelength bins. 
-In the expression above, $(v\sin i)_\mathrm{max}$ is the maximum value of $v\sin i$ we can model with a given value of $W$; for this experiment, we set $(v\sin i)_\mathrm{max}=50$~km/s, which is larger than the actual value of $v\sin i$ we used to generate the data (see above).
+In total, the rest frame spectrum $\bvec{s}$ consists of 
+%
+$K = 351$ 
+%
+wavelength bins in the range $642.85~\mathrm{nm} \leq \lambda \leq 643.15~\mathrm{nm}$ plus an additional
+%
+$W - 1 = 252$ 
+%
+bins of padding 
+%
+(126 on either side) 
+%
+to eliminate edge effects due to the convolution, for a total of 
+%
+$K' = 603$
+%
+wavelength bins. 
 Finally, we linearly interpolate this spectrum to a wavelength grid uniform in log space to obtain the vector $\bvec{s}$ evaluated at each $\lnlam$.
 
-Given $\bvec{y}$ and $\bvec{s}$, we use Equations~(\ref{eq:deconv:F}) and~(\ref{eq:inverse:alm}) to compute the data vector $\bvec{f}$ at $M = 16$ equally spaced rotational phases; these phases are shown in orthographic projection (as an observer would see the star) in the center panel of Figure~\ref{fig:spot_setup}.
+Given $\bvec{y}$ and $\bvec{s}$, we use Equations~(\ref{eq:deconv:F}) and~(\ref{eq:inverse:alm}) to compute the data vector $\bvec{f}$, which we downsample to a grid of 
+%
+$K_\mathrm{obs} = 70$ 
+%
+wavelength bins in the range $642.85~\mathrm{nm} \leq \lambda \leq 643.15~\mathrm{nm}$, corresponding to a resolution of
+%
+$R = 150,000$.
+%
+We compute $\bvec{f}$ at $M = 16$ equally spaced rotational phases; these phases are shown in orthographic projection (as an observer would see the star) in the center panel of Figure~\ref{fig:spot_setup}.
 The synthetic spectra for each phase are shown as the orange curves in the bottom panel of the figure (note the different scaling, as all spectral lines become shallower due to the broadening). 
+%
 We assume a wavelength-independent, quadratic limb darkening law with $u_1 = 0.5$ and $u_2 = 0.25$. 
 Finally, we divide the flux by the baseline at each epoch (Equation~\ref{eq:norm:f}) and add random Gaussian noise with covariance matrix $\boldsymbol{\Sigma}_\bvec{f} = \sigma_\bvec{f}^2 \mathbf{I}$, with $\sigma_\bvec{f} = 2\times 10^{-4}$ to simulate a very high signal-to-noise ratio (SNR) spectrum.
-The mean standard deviation in each wavelength bin across all 16 epochs in the noiseless data vector is about $2\times 10^{-2}$, so our choice of $\sigma_\bvec{f}$ corresponds to SNR $\sim$ 100 in each of the 200 wavelength bins of $\bvec{f}$.
-
-%For reference, \citet{Vogt1987} report SNRs per 60 m\AA\, pixel, while our
-%resolution elements are approximately $\lambda_r\Delta\lnlam/K \approx 100$ m\AA\,
-%across, so our SNR in the same units as \citet{Vogt1987} is about 80.
-%
-% TODO: Perhaps Vogt computes the "signal" as the line depth, rather than
-% as the amplitude of the perturbations? Check this.
-% We Recover images with an effective resolution of $12^\circ$.
+The typical fractional line depth in the observed spectrum is 0.2,
+so our choice of $\sigma_\bvec{f}$ corresponds to SNR $\sim 10^{3}$ in each of the 70 wavelength bins of $\bvec{f}$.
 
@@
 %
-After some tuning, we find it necessary to increase our prior variances slightly to get good fits to the data: we set $\boldsymbol{\Lambda}_\bvec{y} = 2.5\times 10^{-4} \bvec{I}$ and $\boldsymbol{\Lambda}_\bvec{s} = 5\times 10^{-3}\bvec{I}$.
+After some tuning, we find it necessary to increase our prior variances slightly to get good fits to the data: we set $\boldsymbol{\Lambda}_\bvec{y} = 2\times 10^{-4} \bvec{I}$ and $\boldsymbol{\Lambda}_\bvec{s} = 2\times 10^{-2}\bvec{I}$.
 %
@@
 %
-We generate the synthetic dataset in the same way as in \S\ref{sec:spot_y1}: 16 spectra, each with 200 wavelength bins observed with SNR$\sim$100.
+We generate the synthetic dataset in the same way as in \S\ref{sec:spot_y1}: 16 spectra, each with 70 wavelength bins observed with SNR$\sim 10^{3}$.
 
@@
 %
-We further place a Gaussian Process prior on the spectra to enforce smoothness, adopting a squared exponential kernel with amplitude $10^{-1}$ and lengthscale $10^{-2}$~nm.
-%
-We also solve for a single scale parameter $r \sim \mathrm{Uniform}(0, 1)$, equal to the ratio of the continuum levels of the two spectra (whose true value is 0.5).
+We further place a Gaussian process prior on the spectra to enforce smoothness, adopting a squared exponential kernel with amplitude $10^{-1}$ and lengthscale $10^{-2}$~nm.
+%
+We also solve for a single scale parameter $r \sim \mathrm{Uniform}(0, 0.75)$, equal to the ratio of the continuum levels of the two spectra (whose true value is 0.5).
 Finally, in order to enforce that the two component surface maps sum to unity (as described above), we optimize for the actual \emph{pixel} intensities of the photosphere map, on which we place a simple uniform prior on $[0, 1]$; the spot map is then simply the complement.
@@
 Figure~\ref{fig:snr} shows the effect of different SNR on the quality of the inferred map. 
-As before, the SNR we report is the ratio of the standard deviation of the true model in each wavelength bin across all epochs, averaged over all wavelength bins (i.e., the ``signal''), to the standard deviation of the added noise term, $\sigma_\bvec{f}$ (the ``noise'').
-The panels in Figure~\ref{fig:snr} show the inferred map for SNR in the range 1---1000, where SNR $\sim 100$ is the fiducial case considered in the examples so far. 
+As before, the SNR we report is the ratio of the typical line depth in the observed spectrum to the standard deviation of the added noise term, $\sigma_\bvec{f}$.
+The panels in Figure~\ref{fig:snr} show the inferred map for SNR in the range 10---10,000, where SNR $\sim 1,000$ is the fiducial case considered in the examples so far. 
 The setup is the same as that in \S\ref{sec:spot_y1b}, where the spectrum is known exactly but the map coefficients and the baseline are not.
@@
 
-As the SNR incraeses, however, the quality of the \spot feature does not improve appreciably, since a SNR of 100 is more than sufficient to recover a $l_\mathrm{max} = 15$ band-limited map. 
+As the SNR incraeses, however, the quality of the \spot feature does not improve appreciably, since a SNR of 1,000 is more than sufficient to recover a $l_\mathrm{max} = 15$ band-limited map. 
 Interestingly, at constant spatial prior variance ($\boldsymbol{\Lambda}_\bvec{y} = 10^{-4}\bvec{I}$), the map quality actually begins to degrade with higher SNR south of the equator due to overfitting.
@@
 %
-\begin{figure}[t!]
+\begin{figure}[p!]
     \begin{centering}
-        \includegraphics[width=0.45\linewidth]{figures/luhman16b_map.pdf} % 
-        \includegraphics[width=0.42\linewidth]{static/luhman16b_crossfield.png} % 
+        \includegraphics[width=\linewidth]{figures/luhman16b_data_model.pdf} % 
         \caption{%
-            Maximum \emph{a posteriori} surface maps of Luhman 16B inferred from the CRIRES spectra obtained in \citet{Crossfield2014}.
+            Calibrated and tellurics-corrected CRIRES spectra of Luhman 16B from \citet{Crossfield2014} taken at 14 epochs spanning a full rotation of the brown dwarf (black points).
+The maximum \emph{a posteriori} solution is shown as the orange curves.
+        }
+        \label{fig:luhman16b:data_model}
+    \end{centering}
+\end{figure}
+%
+\begin{figure}[p!]
+    \begin{centering}
+        \begin{minipage}[t]{0.49\linewidth}
+            \centering
+            \quad\quad\quad
+            \textbf{Luger et al. (2021)}
+        \end{minipage}
+        \vspace{1em}
+        \begin{minipage}[t]{0.49\linewidth}
+            \centering
+            \textbf{Crossfield et al. (2014)}
+        \end{minipage}
+        \includegraphics[width=0.495\linewidth]{figures/luhman16b_map.pdf} % 
+        \includegraphics[width=0.462\linewidth]{static/luhman16b_crossfield.png} % 
+        \caption{%
+            Maximum \emph{a posteriori} surface maps of Luhman 16B inferred from the spectra in Figure~\ref{fig:luhman16b:data_model}.
 \emph{Left:} surface map inferred using the algorithm developed in this work.
 \emph{Right}: surface map inferred in \citet{Crossfield2014}, reproduced from Figure~2 in that paper.
-We infer the presence of a bright circumpolar spot, as well as the presence of a few dark features, most of which agree with the map presented in \citet{Crossfield2014}.
-        }
-        \label{fig:luhman16b_maps}
+We infer the presence of a bright circumpolar spot, as well as the presence of a few dark features, most of which agree with the map presented in the original work.
+        }
+        \label{fig:luhman16b:maps}
     \end{centering}
@@
 %
+\begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/luhman16b_spectra.pdf} % 
+        \caption{%
+            Unbroadened template spectra used to model the data in \citet{Crossfield2014} (blue curves).
+These were used as a prior on the spectra inferred in this work (orange curves).
+We infer a slightly different depth for some lines, as well as subtle changes in the continuum.
+        }
+        \label{fig:luhman16b:template_spectra}
+    \end{centering}
+\end{figure}
 
@@
         $J$                                                 & \# of spectral components                                    & \S\ref{sec:eigen}                          \\
-        $K$                                                 & \# of wavelength bins in the observed spectrum               & \S\ref{sec:linear}                         \\
+        $K$                                                 & \# of wavelength bins in the broadened spectrum              & \S\ref{sec:linear}                         \\
         $K'$                                                & \# of wavelength bins in the latent spectrum                 & \S\ref{sec:linear}                         \\
+        $K_\mathrm{obs}$                                    & \# of wavelength bins in the observed spectrum               & \S\ref{sec:spotstar}                       \\
         $M$                                                 & \# of epochs observed                                        & \S\ref{sec:linear}                         \\

### 2021-09-30 src/figures/linalg.py

@@ -85,7 +85,7 @@ def get_ortho_longitude_lines(
 ):
     """
     Return the lines of constant longitude on an orthographic projection.
-    
+
     """
 
     # Angular quantities
@@ -212,6 +212,16 @@ for l in range(ydeg + 1):
         axins.set_ylim(-1.2, 1.2)
         n += 1
         axins.axis("off")
+        axins.annotate(
+            fr"$Y_{{{l},{m}}}$",
+            xy=(0.5, 1),
+            xycoords="axes fraction",
+            xytext=(0, 0),
+            textcoords="offset points",
+            ha="center",
+            va="bottom",
+            fontsize=10,
+        )
 
 # Plot the map orientation
 x0 = -1.0 / 11.0

### 2021-09-30 src/figures/snr.py

@@ -13,17 +13,19 @@ from matplotlib.colors import Normalize
 ydeg = 15
 smoothing = 0.075
 
-# Compute model at infinite SNR to get the "signal"
-# This is the standard deviation in each wavelength
-# bin across all epochs.
+# Compute model at infinite SNR
 data = generate_data(flux_err=0, ydeg=ydeg, smoothing=smoothing)
 theta = data["data"]["theta"]
 flux = data["data"]["flux"]
-signal = np.mean(np.std(flux, axis=0))
+
+# Typical line depth
+signal = 0.2
 
 # Compute the pointwise uncertainty for a given SNR
-snrs = np.array([1.0, 2.0, 5.0, 10.0, 50.0, 100.0, 200.0, 500.0, 1000.0])
-spatial_cov = np.minimum(1e-4, 1e-4 * (100 / snrs) ** 2)
+snrs = np.array(
+    [10.0, 20.0, 50.0, 100.0, 500.0, 1000.0, 2000.0, 5000.0, 10000.0]
+)
+spatial_cov = np.minimum(1e-4, 1e-4 * (1000 / snrs) ** 2)
 flux_errs = signal / snrs
 
 # Plot the true map

### 2021-09-30 src/ms.tex
address ian's comments

@@
 Figure~\ref{fig:linalg} shows an example of $\Doppler$.
+Note, importantly, that this expression does not account for limb darkening or for the fact that spectra are often normalized to the continuum level; we account for these two effects in \S\ref{sec:norm} and \S\ref{sec:ld} below.
 
@@
 %
-If we choose a prior with zero mean ($\boldsymbol{\mu}_\bvec{y} = 0$)
-and a diagonal covariance that is constant for each spherical harmonic order $m$,
+If we choose a prior with diagonal covariance that is constant for each spherical harmonic order $m$,
 %
@@
 Importantly, the framework developed here allows one to analytically compute not only the ``optimal'' solution to the Doppler imaging problem, but also its uncertainty. 
-The problem of re-constructing surface images of stars from spectra and/or light curves is fundamentally ill-posed because of intrinsic degeneracies and a large null space \citep[e.g.,][]{Cowan2017,Luger2019}.
-Coupled to uncertainties in the observations themselves, this makes the process of searching for the ``optimal'' solution flawed at best, and meaningless at worst. 
+The problem of re-constructing surface images of stars from spectra and/or light curves is fundamentally ill-posed because of intrinsic degeneracies and a large null space \citep[e.g.,][]{Cowan2017,Luger2019,Luger2021a}.
+Coupled to uncertainties in properties like the stellar inclination, rotation period, and limb darkening coefficients, as well as the finite signal-to-noise ratio of the data, this makes the process of searching for the ``optimal'' solution flawed at best, and meaningless at worst.
 Access to the full covariance matrix of the solution is therefore essential to assessing our confidence in the various features of the inferred surface maps.
@@
 If neither are known exactly \emph{a priori}, which is quite often the case, we can still find the MAP solution quickly by guessing at an initial spectrum $\bvec{s}$ and iterating between optimizing for $\bvec{y}$ and optimizing for $\bvec{s}$.
-This bilinear problem is not generally convex, but given a good starting point for $\bvec{s}$ and sufficient regularization on $\bvec{y}$, we find that it typically converges to the correct solution, especially after refinement with a nonlinear solver; we discuss this in detail below.
+Note, importantly, that this bilinear problem is not generally convex: the likelihood space often has many local minima, which can in principle make it difficult to find the true solution.
+Nevertheless, given a good starting point for $\bvec{s}$ and sufficient regularization on $\bvec{y}$, we find that it typically converges to the correct solution; see \S\ref{sec:spotstar}.
 
@@
 To \emph{correctly} account for this, one must resort to Monte Carlo methods or other sampling techniques. 
-We discuss this further below.
+We discuss this further in \S\ref{sec:discussion}.
 
@@
             The specific intensity at each point on the surface is equal to this spectrum weighted by the intensity of the map, which is close to zero within the spot (point labeled \texttt{B}) and close to unity outside the spot (point labeled \texttt{A}).
-            To generate the synthetic dataset (orange curves in the bottom panel), the star is inclined at $40^\circ$ with respect to the line of sight and the disk-integrated spectrum is computed at 16 equally-spaced phases between $-180^\circ$ and $180^\circ$ (middle panel).
+            To generate the synthetic dataset (orange curves in the bottom panel), the star is inclined at $40^\circ$ with respect to the line of sight and the disk-integrated spectrum is computed at 16 equally-spaced phases between $-180^\circ$ and $180^\circ$, assuming an equatorial velocity $v = 60$ km/s (middle panel).
             The grey regions indicate wavelength regions outside the observation window, but whose features can still contribute to the observed spectrum due to rotational broadening.
@@
 When solving for the rest frame spectrum, we also place a Gaussian prior on $\bvec{s}$ with unit mean and covariance $\boldsymbol{\Lambda}_\bvec{s} = 10^{-3}\bvec{I}$.
+These choices are arbitrary and primarily based on trial-and-error given knowledge of the true solutions.
+We discuss strategies for choosing optimal priors for real datasets in \S\ref{sec:discussion} below.
 
@@
 %
-In our first experiment, we attempt to infer the stellar map assuming we have perfect knowledge of the rest frame spectrum $\bvec{s}$ and the baseline.
+In our first experiment, we attempt to infer the stellar map assuming we have perfect knowledge of the rest frame spectrum $\bvec{s}$ and the baseline, as well as the stellar inclination, rotation period, and limb darkening coefficients.
 This is analogous to the case where a good physical model exists for the stellar spectrum and simultaneous photometry is available to constrain the baseline variations.
@@
 Because the problem is generally not convex, we need a good starting guess for either the spectrum or the map coefficients. 
-We note that we can very crudely approximate the rest frame spectrum by deconvolving the average observed spectrum with the first term of the convolution kernel $\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{figures/kT00.pdf}}).
+We note that we can very crudely approximate the rest frame spectrum by deconvolving the average observed spectrum with the first term of the convolution kernel $\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{figures/kT00.pdf}}); we do this by solving the linear problem in Equation~(\ref{eq:linear:convolution_def}) with aggressive regularization.
 In practice, this is a fairly poor approximation, but we find that it suffices as an initial guess. 
@@
 %
+
+Discuss: how to choose priors
+
 \xxx{%

### 2021-09-30 src/ms.tex
more text

@@
 
-\section{Discussion}
-\label{sec:discussion}
-%
-
-\xxx{%
-    \begin{enumerate}
-        %
-        \item%
-              A gaussian prior with unit mean is a pretty bad prior for the spectrum.
-              In a more realistic scenario, we'd know a lot more information about the spectrum---such as where the lines are and some estimate of their shapes and depths---so the fidelity of our maps would be higher.
-              %
-        \item%
-              We are not addressing differential rotation and convective blueshift.
-              These make the integral in Equation~(\ref{eq:deconv:kT}) very difficult to solve. 
-              We will tackle this in the next paper.
-              %
-        \item%
-              Telluric lines could be treated much as in Figure~\ref{fig:twospec}, and marginalized over as in \citet{Bedell2019}.
-              %
-        \item% 
-              The instrumental profile is another Toeplitz matrix that can be dotted into Equation~(\ref{eq:linear:f}).
-              %
-        \item Discuss the case where the inclination/period/velocity is unknown.
-              The problem is not linear in these variables, so we need MCMC. 
-              But our model is differentiable, so we can easily use HMC. 
-              Discuss.
-              %
-        \item%
-              Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires first the rotation of the $(\lmax + 1)^2$ $\kT$ kernels (each of length $W$) to the correct stellar rotational phase, an operation that scales approximately as $W \lmax^3$, followed by $(\lmax + 1)^2$ linear convolutions of the rotated $\kT$ kernels with the spectral components (each of length $K$), which scales approximately as $W K \lmax^2$.
-              Since typically $K \gg \lmax$, the latter computation dominates and the entire evaluation takes $\mathcal{O}(W K \lmax^2)$ operations.
-    \end{enumerate}
-}
-
 \subsection{Dependence on SNR}
@@
 %
+
+Having shown that our model performs well on synthetic data, we now turn to a real dataset: the VLT/CRIRES observations of Luhman 16B presented in the Doppler imaging study of \citet{Crossfield2014}.
+Luhman 16B belongs to a binary brown dwarf system, which at a distance of 2 pc are the closest known brown dwarfs to the Solar system.
+Nevertheless, the object is intrinsically dim and, with a projected rotational velocity $v \sin i = 26.1$ km/s, is at the slow end of what can be imaged using the traditional Doppler imaging technique.
+Therefore, unlike those of classical Doppler imaging targets, the spectral lines of Luhman 16B do not show obvious spot modulation (Figure~\ref{fig:spot}) from one epoch to the next; nor are the spectral templates for these objects particularly well understood.
+Nonetheless, we chose to model Luhman 16B specifically to show the power behind our new methodology, in particular its ability to learn both the surface map and the rest frame spectrum simultaneously from the entire dataset---not just from unblended spectral lines that have reliable templates.
+
+In the original Doppler imaging study of this target, \citet{Crossfield2014} took 56 spectra of each object (the angular resolution was high enough to obtain individual spectra of both brown dwarfs) in four channels in the range $2.288-2.345 \mu$m over a time span of 5 hours, with individual exposures of 300 s.
+The 5 hour baseline was enough to capture one full rotation of Luhman 16B, whose period was constrained to be about 4.9 hours from its photometric variability \citep{Gillon2013}.
+These spectra were then downbinned to 14 epochs, corrected for tellurics and spectrograph systematics, and continuum-normalized.
+Each of the 14 spectra consist of 1,024 intensity measurements in each of 4 channels, for a total of $57,344$ data points.
+For more details on the data reduction, refer to \citet{Crossfield2014}.
+
+The black points in Figure~\ref{fig:luhman16b:data_model} show the exact dataset used in the Doppler imaging analysis of \citet{Crossfield2014}, except for the fact that we masked additional outliers at $>4\sigma$ as well as regions of the spectrum that had been visibly overcorrected for tellurics.
+This figure shows the same data as the lower panel of Extended Data Figure 2 in \citet{Crossfield2014}.
+
+In order to produce Doppler images of Luhman 16B, \citet{Crossfield2014} used brown dwarf template spectra from the BT-Settl library \citep{Allard2013}, finding that the spectrum with $\log_{10} g = 5.0$ and $T_\mathrm{eff} = 1450$ K provided the best match to the dataset.
+This spectrum was then Doppler-shifted by the systemic radial velocity of the brown dwarf and broadened to match the spectrograph resolution.
+This final template spectrum is shown as the blue curves in Figure~\ref{fig:luhman16b:template_spectra}, where we again masked regions where data was discarded.
+
+\citet{Crossfield2014} then employed the common technique of Least Squares Deconvolution \citep[LSD;][]{Donati1997} to transform each of the 14 spectra in Figure~\ref{fig:luhman16b:data_model} into a single high-SNR line spanning 35 pixels, which was used as the input to their Doppler imaging code, based on that of \citet{Vogt1987}.
+They discretized the stellar surface using 200 cells and solved for the optimal surface map with a maximum entropy prior as in \citet{Vogt1987}, assuming a fiducial inclination $i=60^\circ$ roughly based on the photometric rotation period and the inferred value of $v\sin i$; given the low SNR of the dataset, they were unable to place meaningful constraints on $i$.
+We reproduce their resulting surface brightness map in the right panel of Figure~\ref{fig:luhman16b:maps}.
+
+In our analysis, we use the same data (Figure~\ref{fig:luhman16b:data_model}) and the same spectral template (Figure~\ref{fig:luhman16b:template_spectra}), but instead following the methodology derived in this work.
+Our problem is similar to that in \S\ref{sec:spot_y1bs}, in which we treat both the spectrum and the surface map as unknowns given continuum-normalized spectra as input.
+However, this time we use the template spectrum as the prior mean on the true rest frame spectrum $\bvec{s}$, setting the prior standard deviation to one percent (i.e., a covariance $\boldsymbol{\Lambda}_\bvec{s} = 10^{-4}\bvec{I}$) to allow the model to learn any small deviations from the template.
+We must also change the way we model the continuum normalization (\S\ref{sec:norm}), given the high density of spectral lines and the consequent difficulty of finding a reliable continuum level to normalize against.
+Instead, we treat the unknown continuum normalization factor for each of the 14 epochs as a free parameter of the model, $f \sim \mathrm{Uniform}(0.3, 3.0)$; we also allow for a small, time-independent, additive offset $\Delta \sim \mathcal{N}(0, 0.1^2)$ for each of the four spectral channels.
+We assume the same fiducial inclination $i = 60^\circ$, a rotational period $P = 4.9$ days, and allow the linear limb darkening coefficient and projected velocity to vary subject to $u_1 \sim \mathrm{Uniform}(0, 1)$ and $v \sin i \sim \mathcal{N}(26.1, 0.2^2)$ km/s, respectively, as in \citet{Crossfield2014}.
+Finally, we place a uniform prior on the pixel intensities $\bvec{p} \sim \mathrm{Uniform}(0, 1)$ as in \S\ref{sec:twospec}, linearly transforming to an $l_\mathrm{max} = 10$ spherical harmonic representation of the map to compute the model at each step.
+We must therefore solve for $2 \times (l_\mathrm{max} + 1)^2 = 242$ free parameters for the pixelized surface map, $3,748$ free parameters for the rest frame spectrum across each of the four channels (equal to the size of our template spectrum after removing outliers), $18$ parameters describing the continuum normalization, and $2$ stellar parameters (the linear limb darkening coefficient and the projected velocity).
+In total, our model has just over $4,000$ free parameters.
+
+As in \S\ref{sec:twospec}, our choice of parametrization and priors precludes the use of the fast bilinear approach outlined in \S\ref{sec:inverse}.
+We therefore follow the same approach as in \S\ref{sec:twospec}, optimizing our log-likelihood function using \texttt{Adam} with a learning rate of $10^{-3}$.
+Since we have a very good guess for the template spectrum, this optimization is much faster than in \S\ref{sec:twospec}, converging within $1,000$ steps.
+Because of our efficient gradient-based implementation (\S\ref{sec:starry}), the entire optimization takes only about 3 minutes of runtime on a typical Macbook laptop.
+
+Our results are shown in Figures~\ref{fig:luhman16b:data_model}, \ref{fig:luhman16b:template_spectra}, and \ref{fig:luhman16b:maps}.
+In Figure~\ref{fig:luhman16b:data_model}, our maximum \emph{a posteriori} (MAP) model for each of the 14 spectra is shown as the orange line; it agrees with the data to within the measurement uncertainties.
+In Figure~\ref{fig:luhman16b:template_spectra} we show our MAP \emph{template} (rest frame) spectrum as the orange curve.
+Since we used the \citet{Crossfield2014} template as a prior (blue curve), our solution is very similar to the input spectrum.
+Nevertheless, we infer slightly different line depths for several of the lines at the level of a few percent; we also infer slightly different continuum levels in certain portions of the spectrum.
+Note, importantly, since we only performed an optimization (rather than full posterior inference), we cannot quantify the actual significance of these differences.
+
+The right panel of Figure~\ref{fig:luhman16b:maps} shows our principal result: the inferred solution for the surface brightness map of Luhman 16B.
+
 \begin{figure}[p!]
@@
             Calibrated and tellurics-corrected CRIRES spectra of Luhman 16B from \citet{Crossfield2014} taken at 14 epochs spanning a full rotation of the brown dwarf (black points).
-The maximum \emph{a posteriori} solution is shown as the orange curves.
+Our maximum \emph{a posteriori} solution is shown as the orange curves.
         }
@@
 \begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=0.8\linewidth]{figures/luhman16b_spectra.pdf} % 
+        \caption{%
+            Unbroadened template spectra used to model the data in \citet{Crossfield2014} (blue curves).
+These were used as a prior on the spectra inferred in this work (orange curves).
+We infer a slightly different depth for some lines, as well as subtle changes in the continuum.
+        }
+        \label{fig:luhman16b:template_spectra}
+    \end{centering}
+\end{figure}
+%
+\begin{figure}[t!]
     \begin{centering}
@@
 %
-\begin{figure}[p!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/luhman16b_spectra.pdf} % 
-        \caption{%
-            Unbroadened template spectra used to model the data in \citet{Crossfield2014} (blue curves).
-These were used as a prior on the spectra inferred in this work (orange curves).
-We infer a slightly different depth for some lines, as well as subtle changes in the continuum.
-        }
-        \label{fig:luhman16b:template_spectra}
-    \end{centering}
-\end{figure}
+
+\section{Discussion}
+\label{sec:discussion}
+%
+
+\xxx{%
+    \begin{enumerate}
+        %
+        \item%
+              A gaussian prior with unit mean is a pretty bad prior for the spectrum.
+              In a more realistic scenario, we'd know a lot more information about the spectrum---such as where the lines are and some estimate of their shapes and depths---so the fidelity of our maps would be higher.
+              %
+        \item%
+              We are not addressing differential rotation and convective blueshift.
+              These make the integral in Equation~(\ref{eq:deconv:kT}) very difficult to solve. 
+              We will tackle this in the next paper.
+              %
+        \item%
+              Telluric lines could be treated much as in Figure~\ref{fig:twospec}, and marginalized over as in \citet{Bedell2019}.
+              %
+        \item% 
+              The instrumental profile is another Toeplitz matrix that can be dotted into Equation~(\ref{eq:linear:f}).
+              %
+        \item Discuss the case where the inclination/period/velocity is unknown.
+              The problem is not linear in these variables, so we need MCMC. 
+              But our model is differentiable, so we can easily use HMC. 
+              Discuss.
+              %
+        \item%
+              Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires first the rotation of the $(\lmax + 1)^2$ $\kT$ kernels (each of length $W$) to the correct stellar rotational phase, an operation that scales approximately as $W \lmax^3$, followed by $(\lmax + 1)^2$ linear convolutions of the rotated $\kT$ kernels with the spectral components (each of length $K$), which scales approximately as $W K \lmax^2$.
+              Since typically $K \gg \lmax$, the latter computation dominates and the entire evaluation takes $\mathcal{O}(W K \lmax^2)$ operations.
+        \item%
+              Discuss: how to choose priors
+    \end{enumerate}
+}
+
+\section{Implementation in starry}
+\label{sec:starry}
 
@@
 %
-
-Discuss: how to choose priors
 

### 2021-09-30 src/ms.tex
completeish skeleton draft

@@
 \begin{abstract}
-    We derive a closed form, analytic solution to the problem of Doppler imaging of stellar surfaces in the limit of negligible differential rotation and convective blueshift.
+    We derive a closed form solution to the problem of Doppler imaging of stellar surfaces in the limit of negligible differential rotation and convective blueshift.
     The model for the observed spectrum is linear in the coefficients of the spherical harmonic expansion of the specific intensity distribution on the surface and, in certain limits, the posterior over surface maps has a closed form, analytic solution that is computationally trivial to evaluate.
@@
 \section{Introduction}
+
+\xxx{%
+    \noindent Introduce the problem of Doppler imaging. Then cite the following papers:\\[0.5em]
+    \noindent\textbf{Misc.} \\
+    \noindent\citet{Luger2019} --- Surface modeling with spherical harmonics: \starry \\
+    \noindent\citet{Bedell2019} --- Data-driven spectral inference: \texttt{wobble} \\[0.5em]
+    %
+    \noindent\textbf{Theory} \\
+    \noindent\citet{Khokhlova1976,Goncharskii1977} --- Local line profile from observed spectrum\\
+    \noindent\citet{Vogt1983,Vogt1987} --- Seminal papers on Doppler imaging \\
+    \noindent\citet{Rice1989} ---  Another seminal paper\\
+    \noindent\citet{Deutsch1958,Deutsch1970,Falk1974} ---  Ylms + Doppler imaging\\
+    \noindent\citet{Unruh1995} --- sensitivity to line profile models\\
+    \noindent\citet{Piskunov1990} --- notes on regularization \\[0.5em]
+    %
+    \noindent\textbf{Application} \\
+    \noindent\citet{Crossfield2014} --- Global cloud map of Luhman 16B \\
+    \noindent\citet{Roettenbacher2017} --- Doppler imaging of $\sigma$ Geminorum \\
+}
+
 The paper is organized as follows: in \S\ref{sec:the_problem}~and~\S\ref{sec:the_solution} we introduce the math behind the Doppler imaging problem and derive a closed form expression for the model. 
@@
 They discretized the stellar surface using 200 cells and solved for the optimal surface map with a maximum entropy prior as in \citet{Vogt1987}, assuming a fiducial inclination $i=60^\circ$ roughly based on the photometric rotation period and the inferred value of $v\sin i$; given the low SNR of the dataset, they were unable to place meaningful constraints on $i$.
-We reproduce their resulting surface brightness map in the right panel of Figure~\ref{fig:luhman16b:maps}.
+We reproduce their resulting surface brightness map in the right panel of Figure~\ref{fig:luhman16b:maps}, seen at six different phases spanning a full rotation.
+
+\begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/luhman16b_data_model.pdf} % 
+        \caption{%
+            Calibrated and tellurics-corrected CRIRES spectra of Luhman 16B from \citet{Crossfield2014} taken at 14 epochs spanning a full rotation of the brown dwarf (black points).
+Our maximum \emph{a posteriori} solution is shown as the orange curves.
+        }
+        \label{fig:luhman16b:data_model}
+    \end{centering}
+\end{figure}
+%
+\begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=0.8\linewidth]{figures/luhman16b_spectra.pdf} % 
+        \caption{%
+            Unbroadened template spectra used to model the data in \citet{Crossfield2014} (blue curves).
+These were used as a prior on the spectra inferred in this work (orange curves).
+We infer a slightly different depth for some lines, as well as subtle changes in the continuum.
+        }
+        \label{fig:luhman16b:template_spectra}
+    \end{centering}
+\end{figure}
 
@@
 
-Our results are shown in Figures~\ref{fig:luhman16b:data_model}, \ref{fig:luhman16b:template_spectra}, and \ref{fig:luhman16b:maps}.
-In Figure~\ref{fig:luhman16b:data_model}, our maximum \emph{a posteriori} (MAP) model for each of the 14 spectra is shown as the orange line; it agrees with the data to within the measurement uncertainties.
-In Figure~\ref{fig:luhman16b:template_spectra} we show our MAP \emph{template} (rest frame) spectrum as the orange curve.
-Since we used the \citet{Crossfield2014} template as a prior (blue curve), our solution is very similar to the input spectrum.
-Nevertheless, we infer slightly different line depths for several of the lines at the level of a few percent; we also infer slightly different continuum levels in certain portions of the spectrum.
-Note, importantly, since we only performed an optimization (rather than full posterior inference), we cannot quantify the actual significance of these differences.
-
-The right panel of Figure~\ref{fig:luhman16b:maps} shows our principal result: the inferred solution for the surface brightness map of Luhman 16B.
-
-\begin{figure}[p!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/luhman16b_data_model.pdf} % 
-        \caption{%
-            Calibrated and tellurics-corrected CRIRES spectra of Luhman 16B from \citet{Crossfield2014} taken at 14 epochs spanning a full rotation of the brown dwarf (black points).
-Our maximum \emph{a posteriori} solution is shown as the orange curves.
-        }
-        \label{fig:luhman16b:data_model}
-    \end{centering}
-\end{figure}
-%
-\begin{figure}[p!]
-    \begin{centering}
-        \includegraphics[width=0.8\linewidth]{figures/luhman16b_spectra.pdf} % 
-        \caption{%
-            Unbroadened template spectra used to model the data in \citet{Crossfield2014} (blue curves).
-These were used as a prior on the spectra inferred in this work (orange curves).
-We infer a slightly different depth for some lines, as well as subtle changes in the continuum.
-        }
-        \label{fig:luhman16b:template_spectra}
-    \end{centering}
-\end{figure}
-%
 \begin{figure}[t!]
@@
 \end{figure}
-%
+
+Our results are shown in Figures~\ref{fig:luhman16b:data_model}, \ref{fig:luhman16b:template_spectra}, and \ref{fig:luhman16b:maps}.
+In Figure~\ref{fig:luhman16b:data_model}, our maximum \emph{a posteriori} (MAP) model for each of the 14 spectra is shown as the orange line; it agrees with the data to within the measurement uncertainties.
+In Figure~\ref{fig:luhman16b:template_spectra} we show our MAP \emph{template} (rest frame) spectrum as the orange curve.
+Since we used the \citet{Crossfield2014} template as a prior (blue curve), our solution is very similar to the input spectrum.
+Nevertheless, we infer slightly different line depths for several of the lines at the level of a few percent; we also infer slightly different continuum levels in certain portions of the spectrum.
+Note, importantly, since we only performed an optimization (rather than full posterior inference), we cannot quantify the actual significance of these differences.
+
+The right panel of Figure~\ref{fig:luhman16b:maps} shows our principal result: the inferred solution for the surface brightness map of Luhman 16B; compare to the right panel, showing the solution inferred by \citet{Crossfield2014}.
+Broadly speaking, the two surface maps agree rather well: we infer the same circumpolar bright spot, of about the same size and at roughly the same phase, as in the earlier work.
+We also infer a similar dark feature on the ``back'' side of the object (visible near the sub-observer point at $t = 2.4$ hours).
+Bright equatorial regions also broadly match between both solutions.
+There are some important differences, such as the contrast of the dark feature seen at $t = 0.0$ hours and the behavior of the $t = 2.4$ hour dark region beyond $60^\circ$ of the visible pole.
+In general, we find that different choices for our priors---in particular the regularization on the pixels, the prior on the limb darkening coefficient, and the value of the inclination of the star---result in maps that differ substantially.
+We do, however, agree with \citet{Crossfield2014} in that the polar bright spot is the most robust of the inferred features, followed by the bottom portion of the dark spot seen at $t = 2.4$ hours.
+Once again, since this is simply an \emph{optimization}, we are unable to place reliable uncertainties on our solutions.
+These require a sampling scheme like MCMC (\S\ref{sec:discussion}).
 
@@
         \item%
-              A gaussian prior with unit mean is a pretty bad prior for the spectrum.
+              Concerning our SPOT maps: a gaussian prior with unit mean is a pretty bad prior for the spectrum.
               In a more realistic scenario, we'd know a lot more information about the spectrum---such as where the lines are and some estimate of their shapes and depths---so the fidelity of our maps would be higher.
+This is what we did in the Luhman 16B case, and it works well.
               %
@@
         \item%
-              Telluric lines could be treated much as in Figure~\ref{fig:twospec}, and marginalized over as in \citet{Bedell2019}.
+              We are always integrating over the entire disk of the star. Can integrate over the unocculted
+              disk during an occultation (should actually be pretty trivial) so this can be used for Doppler
+              tomography once I have some time to work it out!
+        \item%
+              Telluric lines could be learned from the data as in \citet{Bedell2019}.
               %
@@
               %
-        \item Discuss the case where the inclination/period/velocity is unknown.
+        \item Discuss the case where the inclination/period/velocity is unknown, such as the case 
+              with Luhman 16B.
               The problem is not linear in these variables, so we need MCMC. 
@@
               Since typically $K \gg \lmax$, the latter computation dominates and the entire evaluation takes $\mathcal{O}(W K \lmax^2)$ operations.
+              [Is this still true? we do fast 2d convolutions, so it's actually much faster]
         \item%
-              Discuss: how to choose priors
+              Discuss: how to choose priors. Can use cross-validation to choose best regularization strength. In general, a positivity prior on the pixels is preferred.
+        \item%
+              Luhman 16B: we didn't account for finite exposure time.
+We didn't properly model instrumental broadening.
+We didn't do MCMC.
+We didn't vary the inclination.
+We didn't use maximum entropy regularization.
+But we solved for a whopping 4,000 parameters in under 3 minutes.
+We used the full spectrum.
     \end{enumerate}
@@
 \label{sec:starry}
+
+\xxx{A short section discussing the implementation in starry. Perhaps a figure showing how the runtime scales.}
 
@@
         \item Use in MCMC to marginalize over inclination and stuff
+        \item Advertise showyourwork for open source papers!
     \end{enumerate}

### 2021-09-30 src/ms.tex
text

@@
 \begin{abstract}
-    We derive a closed form solution to the problem of Doppler imaging of stellar surfaces in the limit of negligible differential rotation and convective blueshift.
-    The model for the observed spectrum is linear in the coefficients of the spherical harmonic expansion of the specific intensity distribution on the surface and, in certain limits, the posterior over surface maps has a closed form, analytic solution that is computationally trivial to evaluate.
-    The model is also linear in the local (rest frame) stellar spectrum, which may itself be spatially variable.
-    This allows one to perform Doppler imaging without knowledge of the local stellar spectrum and therefore works on blended lines or regions of the spectrum where line formation mechanisms are not well understood.
-    Finally, the model is fast, differentiable, and allows one to calculate uncertainties on the inferred surface map.
+    We derive a novel, efficient, and closed form solution to the problem of Doppler imaging of stellar surfaces from high resolution spectral timeseries datasets.
+    %
+    Our model for the observed spectrum is linear in the parameters describing the specific intensity distribution on the surface, which makes the posterior over surface maps computationally trivial to evaluate under certain choices of priors.
+    %
+    Our model is also linear in the local (rest frame) stellar spectrum, which may itself be spatially variable; this allows one to perform Doppler imaging with limited knowledge of the local stellar spectrum and therefore works on blended lines, regions of the spectrum where line formation mechanisms are not well understood, or stars whose spots have intrinsically different spectra from the rest of the photosphere.
+    %
+    We implement the model within the open-source \starry stellar modeling framework, making it fast, differentiable, and easy to use in both optimization and posterior inference settings.
+    %
+    As a proof-of-concept, we use our model to infer the surface map of the brown dwarf Luhman 16B, finding close agreement with the solution of \citet{Crossfield2014}.
+    %
+    %While our derivation neglects the effects of differential rotation and convective blueshift, these are straightforward to include and will be addressed in an upcoming paper, which will also extend the present formalism to the problem of Doppler tomography.
+    %
+    This paper was prepared using the \texttt{showyourwork} scientific article workflow, which exposes the data, source code, and package dependencies for all of the paper's figures, allowing readers to reproduce the results in this paper exactly and with minimal effort.
 \end{abstract}
@@
 In \S\ref{sec:linear},~\S\ref{sec:inverse},~and~\S\ref{sec:bellswhistles} we demonstrate how to re-express the model as a linear operation on the input spectrum and stellar map and derive closed form expressions for the two conditioned on the data and priors.
-In \S\ref{sec:spotstar} we apply our techniques to a mock problem. 
-We further discuss and summarize our results in \S\ref{sec:discussion}~and~\S\ref{sec:conclusions}. 
-Finally, auxiliary derivations are presented in the Appendix.
+In \S\ref{sec:spotstar} we apply our techniques to a mock problem,
+and in \S\ref{sec:luhman16b} we apply it to a real spectral dataset of the brown dwarf Luhman 16B.
+We further discuss our results in \S\ref{sec:discussion}~and~our implementation within the \starry framework in \S\ref{sec:starry}. We present a summary of the paper in \S\ref{sec:conclusions}.
 
@@
 The standard approach to solving this integral is therefore to discretize the surface of the star with a fine grid, evaluate the Doppler-shifted spectrum in each cell, and sum over the spatial axes to approximate the integral.
-Depending on the resolution of the grid, this is either numerically inaccurate or computationally inefficient.
+Depending on the resolution of the grid, this may be either numerically inaccurate or computationally inefficient.
 

### 2021-10-01 src/ms.tex
starry section

@@
 
-Having shown that our model performs well on synthetic data, we now turn to a real dataset: the VLT/CRIRES observations of Luhman 16B presented in the Doppler imaging study of \citet{Crossfield2014}.
+Having shown that our model performs well on synthetic data, we now turn to a real dataset: the VLT/CRIRES observations of Luhman 16B (WISE 1049-5319B) presented in the Doppler imaging study of \citet{Crossfield2014}.
 Luhman 16B belongs to a binary brown dwarf system, which at a distance of 2 pc are the closest known brown dwarfs to the Solar system.
 Nevertheless, the object is intrinsically dim and, with a projected rotational velocity $v \sin i = 26.1$ km/s, is at the slow end of what can be imaged using the traditional Doppler imaging technique.
-Therefore, unlike those of classical Doppler imaging targets, the spectral lines of Luhman 16B do not show obvious spot modulation (Figure~\ref{fig:spot}) from one epoch to the next; nor are the spectral templates for these objects particularly well understood.
+Therefore, unlike those of classical Doppler imaging targets, the spectral lines of Luhman 16B do not individually show obvious spot modulation (Figure~\ref{fig:spot}) from one epoch to the next; nor are the spectral templates for these objects particularly well understood.
 Nonetheless, we chose to model Luhman 16B specifically to show the power behind our new methodology, in particular its ability to learn both the surface map and the rest frame spectrum simultaneously from the entire dataset---not just from unblended spectral lines that have reliable templates.
 
-In the original Doppler imaging study of this target, \citet{Crossfield2014} took 56 spectra of each object (the angular resolution was high enough to obtain individual spectra of both brown dwarfs) in four channels in the range $2.288-2.345 \mu$m over a time span of 5 hours, with individual exposures of 300 s.
+In the original Doppler imaging study of this target, \citet{Crossfield2014} took 56 spectra of each object (the angular resolution was high enough to obtain individual spectra of both brown dwarfs) over the four CRIRES detectors in the range $2.288-2.345 \mu$m over a time span of 5 hours, with individual exposures of 300 s.
 The 5 hour baseline was enough to capture one full rotation of Luhman 16B, whose period was constrained to be about 4.9 hours from its photometric variability \citep{Gillon2013}.
-These spectra were then downbinned to 14 epochs, corrected for tellurics and spectrograph systematics, and continuum-normalized.
-Each of the 14 spectra consist of 1,024 intensity measurements in each of 4 channels, for a total of $57,344$ data points.
+These spectra were then downbinned to 14 epochs to boost the SNR, corrected for tellurics and spectrograph systematics, and continuum-normalized.
+Each of the 14 spectra consist of 1,024 intensity measurements in each of 4 detectors, for a total of $57,344$ data points.
 For more details on the data reduction, refer to \citet{Crossfield2014}.
 
-The black points in Figure~\ref{fig:luhman16b:data_model} show the exact dataset used in the Doppler imaging analysis of \citet{Crossfield2014}, except for the fact that we masked additional outliers at $>4\sigma$ as well as regions of the spectrum that had been visibly overcorrected for tellurics.
+The black points in Figure~\ref{fig:luhman16b:data_model} show the exact dataset used in the Doppler imaging analysis of \citet{Crossfield2014}, except for the fact that we masked additional outliers at $>4\sigma$ (identified by subtracting a version of the spectrum smoothed on a lengthscale of 20 pixels) as well as regions of the spectrum that had been visibly overcorrected for tellurics.
 This figure shows the same data as the lower panel of Extended Data Figure 2 in \citet{Crossfield2014}.
@@
 We must also change the way we model the continuum normalization (\S\ref{sec:norm}), given the high density of spectral lines and the consequent difficulty of finding a reliable continuum level to normalize against.
-Instead, we treat the unknown continuum normalization factor for each of the 14 epochs as a free parameter of the model, $f \sim \mathrm{Uniform}(0.3, 3.0)$; we also allow for a small, time-independent, additive offset $\Delta \sim \mathcal{N}(0, 0.1^2)$ for each of the four spectral channels.
+Instead, we treat the unknown continuum normalization factor for each of the 14 epochs as a free parameter of the model, $f \sim \mathrm{Uniform}(0.3, 3.0)$; we also allow for a small, time-independent, additive offset $\Delta \sim \mathcal{N}(0, 0.1^2)$ for each of the four detectors.
 We assume the same fiducial inclination $i = 60^\circ$, a rotational period $P = 4.9$ days, and allow the linear limb darkening coefficient and projected velocity to vary subject to $u_1 \sim \mathrm{Uniform}(0, 1)$ and $v \sin i \sim \mathcal{N}(26.1, 0.2^2)$ km/s, respectively, as in \citet{Crossfield2014}.
 Finally, we place a uniform prior on the pixel intensities $\bvec{p} \sim \mathrm{Uniform}(0, 1)$ as in \S\ref{sec:twospec}, linearly transforming to an $l_\mathrm{max} = 10$ spherical harmonic representation of the map to compute the model at each step.
-We must therefore solve for $2 \times (l_\mathrm{max} + 1)^2 = 242$ free parameters for the pixelized surface map, $3,748$ free parameters for the rest frame spectrum across each of the four channels (equal to the size of our template spectrum after removing outliers), $18$ parameters describing the continuum normalization, and $2$ stellar parameters (the linear limb darkening coefficient and the projected velocity).
+We must therefore solve for $2 \times (l_\mathrm{max} + 1)^2 = 242$ free parameters for the pixelized surface map, $3,748$ free parameters for the rest frame spectrum across each of the four detectors (equal to the size of our template spectrum after removing outliers), $18$ parameters describing the continuum normalization, and $2$ stellar parameters (the linear limb darkening coefficient and the projected velocity).
 In total, our model has just over $4,000$ free parameters.
@@
         \item%
-              Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires first the rotation of the $(\lmax + 1)^2$ $\kT$ kernels (each of length $W$) to the correct stellar rotational phase, an operation that scales approximately as $W \lmax^3$, followed by $(\lmax + 1)^2$ linear convolutions of the rotated $\kT$ kernels with the spectral components (each of length $K$), which scales approximately as $W K \lmax^2$.
-              Since typically $K \gg \lmax$, the latter computation dominates and the entire evaluation takes $\mathcal{O}(W K \lmax^2)$ operations.
-              [Is this still true? we do fast 2d convolutions, so it's actually much faster]
-        \item%
               Discuss: how to choose priors. Can use cross-validation to choose best regularization strength. In general, a positivity prior on the pixels is preferred.
@@
 
-\section{Implementation in starry}
+\section{Implementation in \starry}
 \label{sec:starry}
 
-\xxx{A short section discussing the implementation in starry. Perhaps a figure showing how the runtime scales.}
+We implement the algorithm presented here in the \starry package \citep{Luger2019,Luger2021c}, an open-source \texttt{Python} library for stellar and planetary light curve analysis. 
+All of the figures in this paper were generated via the Doppler imaging API in \starry. 
+The scripts used to generate them are available on GitHub\footnote{\url{https://github.com/rodluger/paparazzi}} and can be directly accessed via the GitHub icons next to each figure caption.
+These are well-commented and can be used as a starting point for other Doppler imaging projects.
+
+The algorithm is implemented using \texttt{theano} \citep{Bergstra2010}, a just-in-time compiling framework for \texttt{Python} with powerful autodifferentiation and optimization capabilities.
+As such, the algorithm is fully differentiable and thus easy to use within gradient-based optimization and/or inference schemes such as Hamiltonian Monte Carlo.
+The analysis presented in Figures~\ref{fig:spot_infer_ybs} and \ref{fig:luhman16b:data_model}---\ref{fig:luhman16b:maps} harnesses this capability within the \texttt{pymc3} modeling framework; refer to the corresponding scripts for details.
+
+The implementation of the algorithm in \starry is highly optimized.
+Even though we derived the model for the flux as a purely linear operation on the spectral/spatial expansion of the stellar surface (Equation~\ref{eq:deconv:F}), it is more  efficient in practice to compute it as a convolution using the highly optimized \texttt{conv2d} operations in \texttt{theano}.
+Typical runtimes and scalings for the \starry algorithm are shown in Figure~\ref{fig:runtime}, where we plot the evaluation of the full forward model for all spectra in a dataset as a function of several parameters.
+%
+\begin{figure}[t!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/runtime.pdf}
+        \caption{%
+            Model evaluation time as a function of various parameters, for spherical harmonic degree $l_\mathrm{max} = 10$, $M = 10$ spectral epochs, $K = 200$ wavelength bins, and $v\sin i = 50$ km/s.
+Thin lines correspond to individual trials; the thick lines show the median evaluation time.
+Timing tests were performed on a 2-core Linux virtual GitHub Actions machine.
+        }
+        \label{fig:runtime}
+    \end{centering}
+\end{figure}
+%
+Equation~(\ref{eq:deconv:F}) requires first the rotation of the $(\lmax + 1)^2$ $\kT$ kernels (each of length $W$) to the correct stellar rotational phase, an operation that scales approximately as $W \lmax^3$, followed by $(\lmax + 1)^2$ linear convolutions of the rotated $\kT$ kernels with the spectral components (each of length $K$), which scales approximately as $W K \lmax^2$.
+Since typically $K \gg \lmax$, the latter computation dominates and the entire evaluation of the model for $M$ spectral epochs takes $\mathcal{O}(M W K \lmax^2)$ operations. 
+This is consistent with the relationships shown in Figure~\ref{fig:runtime}: the runtime is linearly proportional to the number of spectral epochs $M$, the number of wavelength bins $K$, and the width of the convolution kernel $W \propto v\sin i$; and it scales quadratically with the degree of the spherical harmonic expansion $l_\mathrm{max}$.
+In general, evalution of the model for a typical dataset takes on the order of 10 or a few tens of milliseconds.
 
@@
         \item Advertise showyourwork for open source papers!
+        \item \citet{Crossfield2014b} and \citet{Snellen2014}: people talk seriously about making Doppler Imaging maps of directly-imaged planets like beta Pic b with the ELTs.
+Those will be tough measurements but could be the first real, global​ maps of any planet beyond the solar system (sorry, but eclipse-mapping just doesn't quite cut it so far...).
+So we need the best possible algorithms to maximize what we get our of the data.
+        \item \citep{Tan2019,Tan2020,Tan2021a,Tan2021b}: Xianyu is the main person running simulations of brown dwarf global weather patterns, and the techniques outlined in your paper will offer the best way to test those models.
     \end{enumerate}

### 2021-10-02 src/ms.tex
fix color normalization and inclination

@@
 Alternatively, we may compute $\boldsymbol{\Lambda}_\bvec{y}$ from the Gaussian process formalism in \citet{Luger2021b} to incorporate explicit prior information on the typical latitudes, sizes, and contrasts of spots.
-We discuss this point further in \S\ref{sec:discussion}.
+We discuss this point further in \S\ref{sec:discussion:priors}.
 
@@
 To \emph{correctly} account for this, one must resort to Monte Carlo methods or other sampling techniques. 
-We discuss this further in \S\ref{sec:discussion}.
+We discuss this further in \S\ref{sec:discussion:mcmc}.
 
@@
 These choices are arbitrary and primarily based on trial-and-error given knowledge of the true solutions.
-We discuss strategies for choosing optimal priors for real datasets in \S\ref{sec:discussion} below.
+We discuss strategies for choosing optimal priors for real datasets in \S\ref{sec:discussion:priors} below.
 
@@
 In order to constrain the true uncertainty on the solution to this bilinear problem, we must resort to approximate sampling methods such as MCMC. 
-We discuss this further in \S\ref{sec:discussion}.
+We discuss this further in \S\ref{sec:discussion:mcmc}.
 
@@
 %
-We generate the synthetic dataset in the same way as in \S\ref{sec:spot_y1}: 16 spectra, each with 70 wavelength bins observed with SNR$\sim 10^{3}$.
+We generate the synthetic dataset in the same way as in \S\ref{sec:spot_y1}: 16 spectra, each with 70 wavelength bins observed with SNR $\sim 10^{3}$.
 
@@
 We also slightly overestimate the baseline level of the spot spectrum, but we correctly recover the locations, shapes, and depths of the two absorption lines.
-Note, importantly, that the nonlinear optimization step does not yield uncertainties (or lower bounds, like the bilinear solver); for this, we must resort to MCMC sampling (see \S\ref{sec:discussion}).
+Note, importantly, that the nonlinear optimization step does not yield uncertainties (or lower bounds, like the bilinear solver); for this, we must resort to MCMC sampling (see \S\ref{sec:discussion:mcmc}).
 
@@
 Nevertheless, the object is intrinsically dim and, with a projected rotational velocity $v \sin i = 26.1$ km/s, is at the slow end of what can be imaged using the traditional Doppler imaging technique.
-Therefore, unlike those of classical Doppler imaging targets, the spectral lines of Luhman 16B do not individually show obvious spot modulation (Figure~\ref{fig:spot}) from one epoch to the next; nor are the spectral templates for these objects particularly well understood.
+Therefore, unlike those of classical Doppler imaging targets, the spectral lines of Luhman 16B do not individually show large scale spot modulation (Figure~\ref{fig:spot}) from one epoch to the next; nor are the spectral templates for these objects particularly well understood.
 Nonetheless, we chose to model Luhman 16B specifically to show the power behind our new methodology, in particular its ability to learn both the surface map and the rest frame spectrum simultaneously from the entire dataset---not just from unblended spectral lines that have reliable templates.
@@
 \citet{Crossfield2014} then employed the common technique of Least Squares Deconvolution \citep[LSD;][]{Donati1997} to transform each of the 14 spectra in Figure~\ref{fig:luhman16b:data_model} into a single high-SNR line spanning 35 pixels, which was used as the input to their Doppler imaging code, based on that of \citet{Vogt1987}.
-They discretized the stellar surface using 200 cells and solved for the optimal surface map with a maximum entropy prior as in \citet{Vogt1987}, assuming a fiducial inclination $i=60^\circ$ roughly based on the photometric rotation period and the inferred value of $v\sin i$; given the low SNR of the dataset, they were unable to place meaningful constraints on $i$.
+They discretized the stellar surface using 200 cells and solved for the optimal surface map with a maximum entropy prior as in \citet{Vogt1987}, assuming a fiducial inclination $i=70^\circ$ roughly based on the photometric rotation period and the inferred value of $v\sin i$; given the low SNR of the dataset, they were unable to place meaningful constraints on $i$.
 We reproduce their resulting surface brightness map in the right panel of Figure~\ref{fig:luhman16b:maps}, seen at six different phases spanning a full rotation.
@@
     \begin{centering}
-        \includegraphics[width=0.8\linewidth]{figures/luhman16b_spectra.pdf} % 
+        \includegraphics[width=\linewidth]{figures/luhman16b_spectra.pdf} % 
         \caption{%
@@
 Instead, we treat the unknown continuum normalization factor for each of the 14 epochs as a free parameter of the model, $f \sim \mathrm{Uniform}(0.3, 3.0)$; we also allow for a small, time-independent, additive offset $\Delta \sim \mathcal{N}(0, 0.1^2)$ for each of the four detectors.
-We assume the same fiducial inclination $i = 60^\circ$, a rotational period $P = 4.9$ days, and allow the linear limb darkening coefficient and projected velocity to vary subject to $u_1 \sim \mathrm{Uniform}(0, 1)$ and $v \sin i \sim \mathcal{N}(26.1, 0.2^2)$ km/s, respectively, as in \citet{Crossfield2014}.
+We assume the same fiducial inclination $i = 70^\circ$, a rotational period $P = 4.9$ days, and allow the linear limb darkening coefficient and projected velocity to vary subject to $u_1 \sim \mathrm{Uniform}(0, 1)$ and $v \sin i \sim \mathcal{N}(26.1, 0.2^2)$ km/s, respectively, as in \citet{Crossfield2014}.
 Finally, we place a uniform prior on the pixel intensities $\bvec{p} \sim \mathrm{Uniform}(0, 1)$ as in \S\ref{sec:twospec}, linearly transforming to an $l_\mathrm{max} = 10$ spherical harmonic representation of the map to compute the model at each step.
@@
 Once again, since this is simply an \emph{optimization}, we are unable to place reliable uncertainties on our solutions.
-These require a sampling scheme like MCMC (\S\ref{sec:discussion}).
+These require a sampling scheme like MCMC (\S\ref{sec:discussion:mcmc}).
 
@@
 
-\xxx{%
-    \begin{enumerate}
-        %
-        \item%
-              Concerning our SPOT maps: a gaussian prior with unit mean is a pretty bad prior for the spectrum.
-              In a more realistic scenario, we'd know a lot more information about the spectrum---such as where the lines are and some estimate of their shapes and depths---so the fidelity of our maps would be higher.
-This is what we did in the Luhman 16B case, and it works well.
-              %
-        \item%
-              We are not addressing differential rotation and convective blueshift.
-              These make the integral in Equation~(\ref{eq:deconv:kT}) very difficult to solve. 
-              We will tackle this in the next paper.
-              %
-        \item%
-              We are always integrating over the entire disk of the star. Can integrate over the unocculted
-              disk during an occultation (should actually be pretty trivial) so this can be used for Doppler
-              tomography once I have some time to work it out!
-        \item%
-              Telluric lines could be learned from the data as in \citet{Bedell2019}.
-              %
-        \item% 
-              The instrumental profile is another Toeplitz matrix that can be dotted into Equation~(\ref{eq:linear:f}).
-              %
-        \item Discuss the case where the inclination/period/velocity is unknown, such as the case 
-              with Luhman 16B.
-              The problem is not linear in these variables, so we need MCMC. 
-              But our model is differentiable, so we can easily use HMC. 
-              Discuss.
-              %
-        \item%
-              Discuss: how to choose priors. Can use cross-validation to choose best regularization strength. In general, a positivity prior on the pixels is preferred.
-        \item%
-              Luhman 16B: we didn't account for finite exposure time.
+\subsection{Luhman 16B}
+\label{sec:discussion:luhman}
+
+In \S\ref{sec:luhman16b} we validated our novel approach by reproducing the results of \citet{Crossfield2014}.
+Despite the fact that we obtained a qualitatively similar surface map for Luhman 16B (Figure~\ref{fig:luhman16b:maps}), there are several aspects to our approach that could be improved in future work.
+First, we did not vary the inclination, but instead kept it fixed at the fiducial value $i = 70^\circ$ used in \citet{Crossfield2014}.
+The authors of that study argued that the SNR of the dataset was too low to constrain the inclination, and that their surface maps did not qualitatively change by varying the inclination between $60^\circ$ and $90^\circ$, the range consistent with the joint knowledge of the rotation period and $v\sin i$.
+\xxx{...}
+
+We didn't account for finite exposure time.
 We didn't properly model instrumental broadening.
@@
 We used the full spectrum.
-    \end{enumerate}
-}
+\xxx{...}
+
+Concerning our SPOT maps: a gaussian prior with unit mean is a pretty bad prior for the spectrum.
+In a more realistic scenario, we'd know a lot more information about the spectrum---such as where the lines are and some estimate of their shapes and depths---so the fidelity of our maps would be higher.
+This is what we did in the Luhman 16B case, and it works well.
+\xxx{...}
+
+\subsection{Priors and regularization}
+\label{sec:discussion:priors}
+Discuss: how to choose priors. Can use cross-validation to choose best regularization strength. In general, a positivity prior on the pixels is preferred.
+\xxx{...}
+
+\subsection{Posterior sampling}
+\label{sec:discussion:mcmc}
+
+Discuss the case where the inclination/period/velocity is unknown, such as the case with Luhman 16B.
+The problem is not linear in these variables, so we need MCMC. 
+But our model is differentiable, so we can easily use HMC. 
+Discuss.
+\xxx{...}
+
+\subsection{Limitations and future work}
+\label{sec:discussion:caveats}
+
+We are not addressing differential rotation and convective blueshift.
+These make the integral in Equation~(\ref{eq:deconv:kT}) very difficult to solve. 
+We will tackle this in the next paper.
+\xxx{...}
+
+The instrumental profile is another Toeplitz matrix that can be dotted into Equation~(\ref{eq:linear:f}).
+\xxx{...}
+
+We are always integrating over the entire disk of the star.
+Can integrate over the unocculted disk during an occultation (should actually be pretty trivial) so this can be used for Doppler tomography once I have some time to work it out!
+\xxx{...}
+
+Telluric lines could be learned from the data as in \citet{Bedell2019}.
+\xxx{...}
 

### 2021-10-02 src/ms.tex
more text

@@
 \xxx{%
-    \noindent Introduce the problem of Doppler imaging. Then cite the following papers:\\[0.5em]
+    \noindent Introduce the problem of Doppler imaging.
+    Then cite the following papers:\\[0.5em]
     \noindent\textbf{Misc.} \\
@@
 In \S\ref{sec:linear},~\S\ref{sec:inverse},~and~\S\ref{sec:bellswhistles} we demonstrate how to re-express the model as a linear operation on the input spectrum and stellar map and derive closed form expressions for the two conditioned on the data and priors.
-In \S\ref{sec:spotstar} we apply our techniques to a mock problem,
-and in \S\ref{sec:luhman16b} we apply it to a real spectral dataset of the brown dwarf Luhman 16B.
-We further discuss our results in \S\ref{sec:discussion}~and~our implementation within the \starry framework in \S\ref{sec:starry}. We present a summary of the paper in \S\ref{sec:conclusions}.
+In \S\ref{sec:spotstar} we apply our techniques to a mock problem, and in \S\ref{sec:luhman16b} we apply it to a real spectral dataset of the brown dwarf Luhman 16B.
+We further discuss our results in \S\ref{sec:discussion}~and~our implementation within the \starry framework in \S\ref{sec:starry}.
+We present a summary of the paper in \S\ref{sec:conclusions}.
 
@@
 %
-The first thing we will do is to express Equation~(\ref{eq:the_problem:Ixi})
-as a convolution:
+The first thing we will do is to express Equation~(\ref{eq:the_problem:Ixi}) as a convolution:
 %
@@
 where it is clear that we have fully separated the spatial, temporal, and spectral terms. 
-Inserting this into Equation~(\ref{eq:deconv:convolution})
-and integrating over the visible portion of the star, we arrive at the expression for the observed spectrum:
+Inserting this into Equation~(\ref{eq:deconv:convolution}) and integrating over the visible portion of the star, we arrive at the expression for the observed spectrum:
 %
@@
         \caption{%
-            The observed spectrum when the spot is in view computed with
-            our algorithm (blue) and numerically (orange). 
+            The observed spectrum when the spot is in view computed with our algorithm (blue) and numerically (orange). 
             The problem setup is the same as that in Figure~\ref{fig:spot}. 
@@
 
-Although the convolution operator (Equation~\ref{eq:deconv:convolution_def})
-is defined for continuous functions, the problem of Doppler imaging deals with discrete measurements of a spectrum in bins of log wavelength. 
+Although the convolution operator (Equation~\ref{eq:deconv:convolution_def}) is defined for continuous functions, the problem of Doppler imaging deals with discrete measurements of a spectrum in bins of log wavelength.
 Provided our wavelength grid is fine enough, we may therefore approximate Equation~(\ref{eq:deconv:convolution_def}) with a discrete convolution.
@@
 The advantage of this linearity is that, given suitable priors, it allows one to compute both the maximum likelihood solution for $\alm$ and its uncertainty \emph{analytically}. 
-In particular, if one places a (multidimensional) Gaussian prior on $\alm$ with mean $\boldsymbol{\mu}_\mathbf{a}$ and covariance $\boldsymbol{\Lambda}_\mathbf{a}$, the maximum \emph{a posteriori} (MAP)
-solution for $\alm$ is given by the solution to the L2 regularization problem \citep[see, e.g.,][]{Luger2016}:
+In particular, if one places a (multidimensional) Gaussian prior on $\alm$ with mean $\boldsymbol{\mu}_\mathbf{a}$ and covariance $\boldsymbol{\Lambda}_\mathbf{a}$, the maximum \emph{a posteriori} (MAP) solution for $\alm$ is given by the solution to the L2 regularization problem \citep[see, e.g.,][]{Luger2016}:
 %
@@
 %
-Given Gaussian priors on these two quantities,
-it is straightforward to show that because Equation~(\ref{eq:linear:f}) is linear in $\alm$, it is also linear in both $\bvec{s}$ and $\bvec{y}$, so MAP solutions can be found analytically for $\bvec{s}$ (conditioned on $\bvec{y}$) and $\bvec{y}$ (conditioned on $\bvec{s}$).
+Given Gaussian priors on these two quantities, it is straightforward to show that because Equation~(\ref{eq:linear:f}) is linear in $\alm$, it is also linear in both $\bvec{s}$ and $\bvec{y}$, so MAP solutions can be found analytically for $\bvec{s}$ (conditioned on $\bvec{y}$) and $\bvec{y}$ (conditioned on $\bvec{s}$).
 A solution to the full problem of determining both $\bvec{s}$ and $\bvec{y}$ can then be obtained by iteratively solving these two problems.
@@
 To \emph{correctly} account for this, one must resort to Monte Carlo methods or other sampling techniques. 
-We discuss this further in \S\ref{sec:discussion:mcmc}.
+We discuss this further in \S\ref{sec:discussion:priors}.
 
@@
 %
-where $\fnorm$ is the normalized spectral timeseries,
-$\bvec{B}$ is the baseline design matrix, and the vector division is performed
-elementwise. 
+where $\fnorm$ is the normalized spectral timeseries, $\bvec{B}$ is the baseline design matrix, and the vector division is performed elementwise. 
 If $c$ is an index in the observed spectrum corresponding to the continuum (at all epochs), the elements of $\bvec{B}$ are computed from
@@
 When solving for the spectrum given the spherical harmonic vector (\S\ref{sec:solve_s}), we need only make the replacements 
+%
 $\bvec{f} \rightarrow \fnorm \circ (\bvec{B}\, \bvec{a})$ 
+%
 and 
+%
 $\boldsymbol{\Sigma}_\mathbf{f} \rightarrow \boldsymbol{\Sigma}_{\fnorm} \circ (\bvec{B}\, \bvec{a})^2$ 
+%
 in Equations~(\ref{eq:inverse:shat}) and (\ref{eq:inverse:scov}), where $\circ$ denotes the elementwise product.
@@
 The model remains linear in both the spherical harmonic coefficients and the spectral components, and the procedures outlined in \S\ref{sec:inverse} may still be followed to solve the inverse problem, provided we unroll these matrices into vectors, letting $\mathbf{s} = \mathrm{vec}(\boldsymbol{\mathbb{S}})$ and $\mathbf{y} = \mathrm{vec}(\boldsymbol{\mathbb{Y}})$.
-We present an example of inference on a two-component stellar spectrum in \S\ref{sec:twospec}
-below.
+We present an example of inference on a two-component stellar spectrum in \S\ref{sec:twospec} below.
 
@@
 Finally, we divide the flux by the baseline at each epoch (Equation~\ref{eq:norm:f}) and add random Gaussian noise with covariance matrix $\boldsymbol{\Sigma}_\bvec{f} = \sigma_\bvec{f}^2 \mathbf{I}$, with $\sigma_\bvec{f} = 2\times 10^{-4}$ to simulate a very high signal-to-noise ratio (SNR) spectrum.
-The typical fractional line depth in the observed spectrum is 0.2,
-so our choice of $\sigma_\bvec{f}$ corresponds to SNR $\sim 10^{3}$ in each of the 70 wavelength bins of $\bvec{f}$.
+The typical fractional line depth in the observed spectrum is 0.2, so our choice of $\sigma_\bvec{f}$ corresponds to SNR $\sim 10^{3}$ in each of the 70 wavelength bins of $\bvec{f}$.
 
@@
 This is analogous to the case where a good physical model exists for the stellar spectrum and simultaneous photometry is available to constrain the baseline variations.
-As we showed in \S\ref{sec:solve_y}, the posterior distribution for the map coefficients $\bvec{y}$ is analytic in this case, with mean given by Equation~(\ref{eq:inverse:y1hat})
-and covariance given by Equation~(\ref{eq:inverse:y1cov}). 
+As we showed in \S\ref{sec:solve_y}, the posterior distribution for the map coefficients $\bvec{y}$ is analytic in this case, with mean given by Equation~(\ref{eq:inverse:y1hat}) and covariance given by Equation~(\ref{eq:inverse:y1cov}).
 Note that we must first scale the data vector $\fnorm$ by the baseline (which in this case is known) to obtain $\bvec{f}$.
@@
             The solution to the \spot problem at high SNR when both the rest frame spectrum and the baseline are known.
-            The panel on the left shows the inferred map at each of the 16
-            epochs, alongside the observed spectrum (black points) and the best-fit model (orange lines). 
+            The panel on the left shows the inferred map at each of the 16 epochs, alongside the observed spectrum (black points) and the best-fit model (orange lines). 
             The Mollweide projection of the original map is shown at the top right; the inferred map is displayed below it. 
@@
 The left hand panel shows the inferred map alongside the data (black points) and best fit model (orange curves) at each of the 16 epochs.
-The panels on the right show the true map (top), the inferred map (center)
-and the posterior pointwise uncertainty (bottom) on a Mollweide grid. 
+The panels on the right show the true map (top), the inferred map (center) and the posterior pointwise uncertainty (bottom) on a Mollweide grid. 
 The uncertainty on the vector of pixels $\bvec{p}$ where we evaluate the map is equal to the square root of the diagonal of the posterior covariance matrix for the pixel values, computed from
@@
 We next investigate the case where the spectrum is known exactly, but the baseline is not. 
-This corresponds to the case discussed in
-\S\ref{sec:norm}, in which each spectrum is normalized to its continuum, and the true difference in continuum levels across spectral epochs is not precisely known.
+This corresponds to the case discussed in \S\ref{sec:norm}, in which each spectrum is normalized to its continuum, and the true difference in continuum levels across spectral epochs is not precisely known.
 This is likely to be the most common application of the methodology presented in this work.
@@
             Similar to Figure~\ref{fig:spot_infer_y}, but assuming the input spectra are continuum-normalized.
-            We are able to infer the surface map just as
-            well as in the case where the true continuum level
-            is known (Figure~\ref{fig:spot_infer_y}). As before,
-            regions south of the equator are almost never in view, so that portion of our inferred map is dominated by the prior.
+            We are able to infer the surface map just as well as in the case where the true continuum level is known (Figure~\ref{fig:spot_infer_y}). 
+            As before, regions south of the equator are almost never in view, so that portion of our inferred map is dominated by the prior.
             Note that the uncertainty shown (lower panel) is a strict lower bound on the true uncertainty, as it is conditioned on our point estimate of the baseline level.
@@
 In order to constrain the true uncertainty on the solution to this bilinear problem, we must resort to approximate sampling methods such as MCMC. 
-We discuss this further in \S\ref{sec:discussion:mcmc}.
+We discuss this further in \S\ref{sec:discussion:priors}.
 
@@
 
-Figure~\ref{fig:spot_infer_ybs} shows the results; 
-the top portion of the figure is the same as in Figure~\ref{fig:spot_infer_yb}.
+Figure~\ref{fig:spot_infer_ybs} shows the results; the top portion of the figure is the same as in Figure~\ref{fig:spot_infer_yb}.
 A panel has been added at the bottom showing the true rest frame spectrum (blue), the initial guess based on the deconvolution (dashed orange), and the inferred spectrum with 1-$\sigma$ uncertainty shading (orange).
@@
 Finally, in order to enforce that the two component surface maps sum to unity (as described above), we optimize for the actual \emph{pixel} intensities of the photosphere map, on which we place a simple uniform prior on $[0, 1]$; the spot map is then simply the complement.
-The spherical harmonic coefficients are then computed via a fast, linear spherical harmonic transform (SHT) operation at each step.
+The spherical harmonic coefficients are then computed via a fast, linear spherical harmonic transform (SHT) operation at each step, as in \citep{Bartolic2021}.
 In order to satisfy the Nyquist criterion, our pixel grid consists of twice as many pixels as spherical harmonic coefficients.
@@
 We also slightly overestimate the baseline level of the spot spectrum, but we correctly recover the locations, shapes, and depths of the two absorption lines.
-Note, importantly, that the nonlinear optimization step does not yield uncertainties (or lower bounds, like the bilinear solver); for this, we must resort to MCMC sampling (see \S\ref{sec:discussion:mcmc}).
+Note, importantly, that the nonlinear optimization step does not yield uncertainties (or lower bounds, like the bilinear solver); for this, we must resort to MCMC sampling (see \S\ref{sec:discussion:priors}).
 
@@
         \caption{%
-            Recovered \spot map as a function of SNR per resolution element. The observed spectra are continuum-normalized and the rest frame spectrum is assumed to be known exactly.
+            Recovered \spot map as a function of SNR per resolution element. 
+            The observed spectra are continuum-normalized and the rest frame spectrum is assumed to be known exactly.
         }
@@
 Having shown that our model performs well on synthetic data, we now turn to a real dataset: the VLT/CRIRES observations of Luhman 16B (WISE 1049-5319B) presented in the Doppler imaging study of \citet{Crossfield2014}.
-Luhman 16B belongs to a binary brown dwarf system, which at a distance of 2 pc are the closest known brown dwarfs to the Solar system.
-Nevertheless, the object is intrinsically dim and, with a projected rotational velocity $v \sin i = 26.1$ km/s, is at the slow end of what can be imaged using the traditional Doppler imaging technique.
-Therefore, unlike those of classical Doppler imaging targets, the spectral lines of Luhman 16B do not individually show large scale spot modulation (Figure~\ref{fig:spot}) from one epoch to the next; nor are the spectral templates for these objects particularly well understood.
+Luhman 16B belongs to a binary brown dwarf system, which, at a distance of 2 pc, consists of the two closest known brown dwarfs to the Solar system.
+Despite its proximity, Luhman 16B is intrinsically dim and, with a projected rotational velocity $v \sin i = 26.1$ km/s, is at the slow end of what can be imaged using the traditional Doppler imaging technique.
+Therefore, unlike those of classical Doppler imaging targets, the spectral lines of Luhman 16B do not individually show large scale spot modulation (Figure~\ref{fig:spot}) from one epoch to the next; nor are the spectral templates for brown dwarfs particularly well understood.
 Nonetheless, we chose to model Luhman 16B specifically to show the power behind our new methodology, in particular its ability to learn both the surface map and the rest frame spectrum simultaneously from the entire dataset---not just from unblended spectral lines that have reliable templates.
@@
 We must also change the way we model the continuum normalization (\S\ref{sec:norm}), given the high density of spectral lines and the consequent difficulty of finding a reliable continuum level to normalize against.
-Instead, we treat the unknown continuum normalization factor for each of the 14 epochs as a free parameter of the model, $f \sim \mathrm{Uniform}(0.3, 3.0)$; we also allow for a small, time-independent, additive offset $\Delta \sim \mathcal{N}(0, 0.1^2)$ for each of the four detectors.
+We therefore treat the unknown continuum normalization factor for each of the 14 epochs as a free parameter of the model, $f \sim \mathrm{Uniform}(0.3, 3.0)$; we also allow for a small, time-independent, additive offset $\Delta \sim \mathcal{N}(0, 0.1^2)$ for each of the four detectors.
 We assume the same fiducial inclination $i = 70^\circ$, a rotational period $P = 4.9$ days, and allow the linear limb darkening coefficient and projected velocity to vary subject to $u_1 \sim \mathrm{Uniform}(0, 1)$ and $v \sin i \sim \mathcal{N}(26.1, 0.2^2)$ km/s, respectively, as in \citet{Crossfield2014}.
@@
 The right panel of Figure~\ref{fig:luhman16b:maps} shows our principal result: the inferred solution for the surface brightness map of Luhman 16B; compare to the right panel, showing the solution inferred by \citet{Crossfield2014}.
-Broadly speaking, the two surface maps agree rather well: we infer the same circumpolar bright spot, of about the same size and at roughly the same phase, as in the earlier work.
+Broadly speaking, the two surface maps agree rather well: we infer the same circumpolar bright spot, of about the same size and at roughly the same phase, although the exact latitude is different.
 We also infer a similar dark feature on the ``back'' side of the object (visible near the sub-observer point at $t = 2.4$ hours).
 Bright equatorial regions also broadly match between both solutions.
-There are some important differences, such as the contrast of the dark feature seen at $t = 0.0$ hours and the behavior of the $t = 2.4$ hour dark region beyond $60^\circ$ of the visible pole.
-In general, we find that different choices for our priors---in particular the regularization on the pixels, the prior on the limb darkening coefficient, and the value of the inclination of the star---result in maps that differ substantially.
+There are some important differences, such as the behavior of the $t = 2.4$ hour dark region beyond $60^\circ$ of the visible pole.
+In general, we find that different choices for our priors---in particular the regularization on the pixels and the template spectrum, the prior on the limb darkening coefficient, and the value of the inclination of the star---result in maps that differ somewhat.
 We do, however, agree with \citet{Crossfield2014} in that the polar bright spot is the most robust of the inferred features, followed by the bottom portion of the dark spot seen at $t = 2.4$ hours.
 Once again, since this is simply an \emph{optimization}, we are unable to place reliable uncertainties on our solutions.
-These require a sampling scheme like MCMC (\S\ref{sec:discussion:mcmc}).
+These require a sampling scheme like MCMC (\S\ref{sec:discussion:priors}).
 
@@
 Despite the fact that we obtained a qualitatively similar surface map for Luhman 16B (Figure~\ref{fig:luhman16b:maps}), there are several aspects to our approach that could be improved in future work.
+%
 First, we did not vary the inclination, but instead kept it fixed at the fiducial value $i = 70^\circ$ used in \citet{Crossfield2014}. 
 The authors of that study argued that the SNR of the dataset was too low to constrain the inclination, and that their surface maps did not qualitatively change by varying the inclination between $60^\circ$ and $90^\circ$, the range consistent with the joint knowledge of the rotation period and $v\sin i$.
-\xxx{...}
-
-We didn't account for finite exposure time.
-We didn't properly model instrumental broadening.
-We didn't do MCMC.
-We didn't vary the inclination.
-We didn't use maximum entropy regularization.
-But we solved for a whopping 4,000 parameters in under 3 minutes.
-We used the full spectrum.
-\xxx{...}
-
-Concerning our SPOT maps: a gaussian prior with unit mean is a pretty bad prior for the spectrum.
-In a more realistic scenario, we'd know a lot more information about the spectrum---such as where the lines are and some estimate of their shapes and depths---so the fidelity of our maps would be higher.
-This is what we did in the Luhman 16B case, and it works well.
-\xxx{...}
-
-\subsection{Priors and regularization}
+We find a similar result, but we note that the likelihood of the solution improves marginally when we allow the inclination to vary.
+A posterior inference scheme may thus be able to place stronger constraints on the value of $i$.
+%
+Second, neither our study nor that of \citet{Crossfield2014} accounted for the finite exposure time of the observations; given that each of the 14 spectra were collected over 20 minutes, the object rotates through $\frac{20\,\mathrm{min}}{4.9\,\mathrm{hr}}\times 360^\circ \approx 24^\circ$ during each exposure.
+Nevertheless, this is comparable to the limiting resolution of our $l_\mathrm{max} = 10$ spherical harmonic expansion (equal to about $180^\circ / l_\mathrm{max} = 18^\circ$), so it is unlikely to substantially change our results.
+%
+Third, as in \citet{Crossfield2014}, we accounted for instrumental broadening in the template spectrum; in other words, the spectrum shown in Figure~\ref{fig:luhman16b:template_spectra}, the input into our Doppler imaging code, includes broadening due to the finite spectral resolution of CRIRES.
+A better approach is to compute the Doppler-broadened spectrum based on the true rest frame spectrum and \emph{then} apply instrumental broadening (i.e., the order in which events take place in reality).
+%
+Finally, and most importantly, our results (like those of \citet{Crossfield2014}) are just a point estimate.
+While the main features inferred in the map---the polar bright spot and the dark spot on the back side of the object---appear to be robust to changes in our priors, we are unable to quantify our confidence in the map solution.
+%
+Doing so is straightforward with the \starry implementation of our algorithm, but we defer it to future work.
+
+\subsection{Regularization, priors, and posteriors}
 \label{sec:discussion:priors}
-Discuss: how to choose priors. Can use cross-validation to choose best regularization strength. In general, a positivity prior on the pixels is preferred.
-\xxx{...}
-
-\subsection{Posterior sampling}
-\label{sec:discussion:mcmc}
-
-Discuss the case where the inclination/period/velocity is unknown, such as the case with Luhman 16B.
+%
+\subsubsection{Gaussian priors}
+\label{sec:discussion:priors:gaussian}
+%
+In \S\ref{sec:spotstar} we took advantage of the bilinear nature of the problem to compute the uncertainty (\S\ref{sec:spot_y1}) and lower bounds on the uncertainty (\S\ref{sec:spot_y1b} and \S\ref{sec:spot_y1bs}) of the surface map solution.
+In particular, we found that the posterior uncertainty on the map ranges from about one percent at the north (visible) pole of the star to upwards of 10 percent at the south (hidden) pole (see Figures~\ref{fig:spot_infer_y}--\ref{fig:spot_infer_ybs}).
+It is important to keep in mind that these values are entirely dependent on our choice of prior (namely, a zero-mean Gaussian prior on the spherical harmonic coefficients with constant variance equal to $10^{-4}$).
+In particular, the value of the posterior uncertainty close to the south pole of the star---which is never in view, and whose true intensity cannot be constrained from the data---is determined exclusively from the prior variance we chose above (via Equation~\ref{eq:spotstar:uncert}).
+Its value is therefore as arbitrary as our choice of prior.%
+\footnote{While the exact \emph{value} of the posterior variance scales with the prior variance, the \emph{ratio} between the uncertainty in the north and the south does not. 
+The gradient seen in the uncertainty maps of Figures~\ref{fig:spot_infer_y}--\ref{fig:spot_infer_ybs} \emph{is} therefore meaningful, as it directly encodes the spatial distribution of the information content of the data.}
+In \S\ref{sec:spotstar} we chose a variance of $10^{-4}$ because we had access to the true maps and found, via trial and error, that this value yielded a good balance between underfitting and overfitting the synthetic data.
+In a realistic application, however, we could not do this, so we must naturally wonder: how should we go about choosing the prior variance in a principled way?
+
+There are (at least) two general approaches. 
+The first, and most Bayesian, is to choose priors that truly encode our prior knowledge of the system. 
+Absent prior observations of the system, these priors usually come from physics, such as our knowledge of the typical stellar photospheric temperatures or our understanding of the kinds of inhomogeneities we would expect on their surfaces (dark spots on stars, or patchy clouds on brown dwarfs).
+The most straightforward way to encode this information in our priors is to recognize that the prior variance on a spherical harmonic vector is closely related to a prior on its angular power spectrum \citep[see, e.g.,][]{Baldi2006,Wandelt2012}.
+In particular, our choice for prior covariance in \S\ref{sec:spotstar}, namely $\boldsymbol{\Lambda}_\bvec{y} = 10^{-4}\bvec{I}$, implies an isotropic, flat angular power spectrum prior on our surface maps with power equal to $10^{-4}$ in each spherical harmonic degree.
+Increasing this value will in general lead to solutions with more structure on all scales; decreasing it will favor more homogeneous maps.
+This may be an acceptable prior if truly nothing is known about the typical angular scale of features on the surface, but this is seldom the case.
+Both observations of the Sun and magnetohydrodynamic simulations of stellar magnetic fields give us prior constraints on the typical scales of starspots \xxx{(cite me)}, and climate models of brown dwarfs tell us about typical sizes of clouds and other atmospheric features \citep[e.g.,][]{Tan2019,Tan2020,Tan2021a,Tan2021b}.
+These can be encoded into our Gaussian prior by choosing a prior variance that scales with spherical harmonic degree:
+%
+\begin{align}
+    \boldsymbol{\Lambda}_\bvec{y} = 
+    \begin{pmatrix}
+        \sigma_0^2 & & & & & & & & & \\[-0.35em]
+        & \sigma_1^2 & & & & & & & & \\[-0.35em]
+        & & \sigma_1^2 & & & & & & & \\[-0.35em]
+        & & & \sigma_1^2 & & & & & & \\[-0.35em]
+        & & & & \sigma_2^2 & & & & & \\[-0.35em]
+        & & & & & \sigma_2^2 & & & & \\[-0.35em]
+        & & & & & & \sigma_2^2 & & & \\[-0.35em]
+        & & & & & & & \sigma_2^2 & & \\[-0.35em]
+        & & & & & & & & \sigma_2^2 & \\[-0.35em]
+        & & & & & & & & & \ddots
+    \end{pmatrix}
+    \quad,
+\end{align}
+%
+where the variance at each degree is parametrized as, e.g.,
+%
+\begin{align}
+    \sigma_l^2(\alpha, \lambda, \tau) = \alpha^2 \exp\left(-\frac{(l - \lambda)^2}{2\tau^2}\right)
+    \quad,
+\end{align}
+%
+where $\lambda$ is the typical spherical harmonic degree of features, $\alpha^2$ is the prior variance at that degree, and $\tau$ controls the uncertainty in $\lambda$.
+These hyperparameters can be either imposed or even \emph{learned} from the data; see below.
+
+Sometimes, however, we may have even more information to encode in our priors, such as the typical \emph{latitude} of the features.
+This might be the case for Solar-like or low mass stars, which have specific active latitudes at which spots form.
+An isotropic prior of the form discussed above cannot encode this, but a dense covariance matrix (with structure in the off-diagonal elements) \emph{can}.
+
+\xxx{Can use cross-validation to choose best regularization strength.
+In general, a positivity prior on the pixels is preferred.}
+
+\xxx{Discuss the case where the inclination/period/velocity is unknown, such as the case with Luhman 16B.
 The problem is not linear in these variables, so we need MCMC. 
 But our model is differentiable, so we can easily use HMC. 
-Discuss.
-\xxx{...}
+Discuss.}
 

### 2021-10-03 src/ms.tex
more text

@@
 %
-Doing so is straightforward with the \starry implementation of our algorithm, but we defer it to future work.
+Doing so with gradient-based posterior sampling methods is straightforward with the \starry implementation of our algorithm, but we defer it to future work.
 
@@
 %
+\subsubsection{The need for good priors}
+\label{sec:discussion:priors:need}
+%
+\xxx{
+    Light curve inversion is super not well-posed. 
+    Doppler imaging is better, but there are still degeneracies. 
+    See \citet{Luger2021a} \citep[see also][]{Basri2020}. 
+    It's therefore important to have a good prior to break these degeneracies.
+}
+
 \subsubsection{Gaussian priors}
@@
 
-There are (at least) two general approaches. 
-The first, and most Bayesian, is to choose priors that truly encode our prior knowledge of the system. 
+The Bayesian approach to this is to choose priors that truly encode our prior knowledge of the system. 
 Absent prior observations of the system, these priors usually come from physics, such as our knowledge of the typical stellar photospheric temperatures or our understanding of the kinds of inhomogeneities we would expect on their surfaces (dark spots on stars, or patchy clouds on brown dwarfs).
@@
     \begin{pmatrix}
-        \sigma_0^2 & & & & & & & & & \\[-0.35em]
-        & \sigma_1^2 & & & & & & & & \\[-0.35em]
-        & & \sigma_1^2 & & & & & & & \\[-0.35em]
-        & & & \sigma_1^2 & & & & & & \\[-0.35em]
-        & & & & \sigma_2^2 & & & & & \\[-0.35em]
-        & & & & & \sigma_2^2 & & & & \\[-0.35em]
-        & & & & & & \sigma_2^2 & & & \\[-0.35em]
-        & & & & & & & \sigma_2^2 & & \\[-0.35em]
-        & & & & & & & & \sigma_2^2 & \\[-0.35em]
+        \sigma_0^2 & & & & & & & & & \\[-0.5em]
+        & \sigma_1^2 & & & & & & & & \\[-0.5em]
+        & & \sigma_1^2 & & & & & & & \\[-0.5em]
+        & & & \sigma_1^2 & & & & & & \\[-0.5em]
+        & & & & \sigma_2^2 & & & & & \\[-0.5em]
+        & & & & & \sigma_2^2 & & & & \\[-0.5em]
+        & & & & & & \sigma_2^2 & & & \\[-0.5em]
+        & & & & & & & \sigma_2^2 & & \\[-0.5em]
+        & & & & & & & & \sigma_2^2 & \\[-0.5em]
         & & & & & & & & & \ddots
@@
 \begin{align}
-    \sigma_l^2(\alpha, \lambda, \tau) = \alpha^2 \exp\left(-\frac{(l - \lambda)^2}{2\tau^2}\right)
+    \sigma_l^2(\alpha, \lambda, \tau) = \sigma_\lambda^2 \exp\left(-\frac{(l - \lambda)^2}{2\tau^2}\right)
     \quad,
@@
 %
-where $\lambda$ is the typical spherical harmonic degree of features, $\alpha^2$ is the prior variance at that degree, and $\tau$ controls the uncertainty in $\lambda$.
-These hyperparameters can be either imposed or even \emph{learned} from the data; see below.
-
-Sometimes, however, we may have even more information to encode in our priors, such as the typical \emph{latitude} of the features.
-This might be the case for Solar-like or low mass stars, which have specific active latitudes at which spots form.
+where $\lambda$ is the typical spherical harmonic degree of features, $\sigma_\lambda^2$ is the prior variance at that degree, and $\tau$ controls the uncertainty in $\lambda$.
+These hyperparameters can be either imposed or even \emph{learned} from the data; see \S\ref{sec:discussion:priors:mcmc}.
+
+Sometimes, however, we may have even more information to encode in our priors, such as the typical \emph{location} of the features. 
+This might be the case for solar-like or lower mass stars, which have specific active latitudes at which spots form. 
 An isotropic prior of the form discussed above cannot encode this, but a dense covariance matrix (with structure in the off-diagonal elements) \emph{can}. 
-
-\xxx{Can use cross-validation to choose best regularization strength.
-In general, a positivity prior on the pixels is preferred.}
-
-\xxx{Discuss the case where the inclination/period/velocity is unknown, such as the case with Luhman 16B.
+\citet{Luger2021b} showed that it is possible to encode properties such as the distribution of spot latitudes, spot contrasts, and spot sizes into the prior covariance on the spherical harmonic coefficients; see \citet{Luger2021d} for an efficient implementation of this.
+Priors of this form can, once again, be imposed (if prior knowledge of the active latitudes or spot properties is available) or learned from the data by sampling over the corresponding hyperpriors. 
+We discuss this in more detail in \S\ref{sec:discussion:priors:mcmc} below.
+
+\subsubsection{Cross-validation}
+\label{sec:discussion:priors:crossval}
+%
+The approach discussed above for choosing one's priors is distinctly Bayesian.
+Alternatively, one may choose a data-driven approach: to learn the optimal value of the priors from the data itself.
+One common approach to this is \emph{cross-validation}, in which one's prior is optimized to yield the best predictive power for the data.
+Typically, cross-validation consists of choosing a specific value for the prior, masking one (``leave-one-out-cross-validation'') or several (``leave-p-out-cross-validation'') data points, optimizing the parameters of the model given this smaller dataset, then using the optimized model to predict the values of the missing data \xxx{(cite me)}.
+The optimal value of the prior is then chosen as the one with the highest predictive power, i.e., the smallest loss when fitting the missing data points \citep[for an example of this, see \S 3.7 in][]{Luger2018}.
+
+In this context, the prior is usually referred to as a ``regularization'' term, since this procedure is not exactly Bayesian. 
+Specifically, it regularizes the model to ensure a balance between underfitting (the model doesn't fit the data well) and overfitting (the model fits the data so well that it's also fitting the noise, leading to spurious results).
+In addition to helping one choose the value for (say) the prior covariance on the surface map, cross-validation can be used to optimize most of the numerical choices one makes when fitting a dataset, such as the degree $l_\mathrm{max}$ of the spherical harmonic expansion (or, in a discrete basis, the number of pixels in the surface grid) and the number of map components (\S\ref{sec:twospec}).
+
+\subsubsection{Other priors}
+\label{sec:discussion:priors:nongaussian}
+
+While we used Gaussian priors in most of our examples (\S\ref{sec:spotstar}), other kinds of priors might make more sense in different contexts. 
+In particular, in \S\ref{sec:luhman16b} we enforced a uniform prior in the range $[0, 1]$ on the pixel intensities. 
+This encodes our seemingly trivial but surprisingly restrictive \citep[see][]{Fienup1982} belief that stellar intensities must be non-negative, which a Gaussian prior cannot do.
+Priors like this one break the analyticity of the MAP solution (\S\ref{sec:inverse}), but they can be especially important in the limit that the data is not sufficiently constraining.
+Traditionally, many Doppler imaging studies impose an additional \emph{maximum entropy} constraint \citep{Vogt1987}, whose objective is to ensure a similar balance between underfitting and overfitting as discussed above.
+These can also easily be incorporated into our formalism, although we recommend using a method such as cross-validation to choose the optimal regularization strength in this context.
+
+\subsubsection{Posterior sampling}
+\label{sec:discussion:priors:mcmc}
+
+\xxx{
+    Discuss the case where the inclination/period/velocity is unknown, such as the case with Luhman 16B.
     The problem is not linear in these variables, so we need MCMC. 
     But our model is differentiable, so we can easily use HMC. 
-Discuss.}
+    Within HMC, we can learn hyperpriors and marginalize over the unknowns.
+}
 
@@
 
+\xxx{
     We are not addressing differential rotation and convective blueshift.
@@
     We will tackle this in the next paper.
-\xxx{...}
-
+}
+
+\xxx{
     The instrumental profile is another Toeplitz matrix that can be dotted into Equation~(\ref{eq:linear:f}).
-\xxx{...}
-
+}
+
+\xxx{
     We are always integrating over the entire disk of the star.
     Can integrate over the unocculted disk during an occultation (should actually be pretty trivial) so this can be used for Doppler tomography once I have some time to work it out!
-\xxx{...}
-
+}
+
+\xxx{
     Telluric lines could be learned from the data as in \citet{Bedell2019}.
-\xxx{...}
+}
 

### 2021-10-03 src/ms.tex
look, more text

@@
 Indeed, the uncertainties shown in the figure are conditioned on our estimate of the baseline, so they are actually a strict \emph{lower bound} on the map uncertainty.
-In order to constrain the true uncertainty on the solution to this bilinear problem, we must resort to approximate sampling methods such as MCMC. 
+In order to constrain the true uncertainty on the solution to this bilinear problem, we must resort to approximate sampling methods such as Markov Chain Monte Carlo (MCMC). 
 We discuss this further in \S\ref{sec:discussion:priors}.
@@
 %
-\xxx{
-    Light curve inversion is super not well-posed. 
-    Doppler imaging is better, but there are still degeneracies. 
-    See \citet{Luger2021a} \citep[see also][]{Basri2020}. 
-    It's therefore important to have a good prior to break these degeneracies.
-}
+Inferring surface maps from unresolved astronomical observations is a hard problem.
+It is ``hard'' in the usual sense, requiring the development of complicated algorithms and the evaluation of computationally expensive models; but it is also ``hard'' in the sense that quite often the true answer is \emph{unknowable} because the data simply do not contain sufficient information about it.
+This is especially the case in photometric studies, where one might seek to infer the distribution of spots on the surface of a star from its rotational light curve alone.
+Recently, \citet{Luger2021a} showed that this problem is extremely ill-posed: only a very small fraction of the information about the two-dimensional intensity distribution on the stellar surface is encoded in the light curve \citep[see also][]{Basri2020}.
+Even at infinite SNR, there exist an infinite number of solutions to the inverse problem, most of which look nothing alike.
+In a photometric study, the \emph{only} way to obtain a unique solution is to supplement the dataset with external information, usually in the form of restrictive assumptions or explicit priors on the quantities of interest.
+Most of the information in the solution to a light curve inversion problem comes from these prior assumptions, so it is extremely important to get them right.
+
+In the case of Doppler imaging datasets, the problem is much more well-posed because of the availability of an entire new dimension of information (wavelength). 
+In the limit of infinite SNR, spectral resolution, and temporal sampling, and if the rest frame spectrum is known exactly, in many cases there \emph{are} unique solutions to the visible portion of the stellar surface\footnote{Recall that, except in the pathological case where $i = 90^\circ$, there is always a region on the ``back'' side of the star that is never in view at any phase.
+No amount of statistical or algorithmic cleverness can ever tell us what that region looks like!}.
+In this limit, the data is sufficiently informative and changing one's prior does not substantially change the inferred surface map.
+This is approximately the case in \S\ref{sec:spot_y1}, in which we inferred the true surface map given a very high SNR dataset and perfect knowledge of the rest frame spectrum (see Figure~\ref{fig:spot_infer_y}).
+However, it is not the case in many of the other examples in that section, particularly when the rest frame spectrum is not known exactly and when the SNR of the dataset is finite.
+In those cases, good solutions to the surface map (ones in which the \texttt{SPOT} feature is clearly legible in the inferred map) can be obtained only under certain choices of our priors (or the strength of the regularization term).
+In the sections below we discuss how to choose these priors in a principled way.
 
@@
 \label{sec:discussion:priors:mcmc}
+%
+In the limit of finite SNR, and when things like the true stellar spectrum, the stellar inclination, and the limb darkening profile are not well known (which is usually the case in Doppler imaging studies!), it is important to recognize the limitation of point estimates like those obtained in this work.
+The maps of Luhman 16B presented in Figure~\ref{fig:luhman16b:maps}, for instance, are just that: point estimates that carry no sense of the uncertainty associated with any of those features.
+Given the low SNR of the dataset (Figure~\ref{fig:luhman16b:data_model}), the unknown inclination of the star, and the uncertainty in parameters like the rotation period, $v\sin i$, and the limb darkening profile, the maps shown in Figure~\ref{fig:luhman16b:maps} are almost certainly \emph{not} what Luhman 16B actually looks like in reality.
+The fact that we obtained a solution that is qualitatively similar to that of \citet{Crossfield2014} is encouraging, but it is not sufficient.
+Doppler imaging studies are notorious at producing features that are artificially elongated in latitude, just like the dark spot seen in the figure \xxx{(cite me)}.
+The Doppler imaging method is also less sensitive to azimuthally symmetric features, like the zonal bands that may be present on brown dwarfs as on Jupiter.
+Effects like these can bias the point estimates obtained in Doppler imaging studies, but they \emph{can} be captured if one fully propagates uncertainties to the final result.
+This requires computing the posterior distribution of the model parameters (including the parametrization of the surface map), which is absolutely critical when one wishes to \emph{interpret} a Doppler map.
+
+In some restricted cases, it is possible to obtain the full surface map posterior analytically (\S\ref{sec:inverse}), but only when all priors are Gaussian and the inclination, limb darkening profile, and template spectrum are known exactly.
+In all other cases, one must compute an approximation to the posterior distribution over all these quantities numerically, such as with MCMC.
 
 \xxx{
-    Discuss the case where the inclination/period/velocity is unknown, such as the case with Luhman 16B.
-    The problem is not linear in these variables, so we need MCMC. 
-    But our model is differentiable, so we can easily use HMC. 
+    Our model is differentiable, so we can easily use HMC. 
     Within HMC, we can learn hyperpriors and marginalize over the unknowns.
+    Stress that it is NOT correct to infer things like active latitudes, differential rotation, etc.
+from point estimates obtained with Doppler imaging.
+Those will always be biased.
+You have to infer that stuff probabilistically!
 }
@@
 
-\xxx{
-    We are not addressing differential rotation and convective blueshift.
-    These make the integral in Equation~(\ref{eq:deconv:kT}) very difficult to solve. 
-    We will tackle this in the next paper.
-}
-
-\xxx{
-    The instrumental profile is another Toeplitz matrix that can be dotted into Equation~(\ref{eq:linear:f}).
-}
-
-\xxx{
-    We are always integrating over the entire disk of the star.
-    Can integrate over the unocculted disk during an occultation (should actually be pretty trivial) so this can be used for Doppler tomography once I have some time to work it out!
-}
-
-\xxx{
-    Telluric lines could be learned from the data as in \citet{Bedell2019}.
-}
+There are a few important limitations of the algorithm presented here and its implementation in \starry that we will address in future work.
+First, we do not currently address the effects of differential rotation and convective blueshift.
+Both are straightforward to account for by modifying the path $\mathcal{C}(\lnlam,\bvec{x})$ of the line integral in Equation~(\ref{eq:deconv:kT}) to correspond to the isovelocity lines in the velocity field accounting for these two effects.
+Under the common assumption of linear differential rotation, in which the shear is proportional to the square of the sine of the latitude, the velocity field may be written exactly as a cubic polynomial in the Cartesian coordinates of the stellar surface \citep{Short2018}, therefore admitting an exact representation in terms of an $l_\mathrm{max} = 3$ spherical harmonic expansion\footnote{\url{https://starry.readthedocs.io/en/latest/notebooks/RVDerivation}}.
+Similarly, the effect of convective blueshift on the velocity field can be modeled with a low degree spherical harmonic expansion consisting only of radial ($m = 0$) modes.
+In the Appendix, we showed that in the absence of these effects, the curves $\mathcal{C}(\lnlam,\bvec{x})$ are straight lines, so the line integral in Equation~(\ref{eq:deconv:kT}) is trivial to solve.
+In the presence of differential rotation and convective blueshift, these curves become polynomials, making the integration trickier.
+While we were unable to find simple closed-form expressions for the resulting line integrals, they may still exist; we will investigate this in future work.
+Even if a closed form solution is unavailable, it is likely still possible to efficiently evaluate the integrals numerically.
+
+Another effect we do not presently model is stellar oblateness.
+Many of the Doppler imaging targets are massive stars, which tend to be fast-rotating and therefore oblate.
+We recently expanded the \starry framework to model stellar oblateness \citet{Dholakia2021}, and will similarly adapt our Doppler imaging framework in an upcoming paper. 
+In the absence of differential rotation and convective blueshift, oblateness can be accounted for by simply weighting the integration limits in Equation~(\ref{eq:appendix:kT}) by the semi-minor axis of the elliptical boundary of the star in projection.
+Accounting for those effects may require numerical integration, as discussed above.
+
+In a similar vein, our present model involves an integration over the entire stellar disk. 
+This is the desired approach in Doppler imaging studies, but does apply in the context of Doppler \emph{tomography} \citep[e.g.,][]{Johnson2017}, in which the star is observed during a transit of an orbiting planet to infer, e.g., the degree of misalignment between the planet's orbit and the stellar spin axis.
+Our formalism can be adapted to Doppler tomography by changing the limits of integration in Equation~(\ref{eq:appendix:kT}) to exclude the region occulted by the planet; we will also investigate this in upcoming work.
+
+Regarding systematic effects, we do not explicitly account for instrumental broadening. 
+The observed spectrum is a convolution of the Doppler-shifted, disk-integrated stellar spectrum (whose model our algorithm calculates) with the point spread function (PSF) of the spectograph.
+This convolution can be modeled as a dot product of a Toeplitz matrix with the Doppler design matrix $\bvec{D}$, much in the same way as Equation~(\ref{eq:linear:convolution_def}).
+
+Finally, our formalism assumes the data has been corrected for telluric contamination. 
+This is typically done by removing a telluric model (based on a template spectrum) from the data in a pre-processing step \citep[as in][]{Crossfield2014}, but in the data-driven approach of this paper, they could also be learned from the data, similar to the approach in \citet{Bedell2019}.
+We will investigate this in future work.
 

### 2021-10-04 src/ms.tex
finished main body

@@
 Returning to our point about priors, note that all of the entries of $\alm$ are the product of two independent random variables. 
-Since the product of two random variables is generally non-Gaussian, even when the variables themselves are Gaussian%
+Since the product of two random variables is generally non-Gaussian, even when the variables themselves are Gaussian,%
 \footnote{see, e.g., \url{http://mathworld.wolfram.com/NormalProductDistribution.html}}%
-, so too is the prior on $\alm$. 
+so too is the prior on $\alm$. 
 This point makes Equation~(\ref{eq:inverse:ahat}) tricky to use in practice, since a multivariate Gaussian is not generally the most suitable prior for $\alm$.
@@
 %
-\subsubsection{The need for good priors}
-\label{sec:discussion:priors:need}
+%\subsubsection{The need for good priors}
+%\label{sec:discussion:priors:need}
 %
@@
 In the case of Doppler imaging datasets, the problem is much more well-posed because of the availability of an entire new dimension of information (wavelength). 
-In the limit of infinite SNR, spectral resolution, and temporal sampling, and if the rest frame spectrum is known exactly, in many cases there \emph{are} unique solutions to the visible portion of the stellar surface\footnote{Recall that, except in the pathological case where $i = 90^\circ$, there is always a region on the ``back'' side of the star that is never in view at any phase.
-No amount of statistical or algorithmic cleverness can ever tell us what that region looks like!}.
+In the limit of infinite SNR, spectral resolution, and temporal sampling, and if the rest frame spectrum is known exactly, in many cases there \emph{are} unique solutions to the visible portion of the stellar surface.%
+\footnote{
+    Recall that, except in the pathological case where $i = 90^\circ$, there is always a region on the ``back'' side of the star that is never in view at any phase. 
+    No amount of statistical or algorithmic cleverness can ever tell us what that region looks like!%
+}%
 In this limit, the data is sufficiently informative and changing one's prior does not substantially change the inferred surface map.
@@
 \begin{align}
+    \label{eq:powerspec}
     \sigma_l^2(\alpha, \lambda, \tau) = \sigma_\lambda^2 \exp\left(-\frac{(l - \lambda)^2}{2\tau^2}\right)
@@
 
-In some restricted cases, it is possible to obtain the full surface map posterior analytically (\S\ref{sec:inverse}), but only when all priors are Gaussian and the inclination, limb darkening profile, and template spectrum are known exactly.
+In all but the simplest cases, maximum likelihood estimators are typically biased estimators of the true parameters \citep[e.g.,][]{Lehman1998}, meaning point estimates like those shown in Figure~\ref{fig:luhman16b:maps}, as well as in many other Doppler imaging studies, are also biased.
+If the goal of a study is \emph{only} to produce a map of the stellar surface, this may not be too much of an issue, especially because it is generally understood that Doppler maps are subject to artifacts like latitudinal elongation and suppression of azimuthally-symmetric features like bands, as mentioned above.
+Some of the features in Figure~\ref{fig:luhman16b:maps}, for instance, are likely to be real, such as the bright polar spot and the dark spot on the back side of the object; but their exact properties are uncertain, and many of the other features in the maps may be spurious.
+However, generating a surface map is often \emph{not} the ultimate end goal of Doppler imaging studies.
+Rather, we are usually interested in a more fundamental question: what does our inferred map tell us about the star's properties, or even about stellar physics in general?
+And therein lies the problem: as soon as we attempt to interpret the maps we've generated in terms of metadata such as the typical contrast of the star spots, their typical latitudes, or  the rate of differential rotation (based on comparing Doppler imaging maps taken at different epochs), we are subject to substantial bias due to the point estimate problem \citep[for an example of this same problem in the context of inferring the exoplanet eccentricity distribution, see][]{Hogg2010}.
+
+For this reason, it is crucial to treat Doppler imaging as a posterior inference problem, when at all possible.
+In some restricted cases, we showed that is possible to obtain the full surface map posterior analytically (\S\ref{sec:inverse}), but only when all priors are Gaussian and the inclination, limb darkening profile, and template spectrum are known exactly.
 In all other cases, one must compute an approximation to the posterior distribution over all these quantities numerically, such as with MCMC.
-
-\xxx{
-    Our model is differentiable, so we can easily use HMC. 
-    Within HMC, we can learn hyperpriors and marginalize over the unknowns.
-    Stress that it is NOT correct to infer things like active latitudes, differential rotation, etc.
-from point estimates obtained with Doppler imaging.
-Those will always be biased.
-You have to infer that stuff probabilistically!
-}
+This is typically a computationally expensive problem, given the intricate degeneracies at play (which makes posterior sampling difficult), but also the sheer number of parameters, as we must sample over all the parameters representing our surface map (typically on the order of several hundred).
+When the input spectrum is unknown, the dimension of our problem can easily exceed a few thousand (\S\ref{sec:luhman16b}).
+
+Fortunately, our model is computationally efficient to evaluate and, given its analyticity, trivial to differentiate using an autodifferentiation scheme (see \S\ref{sec:starry}).
+It can therefore be used out-of-the-box within gradient-based sampling schemes such as \texttt{pymc3} \citep{Salvatier2016}, in particular the No-U-Turn Sampler (NUTS), a variant of Hamiltonian Monte Carlo that harnesses gradient information to greatly speed up the convergence of the MCMC chains.
+The script used to infer the MAP solution for the map of Luhman 16B (see Figure~\ref{fig:luhman16b:maps}) uses \texttt{pymc3} to perform the optimization; extending it to perform posterior inference is straightforward.
+However, doing so is beyond the scope of the present paper, given that this task is still likely to be challenging given the very large number of parameters (${\sim}4{,}000$). 
+We will therefore revisit this system in the context of posterior estimation in a future paper.
+
+One final word regarding posterior inference: given that our end goal is often to infer something about the physics of stellar atmospheres rather than exactly what they look like, posterior sampling can be employed to explicitly marginalize over all possible surface maps to directly constrain our posterior beliefs about the physics.
+An example of this is the model suggested in \S\ref{sec:discussion:priors:gaussian} above, where we express our prior covariance in terms of hyperparameters controlling the amplitude of the surface features and their typical lengthscale (Equation~\ref{eq:powerspec}) or in terms of the typical size, contrast, and latitude of spots \citep{Luger2021b,Luger2021d}.
+When the value of those hyperparameters is not known \emph{a priori}, we can include them as free variables in our model and perform MCMC to compute their marginal distribution (i.e., marginalized over everything else, including all possible surface maps that are consistent with the data).
+We can even imagine doing this in an ensemble setting under a fully hierarchical model, in which we attempt to constrain these properties from the analysis of many Doppler imaging datasets of different stars simultaneously.
+This procedure is likely computationally prohibitive, but the linearity of our model (\S\ref{sec:linear}) allows us to extend the Gaussian process formalism of \citet{Luger2021b} to Doppler imaging datasets, allowing us to marginalize over the surface maps consistent with the data \emph{analytically}.
+We will explore this point in detail in upcoming work.
 
@@
 Both are straightforward to account for by modifying the path $\mathcal{C}(\lnlam,\bvec{x})$ of the line integral in Equation~(\ref{eq:deconv:kT}) to correspond to the isovelocity lines in the velocity field accounting for these two effects.
-Under the common assumption of linear differential rotation, in which the shear is proportional to the square of the sine of the latitude, the velocity field may be written exactly as a cubic polynomial in the Cartesian coordinates of the stellar surface \citep{Short2018}, therefore admitting an exact representation in terms of an $l_\mathrm{max} = 3$ spherical harmonic expansion\footnote{\url{https://starry.readthedocs.io/en/latest/notebooks/RVDerivation}}.
+Under the common assumption of linear differential rotation, in which the shear is proportional to the square of the sine of the latitude, the velocity field may be written exactly as a cubic polynomial in the Cartesian coordinates of the stellar surface \citep{Short2018}, therefore admitting an exact representation in terms of an $l_\mathrm{max} = 3$ spherical harmonic expansion.\footnote{\url{https://starry.readthedocs.io/en/latest/notebooks/RVDerivation}}
 Similarly, the effect of convective blueshift on the velocity field can be modeled with a low degree spherical harmonic expansion consisting only of radial ($m = 0$) modes.

### 2021-10-04 src/ms.tex
finished conclusions

@@
     No amount of statistical or algorithmic cleverness can ever tell us what that region looks like!%
-}%
+}
 In this limit, the data is sufficiently informative and changing one's prior does not substantially change the inferred surface map.
@@
         \caption{%
-            Model evaluation time as a function of various parameters, for spherical harmonic degree $l_\mathrm{max} = 10$, $M = 10$ spectral epochs, $K = 200$ wavelength bins, and $v\sin i = 50$ km/s.
+            Model evaluation time in milliseconds as a function of various parameters, for spherical harmonic degree $l_\mathrm{max} = 10$, $M = 10$ spectral epochs, $K = 200$ wavelength bins, and $v\sin i = 50$ km/s.
             Thin lines correspond to individual trials; the thick lines show the median evaluation time.
@@
 
-\xxx{%
-    \begin{enumerate}
-        \item Advantages of data-driven modeling
-        \item Interpretable priors
-        \item Works on blended lines
-        \item Uses the whole spectrum
-        \item Yields uncertainties!
-        \item Probably works on slow rotators
-        \item Differentiable!
-        \item Fast!
-        \item Use in MCMC to marginalize over inclination and stuff
-        \item Advertise showyourwork for open source papers!
-        \item \citet{Crossfield2014b} and \citet{Snellen2014}: people talk seriously about making Doppler Imaging maps of directly-imaged planets like beta Pic b with the ELTs.  
-        Those will be tough measurements but could be the first real, global​ maps of any planet beyond the solar system (sorry, but eclipse-mapping just doesn't quite cut it so far...).  
-        So we need the best possible algorithms to maximize what we get our of the data.
-        \item \citep{Tan2019,Tan2020,Tan2021a,Tan2021b}: Xianyu is the main person running simulations of brown dwarf global weather patterns, and the techniques outlined in your paper will offer the best way to test those models.
-    \end{enumerate}
-}
+We have derived a novel method to infer the surface brightness maps of stars from high resolution spectroscopic timeseries data.
+Our method is based on that of \citet{Vogt1987}, but it explicitly exposes the linear dependence of the observed spectrum on both the representation of the surface map (expressed as a vector of spherical harmonic coefficients) and the template (rest frame) spectrum, making it fast, differentiable, and, in certain cases, trivially invertible.
+It also naturally extends to stellar surfaces with multiple spectral components, such as a star whose spectrum differs between spot and photosphere.
+Ours is fundamentally a data-driven approach to the problem of Doppler imaging, where one can not only impose knowledge of the template spectrum but also \emph{learn} it from the data.
+This is particularly useful in the case where reliable spectral templates are not available, such as in certain wavelength regimes or for certain objects, like the brown dwarf considered in \S\ref{sec:luhman16b}.
+Importantly, we derive a model for the \emph{entire observed spectrum}.
+Most Doppler imaging studies rely on techniques like template matching \xxx{(cite me)} or least squares deconvolution \citep[LSD;][]{Donati1997} to infer a mean spectral line shape at each epoch, which is then treated as the input to the Doppler imaging step.
+These studies usually focus on a few distinct, unblended, and well-understood spectral lines, which are transformed into a single mean profile evaluated over a relatively small number of wavelength bins.
+Our approach, however, is to model the entire observed spectrum at full resolution, including line blends and wavelength regimes where the template spectrum may be unreliable.
+This is made computationally possible given our highly optimized \texttt{Python} implementation within the \starry stellar modeling framework \citep{Luger2019}, which is openly available on GitHub with ample documentation.
+By using the entire dataset and learning the template spectrum where in regions where it is unavailable, we are able to maximize the information content of the inputs.
+Our approach therefore has potential applications to slow rotators, low signal-to-noise spectra, and spectra of objects, such as brown dwarfs and directly imaged exoplanets, whose templates are not well known \emph{a priori}.
+
+As a proof-of-concept, we qualitatively reproduced the Doppler map of the brown dwarf Luhman 16B (WISE 1049-5319B) inferred in \citet{Crossfield2014} from VLT/CRIRES observations; see Figure~\ref{fig:luhman16b:maps}.
+We also tested our model's ability to accurately infer the surface maps and rest frame spectra from synthetic high SNR spectral timeseries observations, even in the limit of minimally informative priors on both quantities.
+Finally, we showed that we can infer the spectrum within spots when it is significantly different from that of the surrounding photosphere, again in the limit of high SNR and uninformative priors.
+
+Given the linearity of our model, under certain choices of prior one can obtain the posterior distribution of surface maps analytically and in under a second for most datasets. 
+However, given the usual uncertainty on stellar properties such as the inclination angle, the equatorial velocity, and the limb darkening profile, as well as the common need for restrictive priors on the surface map, most realistic applications of Doppler imaging require the use of computationally expensive numerical methods to infer the posterior distribution of the parameters.
+For this reason, Doppler imaging is traditionally performed in an optimization setting: most studies thus far yield only point estimates of the inferred surface maps, with no formal uncertainties.
+As we argued in \S\ref{sec:discussion:priors:mcmc}, this can lead to significant biases when these maps are interpreted to infer higher-level properties of stars, such as the typical sizes and active latitudes of star spots, or the average spot coverage fraction.
+These biases are due to both the use of shrinkage priors (such as the commonly used maximum entropy constraint) and the fact that point estimates usually include spurious artifacts (like latititudinally elongated features) while suppressing certain surface modes (like azimuthally-symmetric features).
+To accurately infer spot properties from Doppler maps, one must treat the problem probabilistically, by explicitly marginalizing over unknown quantities to obtain a posterior \emph{distribution} over the quantities of interest.
+The model presented here, as well as its implementation in \starry, is easy to use in a posterior inference setting.
+In particular, our implementation harnesses the autodifferentation capabilities of the \texttt{theano} \citep{Bergstra2010} package within the \texttt{pymc3} \citep{Salvatier2016} probabilistic modeling framework, allowing for efficient posterior inference using Hamiltonian Monte Carlo (HMC) techniques.
+
+While Doppler imaging has classically been used to infer the surfaces of massive stars \xxx{(cite me)}, the study of \citet{Crossfield2014} used the method to infer the first Doppler map of a brown dwarf, which we reproduced in this work.
+Future studies could help us understand the intricate atmospheric dynamics of brown dwarfs \citep{Tan2021a,Tan2021b}, as well as the global properties of exoplanets, which may be amenable to Doppler imaging given the advent of a new generation of extremely large ground-based telescopes \citep{Crossfield2014b}.
+A likely first target will be the directly-imaged giant planet $\beta$ Pictoris b, which is only an order of magnitude dimmer than Luhman 16B; \citet{Snellen2014} showed that future observations with the planned Extremely Large Telecope (ELT) should be able to produce a global map of its surface.
+Given the expected low SNR of such observations and the considerable uncertainty in the rest-frame spectra of directly imaged exoplanets, a probabilistic Doppler imaging approach like the one developed in this work will be imperative to maximizing the scientific output of those studies.
+
+\vspace{1em}
+
+This paper was prepared using the \showyourwork open source scientific article workflow\footnote{\url{https://github.com/rodluger/showyourwork}}.
+The PDF was generated automatically from a GitHub repository\footnote{\url{https://github.com/rodluger/paparazzi}} using a frozen \texttt{conda} environment on GitHub Actions CI\footnote{\url{https://github.com/features/actions}}, ensuring that all the results are exactly reproducible and easily extensible with minimal effort from the user.
+The algorithm derived in this paper is fully implemented in the \starry \texttt{Python} package, which is installable via \texttt{pip} or directly from GitHub\footnote{\url{https://github.com/rodluger/starry}}, with ample documentation, examples, and tutorials.\footnote{\url{https://starry.readthedocs.io}}
+
+\vspace{1em}
+
+We would like to thank Eric Agol, Rachael Roettenbacher, and the Astronomical Data Group at the Center for Computational Astrophysics (CCA) for useful comments, suggestions, and insights.
+RL and LZ are supported by Flatiron Fellowships at the CCA, a division of the Simons Foundation.
 

### 2021-10-04 src/ms.tex
intro sketch

@@
 % Title
-\title{A Closed-Form Solution to the Doppler Imaging Problem}
+\title{%
+    Mapping stellar surfaces\\
+    III: A Bayesian Approach to Doppler Imaging
+}
 
@@
     %
-    %While our derivation neglects the effects of differential rotation and convective blueshift, these are straightforward to include and will be addressed in an upcoming paper, which will also extend the present formalism to the problem of Doppler tomography.
-    %
     This paper was prepared using the \texttt{showyourwork} scientific article workflow, which exposes the data, source code, and package dependencies for all of the paper's figures, allowing readers to reproduce the results in this paper exactly and with minimal effort.
@@
 
-\xxx{%
-    \noindent Introduce the problem of Doppler imaging.
-    Then cite the following papers:\\[0.5em]
-    \noindent\textbf{Misc.} \\
-    \noindent\citet{Luger2019} --- Surface modeling with spherical harmonics: \starry \\
-    \noindent\citet{Bedell2019} --- Data-driven spectral inference: \texttt{wobble} \\[0.5em]
-    %
-    \noindent\textbf{Theory} \\
-    \noindent\citet{Khokhlova1976,Goncharskii1977} --- Local line profile from observed spectrum\\
-    \noindent\citet{Vogt1983,Vogt1987} --- Seminal papers on Doppler imaging \\
-    \noindent\citet{Rice1989} ---  Another seminal paper\\
-    \noindent\citet{Deutsch1958,Deutsch1970,Falk1974} ---  Ylms + Doppler imaging\\
-    \noindent\citet{Unruh1995} --- sensitivity to line profile models\\
-    \noindent\citet{Piskunov1990} --- notes on regularization \\[0.5em]
-    %
-    \noindent\textbf{Application} \\
-    \noindent\citet{Crossfield2014} --- Global cloud map of Luhman 16B \\
-    \noindent\citet{Roettenbacher2017} --- Doppler imaging of $\sigma$ Geminorum \\
-}
+Most modern Doppler imaging studies are based on the methodology developed in \citet{Goncharskii1977} and \citet{Goncharskii1982}, and updated in \citet{Vogt1983} and \citet{Vogt1987}, who formalised the technique of forward-modeling the line shape changes due to arbitrary brightness variations rotating in and out of view.
+
+\xxx{...}
+
+The idea behind modeling the stellar surface map as a spherical harmonic expansion is not new; in fact, it dates back to at least \citet{Deutsch1958}, who used a low-degree spherical harmonic expansion to model chemical peculiarities in massive Ap stars; \citep[see also][]{Deutsch1970,Falk1974}.
+More recently, spherical harmonic expansions are used in the context of Zeeman Doppler Imaging (ZDI), whose goal is to constrain the magnetic field topology from spectropolarimetric observations.
+In particular, \citet{Donati2006} used a spherical harmonic expansion to model the magnetic topology from ZDI observations of the star $\tau$ Sco, while \citet{Kochukhov2014} employed a similar approach to map the magnetic fields of CU Virginis.
+
+\xxx{...}
+
+Several studies have recognized the importance of accurate spectral templates when attempting to infer maps using Doppler imaging, showing that errors in the templates or the presence of unresolved line blends can introduce signficant artifacts in the map solution \citep[e.g.,][]{Rice1989,Unruh1995}.
+
+\xxx{...}
+
+Attempting to learn the local (rest-frame) spectrum across the surface of the star from observed spectra is not a new idea.
+\citet{Khokhlova1976}, \citet{Goncharskii1977}, and \citet{Goncharskii1982} solved for the local line profiles, assuming that changes in the intensity across the star were small.
+\xxx{But doing everything simultaneously in a Bayesian context \emph{is}.}
+
+\xxx{...}
+
+\citet{Piskunov1990} --- notes on regularization.
+
+\xxx{...}
+
+Different solutions using Doppler imaging, photometric light curve inversion, and interferometry: \citep{Roettenbacher2017}. Need a more robust framework. Gotta be Bayesian.
+\citet{AsensioRamos2021}: importance of Doppler imaging in a Bayesian context.
+
+\xxx{...}
+
+In this paper, the third in a series dedicated to mapping stellar surfaces \citep{Luger2021a,Luger2021b}, we \xxx{...}
+
+\xxx{...}
+
+This paper is a continuation of the work in \citep{Bedell2019} and \citep{Luger2019}.
+
+\xxx{...}
 
@@
             We are able to infer both the surface map of the star (upper right) and the two component spectra (lower two panels), assuming virtually no prior knowledge of either.
-            The optimization step in this experiment ran in \timeInferTwoSpec.
+            Starting from a random initial guess for the maps and the spectra, the optimization step in this experiment ran in \timeInferTwoSpec.
         }
@@
 The fact that we obtained a solution that is qualitatively similar to that of \citet{Crossfield2014} is encouraging, but it is not sufficient.
-Doppler imaging studies are notorious at producing features that are artificially elongated in latitude, just like the dark spot seen in the figure \xxx{(cite me)}.
+Doppler imaging studies are notorious at producing features that are artificially elongated in latitude, just like the dark spot seen in the figure \citep[see, e.g.,][]{Unruh1995}.
 The Doppler imaging method is also less sensitive to azimuthally symmetric features, like the zonal bands that may be present on brown dwarfs as on Jupiter.
@@
 This procedure is likely computationally prohibitive, but the linearity of our model (\S\ref{sec:linear}) allows us to extend the Gaussian process formalism of \citet{Luger2021b} to Doppler imaging datasets, allowing us to marginalize over the surface maps consistent with the data \emph{analytically}.
-We will explore this point in detail in upcoming work.
+We will explore this point in detail in the following paper in this series.
 
@@
 
-There are a few important limitations of the algorithm presented here and its implementation in \starry that we will address in future work.
+There are a few important limitations of the algorithm presented here and its implementation in \starry that we will address in future papers in this series.
 First, we do not currently address the effects of differential rotation and convective blueshift.
@@
 A likely first target will be the directly-imaged giant planet $\beta$ Pictoris b, which is only an order of magnitude dimmer than Luhman 16B; \citet{Snellen2014} showed that future observations with the planned Extremely Large Telecope (ELT) should be able to produce a global map of its surface.
-Given the expected low SNR of such observations and the considerable uncertainty in the rest-frame spectra of directly imaged exoplanets, a probabilistic Doppler imaging approach like the one developed in this work will be imperative to maximizing the scientific output of those studies.
+Given the expected low SNR of such observations and the considerable uncertainty in the rest-frame spectra of directly imaged exoplanets, an efficient, probabilistic Doppler imaging approach like the one developed in this work will be imperative to maximizing the scientific output of those studies.
 

### 2021-10-05 src/ms.tex
gps woot

@@
     %
-    This paper was prepared using the \texttt{showyourwork} scientific article workflow, which exposes the data, source code, and package dependencies for all of the paper's figures, allowing readers to reproduce the results in this paper exactly and with minimal effort.
+    This paper was prepared using the \showyourwork scientific article workflow, which exposes the data, source code, and package dependencies for all of the paper's figures, allowing readers to reproduce the results in this paper exactly and with minimal effort.
 \end{abstract}
@@
 
-Most modern Doppler imaging studies are based on the methodology developed in \citet{Goncharskii1977} and \citet{Goncharskii1982}, and updated in \citet{Vogt1983} and \citet{Vogt1987}, who formalised the technique of forward-modeling the line shape changes due to arbitrary brightness variations rotating in and out of view.
+Most modern Doppler imaging studies are based on the methodology developed in \citet{Khokhlova1976}, \citet{Goncharskii1977}, and \citet{Goncharskii1982}, and updated in \citet{Vogt1983} and \citet{Vogt1987}.
+These studies formalised the technique of forward-modeling the line shape changes due to arbitrary brightness variations rotating in and out of view.
+The latter study, in particular, presented a now common technique for solving the inverse problem---inferring the map of the star given a spectroscopic dataset---under certain regularizing assumptions.
 
@@
 
-\citet{Piskunov1990} --- notes on regularization.
-
 \xxx{...}
@@
 
+Most studies either use maximum entropy regularization \citep{Vogt1987} or Tikhonov regularization \citep[e.g.,][]{Piskunov1990}, which typically enforce sparsity and smoothness in the solution, respectively.
+
 In this paper, the third in a series dedicated to mapping stellar surfaces \citep{Luger2021a,Luger2021b}, we \xxx{...}
@@
 This paper is a continuation of the work in \citep{Bedell2019} and \citep{Luger2019}.
+
+We present a closed-form solution.
 
@@
 In \S\ref{sec:spotstar} we took advantage of the bilinear nature of the problem to compute the uncertainty (\S\ref{sec:spot_y1}) and lower bounds on the uncertainty (\S\ref{sec:spot_y1b} and \S\ref{sec:spot_y1bs}) of the surface map solution.
-In particular, we found that the posterior uncertainty on the map ranges from about one percent at the north (visible) pole of the star to upwards of 10 percent at the south (hidden) pole (see Figures~\ref{fig:spot_infer_y}--\ref{fig:spot_infer_ybs}).
+We found that the posterior uncertainty on the map ranges from about one percent at the north (visible) pole of the star to upwards of 10 percent at the south (hidden) pole (see Figures~\ref{fig:spot_infer_y}--\ref{fig:spot_infer_ybs}).
 It is important to keep in mind that these values are entirely dependent on our choice of prior (namely, a zero-mean Gaussian prior on the spherical harmonic coefficients with constant variance equal to $10^{-4}$).
@@
 The most straightforward way to encode this information in our priors is to recognize that the prior variance on a spherical harmonic vector is closely related to a prior on its angular power spectrum \citep[see, e.g.,][]{Baldi2006,Wandelt2012}.
-In particular, our choice for prior covariance in \S\ref{sec:spotstar}, namely $\boldsymbol{\Lambda}_\bvec{y} = 10^{-4}\bvec{I}$, implies an isotropic, flat angular power spectrum prior on our surface maps with power equal to $10^{-4}$ in each spherical harmonic degree.
+Our choice for prior covariance in \S\ref{sec:spotstar}, namely $\boldsymbol{\Lambda}_\bvec{y} = 10^{-4}\bvec{I}$, implies an isotropic, flat angular power spectrum prior on our surface maps with power equal to $10^{-4}$ in each spherical harmonic degree.
 Increasing this value will in general lead to solutions with more structure on all scales; decreasing it will favor more homogeneous maps.
@@
 We can even imagine doing this in an ensemble setting under a fully hierarchical model, in which we attempt to constrain these properties from the analysis of many Doppler imaging datasets of different stars simultaneously.
-This procedure is likely computationally prohibitive, but the linearity of our model (\S\ref{sec:linear}) allows us to extend the Gaussian process formalism of \citet{Luger2021b} to Doppler imaging datasets, allowing us to marginalize over the surface maps consistent with the data \emph{analytically}.
-We will explore this point in detail in the following paper in this series.
+This procedure is likely computationally prohibitive, but the linearity of our model (\S\ref{sec:linear}) allows us to extend the Gaussian process formalism of \citet{Luger2021b} to Doppler imaging datasets, allowing us to marginalize over the surface maps consistent with the data \emph{analytically}; see \S\ref{sec:discussion:caveats} below.
 
@@
 This convolution can be modeled as a dot product of a Toeplitz matrix with the Doppler design matrix $\bvec{D}$, much in the same way as Equation~(\ref{eq:linear:convolution_def}).
-
-Finally, our formalism assumes the data has been corrected for telluric contamination. 
+In a similar vein, our formalism assumes the data has been corrected for telluric contamination. 
 This is typically done by removing a telluric model (based on a template spectrum) from the data in a pre-processing step \citep[as in][]{Crossfield2014}, but in the data-driven approach of this paper, they could also be learned from the data, similar to the approach in \citet{Bedell2019}.
 We will investigate this in future work.
+
+%
+\begin{figure}[t!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/gp.pdf}
+        \caption{%
+            Samples from a spectral-spatial-temporal Gaussian Process.
+        }
+        \label{fig:gp}
+    \end{centering}
+\end{figure}
+%
+
+Finally, an immediate extension of the work presented here is to cast the Doppler imaging problem as a Gaussian process. Figure~\ref{fig:gp}.
+\xxx{FOO BAR.}
 
@@
 This is made computationally possible given our highly optimized \texttt{Python} implementation within the \starry stellar modeling framework \citep{Luger2019}, which is openly available on GitHub with ample documentation.
-By using the entire dataset and learning the template spectrum where in regions where it is unavailable, we are able to maximize the information content of the inputs.
+By using the entire dataset and learning the template spectrum in regions where it is unavailable, we are able to maximize the information content of the inputs.
 Our approach therefore has potential applications to slow rotators, low signal-to-noise spectra, and spectra of objects, such as brown dwarfs and directly imaged exoplanets, whose templates are not well known \emph{a priori}.

### 2021-10-05 src/ms.tex
foo

@@
 
+\subsection{A Spectral-Spatial-Temporal Gaussian Process}
+\label{sec:discussion:gp}
+
 %
@@
         \caption{%
-            Samples from a spectral-spatial-temporal Gaussian Process.
+            Ten samples from a spectral-spatial-temporal Gaussian Process constructed from the algorithm presented here.
+            Each panel shows a different sample, each of which consists of ten epochs, offset vertically for visibility.
+            The rest frame spectrum is the same as in Figure~\ref{fig:spot_setup} and the star is inclined at $i = 40^\circ$ with equatorial velocity $v = 50{,}000$ km/s.
+            The star is assumed to have spots with radius $r = 15^\circ$, ten percent contrast, and active latitude $\phi = 30^\circ \pm 5^\circ$.
         }

### 2021-10-05 src/figures/gp.py

@@ -45,16 +45,23 @@ samples = np.rollaxis(samples, -1, 0)  # shape (nsamples, nt, nw)
 samples /= samples[:, :, 0].reshape(nsamples, map.nt, 1)
 
 # Plot the samples
-fig, ax = plt.subplots(1, nsamples, figsize=(12, 2), sharex=True, sharey=True)
+fig, ax = plt.subplots(2, nsamples // 2, figsize=(12, 4))
+ax = ax.flatten()
 for n in range(nsamples):
     for k in range(map.nt):
-        ax[n].plot(
-            map.wav,
-            0.03 * k + samples[n][k],
-            "k-",
-            lw=0.75,
-            alpha=0.75,
-        )
-    ax[n].set_xticklabels([])
-    ax[n].set_yticklabels([])
+        ax[n].plot(map.wav, 0.03 * k + samples[n][k], "C0-", lw=0.75)
+
+# Appearance
+N = nsamples // 2
+for n in range(nsamples):
+    if n != N:
+        ax[n].set_xticklabels([])
+        ax[n].set_yticklabels([])
+        ax[n].set_xlim(*ax[N].get_xlim())
+        ax[n].set_ylim(*ax[N].get_ylim())
+for tick in ax[N].get_xticklabels() + ax[N].get_yticklabels():
+    tick.set_fontsize(8)
+ax[N].set_xlabel(r"$\lambda$ [nm]", fontsize=10)
+ax[N].set_ylabel(r"intensity", fontsize=10)
+
 fig.savefig("gp.pdf", bbox_inches="tight")

### 2021-10-05 src/ms.tex
everything but the kitchen sink

--- 2021-10-05 src/ms.tex
@@
 This is especially useful if the typical angular scale of features on the surface of the star is known or if a Gaussian prior can be placed on it.
-Alternatively, we may compute $\boldsymbol{\Lambda}_\bvec{y}$ from the Gaussian process formalism in \citet{Luger2021b} to incorporate explicit prior information on the typical latitudes, sizes, and contrasts of spots.
+Alternatively, we may compute $\boldsymbol{\Lambda}_\bvec{y}$ from the Gaussian process (GP) formalism in \citet{Luger2021b} to incorporate explicit prior information on the typical latitudes, sizes, and contrasts of spots.
 We discuss this point further in \S\ref{sec:discussion:priors}.
@@
 %
-We further place a Gaussian process prior on the spectra to enforce smoothness, adopting a squared exponential kernel with amplitude $10^{-1}$ and lengthscale $10^{-2}$~nm.
+We further place a Gaussian process (GP) prior on the spectra to enforce smoothness, adopting a squared exponential kernel with amplitude $10^{-1}$ and lengthscale $10^{-2}$~nm.
 %
@@
 We can even imagine doing this in an ensemble setting under a fully hierarchical model, in which we attempt to constrain these properties from the analysis of many Doppler imaging datasets of different stars simultaneously.
-This procedure is likely computationally prohibitive, but the linearity of our model (\S\ref{sec:linear}) allows us to extend the Gaussian process formalism of \citet{Luger2021b} to Doppler imaging datasets, allowing us to marginalize over the surface maps consistent with the data \emph{analytically}; see \S\ref{sec:discussion:caveats} below.
+This procedure is likely computationally prohibitive, but the linearity of our model (\S\ref{sec:linear}) allows us to extend the Gaussian process formalism of \citet{Luger2021b} to Doppler imaging datasets, allowing us to marginalize over the surface maps consistent with the data \emph{analytically}; see \S\ref{sec:discussion:gp} below.
 
@@
         \caption{%
-            Samples from a spectral-spatial-temporal Gaussian Process.
+            20 samples from a spectral-spatial-temporal Gaussian process constructed from the algorithm presented here.
+            Each panel shows a different sample, each of which consists of 16 epochs, offset vertically for visibility.
+            The rest frame spectrum is the same as in Figure~\ref{fig:spot_setup} and the star is inclined at $i = 40^\circ$ with equatorial velocity $v = 50{,}000$ km/s.
+            The star is assumed to have spots with radius $r = 15^\circ$, 25 percent contrast, and active latitude $\phi = 30^\circ \pm 5^\circ$.
         }
@@
 
-Finally, an immediate extension of the work presented here is to cast the Doppler imaging problem as a Gaussian process. Figure~\ref{fig:gp}.
-\xxx{FOO BAR.}
+There is one immediate extension of the formalism developed in this work that merits a more in-depth discussion: the adaption of the Doppler imaging method into a Gaussian process (GP) for stellar spectroscopy.
+While the goal of Doppler imaging is often to infer the actual surface map of the star, sometimes the goal may be to infer higher-level statistical information, such as the active latitude of spots or their typical sizes.
+And sometimes, the goal of a spectroscopic analysis may not be to infer something about the star at all, such as in the case of radial velocity surveys of exoplanets.
+In both of these cases, one does not really care about what the \emph{actual} map of the star is irrelevant; rather, the goal is to \emph{marginalize} over all the possible stellar surfaces consistent with the data to obtain the marginal posterior of the quantities of interest, such as the active latitude or the properties of an orbiting exoplanet.
+In \S\ref{sec:discussion:priors:mcmc}, we discussed how one might perform this marginalization via MCMC sampling.
+However, thanks to the linearity of the model developed here, we can use the formalism developed in \citet{Luger2021b} to do this \emph{analytically}.
+
+\citet{Luger2021b} presented an interpretable GP for stellar photometric variability, based on the fact that it is possible to analytically compute the covariance matrix $\boldsymbol{\Lambda}_\bvec{y}$ describing the distribution of spherical harmonic coefficients characterizing a given stellar surface conditioned on certain bulk spot properties $\boldsymbol{\theta}$, such as their radius, latitude, and contrast distributions.%
+\footnote{In \citet{Luger2021b}, this covariance matrix is denoted $\boldsymbol{\Sigma}_\bvec{y}$.}
+Since the model for the (photometric) flux is linear in the spherical harmonic coefficients \citep{Luger2019}, the covariance of the GP for stellar light curves is then simply
+%
+\begin{align}
+    \boldsymbol{\Sigma}_\mathrm{photo} = \mathbf{A} \, \boldsymbol{\Lambda}_\bvec{y} (\boldsymbol{\theta}) \, \mathbf{A}^\top
+    \quad,
+\end{align}
+%
+where $\mathbf{A}$ is the design matrix that transforms from spherical harmonic coefficients to flux, which implicitly depends on the stellar inclination, rotation period, etc.
+
+Conditioned on a fixed spectrum, the Doppler imaging problem is also linear in $\bvec{y}$ (Equation~\ref{eq:inverse:fy}), so we can write the covariance of the GP for a spectroscopic timeseries dataset as
+%
+\begin{align}
+    \label{eq:discussion:gpcov}
+    \boldsymbol{\Sigma}_\mathrm{Doppler} = \mathbf{D} \, \mathbf{S} \, \boldsymbol{\Lambda}_\bvec{y} (\boldsymbol{\theta}) \, \mathbf{S}^\top \, \mathbf{D}^\top
+    \quad,
+\end{align}
+%
+where $\bvec{S}$ is given by Equation~(\ref{eq:inverse:S}) and $\bvec{D}$ is the Doppler design matrix (Equation~\ref{eq:linear:D}).
+The likelihood of the Gaussian with covariance given by Equation~(\ref{eq:discussion:gpcov}) is the probability of the observed spectra conditioned on spot hyperparameters $\boldsymbol{\theta}$, \emph{marginalized} over all possible stellar surface maps.
+Since this marginalization is done analytically, one need only sample over the parameters of interest (the components of $\boldsymbol{\theta}$, as well as the properties of the orbiting planet, in the case of a radial velocity study) in an inference problem.
+Thus, this GP formalism can reduce the dimensionality of one's model from several hundred (the number of parameters used to model the surface map) to a handful (the hyperparameters of the GP, plus the parameters of the planet model, if applicable).
+
+As an example, Figure~\ref{fig:gp} shows twenty samples from the GP described above. 
+We condition the GP on the same spectrum used in \S\ref{sec:spotstar} and on a stellar inclination $i = 40^\circ$ and equatorial velocity $v = 50{,}000$ km/s, and choose hyperparameters $\boldsymbol{\theta}$ corresponding to spots with mean radius $r = 15^\circ$, mean fractional contrast $c = 0.25$, and active latitude $\phi = 30^\circ \pm 5^\circ$.
+Each panel shows a full spectral-temporal dataset sampled from this GP, where individual spectra are vertically offset from each other for visibility.
+
+The main application of our GP, of course, will not be for drawing samples, but for doing inference. 
+In particular, we expect this GP to be useful for extreme precision radial velocity (EPRV) planet searches, which must contend with stellar variability signals that are often orders of magnitude stronger than the planetary signals of interest.
+Our GP can be used as a principled, physically-motivated way to marginalize over the stellar signal to robustly detect the Keplerian signal of an orbiting planet.
+
+The next paper in the \emph{Mapping Stellar Surfaces} series will focus on further development of this GP, including accounting for uncertainty in the spectral template, accounting for the nonlinearity introduced by the continuum normalization, marginalizing over unknowns such as the inclination and limb darkening parameters, and rigorously testing the formalism on both synthetic and real datasets.
 
@@
 
-We implement the algorithm presented here in the \starry package \citep{Luger2019,Luger2021c}, an open-source \texttt{Python} library for stellar and planetary light curve analysis. 
+We implement the Doppler imaging algorithm presented here in the \starry package \citep{Luger2019,Luger2021c}, an open-source \texttt{Python} library for stellar and planetary light curve analysis. 
 All of the figures in this paper were generated via the Doppler imaging API in \starry. 
@@
 In particular, our implementation harnesses the autodifferentation capabilities of the \texttt{theano} \citep{Bergstra2010} package within the \texttt{pymc3} \citep{Salvatier2016} probabilistic modeling framework, allowing for efficient posterior inference using Hamiltonian Monte Carlo (HMC) techniques.
+We also present a sketch of how to incorporate our model into an interpretable, physically-motivated Gaussian process (GP) formalism for stellar spectroscopic timeseries datasets, a method that is highly relevant to extreme precision radial velocity (EPRV) searches for exoplanets.
+We will explore this application in more detail in the next paper in this series.
 
@@
 
-We would like to thank Eric Agol, Rachael Roettenbacher, and the Astronomical Data Group at the Center for Computational Astrophysics (CCA) for useful comments, suggestions, and insights.
+We would like to thank Eric Agol, Christina Hedges, Rachael Roettenbacher, and the Astronomical Data Group at the Center for Computational Astrophysics (CCA) for useful comments, suggestions, and insights.
 RL and LZ are supported by Flatiron Fellowships at the CCA, a division of the Simons Foundation.

### 2021-10-05 src/figures/gp.py

@@ -4,7 +4,7 @@ import starry
 import starry_process
 
 # Number of samples to draw
-nsamples = 10
+nsamples = 20
 
 # Instantiate the Doppler map
 wav = np.linspace(642.85, 643.15, 70)
@@ -13,7 +13,7 @@ map = starry.DopplerMap(
     ydeg=15,
     nc=1,
     vsini_max=50000,
-    nt=10,
+    nt=16,
     wav=wav,
 )
 
@@ -32,7 +32,7 @@ D = map.design_matrix(fix_spectrum=True)
 # Note that in general it is more efficient to *compile* the theano
 # function (rather than call the `eval` method); see the starry-process
 # docs for details!
-sp = starry_process.StarryProcess(r=15.0, n=10.0, mu=30.0, sigma=5.0, c=0.1)
+sp = starry_process.StarryProcess(r=15.0, n=10.0, mu=30.0, sigma=5.0, c=0.25)
 np.random.seed(0)
 y = sp.sample_ylm(nsamples=nsamples).eval()
 y[:, 0] += 1  # starry processes are zero-mean; we need to offset our baseline
@@ -45,14 +45,14 @@ samples = np.rollaxis(samples, -1, 0)  # shape (nsamples, nt, nw)
 samples /= samples[:, :, 0].reshape(nsamples, map.nt, 1)
 
 # Plot the samples
-fig, ax = plt.subplots(2, nsamples // 2, figsize=(12, 4))
+fig, ax = plt.subplots(4, nsamples // 4, figsize=(12, 10))
 ax = ax.flatten()
 for n in range(nsamples):
     for k in range(map.nt):
-        ax[n].plot(map.wav, 0.03 * k + samples[n][k], "C0-", lw=0.75)
+        ax[n].plot(map.wav, 0.05 * k + samples[n][k], "C0-", lw=0.75)
 
 # Appearance
-N = nsamples // 2
+N = nsamples - nsamples // 4
 for n in range(nsamples):
     if n != N:
         ax[n].set_xticklabels([])

### 2021-10-06 src/ms.tex
the kitchen sink

@@
     %
-    We implement the model within the open-source \starry stellar modeling framework, making it fast, differentiable, and easy to use in both optimization and posterior inference settings.
+    We implement the model within the open source \starry stellar modeling framework, making it fast, differentiable, and easy to use in both optimization and posterior inference settings.
     %
@@
 
-Most modern Doppler imaging studies are based on the methodology developed in \citet{Khokhlova1976}, \citet{Goncharskii1977}, and \citet{Goncharskii1982}, and updated in \citet{Vogt1983} and \citet{Vogt1987}.
+High resolution spectra encode a vast amount of information about the structure, dynamics, and chemical composition of stars.
+Spectra of fast-rotating stars, in particular, also encode the two-dimensional brightness map of the photosphere via subtle line shape changes as inhomogeneities rotate from the blueshifted side to the redshifted side of the star.
+The process of inferring the map of a stellar ``surface'' given high resolution spectra taken at different rotational phases is known as \emph{Doppler imaging}, a technique that dates back to at least \citet{Deutsch1958}.
+Most modern Doppler imaging studies, however, are based on the methodology developed in \citet{Khokhlova1976}, \citet{Goncharskii1977}, and \citet{Goncharskii1982}, and updated in \citet{Vogt1983} and \citet{Vogt1987}.
 These studies formalised the technique of forward-modeling the line shape changes due to arbitrary brightness variations rotating in and out of view.
@@
 
-\xxx{...}
-
-The idea behind modeling the stellar surface map as a spherical harmonic expansion is not new; in fact, it dates back to at least \citet{Deutsch1958}, who used a low-degree spherical harmonic expansion to model chemical peculiarities in massive Ap stars; \citep[see also][]{Deutsch1970,Falk1974}.
-More recently, spherical harmonic expansions are used in the context of Zeeman Doppler Imaging (ZDI), whose goal is to constrain the magnetic field topology from spectropolarimetric observations.
-In particular, \citet{Donati2006} used a spherical harmonic expansion to model the magnetic topology from ZDI observations of the star $\tau$ Sco, while \citet{Kochukhov2014} employed a similar approach to map the magnetic fields of CU Virginis.
-
-\xxx{...}
-
-Several studies have recognized the importance of accurate spectral templates when attempting to infer maps using Doppler imaging, showing that errors in the templates or the presence of unresolved line blends can introduce signficant artifacts in the map solution \citep[e.g.,][]{Rice1989,Unruh1995}.
-
-\xxx{...}
-
-Attempting to learn the local (rest-frame) spectrum across the surface of the star from observed spectra is not a new idea.
-\citet{Khokhlova1976}, \citet{Goncharskii1977}, and \citet{Goncharskii1982} solved for the local line profiles, assuming that changes in the intensity across the star were small.
-\xxx{But doing everything simultaneously in a Bayesian context \emph{is}.}
-
-\xxx{...}
-
-\xxx{...}
-
-Different solutions using Doppler imaging, photometric light curve inversion, and interferometry: \citep{Roettenbacher2017}. Need a more robust framework. Gotta be Bayesian.
-\citet{AsensioRamos2021}: importance of Doppler imaging in a Bayesian context.
-
-\xxx{...}
-
-Most studies either use maximum entropy regularization \citep{Vogt1987} or Tikhonov regularization \citep[e.g.,][]{Piskunov1990}, which typically enforce sparsity and smoothness in the solution, respectively.
-
-In this paper, the third in a series dedicated to mapping stellar surfaces \citep{Luger2021a,Luger2021b}, we \xxx{...}
-
-\xxx{...}
-
-This paper is a continuation of the work in \citep{Bedell2019} and \citep{Luger2019}.
-
-We present a closed-form solution.
-
-\xxx{...}
+Since those pioneering studies several decades ago, Doppler maps have now been obtained for a variety of targets, ranging from red giant stars \citep{Roettenbacher2017} to massive main sequence stars \xxx{(cite me)} to cool dwarfs \citep{Rosen2015}.
+Recently, \citet{Crossfield2014} produced a Doppler map of Luhman 16B, a brown dwarf in the solar neighborhood.
+Future observations with extremely large telescopes may even allow one to obtain Doppler maps of directly imaged extrasolar planets \citep{Snellen2014}.
+
+As more and more stars are imaged in this way, it becomes tempting to interpret Doppler images in the broader context of stellar physics and evolution.
+For instance, one may be interested in understanding trends in the population-level magnetic properties of giant stars, or in how those properties change as a function of spectral type or stellar age.
+However, the vast majority of Doppler imaging studies produce \emph{point estimates}: that is, they usually report the maximum likelihood solution to the stellar surface map, with no formal assessment of its uncertainty.
+In all but the simplest cases, maximum likelihood estimators are biased \citep[e.g.,][]{Lehman1998}, meaning any attempt to understand these estimates in bulk is prone to significant bias \citep[see, e.g.,][]{Hogg2010}.
+This problem is compounded by four factors.
+%
+First, Doppler imaging is usually an ill-posed problem, meaning there is no unique solution to the surface map given a spectroscopic dataset.
+This issue is typically well understood \xxx{(cite me)}, and most studies circumvent this issue by employing restrictive priors to ensure the uniqueness of the solution. 
+These include maximum entropy regularization \citep{Vogt1987} and Tikhonov regularization \citep[e.g.,][]{Piskunov1990}, which typically enforce sparsity and smoothness in the solution, respectively.
+However, while useful for obtaining a maximum likelihood solution, both choices can lead to significant bias in the inferred map, as they can both suppress features and introduce spurious artifacts.
+In fact, a recent comparison of Doppler imaging, photometric light curve inversion, and interferometry revealed qualitatively diffferent maps of the the same star \citep{Roettenbacher2017}, due to the various degeneracies afflicting each method.
+%
+Second, the Doppler imaging technique is generally more sensitive to longitudinal than latitudinal variations, often leading to spurious, latititudinally elongated features in the maximum likelihood solution \citep[e.g.,][]{Unruh1995,Crossfield2014b}.
+%
+Third, the Doppler imaging technique requires the availability of accurate spectral templates for the local rest frame spectrum of the star.
+Several studies have shown that errors in these templates or the presence of unresolved line blends in the observed spectrum can introduce signficant artifacts in the map solution \citep[e.g.,][]{Rice1989,Unruh1995}.
+Moreover, changes in the local spectrum over the surface of the star (such as different line depths or the presence of different absorption lines within spots) can similarly bias the inferred map if these are not properly modeled \xxx{(cite me)}.
+While some past studies have solved for variations in the local line profiles \citep{Khokhlova1976,Goncharskii1977,Goncharskii1982}, these usually make the assumption that the intensity variation is small across the surface of the star; that is, they do not simultaneously solve for the Doppler map of the surface brightness variations.
+%
+Fourth, and finally, most Doppler imaging codes are not open source \xxx{(cite me)}, nor are the data used to produce many of the maps found in the literature, making it difficult to reproduce results and compare Doppler images of different stars on the same footing.
+
+In this paper, the third in a series dedicated to mapping stellar surfaces \citep{Luger2021a,Luger2021b}, we seek to address these issues by developing a novel algorithm for Doppler imaging.
+The various pitfalls of Doppler imaging outlined above necessitate an algorithm that is efficient enough to be used in a Bayesian posterior inference context, where one can formally address the degeneracies at play and quantify their effect on the uncertainties of the inferred stellar maps.
+They also necessitate an algorithm that is flexible, capable of learning deviations from the template or capturing spatial variations in the rest-frame spectrum.
+And most of all, they necessitate a user-friendly, well-documented, and open source implementation, which is sorely lacking the literature.
+Our algorithm addresses these various issues by building on the work of \citet{Luger2019}, who derived analytic solutions to the light curve mapping problem by expanding the stellar surface map in the spherical harmonic basis.
+While spherical harmonics are routinely used in Doppler imaging problems \citep{Deutsch1958,Deutsch1970,Falk1974,Donati2006,Kochukhov2014}, we present a new closed-form solution to the forward model for Doppler imaging when working in this basis, making our model both precise and computationally efficient.
+We also expose a fundamental linearity of the model in terms of both the surface map and the rest frame spectrum, allowing us to learn both using a fast bilinear solver.
+Finally, we implement our algorithm within the open source \starry code package with ample documentation, examples, and tutorials.\footnote{\url{https://github.com/rodluger/starry}}.
+All of the figures in this paper are also open source; clickable \GitHubIconBlue icons next to each figure link to the exact version of the \texttt{Python} script used to generate them.
+To ensure the full reproducibility of this paper, we prepared it using the \showyourwork workflow\footnote{\url{https://github.com/rodluger/showyourwork}}, which exposes the datasets, source code, and all package dependencies needed to exactly reproduce the results.
 
@@
 
-For this reason, it is crucial to treat Doppler imaging as a posterior inference problem, when at all possible.
-In some restricted cases, we showed that is possible to obtain the full surface map posterior analytically (\S\ref{sec:inverse}), but only when all priors are Gaussian and the inclination, limb darkening profile, and template spectrum are known exactly.
+For this reason, it is crucial to treat Doppler imaging as a posterior inference problem, when at all possible; see \citet{AsensioRamos2021} for recent work on a Doppler imaging model that harnesses approximate Bayesian techniques to perform posterior inference.
+In some restricted cases, we showed that is possible to obtain the full surface map posterior analytically with our method (\S\ref{sec:inverse}), but only when all priors are Gaussian and the inclination, limb darkening profile, and template spectrum are known exactly.
 In all other cases, one must compute an approximation to the posterior distribution over all these quantities numerically, such as with MCMC.
@@
 
-We implement the Doppler imaging algorithm presented here in the \starry package \citep{Luger2019,Luger2021c}, an open-source \texttt{Python} library for stellar and planetary light curve analysis. 
+We implement the Doppler imaging algorithm presented here in the \starry package \citep{Luger2019,Luger2021c}, an open source \texttt{Python} library for stellar and planetary light curve analysis. 
 All of the figures in this paper were generated via the Doppler imaging API in \starry. 

### 2021-10-06 src/ms.tex
tweaks

@@
 We also expose a fundamental linearity of the model in terms of both the surface map and the rest frame spectrum, allowing us to learn both using a fast bilinear solver.
-Finally, we implement our algorithm within the open source \starry code package with ample documentation, examples, and tutorials.\footnote{\url{https://github.com/rodluger/starry}}.
+Finally, we implement our algorithm within the open source \starry code package with ample documentation, examples, and tutorials.\footnote{\url{https://github.com/rodluger/starry}}
 All of the figures in this paper are also open source; clickable \GitHubIconBlue icons next to each figure link to the exact version of the \texttt{Python} script used to generate them.
@@
 Fortunately, our model is computationally efficient to evaluate and, given its analyticity, trivial to differentiate using an autodifferentiation scheme (see \S\ref{sec:starry}).
-It can therefore be used out-of-the-box within gradient-based sampling schemes such as \texttt{pymc3} \citep{Salvatier2016}, in particular the No-U-Turn Sampler (NUTS), a variant of Hamiltonian Monte Carlo that harnesses gradient information to greatly speed up the convergence of the MCMC chains.
+It can therefore be used out-of-the-box within gradient-based sampling schemes such as \texttt{pymc3} \citep{Salvatier2016}, in particular the No-U-Turn Sampler (NUTS), a variant of Hamiltonian Monte Carlo that harnesses gradient information to greatly speed up the convergence of the MCMC chains \citep{for a recent application of HMC in the context of spectroscopy, see}{Kawahara2021}.
 The script used to infer the MAP solution for the map of Luhman 16B (see Figure~\ref{fig:luhman16b:maps}) uses \texttt{pymc3} to perform the optimization; extending it to perform posterior inference is straightforward.

### 2021-10-11 src/ms.tex
fix citations

--- 2021-10-06 src/ms.tex
@@
 %
-\author[0000-0002-1835-1891]{Ian Crossfield}
+\author[0000-0002-1835-1891]{Ian J. M. Crossfield}
 \affil{Department~of~Physics~and~Astronomy, Kansas University, Lawrence, KS}
 %
-\author[0000-0002-3852-3590]{Lily Zhao}
+\author[0000-0002-3852-3590]{Lily L. Zhao}
 \affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
@@
 
-Since those pioneering studies several decades ago, Doppler maps have now been obtained for a variety of targets, ranging from red giant stars \citep{Roettenbacher2017} to massive main sequence stars \xxx{(cite me)} to cool dwarfs \citep{Rosen2015}.
-Recently, \citet{Crossfield2014} produced a Doppler map of Luhman 16B, a brown dwarf in the solar neighborhood.
-Future observations with extremely large telescopes may even allow one to obtain Doppler maps of directly imaged extrasolar planets \citep{Snellen2014}.
-
-As more and more stars are imaged in this way, it becomes tempting to interpret Doppler images in the broader context of stellar physics and evolution.
+Since those pioneering studies several decades ago, Doppler maps have now been obtained for a variety of targets, ranging from giant and subgiant stars \citep{Donati1999,Strassmeier1999,Roettenbacher2017} to massive main sequence and pre-main sequence stars \citep{Collier1994,Hatzes1995} to cool dwarfs \citep{Rosen2015,Zaire2021}.
+A Doppler map has even been obtained for a brown dwarf in the solar neighborhood \citep{Crossfield2014}.
+Future observations with extremely large telescopes may also allow one to obtain Doppler maps of directly imaged extrasolar planets \citep{Snellen2014,Crossfield2014b}.
+
+As more and more objects are imaged in this way, it becomes tempting to interpret Doppler images in the broader context of stellar physics and evolution.
 For instance, one may be interested in understanding trends in the population-level magnetic properties of giant stars, or in how those properties change as a function of spectral type or stellar age.
-However, the vast majority of Doppler imaging studies produce \emph{point estimates}: that is, they usually report the maximum likelihood solution to the stellar surface map, with no formal assessment of its uncertainty.
+However, the vast majority of Doppler imaging studies produce \emph{point estimates}: that is, they usually report the maximum likelihood solution for the stellar surface map, with no formal assessment of its uncertainty.
 In all but the simplest cases, maximum likelihood estimators are biased \citep[e.g.,][]{Lehman1998}, meaning any attempt to understand these estimates in bulk is prone to significant bias \citep[see, e.g.,][]{Hogg2010}.
 This problem is compounded by four factors.
-%
-First, Doppler imaging is usually an ill-posed problem, meaning there is no unique solution to the surface map given a spectroscopic dataset.
-This issue is typically well understood \xxx{(cite me)}, and most studies circumvent this issue by employing restrictive priors to ensure the uniqueness of the solution. 
+
+First, Doppler imaging is usually an ill-posed problem, meaning there is no unique solution for the surface map given a spectroscopic dataset.
+This issue is typically well understood \citep[e.g.,][]{Piskunov1990,Rice2002}, and most studies circumvent this issue by employing restrictive priors to ensure the uniqueness of the solution. 
 These include maximum entropy regularization \citep{Vogt1987} and Tikhonov regularization \citep[e.g.,][]{Piskunov1990}, which typically enforce sparsity and smoothness in the solution, respectively.
@@
 Several studies have shown that errors in these templates or the presence of unresolved line blends in the observed spectrum can introduce signficant artifacts in the map solution \citep[e.g.,][]{Rice1989,Unruh1995}.
-Moreover, changes in the local spectrum over the surface of the star (such as different line depths or the presence of different absorption lines within spots) can similarly bias the inferred map if these are not properly modeled \xxx{(cite me)}.
+Moreover, changes in the local spectrum over the surface of the star (such as different line depths or the presence of different absorption lines within spots) can similarly bias the inferred map if these are not properly modeled.
 While some past studies have solved for variations in the local line profiles \citep{Khokhlova1976,Goncharskii1977,Goncharskii1982}, these usually make the assumption that the intensity variation is small across the surface of the star; that is, they do not simultaneously solve for the Doppler map of the surface brightness variations.
 %
-Fourth, and finally, most Doppler imaging codes are not open source \xxx{(cite me)}, nor are the data used to produce many of the maps found in the literature, making it difficult to reproduce results and compare Doppler images of different stars on the same footing.
+Fourth, and finally, most Doppler imaging codes are not open source \citep[][to name a few]{Collier1997,Hackman2001,Carroll2012,Rosen2015,AsensioRamos2021},
+% DOTS, INVERS7-PD, iMAP, INVERSLSD, ??
+nor are the data used to produce many of the maps found in the literature, making it difficult to reproduce results and compare Doppler images of different stars on the same footing.
 
@@
 We also expose a fundamental linearity of the model in terms of both the surface map and the rest frame spectrum, allowing us to learn both using a fast bilinear solver.
-Finally, we implement our algorithm within the open source \starry code package with ample documentation, examples, and tutorials.\footnote{\url{https://github.com/rodluger/starry}}.
+Finally, we implement our algorithm within the open source \starry code package with accompanying documentation, examples, and tutorials.\footnote{\url{https://github.com/rodluger/starry}}
 All of the figures in this paper are also open source; clickable \GitHubIconBlue icons next to each figure link to the exact version of the \texttt{Python} script used to generate them.
@@
 This may be an acceptable prior if truly nothing is known about the typical angular scale of features on the surface, but this is seldom the case.
-Both observations of the Sun and magnetohydrodynamic simulations of stellar magnetic fields give us prior constraints on the typical scales of starspots \xxx{(cite me)}, and climate models of brown dwarfs tell us about typical sizes of clouds and other atmospheric features \citep[e.g.,][]{Tan2019,Tan2020,Tan2021a,Tan2021b}.
+Both observations of the Sun and magnetohydrodynamic simulations of stellar magnetic fields give us prior constraints on the typical scales of starspots \citep[e.g.,][]{Berdyugina2005,Solanki2006}, and climate models of brown dwarfs tell us about typical sizes of clouds and other atmospheric features \citep[e.g.,][]{Tan2019,Tan2020,Tan2021a,Tan2021b}.
 These can be encoded into our Gaussian prior by choosing a prior variance that scales with spherical harmonic degree:
@@
 One common approach to this is \emph{cross-validation}, in which one's prior is optimized to yield the best predictive power for the data.
-Typically, cross-validation consists of choosing a specific value for the prior, masking one (``leave-one-out-cross-validation'') or several (``leave-p-out-cross-validation'') data points, optimizing the parameters of the model given this smaller dataset, then using the optimized model to predict the values of the missing data \xxx{(cite me)}.
+Typically, cross-validation consists of choosing a specific value for the prior, masking one (``leave-one-out-cross-validation'') or several (``leave-p-out-cross-validation'') data points, optimizing the parameters of the model given this smaller dataset, then using the optimized model to predict the values of the missing data \citep[e.g.,][]{Stone1974}.
 The optimal value of the prior is then chosen as the one with the highest predictive power, i.e., the smallest loss when fitting the missing data points \citep[for an example of this, see \S 3.7 in][]{Luger2018}.
@@
 Fortunately, our model is computationally efficient to evaluate and, given its analyticity, trivial to differentiate using an autodifferentiation scheme (see \S\ref{sec:starry}).
-It can therefore be used out-of-the-box within gradient-based sampling schemes such as \texttt{pymc3} \citep{Salvatier2016}, in particular the No-U-Turn Sampler (NUTS), a variant of Hamiltonian Monte Carlo that harnesses gradient information to greatly speed up the convergence of the MCMC chains.
+It can therefore be used out-of-the-box within gradient-based sampling schemes such as \texttt{pymc3} \citep{Salvatier2016}, in particular the No-U-Turn Sampler (NUTS), a variant of Hamiltonian Monte Carlo that harnesses gradient information to greatly speed up the convergence of the MCMC chains \citep[for a recent application of HMC in the context of spectroscopy, see][]{Kawahara2021}.
 The script used to infer the MAP solution for the map of Luhman 16B (see Figure~\ref{fig:luhman16b:maps}) uses \texttt{pymc3} to perform the optimization; extending it to perform posterior inference is straightforward.
@@
 Our formalism can be adapted to Doppler tomography by changing the limits of integration in Equation~(\ref{eq:appendix:kT}) to exclude the region occulted by the planet; we will also investigate this in upcoming work.
+%
+We will also explore an extension of the method to the case of Zeeman-Doppler imaging \citep{Marsh1988}, which makes use of spectropolarimetric observations to map the stellar magnetic field topology.
 
@@
             Each panel shows a different sample, each of which consists of 16 epochs, offset vertically for visibility.
-            The rest frame spectrum is the same as in Figure~\ref{fig:spot_setup} and the star is inclined at $i = 40^\circ$ with equatorial velocity $v = 50{,}000$ km/s.
+            The rest frame spectrum is the same as in Figure~\ref{fig:spot_setup} and the star is inclined at $i = 40^\circ$ with equatorial velocity $v = 50$ km/s.
             The star is assumed to have spots with radius $r = 15^\circ$, 25 percent contrast, and active latitude $\phi = 30^\circ \pm 5^\circ$.
@@
 Importantly, we derive a model for the \emph{entire observed spectrum}.
-Most Doppler imaging studies rely on techniques like template matching \xxx{(cite me)} or least squares deconvolution \citep[LSD;][]{Donati1997} to infer a mean spectral line shape at each epoch, which is then treated as the input to the Doppler imaging step.
+Most Doppler imaging studies rely on techniques like least squares deconvolution \citep[LSD;][]{Donati1997} to infer a mean spectral line shape at each epoch, which is then treated as the input to the Doppler imaging step.
 These studies usually focus on a few distinct, unblended, and well-understood spectral lines, which are transformed into a single mean profile evaluated over a relatively small number of wavelength bins.
@@
 
-While Doppler imaging has classically been used to infer the surfaces of massive stars \xxx{(cite me)}, the study of \citet{Crossfield2014} used the method to infer the first Doppler map of a brown dwarf, which we reproduced in this work.
+While Doppler imaging has classically been used to infer the surfaces of giant or luminous pre-main sequence stars, the study of \citet{Crossfield2014} used the method to infer the first Doppler map of a brown dwarf, which we reproduced in this work.
 Future studies could help us understand the intricate atmospheric dynamics of brown dwarfs \citep{Tan2021a,Tan2021b}, as well as the global properties of exoplanets, which may be amenable to Doppler imaging given the advent of a new generation of extremely large ground-based telescopes \citep{Crossfield2014b}.
@@
 We would like to thank Eric Agol, Christina Hedges, Rachael Roettenbacher, and the Astronomical Data Group at the Center for Computational Astrophysics (CCA) for useful comments, suggestions, and insights.
-RL and LZ are supported by Flatiron Fellowships at the CCA, a division of the Simons Foundation.
+RL and LLZ are supported by Flatiron Fellowships at the CCA, a division of the Simons Foundation.
 

### 2021-10-11 src/ms.tex
more tweaks

@@
 % TIMING RESULTS
-\def\timeInferY{under 1 second}
-\def\timeInferYB{about 5 seconds}
-\def\timeInferYBS{about 30 seconds}
-\def\timeInferYBSLOSNR{about 30 seconds}
-\def\timeInferTwoSpec{about 20 minutes}
+\def\timeInferY{under 1 second\xspace}
+\def\timeInferYB{about 5 seconds\xspace}
+\def\timeInferYBS{about 30 seconds\xspace}
+\def\timeInferYBSLOSNR{about 30 seconds\xspace}
+\def\timeInferTwoSpec{about 20 minutes\xspace}
 
@@
     %
-    Our model for the observed spectrum is linear in the parameters describing the specific intensity distribution on the surface, which makes the posterior over surface maps computationally trivial to evaluate under certain choices of priors.
+    Our model for the observed spectrum is linear in the parameters describing the specific intensity distribution on the surface, which makes the posterior distribution over surface maps computationally trivial to evaluate under certain choices of priors.
     %
@@
 %
-Let $I(\lnlam, \x, t)$ be the specific intensity observed at log wavelength $\lnlam \equiv \ln\frac{\lambda}{\lambda_\mathrm{r}}$ and at sky-projected Cartesian position $\x = (x, y, z)$ on the surface of the star at time $t$, where $\lambda_\mathrm{r}$ is a reference wavelength.
+Let $I(\lnlam, \x, t)$ be the specific intensity observed at log wavelength $\lnlam \equiv \ln\frac{\lambda}{\lambda_\mathrm{r}}$ and at sky-projected Cartesian position $\x = (x, y, z)$ on the surface of the star at time $t$, where $\lambda_\mathrm{r}$ is an arbitrary reference wavelength, such as the central wavelength in the observed spectrum.
 We may express this intensity as
@@
 %
-In the case that the star's rotation is rigid (i.e., differential rotation is negligible) and other effects such as convective blueshift may be ignored, the radial velocity at any point on the surface is simply proportional to the distance to the axis of rotation.
+In the case that the star's rotation is rigid (i.e., the effect of differential rotation on the spectrum is small) and other effects such as convective blueshift may be ignored, the radial velocity at any point on the surface is simply proportional to the distance to the axis of rotation.
 Without loss of generality, if we assume the axis of rotation lies along the $y-z$ plane, we have
@@
 We generated a synthetic stellar surface with a large, circular spot at a latitude of $30^\circ$ and computed its spherical harmonic expansion up to $l_\mathrm{max}=20$ in the form of the vector of coefficients $\bvec{y}$.
-The stellar rest frame spectrum $I(\lnlam_0)$ is taken to be a single Gaussian absorption line that is spatially constant everywhere save for a multiplicative factor equal to the local spot intensity.
-This corresponds to a spectral/spatial expansion vector $\alm(\lnlam_0)$ whose coefficient at degree $l$ and order $m$ is equal to $y_{lm} I(\lnlam_0)$.
+The stellar rest frame spectrum $I(\lnlam_0)$ is taken to be a single Gaussian absorption line that is spatially constant everywhere save for a multiplicative factor equal to the local spot intensity, which is described by the spherical harmonic expansion.
+%This corresponds to a spectral/spatial expansion vector $\alm(\lnlam_0)$ whose coefficient at degree $l$ and order $m$ is equal to $y_{lm} I(\lnlam_0)$.
 In the Figure, we rotated the star about an axis perpendicular to the line of sight (left panel) and computed the observed spectrum using Equation~(\ref{eq:deconv:F}) (center panel). 
@@
             As the spot rotates into view (left panel), the line shape changes slightly (center panel). 
-            The residuals between the line when the spot is in view (solid) and when it is on the backside of the star (dotted) are shown in the right panel, where a Gaussian-like feature can be seen tracking the spot as it rotates from the blueshifted hemisphere to the redshifted hemisphere of the star.
+            The difference between the line when the spot is in view (solid) and when it is on the backside of the star (dotted) are shown in the right panel, where a Gaussian-like feature can be seen tracking the spot as it rotates from the blueshifted hemisphere to the redshifted hemisphere of the star.
         }
@@
             The bottom panel shows the absolute value of the difference between the two spectra for different number of grid points in the numerical solution.
-            As the number of grid points increases, the numerical solution approaches the \starry solution.
+            As the number of grid points increases, the numerical solution approaches our solution.
         }
@@
 Since the product of two random variables is generally non-Gaussian, even when the variables themselves are Gaussian,%
-\footnote{see, e.g., \url{http://mathworld.wolfram.com/NormalProductDistribution.html}}%
+\footnote{see, e.g., \url{http://mathworld.wolfram.com/NormalProductDistribution.html}}
 so too is the prior on $\alm$. 
@@
 \begin{align}
+    \label{eq:isotropicprior}
     \boldsymbol{\Lambda}_\bvec{y} & =
@@
 However, what is not shown in the figure is the fact that overall, the star also gets \emph{dimmer}: the continuum level drops in the presence of the spot. 
-Unfortunately, spectrographs are not usually designed to measure this, since the change in the star's overall brightness from one observation to the next is often dwarfed by (unknown) changes in the spectrograph sensitivity, cloud cover, etc.
-For this reason, the spectra are usually normalized to have a fixed baseline continuum, and Equation~\ref{eq:linear:f} is no longer a good model for the data.
+Unfortunately, spectrographs are not usually designed to measure this, since the change in the star's overall brightness from one observation to the next is often dwarfed by (unknown) changes in the spectrograph stability, cloud cover, etc.
+For this reason, the spectra are usually normalized to have a fixed baseline continuum, and Equation~(\ref{eq:linear:f}) is no longer a good model for the data.
 
@@
             The latter is the uncertainty associated with our particular choice of prior, as the southernmost latitudes of the star are never visible to the observer.
-            The optimization step in this experiment ran in \timeInferY.
+            The optimization step in this experiment ran in \timeInferY on a two-core virtual machine.
         }
@@
 
-As the SNR incraeses, however, the quality of the \spot feature does not improve appreciably, since a SNR of 1,000 is more than sufficient to recover a $l_\mathrm{max} = 15$ band-limited map. 
+As the SNR increases, however, the quality of the \spot feature does not improve appreciably, since a SNR of 500 is sufficient to recover a $l_\mathrm{max} = 15$ band-limited map. 
 Interestingly, at constant spatial prior variance ($\boldsymbol{\Lambda}_\bvec{y} = 10^{-4}\bvec{I}$), the map quality actually begins to degrade with higher SNR south of the equator due to overfitting.
@@
             The observed spectra are continuum-normalized and the rest frame spectrum is assumed to be known exactly.
+            The SNR=1,000 panel corresponds to the solution presented in Figure~\ref{fig:spot_infer_yb}.
         }
@@
 They discretized the stellar surface using 200 cells and solved for the optimal surface map with a maximum entropy prior as in \citet{Vogt1987}, assuming a fiducial inclination $i=70^\circ$ roughly based on the photometric rotation period and the inferred value of $v\sin i$; given the low SNR of the dataset, they were unable to place meaningful constraints on $i$.
-We reproduce their resulting surface brightness map in the right panel of Figure~\ref{fig:luhman16b:maps}, seen at six different phases spanning a full rotation.
+We show their resulting surface brightness map in the right panel of Figure~\ref{fig:luhman16b:maps}, seen at six different phases spanning a full rotation.
 
@@
 Both observations of the Sun and magnetohydrodynamic simulations of stellar magnetic fields give us prior constraints on the typical scales of starspots \citep[e.g.,][]{Berdyugina2005,Solanki2006}, and climate models of brown dwarfs tell us about typical sizes of clouds and other atmospheric features \citep[e.g.,][]{Tan2019,Tan2020,Tan2021a,Tan2021b}.
-These can be encoded into our Gaussian prior by choosing a prior variance that scales with spherical harmonic degree:
-%
-\begin{align}
-    \boldsymbol{\Lambda}_\bvec{y} = 
-    \begin{pmatrix}
-        \sigma_0^2 & & & & & & & & & \\[-0.5em]
-        & \sigma_1^2 & & & & & & & & \\[-0.5em]
-        & & \sigma_1^2 & & & & & & & \\[-0.5em]
-        & & & \sigma_1^2 & & & & & & \\[-0.5em]
-        & & & & \sigma_2^2 & & & & & \\[-0.5em]
-        & & & & & \sigma_2^2 & & & & \\[-0.5em]
-        & & & & & & \sigma_2^2 & & & \\[-0.5em]
-        & & & & & & & \sigma_2^2 & & \\[-0.5em]
-        & & & & & & & & \sigma_2^2 & \\[-0.5em]
-        & & & & & & & & & \ddots
-    \end{pmatrix}
-    \quad,
-\end{align}
-%
-where the variance at each degree is parametrized as, e.g.,
+These can be encoded into our Gaussian prior by choosing a prior variance that scales with spherical harmonic degree, as in Equation~(\ref{eq:isotropicprior}), where the variance at each degree is parametrized as, e.g.,
 %
@@
 The fact that we obtained a solution that is qualitatively similar to that of \citet{Crossfield2014} is encouraging, but it is not sufficient.
-Doppler imaging studies are notorious at producing features that are artificially elongated in latitude, just like the dark spot seen in the figure \citep[see, e.g.,][]{Unruh1995}.
+Doppler imaging studies are notorious for producing features that are artificially elongated in latitude, just like the dark spot seen in the figure \citep[see, e.g.,][]{Unruh1995}.
 The Doppler imaging method is also less sensitive to azimuthally symmetric features, like the zonal bands that may be present on brown dwarfs as on Jupiter.

### 2021-10-11 src/figures/compare.py

@@ -75,7 +75,7 @@ ax[1].set_yscale("log")
 ax[1].set_xlabel(r"$\lambda$ [nm]")
 ax[1].legend(fontsize=10, loc="upper right")
 ax[1].set_ylim(1e-10, 1e0)
-ax[1].set_ylabel(r"residuals")
+ax[1].set_ylabel(r"relative error (numerical)")
 
 # Show the image
 aximg = inset_axes(ax[0], width="15%", height="45%", loc=4, borderpad=1)

### 2021-10-11 src/ms.tex
fix showyourwork; address some tex comments

@@
 %
-Fourth, and finally, most Doppler imaging codes are not open source \citep[][to name a few]{Collier1997,Hackman2001,Carroll2012,Rosen2015,AsensioRamos2021},
-% DOTS, INVERS7-PD, iMAP, INVERSLSD, ??
-nor are the data used to produce many of the maps found in the literature, making it difficult to reproduce results and compare Doppler images of different stars on the same footing.
+Fourth, and finally, Doppler imaging results reported in the literature use a variety of custom data analysis codes, most of which are not open source 
+\citep[][to name a few]{Collier1997,Hackman2001,Carroll2012,Rosen2015,AsensioRamos2021}; % DOTS, INVERS7-PD, iMAP, INVERSLSD, ??
+many studies also utilize data that is often not included in the resulting publication or made easily available online. 
+This makes it difficult to reproduce results and compare Doppler images of different stars on the same footing. 
+As argued above, detailed choices in a Doppler imaging analysis will have a significant effect on the reported point-estimate result, so this inability to compare uniformly analyzed observations is a significant hindrance to interpretation.
 
@@
 In a similar vein, our present model involves an integration over the entire stellar disk. 
-This is the desired approach in Doppler imaging studies, but does apply in the context of Doppler \emph{tomography} \citep[e.g.,][]{Johnson2017}, in which the star is observed during a transit of an orbiting planet to infer, e.g., the degree of misalignment between the planet's orbit and the stellar spin axis.
-Our formalism can be adapted to Doppler tomography by changing the limits of integration in Equation~(\ref{eq:appendix:kT}) to exclude the region occulted by the planet; we will also investigate this in upcoming work.
+This is the desired approach in Doppler imaging studies, but does not apply in the context of Doppler \emph{tomography} \citep[e.g.,][]{Johnson2017}, in which the star is observed during a transit of an orbiting companion to infer, e.g., the degree of misalignment between the companion's orbit and the stellar spin axis.
+Our formalism can be adapted to Doppler tomography by changing the limits of integration in Equation~(\ref{eq:appendix:kT}) to exclude the region occulted by the companion; we will also investigate this in upcoming work.
 %

### 2021-10-11 src/ms.tex
make spot ten percent

@@
 \def\timeInferY{under 1 second\xspace}
-\def\timeInferYB{about 5 seconds\xspace}
+\def\timeInferYB{about 1 second\xspace}
 \def\timeInferYBS{about 30 seconds\xspace}
@@
             Each point on the surface is given the same spectrum, composed of a sum of synthetic Gaussian absorption lines (blue curve in the bottom panel).
-            The specific intensity at each point on the surface is equal to this spectrum weighted by the intensity of the map, which is close to zero within the spot (point labeled \texttt{B}) and close to unity outside the spot (point labeled \texttt{A}).
+            The specific intensity at each point on the surface is equal to this spectrum weighted by the intensity of the map, which is about ten percent within the spot (point labeled \texttt{B}) and close to unity outside the spot (point labeled \texttt{A}).
             To generate the synthetic dataset (orange curves in the bottom panel), the star is inclined at $40^\circ$ with respect to the line of sight and the disk-integrated spectrum is computed at 16 equally-spaced phases between $-180^\circ$ and $180^\circ$, assuming an equatorial velocity $v = 60$ km/s (middle panel).

### 2021-10-12 src/ms.tex
final tweaks

@@
 \begin{abstract}
-    We derive a novel, efficient, and closed form solution to the problem of Doppler imaging of stellar surfaces from high resolution spectral timeseries datasets.
-    %
-    Our model for the observed spectrum is linear in the parameters describing the specific intensity distribution on the surface, which makes the posterior distribution over surface maps computationally trivial to evaluate under certain choices of priors.
-    %
-    Our model is also linear in the local (rest frame) stellar spectrum, which may itself be spatially variable; this allows one to perform Doppler imaging with limited knowledge of the local stellar spectrum and therefore works on blended lines, regions of the spectrum where line formation mechanisms are not well understood, or stars whose spots have intrinsically different spectra from the rest of the photosphere.
+    %
+    The study of stellar surfaces can reveal information about the chemical composition, interior structure, and magnetic properties of stars.
+    It is also critical to the detection and characterization of extrasolar planets, in particular those targeted in extreme precision radial velocity (EPRV) searches, which must contend with stellar variability that is often orders of magnitude stronger than the planetary signal.
+    %
+    One of the most successful methods to map the surfaces of stars is Doppler imaging, in which the presence of inhomogeneities is inferred from subtle line shape changes in high resolution stellar spectra.
+    %
+    \textbf{In this paper, we present a novel, efficient, and closed-form solution to the problem of Doppler imaging of stellar surfaces.}
+    %
+    Our model explicitly allows for incomplete knowledge of the local (rest frame) stellar spectrum, allowing one to learn differences from spectral templates while simultaneously mapping the stellar surface.
+    It therefore works on blended lines, regions of the spectrum where line formation mechanisms are not well understood, or stars whose spots have intrinsically different spectra from the rest of the photosphere.
     %
@@
     %
-    As a proof-of-concept, we use our model to infer the surface map of the brown dwarf Luhman 16B, finding close agreement with the solution of \citet{Crossfield2014}.
+    As a proof-of-concept, we use our model to infer the surface map of the brown dwarf WISE 1049-5319B, finding close agreement with the solution of \citet{Crossfield2014}.
+    %
+    We also discuss Doppler imaging in the context of EPRV studies and describe an interpretable spectral-temporal Gaussian process for stellar spectral variability that we expect will be important for EPRV exoplanet searches.
     %
@@
 
-First, Doppler imaging is usually an ill-posed problem, meaning there is no unique solution for the surface map given a spectroscopic dataset.
+\textbf{First}, Doppler imaging is usually an ill-posed problem, meaning there is no unique solution for the surface map given a spectroscopic dataset.
 This issue is typically well understood \citep[e.g.,][]{Piskunov1990,Rice2002}, and most studies circumvent this issue by employing restrictive priors to ensure the uniqueness of the solution. 
@@
 %
-Second, the Doppler imaging technique is generally more sensitive to longitudinal than latitudinal variations, often leading to spurious, latititudinally elongated features in the maximum likelihood solution \citep[e.g.,][]{Unruh1995,Crossfield2014b}.
-%
-Third, the Doppler imaging technique requires the availability of accurate spectral templates for the local rest frame spectrum of the star.
-Several studies have shown that errors in these templates or the presence of unresolved line blends in the observed spectrum can introduce signficant artifacts in the map solution \citep[e.g.,][]{Rice1989,Unruh1995}.
+\textbf{Second}, the Doppler imaging technique is generally more sensitive to longitudinal than latitudinal variations, often leading to spurious, latititudinally elongated features in the maximum likelihood solution \citep[e.g.,][]{Unruh1995,Crossfield2014b}.
+%
+\textbf{Third}, the Doppler imaging technique requires the availability of accurate spectral templates for the local rest frame spectrum of the star.
+Several studies have shown that errors in line templates or the presence of unresolved line blends in the observed spectrum can introduce signficant artifacts in the map solution \citep[e.g.,][]{Rice1989,Unruh1995}.
 Moreover, changes in the local spectrum over the surface of the star (such as different line depths or the presence of different absorption lines within spots) can similarly bias the inferred map if these are not properly modeled.
@@
 %
-Fourth, and finally, Doppler imaging results reported in the literature use a variety of custom data analysis codes, most of which are not open source 
+\textbf{Fourth}, and finally, Doppler imaging results reported in the literature use a variety of custom data analysis codes, most of which are not open source 
 \citep[][to name a few]{Collier1997,Hackman2001,Carroll2012,Rosen2015,AsensioRamos2021}; % DOTS, INVERS7-PD, iMAP, INVERSLSD, ??
@@
 
-In this paper, the third in a series dedicated to mapping stellar surfaces \citep{Luger2021a,Luger2021b}, we seek to address these issues by developing a novel algorithm for Doppler imaging.
+In this paper, the third in a series dedicated to mapping stellar surfaces \citep{Luger2021a,Luger2021b}, we develop a novel algorithm for Doppler imaging that addresses each of these issues.
 The various pitfalls of Doppler imaging outlined above necessitate an algorithm that is efficient enough to be used in a Bayesian posterior inference context, where one can formally address the degeneracies at play and quantify their effect on the uncertainties of the inferred stellar maps.
 They also necessitate an algorithm that is flexible, capable of learning deviations from the template or capturing spatial variations in the rest-frame spectrum.
-And most of all, they necessitate a user-friendly, well-documented, and open source implementation, which is sorely lacking the literature.
-Our algorithm addresses these various issues by building on the work of \citet{Luger2019}, who derived analytic solutions to the light curve mapping problem by expanding the stellar surface map in the spherical harmonic basis.
+And most of all, they necessitate a user-friendly, well-documented, and open source implementation, which is currently lacking the literature.
+Our algorithm addresses these various issues by building on our previous work \citep{Luger2019}, where we derived analytic solutions to the light curve mapping problem by expanding the stellar surface map in the spherical harmonic basis.
 While spherical harmonics are routinely used in Doppler imaging problems \citep{Deutsch1958,Deutsch1970,Falk1974,Donati2006,Kochukhov2014}, we present a new closed-form solution to the forward model for Doppler imaging when working in this basis, making our model both precise and computationally efficient.
@@
 
-The paper is organized as follows: in \S\ref{sec:the_problem}~and~\S\ref{sec:the_solution} we introduce the math behind the Doppler imaging problem and derive a closed form expression for the model. 
-In \S\ref{sec:linear},~\S\ref{sec:inverse},~and~\S\ref{sec:bellswhistles} we demonstrate how to re-express the model as a linear operation on the input spectrum and stellar map and derive closed form expressions for the two conditioned on the data and priors.
-In \S\ref{sec:spotstar} we apply our techniques to a mock problem, and in \S\ref{sec:luhman16b} we apply it to a real spectral dataset of the brown dwarf Luhman 16B.
-We further discuss our results in \S\ref{sec:discussion}~and~our implementation within the \starry framework in \S\ref{sec:starry}.
-We present a summary of the paper in \S\ref{sec:conclusions}.
+The paper is organized as follows: in \S\ref{sec:the_problem}~and~\S\ref{sec:the_solution} we introduce the math behind the Doppler imaging problem and derive a closed-form expression for the model. 
+In \S\ref{sec:linear},~\S\ref{sec:inverse},~and~\S\ref{sec:bellswhistles} we demonstrate how to re-express the model as a linear operation on the input spectrum and stellar map and derive closed-form expressions for the two conditioned on the data and priors.
+In \S\ref{sec:spotstar} we apply our techniques to a mock problem, and in \S\ref{sec:luhman16b} we apply it to a real spectral dataset of the brown dwarf WISE 1049-5319B.
+We further discuss our results in \S\ref{sec:discussion}, and in \S\ref{sec:gp} we focus on an immediate extension of our work: the development of an interpretable spectral-temporal Gaussian process for stellar spectral variability.
+Finally, we discuss the implementation of our Doppler imaging algorithm within the \starry framework in \S\ref{sec:starry}, and present a summary of the paper in \S\ref{sec:conclusions}.
 
@@
             As the number of grid points increases, the numerical solution approaches our solution.
+            Note that here we assume the stellar surface can be expressed exactly as an $l_\mathrm{max} = 20$ spherical harmonic decomposition.
+            When our algorithm is applied to real data, there will be errors due to the truncation of the expansion at finite spherical harmonic degree.
         }
@@
 %
-Unfortunately, this equation does not admit a closed form solution for $\mathbf{y}$. 
-One can, however, still solve for the maximum a posteriori value of $\mathbf{y}$ in an efficient manner by iteratively solving for the baseline and then for the spherical harmonic coefficients.
+Unfortunately, this equation does not admit a closed-form solution for $\mathbf{y}$. 
+One can, however, still solve for the maximum \emph{a posteriori} value of $\mathbf{y}$ in an efficient manner by iteratively solving for the baseline and then for the spherical harmonic coefficients.
 We describe a procedure for this in \S\ref{sec:spotstar} below.
@@
 These choices are arbitrary and primarily based on trial-and-error given knowledge of the true solutions.
-We discuss strategies for choosing optimal priors for real datasets in \S\ref{sec:discussion:priors} below.
+We discuss strategies for choosing priors for real datasets in \S\ref{sec:discussion:priors} below.
 
@@
 Finally, in order to enforce that the two component surface maps sum to unity (as described above), we optimize for the actual \emph{pixel} intensities of the photosphere map, on which we place a simple uniform prior on $[0, 1]$; the spot map is then simply the complement.
-The spherical harmonic coefficients are then computed via a fast, linear spherical harmonic transform (SHT) operation at each step, as in \citep{Bartolic2021}.
-In order to satisfy the Nyquist criterion, our pixel grid consists of twice as many pixels as spherical harmonic coefficients.
+The spherical harmonic coefficients are then computed via a fast, linear spherical harmonic transform (SHT) operation at each step, as in \citet{Bartolic2021}.
+In order to satisfy the Nyquist criterion, our pixel grid consists of twice as many pixels as spherical harmonic coefficients.%
+\footnote{%
+While it may seem strange to return to a discretized parametrization of the surface---after all the work we did to derive a closed-form solution in the spherical harmonic basis---our approach capitalizes on the strengths of both parametrizations: the ease of incorporating a nonnegativity prior in the pixel basis and the efficiency with which we can compute the model in the spherical harmonic basis.
+Thanks to the linear relationship between these two bases, the transformation between them accrues virtually no overhead.}
 
@@
 
-\section{Application to Luhman 16B}
+\section{Application to WISE 1049-5319B}
 \label{sec:luhman16b}
@@
 
-Having shown that our model performs well on synthetic data, we now turn to a real dataset: the VLT/CRIRES observations of Luhman 16B (WISE 1049-5319B) presented in the Doppler imaging study of \citet{Crossfield2014}.
-Luhman 16B belongs to a binary brown dwarf system, which, at a distance of 2 pc, consists of the two closest known brown dwarfs to the Solar system.
-Despite its proximity, Luhman 16B is intrinsically dim and, with a projected rotational velocity $v \sin i = 26.1$ km/s, is at the slow end of what can be imaged using the traditional Doppler imaging technique.
-Therefore, unlike those of classical Doppler imaging targets, the spectral lines of Luhman 16B do not individually show large scale spot modulation (Figure~\ref{fig:spot}) from one epoch to the next; nor are the spectral templates for brown dwarfs particularly well understood.
-Nonetheless, we chose to model Luhman 16B specifically to show the power behind our new methodology, in particular its ability to learn both the surface map and the rest frame spectrum simultaneously from the entire dataset---not just from unblended spectral lines that have reliable templates.
+Having shown that our model performs well on synthetic data, we now turn to a real dataset: the VLT/CRIRES observations of WISE 1049-5319B (Luhman 16B) presented in the Doppler imaging study of \citet{Crossfield2014}.
+WISE 1049-5319B belongs to a binary brown dwarf system, which, at a distance of 2 pc, consists of the two closest known brown dwarfs to the Solar system.
+Despite its proximity, WISE 1049-5319B is intrinsically dim and, with a projected rotational velocity $v \sin i = 26.1$ km/s, is at the slow end of what can be imaged using the traditional Doppler imaging technique.
+Therefore, unlike those of classical Doppler imaging targets, the spectral lines of WISE 1049-5319B do not individually show large scale spot modulation (Figure~\ref{fig:spot}) from one epoch to the next; nor are the spectral templates for brown dwarfs particularly well understood.
+Nonetheless, we chose to model WISE 1049-5319B specifically to show the power behind our new methodology, in particular its ability to learn both the surface map and the rest frame spectrum simultaneously from the entire dataset---not just from unblended spectral lines that have reliable templates.
 
 In the original Doppler imaging study of this target, \citet{Crossfield2014} took 56 spectra of each object (the angular resolution was high enough to obtain individual spectra of both brown dwarfs) over the four CRIRES detectors in the range $2.288-2.345 \mu$m over a time span of 5 hours, with individual exposures of 300 s.
-The 5 hour baseline was enough to capture one full rotation of Luhman 16B, whose period was constrained to be about 4.9 hours from its photometric variability \citep{Gillon2013}.
+The 5 hour baseline was enough to capture one full rotation of WISE 1049-5319B, whose period was constrained to be about 4.9 hours from its photometric variability \citep{Gillon2013}.
 These spectra were then downbinned to 14 epochs to boost the SNR, corrected for tellurics and spectrograph systematics, and continuum-normalized.
@@
 
-In order to produce Doppler images of Luhman 16B, \citet{Crossfield2014} used brown dwarf template spectra from the BT-Settl library \citep{Allard2013}, finding that the spectrum with $\log_{10} g = 5.0$ and $T_\mathrm{eff} = 1450$ K provided the best match to the dataset.
+In order to produce Doppler images of WISE 1049-5319B, \citet{Crossfield2014} used brown dwarf template spectra from the BT-Settl library \citep{Allard2013}, finding that the spectrum with $\log_{10} g = 5.0$ and $T_\mathrm{eff} = 1450$ K provided the best match to the dataset.
 This spectrum was then Doppler-shifted by the systemic radial velocity of the brown dwarf and broadened to match the spectrograph resolution.
@@
         \caption{%
-            Calibrated and tellurics-corrected CRIRES spectra of Luhman 16B from \citet{Crossfield2014} taken at 14 epochs spanning a full rotation of the brown dwarf (black points).
+            Calibrated and tellurics-corrected CRIRES spectra of WISE 1049-5319B from \citet{Crossfield2014} taken at 14 epochs spanning a full rotation of the brown dwarf (black points).
             Our maximum \emph{a posteriori} solution is shown as the orange curves.
@@
 Since we have a very good guess for the template spectrum, this optimization is much faster than in \S\ref{sec:twospec}, converging within $1,000$ steps.
-Because of our efficient gradient-based implementation (\S\ref{sec:starry}), the entire optimization takes only about 3 minutes of runtime on a typical Macbook laptop.
+Because of our efficient gradient-based implementation (\S\ref{sec:starry}), the entire optimization takes only about 3 minutes of runtime on a 2018 Macbook laptop.
 
@@
         \caption{%
-            Maximum \emph{a posteriori} surface maps of Luhman 16B inferred from the spectra in Figure~\ref{fig:luhman16b:data_model}. 
+            Maximum \emph{a posteriori} surface maps of WISE 1049-5319B inferred from the spectra in Figure~\ref{fig:luhman16b:data_model}. 
             \emph{Left:} surface map inferred using the algorithm developed in this work. 
             \emph{Right}: surface map inferred in \citet{Crossfield2014}, reproduced from Figure~2 in that paper.
-            We infer the presence of a bright circumpolar spot, as well as the presence of a few dark features, most of which agree with the map presented in the original work.
+            We infer the same two dominant features as in \citet{Crossfield2014b}:
+            a bright circumpolar spot, seen along the sub-observer meridian at $t = 0.0$ hr,
+            and a dark, latitudinally elongated band prominent at $t = 2.4$ hr.
+            While the exact latitude of the bright spot and the behaviour of the dark spot equatorward of $-30^\circ$ latitude differ betwee the two solutions, both are point estimates obtained under different choices of prior and from significantly different methods.
+            We take their qualitative agreement to be a successful validation of our method.
         }
@@
 
-The right panel of Figure~\ref{fig:luhman16b:maps} shows our principal result: the inferred solution for the surface brightness map of Luhman 16B; compare to the right panel, showing the solution inferred by \citet{Crossfield2014}.
+The right panel of Figure~\ref{fig:luhman16b:maps} shows our principal result: the inferred solution for the surface brightness map of WISE 1049-5319B; compare to the right panel, showing the solution inferred by \citet{Crossfield2014}.
 Broadly speaking, the two surface maps agree rather well: we infer the same circumpolar bright spot, of about the same size and at roughly the same phase, although the exact latitude is different.
@@
 
-\subsection{Luhman 16B}
+\subsection{WISE 1049-5319B}
 \label{sec:discussion:luhman}
@@
 In \S\ref{sec:luhman16b} we validated our novel approach by reproducing the results of \citet{Crossfield2014}. 
-Despite the fact that we obtained a qualitatively similar surface map for Luhman 16B (Figure~\ref{fig:luhman16b:maps}), there are several aspects to our approach that could be improved in future work.
+Despite the fact that we obtained a qualitatively similar surface map for WISE 1049-5319B (Figure~\ref{fig:luhman16b:maps}), there are several aspects to our approach that could be improved in future work.
 %
@@
 The approach discussed above for choosing one's priors is distinctly Bayesian.
-Alternatively, one may choose a data-driven approach: to learn the optimal value of the priors from the data itself.
+Alternatively, one may take a data-driven approach: to learn the ``optimal'' value of the priors from the data itself.
 One common approach to this is \emph{cross-validation}, in which one's prior is optimized to yield the best predictive power for the data.
 Typically, cross-validation consists of choosing a specific value for the prior, masking one (``leave-one-out-cross-validation'') or several (``leave-p-out-cross-validation'') data points, optimizing the parameters of the model given this smaller dataset, then using the optimized model to predict the values of the missing data \citep[e.g.,][]{Stone1974}.
-The optimal value of the prior is then chosen as the one with the highest predictive power, i.e., the smallest loss when fitting the missing data points \citep[for an example of this, see \S 3.7 in][]{Luger2018}.
-
-In this context, the prior is usually referred to as a ``regularization'' term, since this procedure is not exactly Bayesian. 
+The value of the prior is then chosen as the one with the highest predictive power, i.e., the smallest loss when fitting the missing data points \citep[for an example of this, see \S 3.7 in][]{Luger2018}.
+
+In this context, the prior is usually referred to as a ``regularization'' term, since this procedure is decidedly not Bayesian.
 Specifically, it regularizes the model to ensure a balance between underfitting (the model doesn't fit the data well) and overfitting (the model fits the data so well that it's also fitting the noise, leading to spurious results).
@@
 Traditionally, many Doppler imaging studies impose an additional \emph{maximum entropy} constraint \citep{Vogt1987}, whose objective is to ensure a similar balance between underfitting and overfitting as discussed above.
-These can also easily be incorporated into our formalism, although we recommend using a method such as cross-validation to choose the optimal regularization strength in this context.
+These can also easily be incorporated into our formalism, although we recommend using a method such as cross-validation to choose the regularization strength in this context.
 
@@
 In the limit of finite SNR, and when things like the true stellar spectrum, the stellar inclination, and the limb darkening profile are not well known (which is usually the case in Doppler imaging studies!), it is important to recognize the limitation of point estimates like those obtained in this work.
-The maps of Luhman 16B presented in Figure~\ref{fig:luhman16b:maps}, for instance, are just that: point estimates that carry no sense of the uncertainty associated with any of those features.
-Given the low SNR of the dataset (Figure~\ref{fig:luhman16b:data_model}), the unknown inclination of the star, and the uncertainty in parameters like the rotation period, $v\sin i$, and the limb darkening profile, the maps shown in Figure~\ref{fig:luhman16b:maps} are almost certainly \emph{not} what Luhman 16B actually looks like in reality.
+The maps of WISE 1049-5319B presented in Figure~\ref{fig:luhman16b:maps}, for instance, are just that: point estimates that carry no sense of the uncertainty associated with any of those features.
+Given the low SNR of the dataset (Figure~\ref{fig:luhman16b:data_model}), the unknown inclination of the star, and the uncertainty in parameters like the rotation period, $v\sin i$, and the limb darkening profile, the maps shown in Figure~\ref{fig:luhman16b:maps} are almost certainly \emph{not} what WISE 1049-5319B actually looks like in reality.
 The fact that we obtained a solution that is qualitatively similar to that of \citet{Crossfield2014} is encouraging, but it is not sufficient.
@@
 It can therefore be used out-of-the-box within gradient-based sampling schemes such as \texttt{pymc3} \citep{Salvatier2016}, in particular the No-U-Turn Sampler (NUTS), a variant of Hamiltonian Monte Carlo that harnesses gradient information to greatly speed up the convergence of the MCMC chains \citep[for a recent application of HMC in the context of spectroscopy, see][]{Kawahara2021}.
-The script used to infer the MAP solution for the map of Luhman 16B (see Figure~\ref{fig:luhman16b:maps}) uses \texttt{pymc3} to perform the optimization; extending it to perform posterior inference is straightforward.
+Our model may also be useful in the context of variational inference (VI), and in particular automatic differentiation variational inference \citep[ADVI;][]{Kucukelbir2016}, which casts posterior inference as an optimization problem; both VI and ADVI are also implemented in \texttt{pymc3}.
+The script used to infer the MAP solution for the map of WISE 1049-5319B (see Figure~\ref{fig:luhman16b:maps}) uses \texttt{pymc3} to perform the optimization; extending it to perform posterior inference is straightforward.
 However, doing so is beyond the scope of the present paper, given that this task is still likely to be challenging given the very large number of parameters (${\sim}4{,}000$). 
@@
 We can even imagine doing this in an ensemble setting under a fully hierarchical model, in which we attempt to constrain these properties from the analysis of many Doppler imaging datasets of different stars simultaneously.
-This procedure is likely computationally prohibitive, but the linearity of our model (\S\ref{sec:linear}) allows us to extend the Gaussian process formalism of \citet{Luger2021b} to Doppler imaging datasets, allowing us to marginalize over the surface maps consistent with the data \emph{analytically}; see \S\ref{sec:discussion:gp} below.
+This procedure is likely computationally prohibitive, but the linearity of our model (\S\ref{sec:linear}) allows us to extend the Gaussian process formalism of \citet{Luger2021b} to Doppler imaging datasets, allowing us to marginalize over the surface maps consistent with the data \emph{analytically}; see \S\ref{sec:gp} below.
+
+\subsection{Assumptions}
+\label{sec:discussion:assumptions}
+
+Both the derivation and application of our model make several assumptions, many of which we have already discussed. Nevertheless, we present a detailed list of these assumptions here for clarity:
+
+\begin{itemize}
+    \item We assume there is a well-defined stellar ``surface'', an effective layer from which the star emits its light. 
+    This is certainly an oversimplification, as stars are fundamentally three-dimensional objects with complex vertical temperature gradients.
+    \item We assume the emission is isotropic. 
+    We relax this assumption by allowing for limb darkening (\S\ref{sec:ld}), but this is treated as a suppression of flux toward the limb rather than by self-consistently solving the equations of radiative transfer.
+    \item We assume the radial velocity field of the stellar surface is a simple dipole, controlled only by the rigid body rotation of the star.
+This ignores effects like convective blueshift and differential rotation.
+We discuss incorporating these into our work in \S\ref{sec:discussion:caveats} below.
+    \item We assume the surface map is constant over time, and that all time variability comes from stellar rotation. 
+    We discuss modeling temporal surface variability in the context of a stochastic process in \S\ref{sec:gp} below.
+    \item We assume that the surface map may be well modeled by a spherical harmonic expansion truncated at some degree $l_\mathrm{max}$. 
+    The spherical harmonic basis is complete, meaning this assumption is rigorously correct in the limit  $l_\mathrm{max} \rightarrow \infty$.
+    In our experiments, we chose $l_\mathrm{max} = 10-20$, which allows us to model surface features on scales larger than about $18^\circ$ and $9^\circ$, respectively.
+    \item We assume the rest frame spectrum is defined on a grid with sufficiently high resolution that the convolution with the Doppler kernel may be approximated as a discrete linear convolution (Equation~\ref{eq:linear:convolution_def}).
+    \item In our base case (\S\ref{sec:the_solution}), we assume the star has a single rest frame spectrum, and that spatial changes are strictly changes in overall intensity. 
+    We relax this assumption in \S\ref{sec:eigen}, where we assume that variations in the spectrum with location can be expressed as the outer product of a set of $J$ spectral principal components $\boldsymbol{\mathbb{S}}$ and a set of $J$ spatial principal components $\boldsymbol{\mathbb{Y}}$.
+    If we choose $J = (l_\mathrm{max} + 1)^2$ (the number of spherical harmonic coefficients in the expansion of each component), this allows us to model \emph{any} spectral-spatial configuration on the surface of the star, band-limited to degree $l_\mathrm{max}$.
+    Truncation of this basis at smaller values of $J$ limits our ability to model arbitrary spatial variability in the spectrum.
+\end{itemize}
+
+All of the assumptions listed above relate to our \emph{forward} model (\S\ref{sec:linear}).
+Throughout the paper, we make several additional assumptions when solving the \emph{inverse} problem, that is, solving for the map and/or spectrum given a dataset.
 
@@
 While we were unable to find simple closed-form expressions for the resulting line integrals, they may still exist; we will investigate this in future work.
-Even if a closed form solution is unavailable, it is likely still possible to efficiently evaluate the integrals numerically.
+Even if a closed-form solution is unavailable, it is likely still possible to efficiently evaluate the integrals numerically.
 
@@
 
-\subsection{A Spectral-Spatial-Temporal Gaussian Process}
-\label{sec:discussion:gp}
+\section{A Spectral-Temporal Gaussian Process}
+\label{sec:gp}
 
@@
         \caption{%
-            20 samples from a spectral-spatial-temporal Gaussian process constructed from the algorithm presented here.
+            20 samples from a spectral-temporal Gaussian process constructed from the algorithm presented here.
             Each panel shows a different sample, each of which consists of 16 epochs, offset vertically for visibility.
@@
 
+\xxx{TEMPORAL VARIABILITY}
+
 \section{Implementation in \starry}
@@
 
-The algorithm is implemented using \texttt{theano} \citep{Bergstra2010}, a just-in-time compiling framework for \texttt{Python} with powerful autodifferentiation and optimization capabilities.
+The algorithm is implemented using \texttt{theano}/\texttt{aesara} \citep{Bergstra2010,Willard2021}, a just-in-time compiling framework for \texttt{Python} with powerful autodifferentiation and optimization capabilities.
 As such, the algorithm is fully differentiable and thus easy to use within gradient-based optimization and/or inference schemes such as Hamiltonian Monte Carlo.
@@
 The implementation of the algorithm in \starry is highly optimized.
-Even though we derived the model for the flux as a purely linear operation on the spectral/spatial expansion of the stellar surface (Equation~\ref{eq:deconv:F}), it is more  efficient in practice to compute it as a convolution using the highly optimized \texttt{conv2d} operations in \texttt{theano}.
+Even though we derived the model for the flux as a purely linear operation on the spectral/spatial expansion of the stellar surface (Equation~\ref{eq:deconv:F}), it is more  efficient in practice to compute it as a convolution using the highly optimized \texttt{conv2d} operations in \texttt{theano}/\texttt{aesara}.
 Typical runtimes and scalings for the \starry algorithm are shown in Figure~\ref{fig:runtime}, where we plot the evaluation of the full forward model for all spectra in a dataset as a function of several parameters.
@@
 
-As a proof-of-concept, we qualitatively reproduced the Doppler map of the brown dwarf Luhman 16B (WISE 1049-5319B) inferred in \citet{Crossfield2014} from VLT/CRIRES observations; see Figure~\ref{fig:luhman16b:maps}.
+As a proof-of-concept, we qualitatively reproduced the Doppler map of the brown dwarf WISE 1049-5319B (Luhman 16B) inferred in \citet{Crossfield2014} from VLT/CRIRES observations; see Figure~\ref{fig:luhman16b:maps}.
 We also tested our model's ability to accurately infer the surface maps and rest frame spectra from synthetic high SNR spectral timeseries observations, even in the limit of minimally informative priors on both quantities.
@@
 The model presented here, as well as its implementation in \starry, is easy to use in a posterior inference setting.
-In particular, our implementation harnesses the autodifferentation capabilities of the \texttt{theano} \citep{Bergstra2010} package within the \texttt{pymc3} \citep{Salvatier2016} probabilistic modeling framework, allowing for efficient posterior inference using Hamiltonian Monte Carlo (HMC) techniques.
+In particular, our implementation harnesses the autodifferentation capabilities of the \texttt{theano}/\texttt{aesara} \citep{Bergstra2010,Willard2021} package within the \texttt{pymc3} \citep{Salvatier2016} probabilistic modeling framework, allowing for efficient posterior inference using Hamiltonian Monte Carlo (HMC) techniques.
 We also present a sketch of how to incorporate our model into an interpretable, physically-motivated Gaussian process (GP) formalism for stellar spectroscopic timeseries datasets, a method that is highly relevant to extreme precision radial velocity (EPRV) searches for exoplanets.
@@
 Future studies could help us understand the intricate atmospheric dynamics of brown dwarfs \citep{Tan2021a,Tan2021b}, as well as the global properties of exoplanets, which may be amenable to Doppler imaging given the advent of a new generation of extremely large ground-based telescopes \citep{Crossfield2014b}.
-A likely first target will be the directly-imaged giant planet $\beta$ Pictoris b, which is only an order of magnitude dimmer than Luhman 16B; \citet{Snellen2014} showed that future observations with the planned Extremely Large Telecope (ELT) should be able to produce a global map of its surface.
+A likely first target will be the directly-imaged giant planet $\beta$ Pictoris b, which is only an order of magnitude dimmer than WISE 1049-5319B; \citet{Snellen2014} showed that future observations with the planned Extremely Large Telecope (ELT) should be able to produce a global map of its surface.
 Given the expected low SNR of such observations and the considerable uncertainty in the rest-frame spectra of directly imaged exoplanets, an efficient, probabilistic Doppler imaging approach like the one developed in this work will be imperative to maximizing the scientific output of those studies.

### 2021-10-12 src/figures/inclinations.py

@@ -38,6 +38,7 @@ ax[0, 1].annotate(
     color="k",
     zorder=101,
 )
+ax[0, 1].set_rasterization_zorder(0)
 
 # Solve & plot
 ax = ax[1:].flatten()
@@ -94,4 +95,5 @@ for i, inc in enumerate(incs):
         color="k",
         zorder=101,
     )
-fig.savefig("inclinations.pdf", bbox_inches="tight")
+    ax[i].set_rasterization_zorder(0)
+fig.savefig("inclinations.pdf", bbox_inches="tight", dpi=100)

### 2021-10-12 src/figures/spot_infer_yb.py

@@ -46,7 +46,7 @@ y_uncert = Q @ np.sqrt(np.diag(W @ W.T))
 
 # Plot the maps
 fig = plot_maps(y_true, y_inferred, y_uncert)
-fig.savefig("spot_infer_yb_maps.pdf", bbox_inches="tight", dpi=300)
+fig.savefig("spot_infer_yb_maps.pdf", bbox_inches="tight", dpi=150)
 
 # Plot the timeseries
 fig = plot_timeseries(

### 2021-10-12 src/ms.tex
for realz now

@@
 
+% HACK
+\pagebreak
+
 \section{Application to a spotted star}
@@
 Throughout the paper, we make several additional assumptions when solving the \emph{inverse} problem, that is, solving for the map and/or spectrum given a dataset.
+None of these assumptions are necessary for the application of our model to other datasets, but we include them here for completeness:
+
+\begin{itemize}
+    \item We assume the data are correctly calibrated and free of significant outliers, and that the noise model (e.g., Gaussian errors with known standard deviation) is known.
+    \item We assume there are either no telluric lines, or that these have been removed in a pre-processing step.
+    These may also be modeled simultaneously, but that is beyond the scope of the present work.
+    \item We assume the SNR of the data is high enough that the maximum \emph{a posteriori} solution to the surface map is meaningful.
+    In general, however, we stress the importance of performing posterior inference to constrain the uncertainties and one's degree of confidence in the solution.
+    \item In all of our examples, we assume the stellar rotation period and inclination are known exactly.
+    In practice, this is rarely ever the case, and one should optimize for (or, ideall, sample over) these variables.
+\end{itemize}
 
@@
 Our GP can be used as a principled, physically-motivated way to marginalize over the stellar signal to robustly detect the Keplerian signal of an orbiting planet.
+It is even straightforward to account for time variability in the stellar surface with this formalism.
+\citet{Luger2021b} discussed how to incorporate a stochastic time-variable component into the photometric variability GP, which can be directly incorporated into Equation~(\ref{eq:discussion:gpcov}) via the inclusion of a decoherence timescale $\tau$ in the set of GP hyperparameters $\boldsymbol{\theta}$.
 
 The next paper in the \emph{Mapping Stellar Surfaces} series will focus on further development of this GP, including accounting for uncertainty in the spectral template, accounting for the nonlinearity introduced by the continuum normalization, marginalizing over unknowns such as the inclination and limb darkening parameters, and rigorously testing the formalism on both synthetic and real datasets.
-
-\xxx{TEMPORAL VARIABILITY}
 

### 2021-10-12 src/ms.tex
new title
tweak

@@
     Mapping stellar surfaces\\
-    III: A Bayesian Approach to Doppler Imaging
+    III: An Efficient, Scalable, and Open-Source Doppler Imaging Model
 }
@@
     %
-    \textbf{In this paper, we present a novel, efficient, and closed-form solution to the problem of Doppler imaging of stellar surfaces.}
+    In this paper, we present a novel, efficient, and closed-form solution to the problem of Doppler imaging of stellar surfaces.
     %

### 2022-05-29 src/tex/ms.tex
update to syw 0.3.0

--- 2021-10-12 src/ms.tex
@@
 \include{style}
+\usepackage{showyourwork}
 
@@
 Finally, we implement our algorithm within the open source \starry code package with accompanying documentation, examples, and tutorials.\footnote{\url{https://github.com/rodluger/starry}}
-All of the figures in this paper are also open source; clickable \GitHubIconBlue icons next to each figure link to the exact version of the \texttt{Python} script used to generate them.
+All of the figures in this paper are also open source; clickable \faGithub icons next to each figure link to the exact version of the \texttt{Python} script used to generate them.
 To ensure the full reproducibility of this paper, we prepared it using the \showyourwork workflow\footnote{\url{https://github.com/rodluger/showyourwork}}, which exposes the datasets, source code, and all package dependencies needed to exactly reproduce the results.
@@
         \label{fig:kT}
+        \script{kT.py}
     \end{centering}
@@
         \label{fig:spot}
+        \script{spot.py}
     \end{centering}
@@
         \label{fig:compare}
+        \script{compare.py}
     \end{centering}
@@
         \label{fig:linalg}
+        \script{linalg.py}
     \end{centering}
@@
         \label{fig:ld}
+        \script{ld.py}
     \end{centering}
@@
         \label{fig:spot_setup}
+        \script{spot_setup.py}
     \end{centering}
@@
         \label{fig:spot_infer_y}
+        \script{spot_infer_y.py}
     \end{centering}
@@
         \label{fig:spot_infer_yb}
+        \script{spot_infer_yb.py}
     \end{centering}
@@
         \label{fig:spot_infer_ybs}
+        \script{spot_infer_ybs.py}
     \end{centering}
@@
         \label{fig:spot_infer_ybs_low_snr}
+        \script{spot_infer_ybs_low_snr.py}
     \end{centering}
@@
         \label{fig:twospec}
+        \script{twospec.py}
     \end{centering}
@@
         \label{fig:snr}
+        \script{snr.py}
     \end{centering}
@@
         \label{fig:inclinations}
+        \script{inclinations.py}
     \end{centering}
@@
         \includegraphics[width=0.495\linewidth]{figures/luhman16b_map.pdf} % 
-        \includegraphics[width=0.462\linewidth]{static/luhman16b_crossfield.png} % 
+        \includegraphics[width=0.462\linewidth]{figures/luhman16b_crossfield.png} % 
         \caption{%
@@
         \label{fig:gp}
+        \script{gp.py}
     \end{centering}
@@
         \label{fig:runtime}
+        \script{runtime.py}
     \end{centering}

### 2022-05-29 src/figures/Y1m1.py

@@ -1,19 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Plots the ``Y_{1,-1}`` spherical harmonic.
-
-"""
-import matplotlib.pyplot as plt
-import starry
-
-map = starry.Map(ydeg=1, lazy=False)
-map[1, -1] = 1
-img = map.render(res=300)
-fig, ax = plt.subplots(1, figsize=(0.25, 0.25))
-fig.subplots_adjust(left=0, right=1, bottom=0, top=1)
-ax.imshow(img, origin="lower", cmap="plasma", extent=(-1, 1, -1, 1))
-ax.axis("off")
-eps = 0.01
-ax.set_xlim(-1 - eps, 1 + eps)
-ax.set_ylim(-1 - eps, 1 + eps)
-fig.savefig("Y1m1.pdf", dpi=300)

### 2022-05-29 src/figures/inclinations.py

@@ -1,99 +1,0 @@
-"""
-Investigate how our recovered map varies with the
-stellar inclination (assumed to be known exactly).
-
-"""
-from utils.generate import generate_data
-import starry
-import numpy as np
-import matplotlib.pyplot as plt
-import os
-
-
-# Settings
-ydeg = 15
-smoothing = 0
-
-# Array of inclinations
-incs = np.array([10, 20, 30, 40, 50, 60, 70, 80, 90])
-veq = 60000.0  # m/s
-
-# Plot the true map
-fig, ax = plt.subplots(4, 3, figsize=(15, 10))
-ax[0, 0].set_visible(False)
-ax[0, 2].set_visible(False)
-map = starry.Map(ydeg=ydeg)
-map.load("spotdots", smoothing=smoothing)
-map.show(ax=ax[0, 1], projection="moll")
-ax[0, 1].annotate(
-    r"true",
-    xy=(0, 1),
-    xytext=(7, 7),
-    clip_on=False,
-    xycoords="axes fraction",
-    textcoords="offset points",
-    ha="left",
-    va="top",
-    fontsize=14,
-    color="k",
-    zorder=101,
-)
-ax[0, 1].set_rasterization_zorder(0)
-
-# Solve & plot
-ax = ax[1:].flatten()
-map = None
-for i, inc in enumerate(incs):
-
-    # Generate the data
-    data = generate_data(
-        inc=inc,
-        veq=veq,
-        image="spotdots",
-        flux_err=1e-4,
-        ydeg=ydeg,
-        smoothing=smoothing,
-        vsini_max=veq,
-    )
-    theta = data["data"]["theta"]
-    flux = data["data"]["flux"]
-    flux_err = data["data"]["flux_err"]
-
-    # Instantiate the map
-    if map is None:
-        map = starry.DopplerMap(lazy=False, **data["kwargs"])
-        map.spectrum = data["truths"]["spectrum"]
-        for n in range(map.udeg):
-            map[1 + n] = data["props"]["u"][n]
-    else:
-        map.inc = inc
-        map.veq = veq
-
-    # Solve
-    soln = map.solve(
-        flux,
-        theta=theta,
-        normalized=True,
-        fix_spectrum=True,
-        flux_err=flux_err,
-        spatial_cov=3e-5,
-        quiet=os.getenv("CI", "false") == "true",
-    )
-
-    # Visualize
-    map.show(ax=ax[i], projection="moll")
-    ax[i].annotate(
[…]

### 2022-05-29 src/figures/kT.py

@@ -1,68 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Plots the basis of `g` kernels.
-
-"""
-import matplotlib
-import matplotlib.pyplot as plt
-import numpy as np
-import starry
-
-
-# Get the `kT` functions at high res
-ydeg = 10
-map = starry.DopplerMap(ydeg)
-vsini = map.ops.vsini_max
-x = map.ops.get_x(vsini)
-rT = map.ops.get_rT(x)
-kT = map.ops.get_kT0(rT)
-
-# Set up the plot
-fig, ax = plt.subplots(
-    ydeg + 1, 2 * ydeg + 1, figsize=(16, 10), sharex=True, sharey=True
-)
-fig.subplots_adjust(hspace=0)
-for axis in ax.flatten():
-    axis.spines["top"].set_visible(False)
-    axis.spines["right"].set_visible(False)
-    axis.spines["bottom"].set_visible(False)
-    axis.spines["left"].set_visible(False)
-    axis.set_xticks([])
-    axis.set_yticks([])
-
-# Loop over the orders and degrees
-n = 0
-for i, l in enumerate(range(ydeg + 1)):
-    for j, m in enumerate(range(-l, l + 1)):
-        j += ydeg - l
-        ax[i, j].plot(kT[n])
-        n += 1
-
-# Labels
-for j, m in enumerate(range(-ydeg, ydeg + 1)):
-    ax[-1, j].set_xlabel("%d" % m, fontsize=14, alpha=0.5)
-for i, l in enumerate(range(ydeg + 1)):
-    ax[i, ydeg - l].set_ylabel(
-        "%d" % l, fontsize=14, rotation=45, labelpad=20, alpha=0.5
-    )
-
-plt.annotate(
-    r"$\ell$",
-    xy=(0.18, 0.55),
-    xycoords="figure fraction",
-    rotation=45,
-    fontsize=22,
-    alpha=0.5,
-)
-plt.annotate(
-    r"$m$",
-    xy=(0.415, 0.02),
-    ha="center",
-    xycoords="figure fraction",
-    fontsize=20,
-    alpha=0.5,
-    clip_on=False,
-)
-
-# Save
-fig.savefig("kT.pdf", bbox_inches="tight")

### 2022-05-29 src/figures/snr.py

@@ -1,87 +1,0 @@
-"""
-Investigate how our recovered map varies with the
-signal to noise ratio of the data.
-
-"""
-from utils.generate import generate_data
-import starry
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.colors import Normalize
-
-# Settings
-ydeg = 15
-smoothing = 0.075
-
-# Compute model at infinite SNR
-data = generate_data(flux_err=0, ydeg=ydeg, smoothing=smoothing)
-theta = data["data"]["theta"]
-flux = data["data"]["flux"]
-
-# Typical line depth
-signal = 0.2
-
-# Compute the pointwise uncertainty for a given SNR
-snrs = np.array(
-    [10.0, 20.0, 50.0, 100.0, 500.0, 1000.0, 2000.0, 5000.0, 10000.0]
-)
-spatial_cov = np.minimum(1e-4, 1e-4 * (1000 / snrs) ** 2)
-flux_errs = signal / snrs
-
-# Plot the true map
-fig, ax = plt.subplots(4, 3, figsize=(15, 10))
-ax[0, 0].set_visible(False)
-ax[0, 2].set_visible(False)
-map = starry.Map(ydeg=ydeg)
-map.load("spot", smoothing=smoothing)
-map.show(ax=ax[0, 1], projection="moll")
-ax[0, 1].annotate(
-    r"true",
-    xy=(0, 1),
-    xytext=(7, 7),
-    clip_on=False,
-    xycoords="axes fraction",
-    textcoords="offset points",
-    ha="left",
-    va="top",
-    fontsize=14,
-    color="k",
-    zorder=101,
-)
-ax[0, 1].set_rasterization_zorder(0)
-
-# Instantiate the map we'll use for inference
-map = starry.DopplerMap(lazy=False, **data["kwargs"])
-map.spectrum = data["truths"]["spectrum"]
-for n in range(map.udeg):
-    map[1 + n] = data["props"]["u"][n]
-
-# Solve & plot
-ax = ax[1:].flatten()
-for i, flux_err in enumerate(flux_errs):
-
-    soln = map.solve(
-        flux + flux_err * np.random.randn(*flux.shape),
-        theta=theta,
-        normalized=True,
-        fix_spectrum=True,
-        flux_err=flux_err,
-        spatial_cov=spatial_cov[i],
-    )
-
-    map.show(ax=ax[i], projection="moll", norm=Normalize(vmin=0, vmax=0.5))
[…]

### 2022-05-29 src/figures/spot_infer_ybs_low_snr.py

@@ -1,78 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Setup for the SPOT problem.
-
-"""
-from utils.generate import generate_data
-from utils.plot import plot_timeseries, plot_maps, plot_spectra
-import starry
-import numpy as np
-import os
-
-
-# Generate the synthetic dataset
-data = generate_data(flux_err=2e-3)
-y_true = data["truths"]["y"]
-spectrum_true = data["truths"]["spectrum"].reshape(-1)
-theta = data["data"]["theta"]
-flux = data["data"]["flux"]
-flux_err = data["data"]["flux_err"]
-
-# Instantiate the map
-map = starry.DopplerMap(lazy=False, **data["kwargs"])
-for n in range(map.udeg):
-    map[1 + n] = data["props"]["u"][n]
-
-# Solve for the Ylm coeffs and the spectrum
-soln = map.solve(
-    flux,
-    theta=theta,
-    normalized=True,
-    flux_err=flux_err,
-    spectral_lambda=1e4,
-    spectral_cov=2e-2,
-    spatial_cov=2e-4,
-    quiet=os.getenv("CI", "false") == "true",
-)
-
-# Get the inferred map and spectrum
-y_inferred = map.y
-wav0 = map.wav0
-wav = map.wav
-spectrum_inferred = map.spectrum.reshape(-1)
-
-# Compute the Ylm expansion of the posterior standard deviation field
-P = map.sht_matrix(inverse=True)
-Q = map.sht_matrix()
-L = np.tril(soln["cho_ycov"])
-W = P @ L
-y_uncert = Q @ np.sqrt(np.diag(W @ W.T))
-
-# Get the spectrum guess &  uncertainty
-M = np.array(map._S0i2eTr.todense())  # converts from wav0_ grid to wav0 grid
-spectrum_guess = (soln["spectrum_guess"] @ M).reshape(-1)
-L = np.tril(soln["cho_scov"])
-spectrum_uncert = (np.sqrt(np.diag(L @ L.T)) @ M).reshape(-1)
-
-# Plot the maps
-fig = plot_maps(y_true, y_inferred, y_uncert)
-fig.savefig("spot_infer_ybs_low_snr_maps.pdf", bbox_inches="tight", dpi=150)
-
-# Plot the spectra
-fig = plot_spectra(
-    wav,
-    wav0,
-    spectrum_true,
-    spectrum_guess,
[…]

### 2022-05-29 src/figures/utils/__init__.py

@@ -1,1 +1,0 @@
-from . import generate, plot

### 2022-05-29 src/scripts/kT00.py

@@ -1,0 +1,24 @@
+# -*- coding: utf-8 -*-
+"""
+Plots the first term of the convolution kernel.
+
+"""
+from utils import patch_theano
+import matplotlib.pyplot as plt
+import starry
+import paths
+
+# Get the first term in the kernel
+map = starry.DopplerMap(1)
+vsini = map.ops.vsini_max
+x = map.ops.get_x(vsini)
+rT = map.ops.get_rT(x)
+kT = map.ops.get_kT0(rT)
+kT00 = kT[0]
+
+fig, ax = plt.subplots(1, figsize=(0.5, 0.25))
+fig.subplots_adjust(left=0, right=1, bottom=0, top=1)
+ax.plot(kT00)
+ax.axis("off")
+ax.margins(0.2, 0.2)
+fig.savefig(paths.figures / "kT00.pdf", dpi=500)

### 2022-05-29 src/scripts/runtime.py

@@ -1,0 +1,119 @@
+from utils import patch_theano
+import starry
+import numpy as np
+import matplotlib.pyplot as plt
+import time
+import os
+from tqdm import tqdm
+import paths
+
+
+starry.config.quiet = True
+ntimes = 100
+alpha = 0.05
+
+
+def timeit(ydeg=10, nt=10, nw=100, vsini=50000.0):
+    wav = np.linspace(642.85, 643.15, nw)
+    wav0 = np.linspace(642.00, 644.00, nw)
+    map = starry.DopplerMap(
+        ydeg=ydeg, nt=nt, wav=wav, wav0=wav0, lazy=False, vsini_max=vsini
+    )
+    map.spectrum = np.random.random(map.nw0)
+    map[:, :] = np.random.randn(map.Ny)
+    flux = map.flux()
+    times = np.zeros(ntimes)
+    for n in range(ntimes):
+        start = time.time()
+        flux = map.flux()
+        times[n] = time.time() - start
+    return times * 1e3
+
+
+# Set up
+fig, ax = plt.subplots(2, 2, sharey=True, figsize=(8, 4))
+fig.subplots_adjust(hspace=0.4, wspace=0.1)
+ax[0, 0].set_ylim(0, 25)
+
+
+# Versus spherical harmonic degree
+ydegs = np.arange(1, 21)
+times = np.zeros((len(ydegs), ntimes))
+for n, ydeg in tqdm(
+    enumerate(ydegs),
+    total=len(ydegs),
+    disable=os.getenv("CI", "false") == "true",
+):
+    times[n] = timeit(ydeg=ydeg)
+ax[0, 0].plot(ydegs, times, "C0-", lw=1, alpha=alpha)
+ax[0, 0].plot(ydegs, np.median(times, axis=1), "C0-", lw=2)
+ax[0, 0].set_xlabel("spherical harmonic degree", fontsize=12)
+ax[0, 0].set_xticks([0, 5, 10, 15, 20])
+ax[0, 0].set_xlim(0, 20)
+ax[0, 0].set_yticks([0, 5, 10, 15, 20, 25])
+
+# Versus number of epochs
+nts = np.array(np.linspace(1, 51, 20), dtype=int)
+times = np.zeros((len(nts), ntimes))
+for n, nt in tqdm(
+    enumerate(nts),
+    total=len(nts),
[…]

### 2022-05-29 src/scripts/spot_infer_y.py

@@ -1,0 +1,59 @@
+# -*- coding: utf-8 -*-
+"""
+Setup for the SPOT problem.
+
+"""
+from utils import patch_theano
+from utils.generate import generate_data
+from utils.plot import plot_timeseries, plot_maps
+import starry
+import numpy as np
+import os
+import paths
+
+
+# Generate the synthetic dataset
+data = generate_data()
+y_true = data["truths"]["y"]
+spectrum_true = data["truths"]["spectrum"]
+theta = data["data"]["theta"]
+flux = data["data"]["flux0"]
+flux_err = data["data"]["flux0_err"]
+
+# Instantiate the map
+map = starry.DopplerMap(lazy=False, **data["kwargs"])
+map.spectrum = data["truths"]["spectrum"]
+for n in range(map.udeg):
+    map[1 + n] = data["props"]["u"][n]
+
+# Solve for the Ylm coeffs
+soln = map.solve(
+    flux,
+    theta=theta,
+    normalized=False,
+    fix_spectrum=True,
+    flux_err=flux_err,
+    quiet=os.getenv("CI", "false") == "true",
+)
+
+# Get the inferred map
+y_inferred = map.y
+
+# Compute the Ylm expansion of the posterior standard deviation field
+P = map.sht_matrix(inverse=True)
+Q = map.sht_matrix()
+L = np.tril(soln["cho_ycov"])
+W = P @ L
+y_uncert = Q @ np.sqrt(np.diag(W @ W.T))
+
+# Plot the maps
+fig = plot_maps(y_true, y_inferred, y_uncert)
+fig.savefig(
+    paths.figures / "spot_infer_y_maps.pdf", bbox_inches="tight", dpi=150
+)
+
+# Plot the timeseries
+fig = plot_timeseries(data, y_inferred, spectrum_true, normalized=False)
+fig.savefig(
+    paths.figures / "spot_infer_y_timeseries.pdf", bbox_inches="tight", dpi=300
+)

### 2022-05-29 src/scripts/utils/__init__.py

@@ -1,0 +1,1 @@
+from . import generate, plot, patch_theano

### 2022-05-29 src/scripts/luhman16b_plot.py
upgrade to new syw

@@ -1,0 +1,133 @@
+import paths
+import matplotlib.pyplot as plt
+from matplotlib.colors import Normalize
+
+
+# Set up the model
+exec(open(paths.scripts / "luhman16b_model.py").read())
+
+# Load
+solution = np.load(paths.data / "luhman16b_solution.npz", allow_pickle=True)
+loss = solution["loss"]
+map_soln = solution["map_soln"].item()
+
+# Plot the loss
+fig, ax = plt.subplots(1, figsize=(5, 5))
+ax.plot(loss)
+ax.set_xlabel("iteration number")
+ax.set_ylabel("loss")
+fig.savefig(paths.figures / "luhman16b_loss.pdf", bbox_inches="tight")
+
+# Plot the rest frame spectra
+fig, ax = plt.subplots(4, figsize=(18, 10), sharey=True)
+with model:
+    for c in range(4):
+        # Mask breaks in the spectrum
+        # so matplotlib doesn't linearly
+        # interpolate
+        dw = np.diff(wav0[c])
+        dwm = np.mean(dw)
+        dws = np.std(dw)
+        x = np.array(wav0[c])
+        x[1:][np.abs(dw - dwm) > 3 * dws] = np.nan
+        ax[c].plot(x, mean_spectrum[c], label="template")
+        ax[c].plot(
+            x, pmx.eval_in_model(spectrum[c], point=map_soln), label="MAP"
+        )
+        ax[c].set_ylabel("intensity")
+        ax[c].margins(0, None)
+ax[0].legend(loc="lower left")
+ax[-1].set_xlabel(r"$\lambda$ [nm]", fontsize=16)
+fig.savefig(paths.figures / "luhman16b_spectra.pdf", bbox_inches="tight")
+
+# Plot the data & model
+fig, ax = plt.subplots(1, 4, figsize=(16, 10), sharey=True)
+fig.subplots_adjust(wspace=0.1)
+with model:
+    for c in range(4):
+        # Mask breaks in the spectrum
+        # so matplotlib doesn't linearly
+        # interpolate
+        dw = np.diff(wav[c])
+        dwm = np.mean(dw)
+        dws = np.std(dw)
+        x = np.array(wav[c])
+        x[1:][np.abs(dw - dwm) > 3 * dws] = np.nan
+        for k in range(14):
[…]
